### 2011-06-10 Text/paper.tex
Working on mass transfer. Results are coming soon.

\documentclass{article}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{tabularx}
\begin{document}
\section{Motivation}
The mass transfer is a very important characteristic for design of the microchannels. It allows to
properly understand the properties of the channel length, channel length to microchannel ratios. In
what follows the mass transfer associated with the bubble moving in the microchannel through liquid
medium.

A few questions need to be addressed:
\begin{description}
 \item[I] The efficiency of the mass transfer depending on the capillary number. For small capillary
numbers as $Ca<0.6$ for square microchannels there is a vortex in the moving with the bubble
reference frame, which certainly will improve the corresponding mass transfer. Note that the flow
patterns highly depend on the number of parameters as the slug length, the thickness of the
thickness and the existence of the vortex in front of the bubble. There are some available
correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
this study is to study mass transfer dependence on the number of parameters. As well to validate or
to come up with another correlation describing the mass transfer.

 \item[II] Another important quantity is to study the mixing processes inside the slug. One of the
possible characteristics of the mixing is a residence time distribution. Once the step function
of tracer is introduced in the liquid film, then the concentration of tracer with time is
measured at the outlet. The form of the signal and especially its standard deviation is responsible
for mixing. However, from numerical point of view this study requires the repetition of domain a
few times to see the tracer propagation. Thus, we do not currently address mixing with our
simulations.
\end{description}

To address the questions arised we will utilize the results of numerical simulations of flow
obtained
before \cite{kuzmin-binary2d}. The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
the same figure, one can see the proposed benchmark for the concentration profile. The physical
picture for the proposed numerical benchmark is  related to classical experiments conducted by
\citet{bercic-mass}. In their work authors studied gas-liquid mass transfer coefficient by
injecting methane as the gas bubble and measuring the dissolved concentration of methane in water
along the channel. This situation implies the periodic boundary conditions and steady-state motion
of bubbles.

The numerical  procedure of studying mass transfer is presented in the following steps:
\begin{description}
 \item[Flow field] The hydrodynamics for the bubble motion in the periodic domain is obtained
according to the work \cite{kuzmin-binary2d}. The grid resolution is taken to insure grid
independency of results.  
 \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
are conducted in the moving
reference frame with the bubble. Then the bubble stands still and the flow is coming around the
bubble. We impose a steady concentration of solutant on the surface of the bubble.
\item[Mass transfer] One needs not only perform a Galilean transformation to the moving reference
frame of the bubble but also to
transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
slug. 
\end{description}
\begin{figure}
\includegraphics[width=\textwidth]{Figures/benchmark_new.eps}\\
\\
\\
\\
\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}
\caption{The two-dimensional benchmarks for the hydrodynamics (top) and the mass transfer
coefficient (bottom). \label{fig:benchmark}}
\end{figure}

\section{Parameters choice}
In what follows we want to address the following empirical correlation addressed in the recent
publication by \citet{yue-mass}:
\begin{equation}
k_L a=\frac{2}{d_h} \Bigl(\frac{D
U_{\mathrm{bubble}}}{L_{\mathrm{bubble}}+L_{\mathrm{slug}}}\Bigr)^{0.5}
\Bigl(\frac{L_{\mathrm{bubble}}}{L_{\mathrm{bubble}}+L_{\mathrm{slug}}}\Bigr)^{0.3}.
\end{equation}
This correlation is within $10\%$ accuracy for experimental results within the following range of
parameters: $0.4\,\mathrm{m/s}<U_{\mathrm{bubble}}<2\,\mathrm{m/s}$,
$1.4<\frac{L_{\mathrm{bubble}}}{d_h}<6.3$, $1<\frac{L_{\mathrm{slug}}}{d_h}<3.2$, $d_h = 400
\mathrm{\mu m}$.

For long slug lengths in circular capillaries the folowing correlation is derived by
\citet{bercic-mass}:
\begin{equation}
k_L a = \frac{0.111
(j_{\mathrm{gas}}+j_{\mathrm{liq}})^{1.19}}{\bigl((1-\varepsilon_{\mathrm{gas}})(L_{\mathrm{bubble}}
+L_ {\mathrm{slug}} )\bigr)^{0.57} },
\end{equation}
where $\varepsilon_{\mathrm{gas}}=\frac{U_{\mathrm{gas}}}{U_{\mathrm{bubble}}}$ is the gas holdup,
$j_{\mathrm{gas}}=U_{\mathrm{gas}} \pi R^2$ is the volumetric gas flow rate,
$j_{\mathrm{liq}}=U_{\mathrm{liq}} \pi R^2$ is the volumetric liquid flow rate. In their
experiments \citeauthor{bercic-mass} dealt with long slug lengths. Thus, they concluded that the
mass transfer from bubble caps was predominant.

\citet{vanbaten-circular} performed numerical simulations for circular capillaries by assuming that
there is a separate contribution of the liquid film and the bubble caps to mass transfer. Their
correlation is as:
\begin{equation}
k_L a = \frac{2}{\sqrt{\pi}}\sqrt{\frac{D U_{\mathrm{bubble}}}{(L_{\mathrm{bubble}}-d_h)}}
\frac{4(L_{\mathrm{bubble}}-d_h)}{d_h(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}+2\frac{\sqrt{2}}{\pi}
 \sqrt{\frac{D U_{\mathrm{bubble}}}{d_h}} \frac{4}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}
\end{equation}
This correlation is valid for short contact times, when the mass transfer is important from bubble
caps as well as from the film. Short contact times are defined through Fourier number as:
\begin{equation}
Fo=\frac{D t_{\mathrm{film}}}{\delta^2},
\end{equation}
where $t_{\mathrm{film}}=\frac{L_{\mathrm{film}}}{U_{\mathrm{bubble}}}$ is the time exposure of the
bubble while it propagates through distance $L_{\mathrm{film}}$.

Our goal is to compare numerical simulations with given correlations.

\section{Mass transfer}
The mass transfer is characterized by non-dimensional numbers as Schmidt number (viscous diffusion
rate over the mass diffusion rate), the Peclet number (convection over diffusion) and the Sherwood
number (convection mass transfer over the diffusion mass transfer):
\begin{equation}
\begin{aligned}
&Pe=\frac{U L}{D}\\
&Sh=\frac{K L}{D}\\
&Sc=\frac{\nu}{D}\\
\end{aligned}
\end{equation}

As far as parameters of the lattice Boltzmann system are not connected with real ones, one needs to
match the non-dimensional parameters with physical one.  One of the particular examples is the
work by \citet{bercic-mass} who used the methane dissolution to characterize the mass transfer for
bubble train flow. Thus, assumption for periodic boundary conditions stays.

In what follows we will perform the matching of obtained hydrodynamics results
\cite{kuzmin-binary2d} with physical ones from experiment of \citet{bercic-mass}. The diffusion
coefficient of the methane under standard conditions \cite{methane-properties} is
$1.84\times 10^{-5} \mathrm{cm}^2/\mathrm{s}$. The diameters of capillaries were as $1.5$, $2.5$ and
$3.1$ $\mathrm{mm}$. For simplicity reasons we will choose the diameter of capillary as $1.5\,
\mathrm{mm}$. 
We will match parameters through given non-dimensional numbers. From the hydrodynamics
simulations the following parameters supplied:
\begin{equation}
\begin{aligned}
Ca=\frac{U \mu_{\mathrm{liq}}}{\gamma}\\
Re=\frac{\rho_{\mathrm{liq}} U L}{\mu_{\mathrm{liq}}}.
\end{aligned}
\end{equation}
From these two equation one can obtain the physical velocity obtained from non-dimensional numbers:
\begin{equation}
\begin{aligned}
Ca\cdot Re= \frac{\rho_{\mathrm{liq}} U^2 L}{\gamma}\\
U=\sqrt{\frac{Ca\,Re\,\gamma}{\rho_{\mathrm{liq}}L}}
\end{aligned}
\end{equation}

Assuming that the surface tension of water is $0.0728\,\mathrm{N/m}$, the density is
$1000\,\mathrm{kg/m^3}$,the hydraulic diameter of the channel to be $1.5\,\mathrm{mm}$ one can
calculate the physical velocity of the bubble.
Table \ref{table:twod:simulations} represents the number of simulations runs for the grid as
$202\times 3002$ and its nondimensional parameters. One can see that velocity is quite reasonable
as \citet{bercic-mass} declared that experiments were conducted for velocities in the ranges of
$0.01$ to $0.4\,\mathrm{m}/\mathrm{s}$ but for less capillary numbers. 
\begin{table}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
$Ca$&$Re$&$U_{LB}$&$\delta$&$U_{\mathrm{phys}}\mathrm{m/s}$ \\
$0.026$ &$0.449$  &$0.0014$ &$0.040$&$0.023$\\  
$0.047$ &$0.820$  &$0.0027$ &$0.058$&$0.043$\\ 
$0.080$ &$1.378$  &$0.0045$ &$0.085$&$0.073$\\
$0.065$ &$1.126$  &$0.0037$ &$0.076$&$0.059$\\
$0.222$ &$3.807$  &$0.0125$ &$0.122$&$0.202$\\  
$0.479$ &$8.222$  &$0.0271$ &$0.151$&$0.437$\\
$0.736$ &$12.617$ &$0.0416$ &$0.164$&$0.671$\\ 
$0.989$ &$16.960$ &$0.0559$ &$0.172$&$0.902$\\
\end{tabularx}\caption{Two-dimensional simulations for different
capillary numbers. \label{table:twod:simulations}}
\end{table}

\section{Lattice Boltzmann implementation}
For the lattice Boltzmann implementation we took $\omega=1.99$ which results in the following
lattice Boltzmann diffusivity parameter:
\begin{equation}
\begin{aligned}
&D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)\\
&D=0.0008375
\end{aligned}
\end{equation}
In terms of Schmidt number (taking the liquid viscosity in former simulations as $\frac{2}{3}$) that
can result in:
\begin{equation}
\begin{aligned}
&Sc=\frac{\nu_{\mathrm{liq}}}{D}\\
&Sc=796\\
\end{aligned}
\end{equation}
Taking the water as $8.9 \times 10^{-4}\,\mathrm{Pa\cdot s}$ or kinematic viscosity as $8.9 \times
10^{-7} \,\mathrm{m^2/s}$ and the Schmidt number as $796$ that results in the following quantity:
\begin{equation}
D=1.118\times 10^{-5}\,\mathrm{cm^2/s},
\end{equation}
which is less than the diffusivity of the methane $1.84\times 10^{-5}\,\mathrm{cm^2/s}$ but is
physical. After calculation of physical parameters one can calculate characteristics for the mass
theoretical mass transfer. Table \ref{table:lengths} gives nondimensional and physical lengths of a
bubble and a slug.
\begin{table}
\begin{tabularx}{\textwidth}{|X|X|}
Bubbl length& Slug Length\\
5.225&9.775\\
5.22&9.78\\
5.215&9.785\\
4.965&10.035\\
5.25&9.75\\
5.565&9.435\\
5.51&9.49\\
5.505&9.495\\
\end{tabularx}
\caption{The nondimensional to the height of the channel and physical lengths for the same lattice
Boltzmann simulations as in Table \ref{table:twod:simulations}. \label{table:lengths}}
\end{table}

Then the diffusion penetration length is:
\begin{equation}
\delta_{penetration}=\sqrt{D t_{film}}=\sqrt{\frac{D L_{bubble}}{U_{bubble}}}.
\end{equation}
The bubble length is $5$ of diameters. Thus, the bubble length is $7.5\,\mathrm{mm}$. Therefore:
\begin{equation}
\delta_{penetration}=\sqrt{\frac{1.84 10^{-9} \mathrm{m^2/s} 7.5 10^{-3} \mathrm{m}}{4.3 \time
10^{-2}\mathrm{m/s}}}=1.8 \times 10^{-5}
\end{equation}
With the given value of $200$ nodes to resolve the diameter for the given simulation, that results
in $2.4$ nodes, which is small but considerable number to conduct the simulation.
Foirier number which is defined as:
\begin{equation}
Fo=\frac{D t_{film}}{\delta_{film}^2}=\frac{1.84\times 10^{-9} 0.1744}{\times
(8.7\times10^{-5})^2}=0.0423
\end{equation}
As it is indicated by \citet{vanbaten-circular} the Fourier number $Fo<0.1$ stays for short
contact, the film is unsaturated. 
Thus, one can calculate the corresponding parameters:
\begin{equation}
Pe_{min}=\frac{10^{-2} 1.5 10^{-3}}{1.84  10^{-9}}=0.81 \times 10^{4}\gg 1
Sc_{min}=\frac{10^{-6}}{1.84 10^{-9}}=543,
\end{equation}
which imply the Reynolds number to be as:
\begin{equation}
Pe=Re Sc,\,Re=Pe/Sc=14.91
\end{equation}

The Schmidt number $Sc \approx 500$ states for dye in the liquid and assumes the dominance of
convection over diffusion. In terms of the lattice Boltzmann system, the liquid viscosity equals to
$\frac{1}{3}(\tau_{liq}-\frac{1}{2})=\frac{2}{3}$. That means that the relaxation rate for the
advection-diffusion equation should be as:
\begin{equation}
\frac{1}{3}\Bigl(\tau_{\phi}-\frac{1}{2}\Bigr)=\frac{\nu}{Sc}\\
\tau_{\phi}=0.50368,
\end{equation}
which is hard to simulate with the lattice Boltzmann equation, but possible . As it was discussed
\cite{giavedoni-numerical} the inertia can be neglected for the Reynolds number $Re<70$ for bubble
configuration, but not for the hydrodynamics simulations.

The easy way to do is not to match the Peclet number $Pe$ along with the Reynolds number, leaving
only matching the Schmidt number. However, the thorough study needs to be conducted to perform the
matching parameters as $Ca$, $Re$, $Sc$ and $Pe$ numbers.

If we match only the Peclet number then the Reynolds number can be changed as to adjust the
velocity multiplied on coefficient, keeping Reynolds number small and anticipating results to see.

\section{LBM implementation}

\appendix

\section{Boundary conditions}
In what follows we will examine different LBM implementations:
\begin{description}
 \item[BB conditions] The walls can be treated via the simple bounce back rule:
\begin{equation}
f_{\bar{i}B}=f_{iF},\text{ for } \forall i,
\end{equation}
where $B$ is the boundary node with coordinates $\bm{r_F}+\bm{c_i}$, $F$ is the fluid node. This
will fulfill the macroscopic conditions as:
\begin{equation}
J_{fluid}= \sum_{c_i\cdot n>0}{f_i c_i}=J_{wall},
\end{equation}
which is in turn represents the following boundary condition:
\begin{equation}
\partial_n J_n=\partial_n C u_n = u_n \partial_n C=0
\end{equation}

The walls can be treated through simmetric boundary conditions as well, which are really close to
bounce-back formulation. In this case one can insure that the concentration values at the wall and
at the fluid equal to each other.

For the constant concentration at the bubble surface one can use the pressure anti
bounce-back conditions
\cite{ginzburg-boundary-main}:
\begin{equation}
f_{iB}=-f^{*}_{iF}+2 e_i(W),
\end{equation}
where the subscript $*$ stands for after-collision population, $W$ stands for the wall
concentration to be imposed.
\item[Inamuro conditions] Inamuro boundary conditions impose strict conservation of the population
by utilizing diffuse interface kinetic boundary approach \cite{inamuro-scalar-boundary}. The
unknown populations $f_i=w_i \rho^{\prime}\text{ for } \bm{c_i}\cdot \bm{n}>0$ are prescribed
through the equilibrium conditions, where $\rho^{\prime}$ is an unknown parameter.Then the
prescribed wall condition is as: 
\begin{equation}
\rho^{\prime}=\frac{\rho_{w}-\sum_{i,\bm{c_i}\cdot\bm{n}\leq0}
f_i}{\sum_{i,\bm{c_i}\cdot\bm{n}>0}w_i}
\end{equation}
For the zero flux on the wall one can use another equation:
\begin{equation}
\rho^{\prime}=-\frac{i,\bm{c_i}\cdot\bm{n}\leq0}{\sum_{i,\bm{c_i}\cdot \bm{n}}{w_i \bm{c_i}\cdot
\bm{n}}}.
\end{equation}
\end{description}

\section{TRT $D2Q9$ model. Equilibrium functions}
One of the advantages of $D2Q9$ TRT model in comparison with $D2Q5$ usually used for simulations of
the advection-diffusion model is that $D2Q9$ is able to reduce numerical diffusion from diagonal
and non-diagonal diffusion tensor components \cite{kuzmin-stability-optimal}.

In
comparison with the BGK collision operator the TRT collision operator \cite{ginzburg-boundary-main}
decomposes the populations and the equilibrium
distribution into the symmetric and antisymmetric parts:
\begin{equation}
\label{trtdecomp}
f^{\pm}_i=\frac{f_i\pm f_{\bar{i}}}{2}\;,\; 
{eq_i}^{\pm}=\frac{eq_i\pm eq_{\bar{i}}}{2}\;,
\end{equation}
where $\bar{i}$ is the opposite direction to the $i$-th direction.
The collision is performed with two independent relaxation rates for 
symmetric and antisymmetric modes:
\begin{equation}
\label{trt}
\begin{aligned}
&f_i^{*}(\bm{x},t)=f_i(\bm{x},t)-\omega_{+} (f_i^{+} - eq_i^+)-\omega_{-}
(f_i^{-} -
eq_i^-)\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t).
\end{aligned}
\end{equation}
Note that the BGK collision operator is the particular subclass of the TRT relaxation operator with
$\omega_{+}=\omega_{-}$. In comparison with the BGK collision operator,
the TRT collision operator has the additional degree of freedom. Thus, the TRT operator then
introduces
so-called magic (free) parameter
$\Lambda=\Bigl(\frac{1}{\omega_{+}}-\frac{1}{2}\Bigr)\Bigl(\frac{1}{\omega_{-}}-\frac{1}{2}\Bigr)$. 
This free parameter controls the effective location of the bounce-back
walls \cite{ginzburg-multireflection}, second-order accuracy of
boundary \cite{ginzburg-boundary-main} and interface schemes \cite{ginzburg-discontinious}, 
spatial accuracy \cite{ginzburg-recurrence,servan-trt-stability},
consistency \cite{ginzburg-brinkman} and, to some extent,
stability \cite{kuzmin-stability-optimal,kuzmin-d1q3,servan-trt-stability}.
In particular, $\Lambda=\frac{1}{4}$ achieves the optimal stability for the
linear advection-diffusion isotropic equation \cite{kuzmin-stability-optimal}.

The equilibrium functions for $D2Q9$ TRT model are represented as \cite{kuzmin-stability-optimal}:
\begin{equation}
\begin{aligned}
&eq_i^{+}=eq_i^{(m)}+g^{(u)} eq_i^{(u)}\\
&eq_i^{(m)}=t_i^{(m)} c_e+ eq_i^{(a)}\\
&eq_i^{(u)}=t_i^{(u)} \frac{u_x^2+u_y^2}{2}+\frac{u_x^2-u_y^2}{4} p_i^{(xx)}+g_{xy}^{(u)}\frac{u_x
u_y}{4} p_i^{xy}\\
&eq_i^{(a)}=\frac{D_{xx}-D_{yy}}{4} p_i^{xx}+\frac{D_{xy}}{4} p_i^{(xy)},
\end{aligned}
\end{equation}
where $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$ and $p_i^{(xy)}=c_{ix} c_{iy}$.

The following equilibrium functions solve the anisotropic advection-diffusion equation with the
following diffusion tensor:
\begin{equation}
D=
\begin{pmatrix}
D_{xx} + (g^{(u)}-1) u_x^2 & D_{xy}+(g_{xy}^{(u)}-1)u_x u_y\\
D_{xy} + (g_{xy}^{(u)}-1) u_x u_y& D_{yy}+(g^{(u)}-1) u_y^2 
\end{pmatrix}
\end{equation}
To consider the situation when the resolution is not needed to be changed in $x$ and $y$
directions, one can obtain that $D_{xx}=D_{yy}$. The cross-diagonal components of the diffusion
tensor are taken as zeros, i.e. $D_{xy}=0$. The numerical diffusion can be avoided by proper choice
of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$.

As far as the simulated diffusion tensor is close to $0$ the stability limits restrict the velocity
amplitude to be simulated \cite{kuzmin-stability-optimal}. However, particular choice of weights
can drastically help. Fig. \ref{stability:d2q9} shows the stability limits for D2Q9 with removed
numerical diffusion and with it for two particular choices of weights.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
\caption{The non-negativity areas and stable sub-domains of the OTRT schemes ($\Lambda=\frac{1}{4}$)
are plotted for the $D2Q9$ (standard weights, left) and the $D2Q9$ (uniform weights, right) when the
numerical diffusion is removed, partially or completely. Two non-negativity areas where all the
equilibrium populations are positive have curvilinear boundaries: they are smaller when
$g^{(u)}_{xy}=0$ (yellow) and than when $g^{(u)}_{xy}=1$ (green+yellow). The non-negativity
condition is required by BGK collision operator. The stable sub-domains for $g^{(u)} = 1,
g^{(u)}_{xy} = 0$ are small (red+green+yellow) triangles. When the numerical diffusion is removed
the stable area is bounded by magenta and the (blue) domain above. The proper choice of weights can
allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1−c_e$ (the
uniform weights only).
\label{stability:d2q9}}
\end{figure}

From here on we will use the standard weights as:
\begin{equation}
t_i^{(u)}=t_i^{(m)}=t_i^{(a)}=\Bigl\{0,\frac{1}{3},\frac{1}{3},\frac{1}{3},\frac{1}{3},\frac{1}{12},
\frac {1}{12},\frac{1}{12},\frac{1}{12}\Bigr\}
\end{equation}

\subsection{LBM derivation}

\bibliographystyle{unsrtnat}
\bibliography{paper}

\end{document}

### 2011-06-11 Text/paper.tex
Started analysis of codes results. Not very nice steady state.

@@
 \end{description}
-\begin{figure}
+\begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/benchmark_new.eps}\\
@@
 k_L a = \frac{0.111
-(j_{\mathrm{gas}}+j_{\mathrm{liq}})^{1.19}}{\bigl((1-\varepsilon_{\mathrm{gas}})(L_{\mathrm{bubble}}
+(U_{\mathrm{gas}}+U_{\mathrm{liq}})^{1.19}}{\bigl((1-\varepsilon_{\mathrm{gas}})(L_{\mathrm{bubble}}
 +L_ {\mathrm{slug}} )\bigr)^{0.57} },
@@
 where $\varepsilon_{\mathrm{gas}}=\frac{U_{\mathrm{gas}}}{U_{\mathrm{bubble}}}$ is the gas holdup,
-$j_{\mathrm{gas}}=U_{\mathrm{gas}} \pi R^2$ is the volumetric gas flow rate,
-$j_{\mathrm{liq}}=U_{\mathrm{liq}} \pi R^2$ is the volumetric liquid flow rate. In their
-experiments \citeauthor{bercic-mass} dealt with long slug lengths. Thus, they concluded that the
-mass transfer from bubble caps was predominant.
+$U_{\mathrm{gas}}$ is the superficial gas velocity, and $U_{\mathrm{liq}}$ is the superficial
+liquid velocity. The superficial liquid velocity is calculated with the steady state condition in
+the middle of the slug as:
+\begin{equation}
+U_{\mathrm{liq}}=\frac{\oint U \mathrm{d}A}{A}.
+\end{equation}
+The superficial liquid velocity can be calculated through the calculated bubble volume and gas
+holdup:
+\begin{equation}
+\begin{aligned}
+&\varepsilon_{\mathrm{gas}}=\frac{\text{bubble area}}{15 H^2}\\
+&U_{\mathrm{gas}}=\varepsilon_{\mathrm{gas}} U_{\mathrm{bubble}}
+\end{aligned}
+\end{equation}
+
+In their experiments \citeauthor{bercic-mass} dealt with long slug lengths.
+Thus, they concluded that the mass transfer from bubble caps was predominant.
 
@@
 \begin{table}
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
-$Ca$&$Re$&$U_{LB}$&$\delta$&$U_{\mathrm{phys}}\mathrm{m/s}$ \\
-$0.026$ &$0.449$  &$0.0014$ &$0.040$&$0.023$\\  
-$0.047$ &$0.820$  &$0.0027$ &$0.058$&$0.043$\\ 
-$0.080$ &$1.378$  &$0.0045$ &$0.085$&$0.073$\\
-$0.065$ &$1.126$  &$0.0037$ &$0.076$&$0.059$\\
-$0.222$ &$3.807$  &$0.0125$ &$0.122$&$0.202$\\  
-$0.479$ &$8.222$  &$0.0271$ &$0.151$&$0.437$\\
-$0.736$ &$12.617$ &$0.0416$ &$0.164$&$0.671$\\ 
-$0.989$ &$16.960$ &$0.0559$ &$0.172$&$0.902$\\
-\end{tabularx}\caption{Two-dimensional simulations for different
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
+$Ca$    &$Re$     &$U_{LB}$ &$\delta$&$\varepsilon_{\mathrm{gas}}$
+&$U_{\mathrm{phys}}\mathrm{m/s}$\\
+$0.026$ &$0.449$  &$0.0014$ &$0.040$ &$0.306$ &$0.023$   \\ 
+$0.047$ &$0.820$  &$0.0027$ &$0.058$ &$0.293$ &$0.043$   \\ 
+$0.080$ &$1.378$  &$0.0045$ &$0.085$ &$0.280$ &$0.073$ \\
+$0.065$ &$1.126$  &$0.0037$ &$0.076$ &$0.266$ &$0.059$      \\
+$0.222$ &$3.807$  &$0.0125$ &$0.122$ &$0.253$ &$0.202$  \\
+$0.479$ &$8.222$  &$0.0271$ &$0.151$ &$0.249$ &$0.437$  \\
+$0.736$ &$12.617$ &$0.0416$ &$0.164$ &$0.236$ &$0.671$  \\ 
+$0.989$ &$16.960$ &$0.0559$ &$0.172$ &$0.230$ &$0.902$  \\
+\end{tabularx}
+\caption{Two-dimensional simulations for different
 capillary numbers. \label{table:twod:simulations}}
@@
 \begin{table}
-\begin{tabularx}{\textwidth}{|X|X|}
-Bubbl length& Slug Length\\
-5.225&9.775\\
-5.22&9.78\\
-5.215&9.785\\
-4.965&10.035\\
-5.25&9.75\\
-5.565&9.435\\
-5.51&9.49\\
-5.505&9.495\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
+\hline
+$Ca$&Bubble length& Slug Length&
+$U_{\mathrm{gas}}\,\mathrm{m/s}$&$U_{\mathrm{liq}}\,\mathrm{m/s}$&$a,\,\mathrm{m^{-1}}$\\
+\hline
+$0.026$&$5.225$&$9.775$ &$0.0070$ &$0.0209$&$2.5538$\\
+$0.047$&$5.22$ &$9.78$  &$0.0126$ &$0.0379$&$2.5431$\\
+$0.080$&$5.215$&$9.785$ &$0.0204$ &$0.0615$&$2.5326$\\
+$0.065$&$4.965$&$10.035$&$0.0157$ &$0.0504$&$2.4142$\\
+$0.222$&$5.25$ &$9.75$  &$0.0511$ &$0.1560$&$2.5253$\\
+$0.479$&$5.565$&$9.435$ &$0.1089$ &$0.3155$&$2.6518$\\
+$0.736$&$5.51$ &$9.49$  &$0.1584$ &$0.4677$&$2.6269$\\
+$0.989$&$5.505$&$9.495$ &$0.2074$ &$0.6190$&$2.6340$\\
+\hline
 \end{tabularx}
-\caption{The nondimensional to the height of the channel and physical lengths for the same lattice
-Boltzmann simulations as in Table \ref{table:twod:simulations}. \label{table:lengths}}
+
+\caption{The nondimensional (scaled to the height of the channel) lengths for the same
+lattice Boltzmann simulations as in Table \ref{table:twod:simulations}. As well superficial
+gas-liquid velocities are presented.\label{table:lengths}}
 \end{table}
 
+The literature correlations of mass transfer dependence on the bubble velocities are presented in
+Fig. \ref{fig:mass:transfer:theoretical}. Note, that the correlations presented in
+Fig.\ref{fig:mass:transfer:theoretical} are used primarily for circular capillaries
+(\citeauthor{vanbaten-circular,bercic-mass}) and for square capillaries (\citeauthor{yue-mass}). We
+adapt these results for flow between parallel plats by using hydraulic
+diameter \cite{bercic-mass} which can be calculated as:
+\begin{equation}
+d_h = \lim_{W\to\infty}\frac{4A}{P}=\lim_{W\to\infty}\frac{4 W\,H}{2(W+H)}=2 H.
+\end{equation}
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}
+\caption{The literature correlations by various authors. One
+can see the large deviation among them.\label{fig:mass:transfer:theoretical}}
+\end{figure}
+
+The volumetric mass transfer coefficient is calculated according to the work of
+\citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
+average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) at time
+$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
+coefficient is calculated as:
+\begin{equation}
+\label{main:simulation:equation}
+k_L a=\frac{\text{Flux}}{C_s-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell volume}},
+\end{equation}
+where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. To properly do
+non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
+inside the lattice Botlzmann system. The time conversion can be easily obtained:
+\begin{equation}
+\begin{aligned}
+U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
+\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
+\Delta t=1.5\,\mathrm{mm} \frac{0.0559}{0.902\,\mathrm{m/s}}=9.3\times 10^{-5}\,\mathrm{s} 
+\end{aligned}
+\end{equation}
+
+The bubble surface length is the perimeter of the bubble in two-dimensional space and it is
+calculated with the extraction of the bubble countour and representing it with the polygon. After
+that the calculated perimeter is the effective summation of line lengths and ca be represented as:
+\begin{equation}
+P=\sum_i{\sqrt{(x2_i-x1_i)^2+(y2_i-y1_i)^2}},
+\end{equation}
+where the index $i$ represents the polyline consisting of two points $(x1,y1)$ and $(x2,y2)$.
+
+The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
+Table \ref{table:lengths}.
+
+\section{Simulation results}
+
+\subsection{Bubble velocity dependence}
+After calculation of the results and using Eq.\ref{main:simulation:equation} One can see the mass
+transfer coefficients indicated in Fig. \ref{}.
+
+\section{To revise:}
 Then the diffusion penetration length is:
@@
 velocity multiplied on coefficient, keeping Reynolds number small and anticipating results to see.
-
-\section{LBM implementation}
 
@@
 numerical diffusion and with it for two particular choices of weights.
-\begin{figure}
+\begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
@@
 
-\subsection{LBM derivation}
-
 \bibliographystyle{unsrtnat}

### 2011-06-11 Python/curves.py

@@ -1,0 +1,68 @@
+#!/usr/bin/python
+import numpy
+import pylab
+import math
+import os
+
+def Produce_Bunch():
+    print os.getcwd()
+    capillary_str=["3","5","8","10","20","40","60","80"]
+
+
+    for dir_temp in capillary_str:
+        dir_name="Results/"+dir_temp
+        name=dir_name+"/concentration.dat"
+        array=numpy.loadtxt(name)
+        #print array
+        new_conc=numpy.array(zip(array[1:,0]-array[:-1,0],array[1:,1]-array[:-1,1],array[1:,2]))
+        print "Data=",new_conc
+        coefficient=new_conc[:,1]/(new_conc[:,0]*(1.0-new_conc[:,2]))
+        pylab.figure()
+        pylab.plot(coefficient)
+
+
+if __name__=="__main__":
+    capillaries=numpy.array([0.026,0.047,0.080,0.065,0.222,0.479,0.736,0.989])
+    bubble_lengths_non=numpy.array([5.225,5.22,5.215,4.965,5.25,5.565,5.51,5.505])
+    slug_lengths_non=numpy.array([9.775,9.78,9.785,10.035,9.75,9.435,9.49,9.495])
+    bubble_velocities=numpy.array([0.023,0.043,0.073,0.059,0.202,0.437,0.671,0.902])
+    holdups=numpy.array([0.3064,0.2935,0.2800,0.2667,0.2532,0.2494,0.2361,0.2300])
+    superficial_liq_lbm=numpy.array([0.00135,0.00238,0.00383,0.00317,0.00970,0.01959,0.02903,0.03841])
+    widths=numpy.array([0.04015,0.05819,0.08552,0.07622,0.12295,0.15123,0.16457,0.17233])
+    velocities_lbm=numpy.array([0.00148,0.00270,0.00454,0.00371,0.01256,0.02713,0.04164,0.05597]) 
+    reynolds=numpy.array([0.449486,0.82096,1.37800,1.12643,3.80721,8.22257,12.61778,16.96062])
+    a=numpy.array([2.55389217042,2.54312761748,2.53266472281,2.41422758192,2.52531357555,2.65187070664,2.62692244618,2.63404014475])
+    diameter=1.5e-3
+    hydraulic=2*diameter
+    bubble_lengths=diameter*bubble_lengths_non
+    slug_lengths=diameter*slug_lengths_non
[…]

### 2011-06-11 Python/get_coordinates.py

@@ -156,6 +156,35 @@ def Get_Zero(prof):
             zero=-(prof[counter]*(counter+1)-prof[counter+1]*counter)/(prof[counter+1]-prof[counter])
     return (zero-0.5)/(len(prof)-2)
 
+def Calculate_Perimeter(phase):
+       #for counter,omega_value in enumerate(omega_int):
+   #     pylab.figure(1) 
+   #     print "Omega=",omega_value 
+   #     filename="PhaseTRTScript/domainomega"+omega_str[omega.index(omega_value)]+"gamma"+gamma_str+"ux"+ux_str[ux.index(ux_value)]+".dat"
+   #     print "Filename=",filename        
+   #     data=numpy.loadtxt(filename)
+   #     #pylab.figure()        
+   #     CS=pylab.contour(x,y,data,[0.5]) #colors=[colors[counter]],linewidths=[4],linestyles=styles[counter])
+   #     path0=CS.collections[0].get_paths()[0]
+   #     cont=path0.vertices
+   #     pylab.figure(2)
+   #     #if counter<3:
+   #     pylab.plot(cont[:,0],cont[:,1],styles[counter],markerfacecolor="None",markersize=counter+10,alpha=0.5)
+    
+    dims=phase.shape
+    #x,y=numpy.mgrid[0:dims[0],0:dims[1]]
+    pylab.figure(99)
+    CS=pylab.contour(phase,[0.0])
+    path0=CS.collections[0].get_paths()[0]
+    cont=path0.vertices
+    perimeter=0    
+    for i,(x,y) in enumerate(cont[:-1]):
+        perimeter+=math.sqrt((x-cont[i+1,0])**2+(y-cont[i+1,1])**2)
+    print "Perimeter=",perimeter
+    print "a=",perimeter/((dims[0]-2)*dims[1]*1.5e-3);
+    #pylab.plot(cont[:,0],cont[:,1],"+")
+
+
 def Get_Bubble(file_name,dir_name):
     
     #fig=pylab.figure()
@@ -202,7 +231,7 @@ def Get_Bubble(file_name,dir_name):
     bubble_reference=-numpy.fliplr(bubble_reference)
     phase=numpy.fliplr(phase)
     vely=numpy.fliplr(vely)
-    
+    Calculate_Perimeter(phase)
     #pylab.figure()
     #pylab.imshow(bubble_reference)
     
@@ -211,6 +240,7 @@ def Get_Bubble(file_name,dir_name):
     
[…]

### 2011-06-15 Text/paper.tex
Some more results

@@
 \citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
-average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) at time
+average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) 
+{\color{red} (In this particular moment I don't know whether to take the Volume of whole domain or
+just the liquid phase. I will go for whole domain.)}
+at time
 $t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
@@
 \end{equation}
-where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. To properly do
+where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
+{\color{red} Do not understand why we need this ratio bubble surface area/unit cell volume. In this
+case the dimensional units do not coincide. In the calculations I will avoid it until further
+clearance.}
+To properly do
 non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
@@
 \begin{aligned}
-U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
-\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
-\Delta t=1.5\,\mathrm{mm} \frac{0.0559}{0.902\,\mathrm{m/s}}=9.3\times 10^{-5}\,\mathrm{s} 
+&U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
+&\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
+&\Delta t=\frac{1.5\,\mathrm{mm}}{200} \frac{0.0559}{0.902\,\mathrm{m/s}}=4.64\times
+10^{-7}\,\mathrm{s} 
 \end{aligned}
@@
 \section{Simulation results}
-
-\subsection{Bubble velocity dependence}
-After calculation of the results and using Eq.\ref{main:simulation:equation} One can see the mass
-transfer coefficients indicated in Fig. \ref{}.
+\subsection{Steady-state}
+Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
+the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
+a steady-state condition the average of  
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/steady_state.eps}
+\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
+state can be reached after $500000$. The mass transfer coefficient is taken as the average from
+$500000$ to $1000000$.\label{fig:steady:state}}
+\end{figure}
 

### 2011-06-15 Python/curves.py

@@ -6,21 +6,27 @@ import os
 
 def Produce_Bunch():
     print os.getcwd()
-    capillary_str=["3","5","8","10","20","40","60","80"]
-
-
-    for dir_temp in capillary_str:
+    capillary_str=["3","5","8","10","20","40"] #,"60","80"]
+    bubble_velocities=numpy.array([0.023,0.043,0.073,0.059,0.202,0.437]) #,0.671,0.902])
+    styles=['kv','ks','ko','k^','k>','k<','kD','kp']
+    
+    fig=pylab.figure(99)
+    for counter,dir_temp in enumerate(capillary_str):
         dir_name="Results/"+dir_temp
         name=dir_name+"/concentration.dat"
         array=numpy.loadtxt(name)
         #print array
         new_conc=numpy.array(zip(array[1:,0]-array[:-1,0],array[1:,1]-array[:-1,1],array[1:,2]))
         print "Data=",new_conc
-        coefficient=new_conc[:,1]/(new_conc[:,0]*(1.0-new_conc[:,2]))
-        pylab.figure()
-        pylab.plot(coefficient)
-
-
+        coefficient=new_conc[:,1]/(200*3000)/(4.64e-7*new_conc[:,0]*(1.0-numpy.abs(new_conc[:,2])))
+        pylab.figure(99)
+        pylab.plot(array[1:,0],coefficient,styles[counter])
+    legs=[r'''$U_{\mathrm{bubble}}='''+str(vel)[:4]+r'''$''' for vel in bubble_velocities]
+    pylab.xlabel('Iterations',fontsize=20)
+    pylab.ylabel(r'''$k_L a, \mathrm{s^{-1}}$''',fontsize=20)
+    pylab.legend(legs,fancybox=True,labelspacing=0.1)
+    pylab.savefig("steady_state.eps",format="EPS",dpi=300)
+    
 if __name__=="__main__":
     capillaries=numpy.array([0.026,0.047,0.080,0.065,0.222,0.479,0.736,0.989])
     bubble_lengths_non=numpy.array([5.225,5.22,5.215,4.965,5.25,5.565,5.51,5.505])
@@ -42,7 +48,8 @@ if __name__=="__main__":
     print "Liquid superficial=",superficial_liquid
     print "Bubble_velocities=",bubble_velocities
     print "Gas_superficial=",superficial_gas
-    diffusion=1.118e-9    
+    diffusion=1.118e-9
[…]

### 2011-07-19 Text/paper.tex
A bit of changes.

@@
 \section{Motivation}
-The mass transfer is a very important characteristic for design of the microchannels. It allows to
-properly understand the properties of the channel length, channel length to microchannel ratios. In
+The mass transfer is a very important characteristic for microchannels  design. It allows to
+properly design a microchannel properties as the channel length, channel length to ensure best possible chemical reactions . In
 what follows the mass transfer associated with the bubble moving in the microchannel through liquid
-medium.
+medium is studied.
 
@@
  \item[I] The efficiency of the mass transfer depending on the capillary number. For small capillary
-numbers as $Ca<0.6$ for square microchannels there is a vortex in the moving with the bubble
-reference frame, which certainly will improve the corresponding mass transfer. Note that the flow
-patterns highly depend on the number of parameters as the slug length, the thickness of the
+numbers as $Ca<0.6$ for square microchannels there is a vortex in the reference frame moving with the bubble, which certainly influences and improves the corresponding mass transfer. 
+Note that the flow
+patterns strongly depend on the number of parameters as the slug length, the thickness of the
 thickness and the existence of the vortex in front of the bubble. There are some available
@@
 \end{equation}
+We as well need to address the concentration being in a whole system non-dimensionalized towards the equilibrium:
+if the domain size is
 
@@
 The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
-Table \ref{table:lengths}.
+Table \ref{table:volumetric:coefficients}.
 
@@
 the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
-a steady-state condition the average of  
+a steady-state condition the average of concentration values between $500000$ to $1000000$ time steps. The values are presented 
 \begin{figure}
@@
 \caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
-state can be reached after $500000$. The mass transfer coefficient is taken as the average from
-$500000$ to $1000000$.\label{fig:steady:state}}
+state can be reached after $500000$. The mass transfer coefficient is taken as the average of concentration values between $500000$ to $1000000$ time steps..\label{fig:steady:state}}
 \end{figure}

### 2011-07-19 Text/paper.tex
Added Eskin's CFD presentation.

@@
 The mass transfer is a very important characteristic for microchannels  design. It allows to
-properly design a microchannel properties as the channel length, channel length to ensure best possible chemical reactions . In
+properly manufacture a microchannel with necessary properties to ensure that chemical
+reactions are performed in the best manner. In
 what follows the mass transfer associated with the bubble moving in the microchannel through liquid
@@
  \item[I] The efficiency of the mass transfer depending on the capillary number. For small capillary
-numbers as $Ca<0.6$ for square microchannels there is a vortex in the reference frame moving with the bubble, which certainly influences and improves the corresponding mass transfer. 
+numbers as $Ca<0.6$ for square microchannels there is a vortex in the reference frame moving with
+the bubble, which  influences and improves the corresponding mass transfer. 
 Note that the flow
@@
 correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
-this study is to study mass transfer dependence on the number of parameters. As well to validate or
-to come up with another correlation describing the mass transfer.
+this work is to study mass transfer dependence on the number of parameters. Another goal is to
+validate and to come up with another correlation describing the mass transfer.
 
@@
 before \cite{kuzmin-binary2d}. The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
-the same figure, one can see the proposed benchmark for the concentration profile. The physical
+the same figure, one can see the proposed benchmark for the tracer. The
+physical
 picture for the proposed numerical benchmark is  related to classical experiments conducted by
@@
 bubble. We impose a steady concentration of solutant on the surface of the bubble.
-\item[Mass transfer] One needs not only perform a Galilean transformation to the moving reference
-frame of the bubble but also to
+\item[Mass transfer] One needs not only perform a Galilean transformation to the reference
+frame moving with the bubble but also to
 transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
@@
 
-\section{Parameters choice}
-In what follows we want to address the following empirical correlation addressed in the recent
+\section{Mass Transfer Correlations}
+We examine the following three characteristic correlations:
+\begin{description}
+\item[I]
+In what follows we want to address the following empirical correlation for the volumetric mass
+transfer coefficient addressed in the recent
 publication by \citet{yue-mass}:
@@
 This correlation is within $10\%$ accuracy for experimental results within the following range of
-parameters: $0.4\,\mathrm{m/s}<U_{\mathrm{bubble}}<2\,\mathrm{m/s}$,
-$1.4<\frac{L_{\mathrm{bubble}}}{d_h}<6.3$, $1<\frac{L_{\mathrm{slug}}}{d_h}<3.2$, $d_h = 400
+parameters: bubble velocity $0.4\,\mathrm{m/s}<U_{\mathrm{bubble}}<2\,\mathrm{m/s}$, bubble length
+$1.4<\frac{L_{\mathrm{bubble}}}{d_h}<6.3$, slug length $1<\frac{L_{\mathrm{slug}}}{d_h}<3.2$,
+hydrodynamic diameter $d_h = 400
 \mathrm{\mu m}$.
 
-For long slug lengths in circular capillaries the folowing correlation is derived by
+For long slug lengths in circular capillaries, where the mass transfer from bubble caps is
+predominant, the folowing correlation is derived by
 \citet{bercic-mass}:
@@
 &\varepsilon_{\mathrm{gas}}=\frac{\text{bubble area}}{15 H^2}\\
-&U_{\mathrm{gas}}=\varepsilon_{\mathrm{gas}} U_{\mathrm{bubble}}
+&U_{\mathrm{gas}}=\varepsilon_{\mathrm{gas}} U_{\mathrm{bubble}}.
 \end{aligned}
@@
 
-In their experiments \citeauthor{bercic-mass} dealt with long slug lengths.
-Thus, they concluded that the mass transfer from bubble caps was predominant.
-
+\item[III]
 \citet{vanbaten-circular} performed numerical simulations for circular capillaries by assuming that
@@
 \frac{4(L_{\mathrm{bubble}}-d_h)}{d_h(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}+2\frac{\sqrt{2}}{\pi}
- \sqrt{\frac{D U_{\mathrm{bubble}}}{d_h}} \frac{4}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}
+ \sqrt{\frac{D U_{\mathrm{bubble}}}{d_h}} \frac{4}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}.
 \end{equation}
@@
 
+\end{description}
 Our goal is to compare numerical simulations with given correlations.
@@
 
-As far as parameters of the lattice Boltzmann system are not connected with real ones, one needs to
-match the non-dimensional parameters with physical one.  One of the particular examples is the
+As far as the lattice Boltzmann method operates only in the non-dimensional space, one needs to
+match the non-dimensional lattice Boltzmann parameters with non-dimensional physical parameters.
+Therefore, one needs to form non-dimensional numbers from the physical parameters. One of the
+particular experiment examples is the
 work by \citet{bercic-mass} who used the methane dissolution to characterize the mass transfer for
-bubble train flow. Thus, assumption for periodic boundary conditions stays.
+bubble train flow.
 

### 2011-07-20 Text/paper.tex
Need to resolve the two-dimensional cap contributions by automodel solutions.

@@
 \section{Mass Transfer Correlations}
+\label{sec:correlations}
 We examine the following three characteristic correlations:
@@
 \end{equation}
-This correlation is within $10\%$ accuracy for experimental results within the following range of
+This correlation is within $10\%$ accuracy for experimental results for the following range of
 parameters: bubble velocity $0.4\,\mathrm{m/s}<U_{\mathrm{bubble}}<2\,\mathrm{m/s}$, bubble length
@@
 
+\item[II]
 For long slug lengths in circular capillaries, where the mass transfer from bubble caps is
@@
 The superficial liquid velocity can be calculated through the calculated bubble volume and gas
-holdup:
+holdup. For the two-dimensional case it is represented as:
 \begin{equation}
@@
 \end{aligned}
+\end{equation}
+
+Since experiments done by \citeauthor{bercic-mass} were only for one diffusivity coefficient
+$D=2\times 10^{-9}\,\mathrm{m^2/s}$, the effective equation should be rescaled as:
+\begin{equation}
+k_L a = \sqrt{\frac{D}{2\times 10^{-9}\,\mathrm{m^2/s}}}\frac{0.111
+(U_{\mathrm{gas}}+U_{\mathrm{liq}})^{1.19}}{\bigl((1-\varepsilon_{\mathrm{gas}})(L_{\mathrm{bubble}}
++L_ {\mathrm{slug}} )\bigr)^{0.57} },
 \end{equation}
@@
 where $t_{\mathrm{film}}=\frac{L_{\mathrm{film}}}{U_{\mathrm{bubble}}}$ is the time exposure of the
-bubble while it propagates through distance $L_{\mathrm{film}}$.
+bubble while it propagates through distance $L_{\mathrm{film}}$. The Fourier number is assumed to
+be small if $Fo<0.1$. If $Fo>1$ then the liquid film is saturated and the mass transfer occurs from
+the bubble caps.
 
 \end{description}
-Our goal is to compare numerical simulations with given correlations.
+
+Overall work goal is to compare numerical simulations with given correlations and to establish a
+new one.
 
@@
 The mass transfer is characterized by non-dimensional numbers as Schmidt number (viscous diffusion
-rate over the mass diffusion rate), the Peclet number (convection over diffusion) and the Sherwood
-number (convection mass transfer over the diffusion mass transfer):
+rate over mass diffusion rate), the Peclet number (convection over diffusion) and the Sherwood
+number (convection mass transfer over diffusion mass transfer):
 \begin{equation}
@@
 coefficient of the methane under standard conditions \cite{methane-properties} is
-$1.84\times 10^{-5} \mathrm{cm}^2/\mathrm{s}$. The diameters of capillaries were as $1.5$, $2.5$ and
-$3.1$ $\mathrm{mm}$. For simplicity reasons we will choose the diameter of capillary as $1.5\,
+$1.84\times 10^{-5} \mathrm{cm}^2/\mathrm{s}$. The diameters of capillaries in the experiment were
+as $1.5$, $2.5$ and
+$3.1\,\mathrm{mm}$. For simplicity reasons we will choose the diameter of capillary as $1.5\,
 \mathrm{mm}$. 
-We will match parameters through given non-dimensional numbers. From the hydrodynamics
-simulations the following parameters supplied:
+The non-dimensional parameters obtained from the hydrodynamics lattice Boltzmann simulations are
+as:
 \begin{equation}
 \begin{aligned}
-Ca=\frac{U \mu_{\mathrm{liq}}}{\gamma}\\
-Re=\frac{\rho_{\mathrm{liq}} U L}{\mu_{\mathrm{liq}}}.
+&Ca=\frac{U \mu_{\mathrm{liq}}}{\gamma}\\
+&Re=\frac{\rho_{\mathrm{liq}} U L}{\mu_{\mathrm{liq}}}.
 \end{aligned}
 \end{equation}
-From these two equation one can obtain the physical velocity obtained from non-dimensional numbers:
+Given some physical characteristics as the liquid density and the channel length,
+one can obtain the physical velocity obtained from non-dimensional numbers:
 \begin{equation}
@@
 
-Assuming that the surface tension of water is $0.0728\,\mathrm{N/m}$, the density is
-$1000\,\mathrm{kg/m^3}$,the hydraulic diameter of the channel to be $1.5\,\mathrm{mm}$ one can
+Assuming that the surface tension of water is $0.0728\,\mathrm{N/m}$ (methane exhibits the same
+trend \cite{schmidt-methane}), the density is       
+$1000\,\mathrm{kg/m^3}$, the hydraulic diameter of the channel to be $1.5\,\mathrm{mm}$ one can
 calculate the physical velocity of the bubble.
-Table \ref{table:twod:simulations} represents the number of simulations runs for the grid as
-$202\times 3002$ and its nondimensional parameters. One can see that velocity is quite reasonable
+Table \ref{table:twod:simulations} represents lattice Boltzmann simulations results and their
+physical equivalents for the grid $202\times 3002$. One can see
+that velocity is quite reasonable
 as \citet{bercic-mass} declared that experiments were conducted for velocities in the ranges of
-$0.01$ to $0.4\,\mathrm{m}/\mathrm{s}$ but for less capillary numbers. 
+$0.01$ to $0.4\,\mathrm{m}/\mathrm{s}$. 
 \begin{table}
 \begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
+\hline
 $Ca$    &$Re$     &$U_{LB}$ &$\delta$&$\varepsilon_{\mathrm{gas}}$
-&$U_{\mathrm{phys}}\mathrm{m/s}$\\
+&$U_{\mathrm{phys}}, \mathrm{m/s}$\\
+\hline
 $0.026$ &$0.449$  &$0.0014$ &$0.040$ &$0.306$ &$0.023$   \\ 
@@
 $0.989$ &$16.960$ &$0.0559$ &$0.172$ &$0.230$ &$0.902$  \\
+\hline
 \end{tabularx}
@@
 \end{equation}
-In terms of Schmidt number (taking the liquid viscosity in former simulations as $\frac{2}{3}$) that
+In terms of the Schmidt number (taking the lattice Boltzmann liquid viscosity in former simulations
+as $\frac{2}{3}$) that
 can result in:
@@
 \end{equation}
-Taking the water as $8.9 \times 10^{-4}\,\mathrm{Pa\cdot s}$ or kinematic viscosity as $8.9 \times
-10^{-7} \,\mathrm{m^2/s}$ and the Schmidt number as $796$ that results in the following quantity:
+Taking the water dynamic viscosity as $8.9 \times 10^{-4}\,\mathrm{Pa\cdot s}$ or kinematic
+viscosity as $8.9 \times
+10^{-7} \,\mathrm{m^2/s}$ and the Schmidt number as $796$ results in the following physical
+diffusion coefficient:
 \begin{equation}
@@
 which is less than the diffusivity of the methane $1.84\times 10^{-5}\,\mathrm{cm^2/s}$ but is
-physical. After calculation of physical parameters one can calculate characteristics for the mass
-theoretical mass transfer. Table \ref{table:lengths} gives nondimensional and physical lengths of a
-bubble and a slug.
+physical. After calculation of physical parameters one can calculate correlations indicated in
+Section \ref{sec:correlations} for mass transfer. Table \ref{table:lengths} presents extraction
+from the lattice Boltzmann simulation necessary to calculate mass transfer calculations.
+For the two-dimensional case parameter  $a$ is defined as:
+\begin{equation}
+a = \frac{\text{bubble perimeter}}{\text{cell area}}.
+\end{equation}
+For the height of the channel to be $H=1.5 \times 10^{-3}\,\mathrm{m}$, parameters $a$ are
+presented in Table \ref{table:lengths}. 
 \begin{table}
@@
 $Ca$&Bubble length& Slug Length&
-$U_{\mathrm{gas}}\,\mathrm{m/s}$&$U_{\mathrm{liq}}\,\mathrm{m/s}$&$a,\,\mathrm{m^{-1}}$\\
+$U_{\mathrm{gas}},\,\mathrm{m/s}$&$U_{\mathrm{liq}},\,\mathrm{m/s}$&$a,\,\mathrm{m^{-1}}$\\
 \hline
-$0.026$&$5.225$&$9.775$ &$0.0070$ &$0.0209$&$2.5538$\\
-$0.047$&$5.22$ &$9.78$  &$0.0126$ &$0.0379$&$2.5431$\\
-$0.080$&$5.215$&$9.785$ &$0.0204$ &$0.0615$&$2.5326$\\
-$0.065$&$4.965$&$10.035$&$0.0157$ &$0.0504$&$2.4142$\\
-$0.222$&$5.25$ &$9.75$  &$0.0511$ &$0.1560$&$2.5253$\\
-$0.479$&$5.565$&$9.435$ &$0.1089$ &$0.3155$&$2.6518$\\
-$0.736$&$5.51$ &$9.49$  &$0.1584$ &$0.4677$&$2.6269$\\
-$0.989$&$5.505$&$9.495$ &$0.2074$ &$0.6190$&$2.6340$\\
+$0.026$&$5.225$&$9.775$ &$0.0070$ &$0.0209$&$510.77$\\
+$0.047$&$5.22$ &$9.78$  &$0.0126$ &$0.0379$&$508.62$\\
+$0.080$&$5.215$&$9.785$ &$0.0204$ &$0.0615$&$506.53$\\
+$0.065$&$4.965$&$10.035$&$0.0157$ &$0.0504$&$482.84$\\
+$0.222$&$5.25$ &$9.75$  &$0.0511$ &$0.1560$&$505.06$\\
+$0.479$&$5.565$&$9.435$ &$0.1089$ &$0.3155$&$530.37$\\
+$0.736$&$5.51$ &$9.49$  &$0.1584$ &$0.4677$&$525.38$\\
+$0.989$&$5.505$&$9.495$ &$0.2074$ &$0.6190$&$526.80$\\
 \hline
 \end{tabularx}
-
 \caption{The nondimensional (scaled to the height of the channel) lengths for the same
 lattice Boltzmann simulations as in Table \ref{table:twod:simulations}. As well superficial
-gas-liquid velocities are presented.\label{table:lengths}}
+gas and liquid velocities are presented. \label{table:lengths}} 
 \end{table}
@@
 Fig. \ref{fig:mass:transfer:theoretical}. Note, that the correlations presented in
-Fig.\ref{fig:mass:transfer:theoretical} are used primarily for circular capillaries
+Fig. \ref{fig:mass:transfer:theoretical} are used primarily for circular capillaries
 (\citeauthor{vanbaten-circular,bercic-mass}) and for square capillaries (\citeauthor{yue-mass}). We
-adapt these results for flow between parallel plats by using hydraulic
+adapt these results for flow between parallel plates by using hydraulic
 diameter \cite{bercic-mass} which can be calculated as:
@@
 \end{equation}
+For comparison reasons we as well present the correlation when the hydraulic diameter is taken as
+$d_h=H$, see Fig. \ref{fig:mass:transfer:theoretical}.
+
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}
-\caption{The literature correlations by various authors. One
-can see the large deviation among them.\label{fig:mass:transfer:theoretical}}
+\includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}\\
+\includegraphics[width=\textwidth]{Figures/theoretical_correlations_without_hydraulic.eps}\\
+\caption{The literature correlations by various authors with hydraulic diameter taken as $2 H$
+(top) and $H$ (bottom). Correlations deviate a lot among each
+other.\label{fig:mass:transfer:theoretical}}
 \end{figure}
@@
 average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$)
-{\color{red} (In this particular moment I don't know whether to take the Volume of whole domain or
-just the liquid phase. I will go for whole domain.)}
 at time
-$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
-coefficient is calculated as:
+$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$ {\color{red} (In this particular
+moment I don't know whether to take the volume of the whole domain or
+just the liquid phase. I will go for whole domain.)}. Then the volumetric mass transfer
+coefficient is calculated as \cite{vanbaten-circular}:
 \begin{equation}
@@
 case the dimensional units do not coincide. In the calculations I will avoid it until further
-clearance.}
+clearance.} The overall concentration in the lattice Boltzmann system is prescribed as:
+\begin{equation}
+C_{overall}=\frac{\sum{c_i}}{N_x \, (N_y-2)}.
+\end{equation}
+
 To properly do
@@
 \end{equation}
-We as well need to address the concentration being in a whole system non-dimensionalized towards the equilibrium:
-if the domain size is
 
 The bubble surface length is the perimeter of the bubble in two-dimensional space and it is
-calculated with the extraction of the bubble countour and representing it with the polygon. After
-that the calculated perimeter is the effective summation of line lengths and ca be represented as:
+calculated with the extraction of the bubble contour and representing it with the polygon. After
+that the calculated perimeter is the effective summation of line lengths and can be represented as:
 \begin{equation}
@@
 where the index $i$ represents the polyline consisting of two points $(x1,y1)$ and $(x2,y2)$.
-
-The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
-Table \ref{table:volumetric:coefficients}.
+%The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
+%Table \ref{table:volumetric:coefficients}.
 
@@
 the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
-a steady-state condition the average of concentration values between $500000$ to $1000000$ time steps. The values are presented 
-\begin{figure}
+a steady-state condition the average of concentration values between $500000$ to $1000000$ time
+steps.{\color{red} We need to put more time steps. As well it is probably connected with Fourier
+number.} The average calculated volumetric mass transfer coefficients values are presented in Table
+\ref{table:volumetric:coefficients}. For each of the measurements we as well provided the Fourier
+number (for the flow between plates is as follows):
+\begin{equation}
+Fo=\frac{D t_{\mathrm{film}}}{\delta^2}=\frac{D
+(L_{\mathrm{bubble}}-H)}{U_{\mathrm{bubble}}\delta^2}.
+\end{equation}
+\begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/steady_state.eps}
 \caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
-state can be reached after $500000$. The mass transfer coefficient is taken as the average of concentration values between $500000$ to $1000000$ time steps..\label{fig:steady:state}}
+state can be reached after $500000$. The mass transfer coefficient is taken as the average of
+concentration values between $500000$ to $1000000$ time steps.\label{fig:steady:state}}
 \end{figure}
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
+$Ca$&$Fo$&$k_L a,\,\mathrm{s}^{-1}$\\
+\hline
+$0.026$&$0.08493$&$0.2737$\\
+$0.047$&$0.02160$&$0.3664$\\
+$0.080$&$0.00588$&$0.4959$\\
+$0.065$&$0.00862$&$0.4734$\\
+$0.222$&$0.00103$&$0.8505$\\
+$0.479$&$0.00034$&$1.1541$\\
+$0.736$&$0.00018$&$1.1801$\\
+$0.989$&$0.00012$&$1.2215$\\
+\hline
+\end{tabularx}
+\caption{Simulation results for different capillary numbers. \label{table:volumetric:coefficients}}
+\end{table}
 
-\section{To revise:}
-Then the diffusion penetration length is:
-\begin{equation}
-\delta_{penetration}=\sqrt{D t_{film}}=\sqrt{\frac{D L_{bubble}}{U_{bubble}}}.
-\end{equation}
-The bubble length is $5$ of diameters. Thus, the bubble length is $7.5\,\mathrm{mm}$. Therefore:
-\begin{equation}
-\delta_{penetration}=\sqrt{\frac{1.84 10^{-9} \mathrm{m^2/s} 7.5 10^{-3} \mathrm{m}}{4.3 \time
-10^{-2}\mathrm{m/s}}}=1.8 \times 10^{-5}
-\end{equation}
-With the given value of $200$ nodes to resolve the diameter for the given simulation, that results
-in $2.4$ nodes, which is small but considerable number to conduct the simulation.
-Foirier number which is defined as:
-\begin{equation}
-Fo=\frac{D t_{film}}{\delta_{film}^2}=\frac{1.84\times 10^{-9} 0.1744}{\times
-(8.7\times10^{-5})^2}=0.0423
-\end{equation}
-As it is indicated by \citet{vanbaten-circular} the Fourier number $Fo<0.1$ stays for short
-contact, the film is unsaturated. 
-Thus, one can calculate the corresponding parameters:
-\begin{equation}
-Pe_{min}=\frac{10^{-2} 1.5 10^{-3}}{1.84  10^{-9}}=0.81 \times 10^{4}\gg 1
-Sc_{min}=\frac{10^{-6}}{1.84 10^{-9}}=543,
-\end{equation}
-which imply the Reynolds number to be as:
-\begin{equation}
-Pe=Re Sc,\,Re=Pe/Sc=14.91
-\end{equation}
-
-The Schmidt number $Sc \approx 500$ states for dye in the liquid and assumes the dominance of
-convection over diffusion. In terms of the lattice Boltzmann system, the liquid viscosity equals to
-$\frac{1}{3}(\tau_{liq}-\frac{1}{2})=\frac{2}{3}$. That means that the relaxation rate for the
-advection-diffusion equation should be as:
-\begin{equation}
-\frac{1}{3}\Bigl(\tau_{\phi}-\frac{1}{2}\Bigr)=\frac{\nu}{Sc}\\
-\tau_{\phi}=0.50368,
-\end{equation}
-which is hard to simulate with the lattice Boltzmann equation, but possible . As it was discussed
-\cite{giavedoni-numerical} the inertia can be neglected for the Reynolds number $Re<70$ for bubble
-configuration, but not for the hydrodynamics simulations.
-
-The easy way to do is not to match the Peclet number $Pe$ along with the Reynolds number, leaving
-only matching the Schmidt number. However, the thorough study needs to be conducted to perform the
-matching parameters as $Ca$, $Re$, $Sc$ and $Pe$ numbers.
-
-If we match only the Peclet number then the Reynolds number can be changed as to adjust the
-velocity multiplied on coefficient, keeping Reynolds number small and anticipating results to see.
+Comparison between correlations and simulations one can find in Fig.
+\ref{fig:comparison:correlations}.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/comparison_correlations.eps}
+\caption{One can see the comparison between correlations and simulations. {\color{red} Last two
+points can be eliminated due to improper imposement of the concave structure of the bubble. The
+large deviation of the results can be probably explained by the flow between plates in comparison
+with the flow in circular and square microchannels.} \label{fig:comparison:correlations}}
+\end{figure}
 

### 2011-07-20 Python/curves.py

@@ -6,10 +6,14 @@ import os
 
 def Produce_Bunch():
     print os.getcwd()
-    capillary_str=["3","5","8","10","20","40"] #,"60","80"]
-    bubble_velocities=numpy.array([0.023,0.043,0.073,0.059,0.202,0.437]) #,0.671,0.902])
-    styles=['kv','ks','ko','k^','k>','k<','kD','kp']
+    #capillary_str=["3","5","8","10","20","40"] #,"60","80"]
+    #bubble_velocities=numpy.array([0.023,0.043,0.073,0.059,0.202,0.437]) #,0.671,0.902])
     
+    capillary_str=["3","5","8","10","20","40","60","80"]
+    bubble_velocities=numpy.array([0.023,0.043,0.073,0.059,0.202,0.437,0.671,0.902])
+
+    styles=['kv','ks','ko','k^','k>','k<','kD','kp']
+    aver_coefficient=[]
     fig=pylab.figure(99)
     for counter,dir_temp in enumerate(capillary_str):
         dir_name="Results/"+dir_temp
@@ -21,12 +25,15 @@ def Produce_Bunch():
         coefficient=new_conc[:,1]/(200*3000)/(4.64e-7*new_conc[:,0]*(1.0-numpy.abs(new_conc[:,2])))
         pylab.figure(99)
         pylab.plot(array[1:,0],coefficient,styles[counter])
+        aver_coefficient.append(numpy.mean(coefficient[len(coefficient)/2:]))
     legs=[r'''$U_{\mathrm{bubble}}='''+str(vel)[:4]+r'''$''' for vel in bubble_velocities]
     pylab.xlabel('Iterations',fontsize=20)
     pylab.ylabel(r'''$k_L a, \mathrm{s^{-1}}$''',fontsize=20)
     pylab.legend(legs,fancybox=True,labelspacing=0.1)
     pylab.savefig("steady_state.eps",format="EPS",dpi=300)
     
+    print "Aver_coefficient=",aver_coefficient
+    return aver_coefficient
 if __name__=="__main__":
     capillaries=numpy.array([0.026,0.047,0.080,0.065,0.222,0.479,0.736,0.989])
     bubble_lengths_non=numpy.array([5.225,5.22,5.215,4.965,5.25,5.565,5.51,5.505])
@@ -40,6 +47,7 @@ if __name__=="__main__":
[…]

### 2011-07-20 Python/get_coordinates.py

@@ -181,7 +181,7 @@ def Calculate_Perimeter(phase):
     for i,(x,y) in enumerate(cont[:-1]):
         perimeter+=math.sqrt((x-cont[i+1,0])**2+(y-cont[i+1,1])**2)
     print "Perimeter=",perimeter
-    print "a=",perimeter/((dims[0]-2)*dims[1]*1.5e-3);
+    print "a=",perimeter/(dims[1]*1.5e-3);
     #pylab.plot(cont[:,0],cont[:,1],"+")
 
 

### 2011-07-21 Text/paper.tex
Started doing nice analysis. Need to transform all the factors. Don't know what does it mean penetration theory for the cap.

@@
 
+\section{Solution of the semi-infinite concentration problems}
+For short contact times the mass transfer can be decomposed into two parts: transfer from the wall
+to semi-infinite medium and transfer from the sphere to the infinite medium. In what follows we
+derive analytical solutions to these two situations:
+\begin{description}
+\item[Wall mass transfer] The problem by mathematically is stated as:
+\begin{equation}
+\begin{aligned}
+&\partial_t C =D \partial^2_{xx} C\\
+&C(x,0)=0\\
+&C(0,t)=C_0\\
+\end{aligned}
+\end{equation}
+As far as the problem is non-homogenious one needs to decompose the problem into the steady-state
+and homogenous transient problem:
+\begin{equation}
+C=C_h + C_s,
+\end{equation}
+where $C_h$ and $C_s$ satisfy the following equations:
+\begin{equation}
+\begin{aligned}
+&\frac{\mathrm{d^2} C_s}{\mathrm{d}x^2}=0 && \partial_t C_h=D\partial^2_{xx} C_h\\
+&C_s(0)=C_0 && C_h(x,0)=-C_0\\
+&C_s(\infty)=C_0 && C_h(0,t)=0\\
+\end{aligned}
+\end{equation}
+One can easily check that the solution and boundary conditions are satisfied. The solution of
+the steady-state problem is $C_s=C_0$. To find a solution of the semi-infinite medium we will use
+the method of separation of variables:
+\begin{equation}
+\begin{aligned}
+&C_h=\Theta(t)\Phi(x)\\
+&\frac{1}{\Theta(t)}\frac{\mathrm{d}\Theta(t)}{\mathrm{d}t}=D
+\frac{1}{\Phi(x)}\frac{\mathrm{d}^2\Phi(x)}{\mathrm{d}x}=-\alpha^2 D\\
+\end{aligned}
+\end{equation}
+The solution for the time-dependent part is as:
+\begin{equation}
+\Theta(t)=\exp(-\alpha^2 D t).
+\end{equation}
+The solution for the spatial dependence function is as:
+\begin{equation}
+\Phi(x)=A\cos(\alpha x)+ B\sin(\alpha x).
+\end{equation}
+The overall solution of the homogenious part is represented as:
+\begin{equation}
+C_h=(A\cos(\alpha x) + B\sin(\alpha x)) \exp(-\alpha^2 D t),
+\end{equation}
+where one needs to solve the eigenvalue problem to find the necessary $\alpha$ parameter. One can
+find it through the initial and boundary conditions:
+\begin{equation}
+\begin{aligned}
+&C_h(x,0)=-C_0\\
+&C_h(x,0)=A\cos(\alpha x)+B\sin(\alpha x)=-C_0\\
+&C_h(0,t)=0\\
+&C_h(0,t)=A\exp(-\alpha^2 D t)=0\\
+&A=0\\
+\end{aligned}
+\end{equation}
+Therefore one needs to decompose the constant $-C_0$ through the function $\sin(\alpha x)$. It can
+be done through a continuous Fourier transform:
+\begin{equation}
+\begin{aligned}
+&C_h=\int_{\alpha>0}{B(\alpha) \sin(\alpha x) \exp(-\alpha^2 D t) \mathrm{d}\alpha}\\
+&C_h(x,0)=-C_0=\int_{\alpha>0}{B(\alpha)\sin(\alpha x) \mathrm{d}\alpha}\\
+&\int_{0}^{\infty}{B(\alpha) \frac{e^{i\alpha x}-e^{-i\alpha x}}{2 i}\mathrm{d} \alpha}=-C_0\\
+\end{aligned}
+\end{equation}
+To get function $B(\alpha)$ one needs to proof the following Fourier relationship:
+\begin{equation}
+\begin{aligned}
+&F(x)=\frac{2}{\pi}\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \sin(\alpha x)
+\int_{x'=0}^{\infty}{\sin(\alpha x')F(x')\mathrm{d} x'}}\\
+&\frac{2}{\pi}\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \sin(\alpha x)\sin(\alpha x')}=\frac{2}{\pi}
+\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \frac{\cos(\alpha(x+x'))-\cos(\alpha(x-x'))}{2}}\\
+&=\frac{1}{\pi}\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha\Bigl[\frac{e^{i\alpha
+(x+x')}+e^{-i\alpha(x+x')}}{2}-\frac{e^{i\alpha
+(x-x')}+e^{-i\alpha(x-x')}}{2}\Bigr]}\\
+&=\frac{1}{2\pi}\int_{\alpha=-\infty}^{\infty}{\mathrm{d}\alpha\Bigl[e^{i\alpha(x+x')}-e^{
+i\alpha(x-x')} \Bigr]}=\delta(x+x')-\delta(x-x')\\
+&F(x)=\int_{x'=0}^{\infty}{\mathrm{d} x' (\delta(x+x')-\delta(x-x')) F(x')}=F(x) 
+\end{aligned}
+\end{equation}
+Therefore the solution is as follows:
+\begin{equation}
+C_h(x,t)=-\frac{2 C_0}{\pi}\int_{\alpha>0} {\exp{-\alpha^2 t} \int_{x'>0}{\sin(\alpha x) \sin(\alpha
+x')}} 
+\end{equation}
+Integrals can be taken from \citet{ozisik}:
+\begin{equation}
+\begin{aligned}
+&\frac{2}{\pi}\int_{\alpha=0}^{\infty}{e^{-\alpha^2 D t} \sin(\alpha x) \sin(\alpha
+x')}\\
+&=\frac{1}{\sqrt{4\pi D t}}\biggl[\exp\Bigl(-\frac{(x-x')^2}{4 D
+t}\Bigr)-\exp\Bigl(-\frac{(x+x')^2}{4 D t}\Bigr)\biggr]
+\end{aligned}
+\end{equation}
+The final answer for homogenous part becomes \cite{ozisik}:
+\begin{equation}
+C_h(x,t)=-C_0\mathrm{erf}\Bigl(\frac{x}{\sqrt{4 D t}}\Bigr),
+\end{equation}
+where $\mathrm{erf}$ stands for the error function defined as:
+\begin{equation}
+\mathrm{erf(y)}=\frac{2}{\sqrt{\pi}}\int_{0}^{y}{e^{-\eta^2}\mathrm{d}\eta}.
+\end{equation}
+Overall solution then is defined as:
+\begin{equation}
+C(x,t)=C_0-C_0\mathrm{erf}\Bigl(\frac{x}{\sqrt{4 D t}}\Bigr),
+\end{equation}
+with the mass transfer coefficient is defined as the integral of absorbed gas upto time $t_e$
+divided by the time $t_e$. The accumulated  flux is the integral of the derivative
+$-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}$ by time $t$. The incoming flux is as follows:
+\begin{equation}
+\begin{aligned}
+&-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}=D \frac{1}{\sqrt{D t}}\\
+&k_L = \sqrt{\frac{D}{\pi t_{\mathrm{film}}}}.
+\end{aligned}
+\end{equation}
+
+\item[Cylinder mass transfer] For the cylinder mass transfer one needs to solve the heat conduction
+equation one needs to use cylindrical coordinates. The system is prescribed by the following set
+of equations:
+\begin{equation}
+\begin{aligned}
+&\frac{\partial C}{\partial t}=D\frac{\partial^2 C}{\partial r^2} + \frac{D}{r}\frac{\partial
+C}{\partial r}\\
+&C(a,t)=0\\
+&C(r,0)=0\\
+\end{aligned}
+\end{equation}
+The solution is given by \citet{ozisik} as:
+\begin{equation}
+\begin{aligned}
+&C(r,t)=C_0\\
+& - C_0\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \frac{\alpha}{J_0^2(\alpha
+a)+Y_0^2(\alpha a)}e^{-\alpha^2 D t}[J_0(\alpha r) Y_0(\alpha a)-Y_0(\alpha r) J_0(\alpha a)]}\\
+&\times \int_{r'=a}^{\infty}{r'[J_0(\alpha r')Y_0(\alpha a)-Y_0(\alpha r') J_0(\alpha
+a)]\mathrm{d}r'}
+\end{aligned}
+\end{equation}
+These integrals can be taken through the recurrent equations for Bessel functions.
+
+\end{description}
+
 \section{TRT $D2Q9$ model. Equilibrium functions}

### 2011-07-22 Text/paper.tex
Made a small report. Need to recalculate and to rerun everything.

@@
 \end{equation}
-For comparison reasons we as well present the correlation when the hydraulic diameter is taken as
-$d_h=H$, see Fig. \ref{fig:mass:transfer:theoretical}.
+For comparison reasons we derived in Section \ref{mass:transfer:correlation} the correlation for the
+flow between plates, see Fig. \ref{fig:mass:transfer:theoretical}. One can see that the
+difference is negligible.
 
@@
 \includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}\\
-\includegraphics[width=\textwidth]{Figures/theoretical_correlations_without_hydraulic.eps}\\
-\caption{The literature correlations by various authors with hydraulic diameter taken as $2 H$
-(top) and $H$ (bottom). Correlations deviate a lot among each
-other.\label{fig:mass:transfer:theoretical}}
+%\includegraphics[width=\textwidth]{Figures/theoretical_correlations_without_hydraulic.eps}\\
+\caption{The literature correlations by various authors.\label{fig:mass:transfer:theoretical}}
 \end{figure}
@@
 \end{equation}
+To understand the influence of the mass transfer in the film we provided the time needed for
+diffusion to reach the film thickness distance (95\% confidence interval of the film thickness):
+\begin{equation}
+\delta\approx 2\sqrt{2}\sqrt{D t};\ t \approx \frac{\delta^2}{8 D};\ N_{iter}=\frac{t}{\Delta t}.
+\end{equation}
+
 \begin{figure}[htb!]
@@
 \begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|}
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
 \hline
-$Ca$&$Fo$&$k_L a,\,\mathrm{s}^{-1}$\\
+$Ca$&$Fo$&$k_L a,\,\mathrm{s}^{-1}$&$N_{iter}$\\
 \hline
-$0.026$&$0.08493$&$0.2737$\\
-$0.047$&$0.02160$&$0.3664$\\
-$0.080$&$0.00588$&$0.4959$\\
-$0.065$&$0.00862$&$0.4734$\\
-$0.222$&$0.00103$&$0.8505$\\
-$0.479$&$0.00034$&$1.1541$\\
-$0.736$&$0.00018$&$1.1801$\\
-$0.989$&$0.00012$&$1.2215$\\
+$0.026$&$0.08493$&$0.2737$&$873984$\\
+$0.047$&$0.02160$&$0.3664$&$1835817$\\
+$0.080$&$0.00588$&$0.4959$&$3965227$\\
+$0.065$&$0.00862$&$0.4734$&$3149710$\\
+$0.222$&$0.00103$&$0.8505$&$8195770$\\
+$0.479$&$0.00034$&$1.1541$&$12399627$\\
+$0.736$&$0.00018$&$1.1801$&$14683652$\\
+$0.989$&$0.00012$&$1.2215$&$16101062$\\
 \hline
@@
 
+\subsection{Comparison between correlations and results}
 Comparison between correlations and simulations one can find in Fig.
-\ref{fig:comparison:correlations}.
+\ref{fig:comparison:correlations}. The simulated results exhibit larger mass transfer in comparison
+with the given correlations. {\color{red} Need to recalculate and check the kinematic viscosities.}
 \begin{figure}[htb!]
@@
 \section{Solution of the semi-infinite concentration problems}
+\label{mass:transfer:correlation}
 For short contact times the mass transfer can be decomposed into two parts: transfer from the wall
@@
 \begin{aligned}
-&-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}=D \frac{1}{\sqrt{D t}}\\
-&k_L = \sqrt{\frac{D}{\pi t_{\mathrm{film}}}}.
+&-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}=D \frac{1}{\sqrt{\pi D t}}\\
+\end{aligned}
+\end{equation}
+The accumulated concentration and the mass transfer coefficients are:
+\begin{equation}
+\begin{aligned}
+&\int_{0}^{t_{\mathrm{film}}}{-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0} \mathrm{d}t}=2
+\sqrt{ \frac{D t}{\pi}}\\
+&k_L = 2 \sqrt{\frac{D}{\pi t_{\mathrm{film}}}}.
+\end{aligned}
+\end{equation}
+If we account for the two surfaces for the bubble then one can obtain the following volumetric mass
+transfer coefficient:
+\begin{equation}
+\begin{aligned}
+&k_L a= 2\sqrt{\frac{D}{\pi t_{\mathrm{film}}}} 2
+\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{
+\mathrm { slug } } )H_ { \mathrm { eff } } }\\
+&k_L a= 2\sqrt{\frac{D}{\pi
+\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{U_{\mathrm{bubble}}}}} 2
+\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{
+\mathrm { slug } } )H_ { \mathrm { eff } } }\\
+&k_L a=4 \sqrt{\frac{D U_{\mathrm{bubble}}}{\pi}}
+\frac{\sqrt{L_{\mathrm{bubble}}-(H_{\mathrm{eff}-2\delta})}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}
+)H_ { \mathrm { eff } } }
 \end{aligned}
@@
 \end{equation}
-These integrals can be taken through the recurrent equations for Bessel functions.
+These integrals can be taken through the recurrent equations for Bessel functions. However, the
+penetration of the concentrator comes not only from the diffusion but mainly from the advection
+part. According to the penetration theory one can use the following correlation for the mass
+transfer coefficient:
+\begin{equation}
+k_L=2\sqrt{\frac{D}{\pi t_{\mathrm{contact}}}},
+\end{equation}
+where $t_{\mathrm{contact}}$ for the bubble cap can be calculated from the following considerations
+\cite{vanbaten-circular}: the distance travelled by a fluid packet coming to the bubble equals to a
+half of semicircle perimeter until it is swept away by the vortex in the front of the bubble
+{\color{red} (working only for small capillary numbers where a vortex exists in the front of the
+bubble)}. Therefore for the case of the bubble arising with the velocity $U_{\mathrm{bubble}}$ one
+can estimate the mass transfer coefficient as follows:
+\begin{equation}
+k_L=2\sqrt{\frac{D}{\pi t_{\mathrm{contact}}}}=2\sqrt{\frac{D}{\pi \frac{ \pi
+(H_{\mathrm{eff}}-2\delta)/2}{U_{\mathrm{bubble}}}}}=\frac{2\sqrt{2}}{\pi}\sqrt{\frac{D
+U_{\mathrm{bubble}}}{H_{\mathrm{eff}}-2\delta}}
+\end{equation}
+The volumetric mass transfer coefficient is then as follows:
+\begin{equation}
+\begin{aligned}
+k_L a=\frac{2\sqrt{2}}{\pi}\sqrt{\frac{D
+U_{\mathrm{bubble}}}{H_{\mathrm{eff}}-2\delta}} \frac{\pi
+(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}) H_{\mathrm{eff}}}\\
+k_L a=2\sqrt{2}\sqrt{D
+U_{\mathrm{bubble}}}\frac{\sqrt{H_{\mathrm{eff}}-2\delta}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})H_
+{\mathrm{eff}}}
+\end{aligned}
+\end{equation}
 
 \end{description}
+Therefore the overall adjusted for the flow between plates mass transfer coefficient is expressed as
+follows:
+\begin{equation}
+\begin{aligned}
+k_L a =&4 \sqrt{\frac{D U_{\mathrm{bubble}}}{\pi}}
+\frac{\sqrt{L_{\mathrm{bubble}}-(H_{\mathrm{eff}-2\delta})}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}
+)H_ { \mathrm { eff } } }\\
+&+2\sqrt{2}\sqrt{D
+U_{\mathrm{bubble}}}\frac{\sqrt{H_{\mathrm{eff}}-2\delta}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})H_
+{\mathrm{eff}}}.
+\end{aligned}
+\end{equation}
 

### 2011-07-22 Python/curves.py

@@ -3,6 +3,7 @@ import numpy
 import pylab
 import math
 import os
+import subprocess
 
 def Produce_Bunch():
     print os.getcwd()
@@ -34,7 +35,38 @@ def Produce_Bunch():
     
     print "Aver_coefficient=",aver_coefficient
     return aver_coefficient
-if __name__=="__main__":
+def Produce_Pictures():
+    print os.getcwd()
+    capillary_str=["3","5","8","10","20","40","60","80"]
+    capillaries=numpy.array([0.026,0.047,0.080,0.065,0.222,0.479,0.736,0.989])
+    
+    #capillary=capillaries[capillary_str.index(dir_name)]
+    for counter,dir_name in enumerate(capillary_str):
+        dir_name="Results/"+dir_name
+        os.chdir(dir_name)
+
+        capillary=capillaries[counter]
+        file_list=[]    
+        for root,dirs,files in os.walk(os.getcwd()):
+            for file in files:
+                if file[0:7]=="density":
+                    file_list.append(file)
+        #for file_name in sorted(file_list):
+        #    arr=numpy.loadtxt(file_name)
+        #    print file_name        
+        #    pylab.imshow(arr,origin="lower")
+        #    pylab.title(r'''$Ca='''+str(capillary)+r'''$''')
+        #    pylab.text(1500, 100, "Time="+file_name[7:-4])
+        #    pylab.savefig("map"+file_name[7:-4]+".png",format="PNG")
+        #    pylab.clf()
+        #subprocess.call(["mencoder","mf://*.png","-mf","fps=5:type=png","-ovc","lavc","-lavcopts","vcodec=mpeg4","-o","output.mp4"])
+        subprocess.call(["mencoder","mf://*.png","-mf","fps=5:type=png","-ovc","lavc","-lavcopts","vcodec=wmv1","-o","ca0"+str(capillary)[2:]+".avi"])
+        os.chdir("../..")
+    #   #print file
+    #    read_file=numpy.loadtxt(file)
+    #    flux.append(read_file[0].tolist())
+    
+def Produce_Curves():
     capillaries=numpy.array([0.026,0.047,0.080,0.065,0.222,0.479,0.736,0.989])
[…]

### 2011-08-30 Text/paper.tex
More explanations and definitions of the mass transfer.

@@
 \usepackage{tabularx}
+\newcommand{\beq}{\begin{equation}}
+\newcommand{\feq}{\end{equation}}
+\newcommand{\beqstar}{\begin{equation*}}
+\newcommand{\feqstar}{\end{equation*}}                                     
+\newcommand{\beqal}{\begin{equation}\begin{aligned}}
+\newcommand{\feqal}{\end{aligned}\end{equation}}
+\newcommand{\beqalstar}{\begin{equation*}\begin{aligned}}
+\newcommand{\feqalstar}{\end{aligned}\end{equation*}}
 \begin{document}
@@
 
+\section{Mass transfer definitions}
+By the definition the mass transfer coefficient is the following:
+\beq
+k_L=\frac{\dot{m}}{P \Delta C},
+\feq
+where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
+$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference $\Bigl[\frac{kg}{m^3}\Bigr]$.
+Therefore, $k_L$ has a dimension of velocity $\Bigl[\frac{m}{s}\Bigr]$.
+
+There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
+theoretical definitions of the mass transfer in case of the point sources.
+\subsection{Point mass sources}
+Let us look at the infinitisemal small domain of the volume $A \Delta x$ in a steady-state, not
+moving and with the mass source. Then the concentration difference can be found as $\Delta C = C^* -
+C(t)$, where $C*$ is the imposed concentration on the infinitesimal concentration source, $C(t)$ is
+the time depending average concentration. Therefore one can write the time dependent ODE for the
+average concentration in the domain:
+\beq
+\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (C^{*}-C(t)), 
+\feq
+with the initial condition $C(0)=0$
+The solution in time becomes as follows:
+\beq
+C(t)= C^{*}(1-\exp(-k_L a t )), 
+\feq
+where $k_L a$ is the volumetric mass transfer coefficient.
+
+This simple picture is able to predict mass transfer happening in moving with the velocity $U$
+liquid, see Fig. \ref{fig:moving:frame}.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
+\caption{The mass transfer in the moving liquid. \label{fig:moving:frame}}
+\end{figure}
+
+The mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
+mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
+source is a point source with the effective perimeter P. The accumulated mass should be proportional
+to the mass transfer coefficient:
+\beq
+U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P (C^{*}-C(x)), 
+\feq 
+giving the same equation but only in the coordinate domain:
+\beq
+C(x)= C^{*}(1-\exp(-k_L a \frac{x}{U} )).
+\label{main:mass:transfer:expression} 
+\feq
+The expression (\ref{main:mass:transfer:expression}) is exactly used in the experiments by
+\citet{bercic-mass}. One should be accurate with the definition of velocities because we have two
+different phases. Usually, if we cannot distinguish phases one can take the velocity $U$ to be as
+average velocity or $U=U_{sl}+U_{sg}$, where $U_{sl}$ and $U_{sg}$ are liquid and gas superficial
+velocities correspondingly. However, the real picture is much more complicated, as two phases can
+have different mixing patterns from film to slug and from slug to film. For example, one of the
+most important characteristics to properly analytically estimate the mass transfer coefficient is
+the mixing patterns. For example, one can assume that the slug concentration is uniformly
+distributed over the slug, which usually overpredicts the mass transfer \cite{irandoust} since some
+tracer concentration from film is mixed with the slug. Another issue is that if the slug is long
+enough then the film saturates with the tracer concentration and its influence on the mass transfer
+can be negligible \cite{vanbaten-circular}. Mixing patterns of the film and the liquid slugs are of
+great importance for the analytical estimation of the mass transfer \cite{yue-mass}.
+
+\subsection{Numerical calculation}
+In the numerical simulation it is not possible to simulate really long domains with the infinite
+number of the bubbles. Therefore, one needs to come up with the simple smaller domain calculations
+of the mass transfer coefficient. The mixing patterns are extremely important for the analytical
+estimations of the mass transfer coefficient. This is not the case for numerical calculations,
+where one needs to present the adequate picture and the way to calculate the volumetric mass
+transfer coefficient. We consider the following possibilities of conducting numerical simulations:
+\begin{enumerate}
+ \item The tracer picking up procedure can be introduced in the manner of the considerations above.
+We impose the concentration at the entrance to be constant $C(0,y)=C_{inlet}$, at the outlet we
+impose the outflow boundary condition $\frac{\partial C}{\partial x}(L,y)=0$. One can se the sketch
+of the approach in Fig. \ref{fig:benchmark:jos}. Without loss of the generality one can impose
+$C_{inlet}=0$. After that one can estimate the mass transfer coefficient through the mass flux
+depending on the coordinate $x$. The mass flux is calculated through the following equation:
+\beq
+j(x)=\int{U(x) C(x,y) \mathrm{d}y}.
+\feq
+As it was indicated the mass flux is proportional to the mass transfer coefficient $j(x)=k_L \Delta
+C$, where the difference in the concentration is taken as $\Delta C=C^{*}-C_{media}$, where $C^{*}$
+is the saturation concentration. The question remains with the $C_{media}$ which can be treated
+differently. According to the Fick's law $C_{media}$ should be the concentration of the media
+examined. However, that imposes the assumption of the ideal mixing in the liquid slug. Another
+possibility to take $C_{media}$ as the outflow concentration. A few considerations:
+\begin{itemize}
+ \item Note, that in the presence of the
+complicated geometries and non-homogenous concentrations distributions around the bubble one can
+use any definitions. Though the definition of the mass averaged $C_{media}$ is prefered.  
+\item Note, that if the tracer volume is large then $C_{media}$ can be close to zero.
+\item Note, that one cannnot use the definition of the mass transfer coefficient as far as it
+varies through the bubble due to inhomogenoities of the flow. Therefore, the volumetric mass
+transfer coefficient is introduced that takes into the account the bubble geometry.
+\end{itemize}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
+\caption{The numerical mass transfer benchmark. \label{fig:benchmark:jos}}
+\end{figure}
+\item The periodic domain.
+\end{enumerate}
+
 \section{Solution of the semi-infinite concentration problems}

### 2011-08-30 Text/paper.tex
Added results of the mass transfer. Still too large coefficient.

@@
 \usepackage{tabularx}
+
 \newcommand{\beq}{\begin{equation}}
@@
 \newcommand{\feqalstar}{\end{aligned}\end{equation*}}
+\newcommand{\vol}{k_L\,a}
+
 \begin{document}
@@
 \subsection{Point mass sources}
+In what follows we will present three approaches to calculate the mass points mass transfer
+coefficients:
+\begin{enumerate}
+\item
 Let us look at the infinitisemal small domain of the volume $A \Delta x$ in a steady-state, not
 moving and with the mass source. Then the concentration difference can be found as $\Delta C = C^* -
-C(t)$, where $C*$ is the imposed concentration on the infinitesimal concentration source, $C(t)$ is
+C(t)$, where $C^*$ is the imposed concentration on the infinitesimal concentration source, $C(t)$ is
 the time depending average concentration. Therefore one can write the time dependent ODE for the
@@
 
-This simple picture is able to predict mass transfer happening in moving with the velocity $U$
-liquid, see Fig. \ref{fig:moving:frame}.
+\item
+The previous consideration is able to predict mass transfer happening in moving with the velocity
+$U$ liquid, see Fig. \ref{fig:moving:frame}.
 \begin{figure}[htb!]
@@
 \beq
-U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P (C^{*}-C(x)), 
+U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(C^{*}-C(x)\bigr), 
 \feq 
@@
 \beq
-C(x)= C^{*}(1-\exp(-k_L a \frac{x}{U} )).
+C(x)= C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
 \label{main:mass:transfer:expression} 
 \feq
-The expression (\ref{main:mass:transfer:expression}) is exactly used in the experiments by
+
+\item If one transfers to the frame moving with the liquid velocity $U$, then the situation will be
+the same as in the first case. However, one can connect the time and spatial location with the
+velocity $U$ ($t=\frac{x}{U}$) to obtain the same equation as in the case 2.
+\end{enumerate}
+
+The expression (\ref{main:mass:transfer:expression}) was used in the experiments by
 \citet{bercic-mass}. One should be accurate with the definition of velocities because we have two
-different phases. Usually, if we cannot distinguish phases one can take the velocity $U$ to be as
-average velocity or $U=U_{sl}+U_{sg}$, where $U_{sl}$ and $U_{sg}$ are liquid and gas superficial
-velocities correspondingly. However, the real picture is much more complicated, as two phases can
-have different mixing patterns from film to slug and from slug to film. For example, one of the
-most important characteristics to properly analytically estimate the mass transfer coefficient is
-the mixing patterns. For example, one can assume that the slug concentration is uniformly
-distributed over the slug, which usually overpredicts the mass transfer \cite{irandoust} since some
-tracer concentration from film is mixed with the slug. Another issue is that if the slug is long
-enough then the film saturates with the tracer concentration and its influence on the mass transfer
-can be negligible \cite{vanbaten-circular}. Mixing patterns of the film and the liquid slugs are of
-great importance for the analytical estimation of the mass transfer \cite{yue-mass}.
+different phases. Usually, one can take the velocity $U$ to be as
+average velocity or $U=U_{gas}+U_{liq}$, where $U_{gas}$ and $U_{liq}$ are liquid and gas
+superficial velocities correspondingly. In this case, the continuouty assumption is restored and
+all considerations above are valid.
+
+ However, if one wants to analytically estimate the mass transfer coefficients, the situation is
+much more complicated because of the two phases presence. Phases can have different mixing patterns
+from film to slug and from slug to film. The analytical approaches described above assume that the
+contributions from film and bubble caps can be calculated separately. However one can see that such 
+an assumption for bubble caps (slug well mixed and the concentration is uniformly distributed over
+the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
+concentration from film is mixed with the slug and changes the overall concentration in the slug.
+Another issue is that if the slug is long enough then the film saturates with the tracer
+concentration and its influence on the mass transfer can be negligible \cite{vanbaten-circular}.
+Mixing patterns of the film and the liquid slugs are of great importance for the analytical
+estimation of the mass transfer \cite{yue-mass}.
 
@@
 In the numerical simulation it is not possible to simulate really long domains with the infinite
-number of the bubbles. Therefore, one needs to come up with the simple smaller domain calculations
-of the mass transfer coefficient. The mixing patterns are extremely important for the analytical
-estimations of the mass transfer coefficient. This is not the case for numerical calculations,
-where one needs to present the adequate picture and the way to calculate the volumetric mass
-transfer coefficient. We consider the following possibilities of conducting numerical simulations:
+number of the bubbles. As we saw before there are two approaches towards it - either to simulate
+the bubble train and then to measure concentration along the pipe, Eq.
+\ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with bulk
+velocity $U$ and conduct the same measurements through Eq. \ref{main:mass:transfer:expression}.
+However, both methods do require a tracking of moving bubbles which is complicated from the
+numerical point of view.
+
+Therefore, one needs to come up with the simple smaller domain calculations
+of the mass transfer coefficient, which represent the continuous picture with infinite numbers of
+the bubbles closely. In comparison with analytical estimations of the mass transfer coefficient,
+where the mixing patterns are extremely important, the numerical simulations need only to mimic
+the continous picture and provide the way to calculate the volumetric mass transfer coefficient.
+
+We perform simulations in the frame moving with the bubble (velocity
+$U_{bubble}$), that the bubble position stands steady. The bubble velocity $U_{bubble}$ is
+different from the bulk velocity $U_{gas}+U_{liq}$. In this case we need to perform coordinate
+change:
+\beqal
+&x(t)=U_{bubble}t\\
+&C(x)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a \frac{x}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
+&C(t)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)
+\feqal
+If the unit volume that we simulate is quite long one can obtain the values of the concentration
+in the inlet and outlet as a function of time:
+\beqal
+&C(U_{bubble}\, t)=C^{*}\Bigl(1-\exp\bigr(-k_L\, a\, t
+\frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
+&C(U_{bubble}\,t+L_{unit})=C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{
+U_{bubble}\,t+L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
+&=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\exp\bigl(-k_L a
+\frac{L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)
+\feqal
+Therefore the mass transfer coefficient can be calculated as follows:
+\beqal
+&-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
+&k_L a
+=\frac{U_{gas}+U_{liq}}{L_{unit}}\ln\Bigl(\frac{C^{*}-C_{inlet}}{C^{*}-C_{outlet}}
+\Bigr)
+\feqal 
+If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$
+then the expression for the volumetric mass transfer coefficitent $k_L a$ can be simplified:
+\beq
+\vol=\frac{\Delta C}{C^{*}} \frac{U_{gas}+U_{liq}}{L_{unit}},
+\feq
+where $\Delta C=C_{outlet}-C_{inlet}$. If we go to the continuous formulation by changing $L_{unit}$
+to be a continuous coordinate $x$, then the following can be obtained \cite{jos-mass}:
+\beq
+\Delta C = C^{*} \vol \frac{x}{U_{gas}+U_{liq}}
+\label{small:conc:mass:estimation}
+\feq
+
+We consider the following possibilities of conducting numerical simulations:
 \begin{enumerate}
- \item The tracer picking up procedure can be introduced in the manner of the considerations above.
-We impose the concentration at the entrance to be constant $C(0,y)=C_{inlet}$, at the outlet we
-impose the outflow boundary condition $\frac{\partial C}{\partial x}(L,y)=0$. One can se the sketch
-of the approach in Fig. \ref{fig:benchmark:jos}. Without loss of the generality one can impose
-$C_{inlet}=0$. After that one can estimate the mass transfer coefficient through the mass flux
-depending on the coordinate $x$. The mass flux is calculated through the following equation:
+ \item 
+The tracer picking up procedure can be introduced
+in the manner of the considerations above. We impose the concentration at the entrance to be
+constant $C(0,y)=C_{inlet}$, at the outlet we impose the outflow boundary condition $\frac{\partial
+C}{\partial x}(L,y)=0$. To be compliant with the considerations above one needs to impose as well
+the outflow boundary conditions for the inlet as well. However, without loss of the generality one
+can impose $C_{inlet}=0$, since the walls in the reference frame
+moving with the bubble are moving from the inlet to the outlet. That means that no tracer
+concentration leaves domain from the inlet side, which is true for the capillary numbers larger
+than $0.6$.  However, this boundary condition can not be used in the case of small capillary
+numbers, since there is a strong circulation in front of the bubble. One can see the sketch of the
+approach in Fig. \ref{fig:benchmark:jos}. The longer the numerical domain length the better will be
+results. One can estimate the volumetric mass transfer coefficient in this case through the equation
+(\ref{small:conc:mass:estimation}) for small concentrations. Note a few considerations:
+\begin{itemize}
+\item  The considerations above were established for the homogenous velocity field. In the case of
+the non-homogenous velocity field one needs to obtain a concentration from the mass flux:
 \beq
-j(x)=\int{U(x) C(x,y) \mathrm{d}y}.
+C_{outlet}=\frac{\int{U(y) C(L_{unit},y) \mathrm{d}y}}{\int{U(y) \mathrm{d}y}}.
 \feq
-As it was indicated the mass flux is proportional to the mass transfer coefficient $j(x)=k_L \Delta
-C$, where the difference in the concentration is taken as $\Delta C=C^{*}-C_{media}$, where $C^{*}$
-is the saturation concentration. The question remains with the $C_{media}$ which can be treated
-differently. According to the Fick's law $C_{media}$ should be the concentration of the media
-examined. However, that imposes the assumption of the ideal mixing in the liquid slug. Another
-possibility to take $C_{media}$ as the outflow concentration. A few considerations:
-\begin{itemize}
- \item Note, that in the presence of the
-complicated geometries and non-homogenous concentrations distributions around the bubble one can
-use any definitions. Though the definition of the mass averaged $C_{media}$ is prefered.  
-\item Note, that if the tracer volume is large then $C_{media}$ can be close to zero.
 \item Note, that one cannnot use the definition of the mass transfer coefficient as far as it
@@
 \end{itemize}
-
 \begin{figure}
@@
 \end{figure}
-\item The periodic domain.
+
+\item Another possibility is to use the periodic boundary conditions as the limiting case of the
+continuous formulation. In this case the inlet and outlet concentrations are not much different
+($C(x)=C(x+L_{unit})=C(x+\Delta x)\approx C_{media}$, see Fig. \ref{fig:moving:frame}), where
+$C_{media}$ is the mass averaged over domain concentration. This formulation requires the periodic
+boundary condition $C_{inlet}=C_{outlet}$. By the definition the mass transfer coefficient is
+proportional to the gain of the mass in the system divided by the concentration difference:
+\beq
+j=\frac{\dot{m}}{P \Delta C}=\frac{\dot{m}}{P (C^{*}-C_{media})},
+\feq
+where mass difference in the domain can be calculated as:
+\beq
+\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{C(t_2)\mathrm{d}V}-\int{C(t_1)\mathrm{d}V}}{t_2-t_1}.
+\feq
+Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
+considerably large and the tracer is well mixed in the slug, as one can take the concentration
+difference as $\Delta C = C^{*}-C_{media}$. The best case scenario is when $C_{media}$ is close to
+zero, in this case we can be sure that the flux to the domain is calculated precisely and periodic
+boundary conditions are fulfilled.
 \end{enumerate}

### 2011-08-30 Python/curves.py

@@ -125,7 +125,37 @@ def Produce_Curves():
     print "Fourier=",fourier
     
     pylab.show() 
+def Produce_Mass_Bunch_Sailfish():
+    print os.getcwd()
+ 
+    styles=['kv','ks','ko','k^','k>','k<']
+    aver_coefficient=[]
+    bubble_velocities=[]
+    dirs=[3,5,8,10,20,40]
+    fig=pylab.figure(99)
+
+    for counter,dir_name in enumerate(dirs):    
+        dir_name="SailfishMass/"+str(dir_name)+"/"
+        name=dir_name+"concentration.dat"
+        array=numpy.loadtxt(name)
+        #print array
+        new_conc=numpy.array(zip(array[1:,0]-array[:-1,0],array[1:,1]-array[:-1,1],array[1:,2]))
+        print "Data=",new_conc
+        coefficient=new_conc[:,1]/(200*3000)/(4.64e-7*new_conc[:,0]*(1.0-numpy.abs(new_conc[:,2])))
+        pylab.figure(99)
+        pylab.plot(array[1:,0],coefficient,styles[counter])
+        aver_coefficient.append(numpy.mean(coefficient[len(coefficient)/2:]))
+    legs=[r'''$U_{\mathrm{bubble}}='''+str(vel)[:4]+r'''$''' for vel in bubble_velocities]
+    pylab.xlabel('Iterations',fontsize=20)
+    pylab.ylabel(r'''$k_L a, \mathrm{s^{-1}}$''',fontsize=20)
+    #pylab.legend(legs,fancybox=True,labelspacing=0.1)
+    pylab.savefig("steady_state.eps",format="EPS",dpi=300)
+    
+    print "Aver_coefficient=",aver_coefficient
+    return aver_coefficient
     
 if __name__=="__main__":
     #Produce_Pictures()
-    Produce_Curves()
+    #Produce_Curves()
+    Produce_Mass_Bunch_Sailfish()
+    pylab.show()

### 2011-08-30 Python/hydro.py

@@ -223,7 +223,9 @@ def Produce_Mass_Bunch():
     print "Aver_coefficient=",aver_coefficient
     return aver_coefficient
 
+
+
 if __name__=="__main__":
     #Analyze_Simulations()
-    Produce_Mass_Bunch()
+    Produce_Mass_Bunch_Sailfish()
     pylab.show()

### 2011-09-07 Text/paper.tex
More results. Need to do grid convergence and bubble train.

@@
 
+\section{Other boundary conditions}
+We used the outflow boundary conditions for both boundaries and determined the coefficient
+according Eq. \ref{theor:continuous:mass:transfer}. One can see the calculated mass transfer
+coefficient in time in Fig. \ref{fig:steady:state:jos}.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/steady_state_jos.eps}
+\caption{The calculated mass transfer coefficient in time with open boundaries $\partial_x
+C_{inlet}=\partial_x C_{outlet}=0$. One can see some negative values for volumetric coefficients.
+This situation corresponds to the case, then the inlet concentration is greater than the outlet
+$C_{inlet}>C_{outlet}$. This corresponds to smaller capillary numbers due to vortex in front of the
+bubble. It is the indication that one needs to take more time steps to wait until the outlet
+concentration becomes larger than the inlet, which can take a relatively large time period to
+wait. Large numbers of the volumetric mass transfer coefficients means the insuffient number of
+the unit volumes simulated, as the large difference in the outlet and inlet numbers means the
+deviation from the continuous picture. \label{fig:steady:state:jos} }
+\end{figure}
+
 \appendix
@@
 Therefore the mass transfer coefficient can be calculated as follows:
-\beqal
+\begin{equation}
+\label{theor:continuous:mass:transfer}
+\begin{aligned}
 &-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
@@
 \Bigr)
-\feqal 
+\end{aligned}
+\end{equation}
 If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$

### 2011-09-07 Python/curves.py

@@ -104,7 +104,6 @@ def Produce_Curves():
     vanbaten=2.0/math.sqrt(math.pi)*numpy.sqrt(diffusion*bubble_velocities/(bubble_lengths-hydraulic))*4\
             *(bubble_lengths-hydraulic)/(hydraulic*(bubble_lengths+slug_lengths))\
             +2.0*math.sqrt(2.0)/math.pi*numpy.sqrt(diffusion*bubble_velocities/hydraulic)*4/(bubble_lengths+slug_lengths)
-    
     vanbaten_my=4.0*numpy.sqrt(diffusion*bubble_velocities/math.pi)*numpy.sqrt(bubble_lengths-bubble_diameters)/((bubble_lengths+slug_lengths)*diameter)\
                +2.0*math.sqrt(2.0)*numpy.sqrt(diffusion*bubble_velocities)*numpy.sqrt(bubble_diameters)/((bubble_lengths+slug_lengths)*diameter)
     
@@ -131,11 +130,11 @@ def Produce_Mass_Bunch_Sailfish():
     diam=1.5e-3    
     print os.getcwd()
  
-    styles=['kv','ks','ko','k^','k>','k<']
+    styles=['kv','ks','ko','k^','k>','k<','kD','kh']
     aver_coefficient=[]
     bubble_velocities=[]
-    #dirs=[3,5,8,10,20,40]
-    dirs=[3,5,8,10,20]    
+    dirs=[3,5,8,10,20,40,60,80]
+    #dirs=[3,5,8,10,20]    
     fig=pylab.figure(99)
 
     for counter,dir_name in enumerate(dirs):    
@@ -170,8 +169,8 @@ def Produce_Mass_Bunch_Sailfish():
         print "Capillary=",capillary
         print "Reynolds=",reynolds
   
-        #dir_name="SailfishMassBGK/"+str(dir_name)+"/"
-        dir_name="SailfishMassJos/"+str(dir_name)+"/"     
+        dir_name="SailfishMassBGK/"+str(dir_name)+"/"
+        #dir_name="SailfishMassJos/"+str(dir_name)+"/"     
         name=dir_name+"concentration.dat"
         array=numpy.loadtxt(name)
         new_conc=numpy.array(zip(array[1:,0]-array[:-1,0],array[1:,1]-array[:-1,1],array[1:,2]))
@@ -203,9 +202,101 @@ def Produce_Mass_Bunch_Sailfish():
[…]

### 2011-09-07 Python/divergence.py

@@ -50,7 +50,7 @@ if __name__=="__main__":
     name_velx="tmp/velocityx150000.dat"
     name_vely="tmp/velocityy150000.dat"
     #CalculateDivergence(name_phase,name_velx,name_vely)
-    name="SailfishData/20/capillary200000.npz"    
+    name="SailfishData/80/capillary200000.npz"    
     CalculateDivergenceSailfish(name)    
     pylab.show()
     

### 2011-09-07 Python/hydro.py

@@ -26,9 +26,9 @@ def Analyze_Simulations():
         dir_name="HydroResultsRight/"+str(i)
         os.chdir(dir_name)
         
-        name_phi="phase200000.dat"
-        name_velx="velocityx200000.dat"
-        name_vely="velocityy200000.dat"
+        name_phi="phase300000.dat"
+        name_velx="velocityx300000.dat"
+        name_vely="velocityy300000.dat"
         phase=numpy.loadtxt(name_phi)
         velx=numpy.loadtxt(name_velx)
         vely=numpy.loadtxt(name_vely)

### 2011-09-14 Text/paper.tex
Fighting with the codes. Still don't know what is the real number

@@
 
+\subsection{Average concentration}
+As far as we used the inlet/outlet concentration in the expression of the calculation of the
+volumetric mass transfer coefficient. However, the bubble in simulations located closely to the
+inlet and with periodic boundary conditions that can change the volumetric mass transfer
+coefficient significantly. As it will be discussed later in the appendix section, the assumption of
+the periodic boundary conditions requires the continuous picture. The continuous picture requires as
+well the average concentration to be of constant value. If the average concentration is used for
+the calculation of the volumetric mass transfer coefficient {\color{red} (which can be more
+adequate)}, then the volumetric mass transfer coefficient is more close to the correlation values,
+see Fig. \ref{fig:average:concentration}. 
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/steady_state_average.eps}
+\caption{The calculation of the volumetric mass transfer coefficient, if instead the inlet/outlet
+concentration the average concentration is used.\label{fig:average:concentration}}
+\end{figure}
+One can see that the average concentration requires more than 2 millions time iterations to come to
+the steady-state.
+
 \section{Other boundary conditions}
@@
 deviation from the continuous picture. \label{fig:steady:state:jos} }
+\end{figure}
+
+\section{Grid Refinement}
+We performed a grid refinement study and compared it with the original data. For this purpose we
+doubled every fluid node and ran simulations. One can see {\color{red} That's what I have at the
+moment - need to write parallel version for the grid refinement} in Fig. \ref{fig:grid:comparison}
+the comparison between original size and refined grid simulations data. The results are close,
+especially it's important for larger velocities, where diffusion layer is underresolved.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/steady_state_comparison_grid.eps}
+\caption{Comparison between the usual and refined grid simulations. One
+can see that curves are close.\label{fig:grid:comparison}}
 \end{figure}

### 2011-09-14 GridCode/jos_parallel.cpp

@@ -633,48 +633,41 @@ void stream()
 
 void calculate_mass_transfer(int time_counter)
 {
-	static std::ofstream fconc("concentration.dat");
 	
-    double conc=0.0;
-    int counter; 	
-    for(int iY=0;iY<NY;iY++)
-		if (bottom[iY]==top[iY])
-			for(int iX=1;iX<NX-1;iX++)
-				conc+=rho[iY*NX+iX];
-		else
-		{
-			if (top_mid[iY]==bottom_mid[iY])
-			{
-				for(int iX=1;iX<=bottom[iY];iX++)
-					conc+=rho[iY*NX+iX];
-				for(int iX=top[iY];iX<NX-1;iX++)
-					conc+=rho[iY*NX+iX];
-			}
-			else
-			{
-				for(int iX=1;iX<=bottom[iY];iX++)
-					conc+=rho[iY*NX+iX];
-				for(int iX=bottom_mid[iY];iX<=top_mid[iY];iX++)
-					conc+=rho[iY*NX+iX];
-				for(int iX=top[iY];iX<NX-1;iX++)
-					conc+=rho[iY*NX+iX];
-			}
-		}
-		
-	double conc_inlet=0.0;
-	double conc_outlet=0.0;
-	double sum_vel_inlet=0.0;
-	double sum_vel_outlet=0.0;
-	for(int iX=1;iX<NX-1;iX++)
+	if (mpi_rank==0)
 	{
-		conc_inlet+=rho[iX]*uy[iX];
-		sum_vel_inlet+=uy[iX];
-		conc_outlet=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
-		sum_vel_outlet=uy[(NY-1)*NX+iX];
-	}
-	
+		static std::ofstream fconc("concentration.dat");
 
-	fconc<<time_counter<<" "<<conc<<" "<<conc_inlet/sum_vel_inlet<<" "<<conc_outlet/sum_vel_outlet<<"\n"<<std::flush;
+		double conc_inlet=0.0;
+		double sum_vel_inlet=0.0;
+		for(int iX=1;iX<NX-1;iX++)
+		{
+			conc_inlet+=rho[iX]*uy[iX];
+			sum_vel_inlet+=uy[iX];
+		}
+
+		conc_inlet=conc_inlet/sum_vel_inlet;
+		double conc_outlet;
+		MPI_Status status;
[…]

### 2011-09-14 GridCode/mass_transfer_jos_grid.cpp

@@ -553,7 +553,7 @@ void calculate_mass_transfer(int time_counter)
 		conc_inlet+=rho[iX]*uy[iX];
 		sum_vel_inlet+=uy[iX];
 		conc_outlet=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
-		sum_vel_outlet=uy[(NY-1)*NX+iX];
+		sum_vel_outlet+=uy[(NY-1)*NX+iX];
 	}
 	
 

### 2011-09-14 Python/curves.py

@@ -5,6 +5,8 @@ import pylab
 import math
 import os
 import subprocess
+import glob
+
 
 def Produce_Bunch():
     print os.getcwd()
@@ -133,7 +135,8 @@ def Produce_Mass_Bunch_Sailfish():
     styles=['kv','ks','ko','k^','k>','k<','kD','kh']
     aver_coefficient=[]
     bubble_velocities=[]
-    dirs=[3,5,8,10,20,40,60,80]
+    #dirs=[3,5,8,10,20,40,60,80]
+    dirs=[5,8,10,20,40,60]
     #dirs=[3,5,8,10,20]    
     fig=pylab.figure(99)
 
@@ -201,6 +204,169 @@ def Produce_Mass_Bunch_Sailfish():
     print "Aver_coefficient=",aver_coefficient
     return aver_coefficient
 
+def Produce_Mass_Bunch_Sailfish_Average():
+    #physical parameters
+    gamma=0.0728
+    diam=1.5e-3    
+    print os.getcwd()
+ 
+    styles=['kv','ks','ko','k^','k>','k<','kD','kh']
+    aver_coefficient=[]
+    bubble_velocities=[]
+    #dirs=[3,5,8,10,20,40,60,80]
+    dirs=[5,8,10,20,40,60]
+    #dirs=[3,5,8,10,20]    
+    fig=pylab.figure(99)
+
+    for counter,dir_name in enumerate(dirs):    
+        data_dir_name="SailfishData/"+str(dir_name)+"/"
+        file_name=data_dir_name+"capillary200000.npz"        
+        arr=numpy.load(file_name)        
+        phase=arr['phi']
+        velx=arr['v'][0]
+        vely=arr['v'][1]
+        dims=phase.shape
+
+        print "Dimensions=",dims
+
+        center=phase[dims[0]/2,:]
+        z1 = numpy.min(numpy.where(center < 0.0))
+        z2 = numpy.max(numpy.where(center < 0.0))
+        slug_length=dims[1]-z2+z1    
+        if z1==0:
+            z2=numpy.min(numpy.where(center>0.0))+dims[1]
+            z1=numpy.max(numpy.where(center>0.0))
+            slug_length=z1-z2%dims[1]
+        print z1,z2
+
+        interface_velocity=velx[dims[0]/2,z2%dims[1]]
+        capillary=interface_velocity*(2.0/3.0)/math.sqrt(8*0.04*0.04/9.0)
+        reynolds=interface_velocity*dims[0]/(2.0/3.0)        
[…]

### 2011-09-14 SimpleCode/mass_open_boundaries.cpp

@@ -529,7 +529,7 @@ void calculate_mass_transfer(int time_counter)
 		conc_inlet+=rho[iX]*uy[iX];
 		sum_vel_inlet+=uy[iX];
 		conc_outlet=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
-		sum_vel_outlet=uy[(NY-1)*NX+iX];
+		sum_vel_outlet+=uy[(NY-1)*NX+iX];
 	}
 	
 

### 2011-09-15 Text/paper.tex
Minor revisions.

@@
 deviation from the continuous picture. \label{fig:steady:state:jos} }
+\end{figure}
+If two domains are joined together then results are quite different. One can see them in Fig.
+\ref{fig:steady:state:jos:double}.
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/steady_state_double_jos.eps}
+\caption{The mass transfer coefficient versus time for doubled domain. One can see that the
+volumetric mass transfer coefficients are smaller in comparison with one unit volume simulation. As
+well one needs to wait longer time as the mass comes from one bubble to another bubble. 
+\label{fig:steady:state:jos:double}}
 \end{figure}

### 2011-09-15 Python/curves.py

@@ -426,19 +426,53 @@ def Produce_Mass_Bunch_Jos():
         print "Reynolds=",reynolds
   
         #dir_name="SailfishMassBGK/"+str(dir_name)+"/"
-        dir_name="SailfishMassJos/"+str(dir_name)+"/"     
-        name=dir_name+"concentration.dat"
-        array=numpy.loadtxt(name)
         
+        results_dir_name="SailfishMassJos/"+str(dir_name)+"/"     
+        
+        files_names=glob.glob(results_dir_name+"density*.dat")
+        vx=numpy.loadtxt("SailfishResults/"+str(dir_name)+"/ux.dat").transpose()
+        files_names=sorted(files_names)
+        coefficient=[]
+        time_iterations=[]
+        for file_example in files_names:
+            print file_example,
+            density=numpy.loadtxt(file_example)
+            inlet_conc=numpy.sum(density[1:-1,1]*vx[1:-1,1])/numpy.sum(vx[1:-1,1])
+            outlet_conc=numpy.sum(density[1:-1,-2]*vx[1:-1,-2])/numpy.sum(vx[1:-1,-2])
+            coefficient.append((superficial_liquid+gas_holdup*interface_velocity)*phys_velocity/interface_velocity\
+                   /(15*diam)*numpy.log((1-numpy.abs(inlet_conc))/(1-numpy.abs(outlet_conc))))
+            time_iterations.append(int(file_example[-11:-4]))
+        numpy.savetxt(results_dir_name+"coefficient.dat",zip(time_iterations,coefficient))
+
+            
+        #array=numpy.loadtxt(results_dir_name+"concentration.dat")        
         #new_conc=numpy.array(zip(array[1:,0]-array[:-1,0],array[1:,1]-array[:-1,1],array[1:,2]))
         #deltat=interface_velocity/phys_velocity*diam/(dims[0]-2)   
         #print "Data=",new_conc
         #coefficient=new_conc[:,1]/(200*3000)/(deltat*new_conc[:,0]*(1.0-numpy.abs(new_conc[:,2])))
-        coefficient=(superficial_liquid+gas_holdup*interface_velocity)*phys_velocity/interface_velocity\
-                   /(15*diam)*numpy.log((1-numpy.abs(array[:,2]))/(1-numpy.abs(array[:,3])))
+        
[…]

### 2011-10-28 Text/paper.tex
Started analyzing small results available.

@@
 \end{table}
+
+\subsection{Comparison between different boundary conditions}
+The mass transfer coefficient by the definition of used in the paper of \citet{vanbaten} is as
+follows:
+
+In what follows we will examine different boundary conditions for the mass transfer:
+\begin{description}
+ \item[I] Placement the bubble near the entrance with the periodic bondary conditions and using the
+outlet concentration as the characteristic value of the 
+\item[II] 
+\end{description}
+
+\begin{figure}[htb!]
+\caption{Comparison between different simulations and definitions of the characteristic
+concentration.}
+\end{figure}
 

### 2011-10-28 Python/multiple.py

@@ -18,8 +18,8 @@ def Produce_Single():
     aver_coefficient=[]
     bubble_velocities=[]
     #dirs=[3,5,8,10,20,40,60,80]
-    dirs=[3,5,8,10,20,40,60,80]
-    #dirs=[3,5,8,10,20]    
+    #dirs=[3,5,8,10,20,40,60,80]
+    dirs=[3,5,8,10]    
     
    
     for counter,dir_name in enumerate(dirs):    
@@ -77,6 +77,16 @@ def Produce_Single():
         ###Open boundaries options
         open_dir_name="SailfishMassCentralSingle/"+str(dir_name)+"/"     
         open_conc=numpy.loadtxt(open_dir_name+"concentration.dat")       
+         
+        coefficient_open=[]        
+        for file_number in numpy.arange(1160000,4000000,280000):
+            density_number=numpy.loadtxt(open_dir_name+"density"+str(file_number)+".dat")
+            inlet_conc=numpy.sum(density_number[1:-1,1]*ux[1:-1,1])/numpy.sum(ux[1:-1,1])
+            outlet_conc=numpy.sum(density_number[1:-1,-2]*ux[1:-1,-2])/numpy.sum(ux[1:-1,-2])
+            coefficient_open.append((superficial_liquid+gas_holdup*interface_velocity)*phys_velocity/interface_velocity\
+                   /(15*diam)*(1-abs(inlet_conc))/(1-abs(outlet_conc)))
+        open_time=numpy.arange(1160000,4000000,280000) 
+        print coefficient_open        
         #files_names=glob.glob(results_dir_name+"density*.dat")
         #vx=numpy.loadtxt("SailfishResults/"+str(dir_name)+"/ux.dat").transpose()
         #files_names=sorted(files_names)
@@ -90,8 +100,8 @@ def Produce_Single():
         #    time_iterations.append(int(file_example[-11:-4]))
         #numpy.savetxt(results_dir_name+"coefficient.dat",zip(time_iterations,coefficient))
 
-        coefficient_open=((superficial_liquid+gas_holdup*interface_velocity)*phys_velocity/interface_velocity\
-                   /(15*diam)*numpy.log((1-numpy.abs(open_conc[:,2]))/(1-numpy.abs(open_conc[:,3]))))        
[…]

### 2011-10-28 SimpleCode/mass_open_boundaries.cpp

@@ -528,7 +528,7 @@ void calculate_mass_transfer(int time_counter)
 	{
 		conc_inlet+=rho[iX]*uy[iX];
 		sum_vel_inlet+=uy[iX];
-		conc_outlet=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
+		conc_outlet+=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
 		sum_vel_outlet+=uy[(NY-1)*NX+iX];
 	}
 	

### 2011-11-01 Text/introduction.tex
Started a new document about definition of the mass transfer.

--- 2011-09-14 Text/paper.tex
@@
 \documentclass{article}
+\usepackage{amsmath,amssymb}
+\usepackage{bm}
 \usepackage[numbers,sort&compress]{natbib}
 \usepackage{graphicx}
-\usepackage{amssymb,amsmath}
-\usepackage{bm}
 \usepackage{color}
@@
 \begin{document}
-\section{Motivation}
-The mass transfer is a very important characteristic for microchannels  design. It allows to
-properly manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner. In
-what follows the mass transfer associated with the bubble moving in the microchannel through liquid
-medium is studied.
+\section{Mass transfer definitions}
+By the definition the mass transfer coefficient is the following:
+\beq
+k_L=\frac{\dot{m}}{P \Delta C},
+\feq
+where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
+$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference $\Bigl[\frac{kg}{m^3}\Bigr]$.
+Therefore, $k_L$ has a dimension of velocity $\Bigl[\frac{m}{s}\Bigr]$.
 
-A few questions need to be addressed:
-\begin{description}
- \item[I] The efficiency of the mass transfer depending on the capillary number. For small capillary
-numbers as $Ca<0.6$ for square microchannels there is a vortex in the reference frame moving with
-the bubble, which  influences and improves the corresponding mass transfer. 
-Note that the flow
-patterns strongly depend on the number of parameters as the slug length, the thickness of the
-thickness and the existence of the vortex in front of the bubble. There are some available
-correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
-this work is to study mass transfer dependence on the number of parameters. Another goal is to
-validate and to come up with another correlation describing the mass transfer.
+There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
+theoretical definitions of the mass transfer in case of the point sources.
+\subsection{Point mass sources}
+In what follows we will present three approaches to calculate the mass points mass transfer
+coefficients:
+\begin{enumerate}
+\item
+Let us look at the infinitisemal small domain of the volume $A \Delta x$ in a steady-state, not
+moving and with the mass source. Then the concentration difference can be found as $\Delta C = C^* -
+C(t)$, where $C^*$ is the imposed concentration on the infinitesimal concentration source, $C(t)$ is
+the time depending average concentration. Therefore one can write the time dependent ODE for the
+average concentration in the domain:
+\beq
+\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (C^{*}-C(t)), 
+\feq
+with the initial condition $C(0)=0$
+The solution in time becomes as follows:
+\beq
+C(t)= C^{*}(1-\exp(-k_L a t )), 
+\feq
+where $k_L a$ is the volumetric mass transfer coefficient.
 
- \item[II] Another important quantity is to study the mixing processes inside the slug. One of the
-possible characteristics of the mixing is a residence time distribution. Once the step function
-of tracer is introduced in the liquid film, then the concentration of tracer with time is
-measured at the outlet. The form of the signal and especially its standard deviation is responsible
-for mixing. However, from numerical point of view this study requires the repetition of domain a
-few times to see the tracer propagation. Thus, we do not currently address mixing with our
-simulations.
-\end{description}
-
-To address the questions arised we will utilize the results of numerical simulations of flow
-obtained
-before \cite{kuzmin-binary2d}. The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
-the same figure, one can see the proposed benchmark for the tracer. The
-physical
-picture for the proposed numerical benchmark is  related to classical experiments conducted by
-\citet{bercic-mass}. In their work authors studied gas-liquid mass transfer coefficient by
-injecting methane as the gas bubble and measuring the dissolved concentration of methane in water
-along the channel. This situation implies the periodic boundary conditions and steady-state motion
-of bubbles.
-
-The numerical  procedure of studying mass transfer is presented in the following steps:
-\begin{description}
- \item[Flow field] The hydrodynamics for the bubble motion in the periodic domain is obtained
-according to the work \cite{kuzmin-binary2d}. The grid resolution is taken to insure grid
-independency of results.  
- \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
-are conducted in the moving
-reference frame with the bubble. Then the bubble stands still and the flow is coming around the
-bubble. We impose a steady concentration of solutant on the surface of the bubble.
-\item[Mass transfer] One needs not only perform a Galilean transformation to the reference
-frame moving with the bubble but also to
-transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
-slug. 
-\end{description}
+\item
+The previous consideration is able to predict mass transfer happening in moving with the velocity
+$U$ liquid, see Fig. \ref{fig:moving:frame}.
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/benchmark_new.eps}\\
-\\
-\\
-\\
-\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}
-\caption{The two-dimensional benchmarks for the hydrodynamics (top) and the mass transfer
-coefficient (bottom). \label{fig:benchmark}}
+\includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
+\caption{The mass transfer in the moving liquid. \label{fig:moving:frame}}
 \end{figure}
 
-\section{Mass Transfer Correlations}
-\label{sec:correlations}
-We examine the following three characteristic correlations:
-\begin{description}
-\item[I]
-In what follows we want to address the following empirical correlation for the volumetric mass
-transfer coefficient addressed in the recent
-publication by \citet{yue-mass}:
+The mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
+mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
+source is a point source with the effective perimeter P. The accumulated mass should be proportional
+to the mass transfer coefficient:
+\beq
+U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(C^{*}-C(x)\bigr), 
+\feq 
+giving the same equation but only in the coordinate domain:
+\beq
+C(x)= C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
+\label{main:mass:transfer:expression} 
+\feq
+
+\item If one transfers to the frame moving with the liquid velocity $U$, then the situation will be
+the same as in the first case. However, one can connect the time and spatial location with the
+velocity $U$ ($t=\frac{x}{U}$) to obtain the same equation as in the case 2.
+\end{enumerate}
+
+The expression (\ref{main:mass:transfer:expression}) was used in the experiments by
+\citet{bercic-mass}. One should be accurate with the definition of velocities because we have two
+different phases. Usually, one can take the velocity $U$ to be as
+average velocity or $U=U_{gas}+U_{liq}$, where $U_{gas}$ and $U_{liq}$ are liquid and gas
+superficial velocities correspondingly. In this case, the continuouty assumption is restored and
+all considerations above are valid.
+
+ However, if one wants to analytically estimate the mass transfer coefficients, the situation is
+much more complicated because of the two phases presence. Phases can have different mixing patterns
+from film to slug and from slug to film. The analytical approaches described above assume that the
+contributions from film and bubble caps can be calculated separately. However one can see that such 
+an assumption for bubble caps (slug well mixed and the concentration is uniformly distributed over
+the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
+concentration from film is mixed with the slug and changes the overall concentration in the slug.
+Another issue is that if the slug is long enough then the film saturates with the tracer
+concentration and its influence on the mass transfer can be negligible \cite{vanbaten-circular}.
+Mixing patterns of the film and the liquid slugs are of great importance for the analytical
+estimation of the mass transfer \cite{yue-mass}.
+
+\subsection{Numerical calculation}
+In the numerical simulation it is not possible to simulate really long domains with the infinite
+number of the bubbles. As we saw before there are two approaches towards it - either to simulate
+the bubble train and then to measure concentration along the pipe, Eq.
+\ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with bulk
+velocity $U$ and conduct the same measurements through Eq. \ref{main:mass:transfer:expression}.
+However, both methods do require a tracking of moving bubbles which is complicated from the
+numerical point of view.
+
+Therefore, one needs to come up with the simple smaller domain calculations
+of the mass transfer coefficient, which represent the continuous picture with infinite numbers of
+the bubbles closely. In comparison with analytical estimations of the mass transfer coefficient,
+where the mixing patterns are extremely important, the numerical simulations need only to mimic
+the continous picture and provide the way to calculate the volumetric mass transfer coefficient.
+
+We perform simulations in the frame moving with the bubble (velocity
+$U_{bubble}$), that the bubble position stands steady. The bubble velocity $U_{bubble}$ is
+different from the bulk velocity $U_{gas}+U_{liq}$. In this case we need to perform coordinate
+change:
+\beqal
+&x(t)=U_{bubble}t\\
+&C(x)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a \frac{x}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
+&C(t)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)
+\feqal
+If the unit volume that we simulate is quite long one can obtain the values of the concentration
+in the inlet and outlet as a function of time:
+\beqal
+&C(U_{bubble}\, t)=C^{*}\Bigl(1-\exp\bigr(-k_L\, a\, t
+\frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
+&C(U_{bubble}\,t+L_{unit})=C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{
+U_{bubble}\,t+L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
+&=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\exp\bigl(-k_L a
+\frac{L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)
+\feqal
+Therefore the mass transfer coefficient can be calculated as follows:
 \begin{equation}
-k_L a=\frac{2}{d_h} \Bigl(\frac{D
-U_{\mathrm{bubble}}}{L_{\mathrm{bubble}}+L_{\mathrm{slug}}}\Bigr)^{0.5}
-\Bigl(\frac{L_{\mathrm{bubble}}}{L_{\mathrm{bubble}}+L_{\mathrm{slug}}}\Bigr)^{0.3}.
-\end{equation}
-This correlation is within $10\%$ accuracy for experimental results for the following range of
-parameters: bubble velocity $0.4\,\mathrm{m/s}<U_{\mathrm{bubble}}<2\,\mathrm{m/s}$, bubble length
-$1.4<\frac{L_{\mathrm{bubble}}}{d_h}<6.3$, slug length $1<\frac{L_{\mathrm{slug}}}{d_h}<3.2$,
-hydrodynamic diameter $d_h = 400
-\mathrm{\mu m}$.
-
-\item[II]
-For long slug lengths in circular capillaries, where the mass transfer from bubble caps is
-predominant, the folowing correlation is derived by
-\citet{bercic-mass}:
-\begin{equation}
-k_L a = \frac{0.111
-(U_{\mathrm{gas}}+U_{\mathrm{liq}})^{1.19}}{\bigl((1-\varepsilon_{\mathrm{gas}})(L_{\mathrm{bubble}}
-+L_ {\mathrm{slug}} )\bigr)^{0.57} },
-\end{equation}
-where $\varepsilon_{\mathrm{gas}}=\frac{U_{\mathrm{gas}}}{U_{\mathrm{bubble}}}$ is the gas holdup,
-$U_{\mathrm{gas}}$ is the superficial gas velocity, and $U_{\mathrm{liq}}$ is the superficial
-liquid velocity. The superficial liquid velocity is calculated with the steady state condition in
-the middle of the slug as:
-\begin{equation}
-U_{\mathrm{liq}}=\frac{\oint U \mathrm{d}A}{A}.
-\end{equation}
-The superficial liquid velocity can be calculated through the calculated bubble volume and gas
-holdup. For the two-dimensional case it is represented as:
-\begin{equation}
+\label{theor:continuous:mass:transfer}
 \begin{aligned}
-&\varepsilon_{\mathrm{gas}}=\frac{\text{bubble area}}{15 H^2}\\
-&U_{\mathrm{gas}}=\varepsilon_{\mathrm{gas}} U_{\mathrm{bubble}}.
+&-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
+&k_L a
+=\frac{U_{gas}+U_{liq}}{L_{unit}}\ln\Bigl(\frac{C^{*}-C_{inlet}}{C^{*}-C_{outlet}}
+\Bigr)
 \end{aligned}
 \end{equation}
+If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$
+then the expression for the volumetric mass transfer coefficitent $k_L a$ can be simplified:
+\beq
+\vol=\frac{\Delta C}{C^{*}} \frac{U_{gas}+U_{liq}}{L_{unit}},
+\feq
+where $\Delta C=C_{outlet}-C_{inlet}$. If we go to the continuous formulation by changing $L_{unit}$
+to be a continuous coordinate $x$, then the following can be obtained \cite{jos-mass}:
+\beq
+\Delta C = C^{*} \vol \frac{x}{U_{gas}+U_{liq}}
+\label{small:conc:mass:estimation}
+\feq
 
-Since experiments done by \citeauthor{bercic-mass} were only for one diffusivity coefficient
-$D=2\times 10^{-9}\,\mathrm{m^2/s}$, the effective equation should be rescaled as:
-\begin{equation}
-k_L a = \sqrt{\frac{D}{2\times 10^{-9}\,\mathrm{m^2/s}}}\frac{0.111
-(U_{\mathrm{gas}}+U_{\mathrm{liq}})^{1.19}}{\bigl((1-\varepsilon_{\mathrm{gas}})(L_{\mathrm{bubble}}
-+L_ {\mathrm{slug}} )\bigr)^{0.57} },
-\end{equation}
+We consider the following possibilities of conducting numerical simulations:
+\begin{enumerate}
+ \item 
+The tracer picking up procedure can be introduced
+in the manner of the considerations above. We impose the concentration at the entrance to be
+constant $C(0,y)=C_{inlet}$, at the outlet we impose the outflow boundary condition $\frac{\partial
+C}{\partial x}(L,y)=0$. To be compliant with the considerations above one needs to impose as well
+the outflow boundary conditions for the inlet as well. However, without loss of the generality one
+can impose $C_{inlet}=0$, since the walls in the reference frame
+moving with the bubble are moving from the inlet to the outlet. That means that no tracer
+concentration leaves domain from the inlet side, which is true for the capillary numbers larger
+than $0.6$.  However, this boundary condition can not be used in the case of small capillary
+numbers, since there is a strong circulation in front of the bubble. One can see the sketch of the
+approach in Fig. \ref{fig:benchmark:jos}. The longer the numerical domain length the better will be
+results. One can estimate the volumetric mass transfer coefficient in this case through the equation
+(\ref{small:conc:mass:estimation}) for small concentrations. Note a few considerations:
+\begin{itemize}
+\item  The considerations above were established for the homogenous velocity field. In the case of
+the non-homogenous velocity field one needs to obtain a concentration from the mass flux:
+\beq
+C_{outlet}=\frac{\int{U(y) C(L_{unit},y) \mathrm{d}y}}{\int{U(y) \mathrm{d}y}}.
+\feq
+\item Note, that one cannnot use the definition of the mass transfer coefficient as far as it
+varies through the bubble due to inhomogenoities of the flow. Therefore, the volumetric mass
+transfer coefficient is introduced that takes into the account the bubble geometry.
+\end{itemize}
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
+\caption{The numerical mass transfer benchmark. \label{fig:benchmark:jos}}
+\end{figure}
 
-\item[III]
-\citet{vanbaten-circular} performed numerical simulations for circular capillaries by assuming that
-there is a separate contribution of the liquid film and the bubble caps to mass transfer. Their
-correlation is as:
-\begin{equation}
-k_L a = \frac{2}{\sqrt{\pi}}\sqrt{\frac{D U_{\mathrm{bubble}}}{(L_{\mathrm{bubble}}-d_h)}}
-\frac{4(L_{\mathrm{bubble}}-d_h)}{d_h(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}+2\frac{\sqrt{2}}{\pi}
- \sqrt{\frac{D U_{\mathrm{bubble}}}{d_h}} \frac{4}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})}.
-\end{equation}
-This correlation is valid for short contact times, when the mass transfer is important from bubble
-caps as well as from the film. Short contact times are defined through Fourier number as:
-\begin{equation}
-Fo=\frac{D t_{\mathrm{film}}}{\delta^2},
-\end{equation}
-where $t_{\mathrm{film}}=\frac{L_{\mathrm{film}}}{U_{\mathrm{bubble}}}$ is the time exposure of the
-bubble while it propagates through distance $L_{\mathrm{film}}$. The Fourier number is assumed to
-be small if $Fo<0.1$. If $Fo>1$ then the liquid film is saturated and the mass transfer occurs from
-the bubble caps.
-
-\end{description}
-
-Overall work goal is to compare numerical simulations with given correlations and to establish a
-new one.
+\item Another possibility is to use the periodic boundary conditions as the limiting case of the
+continuous formulation. In this case the inlet and outlet concentrations are not much different
+($C(x)=C(x+L_{unit})=C(x+\Delta x)\approx C_{media}$, see Fig. \ref{fig:moving:frame}), where
+$C_{media}$ is the mass averaged over domain concentration. This formulation requires the periodic
+boundary condition $C_{inlet}=C_{outlet}$. By the definition the mass transfer coefficient is
+proportional to the gain of the mass in the system divided by the concentration difference:
+\beq
+j=\frac{\dot{m}}{P \Delta C}=\frac{\dot{m}}{P (C^{*}-C_{media})},
+\feq
+where mass difference in the domain can be calculated as:
+\beq
+\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{C(t_2)\mathrm{d}V}-\int{C(t_1)\mathrm{d}V}}{t_2-t_1}.
+\feq
+Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
+considerably large and the tracer is well mixed in the slug, as one can take the concentration
+difference as $\Delta C = C^{*}-C_{media}$. The best case scenario is when $C_{media}$ is close to
+zero, in this case we can be sure that the flux to the domain is calculated precisely and periodic
+boundary conditions are fulfilled.
+\end{enumerate}
 
@@
 
-\section{Simulation results}
-\subsection{Steady-state}
-Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
-the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
-a steady-state condition the average of concentration values between $500000$ to $1000000$ time
-steps.{\color{red} We need to put more time steps. As well it is probably connected with Fourier
-number.} The average calculated volumetric mass transfer coefficients values are presented in Table
-\ref{table:volumetric:coefficients}. For each of the measurements we as well provided the Fourier
-number (for the flow between plates is as follows):
-\begin{equation}
-Fo=\frac{D t_{\mathrm{film}}}{\delta^2}=\frac{D
-(L_{\mathrm{bubble}}-H)}{U_{\mathrm{bubble}}\delta^2}.
-\end{equation}
-To understand the influence of the mass transfer in the film we provided the time needed for
-diffusion to reach the film thickness distance (95\% confidence interval of the film thickness):
-\begin{equation}
-\delta\approx 2\sqrt{2}\sqrt{D t};\ t \approx \frac{\delta^2}{8 D};\ N_{iter}=\frac{t}{\Delta t}.
-\end{equation}
+\section{Comparison between different approaches}
+We consequently will examine different approaches to the mass transfer definition, Fig.
+\ref{fig:comparison:one:unit:cell}:
+\begin{description}
+\item[I] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
+is located near the entrance of the computational domain, and the characteristic concentration is
+the inlet/outlet concentration, Fig \ref{fig:benchmark}. 
+\item[II] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a
+bubble is located in the middle of the computational domain, and the characteristic concentration
+is the inlet/outlet concentration.
+\item[III] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
+is located in the middle of the computational domain, and the characteristic concentration is the
+average concentration.
+\item[IV] Definition with the concentration jump between inlet and outlet over one unit cell.
+\end{description}
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}
+\caption{The two-dimensional benchmarks for the hydrodynamics (top) and the mass transfer
+coefficient (bottom). \label{fig:benchmark}}
+\end{figure}
 
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/steady_state.eps}
-\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
-state can be reached after $500000$. The mass transfer coefficient is taken as the average of
-concentration values between $500000$ to $1000000$ time steps.\label{fig:steady:state}}
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_entrance.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_aver.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_middle_outlet.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_jos_inlet_outlet.eps}\\
+\caption{\label{fig:comparison:one:unit:cell}}
 \end{figure}
+All the comparison is summarized in Table \ref{table:one_unit_comparison}.
 \begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
 \hline
-$Ca$&$Fo$&$k_L a,\,\mathrm{s}^{-1}$&$N_{iter}$\\
+$Ca$&$Fo$&$\vol_{ent},\,\mathrm{s}^{-1}$&\\
 \hline
-$0.026$&$0.08493$&$0.2737$&$873984$\\
-$0.047$&$0.02160$&$0.3664$&$1835817$\\
-$0.080$&$0.00588$&$0.4959$&$3965227$\\
-$0.065$&$0.00862$&$0.4734$&$3149710$\\
-$0.222$&$0.00103$&$0.8505$&$8195770$\\
-$0.479$&$0.00034$&$1.1541$&$12399627$\\
-$0.736$&$0.00018$&$1.1801$&$14683652$\\
-$0.989$&$0.00012$&$1.2215$&$16101062$\\
+$0.026$&$0.08493$&$0.2737$&$0.1692$&$0.2631$&$3.6756$\\
+$0.047$&$0.02160$&$0.3664$&$0.2852$&$0.4553$&$11.4822$\\
+$0.080$&$0.00588$&$0.4959$&$0.4079$&$0.6920$&$15.1964$\\
+$0.065$&$0.00862$&$0.4734$&$0.4303$&$0.8923$&$21.4517$\\
+$0.222$&$0.00103$&$0.8505$&$0.6109$&$0.8679$&N/A\\
+$0.479$&$0.00034$&$1.1541$&$0.9884$&$1.2995$&N/A\\
+$0.736$&$0.00018$&$1.1801$&$1.2199$&$1.1555$&N/A\\
+$0.989$&$0.00012$&$1.2215$&$1.3400$&$1.0350$&N/A\\
 \hline
 \end{tabularx}
-\caption{Simulation results for different capillary numbers. \label{table:volumetric:coefficients}}
+\caption{Simulation results for different capillary numbers.
+\label{table:one_unit_comparison}}
 \end{table}
-
-\subsection{Comparison between correlations and results}
-Comparison between correlations and simulations one can find in Fig.
-\ref{fig:comparison:correlations}. The simulated results exhibit larger mass transfer in comparison
-with the given correlations. {\color{red} Need to recalculate and check the kinematic viscosities.}
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/comparison_correlations.eps}
-\caption{One can see the comparison between correlations and simulations. {\color{red} Last two
-points can be eliminated due to improper imposement of the concave structure of the bubble. The
-large deviation of the results can be probably explained by the flow between plates in comparison
-with the flow in circular and square microchannels.} \label{fig:comparison:correlations}}
-\end{figure}
-
-\subsection{Average concentration}
-As far as we used the inlet/outlet concentration in the expression of the calculation of the
-volumetric mass transfer coefficient. However, the bubble in simulations located closely to the
-inlet and with periodic boundary conditions that can change the volumetric mass transfer
-coefficient significantly. As it will be discussed later in the appendix section, the assumption of
-the periodic boundary conditions requires the continuous picture. The continuous picture requires as
-well the average concentration to be of constant value. If the average concentration is used for
-the calculation of the volumetric mass transfer coefficient {\color{red} (which can be more
-adequate)}, then the volumetric mass transfer coefficient is more close to the correlation values,
-see Fig. \ref{fig:average:concentration}. 
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/steady_state_average.eps}
-\caption{The calculation of the volumetric mass transfer coefficient, if instead the inlet/outlet
-concentration the average concentration is used.\label{fig:average:concentration}}
-\end{figure}
-One can see that the average concentration requires more than 2 millions time iterations to come to
-the steady-state.
-
-\section{Other boundary conditions}
-We used the outflow boundary conditions for both boundaries and determined the coefficient
-according Eq. \ref{theor:continuous:mass:transfer}. One can see the calculated mass transfer
-coefficient in time in Fig. \ref{fig:steady:state:jos}.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/steady_state_jos.eps}
-\caption{The calculated mass transfer coefficient in time with open boundaries $\partial_x
-C_{inlet}=\partial_x C_{outlet}=0$. One can see some negative values for volumetric coefficients.
-This situation corresponds to the case, then the inlet concentration is greater than the outlet
-$C_{inlet}>C_{outlet}$. This corresponds to smaller capillary numbers due to vortex in front of the
-bubble. It is the indication that one needs to take more time steps to wait until the outlet
-concentration becomes larger than the inlet, which can take a relatively large time period to
-wait. Large numbers of the volumetric mass transfer coefficients means the insuffient number of
-the unit volumes simulated, as the large difference in the outlet and inlet numbers means the
-deviation from the continuous picture. \label{fig:steady:state:jos} }
-\end{figure}
-
-\section{Grid Refinement}
-We performed a grid refinement study and compared it with the original data. For this purpose we
-doubled every fluid node and ran simulations. One can see {\color{red} That's what I have at the
-moment - need to write parallel version for the grid refinement} in Fig. \ref{fig:grid:comparison}
-the comparison between original size and refined grid simulations data. The results are close,
-especially it's important for larger velocities, where diffusion layer is underresolved.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/steady_state_comparison_grid.eps}
-\caption{Comparison between the usual and refined grid simulations. One
-can see that curves are close.\label{fig:grid:comparison}}
-\end{figure}
-
-\appendix
-
-\section{Boundary conditions}
-In what follows we will examine different LBM implementations:
-\begin{description}
- \item[BB conditions] The walls can be treated via the simple bounce back rule:
-\begin{equation}
-f_{\bar{i}B}=f_{iF},\text{ for } \forall i,
-\end{equation}
-where $B$ is the boundary node with coordinates $\bm{r_F}+\bm{c_i}$, $F$ is the fluid node. This
-will fulfill the macroscopic conditions as:
-\begin{equation}
-J_{fluid}= \sum_{c_i\cdot n>0}{f_i c_i}=J_{wall},
-\end{equation}
-which is in turn represents the following boundary condition:
-\begin{equation}
-\partial_n J_n=\partial_n C u_n = u_n \partial_n C=0
-\end{equation}
-
-The walls can be treated through simmetric boundary conditions as well, which are really close to
-bounce-back formulation. In this case one can insure that the concentration values at the wall and
-at the fluid equal to each other.
-
-For the constant concentration at the bubble surface one can use the pressure anti
-bounce-back conditions
-\cite{ginzburg-boundary-main}:
-\begin{equation}
-f_{iB}=-f^{*}_{iF}+2 e_i(W),
-\end{equation}
-where the subscript $*$ stands for after-collision population, $W$ stands for the wall
-concentration to be imposed.
-\item[Inamuro conditions] Inamuro boundary conditions impose strict conservation of the population
-by utilizing diffuse interface kinetic boundary approach \cite{inamuro-scalar-boundary}. The
-unknown populations $f_i=w_i \rho^{\prime}\text{ for } \bm{c_i}\cdot \bm{n}>0$ are prescribed
-through the equilibrium conditions, where $\rho^{\prime}$ is an unknown parameter.Then the
-prescribed wall condition is as: 
-\begin{equation}
-\rho^{\prime}=\frac{\rho_{w}-\sum_{i,\bm{c_i}\cdot\bm{n}\leq0}
-f_i}{\sum_{i,\bm{c_i}\cdot\bm{n}>0}w_i}
-\end{equation}
-For the zero flux on the wall one can use another equation:
-\begin{equation}
-\rho^{\prime}=-\frac{i,\bm{c_i}\cdot\bm{n}\leq0}{\sum_{i,\bm{c_i}\cdot \bm{n}}{w_i \bm{c_i}\cdot
-\bm{n}}}.
-\end{equation}
-\end{description}
-
-\section{Mass transfer definitions}
-By the definition the mass transfer coefficient is the following:
-\beq
-k_L=\frac{\dot{m}}{P \Delta C},
-\feq
-where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
-$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference $\Bigl[\frac{kg}{m^3}\Bigr]$.
-Therefore, $k_L$ has a dimension of velocity $\Bigl[\frac{m}{s}\Bigr]$.
-
-There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
-theoretical definitions of the mass transfer in case of the point sources.
-\subsection{Point mass sources}
-In what follows we will present three approaches to calculate the mass points mass transfer
-coefficients:
-\begin{enumerate}
-\item
-Let us look at the infinitisemal small domain of the volume $A \Delta x$ in a steady-state, not
-moving and with the mass source. Then the concentration difference can be found as $\Delta C = C^* -
-C(t)$, where $C^*$ is the imposed concentration on the infinitesimal concentration source, $C(t)$ is
-the time depending average concentration. Therefore one can write the time dependent ODE for the
-average concentration in the domain:
-\beq
-\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (C^{*}-C(t)), 
-\feq
-with the initial condition $C(0)=0$
-The solution in time becomes as follows:
-\beq
-C(t)= C^{*}(1-\exp(-k_L a t )), 
-\feq
-where $k_L a$ is the volumetric mass transfer coefficient.
-
-\item
-The previous consideration is able to predict mass transfer happening in moving with the velocity
-$U$ liquid, see Fig. \ref{fig:moving:frame}.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
-\caption{The mass transfer in the moving liquid. \label{fig:moving:frame}}
-\end{figure}
-
-The mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
-mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
-source is a point source with the effective perimeter P. The accumulated mass should be proportional
-to the mass transfer coefficient:
-\beq
-U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(C^{*}-C(x)\bigr), 
-\feq 
-giving the same equation but only in the coordinate domain:
-\beq
-C(x)= C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
-\label{main:mass:transfer:expression} 
-\feq
-
-\item If one transfers to the frame moving with the liquid velocity $U$, then the situation will be
-the same as in the first case. However, one can connect the time and spatial location with the
-velocity $U$ ($t=\frac{x}{U}$) to obtain the same equation as in the case 2.
-\end{enumerate}
-
-The expression (\ref{main:mass:transfer:expression}) was used in the experiments by
-\citet{bercic-mass}. One should be accurate with the definition of velocities because we have two
-different phases. Usually, one can take the velocity $U$ to be as
-average velocity or $U=U_{gas}+U_{liq}$, where $U_{gas}$ and $U_{liq}$ are liquid and gas
-superficial velocities correspondingly. In this case, the continuouty assumption is restored and
-all considerations above are valid.
-
- However, if one wants to analytically estimate the mass transfer coefficients, the situation is
-much more complicated because of the two phases presence. Phases can have different mixing patterns
-from film to slug and from slug to film. The analytical approaches described above assume that the
-contributions from film and bubble caps can be calculated separately. However one can see that such 
-an assumption for bubble caps (slug well mixed and the concentration is uniformly distributed over
-the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
-concentration from film is mixed with the slug and changes the overall concentration in the slug.
-Another issue is that if the slug is long enough then the film saturates with the tracer
-concentration and its influence on the mass transfer can be negligible \cite{vanbaten-circular}.
-Mixing patterns of the film and the liquid slugs are of great importance for the analytical
-estimation of the mass transfer \cite{yue-mass}.
-
-\subsection{Numerical calculation}
-In the numerical simulation it is not possible to simulate really long domains with the infinite
-number of the bubbles. As we saw before there are two approaches towards it - either to simulate
-the bubble train and then to measure concentration along the pipe, Eq.
-\ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with bulk
-velocity $U$ and conduct the same measurements through Eq. \ref{main:mass:transfer:expression}.
-However, both methods do require a tracking of moving bubbles which is complicated from the
-numerical point of view.
-
-Therefore, one needs to come up with the simple smaller domain calculations
-of the mass transfer coefficient, which represent the continuous picture with infinite numbers of
-the bubbles closely. In comparison with analytical estimations of the mass transfer coefficient,
-where the mixing patterns are extremely important, the numerical simulations need only to mimic
-the continous picture and provide the way to calculate the volumetric mass transfer coefficient.
-
-We perform simulations in the frame moving with the bubble (velocity
-$U_{bubble}$), that the bubble position stands steady. The bubble velocity $U_{bubble}$ is
-different from the bulk velocity $U_{gas}+U_{liq}$. In this case we need to perform coordinate
-change:
-\beqal
-&x(t)=U_{bubble}t\\
-&C(x)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a \frac{x}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
-&C(t)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)
-\feqal
-If the unit volume that we simulate is quite long one can obtain the values of the concentration
-in the inlet and outlet as a function of time:
-\beqal
-&C(U_{bubble}\, t)=C^{*}\Bigl(1-\exp\bigr(-k_L\, a\, t
-\frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
-&C(U_{bubble}\,t+L_{unit})=C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{
-U_{bubble}\,t+L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
-&=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\exp\bigl(-k_L a
-\frac{L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)
-\feqal
-Therefore the mass transfer coefficient can be calculated as follows:
-\begin{equation}
-\label{theor:continuous:mass:transfer}
-\begin{aligned}
-&-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
-&k_L a
-=\frac{U_{gas}+U_{liq}}{L_{unit}}\ln\Bigl(\frac{C^{*}-C_{inlet}}{C^{*}-C_{outlet}}
-\Bigr)
-\end{aligned}
-\end{equation}
-If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$
-then the expression for the volumetric mass transfer coefficitent $k_L a$ can be simplified:
-\beq
-\vol=\frac{\Delta C}{C^{*}} \frac{U_{gas}+U_{liq}}{L_{unit}},
-\feq
-where $\Delta C=C_{outlet}-C_{inlet}$. If we go to the continuous formulation by changing $L_{unit}$
-to be a continuous coordinate $x$, then the following can be obtained \cite{jos-mass}:
-\beq
-\Delta C = C^{*} \vol \frac{x}{U_{gas}+U_{liq}}
-\label{small:conc:mass:estimation}
-\feq
-
-We consider the following possibilities of conducting numerical simulations:
-\begin{enumerate}
- \item 
-The tracer picking up procedure can be introduced
-in the manner of the considerations above. We impose the concentration at the entrance to be
-constant $C(0,y)=C_{inlet}$, at the outlet we impose the outflow boundary condition $\frac{\partial
-C}{\partial x}(L,y)=0$. To be compliant with the considerations above one needs to impose as well
-the outflow boundary conditions for the inlet as well. However, without loss of the generality one
-can impose $C_{inlet}=0$, since the walls in the reference frame
-moving with the bubble are moving from the inlet to the outlet. That means that no tracer
-concentration leaves domain from the inlet side, which is true for the capillary numbers larger
-than $0.6$.  However, this boundary condition can not be used in the case of small capillary
-numbers, since there is a strong circulation in front of the bubble. One can see the sketch of the
-approach in Fig. \ref{fig:benchmark:jos}. The longer the numerical domain length the better will be
-results. One can estimate the volumetric mass transfer coefficient in this case through the equation
-(\ref{small:conc:mass:estimation}) for small concentrations. Note a few considerations:
-\begin{itemize}
-\item  The considerations above were established for the homogenous velocity field. In the case of
-the non-homogenous velocity field one needs to obtain a concentration from the mass flux:
-\beq
-C_{outlet}=\frac{\int{U(y) C(L_{unit},y) \mathrm{d}y}}{\int{U(y) \mathrm{d}y}}.
-\feq
-\item Note, that one cannnot use the definition of the mass transfer coefficient as far as it
-varies through the bubble due to inhomogenoities of the flow. Therefore, the volumetric mass
-transfer coefficient is introduced that takes into the account the bubble geometry.
-\end{itemize}
-\begin{figure}
-\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
-\caption{The numerical mass transfer benchmark. \label{fig:benchmark:jos}}
-\end{figure}
-
-\item Another possibility is to use the periodic boundary conditions as the limiting case of the
-continuous formulation. In this case the inlet and outlet concentrations are not much different
-($C(x)=C(x+L_{unit})=C(x+\Delta x)\approx C_{media}$, see Fig. \ref{fig:moving:frame}), where
-$C_{media}$ is the mass averaged over domain concentration. This formulation requires the periodic
-boundary condition $C_{inlet}=C_{outlet}$. By the definition the mass transfer coefficient is
-proportional to the gain of the mass in the system divided by the concentration difference:
-\beq
-j=\frac{\dot{m}}{P \Delta C}=\frac{\dot{m}}{P (C^{*}-C_{media})},
-\feq
-where mass difference in the domain can be calculated as:
-\beq
-\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{C(t_2)\mathrm{d}V}-\int{C(t_1)\mathrm{d}V}}{t_2-t_1}.
-\feq
-Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
-considerably large and the tracer is well mixed in the slug, as one can take the concentration
-difference as $\Delta C = C^{*}-C_{media}$. The best case scenario is when $C_{media}$ is close to
-zero, in this case we can be sure that the flux to the domain is calculated precisely and periodic
-boundary conditions are fulfilled.
-\end{enumerate}
-
-\section{Solution of the semi-infinite concentration problems}
-\label{mass:transfer:correlation}
-For short contact times the mass transfer can be decomposed into two parts: transfer from the wall
-to semi-infinite medium and transfer from the sphere to the infinite medium. In what follows we
-derive analytical solutions to these two situations:
-\begin{description}
-\item[Wall mass transfer] The problem by mathematically is stated as:
-\begin{equation}
-\begin{aligned}
-&\partial_t C =D \partial^2_{xx} C\\
-&C(x,0)=0\\
-&C(0,t)=C_0\\
-\end{aligned}
-\end{equation}
-As far as the problem is non-homogenious one needs to decompose the problem into the steady-state
-and homogenous transient problem:
-\begin{equation}
-C=C_h + C_s,
-\end{equation}
-where $C_h$ and $C_s$ satisfy the following equations:
-\begin{equation}
-\begin{aligned}
-&\frac{\mathrm{d^2} C_s}{\mathrm{d}x^2}=0 && \partial_t C_h=D\partial^2_{xx} C_h\\
-&C_s(0)=C_0 && C_h(x,0)=-C_0\\
-&C_s(\infty)=C_0 && C_h(0,t)=0\\
-\end{aligned}
-\end{equation}
-One can easily check that the solution and boundary conditions are satisfied. The solution of
-the steady-state problem is $C_s=C_0$. To find a solution of the semi-infinite medium we will use
-the method of separation of variables:
-\begin{equation}
-\begin{aligned}
-&C_h=\Theta(t)\Phi(x)\\
-&\frac{1}{\Theta(t)}\frac{\mathrm{d}\Theta(t)}{\mathrm{d}t}=D
-\frac{1}{\Phi(x)}\frac{\mathrm{d}^2\Phi(x)}{\mathrm{d}x}=-\alpha^2 D\\
-\end{aligned}
-\end{equation}
-The solution for the time-dependent part is as:
-\begin{equation}
-\Theta(t)=\exp(-\alpha^2 D t).
-\end{equation}
-The solution for the spatial dependence function is as:
-\begin{equation}
-\Phi(x)=A\cos(\alpha x)+ B\sin(\alpha x).
-\end{equation}
-The overall solution of the homogenious part is represented as:
-\begin{equation}
-C_h=(A\cos(\alpha x) + B\sin(\alpha x)) \exp(-\alpha^2 D t),
-\end{equation}
-where one needs to solve the eigenvalue problem to find the necessary $\alpha$ parameter. One can
-find it through the initial and boundary conditions:
-\begin{equation}
-\begin{aligned}
-&C_h(x,0)=-C_0\\
-&C_h(x,0)=A\cos(\alpha x)+B\sin(\alpha x)=-C_0\\
-&C_h(0,t)=0\\
-&C_h(0,t)=A\exp(-\alpha^2 D t)=0\\
-&A=0\\
-\end{aligned}
-\end{equation}
-Therefore one needs to decompose the constant $-C_0$ through the function $\sin(\alpha x)$. It can
-be done through a continuous Fourier transform:
-\begin{equation}
-\begin{aligned}
-&C_h=\int_{\alpha>0}{B(\alpha) \sin(\alpha x) \exp(-\alpha^2 D t) \mathrm{d}\alpha}\\
-&C_h(x,0)=-C_0=\int_{\alpha>0}{B(\alpha)\sin(\alpha x) \mathrm{d}\alpha}\\
-&\int_{0}^{\infty}{B(\alpha) \frac{e^{i\alpha x}-e^{-i\alpha x}}{2 i}\mathrm{d} \alpha}=-C_0\\
-\end{aligned}
-\end{equation}
-To get function $B(\alpha)$ one needs to proof the following Fourier relationship:
-\begin{equation}
-\begin{aligned}
-&F(x)=\frac{2}{\pi}\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \sin(\alpha x)
-\int_{x'=0}^{\infty}{\sin(\alpha x')F(x')\mathrm{d} x'}}\\
-&\frac{2}{\pi}\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \sin(\alpha x)\sin(\alpha x')}=\frac{2}{\pi}
-\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \frac{\cos(\alpha(x+x'))-\cos(\alpha(x-x'))}{2}}\\
-&=\frac{1}{\pi}\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha\Bigl[\frac{e^{i\alpha
-(x+x')}+e^{-i\alpha(x+x')}}{2}-\frac{e^{i\alpha
-(x-x')}+e^{-i\alpha(x-x')}}{2}\Bigr]}\\
-&=\frac{1}{2\pi}\int_{\alpha=-\infty}^{\infty}{\mathrm{d}\alpha\Bigl[e^{i\alpha(x+x')}-e^{
-i\alpha(x-x')} \Bigr]}=\delta(x+x')-\delta(x-x')\\
-&F(x)=\int_{x'=0}^{\infty}{\mathrm{d} x' (\delta(x+x')-\delta(x-x')) F(x')}=F(x) 
-\end{aligned}
-\end{equation}
-Therefore the solution is as follows:
-\begin{equation}
-C_h(x,t)=-\frac{2 C_0}{\pi}\int_{\alpha>0} {\exp{-\alpha^2 t} \int_{x'>0}{\sin(\alpha x) \sin(\alpha
-x')}} 
-\end{equation}
-Integrals can be taken from \citet{ozisik}:
-\begin{equation}
-\begin{aligned}
-&\frac{2}{\pi}\int_{\alpha=0}^{\infty}{e^{-\alpha^2 D t} \sin(\alpha x) \sin(\alpha
-x')}\\
-&=\frac{1}{\sqrt{4\pi D t}}\biggl[\exp\Bigl(-\frac{(x-x')^2}{4 D
-t}\Bigr)-\exp\Bigl(-\frac{(x+x')^2}{4 D t}\Bigr)\biggr]
-\end{aligned}
-\end{equation}
-The final answer for homogenous part becomes \cite{ozisik}:
-\begin{equation}
-C_h(x,t)=-C_0\mathrm{erf}\Bigl(\frac{x}{\sqrt{4 D t}}\Bigr),
-\end{equation}
-where $\mathrm{erf}$ stands for the error function defined as:
-\begin{equation}
-\mathrm{erf(y)}=\frac{2}{\sqrt{\pi}}\int_{0}^{y}{e^{-\eta^2}\mathrm{d}\eta}.
-\end{equation}
-Overall solution then is defined as:
-\begin{equation}
-C(x,t)=C_0-C_0\mathrm{erf}\Bigl(\frac{x}{\sqrt{4 D t}}\Bigr),
-\end{equation}
-with the mass transfer coefficient is defined as the integral of absorbed gas upto time $t_e$
-divided by the time $t_e$. The accumulated  flux is the integral of the derivative
-$-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}$ by time $t$. The incoming flux is as follows:
-\begin{equation}
-\begin{aligned}
-&-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0}=D \frac{1}{\sqrt{\pi D t}}\\
-\end{aligned}
-\end{equation}
-The accumulated concentration and the mass transfer coefficients are:
-\begin{equation}
-\begin{aligned}
-&\int_{0}^{t_{\mathrm{film}}}{-D\frac{\mathrm{d} C(x,t)}{\mathrm{d}x}|_{x=0} \mathrm{d}t}=2
-\sqrt{ \frac{D t}{\pi}}\\
-&k_L = 2 \sqrt{\frac{D}{\pi t_{\mathrm{film}}}}.
-\end{aligned}
-\end{equation}
-If we account for the two surfaces for the bubble then one can obtain the following volumetric mass
-transfer coefficient:
-\begin{equation}
-\begin{aligned}
-&k_L a= 2\sqrt{\frac{D}{\pi t_{\mathrm{film}}}} 2
-\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{
-\mathrm { slug } } )H_ { \mathrm { eff } } }\\
-&k_L a= 2\sqrt{\frac{D}{\pi
-\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{U_{\mathrm{bubble}}}}} 2
-\frac{L_{\mathrm{bubble}}-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{
-\mathrm { slug } } )H_ { \mathrm { eff } } }\\
-&k_L a=4 \sqrt{\frac{D U_{\mathrm{bubble}}}{\pi}}
-\frac{\sqrt{L_{\mathrm{bubble}}-(H_{\mathrm{eff}-2\delta})}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}
-)H_ { \mathrm { eff } } }
-\end{aligned}
-\end{equation}
-
-\item[Cylinder mass transfer] For the cylinder mass transfer one needs to solve the heat conduction
-equation one needs to use cylindrical coordinates. The system is prescribed by the following set
-of equations:
-\begin{equation}
-\begin{aligned}
-&\frac{\partial C}{\partial t}=D\frac{\partial^2 C}{\partial r^2} + \frac{D}{r}\frac{\partial
-C}{\partial r}\\
-&C(a,t)=0\\
-&C(r,0)=0\\
-\end{aligned}
-\end{equation}
-The solution is given by \citet{ozisik} as:
-\begin{equation}
-\begin{aligned}
-&C(r,t)=C_0\\
-& - C_0\int_{\alpha=0}^{\infty}{\mathrm{d}\alpha \frac{\alpha}{J_0^2(\alpha
-a)+Y_0^2(\alpha a)}e^{-\alpha^2 D t}[J_0(\alpha r) Y_0(\alpha a)-Y_0(\alpha r) J_0(\alpha a)]}\\
-&\times \int_{r'=a}^{\infty}{r'[J_0(\alpha r')Y_0(\alpha a)-Y_0(\alpha r') J_0(\alpha
-a)]\mathrm{d}r'}
-\end{aligned}
-\end{equation}
-These integrals can be taken through the recurrent equations for Bessel functions. However, the
-penetration of the concentrator comes not only from the diffusion but mainly from the advection
-part. According to the penetration theory one can use the following correlation for the mass
-transfer coefficient:
-\begin{equation}
-k_L=2\sqrt{\frac{D}{\pi t_{\mathrm{contact}}}},
-\end{equation}
-where $t_{\mathrm{contact}}$ for the bubble cap can be calculated from the following considerations
-\cite{vanbaten-circular}: the distance travelled by a fluid packet coming to the bubble equals to a
-half of semicircle perimeter until it is swept away by the vortex in the front of the bubble
-{\color{red} (working only for small capillary numbers where a vortex exists in the front of the
-bubble)}. Therefore for the case of the bubble arising with the velocity $U_{\mathrm{bubble}}$ one
-can estimate the mass transfer coefficient as follows:
-\begin{equation}
-k_L=2\sqrt{\frac{D}{\pi t_{\mathrm{contact}}}}=2\sqrt{\frac{D}{\pi \frac{ \pi
-(H_{\mathrm{eff}}-2\delta)/2}{U_{\mathrm{bubble}}}}}=\frac{2\sqrt{2}}{\pi}\sqrt{\frac{D
-U_{\mathrm{bubble}}}{H_{\mathrm{eff}}-2\delta}}
-\end{equation}
-The volumetric mass transfer coefficient is then as follows:
-\begin{equation}
-\begin{aligned}
-k_L a=\frac{2\sqrt{2}}{\pi}\sqrt{\frac{D
-U_{\mathrm{bubble}}}{H_{\mathrm{eff}}-2\delta}} \frac{\pi
-(H_{\mathrm{eff}}-2\delta)}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}) H_{\mathrm{eff}}}\\
-k_L a=2\sqrt{2}\sqrt{D
-U_{\mathrm{bubble}}}\frac{\sqrt{H_{\mathrm{eff}}-2\delta}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})H_
-{\mathrm{eff}}}
-\end{aligned}
-\end{equation}
-
-\end{description}
-Therefore the overall adjusted for the flow between plates mass transfer coefficient is expressed as
-follows:
-\begin{equation}
-\begin{aligned}
-k_L a =&4 \sqrt{\frac{D U_{\mathrm{bubble}}}{\pi}}
-\frac{\sqrt{L_{\mathrm{bubble}}-(H_{\mathrm{eff}-2\delta})}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}}
-)H_ { \mathrm { eff } } }\\
-&+2\sqrt{2}\sqrt{D
-U_{\mathrm{bubble}}}\frac{\sqrt{H_{\mathrm{eff}}-2\delta}}{(L_{\mathrm{bubble}}+L_{\mathrm{slug}})H_
-{\mathrm{eff}}}.
-\end{aligned}
-\end{equation}
-
-\section{TRT $D2Q9$ model. Equilibrium functions}
-One of the advantages of $D2Q9$ TRT model in comparison with $D2Q5$ usually used for simulations of
-the advection-diffusion model is that $D2Q9$ is able to reduce numerical diffusion from diagonal
-and non-diagonal diffusion tensor components \cite{kuzmin-stability-optimal}.
-
-In
-comparison with the BGK collision operator the TRT collision operator \cite{ginzburg-boundary-main}
-decomposes the populations and the equilibrium
-distribution into the symmetric and antisymmetric parts:
-\begin{equation}
-\label{trtdecomp}
-f^{\pm}_i=\frac{f_i\pm f_{\bar{i}}}{2}\;,\; 
-{eq_i}^{\pm}=\frac{eq_i\pm eq_{\bar{i}}}{2}\;,
-\end{equation}
-where $\bar{i}$ is the opposite direction to the $i$-th direction.
-The collision is performed with two independent relaxation rates for 
-symmetric and antisymmetric modes:
-\begin{equation}
-\label{trt}
-\begin{aligned}
-&f_i^{*}(\bm{x},t)=f_i(\bm{x},t)-\omega_{+} (f_i^{+} - eq_i^+)-\omega_{-}
-(f_i^{-} -
-eq_i^-)\\
-&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t).
-\end{aligned}
-\end{equation}
-Note that the BGK collision operator is the particular subclass of the TRT relaxation operator with
-$\omega_{+}=\omega_{-}$. In comparison with the BGK collision operator,
-the TRT collision operator has the additional degree of freedom. Thus, the TRT operator then
-introduces
-so-called magic (free) parameter
-$\Lambda=\Bigl(\frac{1}{\omega_{+}}-\frac{1}{2}\Bigr)\Bigl(\frac{1}{\omega_{-}}-\frac{1}{2}\Bigr)$. 
-This free parameter controls the effective location of the bounce-back
-walls \cite{ginzburg-multireflection}, second-order accuracy of
-boundary \cite{ginzburg-boundary-main} and interface schemes \cite{ginzburg-discontinious}, 
-spatial accuracy \cite{ginzburg-recurrence,servan-trt-stability},
-consistency \cite{ginzburg-brinkman} and, to some extent,
-stability \cite{kuzmin-stability-optimal,kuzmin-d1q3,servan-trt-stability}.
-In particular, $\Lambda=\frac{1}{4}$ achieves the optimal stability for the
-linear advection-diffusion isotropic equation \cite{kuzmin-stability-optimal}.
-
-The equilibrium functions for $D2Q9$ TRT model are represented as \cite{kuzmin-stability-optimal}:
-\begin{equation}
-\begin{aligned}
-&eq_i^{+}=eq_i^{(m)}+g^{(u)} eq_i^{(u)}\\
-&eq_i^{(m)}=t_i^{(m)} c_e+ eq_i^{(a)}\\
-&eq_i^{(u)}=t_i^{(u)} \frac{u_x^2+u_y^2}{2}+\frac{u_x^2-u_y^2}{4} p_i^{(xx)}+g_{xy}^{(u)}\frac{u_x
-u_y}{4} p_i^{xy}\\
-&eq_i^{(a)}=\frac{D_{xx}-D_{yy}}{4} p_i^{xx}+\frac{D_{xy}}{4} p_i^{(xy)},
-\end{aligned}
-\end{equation}
-where $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$ and $p_i^{(xy)}=c_{ix} c_{iy}$.
-
-The following equilibrium functions solve the anisotropic advection-diffusion equation with the
-following diffusion tensor:
-\begin{equation}
-D=
-\begin{pmatrix}
-D_{xx} + (g^{(u)}-1) u_x^2 & D_{xy}+(g_{xy}^{(u)}-1)u_x u_y\\
-D_{xy} + (g_{xy}^{(u)}-1) u_x u_y& D_{yy}+(g^{(u)}-1) u_y^2 
-\end{pmatrix}
-\end{equation}
-To consider the situation when the resolution is not needed to be changed in $x$ and $y$
-directions, one can obtain that $D_{xx}=D_{yy}$. The cross-diagonal components of the diffusion
-tensor are taken as zeros, i.e. $D_{xy}=0$. The numerical diffusion can be avoided by proper choice
-of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$.
-
-As far as the simulated diffusion tensor is close to $0$ the stability limits restrict the velocity
-amplitude to be simulated \cite{kuzmin-stability-optimal}. However, particular choice of weights
-can drastically help. Fig. \ref{stability:d2q9} shows the stability limits for D2Q9 with removed
-numerical diffusion and with it for two particular choices of weights.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
-\caption{The non-negativity areas and stable sub-domains of the OTRT schemes ($\Lambda=\frac{1}{4}$)
-are plotted for the $D2Q9$ (standard weights, left) and the $D2Q9$ (uniform weights, right) when the
-numerical diffusion is removed, partially or completely. Two non-negativity areas where all the
-equilibrium populations are positive have curvilinear boundaries: they are smaller when
-$g^{(u)}_{xy}=0$ (yellow) and than when $g^{(u)}_{xy}=1$ (green+yellow). The non-negativity
-condition is required by BGK collision operator. The stable sub-domains for $g^{(u)} = 1,
-g^{(u)}_{xy} = 0$ are small (red+green+yellow) triangles. When the numerical diffusion is removed
-the stable area is bounded by magenta and the (blue) domain above. The proper choice of weights can
-allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1−c_e$ (the
-uniform weights only).
-\label{stability:d2q9}}
-\end{figure}
-
-From here on we will use the standard weights as:
-\begin{equation}
-t_i^{(u)}=t_i^{(m)}=t_i^{(a)}=\Bigl\{0,\frac{1}{3},\frac{1}{3},\frac{1}{3},\frac{1}{3},\frac{1}{12},
-\frac {1}{12},\frac{1}{12},\frac{1}{12}\Bigr\}
-\end{equation}
 

### 2011-11-01 Python/multiple.py

@@ -20,7 +20,9 @@ def Produce_Single():
     #dirs=[3,5,8,10,20,40,60,80]
     #dirs=[3,5,8,10,20,40,60,80]
     dirs=[3,5,8,10]    
-    
+    coeffs_aver=[]
+    coeffs_outlet=[]
+    coeffs_open=[]
    
     for counter,dir_name in enumerate(dirs):    
         data_dir_name="SailfishData/"+str(dir_name)+"/"
@@ -109,6 +111,11 @@ def Produce_Single():
         coefficient_aver=new_conc[:,1]/(200*3000)/(deltat*new_conc[:,0]*(1.0-0.5*(array[1:,1]+array[0:-1,1])/((1-gas_holdup)*200*3000)))                
         coefficient_outlet=new_conc[:,1]/(200*3000)/(deltat*new_conc[:,0]*(1.0-numpy.abs(new_conc[:,2])))        
         coefficient_outlet_sim=new_conc[:,1]/(200*3000)/(deltat*new_conc[:,0]*(1.0-conc_outlet))
+        
+        coeffs_aver.append(numpy.mean(coefficient_aver[numpy.where(array[1:,0]>1500000)]))
+        coeffs_outlet.append(numpy.mean(coefficient_outlet[numpy.where(array[1:,0]>3500000)]))
+        coeffs_open.append(numpy.mean(coefficient_open))
+                
         pylab.figure(1)
         pylab.plot(array[1:,0],coefficient_last,styles[counter])        
         pylab.figure(2)
@@ -123,6 +130,9 @@ def Produce_Single():
         #pylab.title("Open boundaries")
     #pylab.legend(legs,fancybox=True,labelspacing=0.1)
     #pylab.savefig("steady_state.eps",format="EPS",dpi=300)
+    print "Coeffs_aver=",coeffs_aver
+    print "Coeffs_outlet=",coeffs_outlet
+    print "Coeffs_open=",coeffs_open
     
     #print "Aver_coefficient=",aver_coefficient
     pylab.figure(1)
@@ -131,11 +141,14 @@ def Produce_Single():
     pylab.ylabel(r'''$k_L a, \mathrm{s^{-1}}$''',fontsize=20)
     pylab.legend(legs,fancybox=True,labelspacing=0.1)
     pylab.ylim(ymax=3.0)
[…]

### 2011-11-02 Text/introduction.tex
Double results are ready.

@@
 
-\section{Comparison between different approaches}
+\section{Comparison between different approaches for one unit cell}
 We consequently will examine different approaches to the mass transfer definition, Fig.
@@
 the inlet/outlet concentration, Fig \ref{fig:benchmark}. 
-\item[II] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a
+\item[II] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
+is located near the entrance of the computational domain, and the characteristic concentration is
+the average concentration, Fig \ref{fig:benchmark}.
+\item[III] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a
 bubble is located in the middle of the computational domain, and the characteristic concentration
 is the inlet/outlet concentration.
-\item[III] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
+\item[IV] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
 is located in the middle of the computational domain, and the characteristic concentration is the
 average concentration.
-\item[IV] Definition with the concentration jump between inlet and outlet over one unit cell.
+\item[V] Definition with the concentration jump between inlet and outlet over one unit cell.
 \end{description}
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}
-\caption{The two-dimensional benchmarks for the hydrodynamics (top) and the mass transfer
-coefficient (bottom). \label{fig:benchmark}}
+\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}\\
+\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
+\caption{The two-dimensional benchmarks for the  the mass transfer
+coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
+(bottom). \label{fig:benchmark}}
 \end{figure}
@@
 \includegraphics[width=0.5\textwidth]{Figures/steady_state_per_entrance.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_aver.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_middle_outlet.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_inlet_aver.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_aver.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_middle_outlet.eps}\\
 \includegraphics[width=0.5\textwidth]{Figures/steady_state_jos_inlet_outlet.eps}\\
@@
 \hline
-$Ca$&$Fo$&$\vol_{ent},\,\mathrm{s}^{-1}$&\\
+$Ca$&$Fo$&$\vol_{ent},\,\mathrm{s}^{-1}$&$\vol_{aver},\,\mathrm{s}^{-1}$&$\vol_{mid,
+aver},\,\mathrm{s} ^ { -1 }$&$\vol_{mid,out},\,\mathrm{s}^{-1}$&$\vol_{open},\,\mathrm{s}^{-1}$ \\
 \hline
-$0.026$&$0.08493$&$0.2737$&$0.1692$&$0.2631$&$3.6756$\\
-$0.047$&$0.02160$&$0.3664$&$0.2852$&$0.4553$&$11.4822$\\
-$0.080$&$0.00588$&$0.4959$&$0.4079$&$0.6920$&$15.1964$\\
-$0.065$&$0.00862$&$0.4734$&$0.4303$&$0.8923$&$21.4517$\\
-$0.222$&$0.00103$&$0.8505$&$0.6109$&$0.8679$&N/A\\
-$0.479$&$0.00034$&$1.1541$&$0.9884$&$1.2995$&N/A\\
-$0.736$&$0.00018$&$1.1801$&$1.2199$&$1.1555$&N/A\\
-$0.989$&$0.00012$&$1.2215$&$1.3400$&$1.0350$&N/A\\
+$0.026$&$0.08493$&$0.2737$&$0.1775$&$0.1692$&$0.2631$&$3.6756$\\
+$0.047$&$0.02160$&$0.3664$&$0.3431$&$0.2852$&$0.4553$&$11.4822$\\
+$0.080$&$0.00588$&$0.4959$&$0.4185$&$0.4079$&$0.6920$&$15.1964$\\
+$0.065$&$0.00862$&$0.4734$&$0.4517$&$0.4303$&$0.8923$&$21.4517$\\
+$0.222$&$0.00103$&$0.8505$&$0.6799$&$0.6109$&$0.8679$&N/A\\
+$0.479$&$0.00034$&$1.1541$&$1.0460$&$0.9884$&$1.2995$&N/A\\
+$0.736$&$0.00018$&$1.1801$&$1.2395$&$1.2199$&$1.1555$&N/A\\
+$0.989$&$0.00012$&$1.2215$&$1.3493$&$1.3400$&$1.0350$&N/A\\
 \hline
@@
 \label{table:one_unit_comparison}}
+\end{table}
+One can see that the only consistent result is for simulations which take into the account average
+concentration. The results come to the steady-state after $1,000,000$ iterations. However, to
+understand properly what is the real mass transfer coefficient one needs to perform a few units
+simultions.
+
+\section{Two unit cells results}
+As far as one needs to restore the continuous picture one needs to make a simulation of a few
+cells. This section provides results for two units. The results are summarized in Table
+\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
+\caption{Overall mass transfer coefficient (top left), first part (top
+right), second part (bottom left).\label{fig:results:double}}
+\end{figure}
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|}
+$0.7392$&$1.0564$&$0.4220$\\
+$1.8993$&$2.8301$&$0.9684$\\
+$3.3925$&$4.7522$&$2.0328$\\
+$3.7870$&$4.5615$&$3.0125$\\
+\end{tabularx}
+\caption{Simulation results. \label{table:two_units}}
 \end{table}

### 2011-11-02 GridCode/jos_massive_parallel.cpp

@@ -659,7 +659,7 @@ void calculate_mass_transfer(int time_counter)
 	
 		for(int iX=1;iX<NX-1;iX++)
 		{
-			conc_outlet=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
+			conc_outlet+=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
 			sum_vel_outlet+=uy[(NY-1)*NX+iX];
 		}
 	    conc_outlet=conc_outlet/sum_vel_outlet;

### 2011-11-02 GridCode/mass_transfer_jos_grid.cpp

@@ -552,7 +552,7 @@ void calculate_mass_transfer(int time_counter)
 	{
 		conc_inlet+=rho[iX]*uy[iX];
 		sum_vel_inlet+=uy[iX];
-		conc_outlet=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
+		conc_outlet+=rho[(NY-1)*NX+iX]*uy[(NY-1)*NX+iX];
 		sum_vel_outlet+=uy[(NY-1)*NX+iX];
 	}
 	

### 2011-11-02 Python/SailfishMassCentralDouble/checkers_copy2.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+
+for i in 3 5 8 10
+do
+  cd $i
+  for j in `seq 1160000 280000 3960000`
+  do
+    scp "shurik@checkers.westgrid.ca":/home/shurik/MassSailfishJosDouble/$i/density_jos_par$j.dat .
+  done
+cd ..
+  echo "Done with $i"
+done

### 2011-11-02 Python/multiple.py

@@ -18,8 +18,9 @@ def Produce_Single():
     aver_coefficient=[]
     bubble_velocities=[]
     #dirs=[3,5,8,10,20,40,60,80]
-    #dirs=[3,5,8,10,20,40,60,80]
-    dirs=[3,5,8,10]    
+    dirs=[3,5,8,10,20,40,60,80]
+    #dirs=[3,5,8,10]
+    coeffs_inlet_aver=[]
     coeffs_aver=[]
     coeffs_outlet=[]
     coeffs_open=[]
@@ -57,8 +58,20 @@ def Produce_Single():
         print "Interface velocity=",interface_velocity
         print "Capillary=",capillary
         print "Reynolds=",reynolds
+      
+        deltat=interface_velocity/phys_velocity*diam/(dims[0]-2)
+      
+        ###Periodic Inlet analysis
   
-        ###Periodic analysis 
+        inlet_dir_name="SailfishMassBGK/"+str(dir_name)+"/"
+        inlet_name=inlet_dir_name+"concentration.dat"
+        inlet_conc_aver=numpy.loadtxt(inlet_name)
+        inlet_new_conc=numpy.array(zip(inlet_conc_aver[1:,0]-inlet_conc_aver[:-1,0],inlet_conc_aver[1:,1]-inlet_conc_aver[:-1,1],inlet_conc_aver[1:,2]))
+        print inlet_conc_aver.shape
+        print inlet_new_conc.shape
+        
+      
+        ###Periodic Central analysis 
         per_dir_name="SailfishMassCentralPeriodic/"+str(dir_name)+"/"
         name=per_dir_name+"concentration.dat"
         density_name=per_dir_name+"density3960000.dat"
@@ -74,7 +87,6 @@ def Produce_Single():
         conc_outlet=numpy.sum(ux[1:-1,-1]*density[1:-1,-1])/numpy.sum(ux[1:-1,-1])
         print "Outlet=",conc_outlet        
         new_conc=numpy.array(zip(array[1:,0]-array[:-1,0],array[1:,1]-array[:-1,1],array[1:,2]))
-        deltat=interface_velocity/phys_velocity*diam/(dims[0]-2)
         
         ###Open boundaries options
         open_dir_name="SailfishMassCentralSingle/"+str(dir_name)+"/"     
@@ -111,7 +123,10 @@ def Produce_Single():
[…]

### 2011-11-03 Text/introduction.tex
Added triple results.

@@
 \end{tabularx}
-\caption{Simulation results. \label{table:two_units}}
+\caption{Simulation results for two units. \label{table:two_units}}
 \end{table}
+
+\section{Three unit cells results}
+Three unit cells results are subdivided into three cells. We calculate the mass transfer
+coefficients over the each cell, Fig. \ref{fig:results:triple}. The averaged coefficients  after
+$3,300,000$ time steps are represented in Table. \ref{table:three_units}. The most important thing
+is to look at the third column of the Table \ref{table:three_units} or for at the Fig. \ref{fig:re} 
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+0.4928&1.0564&2.8472e-05&0.4219\\
+1.2662&2.8301&0.0146&0.9537\\
+2.3110&4.7532&1.0665&1.1133
+\end{tabularx}
+\caption{Simulation results for three units.\label{table:three_units}}
+\end{table}
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/steady_triple_overall.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_triple_first.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/steady_triple_second.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_triple_third.eps}\\
+\caption{The mass transfer coefficient over time in different locations: overall mass transfer
+coefficient (top left), first part (top right), second part (bottom left), third part (bottom
+right). \label{fig:results:triple}}
+\end{figure}
 

### 2011-11-03 Python/multiple.py

@@ -314,6 +314,7 @@ def Produce_Double():
     print "Coeffs_first=",coeffs_first
     print "Coeffs_second=",coeffs_second
     file_names=["steady_double_overall.eps","steady_double_first.eps","steady_double_second.eps"]        
+    
     for i in range(1,4):    
         pylab.figure(i)        
         legs=[r'''$U_{\mathrm{bubble}}='''+str(vel)[:4]+r'''$''' for vel in bubble_velocities]
@@ -328,7 +329,135 @@ def Produce_Double():
     #print "Aver_coefficient=",aver_coefficient
 
 
+def Produce_Triple():
+
+    #physical parameters
+    gamma=0.0728
+    diam=1.5e-3    
+    print os.getcwd()
+ 
+    styles=['kv-','ks-','ko-','k^-','k>-','k<-']
+    aver_coefficient=[]
+    bubble_velocities=[]
+    interface_velocities=[]
+    liquid_velocities=[]
+    gas_velocities=[]
+    holdups=[]    
+    #dirs=[3,5,8,10,20,40]
+    dirs=[3,5,8]    
+ 
+ 
+    coeffs_overall=[]
+    coeffs_first=[]
+    coeffs_second=[]
+    coeffs_third=[]
+    for counter,dir_name in enumerate(dirs):    
+        data_dir_name="SailfishData/"+str(dir_name)+"/"
+        file_name=data_dir_name+"capillary200000.npz"        
+        arr=numpy.load(file_name)        
+        phase=arr['phi']
+        velx=arr['v'][0]
+        vely=arr['v'][1]
+        dims=phase.shape
+
+        print "Dimensions=",dims
+
+        center=phase[dims[0]/2,:]
+        z1 = numpy.min(numpy.where(center < 0.0))
+        z2 = numpy.max(numpy.where(center < 0.0))
+        slug_length=dims[1]-z2+z1    
+        if z1==0:
+            z2=numpy.min(numpy.where(center>0.0))+dims[1]
+            z1=numpy.max(numpy.where(center>0.0))
+            slug_length=z1-z2%dims[1]
+        print z1,z2
+
+        interface_velocity=velx[dims[0]/2,z2%dims[1]]
+        capillary=interface_velocity*(2.0/3.0)/math.sqrt(8*0.04*0.04/9.0)
+        reynolds=interface_velocity*dims[0]/(2.0/3.0)        
[…]

### 2011-11-03 Text/introduction.tex
Playing with velocity increase.

@@
 \begin{tabularx}{\textwidth}{|X|X|X|}
+\hline
 $0.7392$&$1.0564$&$0.4220$\\
@@
 $3.7870$&$4.5615$&$3.0125$\\
+\hline
 \end{tabularx}
@@
 $3,300,000$ time steps are represented in Table. \ref{table:three_units}. The most important thing
-is to look at the third column of the Table \ref{table:three_units} or for at the Fig. \ref{fig:re} 
+is to look at the third column of the Table \ref{table:three_units} or for at the Fig.
+\ref{fig:results:triple} (bottom left). The coefficients for capillary numbers $0.026$ and $0.047$
+are almost zero which indicates that the concentration at the first part of the channel is almost
+the same as the second part. Thus, there is not enough time steps to transfer concentrate among
+whole the channel (plug flow). In comparison with the first two values for capillary number $0.080$
+the trend is different and concentrate is spread over the channel. However, the drop coefficients
+are still inconsistents. Though last part and the second part exhibit close values (needed to tell
+what is the real mass transfer coefficient). Overall, more time steps are needed.
+$0.080$
 \begin{table}[htb!]
 \begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
 0.4928&1.0564&2.8472e-05&0.4219\\
 1.2662&2.8301&0.0146&0.9537\\
-2.3110&4.7532&1.0665&1.1133
+2.3110&4.7532&1.0665&1.1133\\
+\hline
 \end{tabularx}
@@
 
+{\color{red} Probably we can consider that for capillary number less than $0.08$ the mass transfer
+is a plug flow mass transfer, keeping only the impact from caps.}
+
+\section{Four unit cells results}
+Four unit cells results are subdivided into four cells. The results are presented in Fig.
+\ref{fig:results:quadro}. While we expect certain deviations for the first and the last part, but
+surprisingly the concentration difference over the third segment tends to be zero. That means not
+enough time steps are performed. The results over segments are summarized in Table
+\ref{table:four_units}.
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
+\hline
+$Ca$   &Overall  &I       &II      &III     &IV\\
+$0.080$&$1.7359$ &$4.7533$&$1.0665$&$0.1088$&$1.0150$\\
+$0.065$&$1.9260$ &$4.5620$&$0.9113$&$0.0619$&$2.1689$\\
+\hline
+\end{tabularx}
+\caption{Simulation results for mass transfer coefficients for 4 unit cells
+domain.\label{table:four_units}}
+\end{table}
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_overall.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_first.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_second.eps}
+\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_third.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_fourth.eps}\\
+\caption{The mass transfer coefficient over time in different locations: overall mass transfer
+coefficient (top left), first part (top right), second part (middle left), third part (middle
+right) and fourth part (bottom left). \label{fig:results:quadro}}
+\end{figure}
+
+From Figs. \ref{fig:results:triple} and \ref{fig:results:quadro} one can see that $4,000,000$ time
+steps are enough to saturate the second unit for $Ca=0.080$ number. Let us recall bubble velocities
+and see what are the characteristic lengths for them calculated as time steps multiplied on the
+bubble velocity. From the table one can see that each unit cell is saturated with the timesteps as
+$1.5 \frac{N_x}{U_{bubble}}$ {\color{red}(Pretty important result)}. It's inevitably needs the
+velocity increase.
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
+\hline
+$Ca$ &$U_{bubble}$ &$N_{iter_1}$ &$N_{iter_2}$ &$N_{iter_3}$ &$\frac{L_1}{N_x}$&$\frac{L_2}{N_x}$ 
+&$\frac{L_3}{N_x}$\\
+$0.026$&$0.0014$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$0.4666$ &$0.9333$ &$1.8666 $\\
+$0.047$&$0.0027$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$0.9$    &$1.8$    &$3.6    $\\
+$0.080$&$0.0045$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$1.5$    &$3.0$    &$6.0    $\\
+$0.065$&$0.0037$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$1.2333$ &$2.4666$ &$4.9333 $\\
+$0.222$&$0.0125$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$4.1666$ &$8.3333$ &$16.6666$\\
+$0.479$&$0.0271$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$9.0333$ &$18.0666$&$36.1333$\\
+$0.736$&$0.0416$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$13.8666$&$27.7333$&$55.4666$\\
+$0.989$&$0.0559$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$18.6333$&$37.2666$&$74.5333$\\
+\hline
+\end{tabularx}
+\caption{Table results to understand how many time steps are needed to be performed to reach the
+saturation.\label{table:time:steps}}
+\end{table}
+
+\section{Improving velocity}
+
+\section{Tweaking velocity}
+This section does the job of increasing velocity results. The ulimate goal is to increase velocity
+to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
+nondimensional parameter Peclet number governs the advection-diffusion equation:
+\beq
+Pe=\frac{U_{\bubble} N_y}{D},
+\feq
+where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
+means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
+$5,10,20,40$ times larger than original velocities.
+
 \bibliographystyle{unsrtnat}

### 2011-11-03 Python/multiple.py

@@ -456,8 +456,145 @@ def Produce_Triple():
         pylab.ylim(ymax=9)
         pylab.savefig(file_names[i-1],dpi=300)
 
+def Produce_Quadro():
+
+    #physical parameters
+    gamma=0.0728
+    diam=1.5e-3    
+    print os.getcwd()
+ 
+    styles=['kv-','ks-','ko-','k^-','k>-','k<-']
+    aver_coefficient=[]
+    bubble_velocities=[]
+    interface_velocities=[]
+    liquid_velocities=[]
+    gas_velocities=[]
+    holdups=[]    
+    #dirs=[3,5,8,10,20,40]
+    dirs=[8,10]    
+ 
+ 
+    coeffs_overall=[]
+    coeffs_first=[]
+    coeffs_second=[]
+    coeffs_third=[]
+    coeffs_fourth=[]
+    for counter,dir_name in enumerate(dirs):    
+        data_dir_name="SailfishData/"+str(dir_name)+"/"
+        file_name=data_dir_name+"capillary200000.npz"        
+        arr=numpy.load(file_name)        
+        phase=arr['phi']
+        velx=arr['v'][0]
+        vely=arr['v'][1]
+        dims=phase.shape
+
+        print "Dimensions=",dims
+
+        center=phase[dims[0]/2,:]
+        z1 = numpy.min(numpy.where(center < 0.0))
+        z2 = numpy.max(numpy.where(center < 0.0))
+        slug_length=dims[1]-z2+z1    
+        if z1==0:
+            z2=numpy.min(numpy.where(center>0.0))+dims[1]
+            z1=numpy.max(numpy.where(center>0.0))
+            slug_length=z1-z2%dims[1]
+        print z1,z2
+
+        interface_velocity=velx[dims[0]/2,z2%dims[1]]
+        capillary=interface_velocity*(2.0/3.0)/math.sqrt(8*0.04*0.04/9.0)
+        reynolds=interface_velocity*dims[0]/(2.0/3.0)        
+        phys_velocity=math.sqrt(capillary*reynolds*gamma/(1000*diam))        
+        superficial_liquid=numpy.sum(velx[1:-1,((z1+z2+dims[1])/2)%dims[1]])/(dims[0]-2)
+        gas_holdup=float(len(numpy.where(phase<0)[0]))/(dims[1]*(dims[0]-2))
+        
+        interface_velocities.append(interface_velocity)
+        bubble_velocities.append(phys_velocity)
[…]

### 2011-11-03 Python/velocity_increase.py

@@ -1,0 +1,17 @@
+#!/usr/bin/python
+import numpy
+import pylab
+
+def show_fields(file_name):
+    density=numpy.loadtxt(file_name)
+    pylab.figure(1)    
+    pylab.imshow(density)
+    pylab.figure(2)
+    pylab.plot(density[100,:])
+    
+    print density[100,0],density[100,-1]
+
+if __name__=="__main__":
+    file_name="../VelocityCode/density0002000.dat"
+    show_fields(file_name)
+    pylab.show()

### 2011-11-03 VelocityCode/jos_parallel.cpp

@@ -1,0 +1,716 @@
+//Jos mass transfer
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+#include <mpi.h>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+//MPI variables
+int mpi_rank;
+int mpi_size;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=2000;
+int NOUTPUT=100;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *mpi_rho;
+double *ux;
+double *uy;
+int * geometry;
+double * mpi_left;
+double * mpi_right;
+double * mpi_temp;
+
+
+//Boundary conditions
+double conc_inlet=0.5;
+double conc_bubble=1.0;
+double conc_wall=1.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+//double diffusion=(1.0/omega_minus-0.5)*ce;
+//double ce=diffusion/(1.0/omega_minus-0.5);
+
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
[…]

### 2011-11-03 VelocityCode/open_coefficient.cpp

@@ -1,0 +1,578 @@
+//Jos mass transfer
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+const int coefficient=1;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=20000;
+int NOUTPUT=100;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_inlet=0.5;
+double conc_bubble=1.0;
+double conc_wall=1.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.0/(coefficient*(1.0/1.99-0.5)+0.5);
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+//double diffusion=(1.0/omega_minus-0.5)*ce;
+//double ce=diffusion/(1.0/omega_minus-0.5);
+
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
[…]

### 2011-11-08 Text/introduction.tex
Need to do benchmarking.

@@
 
+\title{Lattice Boltzmann study of mass transfer for complicated geometries}
+
 \begin{document}
+\maketitle
 \section{Mass transfer definitions}
@@
 
-\section{Improving velocity}
+\section{Lattice Boltzmann Benchmarks}
+\citet{vanbaten-circular} represented a bubble with two hemisperes and a thin film. We want to
+perform the benchmarking against these two representative cases.
+
+\subsection{The radial case}
+We want to examine the bounce-back conditions against the analytical solution. The system can be
+prescribed by the following system of equations:
+\beq
+\begin{aligned}
+&\partial_t C(r,t)=\frac{1}{r}\partial_r r \partial_r C(r,t)\\
+&C(a,t)=C_0,\,C(r,0)=C_{init}
+\end{aligned}
+\feq 
+The solution is represented as \cite{chemical-correlations}:
+\beq
+\frac{C(r,t)-C_{0}}{C_{init}-C_{0})}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
+J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})},
+\feq
+where $\mu_n$ is the $n$-th zero root of the $0$th order Bessel polynomial $J_0(\mu_n)=0$. Some of
+the corresponding roots are as follows: $\mu_1=2.4048$,$\mu_2=5.5201$,$\mu_3=8.6537$,
+$\mu_4=11.7915$,$\mu_5=14.9309$.
+By taking initial concentration to be $0$, one can obtain the following solution:
+\beq
+C(r,t)=C_0 \Biggl(1 - \sum_{n=1}^{\infty}{\frac{2}{\mu_n
+J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})}\Biggr).
+\feq
+
+Here some
 
@@
 \beq
-Pe=\frac{U_{\bubble} N_y}{D},
+Pe=\frac{U_{bubble} N_y}{D},
 \feq

### 2011-11-08 Benchmarks/cylinder.cpp

@@ -12,7 +12,6 @@
 int NY;
 int NX;
 int NUM;
-const int coefficient=1;
 
 //Other constants
 const int NPOP=9;
@@ -30,18 +29,14 @@ double *uy;
 int * geometry;
 
 //Boundary conditions
-double conc_inlet=0.5;
-double conc_bubble=1.0;
 double conc_wall=1.0;
 std::vector<int> bb_nodes;
 std::vector<char>* dirs;
 int *bottom;
-int *bottom_mid;
 int *top;
-int *top_mid;
 
 //BGK relaxation parameter
-double omega=1.0/(coefficient*(1.0/1.99-0.5)+0.5);
+double omega=1.0/1.99;
 double omega_plus=2.0-omega;
 double omega_minus=omega;
 
@@ -227,24 +222,7 @@ void collide_bulk()
 {
 
     for(int iY=1;iY<NY-1;iY++)
-		if (bottom[iY]==top[iY])
-			collide_column(iY,1,NX-2);
-			//collide_column_bgk(iY,1,NX-2);
-		else
-		{
-			if(bottom_mid[iY]==top_mid[iY])
-			{
-				collide_column(iY,1,bottom[iY]);
-				collide_column(iY,top[iY],NX-2);
-			}
-			else
-			{
-				collide_column(iY,1,bottom[iY]);
-				collide_column(iY,bottom_mid[iY],top_mid[iY]);
-				collide_column(iY,top[iY],NX-2);
-			}
-			
-		}
+		collide_column(iY,bottom[iY],top[iY]);
 			
 }
 

### 2011-11-08 Python/velocity_increase.py

@@ -5,6 +5,10 @@ import pylab
 def show_fields(dir_name,file_name):
     density=numpy.loadtxt(dir_name+file_name)
     ux=numpy.loadtxt(dir_name+"vely0080000.dat").transpose()    
+    uy=numpy.loadtxt(dir_name+"velx0080000.dat").transpose()
+    #ux_orig=numpy.loadtxt(dir_name+"")
+    #uy_orig=numpy.loadtxt(dir_name+"")
+    dims=density.shape    
     pylab.figure(1)    
     pylab.imshow(density)
     pylab.colorbar()
@@ -18,13 +22,80 @@ def show_fields(dir_name,file_name):
     pylab.figure(4)
     pylab.imshow(ux)
     pylab.colorbar()
-    
+    pylab.figure(5)
+    pylab.plot(ux[:,100])
+    pylab.plot(ux[:,dims[1]/2])
+    pylab.figure(6)
+    pylab.imshow(uy)
+    pylab.colorbar()
+
     
     print density[100,0],density[100,-1]
     print density[numpy.where(density>1.1)]
     print numpy.where(density>1.1)
 
 #To be transfered to C++ file
+def prepare_bunch_files(dir_name):
+    geometry=numpy.loadtxt(dir_name+"geometry.dat").transpose()    
+    ux=numpy.loadtxt(dir_name+"ux.dat").transpose()
+    uy=numpy.loadtxt(dir_name+"uy.dat").transpose()
+    dims=geometry.shape
+
+    pylab.figure(1)
+    pylab.imshow(geometry)
+    pylab.figure(2)
+    pylab.imshow(ux)
+    print numpy.where(ux<-0.01)
+    pylab.colorbar()
+    pylab.title("Original")
+    pylab.figure(3)
+    pylab.plot(ux[:,100])
+    pylab.figure(4)
+    pylab.plot(ux[dims[0]/2,:])
+    
+    pylab.figure(99)
+    pylab.imshow(uy)
+    pylab.colorbar()
+    pylab.title("Original")
+    pylab.figure(199)
+    pylab.plot(uy[dims[0]/2,:])
+
+    interface_velocity=ux[0,0]
+
+   
+    negative=numpy.where(geometry==-1)
+    zerolevel=numpy.where(geometry==0)
+    ux[negative]=0.0
+    uy[negative]=0.0
+    ux[zerolevel]=0.0
+    #ux[0,:]=interface_velocity
+    #ux[-1,:]=interface_velocity
[…]

### 2011-11-10 Benchmarks/cylinder.cpp
Added cylinder benchmark.

@@ -12,13 +12,14 @@
 int NY;
 int NX;
 int NUM;
+int radius;
 
 //Other constants
 const int NPOP=9;
 
 //Time steps
-int N=200000;
-int NOUTPUT=1000;
+int N=64000;
+int NOUTPUT=1600;
 
 //Fields and populations
 double *f;
@@ -36,7 +37,7 @@ int *bottom;
 int *top;
 
 //BGK relaxation parameter
-double omega=1.0/1.99;
+double omega=1.0/(0.5+0.5/32.0); ///1.99;
 double omega_plus=2.0-omega;
 double omega_minus=omega;
 
@@ -70,6 +71,24 @@ void writedensity(std::string const & fname)
 		fout<<"\n";
 	}
 }
+
+void writegeometry(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
+			int counter=iY*NX+iX;
+			fout<<geometry[counter]<<" ";
+		}
+		fout<<"\n";
+	}
+}
+
 
 
 void init()
@@ -138,111 +157,86 @@ void collide_column_bgk(int coor_y,int coor_bottom,int coor_top)
 
 
 
-void collide_column(int coor_y,int coor_bottom,int coor_top)
+
+void collide()
 {
-	for(int iX=coor_bottom;iX<=coor_top;iX++)
-	{
-		int counter=coor_y*NX+iX;
-		rho[counter]=0.0;
-        int offset=counter*NPOP;
- 
-		double sum=0;
-		for(int k=0;k<NPOP;k++)
-			sum+=f[offset+k];
+	for (int counter=0;counter<NUM;counter++)
+		if (geometry[counter]==1)
+		{
+			rho[counter]=0.0;
+		    
+		    int offset=counter*NPOP;
+	 
+			double sum=0;
+			for(int k=0;k<NPOP;k++)
+				sum+=f[offset+k];
 	
-		rho[counter]=sum;
+			rho[counter]=sum;
 
-		double dense_temp=rho[counter];
-		double ux_temp=ux[counter];
[…]

### 2011-11-10 Python/benchmarks.py

@@ -1,0 +1,67 @@
+#!/usr/bin/python
+import numpy
+import pylab
+import scipy.special
+
+coeff=32
+omega=1.0/(0.5+0.5/coeff)
+radius=39
+diffusion=1.0/3.0*(1.0/omega-0.5)
+num_terms=20
+
+def read_file(file_name):
+    concentration=numpy.loadtxt(file_name)
+    pylab.imshow(concentration)
+    
+
+def read_files(file_dir):
+    styles=["kv","k^","ks","ko","kD"]    
+    non_time=[]    
+    legs=[]    
+    for num,counter in enumerate(range(200*coeff,2000*coeff,400*coeff)):
+        file_name=file_dir+"density"+(7-len(str(counter)))*"0"+str(counter)+".dat"
+        concentration=numpy.loadtxt(file_name)
+        dims=concentration.shape
+        #pylab.figure()
+        #pylab.imshow(concentration)
+        x=numpy.arange(0,dims[1])        
+        x_rad=numpy.linspace(0.0,1.0,radius+1)
+
+        
+        bessel=numpy.zeros_like(x)
+        bessel_zeros=scipy.special.jn_zeros(0,num_terms)
+        non_time.append(diffusion*counter/(radius*radius))
+        for term in range(0,num_terms):
+            bessel=bessel+2/(bessel_zeros[term]*scipy.special.jn(1,bessel_zeros[term]))\
+                *numpy.exp(-bessel_zeros[term]*bessel_zeros[term]*diffusion*counter/(radius*radius))\
+                *scipy.special.jn(0,bessel_zeros[term]*x/radius)
+        bessel=1-bessel
+        #bessel[numpy.where(bessel)>1]=0
+        #bessel=numpy.roll(bessel,dims[1]/2)
+        print "Shape",dims        
+        pylab.figure(1)
+        pylab.plot(x_rad,concentration[(dims[0]-1)/2,(dims[1]-1)/2:(dims[1]-1)/2+radius+1],styles[num])        
+        #pylab.plot(concentration[dims[0]/2-1,dims[1]/2:dims[1]/2+radius])
+        #pylab.figure(2)
+        pylab.plot(x_rad,bessel[numpy.where(x<=radius)],styles[num]+"--",markerfacecolor="None")
[…]

### 2011-11-10 Text/introduction.tex
Added cylinder benchmark.
A second benchmark.

@@
 
-Here some
+The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. Some examples for
+different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/cylinder1666.eps}
+\includegraphics[width=0.5\textwidth]{Figures/cylinder0833.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/cylinder0104.eps}
+\includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
+\caption{Profiles for different diffusion parameters. One can see that the diffusion is captured
+accurately in non-dimensional space \label{fig:cylinder:benchmark}.}
+\end{figure}
+
+\subsection{Steady mass transfer}
+The problem we want to address can be formulated through the following PDE:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=0,\, C(x,0)=C_s,\, \frac{\partial C}{\partial_y }(x,\delta)=0\\
+&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
+\end{aligned}
+\feq
 

### 2011-11-10 Benchmarks/film.cpp

@@ -1,0 +1,379 @@
+//Jos mass transfer
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+int radius;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=1000;
+int NOUTPUT=100;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_wall=1.0;
+double conc_inlet=0.0;
+std::vector<int> bb_nodes_inlet;
+std::vector<char>* dirs_inlet;
+
+std::vector<int> bb_nodes_wall;
+std::vector<int> dirs_wall;
+
+//BGK relaxation parameter
+double omega=1.0; ///1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
+			int counter=iY*NX+iX;
+			fout<<rho[counter]<<" ";
+		}
+		fout<<"\n";
+	}
+}
+
[…]

### 2011-11-11 Benchmarks/film.cpp
Wrote a code for film. Need to check it with analytics.

@@ -12,13 +12,12 @@
 int NY;
 int NX;
 int NUM;
-int radius;
 
 //Other constants
 const int NPOP=9;
 
 //Time steps
-int N=1000;
+int N=10000;
 int NOUTPUT=100;
 
 //Fields and populations
@@ -32,6 +31,7 @@ int * geometry;
 //Boundary conditions
 double conc_wall=1.0;
 double conc_inlet=0.0;
+double u0=0.05;
 std::vector<int> bb_nodes_inlet;
 std::vector<char>* dirs_inlet;
 
@@ -71,7 +71,7 @@ void writedensity(std::string const & fname)
 	}
 }
 
-void writegeometry(std::string const & fname)
+void writevelocityx(std::string const & fname)
 {
 	std::string filename=fname+".dat";
 	std::ofstream fout(filename.c_str());
@@ -82,11 +82,29 @@ void writegeometry(std::string const & fname)
 		for (int iY=0; iY<NY; iY++)
 		{
 			int counter=iY*NX+iX;
-			fout<<geometry[counter]<<" ";
+			fout<<ux[counter]<<" ";
 		}
 		fout<<"\n";
 	}
 }
+
+void writevelocityy(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
+			int counter=iY*NX+iX;
+			fout<<uy[counter]<<" ";
+		}
+		fout<<"\n";
+	}
+}
+
 
 
 
@@ -98,8 +116,6 @@ void init()
 	
 	//Bulk nodes initialization
 	double feq;
-	double geq;
-	double sum;
 	
 	for(int iY=0;iY<NY;iY++)
 		for(int iX=0;iX<NX;iX++)
@@ -159,9 +175,10 @@ void collide_column_bgk(int coor_y,int coor_bottom,int coor_top)
 
 void collide()
 {
[…]

### 2011-11-11 Python/benchmarks.py

@@ -57,11 +57,29 @@ def show_bessel():
     x=numpy.arange(0.0,10.0,0.1)
     bessel=scipy.special.jn(0,x)
     pylab.plot(x,bessel)
+
+def read_film(file_dir):
+    concentration=numpy.loadtxt(file_dir+"conc_initial.dat")
+    ux=numpy.loadtxt(file_dir+"ux_initial.dat")
+    uy=numpy.loadtxt(file_dir+"uy_initial.dat")
+    print concentration.shape
+    pylab.figure()    
+    pylab.imshow(concentration)
+    pylab.figure()
+    pylab.plot(concentration[:,200])
+    pylab.figure()
+    pylab.plot(concentration[:,0])
+    pylab.figure()
+    pylab.imshow(uy)
+    pylab.colorbar()
+
 if __name__=="__main__":
-    file_name="../Benchmarks/density0001000.dat"
+    #file_name="../Benchmarks/density0001000.dat"
+    file_name="../Benchmarks/conc_initial.dat"    
     file_dir="../Benchmarks/"
     #read_file(file_name)
     
-    read_files(file_dir)
+    #read_files(file_dir)
     #show_bessel()    
+    read_film(file_dir)    
     pylab.show()

### 2011-12-19 Text/introduction.tex
Film solution.

@@
 &\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=0,\, C(x,0)=C_s,\, \frac{\partial C}{\partial_y }(x,\delta)=0\\
+&C(0,y)=0,\, C(x,0)=C_s,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
 &U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
@@
 \feq
+{\color{red} This problem is different from what I solved on computer.}
 
+In any case here is what we want to solve as the system for :
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
+\end{aligned}
+\feq
+The system after non-dimensionalization becomes as follows:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H} \Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
+\end{aligned}
+\feq
+After a change of variables:
+\beq
+\begin{aligned}
+&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
+&\xi=\frac{y}{H}
+\end{aligned}
+\feq
+, the equation with boundary conditions becomes as follows:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
+&C(0,\xi)=C_0\\
+&C(\zeta,0)=C_{wall}\\
+&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
+\end{aligned}
+\feq 
+Still the equation cannot be solved with the separation of variables as it requires the homogenuos boundary conditions.
+Thus, let us introduce the new variable to be $\Theta=C-C_{wall}$.
+The system will be changed but not considerably:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
+&\Theta(0,\xi)=C_0-C_{wall}\\
+&\Theta(\zeta,0)=0,\, \Theta(\zeta,1)=0\\
+\end{aligned}
+\feq 
+This equation can be solved by separation of variables if the solutions is represented as the multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$.
+The differential equation will become as follows:
+\beq
+\begin{aligned}
+&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
+\end{aligned}
+\feq
 \section{Tweaking velocity}

### 2011-12-29 Text/introduction.tex
Verified numerical analytics. Probably too slow series convergence.

--- 2011-11-10 Text/introduction.tex
@@
 \feq
+{\color{red} This problem is different from what I solved on computer.}
 
+In any case here is what we want to solve as the system for :
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
+\end{aligned}
+\feq
+The system after non-dimensionalization becomes as follows:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H} \Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
+\end{aligned}
+\feq
+After a change of variables:
+\beq
+\begin{aligned}
+&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
+&\xi=\frac{y}{H}
+\end{aligned}
+\feq
+, the equation with boundary conditions becomes as follows:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
+&C(0,\xi)=C_0\\
+&C(\zeta,0)=C_{wall}\\
+&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
+\end{aligned}
+\feq 
+Still the equation cannot be solved with the separation of variables as it requires the homogenuos boundary conditions.
+Thus, let us introduce the new variable to be $\Theta=C-C_{wall}$.
+The system will be changed but not considerably:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
+&\Theta(0,\xi)=C_0-C_{wall}\\
+&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
+\end{aligned}
+\feq 
+This equation can be solved by separation of variables if the solutions is represented as the multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$.
+The differential equation will become as follows:
+\beq
+\begin{aligned}
+&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
+Y(\xi)}{\mathrm{d}\xi^2}\\
+&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
+\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
+\end{aligned}
+\feq
+The left and right parts depend on different variables. Therefore to be equal to each other both
+parts equal to constant, say $-m^4$. Thus, the separation of the variables leads to two ODE
+equations:
+\begin{equation*}
+\begin{aligned}
+&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
+&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
+\end{aligned}
+\end{equation*}
+The solution of the first equation is the exponential function:
+\beq
+X(\zeta)=\exp(-m^4 \zeta)\\
+\feq
+The solutions of the second equation are two hypergeometric function which can be expressed through
+the Bessel functions \cite{abramowitz}:
+\beq
+\begin{aligned}
+&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+\end{aligned}
+\feq
+The solution is the summation of two functions:
+\begin{equation*}
+Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
+\end{equation*}
+One can find coefficients from the boundary conditions:
+\beq
+\begin{aligned}
+&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
+&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
+&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
+&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
+\end{aligned}
+\feq
+Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
+numerical values:
+$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
+Therefore a solution in a general form is represented as:
+\beq
+\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
+\feq
+To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
+condition:
+\beq
+\Theta(0,\xi)=C_0-C_{wall}=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)}\\
+\feq
+Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
+J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
+\beq
+\begin{aligned}
+&\bigl(C_0-C_{wall}\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
+&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+\end{aligned}
+\feq
+Therefore, the overall solution is specified as:
+\beq
+\begin{aligned}
+&C(x,y)=C_{wall}+\sum_{m}{C_m
+\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
+\frac { x }{H}\Bigr)}\\
+&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+\end{aligned}
+\feq
 \section{Tweaking velocity}
+
 This section does the job of increasing velocity results. The ulimate goal is to increase velocity

### 2011-12-29 Python/benchmarks.py

@@ -272,332 +272,136 @@ def compare_full_profiles(file_dir):
 
 def film_reconstruction(file_dir):
     #bessel_zeros=scipy.special.jv(-3.0/4.0,num_terms)
-    wmfivetwo=numpy.array([0.20996479709362217, 0.018180897590318785, 0.006919303361557072,\
-                           0.0037318500468507265, 0.0023673658890243144, \
-                           0.0016504522182779553, 0.0012240656323313512, \
-                           0.0009483894730813764, 0.0007590968780885121, \
-                           0.0006230691899630487, 0.000521773141559365, \
-                           0.0004441474396258039, 0.00038324243624026397, \
-                           0.00033450473194280715, 0.0002948449039830018, \
-                           0.0002621039555673866, 0.0002347343932804438, \
-                           0.00021160239472918784, 0.00019186109713872825, \
-                           0.00017486713895424112, 0.00016012432055124612, \
-                           0.00014724473213250115, 0.0001359214046973261, \
-                           0.00012590872750600792, 0.00011700820222555297, \
-                           0.0001090579288501799, 0.00010192474302362525, \
-                           0.00009549826478267914, 0.00008968634379190777, \
-                           0.00008441153749062422, 0.00007960836196536182, \
-                           0.00007522112702512196, 0.00007120221729922205, \
-                           0.00006751071698186362, 0.0000641113016165315, \
-                           0.000060973339051508034, 0.00005807015547318643, \
-                           0.00005537843263812609, 0.00005287771007323228, \
-                           0.00005054997178480274, 0.000048379301408858354, \
-                           0.00004635159310216252, 0.00004445430807096168, \
-                           0.00004267626865559752, 0.00004100748346843951, \
-                           0.00003943899832564699, 0.000037962768698096496, \
-                           0.000036571550189571094, 0.00003525880417636117, \
-                           0.00003401861624793521, 0.00003284562549298673, \
-                           0.00003173496300815666, 0.000030682198273720266, \
-                           0.00002968329226266342, 0.0000287345563299556, \
-                           0.000027832616078876215, 0.0000269743795242561, \
-                           0.00002615700897675555, 0.00002537789615694936, \
-                           0.000024634640120406708, 0.00002392502763531586, \
-                           0.000023247015704908107, 0.000022598715969558762, \
[…]

### 2011-12-29 Benchmarks/FullProfile/film_iran_antibb.cpp
Something wrong with analytical solution of Irandoust and mine as well.

@@ -1,0 +1,328 @@
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=100000;
+int NOUTPUT=2000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_wall=1.0;
+double conc_inlet=0.0;
+double u0=0.05;
+std::vector<int> bb_nodes_inlet;
+std::vector<char>* dirs_inlet;
+
+std::vector<int> bb_nodes_wall;
+std::vector<int> dirs_wall;
+
+//BGK relaxation parameter
+double omega=1.8; ///1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
+			int counter=iY*NX+iX;
[…]

### 2011-12-29 Benchmarks/FullProfile/film_iran_inamuro.cpp

@@ -1,0 +1,334 @@
+//Jos mass transfer
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=100000;
+int NOUTPUT=2000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_wall=1.0;
+double conc_inlet=0.0;
+double u0=0.05;
+std::vector<int> bb_nodes_inlet;
+std::vector<char>* dirs_inlet;
+
+std::vector<int> bb_nodes_wall;
+std::vector<int> dirs_wall;
+
+//BGK relaxation parameter
+double omega=1.8; ///1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
+			int counter=iY*NX+iX;
+			fout<<rho[counter]<<" ";
+		}
+		fout<<"\n";
+	}
+}
+
+void writevelocityx(std::string const & fname)
+{
[…]

### 2011-12-29 Python/benchmarks.py

@@ -707,6 +707,129 @@ def check_analytics():
     pylab.figure()
     pylab.plot(c[:,0])
     pylab.title("Inlet")
+
+def check_irandoust(file_dir):
+    concentration=numpy.loadtxt(file_dir+"FullProfile/film_iran_antibb0100000.dat")
+    dims=concentration.shape    
+    print dims
+ 
+    pylab.figure()    
+    pylab.imshow(concentration,extent=(0,20,0,1))
+    pylab.title("Simulations")
+    pylab.colorbar()    
+    #pylab.figure()
+    #pylab.plot(concentration[:,dims[1]/2])
+    #pylab.figure()
+    #pylab.plot(concentration[:,0])
+
+    num_terms=50
+    c0=0.0
+    cs=1.0
+    u_bubble=0.05*20
+    omega=1.8
+    diffusion=1.0/3.0*(1.0/omega-0.5)
+
+    y,x=0.01*numpy.mgrid[1:101,1:2001]
+    
+    c=numpy.zeros_like(x)
+    
+    sign=-1
+    for i in range(0,num_terms):
+        sign=-sign
+        c=c+sign*(scipy.special.erfc((y+2.0*i)/numpy.sqrt(4.0*x*diffusion/u_bubble))+scipy.special.erfc((2.0*(i+1)-y)/numpy.sqrt(4.0*x*diffusion/u_bubble)))
+        
+    c=c0-(c0-cs)*c
+    pylab.figure()    
+    pylab.imshow(c,extent=(0,10,0,0.5))
+    pylab.colorbar()
+    pylab.title("Analytics")
+    
+    pylab.figure()
+    pylab.plot(concentration[0,:])
+    pylab.figure()
+    pylab.plot(concentration[:,0])
+    pylab.figure()
+    pylab.plot(concentration[:,dims[1]-1])
+    
+    c_levels=numpy.arange(0.2,1.0,0.2)
+    #print c_levels
+    pylab.figure(figsize=(10,1))
+    c1=pylab.contour(concentration,levels=c_levels,extent=(0.0,20.0,0.0,1.0))
+    pylab.clabel(c1,fontsize=9, inline=1)    
+    #pylab.figure(figsize=(10,1))
+    c2=pylab.contour(c,levels=c_levels,extent=(0.0,10.0,0.0,0.5))
+    #pylab.clabel(c2,fontsize=9, inline=1)    
+    
+    
+def func(a,b,c,d):
+    prod=1
[…]

### 2012-01-04 Python/streamlines.py
Small changes in streamlines. Streamlines look awful need to find something else.

@@ -14,10 +14,10 @@ def produce_streamlines(dir_name):
     dims=ux.shape
     #pylab.figure()
     #pylab.imshow(phase)
-    pylab.figure()
-    pylab.imshow(ux)
-    pylab.figure()
-    pylab.imshow(uy)    
+    #pylab.figure()
+    #pylab.imshow(ux)
+    #pylab.figure()
+    #pylab.imshow(uy)    
     print dims
  
     y,x=numpy.mgrid[0:dims[0],0:dims[1]]        
@@ -80,10 +80,10 @@ def produce_streamlines(dir_name):
     dims=ux.shape
     #pylab.figure()
     #pylab.imshow(phase)
-    pylab.figure()
-    pylab.imshow(ux)
-    pylab.figure()
-    pylab.imshow(uy)    
+    #pylab.figure()
+    #pylab.imshow(ux)
+    #pylab.figure()
+    #pylab.imshow(uy)    
     print dims
  
     x,y=numpy.mgrid[0:dims[0],0:dims[1]]        
@@ -115,8 +115,9 @@ def produce_streamlines(dir_name):
     
 
 if __name__=="__main__":
-    file_dir="TweakingHydro2DRight/"
-    produce_bunch_streamlines(file_dir)
-    Ngl.end()
+    file_dir="TweakingHydro2DRight/90/"
+    print file_dir
+    produce_streamlines(file_dir)
+    #Ngl.end()
     
     

### 2012-01-05 Text/introduction.tex
Tweaked velocities simulations are added. Need to analyze free surface velocities and compare them with original ones.

@@
 \feq
+
 \section{Tweaking velocity}
+The reason to tweak velocity is that the velocity field because of the highly nonlinear binary liquid lattice Boltzmann model do not have nice velocity profile, since some streamlines penetrate the bubble in the reference frame of the bubble.
+Therefore there exists a normal to the surface of the bubble velocity component which destroys right away the advection-diffusion results.
+Therefore, a special additional free-surface solver was developed in order to dispose the vertical components.
+
+The solver was through consequent steps.
+First, we extracted the velocity profiles from the original binary-liquid simulations.
+Then, we imposed walls with velocity of the bubble, so the bubble stays still.
+At the surface of the bubble the free boundary conditions were imposed, see \ref{appendix-free-surface}.
+One of the examples is shown in Fig.
+\ref{fig:streamlines:tweaked:velocity}.
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/original.eps}\\
+\includegraphics[width=\textwidth]{Figures/performed.eps}\\
+\caption{The comparison between original velocity fields and velocity fields obtained from free surface solver. \label{fig:streamlines:tweaked:velocity}}
+\end{figure}
 
@@
 
+\appendix
+\section{Free surface boundary conditions}
+There are a few implementations of free boundary conditions \cite{ginzburg-free,verberg-free}.
+However, we developed the easy solver to impose the free surface boundary conditions at the complicated surface of the bubble.
+The reason is to impose the symmetric boundary conditions.
+Because the boundary is the staircase approximation, one can find the normal to the boundary which is always located by the angle of multiple of $45$, see Fig.
+\ref{fig:free:surface}.
+Imposing the symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$.
+We can copy populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and $c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and $c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and $c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/free_surface.eps}
+\caption{Free-surface boundary condition represented in the lattice Boltzmann. By crosses we outline boundary nodes, by circle the fluid node is outlined. \label{fig:free:surface}}
+\end{figure}
 \bibliographystyle{unsrtnat}

### 2012-01-06 Text/introduction.tex
Need to keep the same Peclet number either with periodic boundary conditions (easiest case). Calculate critical velocities.

@@
 
-The solver was through consequent steps.
-First, we extracted the velocity profiles from the original binary-liquid simulations.
-Then, we imposed walls with velocity of the bubble, so the bubble stays still.
-At the surface of the bubble the free boundary conditions were imposed, see \ref{appendix-free-surface}.
-One of the examples is shown in Fig.
-\ref{fig:streamlines:tweaked:velocity}.
+The solver was through consequent steps. First, we extracted the velocity profiles from the
+original binary-liquid simulations. Then, we imposed walls with velocity of the bubble, so the
+bubble stays still. At the surface of the bubble the free boundary conditions were imposed, see
+\ref{appendix-free-surface}. One of the examples is shown in Fig.
+\ref{fig:streamlines:tweaked:velocity}. Among all the simulations the bulk velocity in film and the
+slug are different of no more than $7$ percent. {\color{red} Add some pictures froms streamlines.py
+if it's required to show more.}
 \begin{figure}
-\includegraphics[width=\textwidth]{Figures/original.eps}\\
-\includegraphics[width=\textwidth]{Figures/performed.eps}\\
+\includegraphics[angle=90,width=\textwidth]{Figures/original.eps}\\
+\includegraphics[angle=90,width=\textwidth]{Figures/performed.eps}\\
 \caption{The comparison between original velocity fields and velocity fields obtained from free surface solver. \label{fig:streamlines:tweaked:velocity}}
@@
 
+\section{Keeping Peclet}
 This section does the job of increasing velocity results. The ulimate goal is to increase velocity
@@
 \section{Free surface boundary conditions}
+\label{appendix-free-surface}
 There are a few implementations of free boundary conditions \cite{ginzburg-free,verberg-free}.
-However, we developed the easy solver to impose the free surface boundary conditions at the complicated surface of the bubble.
-The reason is to impose the symmetric boundary conditions.
-Because the boundary is the staircase approximation, one can find the normal to the boundary which is always located by the angle of multiple of $45$, see Fig.
-\ref{fig:free:surface}.
-Imposing the symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$.
-We can copy populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and $c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and $c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and $c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.
+However, we developed the easy solver to impose the free surface boundary conditions at the
+complicated surface of the bubble. The reason is to impose the symmetric boundary conditions.
+Because the boundary is the staircase approximation, one can find the normal to the boundary which
+is always located by the angle of multiple of $45$, see Fig. \ref{fig:free:surface}. Imposing the
+symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
+populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
+$c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and
+$c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and
+$c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.
 

### 2012-01-06 Python/streamlines.py

@@ -1,11 +1,14 @@
 #!/usr/bin/python
 import numpy
 import pylab
+import os
+import math
 
 def produce_bunch_streamlines(file_dir):
     for x in range(3,93,3):
         produce_streamlines(file_dir+str(x)+"/")
         print "Done with ",x
+
 def produce_streamlines(dir_name):
     from PyNGL import Ngl
     geom=numpy.loadtxt(dir_name+"geometry.dat").transpose()
@@ -40,7 +43,7 @@ def produce_streamlines(dir_name):
     #resources.wkPaperSize="A5"
     #resources.nglFrame = False
     resources.vfXArray=numpy.linspace(0.0,15.0,len(ux[1,::5]))
-    resources.vfYArray=numpy.linspace(0.0,1.0,len(ux[::2,1]))
+    resources.vfYArray=numpy.linspace(0.0,1.0,len(ux[::5,1]))
     resources.nglFrame=False
 
 
@@ -68,15 +71,15 @@ def produce_streamlines(dir_name):
     resources2.sfYArray=numpy.linspace(0.0,1.0,len(ux[:,1]))
  
      
-    plot=Ngl.streamline(wks,uy[::2,::5],ux[::2,::5],resources)
+    plot=Ngl.streamline(wks,uy[::5,::5],ux[::5,::5],resources)
     Ngl.contour(wks,geom,resources2)        
     #Ngl.contour(wks,phase,resources2)        
     #plot=Ngl.streamline(wks,vx,vy,resources)
     #Ngl.end()
     
     ### Producing outcome of velocities
-    ux=numpy.loadtxt(dir_name+"vely0200000.dat")
-    uy=numpy.loadtxt(dir_name+"velx0200000.dat")
+    ux=numpy.loadtxt(dir_name+"velx0200000.dat").transpose()
+    uy=numpy.loadtxt(dir_name+"vely0200000.dat").transpose()
     dims=ux.shape
     #pylab.figure()
     #pylab.imshow(phase)
@@ -93,31 +96,231 @@ def produce_streamlines(dir_name):
  
     wks_type = "eps"
     wks = Ngl.open_wks(wks_type,dir_name+"performed")
-    resources = Ngl.Resources()
+    ##resources = Ngl.Resources()
         
     #resources.tiMainFont    = "Times-Roman"
     #resources.tiMainOn=True
     #resources.tiMainString="Ca=0.22 "
            
[…]

### 2012-01-09 Text/introduction.tex
Compared with analytics. Pretty nice coincedence.

@@
 \usepackage{tabularx}
+\usepackage{leftidx}
 
@@
 
-\subsection{Steady mass transfer}
-The problem we want to address can be formulated through the following PDE:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=0,\, C(x,0)=C_s,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
-&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
-\end{aligned}
-\feq
-{\color{red} This problem is different from what I solved on computer.}
-
+\subsection{Parabolic profile with velocity zero gradient at the wall}
 In any case here is what we want to solve as the system for :
@@
 
+\subsection{The parabolic profile mass transfer and comparison}
+The problem we want to address can be formulated through the following PDE:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=0,\, C(x,\pm \delta)=C_s,\, \frac{\partial C}{\partial y }(x,0)=0\\
+&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
+\end{aligned}
+\feq
+The same procedure can be done as in the previous case to redefine variables. After substitution
+the following can be obtained:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
+\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
+\end{aligned}
+\feq
+After separation of variables, $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$ one can come up with two
+equations:
+\beq
+\label{fourier:separation:variables}
+\begin{aligned}
+&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}+m^4 X(\zeta)=0\\
+&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 (1-\xi^2) Y(\xi)=0
+\end{aligned}
+\feq
+The first equation has a solution:
+\beq
+X(\zeta)=\exp(-m^4 \zeta)
+\feq
+The second equation can be simplified after substitution $\bar{\xi}=m \sqrt{2} \xi$ to the standard
+equation:
+\beq
+Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
+\feq
+The equation above has two solutions via parabolic cylinder functions or through the confluent
+hypergeometric function \cite{abramowitz}:
+\beq
+\begin{aligned}
+&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
+&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
+\end{aligned}
+\feq 
+Taking symmetry conditions in the consideration by leaving only even solution, Eq.
+(\ref{fourier:separation:variables}) has a solution as:
+\beq
+Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
+\feq
+To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
+${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
+found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
+$5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
+\beq
+-C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)} 
+\feq
+One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
+\beq
+\label{coeff:series:parabolic:profile}
+C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)^2\mathrm{d}x}}
+\feq
+Therefore a whole solution can be written as:
+\begin{equation}
+C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
+y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
+\end{equation}
+where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
+between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
+\caption{Comparison between analytical profile and simulations with pressure antibounceback
+conditions. One can see given a low resolution of the profile a nice coincedence.}
+\end{figure}
+
 \section{Tweaking velocity}
@@
 where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
-means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
+means one needs to increase the diffusion coefficient as well.
+
+We make a few runs with velocities
 $5,10,20,40$ times larger than original velocities.

### 2012-01-09 Python/benchmarks.py

@@ -401,7 +401,7 @@ def film_reconstruction(file_dir):
     c0=0
     coeffm=wmfivetwo/wmcubic*(c0-cwall)
     omega=1.8
-    u_bubble=0.05*80
+    u_bubble=0.05*40
     diffusion=1.0/3.0*(1.0/omega-0.5)
 
     pe=u_bubble/diffusion
@@ -900,6 +900,94 @@ def irandoust_construction(file_dir):
     c2=pylab.contour(c,linestyles="dotted",levels=c_levels,extent=(0.0,10.0,0.0,0.5))
     c_iran=pylab.contour(c_iran,levels=c_levels,extent=(0.0,10.0,0.0,0.5))
 
+def final_comparison():
+    from scipy.special import hyp1f1    
+    eig=numpy.array([1.296763402567712, 2.38114622522328, 3.10937975527442, \
+         3.696980043577128, 4.203257494533186, 4.654804542010845, \
+         5.06627047109941, 5.446744077399425, 5.802324195412259, \
+         6.137338548284962])
+
+    coeff=numpy.array([1.20083, -0.299161, 0.160826, -0.107437, 0.0796461, -0.0627757, \
+           0.0515192, -0.0435107, 0.0375418, -0.0329333])
+
+    y,x=0.01*numpy.mgrid[-100:101,0:4000]
+    c=numpy.zeros_like(x)
+    
+    num_terms=10
+
+    cwall=1
+    c0=0
+    print "Coeff=",coeff
+    
+    coeffm=coeff*(c0-cwall)
+    omega=1.8
+    
+    u_bubble=0.05*40
+    diffusion=1.0/3.0*(1.0/omega-0.5)
+
+    pe=u_bubble/diffusion
+    
+    print "Coeff=",coeffm
+    print "Eig=",eig
+    for i in range(0,num_terms):
+        c=c+coeffm[i]*numpy.exp(-(eig[i]**4)*x*diffusion/u_bubble)*numpy.exp(-0.5*eig[i]*eig[i]*y*y)*hyp1f1(0.25-0.25*eig[i]*eig[i],0.5,eig[i]*eig[i]*y*y)
+        print i
+    c=c+cwall
+ 
+    c_levels=numpy.arange(0.2,1.0,0.1)
+ 
+    conc_antibb =numpy.loadtxt(file_dir+"FullProfile/"+"film_antibb0050000.dat")
[…]

### 2012-01-12 Text/introduction.tex
Started doing the Peclet number simulations. Need to find applicable regime.

@@
 \section{Keeping Peclet}
-This section does the job of increasing velocity results. The ulimate goal is to increase velocity
-to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
-nondimensional parameter Peclet number governs the advection-diffusion equation:
+This section addresses the performance of the simulations. The ulimate goal is to increase
+velocity at least by several orders while keeping dimensionless parameters the same. Increasing
+velocity can result in simulations of a lot of unit cells required for continuous picture
+representation.
+
+Only nondimensional parameter Peclet number governs the advection-diffusion equation:
 \beq
@@
 where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
-means one needs to increase the diffusion coefficient as well.
+means one needs to increase the diffusion coefficient as well. The runs were made with
+velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
+its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
+boundary conditions were used and mass transfer coefficient was calculated according to Eq.
+(\ref{main:simulation:equation}).
+\begin{table}[htb!]
+\begin{tabularx}{0.5\textwidth}{|X|X|}
+\hline
+$U_{bubble}$& $Ca$\\
+\hline
+0.0055&0.097\\
+0.0143&0.254\\
+0.0297&0.526\\
+0.0424&0.750\\
+0.0588&1.040\\
+\hline
+\end{tabularx}
+\end{table}
+For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
+thumb that for such simulations the velocity shouldn't be more than $0.05$.
 
-We make a few runs with velocities
-$5,10,20,40$ times larger than original velocities.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
+\caption{The same Peclet number for $Ca=0.0055$. One can see that
+the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
+concentration!!!} \label{fig:ca0055:keeping:peclet}}
+\end{figure}
 

### 2012-01-12 Python/ScalingPeclet/copy_from_checkers.py

@@ -1,0 +1,24 @@
+import numpy
+import os
+import subprocess
+
+def run_simulations():
+    capillary_str=[str(x) for x in [9,21]]
+    scale=[2,4,8,10,20,40]
+    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    for counter,dir_temp in enumerate(capillary_str):
+        os.chdir(dir_temp)
+        for scale_counter in range(0,len(scale_str)-counter):
+            #subprocess.call(['mkdir','-p',scale_str[scale]])
+           
+            os.chdir(scale_str[scale_counter])
+            name=str(20000*scale[len(scale_str)-counter-1]/scale[scale_counter])
+            print name
+            #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+            subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale_counter]+"/density"+'0'*(7-len(name))+name+".dat","."])
+            os.chdir("..")
+        os.chdir("..")
+
+if __name__=="__main__":
+    #modify_file()
+    run_simulations()

### 2012-01-12 Python/ScalingPeclet/govern.py

@@ -1,0 +1,40 @@
+import numpy
+import os
+import subprocess
+def modify_file(scale_str):
+    f=open("binary.pbs","r+")
+    f2=open("binary_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE",scale_str)
+        f2.write(line)
+            
+    f.close()
+    f2.close()
+
+
+def run_simulations():
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    scale_str=[str(x) for x in [2,4,6,8,10,15,20,40]]
+    for counter,dir_temp in enumerate(capillary_str):
+        subprocess.call(['cp','main.out',dir_temp+"/"])
+        subprocess.call(['cp','binary.pbs',dir_temp+"/"])
+        os.chdir(dir_temp)
+        for scale in range(0,len(scale_str)-counter):
+            subprocess.call(['mkdir','-p',scale_str[scale]])
+            subprocess.call(['cp','main.out',scale_str[scale]+"/"])
+            subprocess.call(['cp','binary.pbs',scale_str[scale]+"/"])
+           
+            subprocess.call(['cp','geometry.dat',scale_str[scale]+"/"])
+            subprocess.call(['cp','velx0200000.dat',scale_str[scale]+"/"])
+            subprocess.call(['cp','vely0200000.dat',scale_str[scale]+"/"])
+            os.chdir(scale_str[scale])
+            modify_file(scale_str[scale])
+            #subprocess.call(['qsub'],'binary_new.pbs']) 
+            os.chdir("..")
+            #subprocess.call(['qsub','binary_new.pbs'])
+        os.chdir("..")
+
+if __name__=="__main__":
+    #modify_file()
+    run_simulations()

### 2012-01-12 Python/ScalingPeclet/mass_open.cpp

@@ -1,0 +1,575 @@
+//Jos mass transfer
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=1000000;
+int NOUTPUT=50000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_inlet=0.0;
+double conc_bubble=1.0;
+double conc_wall=1.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+//double diffusion=(1.0/omega_minus-0.5)*ce;
+//double ce=diffusion/(1.0/omega_minus-0.5);
+
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
[…]

### 2012-01-12 Python/ScalingPeclet/mass_periodic.cpp

@@ -1,0 +1,605 @@
+//Simple mass transfer
+
+
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+#include <limits>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Overall scaling parameter
+int scale=1;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=20000;
+int NOUTPUT=20000;
+int NSIGNAL=1000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_inlet=0.0;
+double conc_bubble=1.0;
+double conc_wall=0.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
+		for (int iY=0; iY<NY; iY++)
+		{
+			int counter=iY*NX+iX;
[…]

### 2012-01-12 Python/peclet.py

@@ -1,0 +1,157 @@
+#!/usr/bin/python
+import numpy
+import os
+import subprocess
+import math
+import pylab
+
+def run_simulations():
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    scale_str=[str(x) for x in [2,4,6,8,10,15,20,40]]
+    for counter,dir_temp in enumerate(capillary_str):
+        os.chdir(dir_temp)
+        for scale in range(0,len(scale_str)-counter):
+            subprocess.call(['mkdir','-p',scale_str[scale]])
+           
+            os.chdir(scale_str[scale])
+            subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+            os.chdir("..")
+        os.chdir("..")
+
+def Get_Zero(prof):
+    zero=0
+    #pylab.figure()
+    #pylab.plot(prof)
+    for counter in range(0, len(prof)/2):
+        if prof[counter]>=0 and prof[counter+1]<0:
+            zero=-(prof[counter]*(counter+1)-prof[counter+1]*counter)/(prof[counter+1]-prof[counter])
+    return (zero-0.5)/(len(prof)-2)
+
+def analyze_particular_simulation(dir_name):
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    scale_str=[str(x) for x in [2,4,6,8,10,15,20,40]]
+    gamma=0.0728
+    diam=1.5e-3    
+
+    ind=capillary_str.index(dir_name)    
+    os.chdir("ScalingPeclet/"+dir_name) 
+    
+    name_geom="geometry.dat"
+    name_velx="velx0200000.dat"
+    name_vely="vely0200000.dat"
+    
+    phase=numpy.loadtxt(name_geom)
+    velx=numpy.loadtxt(name_velx)
+    vely=numpy.loadtxt(name_vely)
+
+    dims=phase.shape
+    center=phase[dims[0]/2,:]
+   
+    z1 = numpy.min(numpy.where(center < 0.0))
+    z2 = numpy.max(numpy.where(center < 0.0))
+    if z1==0:
+        z2=numpy.min(numpy.where(center>0.0))+dims[1]
+        z1=numpy.max(numpy.where(center>0.0))
+    print z1,z2
+    #print "Bubble length=",(z2-z1)/200.0
[…]

### 2012-01-12 Python/streamlines.py

@@ -187,6 +187,69 @@ def get_velocities_compare():
     #pylab.ylabel(r'''$\delta$''',fontsize=30)
 
 
+def get_velocities_compare_selection():
+
+    print os.getcwd()
+    widths=[]
+    velocities=[]
+    re=[]
+    
+    for i in [9,21,42,60,84]:
+        dir_name="HydroResultsRight/"+str(i)
+        os.chdir(dir_name)
+        
+        name_phi="phase300000.dat"
+        name_velx="velocityx300000.dat"
+        name_vely="velocityy300000.dat"
+        
+        phase=numpy.loadtxt(name_phi)
+        velx=numpy.loadtxt(name_velx)
+        vely=numpy.loadtxt(name_vely)
+
+        dims=phase.shape
+        center=phase[dims[0]/2,:]
+       
+        z1 = numpy.min(numpy.where(center < 0.0))
+        z2 = numpy.max(numpy.where(center < 0.0))
+        if z1==0:
+            z2=numpy.min(numpy.where(center>0.0))+dims[1]
+            z1=numpy.max(numpy.where(center>0.0))
+        print z1,z2
+        print "Bubble length=",(z2-z1)/200.0
+        print "Slug length=",15.0-(z2-z1)/200.0
+        print "Liquid_velocity",numpy.sum(velx[1:-1,((z1+z2+dims[1])/2)%dims[1]])/(dims[0]-2)
+        #print "Gas holdup",float(len(numpy.where(array['phi']<0)[0]))/(dims[1]*(dims[0]-2))
+        prof=phase[:,((z1+z2)/2)%dims[1]]
+        widths.append(Get_Zero(prof))     
+        velocities.append(velx[dims[0]/2,z2%dims[1]])
+        re.append(velx[dims[0]/2,z2%dims[1]]*dims[0]/(2.0/3.0))
+    
+      
+        os.chdir("../..")
+    
+    capillaries=numpy.array(velocities)*(2.0/3.0)/math.sqrt(8.0*0.04*0.04/9.0)
+    
+    print "Widths=",widths
+    print "Capillaries=",capillaries
+    print "Velocities=",velocities
+    
+    fig1=pylab.figure()  
+    pylab.plot(capillaries,widths,"go-",linewidth=3,markersize=10)
+    fig2=pylab.figure()
+    pylab.loglog(capillaries,widths,"go-",linewidth=3,markersize=10)
+    pylab.xlim(0.02,1.5)
[…]

### 2012-01-17 Text/introduction.tex
Started doing last simulations.

@@
 \begin{table}[htb!]
-\begin{tabularx}{0.5\textwidth}{|X|X|}
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
 \hline
-$U_{bubble}$& $Ca$\\
+Scale&$U_{bubble}$&Time Iterations&$C_{aver}$\\
 \hline
-0.0055&0.097\\
-0.0143&0.254\\
-0.0297&0.526\\
-0.0424&0.750\\
-0.0588&1.040\\
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.097$}\\
+\hline
+$2$ &$0.011$&$400000$&$0.318$\\
+$4$ &$0.023$&$200000$&$0.319$\\
+$8$ &$0.044$&$100000$&$0.320$\\
+$10$&$0.055$&$80000$ &$0.321$\\
+$20$&$0.11 $&$40000$ &$0.324$\\
+$40$&$0.22 $&$20000$ &$0.328$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.254$}\\
+\hline
+$2$& $0.0286$&$800000$&$0.6533$\\
+$4$& $0.0572$&$400000$&$0.6591$\\
+$8$& $0.1144$&$200000$&$0.6692$\\
+$10$&$0.1430$&$160000$&$0.6734$\\
+$20$&$0.2860$&$80000$ &$0.6894$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.526$}\\
+\hline
+$2$&$0.0594$&$200000$&$0.3271$\\
+$4$&$0.1188$&$100000$&$0.3315$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.750$}\\
+\hline
+$2$&$0.0848$&$200000$&$0.3489$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=1.040$}\\
+\hline
+$2$&$0.1176$&$200000$&$0.3675$\\
 \hline
 \end{tabularx}
+\caption{Scaling Peclet table. One can see that scaling is pretty successful. One can see as well
+that the stability limit is approximately around $U_{bubble}=0.1$. That can give us an idea of
+scale of simulations. \label{table:scaling:peclet}}
 \end{table}
-For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
-thumb that for such simulations the velocity shouldn't be more than $0.05$.
 
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
-\caption{The same Peclet number for $Ca=0.0055$. One can see that
-the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
-concentration!!!} \label{fig:ca0055:keeping:peclet}}
+The corresponding to Table \ref{table:scaling:peclet} contour profiles for different scalings are
+presented in Fig. \ref{fig:contours:scaling:peclet}.
+\begin{figure}
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca026.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca054.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca05.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca097.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca14.eps}\\
+\caption{Contours for scaling Peclet number.\label{fig:contours:scaling:peclet}}
 \end{figure}
+
+\section{Performing real simulations}
+As it was found earlier one needs to make a few units simulations to obtain a proper volumetric
+mass transfer coefficient. This section studies the quantity of the unit cells on the volumetric
+mass transfer coefficient to be independent of the number of unit cells. The cases we want to
+examine in terms of the capillary number are indicated above. The number of cells we want to
+simulate are $1$,$4$,$6$,$8$,$10$. As it was discussed in the previous section we want to keep
+velocity around $0.05-0.1$. The number of steps for mass to cross whole domain is approximately
+$1.5 \frac{N_x}{U_{bubble}}$, given the bulk velocity. If $U_{bubble}$ is taken as $0.05$ then for
+the domain size $3000$ one can obtain the following number of iteration for mass transfer to be
+stabilize $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ time iterations are enough for system
+to be stabilized.
+
+%For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
+%thumb that for such simulations the velocity shouldn't be more than $0.05$.
+
+%\begin{figure}[htb!]
+%\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
+%\caption{The same Peclet number for $Ca=0.0055$. One can see that
+%the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
+%concentration!!!} \label{fig:ca0055:keeping:peclet}}
+%\end{figure}
 

### 2012-01-17 Python/ScalingPeclet/copy_from_checkers.py

@@ -19,6 +19,26 @@ def run_simulations():
             os.chdir("..")
         os.chdir("..")
 
+
+def copy_files(dir_name,factor,subtract):
+    scale=[2,4,8,10,20,40]
+    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    os.chdir(dir_name)
+    for scale_counter in range(0,len(scale_str)-subtract):
+        #subprocess.call(['mkdir','-p',scale_str[scale]])
+
+        os.chdir(scale_str[scale_counter])
+        name=str(factor*20000*scale[len(scale_str)-subtract-1]/scale[scale_counter])
+        print name
+            #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+        subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_name+"/"+scale_str[scale_counter]+"/density"+'0'*(7-len(name))+name+".dat","."])
+        os.chdir("..")
+    os.chdir("..")
+
+
 if __name__=="__main__":
     #modify_file()
-    run_simulations()
+    #run_simulations()
+    #copy_files("42",5,4)
+    #copy_files("60",10,5)
+    copy_files("84",10,5)

### 2012-01-17 Python/UnitCells/checkers.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+#mkdir -p 9 21 42 60 84
+scp mass_periodic.cpp "shurik@checkers.westgrid.ca":/home/shurik/ScalingPeclet/$i/
+scp govern.py "shurik@checkers.westgrid.ca":/home/shurik/ScalingPeclet/$i/
+for i in 9 21 42 60 84
+do
+  cd $i
+  scp geometry.dat "shurik@checkers.westgrid.ca":/home/shurik/ScalingPeclet/$i/ 
+  scp vel[x,y]0200000.dat "shurik@checkers.westgrid.ca":/home/shurik/ScalingPeclet/$i/
+  cd ..
+  echo "Done with $i"
+done

### 2012-01-17 Python/UnitCells/copy_from_checkers.py

@@ -1,0 +1,44 @@
+import numpy
+import os
+import subprocess
+
+def run_simulations():
+    capillary_str=[str(x) for x in [9,21]]
+    scale=[2,4,8,10,20,40]
+    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    for counter,dir_temp in enumerate(capillary_str):
+        os.chdir(dir_temp)
+        for scale_counter in range(0,len(scale_str)-counter):
+            #subprocess.call(['mkdir','-p',scale_str[scale]])
+           
+            os.chdir(scale_str[scale_counter])
+            name=str(20000*scale[len(scale_str)-counter-1]/scale[scale_counter])
+            print name
+            #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+            subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale_counter]+"/density"+'0'*(7-len(name))+name+".dat","."])
+            os.chdir("..")
+        os.chdir("..")
+
+
+def copy_files(dir_name,factor,subtract):
+    scale=[2,4,8,10,20,40]
+    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    os.chdir(dir_name)
+    for scale_counter in range(0,len(scale_str)-subtract):
+        #subprocess.call(['mkdir','-p',scale_str[scale]])
+
+        os.chdir(scale_str[scale_counter])
+        name=str(factor*20000*scale[len(scale_str)-subtract-1]/scale[scale_counter])
+        print name
+            #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+        subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_name+"/"+scale_str[scale_counter]+"/density"+'0'*(7-len(name))+name+".dat","."])
+        os.chdir("..")
+    os.chdir("..")
+
+
+if __name__=="__main__":
+    #modify_file()
+    #run_simulations()
+    #copy_files("42",5,4)
+    #copy_files("60",10,5)
+    copy_files("84",10,5)

### 2012-01-17 Python/UnitCells/jos_parallel.cpp

@@ -1,0 +1,756 @@
+//Jos mass transfer
+#include <mpi.h>
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+//MPI variables
+int mpi_rank;
+int mpi_size;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=100000;
+int NOUTPUT=1000;
+int NSIGNAL=100;
+int scale=1;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *mpi_rho;
+double *ux;
+double *uy;
+int * geometry;
+double * mpi_left;
+double * mpi_right;
+double * mpi_temp;
+
+
+//Boundary conditions
+double conc_bubble=1.0;
+double conc_wall=0.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	if (mpi_size==1)
+	{
[…]

### 2012-01-17 Python/peclet.py

@@ -121,37 +121,59 @@ def analyze_particular_simulation(dir_name):
     pylab.figure(1)    
     pylab.savefig("scalingpeclet"+str(capillary)[0]+str(capillary)[2:4]+".eps",format="EPS",dpi=300)
 
-def check_particular_contours(dir_name):
+def check_particular_contours(dir_name,factor,subtract):
     capillary_str=[str(x) for x in [9,21,42,60,84]]
+    capillaries=[0.097,0.254,0.526,0.750,1.040]
     scale=[2,4,8,10,20,40]
     scale_str=[str(x) for x in [2,4,8,10,20,40]]
     os.chdir("ScalingPeclet/"+dir_name)
 
     c_levels=numpy.arange(0.2,1.0,0.2)
-    counter=capillary_str.index(dir_name)
-    for scale_counter in range(0,len(scale_str)-counter):
+    counter=capillary_str.index(dir_name) 
+    capillary=capillaries[counter]
+    for scale_counter in range(0,len(scale_str)-subtract):
         #subprocess.call(['mkdir','-p',scale_str[scale]])
         os.chdir(scale_str[scale_counter])
-        name=str(20000*scale[len(scale_str)-counter-1]/scale[scale_counter])
+        name=str(20000*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter])
         name="density"+"0"*(7-len(name))+name+".dat"        
-        print name
+        print "Filename=",name
+        print "Scale=",scale_str[scale_counter]        
         #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
         arr=numpy.loadtxt(name)
-        print "Overall concentration=",numpy.sum(arr[numpy.where(arr>0.0)])/(200*3000)       
+        dims=arr.shape
+        gas_holdup=float(len(numpy.where(arr>0.0)[0]))/(dims[1]*(dims[0]-2))
+
+        print "Overall concentration=",numpy.sum(arr[numpy.where(arr>0.0)])/(gas_holdup*dims[1]*(dims[0]-2))       
         pylab.figure(scale_counter)
         pylab.imshow(arr)
         pylab.colorbar()
         
-        pylab.figure(99)
         
-        cont=pylab.contour(arr,levels=c_levels,linestyles="dotted",colors=['k'],linewidths=[2])
[…]

### 2012-01-21 Text/introduction.tex
Added some average calculations.

@@
 \newcommand{\vol}{k_L\,a}
+\newcommand{\lbubble}{L_{\mathrm{bubble}}}
+\newcommand{\lunit}{L_{\mathrm{unit}}}
+\newcommand{\lslug}{L_{\mathrm{slug}}}
+\newcommand{\ububble}{U_{\mathrm{bubble}}}
+\newcommand{\uliq}{U_{\mathrm{liq}}}
+\newcommand{\ugas}{U_{\mathrm{gas}}}
+\newcommand{\cbubble}{C_{\mathrm{bubble}}}
 
@@
 \maketitle
+\begin{abstract}
+This work gives the thorough procedure of how to determine the volumetric mass transfer coefficient
+in the context of lattice Boltzmann simulations. The novelty of this work lies in the establishing
+a thorough procedure of how to measure the volumetric mass transfer coefficient in case of mass
+sources to be comparable of the representative unit cell, which accounts for the inhomogenous
+situation. By examining $5$ representative cases taken from microfluidics with the capillary number
+from $Ca=0.1$ to $Ca=1$ the following relationship was established {\color{red} Give main findings
+here}. The work is of use to people performing mass transfer numerical simulations.
+\end{abstract}
+
+\section{Introduction}
+The volumetric mass transfer coefficient is a very important characteristic for microchannels 
+design \cite{kreutzer-overview}. It allows to
+properly manufacture a microchannel with necessary properties to ensure that chemical
+reactions are performed in the best manner.
+
+The volumetric mass transfer coefficient correlations are represented as a function of the diffusion
+coefficient, slug and bubble lengths, and bubble velocity. For example, \citet{yue-mass} established
+experimental correlation for periodic bubble train as: 
+\begin{equation}
+\vol =\frac{2}{d_h} \Bigl(\frac{D
+\ububble}{\lbubble+\lslug}\Bigr)^{0.5}
+\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3},
+\end{equation}
+where $\vol$ is the volumetric mass transfer coefficient, $d_h$ is the hydrodynamic capillary
+diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
+$\ububble$ is the bubble velocity. This correlation is within $10\%$ accuracy for experimental
+results for the following range of
+parameters: bubble velocity $0.4\,\mathrm{m/s}<\ububble<2\,\mathrm{m/s}$, bubble length
+$1.4<\frac{\lbubble}{d_h}<6.3$, slug length $1<\frac{\lslug}{d_h}<3.2$,
+hydrodynamic diameter $d_h = 400 \mathrm{\mu m}$.
+
+Other correlations can be found in works of \citet{kreutzer-overview}
+and \citet{bercic-mass}. Among a variety of experimental works extensively covered
+\cite{yue-mass}, the numerical validations to the best author knowledge are sparse. One of the
+reasons is that the experimental correlations are established for continous system, i.e. one does
+not distinguish separate bubbles, but looks to the system as a whole measuring mass concentration
+in different places. There are some works as how to avoid this approach and perform numerical
+simulations for one unit cell. For example, \citet{vanbaten-circular} perform numerical simulations
+for one unit cell using periodic boundary conditions and measure the volumetric mass transfer
+coefficient as:
+\begin{equation}
+\label{main:simulation:equation}
+k_L a=\frac{\text{Flux}}{\cbubble-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell
+volume}},
+\end{equation}
+where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
+The concentration flux is calculated as the difference between overall
+average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$)
+at time
+$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
+simulations and correlations of \citet{bercic-mass} was good. However, the numerical model only
+accounts for circular capillaries and short contact times (the mass t), which indicate that the
+bubble film is not saturated with the mass concentration. As well, authors took the approximation of
+bubble shapes for small capillary numbers $Ca<0.01$ and then derived the hydrodynamics fields by
+imposing a free-slip condition on the bubble surface.
+
+This work aims at the establishing numerical procedures as to how properly obtain the volumetric
+mass transfer coefficient in the interesting range of capillary numbers, i.e. $0.1\leq Ca\leq1.0$.
+The comparison of volumetric mass transfer coefficient correlations with experimental correlations
+and establishing the Sherwood number as a function of other non-dimensional parameters is the goal
+of the future work.
+
+We chose this type of the problem due to different reasons:
+\begin{description}
+\item[I] The gas holdup, i.e. the ratio of volume occupied by bubble to unit cell volume, is
+significant. Therefore, one cannot assume that the mass source is a point source or one can have
+homogenous picture. Therefore, to establish the volumetric mass transfer coefficient one needs to
+mimic the continuos picture. One of the goals of this work is to establish certain criteria as how
+to simulate it numerically.
+\item[II] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
+the reference frame moving with
+the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
+numbers there is no vortex and stremalines go around the bubble. Thus, the problem is interesting
+because of really different hydrodynamic patterns depending on capillary number. Note that the flow
+patterns strongly depend on the number of parameters as the slug length, the thickness of the
+thickness and the existence of the vortex in front of the bubble. There are some available
+correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
+this work is to study mass transfer dependence on the number of parameters. 
+\end{description}
+
+The approach we want to use is the lattice Boltzmann method, a relatively new CFD
+competitor emerged during last $20$ years \cite{frisch,mcnamara,HJ,HSB}. During years the method
+was applied to simulate not only hydrodynamic problems \cite{yu}, but as well multiphase flows
+\cite{Shan-chen:extended,swift,gunstensen}, heat transfer
+\cite{yuan-thermal,zhang-thermal}, ferrofluids \cite{dellar-ferro,kuzmin-aniso}.
+
+The mass transfer problems in the lattice Boltzmann framework were mainly addressed in series of
+works of Dr. Ginzburg and co-authors
+\cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}. However, all these works
+are of general nature to simulate the advection-diffusion equation via the lattice Boltzmann
+framework. The manuscripts do not establish of how to obtain the volumetric mass transfer
+coefficients. The work of \citet{inamuro-scalar-boundary} simulates heat and mass transfers in the
+porous media. The work of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While
+two last works are focused at the mass transfer problems, both problems are of homogenuous nature
+and do not guide as to how to simulate the non-homogenous problems.
+
+The overall goal of this paper is to address the questions arised and to establish the numerical
+procedure suitable to measure the volumetric mass transfer coefficient. We will utilize the results
+of numerical simulations of flow
+obtained
+before \cite{kuzmin-binary2d}.
+
+The paper is organized as follows. The mass transfer coefficients and volumetric mass transfer
+coefficients are covered. The limiting cases from the continuos representation and their
+application to the present simulation are given. The mass transfer simulations benchmarks are
+presented. Finally, numerical simulations of hypotheses presented in this work and comparison
+between them are presented.
+
 \section{Mass transfer definitions}
-By the definition the mass transfer coefficient is the following:
+By the definition the mass transfer coefficient from the surface with the imposed constant
+concentration $\cbubble$ is the following:
 \beq
@@
 where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
-$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference $\Bigl[\frac{kg}{m^3}\Bigr]$.
-Therefore, $k_L$ has a dimension of velocity $\Bigl[\frac{m}{s}\Bigr]$.
+$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference between the surface and the medium
+$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of velocity
+$\Bigl[\frac{m}{s}\Bigr]$. Usually, the medium concentration is taken at the infinite distance
+from the bubble. However, in the case bubble, the medium concentration can be the average
+concentration in the domain, the flux averaged concentration at the outlet. Thus, one needs to
+establish a thorough definition of the volumetric mass transfer coefficient in the case of complex
+geometries and hydrodynamic patterns.
 
@@
 \subsection{Point mass sources}
-In what follows we will present three approaches to calculate the mass points mass transfer
+In what follows we will present three approaches to calculate point mass transfer
 coefficients:
@@
 moving and with the mass source. Then the concentration difference can be found as $\Delta C = C^* -
-C(t)$, where $C^*$ is the imposed concentration on the infinitesimal concentration source, $C(t)$ is
+C(t)$, where $C^*$ is the imposed point source concentration, $C(t)$ is
 the time depending average concentration. Therefore one can write the time dependent ODE for the
@@
 \beq
-C(t)= C^{*}(1-\exp(-k_L a t )), 
-\feq
-where $k_L a$ is the volumetric mass transfer coefficient.
-
+C(t)= C^{*}(1-\exp(-\vol t )), 
+\feq
+where $\vol$ is the volumetric mass transfer coefficient defined as:
+\beq
+\vol=k_L \frac{P}{V},
+\feq
+where $P$ is the source surface, $V$ is the unit cell volume.
 \item
@@
 \subsection{Numerical calculation}
+
+The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
+the same figure, one can see the proposed benchmark for the tracer. The
+physical
+picture for the proposed numerical benchmark is  related to classical experiments conducted by
+\citet{bercic-mass}. In their work authors studied gas-liquid mass transfer coefficient by
+injecting methane as the gas bubble and measuring the dissolved concentration of methane in water
+along the channel. This situation implies the periodic boundary conditions and steady-state motion
+of bubbles.
+
+The numerical  procedure of studying mass transfer is presented in the following steps:
+\begin{description}
+ \item[Flow field] The hydrodynamics for the bubble motion in the periodic domain is obtained
+according to the work \cite{kuzmin-binary2d}. The grid resolution is taken to insure grid
+independency of results.  
+ \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
+are conducted in the moving
+reference frame with the bubble. Then the bubble stands still and the flow is coming around the
+bubble. We impose a steady concentration of solutant on the surface of the bubble.
+\item[Mass transfer] One needs not only perform a Galilean transformation to the reference
+frame moving with the bubble but also to
+transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
+slug. 
+\end{description}
+
 In the numerical simulation it is not possible to simulate really long domains with the infinite
@@
 
+\section{Performing average approach}
+One can calculate the average domain concentration over the time. According to the definitions of
+the volumetric mass transfer coefficient one can obtain the following concentration depending on
+time, i.e. streamwise coordinate:
+\beqal
+&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{C^*}{C^*-C(t)}\\
+&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-C(t)}\\
+\feqal
+Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
+\ref{fig:aver:conc:different:capillaries}.
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca026.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca054.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca05.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca097.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}\\
+\caption{Volumetric mass transfer coefficient for different capillaries and scales. One can see the
+excellent agreement. \label{fig:aver:conc:different:capillaries}}
+\end{figure}
+One of interesting correlations for the mass transfer volumetric coefficient was presented by
+\citet{yue-mass}:
+\beqal
+&\vol=\frac{2}{d_h}\Bigl(\frac{D \ububble}{\lbubble+\lslug}\Bigr)^{0.5}
+\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^0.3\\
+&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D \varepsilon
+}{(\ububble+\ugas)\lbubble+\lslug}\Bigr)^{0.5}
+\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^0.3 \propto Pe^{-\frac{1}{2}}.
+\feqal
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/volumetric_mass_peclet.eps}
+\end{figure}
+
 \appendix

### 2012-01-21 Python/HydroAlexandra/hermes.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+mkdir -p `seq 3 3 90`
+
+for i in $(seq 3 3 90)
+do
+  cd $i
+  scp "shurik@hermes.westgrid.ca":/home/shurik/HydroAlexandra/$i/tmp/velocityx300000.dat .
+  scp "shurik@hermes.westgrid.ca":/home/shurik/HydroAlexandra/$i/tmp/velocityy300000.dat .
+  scp "shurik@hermes.westgrid.ca":/home/shurik/HydroAlexandra/$i/tmp/phase300000.dat .
+  cd ..
+
+  echo "Done with $i"
+done

### 2012-01-21 Python/UnitCells/copy_from_bugaboo.py

@@ -7,9 +7,9 @@ def copy_files():
     units=[1,4,6,8,10]
     scale=[1,2,4,8,10,20]
     scale_str=[str(x) for x in scale]
-    subprocess.call(['scp','jos_parallel.cpp','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'])
-    subprocess.call(['scp','govern.py','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'])
-    subprocess.call(['scp','binary.pbs','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'])
+    subprocess.call(['scp','jos_parallel.cpp','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'])
+    subprocess.call(['scp','govern.py','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'])
+    subprocess.call(['scp','binary.pbs','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'])
     for counter,dir_temp in enumerate(capillary_str):
         os.chdir(dir_temp)
         #subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
@@ -24,7 +24,7 @@ def copy_one_directory(dir_name):
     velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
     scales=[0.3,0.5,1,2,4,6,8,10,15,20]    
     scale_str=["03","05","1","2","4","6","8","10","15","20"]
-    os.chdir(dir_name)
+    os.chdir("Bugaboo/"+dir_name)
     flag=False
     counter=capillary_str.index(dir_name)
     for scale_counter,scale in enumerate(scales):
@@ -46,7 +46,7 @@ def copy_one_directory(dir_name):
         for unit in units:
             subprocess.call(['mkdir','-p',str(unit)])
             os.chdir(str(unit))            
-            subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_name+"/"+dir_name_scale+"/"+str(unit)+"/density*.dat","."])
+            subprocess.call(['scp','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'+dir_name+"/"+dir_name_scale+"/"+str(unit)+"/density*.dat","."])
             print "Done with ",unit
             os.chdir("..")
         os.chdir("..")

### 2012-01-21 Python/UnitCells/copy_to_checkers.py

@@ -3,18 +3,18 @@ import os
 import subprocess
 
 def copy_files():
-    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    capillary_str=[str(x) for x in [21,42,60,84]]
     units=[1,4,6,8,10]
     scale=[1,2,4,8,10,20]
     scale_str=[str(x) for x in scale]
-    subprocess.call(['scp','jos_parallel.cpp','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'])
-    subprocess.call(['scp','govern.py','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'])
-    subprocess.call(['scp','binary.pbs','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'])
+    subprocess.call(['scp','jos_parallel.cpp','shurik@checkers.westgrid.ca:/home/shurik/UnitCellsOther/'])
+    subprocess.call(['scp','govern.py','shurik@checkers.westgrid.ca:/home/shurik/UnitCellsOther/'])
+    subprocess.call(['scp','binary.pbs','shurik@checkers.westgrid.ca:/home/shurik/UnitCellsOther/'])
     for counter,dir_temp in enumerate(capillary_str):
         os.chdir(dir_temp)
-        #subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
-        #subprocess.call(['scp','velx0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
-        #subprocess.call(['scp','vely0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
+        subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCellsOther/'+dir_temp+"/"])
+        subprocess.call(['scp','velx0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCellsOther/'+dir_temp+"/"])
+        subprocess.call(['scp','vely0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCellsOther/'+dir_temp+"/"])
         print "Done with ",dir_temp 
         os.chdir("..")
 

### 2012-01-21 Python/UnitCells/jos_parallel.cpp

@@ -309,7 +309,18 @@ void update_inlet_outlet()
 				f2[counter_inlet*NPOP+k]=f2[(counter_inlet+NX)*NPOP+k];
 			}
 		}   	
-	
+        if (mpi_size==1)
+        {
+		    for(int iX=1;iX<NX-1;iX++)
+			{
+				int counter_outlet=(NY-1)*NX+iX;
+				for(int k=0;k<NPOP;k++)
+				{
+					rho[counter_outlet]=rho[counter_outlet-NX];
+					f2[counter_outlet*NPOP+k]=f2[(counter_outlet-NX)*NPOP+k];
+				}
+			}    
+        }
 		return;
 	}
 
@@ -578,11 +589,10 @@ void stream_boundaries()
 	}
 	
 	//special treatment of BB nodes
-	f[NX*(NY-1)*NPOP+8]=f2[NX*(NY-1)*NPOP+6];
-	f[NX*(NY-1)*NPOP+(NX-1)*NPOP+7]=f2[NX*(NY-1)*NPOP+(NX-1)*NPOP+5];
-	f[5]=f2[7];
-	f[(NX-1)*NPOP+6]=f2[(NX-1)*NPOP+8];
-	
+	f[NX*(NY-1)*NPOP+NPOP+8]=f2[NX*(NY-1)*NPOP+NPOP+6];
+	f[NX*(NY-1)*NPOP+(NX-2)*NPOP+7]=f2[NX*(NY-1)*NPOP+(NX-2)*NPOP+5];
+	f[NPOP+5]=f2[NPOP+7];
+	f[(NX-2)*NPOP+6]=f2[(NX-2)*NPOP+8];
 }
 
 void stream_column(int coor_y,int coor_bottom,int coor_top)

### 2012-01-21 Python/peclet.py

@@ -4,6 +4,8 @@ import os
 import subprocess
 import math
 import pylab
+import scipy
+import scipy.optimize
 
 def run_simulations():
     capillary_str=[str(x) for x in [9,21,42,60,84]]
@@ -167,6 +169,114 @@ def check_particular_contours(dir_name,factor,subtract):
     pylab.ylabel(r'''$y$''',fontsize=30)    
     pylab.title(r'''$Ca='''+str(capillary)+'''$''',fontsize=30)
     pylab.savefig("contourlines_scale_ca"+str(capillary)[0:1]+str(capillary)[3:]+".eps",format="EPS",dpi=300)
+
+def check_average_concentration(dir_name,factor,subtract):
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    capillaries=[0.097,0.254,0.526,0.750,1.040]
+    velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
+
+    scale=[2,4,8,10,20,40]
+    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    os.chdir("ScalingPeclet/"+dir_name)
+    
+    geometry=numpy.loadtxt("geometry.dat")
+    gas_holdup=len(numpy.where(geometry>0)[0])/(3000.0*200.0)
+    counter=capillary_str.index(dir_name) 
+    capillary=capillaries[counter]
+   
+    #styles=["k+","ko","ks","k^","kv","kd"]    
+    
+    styles=['k-','k--','k-.','k:','k.','k,']    
+    
+    exam_points=[]
+    legs=[]
+    for scale_counter in range(0,len(scale_str)-subtract):
+        os.chdir(scale_str[scale_counter])
+        exam_point=20*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter]
+        #name=str(20000*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter])
+        #name="density"+"0"*(7-len(name))+name+".dat"        
+        #print "Filename=",name
+        #print "Scale=",scale_str[scale_counter]        
+        #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+        #arr=numpy.loadtxt(name)
+        #dims=arr.shape
+        #gas_holdup=float(len(numpy.where(arr>0.0)[0]))/(dims[1]*(dims[0]-2))
+
[…]

### 2012-01-21 Python/streamlines.py

@@ -469,6 +469,85 @@ def produce_one_mass_image():
     pylab.imshow(mass)
     pylab.colorbar()
 
+def produce_new_image():
+    from PyNGL import Ngl    
+    file_dir="/home/shurik/Documents/Projects/binary_mass_transfer/Python/HydroAlexandra/9/"    
+    phase=numpy.loadtxt(file_dir+"phase300000.dat")
+    velx=numpy.loadtxt(file_dir+"velocityx300000.dat")
+    vely=numpy.loadtxt(file_dir+"velocityy300000.dat")
+    pylab.figure()    
+    pylab.imshow(phase)
+    pylab.figure()
+    pylab.imshow(velx)
+    pylab.figure()
+    pylab.imshow(vely)
+    dims=phase.shape
+    center=phase[dims[0]/2,:]
+   
+    z1 = numpy.min(numpy.where(center < 0.0))
+    z2 = numpy.max(numpy.where(center < 0.0))
+    if z1==0:
+        z2=numpy.min(numpy.where(center>0.0))+dims[1]
+        z1=numpy.max(numpy.where(center>0.0))
+    print z1,z2
+    print "Bubble length=",(z2-z1)/200.0
+    print "Slug length=",15.0-(z2-z1)/200.0
+    print "Liquid_velocity",numpy.sum(velx[1:-1,((z1+z2+dims[1])/2)%dims[1]])/(dims[0]-2)
+    print "Bubble velocity",velx[dims[0]/2,z2%dims[1]]        
+    velx=velx-velx[dims[0]/2,z2%dims[1]]    
+    #print "Gas holdup",float(len(numpy.where(array['phi']<0)[0]))/(dims[1]*(dims[0]-2))
+    #prof=phase[:,((z1+z2)/2)%dims[1]]
+    #widths.append(Get_Zero(prof))     
+    #velocities.append()
+
+    wks_type = "eps"
+    wks = Ngl.open_wks(wks_type,"new_force")
+    resources = Ngl.Resources()
+    
+        
+    #resources.tiMainFont    = "Times-Roman"
+    #resources.tiMainOn=True
+    #resources.tiMainString="Ca=0.22 "
+           
+    #resources.tiXAxisString = "streamlines"
+    resources.vpHeightF = 0.25 # Define height, width, and location of plot.
+    resources.vpWidthF  = 3*0.25
+    #resources.wkPaperSize="A5"
+    #resources.nglFrame = False
[…]

### 2012-01-24 Text/introduction.tex
Studying units. Difficult to explain.

@@
 
+\section{Real calculations}
+This section examines different cells for the capillary $Ca=0.097$. The coefficient is
+non-dimensionalized in the following manner $\vol \frac{\lunit}{\ugas+\uliq}$. Therefore, we
+examined the average concentrations in different units and for different scalings. Therefore the
+average concentration between two different cells have to be of the following value:
+\beqal
+&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
+&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
+k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
+\feqal
+One can see that this number is different in comparison with the number used for periodic boundary
+conditions. Thus, the domain transformation from time domain to the coordinate domain is not
+straightforward and require other definitions. For example by definition we took $C_1$ and $C_2$ to
+be average concentrations over different units. One can see Fig. \ref{fig:unit:8:scale:10} for
+average coefficients and corresponding volumetric mass transfer coefficients.
+\subsection{4 units}
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale10.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale15.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
+\caption{Average concentrations and volumetric coefficients for $4$ units.
+\label{fig:unit:4}}
+\end{figure}
+
+\subsection{8 units} 
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale10.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale15.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale15.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale20.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale20.eps}\\
+\caption{Average concentrations and volumetric coefficients for $8$ units.
+\label{fig:unit:8}}
+\end{figure}
+
+\subsection{10 units} 
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale10.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale15.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale15.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale20.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale20.eps}\\
+\caption{Average concentrations and volumetric coefficients for $8$ units.
+\label{fig:unit:10}}
+\end{figure}
+
 \appendix

### 2012-01-24 Python/JosScalingPeclet/copy_to_bugaboo.py

@@ -1,0 +1,50 @@
+import numpy
+import os
+import subprocess
+
+def run_simulations():
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    scale=[2,4,8,10,15,20,40]
+    scale_str=[str(x) for x in scale]
+    
+    subprocess.call(['scp',"open_symmetry.cpp",'shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/']) #+scale_str[scale_counter]+"/density"+'0'*(7-len(name))+name+".dat","."])
+    subprocess.call(['scp',"govern.py",'shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'])
+    subprocess.call(['scp',"binary.pbs",'shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'])
+    
+    for counter,dir_temp in enumerate(capillary_str):
+        os.chdir(dir_temp)
+        print os.getcwd()
+        #for scale_counter in range(0,len(scale_str)-counter):
+            #subprocess.call(['mkdir','-p',scale_str[scale]])
+            #os.chdir(scale_str[scale_counter])
+            #name=str(20000*scale[len(scale_str)-counter-1]/scale[scale_counter])
+            #print name
+            #subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/ScalingPeclet/'+dir_temp+"/"+scale_str[scale]+"/concentration.dat","."])
+        subprocess.call(['scp',"geometry.dat",'shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'+dir_temp+"/"]) #+scale_str[scale_counter]+"/density"+'0'*(7-len(name))+name+".dat","."])
+        subprocess.call(['scp',"velx0200000.dat",'shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'+dir_temp+"/"])
+        subprocess.call(['scp',"vely0200000.dat",'shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'+dir_temp+"/"])
+        os.chdir("..")
+        
+
+def copy_files(dir_name,factor,subtract):
+    scale=[2,4,8,10,20,40]
+    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    os.chdir(dir_name)
[…]

### 2012-01-24 Python/JosScalingPeclet/open_symmetry.cpp

@@ -283,20 +283,17 @@ void update_bounce_back()
 	for(int iY=0;iY<NY;iY++)
 	{
 		int counter=iY*NX;
-		int counter_top=((iY+1+NY)%NY)*NX;
-		int counter_bottom=((iY-1+NY)%NY)*NX;
-
 
 		f2[counter*NPOP+1]=f2[(counter+1)*NPOP+3];
-		f2[counter*NPOP+5]=f2[(counter_top+1)*NPOP+7];
-		f2[counter*NPOP+8]=f2[(counter_bottom+1)*NPOP+6];
+		f2[counter*NPOP+5]=f2[(counter+1)*NPOP+6];
+		f2[counter*NPOP+8]=f2[(counter+1)*NPOP+7];
 
 		f2[(counter+NX-1)*NPOP+3]=f2[(counter+NX-2)*NPOP+1];
-		f2[(counter+NX-1)*NPOP+6]=f2[(counter_top+NX-2)*NPOP+8];
-		f2[(counter+NX-1)*NPOP+7]=f2[(counter_bottom+NX-2)*NPOP+5];
+		f2[(counter+NX-1)*NPOP+6]=f2[(counter+NX-2)*NPOP+5];
+		f2[(counter+NX-1)*NPOP+7]=f2[(counter+NX-2)*NPOP+8];
 
-		rho[counter]=conc_wall;
-		rho[counter+NX-1]=conc_wall;
+		rho[counter]=rho[counter+1];
+		rho[counter+NX-1]=rho[counter+NX-2];
 		ux[counter]=0.0;
 		ux[counter+NX-1]=0.0;
 		uy[counter]=0.0;
@@ -355,7 +352,7 @@ void initialize_geometry()
 			uy[counter]=0.0;
 		}
 		else
-			rho[counter]=1.0;
+			rho[counter]=0.0;
 	}
 	
 	//Finding bulk nodes
@@ -571,6 +568,11 @@ int main(int argc, char* argv[])
 		
 		if (counter%NSIGNAL==0)
 		{
+			if (rho[NX/2]!=rho[NX/2])
+			{
+				std::cout<<"The simulation is unstable!\n";
+				return -1;
+			}
 			std::cout<<"Counter="<<counter<<"\n";
 		    calculate_mass_transfer(counter);
 		}

### 2012-01-24 Python/UnitCells/copy_from_bugaboo_9.py

@@ -1,0 +1,64 @@
+import numpy
+import os
+import subprocess
+
+def copy_files():
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    units=[1,4,6,8,10]
+    scale=[1,2,4,8,10,20]
+    scale_str=[str(x) for x in scale]
+    subprocess.call(['scp','jos_parallel.cpp','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'])
+    subprocess.call(['scp','govern.py','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'])
+    subprocess.call(['scp','binary.pbs','shurik@bugaboo.westgrid.ca:/home/shurik/UnitCells/'])
+    for counter,dir_temp in enumerate(capillary_str):
+        os.chdir(dir_temp)
+        #subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
+        #subprocess.call(['scp','velx0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
+        #subprocess.call(['scp','vely0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/UnitCells/'+dir_temp+"/"])
+        print "Done with ",dir_temp 
+        os.chdir("..")
+
+def copy_one_directory(dir_name):
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    units=[4,6,8,10]
+    velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
+    scales=[0.3,0.5,1,2,4,6,8,10,15,20]    
+    scale_str=["03","05","1","2","4","6","8","10","15","20"]
+    os.chdir("Bugaboo/"+dir_name)
+    flag=False
+    counter=capillary_str.index(dir_name)
+    for scale_counter,scale in enumerate(scales):
+        if velocities[counter]*scale>0.12:
+            scale3=scales[scale_counter-1]
+            scale2=scales[scale_counter-2]
+            scale1=scales[scale_counter-3]
+            flag=True 
+            break
+    if not flag:
+        scale1=scales[-3]
+        scale2=scales[-2]
+        scale3=scales[-1] 
+    print scale1,scale2,scale3,velocities[counter] 
+    for scale in [scale1,scale2,scale3]:
+        dir_name_scale=scale_str[scales.index(scale)]
[…]

### 2012-01-26 Text/introduction.tex
Established the truth about mass transfer coefficient. Need one more simulation.

@@
 &\vol=\frac{2}{d_h}\Bigl(\frac{D \ububble}{\lbubble+\lslug}\Bigr)^{0.5}
-\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^0.3\\
-&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D \varepsilon
-}{(\ububble+\ugas)\lbubble+\lslug}\Bigr)^{0.5}
-\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^0.3 \propto Pe^{-\frac{1}{2}}.
+\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3}\\
+&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D 
+}{\lunit (\ububble+\ugas)} \frac{\ububble}{\ugas+\uliq}\Bigr)^{0.5}
+\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3} \propto Pe^{-\frac{1}{2}}\\
+&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D 
+}{\lunit (\ububble+\ugas)} \frac{\ububble}{\ugas+\uliq}\Bigr)^{0.5}
+\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3} \propto Pe^{-\frac{1}{2}}
 \feqal
@@
 straightforward and require other definitions. For example by definition we took $C_1$ and $C_2$ to
-be average concentrations over different units. One can see Fig. \ref{fig:unit:8:scale:10} for
+be average concentrations over different units. One can see Fig. \ref{fig:unit:8} for
 average coefficients and corresponding volumetric mass transfer coefficients.
@@
 \end{figure}
+The more interesting picture is actually moving window average which is calculated as:
+\beq
+\label{moving:average}
+\vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
+-t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
+\feq
+One can see those moving averages in Fig. \ref{window4}.
+\begin{figure}[htb!]
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale10.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale15.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale20.eps}\\
+\caption{Moving averages defined in Eq. \ref{moving:average} for 4 units
+\label{fig:moving:average:window4}}
+\end{figure}
+
+\subsection{6 units} 
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale10.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale15.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale15.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale20.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale20.eps}\\
+\caption{Average concentrations and volumetric coefficients for $8$ units.
+\label{fig:unit:10}}
+\end{figure}
+
+Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window6}.
+\begin{figure}[htb!]
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale10.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale15.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale20.eps}\\
+\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
+\label{fig:moving:average:window6}}
+\end{figure}
 
@@
 
+Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window8}.
+\begin{figure}[htb!]
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale10.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale15.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale20.eps}\\
+\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
+\label{fig:moving:average:window8}}
+\end{figure}
+
 \subsection{10 units} 
@@
 \label{fig:unit:10}}
+\end{figure}
+
+Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window10}.
+\begin{figure}[htb!]
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale10.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale15.eps}\\
+\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale20.eps}\\
+\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
+\label{fig:moving:average:window10}}
+\end{figure}
+
+\section{Open boundary conditions}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0097.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0254.eps}
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0254.eps}\\
+\caption{Open boundary conditions. \label{fig:open:boundary:jos}}
+\end{figure}
+
+\section{Symmetric boundary conditions}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0097.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0254.eps}
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0254.eps}\\
+\caption{Symmetric boundary conditions. \label{fig:open:boundary:sym}}
 \end{figure}

### 2012-01-26 Python/JosScalingPeclet/copy_from_bugaboo.py

@@ -1,0 +1,21 @@
+import numpy
+import os
+import subprocess
+
+
+def copy_files(dir_name,scales):
+    os.chdir(dir_name)
+    for scale in scales:
+        subprocess.call(['mkdir','-p',scale+"Symmetry"])
+        os.chdir(scale+"Symmetry")
+        subprocess.call(['scp','shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'+dir_name+"/"+scale+"/concentration.dat","."])
+        #subprocess.call(['scp','shurik@bugaboo.westgrid.ca:/home/shurik/SymmetryScalingPeclet/'+dir_name+"/"+scale+"/density*.dat","."])
+        os.chdir("..")
+    os.chdir("..")
+
+
+if __name__=="__main__":
+    copy_files("9",["1","2","4","6","10","15","20","40"])
+    copy_files("21",["15","20"])
+
+    #copy_files("84",10,5)

### 2012-01-26 Python/JosScalingPeclet/copy_from_checkers.py

@@ -1,0 +1,21 @@
+import numpy
+import os
+import subprocess
+
+
+def copy_files(dir_name,scales):
+    os.chdir(dir_name)
+    for scale in scales:
+        subprocess.call(['mkdir','-p',scale])
+        os.chdir(scale)
+        subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/JosScalingPeclet/'+dir_name+"/"+scale+"/concentration.dat","."])
+        subprocess.call(['scp','shurik@checkers.westgrid.ca:/home/shurik/JosScalingPeclet/'+dir_name+"/"+scale+"/density*.dat","."])
+        os.chdir("..")
+    os.chdir("..")
+
+
+if __name__=="__main__":
+    copy_files("9",["2","4","6","8","10","15","20","40"])
+    copy_files("21",["15","20"])
+
+    #copy_files("84",10,5)

### 2012-01-26 Python/peclet.py

@@ -176,7 +176,8 @@ def check_average_concentration(dir_name,factor,subtract):
     velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
 
     scale=[2,4,8,10,20,40]
-    scale_str=[str(x) for x in [2,4,8,10,20,40]]
+    #scale=[8,10,20,40]
+    scale_str=[str(x) for x in scale]
     os.chdir("ScalingPeclet/"+dir_name)
     
     geometry=numpy.loadtxt("geometry.dat")
@@ -192,7 +193,8 @@ def check_average_concentration(dir_name,factor,subtract):
     legs=[]
     for scale_counter in range(0,len(scale_str)-subtract):
         os.chdir(scale_str[scale_counter])
-        exam_point=20*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter]
+        #exam_point=int(20*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter])
+        exam_point=int(24.0/(velocities[counter]*scale[scale_counter]))        
         #name=str(20000*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter])
         #name="density"+"0"*(7-len(name))+name+".dat"        
         #print "Filename=",name
@@ -211,7 +213,7 @@ def check_average_concentration(dir_name,factor,subtract):
         pylab.figure(1)
         pylab.plot(velocities[counter]*scale[scale_counter]*concentration[1:,0],aver_concentration,styles[scale_counter])
         pylab.figure(2)
-        pylab.plot(velocities[counter]*scale[scale_counter]*concentration[1:,0],3000.0/(velocities[counter]*scale[scale_counter]*concentration[1:,0])*numpy.log(1.0/(1.0-aver_concentration)),styles[scale_counter],linewidth=2)                
+        pylab.plot(velocities[counter]*scale[scale_counter]*concentration[1:,0]/3000.0,3000.0/(velocities[counter]*scale[scale_counter]*concentration[1:,0])*numpy.log(1.0/(1.0-aver_concentration)),styles[scale_counter],linewidth=2)                
         #pylab.figure(99,figsize=(12,3))
[…]

### 2012-01-26 Text/introduction.tex
Started working on the manuscript.

@@
 \newcommand{\ugas}{U_{\mathrm{gas}}}
+\newcommand{\uoutlet}{U_{\mathrm{outlet}}}
 \newcommand{\cbubble}{C_{\mathrm{bubble}}}
+\newcommand{\cinlet}{C_{\mathrm{inlet}}}
+\newcommand{\coutlet}{C_{\mathrm{outlet}}}
 
@@
 \begin{abstract}
-This work gives the thorough procedure of how to determine the volumetric mass transfer coefficient
+This work presents a thorough procedure of how to determine the volumetric mass transfer
+coefficient
 in the context of lattice Boltzmann simulations. The novelty of this work lies in the establishing
@@
 properly manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner.
-
-The volumetric mass transfer coefficient correlations are represented as a function of the diffusion
-coefficient, slug and bubble lengths, and bubble velocity. For example, \citet{yue-mass} established
-experimental correlation for periodic bubble train as: 
+reactions are performed in the best manner. Many chemical microchannel configurations
+\cite{kreutzer-pressure-drop}  The flow for microchannels we focus on is the bubble train
+motion, where bubbles organized in a train are traveling through the liquid media. This
+configuration is interesting due to several reasons: hydrodynamic velocity patterns are completely
+different for different capillary numbers, the bubble occupies the significant part of the unit cell
+and the flow can be assumed periodic.
+
+For the bubble train the volumetric mass transfer coefficient correlations are represented as a
+function of the diffusion coefficient, slug and bubble lengths, and bubble velocity. For example,
+\citet{yue-mass} established an experimental correlation for a bubble train as: 
 \begin{equation}
@@
 and \citet{bercic-mass}. Among a variety of experimental works extensively covered
-\cite{yue-mass}, the numerical validations to the best author knowledge are sparse. One of the
+\cite{yue-mass}, the numerical validations to the best authors' knowledge are sparse. One of the
 reasons is that the experimental correlations are established for continous system, i.e. one does
 not distinguish separate bubbles, but looks to the system as a whole measuring mass concentration
-in different places. There are some works as how to avoid this approach and perform numerical
-simulations for one unit cell. For example, \citet{vanbaten-circular} perform numerical simulations
-for one unit cell using periodic boundary conditions and measure the volumetric mass transfer
-coefficient as:
+in different places. Thus, numerical simulations require a significant computational
+resources to be able to simulate enough number of the unit cells to mimic the continuous picture.
+There are some works as how to avoid large scale numerical simulations by performing numerical
+simulations for one unit cell. For example, \citet{vanbaten-circular} perform numerical
+simulations for one unit cell using periodic boundary conditions and measure the volumetric mass
+transfer coefficient as:
 \begin{equation}
 \label{main:simulation:equation}
-k_L a=\frac{\text{Flux}}{\cbubble-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell
-volume}},
-\end{equation}
-where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
+k_L a=\frac{\mathrm{Flux}}{\cbubble-\coutlet} \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\
+cell\ volume}},
+\end{equation}
+where $\coutlet=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$. 
 The concentration flux is calculated as the difference between overall
-average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$)
+average concentration in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$)
 at time
-$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
+$t_1$ and at time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
 simulations and correlations of \citet{bercic-mass} was good. However, the numerical model only
-accounts for circular capillaries and short contact times (the mass t), which indicate that the
-bubble film is not saturated with the mass concentration. As well, authors took the approximation of
-bubble shapes for small capillary numbers $Ca<0.01$ and then derived the hydrodynamics fields by
-imposing a free-slip condition on the bubble surface.
+accounts for circular capillaries and short contact times when the
+bubble film is not saturated with tracer. As well, authors took the
+approximation of bubble shapes for small capillary numbers $Ca<0.01$ and then derived the
+hydrodynamics fields by imposing a free-slip condition at the bubble surface. {\color{red} Give
+another numerical work by Kreutzer.}
 
 This work aims at the establishing numerical procedures as to how properly obtain the volumetric
-mass transfer coefficient in the interesting range of capillary numbers, i.e. $0.1\leq Ca\leq1.0$.
-The comparison of volumetric mass transfer coefficient correlations with experimental correlations
-and establishing the Sherwood number as a function of other non-dimensional parameters is the goal
-of the future work.
-
-We chose this type of the problem due to different reasons:
+mass transfer coefficient in the range of capillary number $0.1\leq Ca\leq 1.0$, where the
+hydrodynamic velocity pattern changes. Different boundary conditions, i.e. the periodic boundary
+conditions, open boundaries conditions will be examined to determine the volumetric mass transfer
+coefficient. As well, large scale simulations are performed, which simulate from 4 to 10 unit
+cells.
+
+The comparison of volumetric mass transfer coefficient
+correlations with experimental correlations and establishing the Sherwood number as a function of
+other non-dimensional parameters is the goal of the future work. However, as an example we will
+show that one of the most recent correlations for the volumetric mass transfer coefficient by
+\citet{yue-mass} resembles current simulations.
+
+We chose to simulate mass transfer of the bubble train due to different reasons:
 \begin{description}
 \item[I] The gas holdup, i.e. the ratio of volume occupied by bubble to unit cell volume, is
-significant. Therefore, one cannot assume that the mass source is a point source or one can have
-homogenous picture. Therefore, to establish the volumetric mass transfer coefficient one needs to
-mimic the continuos picture. One of the goals of this work is to establish certain criteria as how
-to simulate it numerically.
+non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
+to the homogenous advection-diffusion equation with the mass source.  Therefore, there is a logical
+mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
+all velocity pattern details, on the other hand one needs to mimic the continous picture which is
+seen in experiments. One of the goals of this work is to establish certain criteria as how to
+simulate such problems numerically with the help of the lattice Boltzmann method.
 \item[II] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
@@
 the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
-numbers there is no vortex and stremalines go around the bubble. Thus, the problem is interesting
-because of really different hydrodynamic patterns depending on capillary number. Note that the flow
-patterns strongly depend on the number of parameters as the slug length, the thickness of the
-thickness and the existence of the vortex in front of the bubble. There are some available
-correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
-this work is to study mass transfer dependence on the number of parameters. 
+numbers there is no vortex and stremalines go around the bubble {\color{red} Give two pictures
+with corresponding streamlines}. Thus, the problem is interesting because of different
+hydrodynamic patterns depending on the capillary number which governs a number of experimental
+parameters as the slug length, the film thickness and the existence of the vortex in front of the
+bubble. There are some available
+correlations in literature \cite{bercic-mass,kreutzer-overview}. One of the particular goal of
+this work is to study mass transfer dependence on the completely different velocity patterns
+depending on the capillary number $Ca$. 
 \end{description}
 
-The approach we want to use is the lattice Boltzmann method, a relatively new CFD
-competitor emerged during last $20$ years \cite{frisch,mcnamara,HJ,HSB}. During years the method
-was applied to simulate not only hydrodynamic problems \cite{yu}, but as well multiphase flows
-\cite{Shan-chen:extended,swift,gunstensen}, heat transfer
+The numerical approach we take is the lattice Boltzmann method, a relatively new CFD
+competitor emerged during last $20$ years \cite{frisch,mcnamara,HJ,HSB}. During years the
+method was applied to simulate not only hydrodynamic problems \cite{yu}, but as well multiphase
+flows \cite{Shan-chen:extended,swift,gunstensen}, heat transfer
 \cite{yuan-thermal,zhang-thermal}, ferrofluids \cite{dellar-ferro,kuzmin-aniso}.
@@
 are of general nature to simulate the advection-diffusion equation via the lattice Boltzmann
-framework. The manuscripts do not establish of how to obtain the volumetric mass transfer
-coefficients. The work of \citet{inamuro-scalar-boundary} simulates heat and mass transfers in the
-porous media. The work of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While
-two last works are focused at the mass transfer problems, both problems are of homogenuous nature
-and do not guide as to how to simulate the non-homogenous problems.
+framework. In comparison, this work aims to establish the procedure of how to obtain the
+volumetric mass transfer coefficients for bubble train flow. One should mention the work of
+\citet{inamuro-scalar-boundary} simulates heat and mass transfers in the porous media and the work
+of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While two last works are focused
+at the particular mass transfer problems, both problems are of homogenuous nature and do not
+guide as how to simulate the non-homogenous problems.
 
 The overall goal of this paper is to address the questions arised and to establish the numerical
-procedure suitable to measure the volumetric mass transfer coefficient. We will utilize the results
-of numerical simulations of flow
+procedure suitable to measure the volumetric mass transfer coefficient in the context of the
+lattice Boltzmann method. We will utilize the results of numerical simulations of bubble flow
 obtained
-before \cite{kuzmin-binary2d}.
+before \cite{kuzmin-binary2d,kuzmin-binary3d}.
 
 The paper is organized as follows. The mass transfer coefficients and volumetric mass transfer
-coefficients are covered. The limiting cases from the continuos representation and their
-application to the present simulation are given. The mass transfer simulations benchmarks are
-presented. Finally, numerical simulations of hypotheses presented in this work and comparison
-between them are presented.
+coefficients definitions are covered. The limiting cases from the continuos representation and their
+application to present simulations are given. The mass transfer simulations benchmarks are
+presented. Finally, numerical simulations of different boundary conditions and large scale
+simulations and comparison between them are presented.
 
@@
 $\Bigl[\frac{m}{s}\Bigr]$. Usually, the medium concentration is taken at the infinite distance
-from the bubble. However, in the case bubble, the medium concentration can be the average
-concentration in the domain, the flux averaged concentration at the outlet. Thus, one needs to
-establish a thorough definition of the volumetric mass transfer coefficient in the case of complex
-geometries and hydrodynamic patterns.
+from the bubble. However, in the case of complicated geometries and inhomogenuous concentrations, 
+the medium concentration can be the average concentration in the domain, the flux averaged
+concentration at the outlet. Thus, one needs to establish a thorough definition of the volumetric
+mass transfer coefficient in the case of complex geometries and hydrodynamic velocity patterns.
 

### 2012-01-26 Python/IncreasingDiffusion/govern.py

@@ -1,0 +1,105 @@
+#import numpy
+import os
+import subprocess
+def modify_file(scale_str,unit_str,scale_diff_str):
+    f=open("binary.pbs","r+")
+    f2=open("binary_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE1",scale_str)
+            line=line.replace("TOCHANGE2",unit_str)
+            line=line.replace("TOCHANGE3",unit_str)
+            line=line.replace("TOCHANGE4",scale_diff_str)
+        f2.write(line)
+            
+    f.close()
+    f2.close()
+
+def modify_periodic_file(scale_str,unit_str,scale_diff_str):
+    f=open("binary_periodic.pbs","r+")
+    f2=open("binary_periodic_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE1",scale_str)
+            line=line.replace("TOCHANGE2",unit_str)
+            line=line.replace("TOCHANGE3",unit_str)
+            line=line.replace("TOCHANGE4",scale_diff_str)
+        f2.write(line)
+            
+    f.close()
+    f2.close()
+
+def run_simulations(dir_name):
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    units=[4,6,8]
+    velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
+    scales=[0.3,0.5,1,2,4,6,8,10,15,20]    
+    scale_str=["03","05","1","2","4","6","8","10","15","20"]
+    scales_diff=[2,5,10,20,40]
+    counter=capillary_str.index(dir_name)
+    
+    #for counter,dir_temp in enumerate(capillary_str):
+    subprocess.call(['cp','main.out',dir_name+"/"])
+    subprocess.call(['cp','main_diffusion.out',dir_name+"/"])
+    subprocess.call(['cp','binary.pbs',dir_name+"/"])
+    subprocess.call(['cp','binary_periodic.pbs',dir_name+"/"])
+    os.chdir(dir_name)
+    
+    flag=False
+    for scale_counter,scale in enumerate(scales):
+        if velocities[counter]*scale>0.12:
+            scale3=scales[scale_counter-1]
+            scale2=scales[scale_counter-2]
+            scale1=scales[scale_counter-3]
+            flag=True 
+            break
+    if not flag:
+        scale1=scales[-3]
[…]

### 2012-01-26 Python/IncreasingDiffusion/mass_periodic.cpp

@@ -1,0 +1,610 @@
+//Simple mass transfer
+
+
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+#include <limits>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Overall scaling parameter
+double scale_velocity=1.0;
+double scale_diffusion=1.0;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=1000000;
+int NOUTPUT=20000;
+int NSIGNAL=1000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_inlet=0.0;
+double conc_bubble=1.0;
+double conc_wall=0.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
[…]

### 2012-01-27 Text/introduction.tex
Minor changes in text

@@
 where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
-$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference between the surface and the medium
+$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference between the surface and the surrounding medium
 $\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of velocity
-$\Bigl[\frac{m}{s}\Bigr]$. Usually, the medium concentration is taken at the infinite distance
-from the bubble. However, in the case of complicated geometries and inhomogenuous concentrations, 
+$\Bigl[\frac{m}{s}\Bigr]$. Usually, the surrounding medium concentration is taken at the infinite distance
+from the bubble. However, in the case of complicated geometries and non-homogeneous concentrations, 
 the medium concentration can be the average concentration in the domain, the flux averaged
-concentration at the outlet. Thus, one needs to establish a thorough definition of the volumetric
-mass transfer coefficient in the case of complex geometries and hydrodynamic velocity patterns.
+concentration at the inlet or outlet. Thus, one needs to establish a thorough definition of the volumetric
+mass transfer coefficient in the case of complex geometries and non-trivial hydrodynamic velocity patterns.
 
 There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
-theoretical definitions of the mass transfer in case of the point sources.
+theoretical definitions of the mass transfer in case of point mass sources.
 \subsection{Point mass sources}
@@
 \item
-Let us look at the infinitisemal small domain of the volume $A \Delta x$ in a steady-state, not
-moving and with the mass source. Then the concentration difference can be found as $\Delta C = C^* -
+Let us look at the infinitesimal small domain of the volume $A \Delta x$ not
+moving and with the point mass source. Then the concentration difference can be found as $\Delta C = C^* -
 C(t)$, where $C^*$ is the imposed point source concentration, $C(t)$ is
-the time depending average concentration. Therefore one can write the time dependent ODE for the
+the time dependent average concentration. Therefore one can write the time dependent ODE for the
 average concentration in the domain:
@@
 with the initial condition $C(0)=0$
-The solution in time becomes as follows:
+The solution can be found by solving ODE:
 \beq
@@
 
-The mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
+If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
 mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
-source is a point source with the effective perimeter P. The accumulated mass should be proportional
+source is a point source with the effective perimeter (area) $P$. The accumulated mass should be proportional
 to the mass transfer coefficient:

### 2012-01-27 Python/DecreasingDiffusion/copy_to_checkers.py

@@ -18,9 +18,11 @@ def copy_files(dir_name):
     os.chdir(dir_name)
     #for counter,dir_temp in enumerate(capillary_str):
     #    os.chdir(dir_temp)
-    subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/DecreasingDiffusion/'+dir_name+"/"])
-    subprocess.call(['scp','velx0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/DecreasingDiffusion/'+dir_name+"/"])
-    subprocess.call(['scp','vely0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/DecreasingDiffusion/'+dir_name+"/"])
+    
+    #subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/DecreasingDiffusion/'+dir_name+"/"])
+    #subprocess.call(['scp','velx0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/DecreasingDiffusion/'+dir_name+"/"])
+    #subprocess.call(['scp','vely0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/DecreasingDiffusion/'+dir_name+"/"])
+    
     print "Done with ",dir_name 
     os.chdir("..")
 

### 2012-01-27 Python/DecreasingDiffusion/govern.py

@@ -1,4 +1,4 @@
-import numpy
+#import numpy
 import os
 import subprocess
 def modify_file(scale_str,unit_str,scale_diff_str):
@@ -31,16 +31,19 @@ def modify_periodic_file(scale_str,unit_str,scale_diff_str):
 
 def run_simulations(dir_name):
     capillary_str=[str(x) for x in [9,21,42,60,84]]
-    units=[4,6,8,10]
+    units=[4,6,8]
     velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
     scales=[0.3,0.5,1,2,4,6,8,10,15,20]    
     scale_str=["03","05","1","2","4","6","8","10","15","20"]
     scales_diff=[0.05,0.1,0.2,0.4,0.5,1.0]
+    scales_diff_str=["005","01","02","04","05","10"]
     
+    counter=capillary_str.index(dir_name)
     #for counter,dir_temp in enumerate(capillary_str):
     subprocess.call(['cp','main.out',dir_name+"/"])
     subprocess.call(['cp','main_diffusion.out',dir_name+"/"])
     subprocess.call(['cp','binary.pbs',dir_name+"/"])
+    subprocess.call(['cp','binary_periodic.pbs',dir_name+"/"])
     os.chdir(dir_name)
     
     flag=False
@@ -62,6 +65,7 @@ def run_simulations(dir_name):
         subprocess.call(['cp','main.out',dir_name+"/"])
         subprocess.call(['cp','main_diffusion.out',dir_name+"/"])
         subprocess.call(['cp','binary.pbs',dir_name+"/"])
+        subprocess.call(['cp','binary_periodic.pbs',dir_name+"/"])
         subprocess.call(['cp','geometry.dat',dir_name+"/"])
         subprocess.call(['cp','velx0200000.dat',dir_name+"/"])
         subprocess.call(['cp','vely0200000.dat',dir_name+"/"])
@@ -71,14 +75,31 @@ def run_simulations(dir_name):
             subprocess.call(['cp','main.out',str(unit)+"/"])
             subprocess.call(['cp','main_diffusion.out',str(unit)+"/"])
             subprocess.call(['cp','binary.pbs',str(unit)+"/"])
+            subprocess.call(['cp','binary_periodic.pbs',str(unit)+"/"])
             subprocess.call(['cp','geometry.dat',str(unit)+"/"])
             subprocess.call(['cp','velx0200000.dat',str(unit)+"/"])
[…]

### 2012-01-27 Python/DecreasingDiffusion/mass_periodic.cpp

@@ -17,7 +17,8 @@ int NX;
 int NUM;
 
 //Overall scaling parameter
-double scale_velocity=1;
+double scale_velocity=1.0;
+double scale_diffusion=1.0;
 
 //Other constants
 const int NPOP=9;
@@ -558,7 +559,7 @@ int main(int argc, char* argv[])
     	scale_velocity=atof(argv[1]);
     	scale_diffusion=atof(argv[2]);
         omega=2.0*omega/(scale_velocity*(2.0-omega)+omega);
-        omega=2.0*omega/(scale_diffusion*(2.0-omega)+omega)
+        omega=2.0*omega/(scale_diffusion*(2.0-omega)+omega);
         omega_minus=omega;
         omega_plus=2.0-omega;
         std::cout<<"Scaling velocity parameter is "<<scale_velocity<<"\n";
@@ -596,7 +597,7 @@ int main(int argc, char* argv[])
  			counterconvert<<counter;
  			filewritedensity<<std::fixed;
 
-			filewritedensity<<"density"<<std::string(7-counterconvert.str().size(),'0')<<counter;
+			filewritedensity<<"density_periodic"<<std::string(7-counterconvert.str().size(),'0')<<counter;
 			
  			writedensity(filewritedensity.str());
 		}

### 2012-01-27 Text/introduction.tex
Writing a report.

@@
 \newcommand{\coutlet}{C_{\mathrm{outlet}}}
+\newcommand{\coverall}{C_{\mathrm{overall}}}
+\newcommand{\cstar}{C^{*}}
+\newcommand{\cmedium}{C_{\mathrm{medium}}}
+\newcommand{\volnondim}{\vol \frac{\lunit}{\ububble+\ugas}}
 
@@
 The concentration flux is calculated as the difference between overall
-average concentration in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$)
+average concentration in the whole domain ($\coverall=\int_{V} C \mathrm{d}V /V$)
 at time
@@
 Let us look at the infinitesimal small domain of the volume $A \Delta x$ not
-moving and with the point mass source. Then the concentration difference can be found as $\Delta C = C^* -
-C(t)$, where $C^*$ is the imposed point source concentration, $C(t)$ is
+moving and with the point mass source. Then the concentration difference can be found as $\Delta C =
+\cstar -
+C(t)$, where $\cstar$ is the imposed point source concentration, $C(t)$ is
 the time dependent average concentration. Therefore one can write the time dependent ODE for the
@@
 \beq
-\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (C^{*}-C(t)), 
+\dot{m}= A \Delta x \frac{\mathrm{d}C}{\mathrm{d} t} = k_L P (\cstar-C(t)), 
 \feq
@@
 \beq
-C(t)= C^{*}(1-\exp(-\vol t )), 
+C(t)= \cstar (1-\exp(-\vol t )), 
 \feq
@@
 \beq
-U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(C^{*}-C(x)\bigr), 
+U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(\cstar-C(x)\bigr), 
 \feq 
@@
 \beq
-C(x)= C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
+C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
 \label{main:mass:transfer:expression} 
@@
 
-The expression (\ref{main:mass:transfer:expression}) was used in the experiments by
-\citet{bercic-mass}. One should be accurate with the definition of velocities because we have two
-different phases. Usually, one can take the velocity $U$ to be as
-average velocity or $U=U_{gas}+U_{liq}$, where $U_{gas}$ and $U_{liq}$ are liquid and gas
-superficial velocities correspondingly. In this case, the continuouty assumption is restored and
-all considerations above are valid.
-
- However, if one wants to analytically estimate the mass transfer coefficients, the situation is
-much more complicated because of the two phases presence. Phases can have different mixing patterns
-from film to slug and from slug to film. The analytical approaches described above assume that the
-contributions from film and bubble caps can be calculated separately. However one can see that such 
+\subsection{Bubble train}
+In the application to the bubble train flow, if one can think of one bubble to be a point source,
+then all considerations above are valid. For example, the expression
+(\ref{main:mass:transfer:expression}) was used in the experiments by
+\citet{bercic-mass}. However, one should be accurate with the definition of velocities because two
+different phases co-exist in the bubble train flow. Usually, one can take the velocity $U$ to be as
+a bulk velocity or $U=\ugas+\uliq$, where $\ugas$ and $\uliq$ are liquid and gas
+superficial velocities correspondingly.
+
+Though the experimental measurements are straightforward as measuring concentrations at different
+locations and calculating the volumetric mass transfer coefficient through the logarithmic
+function. However, if one wants to analytically estimate the mass transfer coefficients, the
+situation is much more complicated because of two phases presence and complicated bubble
+geometry. Phases can have different mixing patterns
+from film to slug and from slug to film. As it was mentioned before depending on the capillary
+number the mixing velocity pattern is different. Analytical approaches
+\cite{irandoust,vanbaten-circular} assume that the
+contributions from film and bubble caps can be calculated separately. However, one can see that
+such 
 an assumption for bubble caps (slug well mixed and the concentration is uniformly distributed over
@@
 concentration from film is mixed with the slug and changes the overall concentration in the slug.
+Thus, all estimations for the analytical mass as well do not account mutual mass transfer from
+neighbouring bubbles.
+
 Another issue is that if the slug is long enough then the film saturates with the tracer
@@
 Mixing patterns of the film and the liquid slugs are of great importance for the analytical
-estimation of the mass transfer \cite{yue-mass}.
-
-\subsection{Numerical calculation}
-
-The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
-the same figure, one can see the proposed benchmark for the tracer. The
-physical
-picture for the proposed numerical benchmark is  related to classical experiments conducted by
-\citet{bercic-mass}. In their work authors studied gas-liquid mass transfer coefficient by
-injecting methane as the gas bubble and measuring the dissolved concentration of methane in water
-along the channel. This situation implies the periodic boundary conditions and steady-state motion
-of bubbles.
-
-The numerical  procedure of studying mass transfer is presented in the following steps:
-\begin{description}
- \item[Flow field] The hydrodynamics for the bubble motion in the periodic domain is obtained
-according to the work \cite{kuzmin-binary2d}. The grid resolution is taken to insure grid
-independency of results.  
- \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
-are conducted in the moving
-reference frame with the bubble. Then the bubble stands still and the flow is coming around the
-bubble. We impose a steady concentration of solutant on the surface of the bubble.
-\item[Mass transfer] One needs not only perform a Galilean transformation to the reference
-frame moving with the bubble but also to
-transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
-slug. 
-\end{description}
-
-In the numerical simulation it is not possible to simulate really long domains with the infinite
-number of the bubbles. As we saw before there are two approaches towards it - either to simulate
+estimation of the mass transfer \cite{yue-mass}. However, the assumptions usually taken for the
+mass transfer calculation are small capillary number and certain mixing patterns which help to
+estimate the mass transfer using the penetration theory of \citet{higbie}.
+
+The numerical approach can take into the account the complicated mixing patterns and geometries.
+However, there is a  challenge to restore the continous approach as it is seen in experiments. Next
+section gives more details about numerical simulations.
+
+\subsection{Numerical simulations}
+To restore the continuous picture one needs to perform a number of bubbles simulations. As we saw
+before there are two approaches towards it - either to simulate
 the bubble train and then to measure concentration along the pipe, Eq.
-\ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with bulk
-velocity $U$ and conduct the same measurements through Eq. \ref{main:mass:transfer:expression}.
-However, both methods do require a tracking of moving bubbles which is complicated from the
-numerical point of view.
-
-Therefore, one needs to come up with the simple smaller domain calculations
-of the mass transfer coefficient, which represent the continuous picture with infinite numbers of
-the bubbles closely. In comparison with analytical estimations of the mass transfer coefficient,
-where the mixing patterns are extremely important, the numerical simulations need only to mimic
-the continous picture and provide the way to calculate the volumetric mass transfer coefficient.
+\ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with the bulk
+velocity $U$ and conduct same measurements. However, both methods do require a tracking of
+moving bubbles which is complicated from the numerical point of view. Therefore, one needs to come
+up with the simple smaller domain calculations of the mass transfer coefficient, which mimic the
+continuous picture with infinite numbers of the bubbles closely.
+
+To avoid complications with moving grids, our
+approach is to simulate mass transfer in the reference frame moving with the bubble. Therefore, one
+needs to examine the equation for the continuous approach, Eq.
+\ref{main:mass:transfer:expression}.
 
 We perform simulations in the frame moving with the bubble (velocity
-$U_{bubble}$), that the bubble position stands steady. The bubble velocity $U_{bubble}$ is
-different from the bulk velocity $U_{gas}+U_{liq}$. In this case we need to perform coordinate
-change:
+$\ububble$), that the bubble position stands steady. The bubble velocity $\ububble$ is
+different from the bulk velocity $\ugas+\uliq$. In this case we need to perform a coordinate $x$
+variable change:
 \beqal
-&x(t)=U_{bubble}t\\
-&C(x)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a \frac{x}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
-&C(t)=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)
+\label{theor:average:concentration:time}
+&x(t)=\ububble t\\
+&C(x)=\cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\ugas+\uliq}\bigr)\Bigr)\\
+&C(t)=\cstar \Bigl(1-\exp\bigl(-\vol\, t \frac{\ububble}{\ugas+\uliq}\bigr)\Bigr).
 \feqal
-If the unit volume that we simulate is quite long one can obtain the values of the concentration
-in the inlet and outlet as a function of time:
+Therefore, one can obtain the volumetric mass transfer coefficient through the concentration:
 \beqal
-&C(U_{bubble}\, t)=C^{*}\Bigl(1-\exp\bigr(-k_L\, a\, t
-\frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
-&C(U_{bubble}\,t+L_{unit})=C^{*}\Bigl(1-\exp\bigl(-k_L a \frac{
-U_{bubble}\,t+L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)\\
-&=C^{*}\Bigl(1-\exp\bigl(-k_L\, a\, t \frac{U_{bubble}}{U_{gas}+U_{liq}}\bigr)\exp\bigl(-k_L a
-\frac{L_{unit}}{U_{gas}+U_{liq}}\bigr)\Bigr)
+&\vol\, t \frac{\ububble}{\ugas+\uliq}=\ln \frac{\cstar}{\cstar-C(t)}\\
+&\volnondim=\frac{\lunit}{\ububble t}\ln \frac{\cstar}{\cstar-C(t)},
 \feqal
-Therefore the mass transfer coefficient can be calculated as follows:
-\begin{equation}
+where the parameter $\vol \frac{\lunit}{\ugas+\uliq}$ is non-dimensional. One can also measure the
+volumetric mass transfer coefficient from concentrations given at times $t_1$ and $t_2$:
+\beq
 \label{theor:continuous:mass:transfer}
-\begin{aligned}
-&-k_L a \frac{L_{unit}}{U_{gas}+U_{liq}}=\ln\Bigl(\frac{C^{*}-C_{outlet}}{C^{*}-C_{inlet}}\Bigr)\\
-&k_L a
-=\frac{U_{gas}+U_{liq}}{L_{unit}}\ln\Bigl(\frac{C^{*}-C_{inlet}}{C^{*}-C_{outlet}}
-\Bigr)
-\end{aligned}
-\end{equation}
-If inlet and outlet concentrations are small in comparison with the saturation concentration $C^{*}$
-then the expression for the volumetric mass transfer coefficitent $k_L a$ can be simplified:
-\beq
-\vol=\frac{\Delta C}{C^{*}} \frac{U_{gas}+U_{liq}}{L_{unit}},
-\feq
-where $\Delta C=C_{outlet}-C_{inlet}$. If we go to the continuous formulation by changing $L_{unit}$
-to be a continuous coordinate $x$, then the following can be obtained \cite{jos-mass}:
-\beq
-\Delta C = C^{*} \vol \frac{x}{U_{gas}+U_{liq}}
-\label{small:conc:mass:estimation}
-\feq
-
-We consider the following possibilities of conducting numerical simulations:
+\volnondim=\frac{\lunit}{\ububble
+(t_2-t_1)}\ln\frac{C^{*}-C(t_1)}{C^{*}-C(t_2)}.
+\feq
+Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are
+the cornerstones of the present work. The main questions arisen in the present work are to define
+$C(t)$ and  the boundary conditions to produce a proper volumetric mass transfer coefficient
+$\vol$.
+
+Three possible scenarios of conducting numerical simulations are possible: 
 \begin{enumerate}
+\item As far as the hydrodynamic flow is periodic, one can make an assumption of the same boundary
+conditions applied to the tracer concentration. Therefore, only one unit cell is simulated with
+periodic boundary conditions, see Fig. \ref{fig:benchmark}. As well, no tracer leaves a
+domain. The situation resembles a situation for the plug flow, where no tracer can leave a unit
+domain. We expect such a situation happening for small Capillary numbers $Ca<0.1$, where the film
+is thin and saturates fast with the tracer. Though easier to implement, it rises certain critisism
+towards the inlet concentration to be equal to the outlet concentration. In the continuous
+formulation there is the concentration difference between inlet and outlet involving the volumetric
+mass transfer coefficient:
+\beq
+\volnondim=\ln\frac{\cstar-\cinlet}{\cstar-\coutlet}.
+\feq
+The concentration $C(t)$ required for calculation the volumetric mass transfer coefficient, Eq.
+(\ref{theor:average:concentration:time}), can be taken as the average concentration in the domain:
+\beq
+C(t)=\frac{\int_{liquid}{C \mathrm{d}V}}{\int{\mathrm{d}V}}.
+\end
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
+\caption{The two-dimensional benchmarks for the  the mass transfer
+coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
+(bottom). \label{fig:benchmark}}
+\end{figure}
+\item The second approach is the same as the first one but the concentration is taken as in
+\cite{vanbaten-circular}. The characteristic concentration is taken as the inlet/outlet
+concentration:
+\beqal
+\cinlet=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
+\coutlet=\frac{\int{U(y) C(\Lunit,y,t) \mathrm{d}y}}{\int{U(\Lunit,y) \mathrm{d}y}}\\
+\cinlet=\coutlet.
+\feqal
+Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
+considerably large and the tracer is well mixed in the slug.
+
+\item
+The approach of \citet{vanbaten-circular} is taken. Periodic boundary conditions were used. By the
+definition the mass transfer coefficient is
+proportional to the gain of the mass in the system divided by the concentration difference
+multiplied on the surface area:
+\beq
+\vol=\frac{\dot{m}}{P \Delta C}\frac{P}{V}=\frac{\dot{m}}{V (\cstar-C(t))},
+\feq
+where mass difference in the domain can be calculated as:
+\beq
+\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(t_2)\mathrm{d}V}-\int_liq{C(t_1)\mathrm{d}V}}{
+t_2-t_1 } .
+\feq
+In the approach of \citet{vanbaten} the inlet and outlet concentrations were taken as the
+characteristic concentration $C(t)$.
+
 \item 
@@
 
-\item Another possibility is to use the periodic boundary conditions as the limiting case of the
-continuous formulation. In this case the inlet and outlet concentrations are not much different
-($C(x)=C(x+L_{unit})=C(x+\Delta x)\approx C_{media}$, see Fig. \ref{fig:moving:frame}), where
-$C_{media}$ is the mass averaged over domain concentration. This formulation requires the periodic
-boundary condition $C_{inlet}=C_{outlet}$. By the definition the mass transfer coefficient is
-proportional to the gain of the mass in the system divided by the concentration difference:
-\beq
-j=\frac{\dot{m}}{P \Delta C}=\frac{\dot{m}}{P (C^{*}-C_{media})},
-\feq
-where mass difference in the domain can be calculated as:
-\beq
-\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{C(t_2)\mathrm{d}V}-\int{C(t_1)\mathrm{d}V}}{t_2-t_1}.
-\feq
-Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
-considerably large and the tracer is well mixed in the slug, as one can take the concentration
-difference as $\Delta C = C^{*}-C_{media}$. The best case scenario is when $C_{media}$ is close to
-zero, in this case we can be sure that the flux to the domain is calculated precisely and periodic
-boundary conditions are fulfilled.
 \end{enumerate}
+
+The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
+the same figure, one can see the proposed benchmark for the tracer. The
+physical
+picture for the proposed numerical benchmark is  related to classical experiments conducted by
+\citet{bercic-mass}. In their work authors studied gas-liquid mass transfer coefficient by
+injecting methane as the gas bubble and measuring the dissolved concentration of methane in water
+along the channel. This situation implies the periodic boundary conditions and steady-state motion
+of bubbles.
+
+\section{Validation}
+
+\section{Numerical approach}
+\label{sec:numerics}
+The numerical  procedure of studying mass transfer is presented in the following steps:
+\begin{description}
+ \item[Flow field] The hydrodynamics for the bubble motion in the periodic domain is obtained
+according to the work \cite{kuzmin-binary2d}. The grid resolution is taken to insure grid
+independency of results.  
+ \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
+are conducted in the moving
+reference frame with the bubble. Then the bubble stands still and the flow is coming around the
+bubble. We impose a steady concentration of solutant on the surface of the bubble.
+\item[Mass transfer] One needs not only perform a Galilean transformation to the reference
+frame moving with the bubble but also to
+transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
+slug. 
+\end{description}
 
@@
 \end{description}
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}\\
-\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
-\caption{The two-dimensional benchmarks for the  the mass transfer
-coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
-(bottom). \label{fig:benchmark}}
-\end{figure}
 

### 2012-01-27 Python/HydroAlexandra/binary_debug.cpp

@@ -1,0 +1,482 @@
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+#include <limits>
+//Domain size
+const int NY=102;
+const int NX=100;
+
+int width=10;
+//Time steps
+int N=1000;
+int NOUTPUT=10;
+int NSIGNAL=10;
+
+//Fields and populations
+double f[NX][NY][9], f2[NX][NY][9], g[NX][NY][9], g2[NX][NY][9];
+double rho[NX][NY],ux[NX][NY],uy[NX][NY],phase[NX][NY];
+
+double force_x=0.0000009;
+double force_y=0.0;
+
+//Binary-liquid parameters
+double aconst=0.04;
+double kconst=0.04;
+double gammaconst=1.0;
+double wall_gradient=0.0;
+
+double tau_gas=0.7;
+double tau_liq=2.5;
+
+//BGK relaxation parameter
+double omega_rho=1.0;
+double omega_phi=1.0;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+float wxx[] = {0.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+float wyy[] = {0.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+float wxy[] = {0.0, 0.0, 0.0, 0.0, 0.0, 1.0/4.0, -1.0/4.0, 1.0/4.0, -1.0/4.0};
+
+float gradstencilx[9]={0.0,4.0/12.0,0.0,-4.0/12.0,0.0,
+			          1.0/12.0,-1.0/12.0,-1.0/12.0,1.0/12.0};
+
[…]

### 2012-01-30 Text/introduction.tex
Did a few sketches and continue cleaning it up.

@@
 \newcommand{\volnondim}{\vol \frac{\lunit}{\ububble+\ugas}}
+\newcommand{\omegaplus}{\omega_{+}}
+\newcommand{\omegaminus}{\omega_{-}}
 
@@
 \beq
+\label{average:concentration:definition}
 C(t)=\frac{\int_{liquid}{C \mathrm{d}V}}{\int{\mathrm{d}V}}.
-\end
+\feq
 \begin{figure}[htb!]
@@
 \beqal
-\cinlet=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
-\coutlet=\frac{\int{U(y) C(\Lunit,y,t) \mathrm{d}y}}{\int{U(\Lunit,y) \mathrm{d}y}}\\
-\cinlet=\coutlet.
+&\cinlet=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
+&\coutlet=\frac{\int{U(y) C(\lunit,y,t) \mathrm{d}y}}{\int{U(\lunit,y) \mathrm{d}y}}\\
+&\cinlet=\coutlet.
 \feqal
@@
 \feq
-In the approach of \citet{vanbaten} the inlet and outlet concentrations were taken as the
+In the approach of \citet{vanbaten-circular} the inlet and outlet concentrations were taken as the
 characteristic concentration $C(t)$.
@@
 \item 
-The tracer picking up procedure can be introduced
-in the manner of the considerations above. We impose the concentration at the entrance to be
-constant $C(0,y)=C_{inlet}$, at the outlet we impose the outflow boundary condition $\frac{\partial
-C}{\partial x}(L,y)=0$. To be compliant with the considerations above one needs to impose as well
-the outflow boundary conditions for the inlet as well. However, without loss of the generality one
-can impose $C_{inlet}=0$, since the walls in the reference frame
-moving with the bubble are moving from the inlet to the outlet. That means that no tracer
-concentration leaves domain from the inlet side, which is true for the capillary numbers larger
-than $0.6$.  However, this boundary condition can not be used in the case of small capillary
-numbers, since there is a strong circulation in front of the bubble. One can see the sketch of the
-approach in Fig. \ref{fig:benchmark:jos}. The longer the numerical domain length the better will be
-results. One can estimate the volumetric mass transfer coefficient in this case through the equation
-(\ref{small:conc:mass:estimation}) for small concentrations. Note a few considerations:
-\begin{itemize}
-\item  The considerations above were established for the homogenous velocity field. In the case of
-the non-homogenous velocity field one needs to obtain a concentration from the mass flux:
-\beq
-C_{outlet}=\frac{\int{U(y) C(L_{unit},y) \mathrm{d}y}}{\int{U(y) \mathrm{d}y}}.
-\feq
-\item Note, that one cannnot use the definition of the mass transfer coefficient as far as it
-varies through the bubble due to inhomogenoities of the flow. Therefore, the volumetric mass
-transfer coefficient is introduced that takes into the account the bubble geometry.
-\end{itemize}
+The approach of the opened boundaries was examined, see Fig. \ref{fig:benchmark:jos}. At the inlet
+and outlet boundaries the diffusion flux was imposed to be zero, $\frac{\partial C}{\partial x}=0$.
+The characteristic concentration was taken as the average concentration in the whole domain.
 \begin{figure}
 \includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
-\caption{The numerical mass transfer benchmark. \label{fig:benchmark:jos}}
-\end{figure}
-
+\caption{The numerical mass transfer benchmark with open boundaries. The mass transfer is
+calculated according to Eq. \ref{theor:average:concentration:time} with the characteristic
+concentration accoring to Eq. \ref{average:concentration:definition}. \label{fig:benchmark:jos}}
+\end{figure}
+
+\item 
+The last approach to be examined in this paper is the approach of the simulation of a lot of unit
+volumes, see Fig. \ref{big:benchmar:alot}. This situation corresponds to the simulation of the
+bubble train head, after injecting to the pipe and travelling along the pipe. The argument here is
+that behind a certain number of the bubble train head, the influence of the boundaries will be
+diminished. Thus, the average concentration in time will be governed by Eq.
+\ref{theor:continuous:mass:transfer}. This simulation statement is of most correspondence to
+experiments and should give right answer. However, one of the
+disadvantages is to simulate a certain number of unit cells, thus increasing a computational
+complexity.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/benchmark_alot.eps}\\
+\caption{Benchmark for a lot of units. \label{fig:benchmark:alot}}
+\end{figure}
 \end{enumerate}
 
-The numerical benchmark is presented in Fig. \ref{fig:benchmark}. In
-the same figure, one can see the proposed benchmark for the tracer. The
-physical
-picture for the proposed numerical benchmark is  related to classical experiments conducted by
-\citet{bercic-mass}. In their work authors studied gas-liquid mass transfer coefficient by
-injecting methane as the gas bubble and measuring the dissolved concentration of methane in water
-along the channel. This situation implies the periodic boundary conditions and steady-state motion
-of bubbles.
+Before all the approaches will be examined we will perform benchmarks of parts of geometries that
+form a problem.
 
 \section{Validation}
+As for analytical expressions the problem of the mass transfer can be decomposed to the following
+parts: the mass transfer from two hemispheres and the mass transfer from the film. We will examine
+these problems with the help of the lattice Boltzmann method and compare them against analytical
+solutions. The next sections will present the lattice Boltzmann method and a few benchmarks.
+
+\subsection{TRT $D2Q9$ model}
+The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
+physical domain. It utilizes
+probability distribution functions (also known as particle populations)
+containing information about
+macroscopic variables, such as fluid density and momentum. LBE consists of
+two parts: a local collision step, and a propagation step which transports
+information from one node to another along some 
+directions specified by the discrete velocity set.
+The LBE is typically implemented as follows:
+\begin{equation}
+\label{standard:implementation}
+\begin{aligned}
+&f_i^{*}(\bm{x},t)= f_i(\bm{x},t)-\omega \bigl(f_i(\bm{x},t)-f_i^{eq}(\bm{x},t)\bigr),&&\text{
+collision step}\\
+&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{ propagation step}, 
+\end{aligned}
+\end{equation}
+where $f_i$ is the probability distribution function in the direction $\bm{c_i}$,
+ $f_i^{eq}$ is the equilibrium probability distribution function, $\omega$ is the
+relaxation parameter. Collision operator, $-\omega \bigl(f_i- f_i^{eq}\bigr)$ is so-called BGK
+collision operator \cite{bgk}. However, the approach to be used here is the TRT
+(two-relaxation-times) collision operator \cite{ginzburg-main,ginzburg-saturated-flow}. In
+comparison with the widely used BGK collision operator, TRT collision operator have better accuracy
+for diffusion and convection fluxes, larger range of parameters where the LBM scheme is stable.
+
+The TRT collision operator \cite{ginzburg-boundary-main}
+decomposes the populations and the equilibrium
+distribution into the symmetric and antisymmetric parts:
+\begin{equation}
+\label{trtdecomp}
+f^{\pm}_i=\frac{f_i\pm f_{\bar{i}}}{2}\;,\; 
+{eq_i}^{\pm}=\frac{eq_i\pm eq_{\bar{i}}}{2}\;,
+\end{equation}
+where $\bar{i}$ is the opposite direction to the $i$-th direction.
+The collision is performed with two independent relaxation rates for 
+symmetric and antisymmetric modes:
+\begin{equation}
+\label{trt}
+\begin{aligned}
+&f_i^{*}(\bm{x},t)=f_i(\bm{x},t)-\omegaplus (f_i^{+} - eq_i^+)-\omegaminus
+(f_i^{-} -
+eq_i^-)\\
+&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t).
+\end{aligned}
+\end{equation}
+Note that the BGK collision operator is the particular subclass of the TRT relaxation operator with
+$\omegaplus=\omegaminus$. In comparison with the BGK collision operator,
+the TRT collision operator has the additional degree of freedom. Thus, the TRT operator then
+introduces
+so-called magic (free) parameter
+$\Lambda=\Bigl(\frac{1}{\omegaplus}-\frac{1}{2}\Bigr)\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}
+\Bigr)$. 
+This free parameter controls the effective location of the bounce-back
+walls \cite{ginzburg-multireflection}, second-order accuracy of
+boundary \cite{ginzburg-boundary-main} and interface schemes \cite{ginzburg-discontinious}, 
+spatial accuracy \cite{ginzburg-recurrence,servan-trt-stability},
+consistency \cite{ginzburg-brinkman} and, to some extent,
+stability \cite{kuzmin-stability-optimal,kuzmin-d1q3,servan-trt-stability}.
+In particular, $\Lambda=\frac{1}{4}$ achieves the optimal stability for the
+linear advection-diffusion isotropic equation \cite{kuzmin-stability-optimal}.
+
+The parameters $\omegaplus$, $\omegaminus$ and $f_i^{eq}$ fully define the lattice Boltzmann
+procedure. The two-dimensional nine velocities LBM $D2Q9$ is defined on the set of lattice
+velocities with coordinates:
+\beqal
+&c_{ix}=\{0,1,0,-1,0,1,-1,-1,1\},\text{ for } i=0\dots8\\
+&c_{iy}=\{0,0,1,0,-1,1,1,-1,-1\},\text{ for } i=0\dots8\,.
+\feqal
+
+The equilibrium functions for $D2Q9$ TRT model are represented as \cite{kuzmin-stability-optimal}:
+\begin{equation}
+\begin{aligned}
+&eq_i^{+}=eq_i^{(m)}+g^{(u)} eq_i^{(u)}\\
+&eq_i^{(m)}=t_i^{(m)} c_e+ eq_i^{(a)}\\
+&eq_i^{(u)}=t_i^{(u)} \frac{u_x^2+u_y^2}{2}+\frac{u_x^2-u_y^2}{4} p_i^{(xx)}+g_{xy}^{(u)}\frac{u_x
+u_y}{4} p_i^{xy}\\
+&eq_i^{(a)}=\frac{D_{xx}-D_{yy}}{4} p_i^{xx}+\frac{D_{xy}}{4} p_i^{(xy)},
+\end{aligned}
+\end{equation}
+where the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor  $p_i^{(xy)}=c_{ix} c_{iy}$, the weights
+$t_i^{(u,m,a)}$ can be chosen based on stability criteria. Though not the best set of weights for
+stability, but the most spread set of weights, so called ``hydrodynamic`` weights, was chosen:
+\begin{equation}
+t_i^{(u)}=t_i^{(m)}=t_i^{(a)}=\Bigl\{0,\frac{1}{3},\frac{1}{3},\frac{1}{3},\frac{1}{3},\frac{1}{12},
+\frac {1}{12},\frac{1}{12},\frac{1}{12}\Bigr\}
+\end{equation}
+
+It can be shown through the Chapman-Enskog procedure \cite{chapman}, that the simple update rule
+with the equilibrium function presented above restores the anisotropic
+advection-diffusion equation:
+\beq
+\partial_t C+ \partial_{\alpha} C u_{\alpha}=\partial_{\alpha\beta} D_{\alpha\beta} C,
+\feq
+ with the
+following diffusion tensor:
+\begin{equation}
+D_{\alpha\beta}=
+\begin{pmatrix}
+D_{xx} + (g^{(u)}-1) u_x^2 & D_{xy}+(g_{xy}^{(u)}-1)u_x u_y\\
+D_{xy} + (g_{xy}^{(u)}-1) u_x u_y& D_{yy}+(g^{(u)}-1) u_y^2 
+\end{pmatrix}
+\end{equation}
+To consider the situation when the resolution is not needed to be changed in $x$ and $y$
+directions, one can obtain that $D_{xx}=D_{yy}$. The cross-diagonal components of the diffusion
+tensor are taken as zeros, i.e. $D_{xy}=0$. In comparison with $D2Q5$ model, with the $D2Q9$ it is
+possible to cancel the numerical diffusion by the proper choice
+of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$. If one introduces
+
+As far as the simulated diffusion tensor is close to $0$ the stability limits restrict the velocity
+amplitude to be simulated \cite{kuzmin-stability-optimal}. However, particular choice of weights
+can drastically help. Fig. \ref{stability:d2q9} shows the stability limits for D2Q9 with removed
+numerical diffusion and with it for two particular choices of weights.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
+\caption{The non-negativity areas and stable sub-domains of the OTRT schemes ($\Lambda=\frac{1}{4}$)
+are plotted for the $D2Q9$ (standard weights, left) and the $D2Q9$ (uniform weights, right) when the
+numerical diffusion is removed, partially or completely. Two non-negativity areas where all the
+equilibrium populations are positive have curvilinear boundaries: they are smaller when
+$g^{(u)}_{xy}=0$ (yellow) and than when $g^{(u)}_{xy}=1$ (green+yellow). The non-negativity
+condition is required by BGK collision operator. The stable sub-domains for $g^{(u)} = 1,
+g^{(u)}_{xy} = 0$ are small (red+green+yellow) triangles. When the numerical diffusion is removed
+the stable area is bounded by magenta and the (blue) domain above. The proper choice of weights can
+allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1−c_e$ (the
+uniform weights only).
+\label{stability:d2q9}}
+\end{figure}
+
+The set of equations (\ref{set:equilibrium:binary}) restores the
+macroscopic
+fluid equations as:
+\begin{equation}
+\begin{aligned}
+&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
+\end{aligned}
+\label{advection:diffusion:equation}
+\end{equation}
+where $D=c_s^2 (\tau-1/2)$ is the viscosity, 
+$P_{\alpha\beta}=\Bigl(p_0-k\phi \Delta \phi -\frac{k}{2}|\nabla \phi|^2\Bigr)\delta_{\alpha\beta}
++ k \partial_{\alpha} \phi \partial_{\beta} \phi$  \cite{pooley-contact}.
+
+{\color{red}
+While the lattice Boltzmann system has parameters such as the surface tension, the gas and liquid
+viscosities, etc., those parameters are not the representative and
+proportional quantities of the parameters in a physical system. The parameters of the lattice
+Boltzmann are connected with the physical parameters only through the non-dimensional
+numbers governing the physics of the problem. In our case, these numbers are the capillary number
+and the
+viscosity ratio $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}$, which are
+obtained from the physical world and then matched through the lattice Boltzmann quantities.
+Therefore, one can substitute any quantity, i.e.
+$U_{\mathrm{bubble}}$, in the physical units or in the lattice Boltzmann units as soon as the
+capillary number is the same in both worlds.}
+
+\subsection{The radial case}
+We want to examine the bounce-back conditions against the analytical solution. The system can be
+prescribed by the following system of equations:
+\beq
+\begin{aligned}
+&\partial_t C(r,t)=\frac{1}{r}\partial_r r \partial_r C(r,t)\\
+&C(a,t)=C_0,\,C(r,0)=C_{init}
+\end{aligned}
+\feq 
+The solution is represented as \cite{chemical-correlations}:
+\beq
+\frac{C(r,t)-C_{0}}{C_{init}-C_{0})}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
+J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})},
+\feq
+where $\mu_n$ is the $n$-th zero root of the $0$th order Bessel polynomial $J_0(\mu_n)=0$. Some of
+the corresponding roots are as follows: $\mu_1=2.4048$,$\mu_2=5.5201$,$\mu_3=8.6537$,
+$\mu_4=11.7915$,$\mu_5=14.9309$.
+By taking initial concentration to be $0$, one can obtain the following solution:
+\beq
+C(r,t)=C_0 \Biggl(1 - \sum_{n=1}^{\infty}{\frac{2}{\mu_n
+J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})}\Biggr).
+\feq
+
+The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. Some examples for
+different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/cylinder1666.eps}
+\includegraphics[width=0.5\textwidth]{Figures/cylinder0833.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/cylinder0104.eps}
+\includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
+\caption{Profiles for different diffusion parameters. One can see that the diffusion is captured
+accurately in non-dimensional space \label{fig:cylinder:benchmark}.}
+\end{figure}
+
+\subsection{Parabolic profile with velocity zero gradient at the wall}
+In any case here is what we want to solve as the system for :
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
+\end{aligned}
+\feq
+The system after non-dimensionalization becomes as follows:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H}
+\Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
+\end{aligned}
+\feq
+After a change of variables:
+\beq
+\begin{aligned}
+&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
+&\xi=\frac{y}{H}
+\end{aligned}
+\feq
+, the equation with boundary conditions becomes as follows:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
+&C(0,\xi)=C_0\\
+&C(\zeta,0)=C_{wall}\\
+&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
+\end{aligned}
+\feq 
+Still the equation cannot be solved with the separation of variables as it requires the homogenuos
+boundary conditions. Thus, let us introduce the new variable to be $\Theta=C-C_{wall}$. The system
+will be changed but not considerably:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
+&\Theta(0,\xi)=C_0-C_{wall}\\
+&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
+\end{aligned}
+\feq 
+This equation can be solved by separation of variables if the solutions is represented as the
+multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$. The differential equation will
+become as follows:
+\beq
+\begin{aligned}
+&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
+Y(\xi)}{\mathrm{d}\xi^2}\\
+&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
+\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
+\end{aligned}
+\feq
+The left and right parts depend on different variables. Therefore to be equal to each other both
+parts equal to constant, say $-m^4$. Thus, the separation of the variables leads to two ODE
+equations:
+\begin{equation*}
+\begin{aligned}
+&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
+&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
+\end{aligned}
+\end{equation*}
+The solution of the first equation is the exponential function:
+\beq
+X(\zeta)=\exp(-m^4 \zeta)\\
+\feq
+The solutions of the second equation are two hypergeometric function which can be expressed through
+the Bessel functions \cite{abramowitz}:
+\beq
+\begin{aligned}
+&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+\end{aligned}
+\feq
+The solution is the summation of two functions:
+\begin{equation*}
+Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
+\end{equation*}
+One can find coefficients from the boundary conditions:
+\beq
+\begin{aligned}
+&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
+&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
+&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
+&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
+\end{aligned}
+\feq
+Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
+numerical values:
+$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
+Therefore a solution in a general form is represented as:
+\beq
+\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
+\feq
+To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
+condition:
+\beq
+\Theta(0,\xi)=C_0-C_{wall}=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)}\\
+\feq
+Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
+J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
+\beq
+\begin{aligned}
+&\bigl(C_0-C_{wall}\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
+&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+\end{aligned}
+\feq
+Therefore, the overall solution is specified as:
+\beq
+\begin{aligned}
+&C(x,y)=C_{wall}+\sum_{m}{C_m
+\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
+\frac { x }{H}\Bigr)}\\
+&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+\end{aligned}
+\feq
+
+\subsection{The parabolic profile mass transfer and comparison}
+The problem we want to address can be formulated through the following PDE:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=0,\, C(x,\pm \delta)=C_s,\, \frac{\partial C}{\partial y }(x,0)=0\\
+&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
+\end{aligned}
+\feq
+The same procedure can be done as in the previous case to redefine variables. After substitution
+the following can be obtained:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
+\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
+\end{aligned}
+\feq
+After separation of variables, $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$ one can come up with two
+equations:
+\beq
+\label{fourier:separation:variables}
+\begin{aligned}
+&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}+m^4 X(\zeta)=0\\
+&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 (1-\xi^2) Y(\xi)=0
+\end{aligned}
+\feq
+The first equation has a solution:
+\beq
+X(\zeta)=\exp(-m^4 \zeta)
+\feq
+The second equation can be simplified after substitution $\bar{\xi}=m \sqrt{2} \xi$ to the standard
+equation:
+\beq
+Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
+\feq
+The equation above has two solutions via parabolic cylinder functions or through the confluent
+hypergeometric function \cite{abramowitz}:
+\beq
+\begin{aligned}
+&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
+&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
+\end{aligned}
+\feq 
+Taking symmetry conditions in the consideration by leaving only even solution, Eq.
+(\ref{fourier:separation:variables}) has a solution as:
+\beq
+Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
+\feq
+To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
+${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
+found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
+$5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
+\beq
+-C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)} 
+\feq
+One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
+\beq
+\label{coeff:series:parabolic:profile}
+C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)^2\mathrm{d}x}}
+\feq
+Therefore a whole solution can be written as:
+\begin{equation}
+C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
+y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
+\end{equation}
+where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
+between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
+\caption{Comparison between analytical profile and simulations with pressure antibounceback
+conditions. One can see given a low resolution of the profile a nice coincedence.}
+\end{figure}
 
@@
 \section{Lattice Boltzmann Benchmarks}
-\citet{vanbaten-circular} represented a bubble with two hemisperes and a thin film. We want to
-perform the benchmarking against these two representative cases.
-
-\subsection{The radial case}
-We want to examine the bounce-back conditions against the analytical solution. The system can be
-prescribed by the following system of equations:
-\beq
-\begin{aligned}
-&\partial_t C(r,t)=\frac{1}{r}\partial_r r \partial_r C(r,t)\\
-&C(a,t)=C_0,\,C(r,0)=C_{init}
-\end{aligned}
-\feq 
-The solution is represented as \cite{chemical-correlations}:
-\beq
-\frac{C(r,t)-C_{0}}{C_{init}-C_{0})}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
-J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})},
-\feq
-where $\mu_n$ is the $n$-th zero root of the $0$th order Bessel polynomial $J_0(\mu_n)=0$. Some of
-the corresponding roots are as follows: $\mu_1=2.4048$,$\mu_2=5.5201$,$\mu_3=8.6537$,
-$\mu_4=11.7915$,$\mu_5=14.9309$.
-By taking initial concentration to be $0$, one can obtain the following solution:
-\beq
-C(r,t)=C_0 \Biggl(1 - \sum_{n=1}^{\infty}{\frac{2}{\mu_n
-J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})}\Biggr).
-\feq
-
-The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. Some examples for
-different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/cylinder1666.eps}
-\includegraphics[width=0.5\textwidth]{Figures/cylinder0833.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/cylinder0104.eps}
-\includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
-\caption{Profiles for different diffusion parameters. One can see that the diffusion is captured
-accurately in non-dimensional space \label{fig:cylinder:benchmark}.}
-\end{figure}
-
-\subsection{Parabolic profile with velocity zero gradient at the wall}
-In any case here is what we want to solve as the system for :
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
-&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
-\end{aligned}
-\feq
-The system after non-dimensionalization becomes as follows:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H} \Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
-&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
-\end{aligned}
-\feq
-After a change of variables:
-\beq
-\begin{aligned}
-&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
-&\xi=\frac{y}{H}
-\end{aligned}
-\feq
-, the equation with boundary conditions becomes as follows:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
-&C(0,\xi)=C_0\\
-&C(\zeta,0)=C_{wall}\\
-&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
-\end{aligned}
-\feq 
-Still the equation cannot be solved with the separation of variables as it requires the homogenuos boundary conditions.
-Thus, let us introduce the new variable to be $\Theta=C-C_{wall}$.
-The system will be changed but not considerably:
-\beq
-\begin{aligned}
-&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
-&\Theta(0,\xi)=C_0-C_{wall}\\
-&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
-\end{aligned}
-\feq 
-This equation can be solved by separation of variables if the solutions is represented as the multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$.
-The differential equation will become as follows:
-\beq
-\begin{aligned}
-&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
-Y(\xi)}{\mathrm{d}\xi^2}\\
-&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
-\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
-\end{aligned}
-\feq
-The left and right parts depend on different variables. Therefore to be equal to each other both
-parts equal to constant, say $-m^4$. Thus, the separation of the variables leads to two ODE
-equations:
-\begin{equation*}
-\begin{aligned}
-&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
-&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
-\end{aligned}
-\end{equation*}
-The solution of the first equation is the exponential function:
-\beq
-X(\zeta)=\exp(-m^4 \zeta)\\
-\feq
-The solutions of the second equation are two hypergeometric function which can be expressed through
-the Bessel functions \cite{abramowitz}:
-\beq
-\begin{aligned}
-&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-\end{aligned}
-\feq
-The solution is the summation of two functions:
-\begin{equation*}
-Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
-\end{equation*}
-One can find coefficients from the boundary conditions:
-\beq
-\begin{aligned}
-&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
-&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
-&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
-&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
-\end{aligned}
-\feq
-Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
-numerical values:
-$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
-Therefore a solution in a general form is represented as:
-\beq
-\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
-\feq
-To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
-condition:
-\beq
-\Theta(0,\xi)=C_0-C_{wall}=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)}\\
-\feq
-Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
-J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
-\beq
-\begin{aligned}
-&\bigl(C_0-C_{wall}\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
-&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}
-\end{aligned}
-\feq
-Therefore, the overall solution is specified as:
-\beq
-\begin{aligned}
-&C(x,y)=C_{wall}+\sum_{m}{C_m
-\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
-\frac { x }{H}\Bigr)}\\
-&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}
-\end{aligned}
-\feq
-
-\subsection{The parabolic profile mass transfer and comparison}
-The problem we want to address can be formulated through the following PDE:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=0,\, C(x,\pm \delta)=C_s,\, \frac{\partial C}{\partial y }(x,0)=0\\
-&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
-\end{aligned}
-\feq
-The same procedure can be done as in the previous case to redefine variables. After substitution
-the following can be obtained:
-\beq
-\begin{aligned}
-&\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
-\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
-\end{aligned}
-\feq
-After separation of variables, $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$ one can come up with two
-equations:
-\beq
-\label{fourier:separation:variables}
-\begin{aligned}
-&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}+m^4 X(\zeta)=0\\
-&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 (1-\xi^2) Y(\xi)=0
-\end{aligned}
-\feq
-The first equation has a solution:
-\beq
-X(\zeta)=\exp(-m^4 \zeta)
-\feq
-The second equation can be simplified after substitution $\bar{\xi}=m \sqrt{2} \xi$ to the standard
-equation:
-\beq
-Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
-\feq
-The equation above has two solutions via parabolic cylinder functions or through the confluent
-hypergeometric function \cite{abramowitz}:
-\beq
-\begin{aligned}
-&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
-&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
-\end{aligned}
-\feq 
-Taking symmetry conditions in the consideration by leaving only even solution, Eq.
-(\ref{fourier:separation:variables}) has a solution as:
-\beq
-Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
-\feq
-To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
-${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
-found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
-$5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
-\beq
--C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)} 
-\feq
-One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
-\beq
-\label{coeff:series:parabolic:profile}
-C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
-{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
-{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)^2\mathrm{d}x}}
-\feq
-Therefore a whole solution can be written as:
-\begin{equation}
-C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
-y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
-\end{equation}
-where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
-between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
-\caption{Comparison between analytical profile and simulations with pressure antibounceback
-conditions. One can see given a low resolution of the profile a nice coincedence.}
-\end{figure}
 

### 2012-01-31 Text/introduction.tex
More editing.

@@
 \end{equation}
-where the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor  $p_i^{(xy)}=c_{ix} c_{iy}$, the weights
+where $D_{xx,yy,xy}$ are components of the diffusion tensor, $c_e=\frac{D_{xx}+D_{yy}}{2}$, the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor  $p_i^{(xy)}=c_{ix} c_{iy}$, the weights
 $t_i^{(u,m,a)}$ can be chosen based on stability criteria. Though not the best set of weights for
@@
 \beq
-\partial_t C+ \partial_{\alpha} C u_{\alpha}=\partial_{\alpha\beta} D_{\alpha\beta} C,
-\feq
+\partial_t C+ \partial_{\alpha} C u_{\alpha}=\partial_{\alpha\beta} K_{\alpha\beta} C,
+\feq
+where $K_{\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)D_{\alpha\beta}$
 with the
@@
 \end{equation}
-To consider the situation when the resolution is not needed to be changed in $x$ and $y$
-directions, one can obtain that $D_{xx}=D_{yy}$. The cross-diagonal components of the diffusion
-tensor are taken as zeros, i.e. $D_{xy}=0$. In comparison with $D2Q5$ model, with the $D2Q9$ it is
+We want to resolve the isotropic advection-diffusion equation, $D=D_{xx}=D_{yy}$ or $K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components to be zero $D_{xy}=0$.
+In comparison with the $D2Q5$ model, with the $D2Q9$ it is
 possible to cancel the numerical diffusion by the proper choice
-of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$. If one introduces
-
-As far as the simulated diffusion tensor is close to $0$ the stability limits restrict the velocity
-amplitude to be simulated \cite{kuzmin-stability-optimal}. However, particular choice of weights
-can drastically help. Fig. \ref{stability:d2q9} shows the stability limits for D2Q9 with removed
-numerical diffusion and with it for two particular choices of weights.
+of the equilibrium functions, i.e.
+$g_{xy}^{(u)}=g^{(u)}=1$.
+The particular choice of parameters used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$.
+Thus, the diffusion coefficient $K$ is matched through $\omegaminus$, i.e.
+$K=c_e \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
+From hereon, without a loss of generality we refer to diffusion coefficient
+$K$ as $D$.
+Free relaxation parameter $\omegaplus$ can be found through $\Lambda$.
+For particular choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as $\omegaplus=2-\omegaminus$.
+Fig.
+\ref{stability:d2q9} shows the stability limits for the $D2Q9$ model $c_e$ against $U^2=u_x^2+u_y^2$ for two particular choices.
 \begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
-\caption{The non-negativity areas and stable sub-domains of the OTRT schemes ($\Lambda=\frac{1}{4}$)
-are plotted for the $D2Q9$ (standard weights, left) and the $D2Q9$ (uniform weights, right) when the
-numerical diffusion is removed, partially or completely. Two non-negativity areas where all the
-equilibrium populations are positive have curvilinear boundaries: they are smaller when
-$g^{(u)}_{xy}=0$ (yellow) and than when $g^{(u)}_{xy}=1$ (green+yellow). The non-negativity
-condition is required by BGK collision operator. The stable sub-domains for $g^{(u)} = 1,
-g^{(u)}_{xy} = 0$ are small (red+green+yellow) triangles. When the numerical diffusion is removed
-the stable area is bounded by magenta and the (blue) domain above. The proper choice of weights can
-allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1−c_e$ (the
+\caption{The stable sub-domains of the $D2Q9$ schemes ($\Lambda=\frac{1}{4}$)
+are plotted for standard (hydrodynamic) weights (left) and uniform weights (right, not mentioned here) when the
+numerical diffusion is removed, partially or completely.
+For particular choice used in this work (hydrodynamic weights, $c_e=\frac{1}{3}$, left picture), the achieved stable velocity is $u_x^2+u_y^2\leq\frac{2}{3}$.
+The non-negativity of populations (green+yellow) is for BGK stability.
+One can see that the achieved maximum stable velocity is twice smaller $u_x^2+u_y^2\leq \frac{1}{3}$ for the BGK collision operator.The proper choice of weights can
+allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1- c_e$ (the
 uniform weights only).
@@
 \end{figure}
-
-The set of equations (\ref{set:equilibrium:binary}) restores the
-macroscopic
-fluid equations as:
-\begin{equation}
-\begin{aligned}
-&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
-\end{aligned}
-\label{advection:diffusion:equation}
-\end{equation}
-where $D=c_s^2 (\tau-1/2)$ is the viscosity, 
-$P_{\alpha\beta}=\Bigl(p_0-k\phi \Delta \phi -\frac{k}{2}|\nabla \phi|^2\Bigr)\delta_{\alpha\beta}
-+ k \partial_{\alpha} \phi \partial_{\beta} \phi$  \cite{pooley-contact}.
-
-{\color{red}
-While the lattice Boltzmann system has parameters such as the surface tension, the gas and liquid
-viscosities, etc., those parameters are not the representative and
-proportional quantities of the parameters in a physical system. The parameters of the lattice
+{\color{red} Here need to cover boundary conditions}
+
+Note that the parameters of the lattice
 Boltzmann are connected with the physical parameters only through the non-dimensional
-numbers governing the physics of the problem. In our case, these numbers are the capillary number
-and the
-viscosity ratio $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}$, which are
-obtained from the physical world and then matched through the lattice Boltzmann quantities.
+numbers governing the physics of the problem. In our case, this number is the Peclet number, $Pe=\frac{\ububble L}{D}$.
 Therefore, one can substitute any quantity, i.e.
-$U_{\mathrm{bubble}}$, in the physical units or in the lattice Boltzmann units as soon as the
-capillary number is the same in both worlds.}
+$\ububble$ in the lattice Boltzmann units as soon as the
+Peclet number is the matched in physical space and numerical simulations.
+This fact that $\ububble$ can be chosen arbitrarily is extremely useful in the context of numerical simulations, since can increase the time step, or decrease the computational demand by order of magnitude to obtain meaningful results.
+This point will be extensively covered later.
+
+Next section will cover LBM benchmarks for problems that form the mass transfer problem, as mass transfer from the film  and hemispheres.
 
 \subsection{The radial case}
-We want to examine the bounce-back conditions against the analytical solution. The system can be
+The case to be examined here is the mass transfer from the stair-case boundary which represents a circle. It can be
 prescribed by the following system of equations:
@@
 
-The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. Some examples for
+The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$ units. Some examples for
 different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
@@
 \includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
-\caption{Profiles for different diffusion parameters. One can see that the diffusion is captured
-accurately in non-dimensional space \label{fig:cylinder:benchmark}.}
+\caption{Profiles for different diffusion parameters varied with $\omegaminus$. One can see that the diffusion from the non-linear boundaries is captured
+accurately \label{fig:cylinder:benchmark}.}
 \end{figure}
@@
 \subsection{Parabolic profile with velocity zero gradient at the wall}
-In any case here is what we want to solve as the system for :
+The problem is defined in terms of PDE as follows: 
 \beq
@@
 \appendix
+\section{Analytical solution for parabolic profile with zero velocity gradient at $0$}
+The problem is defined in terms of PDE as follows: 
+\beq
+\label{diffusion:zero:gradient:start}
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
+\end{aligned}
+\feq
+The non-dimensional parameters are introduced:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H}
+\Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
+&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
+\end{aligned}
+\feq
+After a change of variables:
+\beq
+\begin{aligned}
+&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
+&\xi=\frac{y}{H}
+\end{aligned}
+\feq
+, Eq. \ref{diffusion:zero:gradient:start} with boundary conditions becomes as follows:
+\beq
+\label{diffusion:zero:gradient:middle}
+\begin{aligned}
+&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
+&C(0,\xi)=C_0\\
+&C(\zeta,0)=C_{wall}\\
+&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
+\end{aligned}
+\feq 
+Still Eq. \ref{diffusion:zero:gradient:middle} cannot be solved with the separation of variables as it requires homogenous
+boundary conditions. Thus, let us introduce the new variable, $\Theta=C-C_{wall}$, which makes the system to be with homogenous boundary conditions:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
+&\Theta(0,\xi)=C_0-C_{wall}\\
+&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
+\end{aligned}
+\feq 
+This equation can be solved by separation of variables if the solutions is represented as the
+multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$:
+\beq
+\begin{aligned}
+&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
+Y(\xi)}{\mathrm{d}\xi^2}\\
+&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
+\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
+\end{aligned}
+\feq
+The left and right parts depend on different variables. Therefore to be equal to each other both
+parts shall equal to constant, say $-m^4$. Thus, the separation of the variables leads to two ODEs:
+\begin{equation*}
+\begin{aligned}
+&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
+&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
+\end{aligned}
+\end{equation*}
+The solution of the first equation is the exponential function:
+\beq
+X(\zeta)=\exp(-m^4 \zeta)\\
+\feq
+The solutions of the second equation are two hypergeometric function which can be expressed through
+the Bessel functions \cite{abramowitz}:
+\beq
+\begin{aligned}
+&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+\end{aligned}
+\feq
+The solution is the summation of two functions:
+\begin{equation*}
+Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
+\end{equation*}
+One can find coefficients from the boundary conditions:
+\beq
+\begin{aligned}
+&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
+&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
+&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
+&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
+\end{aligned}
+\feq
+Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
+numerical values:
+$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
+Therefore, the solution in a general form is represented as:
+\beq
+\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
+\feq
+To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
+condition:
+\beq
+\Theta(0,\xi)=C_0-C_{wall}=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)}\\
+\feq
+Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
+J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
+\beq
+\begin{aligned}
+&\bigl(C_0-C_{wall}\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
+&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+\end{aligned}
+\feq
+Therefore, the overall solution is specified as:
+\beq
+\begin{aligned}
+&C(x,y)=C_{wall}+\sum_{m}{C_m
+\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
+\frac { x }{H}\Bigr)}\\
+&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+\end{aligned}
+\feq
+For the sake of completeness, we list $5$ first coefficients $C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
+\subsection{The parabolic profile mass transfer and comparison}
+The problem we want to address can be formulated through the following PDE:
+\beq
+\begin{aligned}
+&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+&C(0,y)=0,\, C(x,\pm \delta)=C_s,\, \frac{\partial C}{\partial y }(x,0)=0\\
+&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
+\end{aligned}
+\feq
+The same procedure can be done as in the previous case to redefine variables. After substitution
+the following can be obtained:
+\beq
+\begin{aligned}
+&\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
+\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
+\end{aligned}
+\feq
+After separation of variables, $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$ one can come up with two
+equations:
+\beq
+\label{fourier:separation:variables}
+\begin{aligned}
+&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}+m^4 X(\zeta)=0\\
+&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 (1-\xi^2) Y(\xi)=0
+\end{aligned}
+\feq
+The first equation has a solution:
+\beq
+X(\zeta)=\exp(-m^4 \zeta)
+\feq
+The second equation can be simplified after substitution $\bar{\xi}=m \sqrt{2} \xi$ to the standard
+equation:
+\beq
+Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
+\feq
+The equation above has two solutions via parabolic cylinder functions or through the confluent
+hypergeometric function \cite{abramowitz}:
+\beq
+\begin{aligned}
+&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
+&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
+\end{aligned}
+\feq 
+Taking symmetry conditions in the consideration by leaving only even solution, Eq.
+(\ref{fourier:separation:variables}) has a solution as:
+\beq
+Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
+\feq
+To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
+${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
+found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
+$5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
+\beq
+-C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)} 
+\feq
+One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
+\beq
+\label{coeff:series:parabolic:profile}
+C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+x^2\Bigr)^2\mathrm{d}x}}
+\feq
+Therefore a whole solution can be written as:
+\begin{equation}
+C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
+y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
+\end{equation}
+where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
+between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
+\caption{Comparison between analytical profile and simulations with pressure antibounceback
+conditions. One can see given a low resolution of the profile a nice coincedence.}
+\end{figure}
+
 \section{Free surface boundary conditions}

### 2012-01-31 Benchmarks/FullProfile/film.cpp

@@ -124,7 +124,10 @@ void initialize_geometry()
     		rho[counter]=0.0;
     		ux[counter]=0.0;
     		double factor=double(iX-0.5)/double(NX-1.5);
-    		uy[counter]=4.0*u0*(1.0-factor)*factor;
+    		if (iX<NX/2)
+                    uy[counter]=4.0*u0*factor*factor;//4.0*u0*(1.0-factor)*factor;
+                else
+                    uy[counter]=4.0*u0*(1.0-factor)*(1.0-factor);
     		if ((iX==0) || (iX==NX-1))
     			uy[counter]=0.0;
     	}

### 2012-01-31 Python/HydroAlexandra/binary_debug.cpp

@@ -13,13 +13,13 @@ const int NX=100;
 
 int width=10;
 //Time steps
-int N=1000;
-int NOUTPUT=10;
-int NSIGNAL=10;
+int N=200;
+int NOUTPUT=1;
+int NSIGNAL=1;
 
 //Fields and populations
 double f[NX][NY][9], f2[NX][NY][9], g[NX][NY][9], g2[NX][NY][9];
-double rho[NX][NY],ux[NX][NY],uy[NX][NY],phase[NX][NY];
+double rho[NX][NY],ux[NX][NY],uy[NX][NY],phase[NX][NY],laplace[NX][NY];
 
 double force_x=0.0000009;
 double force_y=0.0;
@@ -42,17 +42,17 @@ double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/
 int cx[]={0,1,0,-1,0,1,-1,-1,1};
 int cy[]={0,0,1,0,-1,1,1,-1,-1};
 int compliment[]={0,3,4,1,2,7,8,5,6};
-float wxx[] = {0.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
-float wyy[] = {0.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
-float wxy[] = {0.0, 0.0, 0.0, 0.0, 0.0, 1.0/4.0, -1.0/4.0, 1.0/4.0, -1.0/4.0};
+double wxx[] = {0.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+double wyy[] = {0.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+double wxy[] = {0.0, 0.0, 0.0, 0.0, 0.0, 1.0/4.0, -1.0/4.0, 1.0/4.0, -1.0/4.0};
 
-float gradstencilx[9]={0.0,4.0/12.0,0.0,-4.0/12.0,0.0,
[…]

### 2012-01-31 Python/benchmarks.py

@@ -3,7 +3,7 @@ import numpy
 import pylab
 import scipy.special
 import math
-import matplotlib.tri as tri
+#import matplotlib.tri as tri
 
 coeff=32
 omega=1.0/(0.5+0.5/coeff)
@@ -988,6 +988,106 @@ def final_comparison():
     #ctriang=pylab.tricontour(triang,combined_array[:,2],levels=c_levels,linestyles="dashdot")
     #pylab.legend()    
     #pylab.legend(["Antibb simulations","Analytics"])
+
+def final_comparison_zero_gradient():
+    wmfivetwo=numpy.array([0.20996479709362217, 0.018180897590318785, 0.006919303361557072,0.0037318500468507265, 0.0023673658890243144, \
+                            0.0016504522182779553, 0.0012240656323313512, 0.0009483894730813764, 0.0007590968780885121, \
+                            0.0006230691899630487, 0.000521773141559365, 0.0004441474396258039, 0.00038324243624026397, \
+                            0.00033450473194280715, 0.0002948449039830018, 0.0002621039555673866, 0.0002347343932804438, \
+                            0.00021160239472918784, 0.00019186109713872825,0.00017486713895424112, 0.00016012432055124612, \
+                            0.00014724473213250115, 0.0001359214046973261, 0.00012590872750600792, 0.00011700820222555297, \
+                            0.0001090579288501799, 0.00010192474302362525, 0.00009549826478267914, 0.00008968634379190777, \
+                            0.00008441153749062422, 0.00007960836196536182, 0.00007522112702512196, 0.00007120221729922205, \
+                            0.00006751071698186362, 0.0000641113016165315, 0.000060973339051508034, 0.00005807015547318643, \
+                            0.00005537843263812609, 0.00005287771007323228, 0.00005054997178480274])
+    wmcubic=numpy.array([0.13797406599320738, 0.036854581143239175, 0.02133155594370827, 0.015010686087355087, 0.011579602879061325, 0.009425240459319681, \
+                         0.00794676552988761, 0.006869235708429393, 0.006049027438296182, 0.005403797343711836, 0.004882949141705082, 0.0044536787382349384, \
[…]

### 2012-02-01 Text/introduction.tex
Worked with text.

@@
 &\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
 &U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
@@
 \Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
-&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
+&C(0,y)=C_0,\, C(x,0)=\cstart,\, \frac{\partial C}{\partial y }(x,H)=0\\
 \end{aligned}
@@
 &C(0,\xi)=C_0\\
-&C(\zeta,0)=C_{wall}\\
+&C(\zeta,0)=\cstar\\
 &\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
@@
 Still Eq. \ref{diffusion:zero:gradient:middle} cannot be solved with the separation of variables as it requires homogenous
-boundary conditions. Thus, let us introduce the new variable, $\Theta=C-C_{wall}$, which makes the system to be with homogenous boundary conditions:
+boundary conditions. Thus, let us introduce the new variable, $\Theta=C-\cstar$, which makes the system to be with homogenous boundary conditions:
 \beq
@@
 &\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
-&\Theta(0,\xi)=C_0-C_{wall}\\
+&\Theta(0,\xi)=C_0-\cstar \\
 &\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
@@
 For the sake of completeness, we list $5$ first coefficients $C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
-\subsection{The parabolic profile mass transfer and comparison}
-The problem we want to address can be formulated through the following PDE:
+\subsection{The Poiseuille parabolic profile}
+The problem can be formulated through the following PDE:
 \beq
@@
 The same procedure can be done as in the previous case to redefine variables. After substitution
-the following can be obtained:
+the following equation can be obtained:
 \beq

### 2012-02-02 Text/introduction.tex
Spoilt simulations.. Need to perform new one and finalize.

@@
 \newcommand{\omegaminus}{\omega_{-}}
+\newcommand{\holdup}{\varepsilon_{\mathrm{gas}}}
 
@@
 mass transfer coefficient in the range of capillary number $0.1\leq Ca\leq 1.0$, where the
-hydrodynamic velocity pattern changes. Different boundary conditions, i.e. the periodic boundary
+hydrodynamic velocity pattern changes. The details to obtain velocities and bubble shapes can be
+found in \cite{kuzmin-binary2d}. Fig. \ref{fig:benchmark:hydro} gives the simplified picture for the
+bubble train. Different boundary conditions, i.e. the periodic boundary
 conditions, open boundaries conditions will be examined to determine the volumetric mass transfer
-coefficient. As well, large scale simulations are performed, which simulate from 4 to 10 unit
+coefficient. As well, large scale simulations are performed, which simulate from $4$ to $10$ unit
 cells.
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/benchmark_hydro.eps}
+\caption{Simplified sketch of the bubble train motion. Using periodic conditions for the velocity
+field is natural, but needs validation for the mass transfer. \label{fig:benchmark:hydro}}
+\end{figure}
 
@@
 \subsection{Numerical simulations}
+\label{section:cases}
 To restore the continuous picture one needs to perform a number of bubbles simulations. As we saw
@@
 possible to cancel the numerical diffusion by the proper choice
-of the equilibrium functions, i.e.
-$g_{xy}^{(u)}=g^{(u)}=1$.
-The particular choice of parameters used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$.
-Thus, the diffusion coefficient $K$ is matched through $\omegaminus$, i.e.
-$K=c_e \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
+of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$.  The particular choice of parameters
+used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$. Thus, the diffusion coefficient $K$
+is matched through $\omegaminus$, i.e. $K=c_e
+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
 From hereon, without a loss of generality we refer to diffusion coefficient 
-$K$ as $D$.
-Free relaxation parameter $\omegaplus$ can be found through $\Lambda$.
-For particular choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as $\omegaplus=2-\omegaminus$.
-Fig.
-\ref{stability:d2q9} shows the stability limits for the $D2Q9$ model $c_e$ against $U^2=u_x^2+u_y^2$ for two particular choices.
+$K$ as $D$.  Free relaxation parameter $\omegaplus$ can be found through $\Lambda$. For particular
+choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as
+$\omegaplus=2-\omegaminus$.  Fig. \ref{stability:d2q9} shows the stability limits for the $D2Q9$
+model $c_e$ against $U^2=u_x^2+u_y^2$ for two particular choices.
 \begin{figure}[htb!]
@@
 \end{figure}
-{\color{red} Here need to cover boundary conditions}
+Boundary conditions for the mass transfer used in this work are all of Dirichlet type. We validated
+two types of boundary conditions: Inamuro boundary conditions \cite{inamuro-scalar-boundary} and
+Pressure anti bounce-back boundary conditions \cite{ginzburg-multireflection}. However, the
+simulation results presented in this work are only pressure anti bounce-back due to its simplicity
+to handle any complicated type of boundary:
+\beq
+\label{antibb}
+f^{*}_{B,i}=-f^{*}_{F,\bar{i}} + 2 eq^+(\cstar,\bm{u}),
+\feq
+where $\cstar$ is the concentration to be imposed at the surface, $\bm{u}$ is the surface velocity,
+$i$ is the direction number pointing to the domain (unknown) located at the boundary surface $B$,
+$\bar{i}$ is the direction number opposite to $i$ and is located at the fluid $F$ specifically that
+$B$ is located at the location $F+c_i$.
 
@@
 \subsection{The radial case}
-The case to be examined here is the mass transfer from the stair-case boundary which represents a circle. It can be
+The case to be examined here is the mass transfer from the stair-case boundary forming a circle. It
+can be
 prescribed by the following system of equations:
@@
 \beq
-\frac{C(r,t)-C_{0}}{C_{init}-C_{0})}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
+\frac{C(r,t)-C_{0}}{C_{init}-C_{0}}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
 J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})},
@@
 
-\subsection{Parabolic profile with velocity zero gradient at the wall}
+\subsection{Parabolic profile with the velocity zero gradient at the wall}
 The problem is defined in terms of PDE as follows: 
@@
 &\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,\delta)=0\\
-&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
-\end{aligned}
-\feq
-The system after non-dimensionalization becomes as follows:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H}
-\Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
-&C(0,y)=C_0,\, C(x,0)=C_{wall},\, \frac{\partial C}{\partial y }(x,H)=0\\
-\end{aligned}
-\feq
-After a change of variables:
-\beq
-\begin{aligned}
-&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
-&\xi=\frac{y}{H}
-\end{aligned}
-\feq
-, the equation with boundary conditions becomes as follows:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
-&C(0,\xi)=C_0\\
-&C(\zeta,0)=C_{wall}\\
-&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
-\end{aligned}
-\feq 
-Still the equation cannot be solved with the separation of variables as it requires the homogenuos
-boundary conditions. Thus, let us introduce the new variable to be $\Theta=C-C_{wall}$. The system
-will be changed but not considerably:
-\beq
-\begin{aligned}
-&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
-&\Theta(0,\xi)=C_0-C_{wall}\\
-&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
-\end{aligned}
-\feq 
-This equation can be solved by separation of variables if the solutions is represented as the
-multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$. The differential equation will
-become as follows:
-\beq
-\begin{aligned}
-&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
-Y(\xi)}{\mathrm{d}\xi^2}\\
-&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
-\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
-\end{aligned}
-\feq
-The left and right parts depend on different variables. Therefore to be equal to each other both
-parts equal to constant, say $-m^4$. Thus, the separation of the variables leads to two ODE
-equations:
-\begin{equation*}
-\begin{aligned}
-&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
-&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
-\end{aligned}
-\end{equation*}
-The solution of the first equation is the exponential function:
-\beq
-X(\zeta)=\exp(-m^4 \zeta)\\
-\feq
-The solutions of the second equation are two hypergeometric function which can be expressed through
-the Bessel functions \cite{abramowitz}:
-\beq
-\begin{aligned}
-&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-\end{aligned}
-\feq
-The solution is the summation of two functions:
-\begin{equation*}
-Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
-\end{equation*}
-One can find coefficients from the boundary conditions:
-\beq
-\begin{aligned}
-&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
-&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
-&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
-&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
-\end{aligned}
-\feq
-Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
-numerical values:
-$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
-Therefore a solution in a general form is represented as:
-\beq
-\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
-\feq
-To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
-condition:
-\beq
-\Theta(0,\xi)=C_0-C_{wall}=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)}\\
-\feq
-Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
-J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
-\beq
-\begin{aligned}
-&\bigl(C_0-C_{wall}\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
-&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2.
+\end{aligned}
+\feq
+The procedure to solve this PDE is presented in Appendix \ref{appendix:zero:gradient}:
+\beq
+\label{analytical:solution:zero:gradient}
+\begin{aligned}
+&C(x,y)=\cstar+\sum_{m}{C_m
+\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
+\frac { x }{H}\Bigr)}\\
+&C_m = (C_0-\cstar \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
@@
 \feq
-Therefore, the overall solution is specified as:
-\beq
-\begin{aligned}
-&C(x,y)=C_{wall}+\sum_{m}{C_m
-\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
-\frac { x }{H}\Bigr)}\\
-&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}
-\end{aligned}
-\feq
-
-\subsection{The parabolic profile mass transfer and comparison}
+Fig. \ref{fig:parabolic:zero:gradient} shows the steady-state contours comparison between the
+analytical and the simulation with the Anti Bounce-Back conditions used to impose constant
+concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The grid used in the simulation is
+$80\times1600$. Parameter $\omegaminus=1.8$ implies the diffusion coefficient to be
+$D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)=0.0185$.  
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
+\caption{Comparison with the analytical concentration contours, Eq.
+(\ref{analytical:solution:zero:gradient}), for the diffusion coefficient $D=0.0185$. Simulation was
+performed on grid $80\times 1600$. The constant concentration is imposed with the
+anti bounce-back conditions, Eq.\ref{antibb}. \label{fig:parabolic:zero:gradient}}
+\end{figure}
+
+\subsection{Poiseulle velocity parabolic profile}
 The problem we want to address can be formulated through the following PDE:
@@
 &\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=0,\, C(x,\pm \delta)=C_s,\, \frac{\partial C}{\partial y }(x,0)=0\\
+&C(0,y)=0,\, C(x,\pm \delta)=\cstar,\, \frac{\partial C}{\partial y }(x,0)=0\\
 &U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
@@
 \feq
-The same procedure can be done as in the previous case to redefine variables. After substitution
-the following can be obtained:
-\beq
-\begin{aligned}
-&\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
-\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
-\end{aligned}
-\feq
-After separation of variables, $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$ one can come up with two
-equations:
-\beq
-\label{fourier:separation:variables}
-\begin{aligned}
-&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}+m^4 X(\zeta)=0\\
-&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 (1-\xi^2) Y(\xi)=0
-\end{aligned}
-\feq
-The first equation has a solution:
-\beq
-X(\zeta)=\exp(-m^4 \zeta)
-\feq
-The second equation can be simplified after substitution $\bar{\xi}=m \sqrt{2} \xi$ to the standard
-equation:
-\beq
-Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
-\feq
-The equation above has two solutions via parabolic cylinder functions or through the confluent
-hypergeometric function \cite{abramowitz}:
-\beq
-\begin{aligned}
-&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
-&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
-\end{aligned}
-\feq 
-Taking symmetry conditions in the consideration by leaving only even solution, Eq.
-(\ref{fourier:separation:variables}) has a solution as:
-\beq
-Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
-\feq
-To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
-${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
-found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
-$5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
-\beq
--C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)} 
-\feq
-One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
-\beq
-\label{coeff:series:parabolic:profile}
-C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
-{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
-{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)^2\mathrm{d}x}}
-\feq
-Therefore a whole solution can be written as:
+The procedure to solve this problem is presented in Appendix \ref{appendix:poiseuille} which yields
+the final solution as:
 \begin{equation}
-C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
+C=\cstar-\cstar \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
 y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
@@
 where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
-between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
+between contours of analytical and simulation results is presented in Fig.
+\ref{fig:parabolic:comparison}. Parameters were taken the same as in the previous case: the
+diffusion $D=0.0185$, the grid dimension is $80\times1600$. 
 \begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
-\caption{Comparison between analytical profile and simulations with pressure antibounceback
-conditions. One can see given a low resolution of the profile a nice coincedence.}
-\end{figure}
+\caption{Comparison between the analytical concentration contours and simulations with pressure
+anti bounce-back conditions, Eq. (\ref{antibb}). The parameters were
+taken as $D=0.0185$ and grid $80\times1600$. \label{fig:parabolic:comparison}}
+\end{figure}
+
+After the LBM is validated against the benchmarks relevant for the flow around bubbles, one can
+examine all the cases to calculate the volumetric mass transfer coefficient, Section
+\ref{section:cases}.
 
@@
 \label{sec:numerics}
-The numerical  procedure of studying mass transfer is presented in the following steps:
+The code was utilized to obtain the flow patterns for different capillary numbers
+\cite{kuzmin-binary2d}. Five particular cases were chosen to examine, their results are summarized
+in Table \ref{table:capillary:cases}. 
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|X|}
+\hline
+$Ca$    &$Re$     &$\ububble$ &$\delta$&$\holdup$
+&$\uliq$&$\ugas$&$\lbubble$&$\lslug$\\
+\hline
+$0.097$ &$1.656$  &$0.0055$ &$0.092$ &$0.30$ &$0.0046$&$0.0016$&$5.79$&$9.21$\\ 
+$0.254$ &$4.318$  &$0.0143$ &$0.132$ &$0.28$ &$0.0108$&$0.0041$&$6.12$&$8.88$\\ 
+$0.526$ &$8.938$  &$0.0297$ &$0.157$ &$0.27$ &$0.0209$&$0.0080$&$6.19$&$8.81$\\
+$0.750$ &$12.744$ &$0.0424$ &$0.167$ &$0.25$ &$0.0293$&$0.0107$&$5.96$&$9.04$\\
+$1.040$ &$17.665$ &$0.0588$ &$0.177$ &$0.22$ &$0.0397$&$0.0135$&$5.59$&$9.41$\\
+\hline
+\end{tabularx}
+\caption{Sample results with the binary liquid lattice Boltzmann model \cite{kuzmin-binary2d}. The
+following notations are used: the capillary number $Ca=\frac{\ububble L}{\rho \nu}$, $\delta$ is the
+non-dimensional film thickness, $\uliq$ is the superficial liquid velocity, $\ugas$ is the
+superficial gas velocity. One can see the sketch of the simulation in Fig.
+\ref{fig:benchmark:hydro}. \label{table:capillary:cases}}
+\end{table}
+One can check that velocities in Table \ref{table:capillary:cases} are small. It means that to
+match large Peclet numbers, $Pe=\frac{\ububble L}{D}$, usually seen in experiments to measure
+the mass transfer coefficient, one needs to decrease
+$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. However, for parameters
+$\omegaminus \approx 0.5$ the stability of the lattice Boltzmann method drastically decreases
+\cite{kuzmin-d1q3}. On the other hand, one iteration in the lattice Boltzmann system corresponds
+to the time in the physical domain as $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
+x}{U_{\mathrm{bubble,phys}}}$. This time is proportional to the velocity of the $U_{\mathrm{LB}}$
+and the typical number of simulation steps to obtain necessary number with given velocities for
+$Ca<0.2$ is of the order of a few millions. Thus, one wants to increase the available velocity
+while keeping the Peclet number the same. This helps to stability of the method as well, since
+$\omegaminus$ is not close to its stability limit $\omegaminus=0.5$.
+
+Given all the considerations above, one needs to approach the mass transfer in the following
+steps:
 \begin{description}
- \item[Flow field] The hydrodynamics for the bubble motion in the periodic domain is obtained
-according to the work \cite{kuzmin-binary2d}. The grid resolution is taken to insure grid
+ \item[Flow field] Given the capillary number $Ca$, one needs to obtain hydrodynamic fields around
+the bubble using the binary liquid lattice Boltzmann model according to work
+\cite{kuzmin-binary2d}. Periodic boundary conditions are used. The grid used in this work is
+$202\times 3000$ which corresponds to fluid domain size $200\times3000$. The grid resolution is
+taken to insure grid
 independency of results.  
  \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
-are conducted in the moving
-reference frame with the bubble. Then the bubble stands still and the flow is coming around the
-bubble. We impose a steady concentration of solutant on the surface of the bubble.
-\item[Mass transfer] One needs not only perform a Galilean transformation to the reference
-frame moving with the bubble but also to
-transfer the bubble to the inlet condition. This can insure that the studied phenomenon is a liquid
-slug. 
-\end{description}
-
-\section{Mass transfer}
-The mass transfer is characterized by non-dimensional numbers as Schmidt number (viscous diffusion
+are conducted in the moving reference frame with the bubble. Then the bubble stands still and the
+flow is coming around the
+bubble. We impose a steady concentration of the trace on the surface
+of the bubble with the anti bounce-back condition, Eq. (\ref{antibb}).
+ \item[Velocity improvement] Due to necessity to increase velocity one can scale the velocity to
+perform fast simulations, one needs to improve velocity. This issue arises because of the
+multiphase model used in simulations.The binary liquid lattice Boltzmann model is the diffusive
+interface model. Thus, the
+transition between gas and liquid is the continuous function. We obtain the bubble shape according
+to the phase indicator $\phi$ as used in \cite{kuzmin-binary2d}, say $\phi<0$. The velocity of the
+bubble is calculated as the bubble tip velocity. Because of the highly non-linear diffusive
+interface model the shape of the bubble is determined within accuracy of one grid node, as well
+there is the error in determination in the bubble velocity. Though these errors are small, however
+there is small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
+\cite{kuzmin-binary2d} where some streamlines are penetrating a bubble surface a bit.
+This small velocity is amplified upon the velocity scaling and is inconsistent with the
+advection-diffusion equation.
+
+Thus, before performing the mass transfer simulations one additional one-component hydrodynamic
+simulation is performed. A special additional free-surface solver was developed in order to dispose
+the normal to surface velocity components. We take results from the multiphase simulations, extract
+bubble shape using the phase indicator $\phi<0$, approximate the bubble shape by the stair-case
+line. Then,the obtained bubble velocity is imposed on walls. This corresponds to conducting
+simulation in the reference frame moving with the bubble. In addition, the free-slip boundary
+condition on the bubble surface is imposed. Appendix \ref{appendix-free-surface} covers the simple
+free-slip boundary conditions drastically improving velocity patterns. The system is tterate until a
+steady state is reached. Note, that these type of simulations are much faster than original
+multiphase simulations. As the output all the non-zero velocity components perpendicular to the
+bubble surface are completely illuminated. We compared original multiphase simulations with
+one-component free-slip simulations. All quantities as superficial slug and bubble velocities are
+within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. This small trick helps to
+make mass transfer simulations stable and faster, since the velocity scaling can be done easier. One
+can see in Fig. \ref{fig:free:surface} two streamlines profiles for $Ca=0.097$  and $Ca=1.040$.
+\begin{figure}[htb!]
+\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca0097.eps}\\
+\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca1040.eps}
+\caption{The streamlines patterns produced by the free-surface solver with simplistic approximation
+of the free-slip bubble surface, see Appendix \ref{appendix-free-surface}. Two completely different
+velocity patterns are covered, $Ca=0.097$ (top) and $Ca=1.040$ (bottom).
+\label{fig:streamlines:tweaked:velocity}}
+\end{figure}
+
+\item[Mass transfer] After improved velocity profiles are obtained one can perform any mass
+transfer simulations with different boundary conditions as covered in Section \ref{section:cases}.
+For this purpose one needs to match the Peclet number $Pe$ from experiments. Note that we
+specifically separated the hydrodynamic problem from the mass transfer problem. When one wants to
+solve these simultaneous problems, then one needs to match all the non-dimensional parameters, as
+the capillary number (viscous forces over surface tension), the Schmidt number (viscous diffusion
 rate over mass diffusion rate), the Peclet number (convection over diffusion) and the Sherwood
@@
 \begin{aligned}
-&Pe=\frac{U L}{D}\\
+&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
+&Pe=\frac{\ububble L}{D}\\
 &Sh=\frac{K L}{D}\\
-&Sc=\frac{\nu}{D}\\
+&Sc=\frac{\nu}{D}.
 \end{aligned}
 \end{equation}
-
-As far as the lattice Boltzmann method operates only in the non-dimensional space, one needs to
-match the non-dimensional lattice Boltzmann parameters with non-dimensional physical parameters.
-Therefore, one needs to form non-dimensional numbers from the physical parameters. One of the
-particular experiment examples is the
-work by \citet{bercic-mass} who used the methane dissolution to characterize the mass transfer for
-bubble train flow.
-
-In what follows we will perform the matching of obtained hydrodynamics results
-\cite{kuzmin-binary2d} with physical ones from experiment of \citet{bercic-mass}. The diffusion
-coefficient of the methane under standard conditions \cite{methane-properties} is
-$1.84\times 10^{-5} \mathrm{cm}^2/\mathrm{s}$. The diameters of capillaries in the experiment were
-as $1.5$, $2.5$ and
-$3.1\,\mathrm{mm}$. For simplicity reasons we will choose the diameter of capillary as $1.5\,
-\mathrm{mm}$. 
-The non-dimensional parameters obtained from the hydrodynamics lattice Boltzmann simulations are
-as:
-\begin{equation}
-\begin{aligned}
-&Ca=\frac{U \mu_{\mathrm{liq}}}{\gamma}\\
-&Re=\frac{\rho_{\mathrm{liq}} U L}{\mu_{\mathrm{liq}}}.
-\end{aligned}
-\end{equation}
-Given some physical characteristics as the liquid density and the channel length,
-one can obtain the physical velocity obtained from non-dimensional numbers:
-\begin{equation}
-\begin{aligned}
-Ca\cdot Re= \frac{\rho_{\mathrm{liq}} U^2 L}{\gamma}\\
-U=\sqrt{\frac{Ca\,Re\,\gamma}{\rho_{\mathrm{liq}}L}}
-\end{aligned}
-\end{equation}
-
-Assuming that the surface tension of water is $0.0728\,\mathrm{N/m}$ (methane exhibits the same
-trend \cite{schmidt-methane}), the density is       
-$1000\,\mathrm{kg/m^3}$, the hydraulic diameter of the channel to be $1.5\,\mathrm{mm}$ one can
-calculate the physical velocity of the bubble.
-Table \ref{table:twod:simulations} represents lattice Boltzmann simulations results and their
-physical equivalents for the grid $202\times 3002$. One can see
-that velocity is quite reasonable
-as \citet{bercic-mass} declared that experiments were conducted for velocities in the ranges of
-$0.01$ to $0.4\,\mathrm{m}/\mathrm{s}$. 
-\begin{table}
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
-\hline
-$Ca$    &$Re$     &$U_{LB}$ &$\delta$&$\varepsilon_{\mathrm{gas}}$
-&$U_{\mathrm{phys}}, \mathrm{m/s}$\\
-\hline
-$0.026$ &$0.449$  &$0.0014$ &$0.040$ &$0.306$ &$0.023$   \\ 
-$0.047$ &$0.820$  &$0.0027$ &$0.058$ &$0.293$ &$0.043$   \\ 
-$0.080$ &$1.378$  &$0.0045$ &$0.085$ &$0.280$ &$0.073$ \\
-$0.065$ &$1.126$  &$0.0037$ &$0.076$ &$0.266$ &$0.059$      \\
-$0.222$ &$3.807$  &$0.0125$ &$0.122$ &$0.253$ &$0.202$  \\
-$0.479$ &$8.222$  &$0.0271$ &$0.151$ &$0.249$ &$0.437$  \\
-$0.736$ &$12.617$ &$0.0416$ &$0.164$ &$0.236$ &$0.671$  \\ 
-$0.989$ &$16.960$ &$0.0559$ &$0.172$ &$0.230$ &$0.902$  \\
+\end{description}
+
+\section{Keeping Peclet}
+This section addresses the performance of the simulations. The ulimate goal is to increase
+velocity at least by several orders while keeping dimensionless parameters the same. Increasing
+velocity can result in simulations of a lot of unit cells required for continuous picture
+representation.
+
+Only nondimensional parameter Peclet number governs the advection-diffusion equation:
+\beq
+Pe=\frac{U_{bubble} N_y}{D},
+\feq
+where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
+means one needs to increase the diffusion coefficient as well. The runs were made with
+velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
+its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
+boundary conditions were used and mass transfer coefficient was calculated according to Eq.
+(\ref{main:simulation:equation}).
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+Scale&$U_{bubble}$&Time Iterations&$C_{aver}$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.097$}\\
+\hline
+$2$ &$0.011$&$400000$&$0.318$\\
+$4$ &$0.023$&$200000$&$0.319$\\
+$8$ &$0.044$&$100000$&$0.320$\\
+$10$&$0.055$&$80000$ &$0.321$\\
+$20$&$0.11 $&$40000$ &$0.324$\\
+$40$&$0.22 $&$20000$ &$0.328$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.254$}\\
+\hline
+$2$& $0.0286$&$800000$&$0.6533$\\
+$4$& $0.0572$&$400000$&$0.6591$\\
+$8$& $0.1144$&$200000$&$0.6692$\\
+$10$&$0.1430$&$160000$&$0.6734$\\
+$20$&$0.2860$&$80000$ &$0.6894$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.526$}\\
+\hline
+$2$&$0.0594$&$200000$&$0.3271$\\
+$4$&$0.1188$&$100000$&$0.3315$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=0.750$}\\
+\hline
+$2$&$0.0848$&$200000$&$0.3489$\\
+\hline
+\multicolumn{4}{c}{}\\
+\multicolumn{4}{c}{$Ca=1.040$}\\
+\hline
+$2$&$0.1176$&$200000$&$0.3675$\\
 \hline
 \end{tabularx}
-\caption{Two-dimensional simulations for different
-capillary numbers. \label{table:twod:simulations}}
+\caption{Scaling Peclet table. One can see that scaling is pretty successful. One can see as well
+that the stability limit is approximately around $U_{bubble}=0.1$. That can give us an idea of
+scale of simulations. \label{table:scaling:peclet}}
 \end{table}
 
-\section{Lattice Boltzmann implementation}
-For the lattice Boltzmann implementation we took $\omega=1.99$ which results in the following
-lattice Boltzmann diffusivity parameter:
-\begin{equation}
-\begin{aligned}
-&D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)\\
-&D=0.0008375
-\end{aligned}
-\end{equation}
-In terms of the Schmidt number (taking the lattice Boltzmann liquid viscosity in former simulations
-as $\frac{2}{3}$) that
-can result in:
-\begin{equation}
-\begin{aligned}
-&Sc=\frac{\nu_{\mathrm{liq}}}{D}\\
-&Sc=796\\
-\end{aligned}
-\end{equation}
-Taking the water dynamic viscosity as $8.9 \times 10^{-4}\,\mathrm{Pa\cdot s}$ or kinematic
-viscosity as $8.9 \times
-10^{-7} \,\mathrm{m^2/s}$ and the Schmidt number as $796$ results in the following physical
-diffusion coefficient:
-\begin{equation}
-D=1.118\times 10^{-5}\,\mathrm{cm^2/s},
-\end{equation}
-which is less than the diffusivity of the methane $1.84\times 10^{-5}\,\mathrm{cm^2/s}$ but is
-physical. After calculation of physical parameters one can calculate correlations indicated in
-Section \ref{sec:correlations} for mass transfer. Table \ref{table:lengths} presents extraction
-from the lattice Boltzmann simulation necessary to calculate mass transfer calculations.
-For the two-dimensional case parameter  $a$ is defined as:
-\begin{equation}
-a = \frac{\text{bubble perimeter}}{\text{cell area}}.
-\end{equation}
-For the height of the channel to be $H=1.5 \times 10^{-3}\,\mathrm{m}$, parameters $a$ are
-presented in Table \ref{table:lengths}. 
-\begin{table}
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
-\hline
-$Ca$&Bubble length& Slug Length&
-$U_{\mathrm{gas}},\,\mathrm{m/s}$&$U_{\mathrm{liq}},\,\mathrm{m/s}$&$a,\,\mathrm{m^{-1}}$\\
-\hline
-$0.026$&$5.225$&$9.775$ &$0.0070$ &$0.0209$&$510.77$\\
-$0.047$&$5.22$ &$9.78$  &$0.0126$ &$0.0379$&$508.62$\\
-$0.080$&$5.215$&$9.785$ &$0.0204$ &$0.0615$&$506.53$\\
-$0.065$&$4.965$&$10.035$&$0.0157$ &$0.0504$&$482.84$\\
-$0.222$&$5.25$ &$9.75$  &$0.0511$ &$0.1560$&$505.06$\\
-$0.479$&$5.565$&$9.435$ &$0.1089$ &$0.3155$&$530.37$\\
-$0.736$&$5.51$ &$9.49$  &$0.1584$ &$0.4677$&$525.38$\\
-$0.989$&$5.505$&$9.495$ &$0.2074$ &$0.6190$&$526.80$\\
-\hline
-\end{tabularx}
-\caption{The nondimensional (scaled to the height of the channel) lengths for the same
-lattice Boltzmann simulations as in Table \ref{table:twod:simulations}. As well superficial
-gas and liquid velocities are presented. \label{table:lengths}} 
-\end{table}
-
-The literature correlations of mass transfer dependence on the bubble velocities are presented in
-Fig. \ref{fig:mass:transfer:theoretical}. Note, that the correlations presented in
-Fig. \ref{fig:mass:transfer:theoretical} are used primarily for circular capillaries
-(\citeauthor{vanbaten-circular,bercic-mass}) and for square capillaries (\citeauthor{yue-mass}). We
-adapt these results for flow between parallel plates by using hydraulic
-diameter \cite{bercic-mass} which can be calculated as:
-\begin{equation}
-d_h = \lim_{W\to\infty}\frac{4A}{P}=\lim_{W\to\infty}\frac{4 W\,H}{2(W+H)}=2 H.
-\end{equation}
-For comparison reasons we derived in Section \ref{mass:transfer:correlation} the correlation for the
-flow between plates, see Fig. \ref{fig:mass:transfer:theoretical}. One can see that the
-difference is negligible.
-
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/theoretical_correlations.eps}\\
-%\includegraphics[width=\textwidth]{Figures/theoretical_correlations_without_hydraulic.eps}\\
-\caption{The literature correlations by various authors.\label{fig:mass:transfer:theoretical}}
-\end{figure}
-
-The volumetric mass transfer coefficient is calculated according to the work of
-\citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
-average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$)
-at time
-$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$ {\color{red} (In this particular
-moment I don't know whether to take the volume of the whole domain or
-just the liquid phase. I will go for whole domain.)}. Then the volumetric mass transfer
-coefficient is calculated as \cite{vanbaten-circular}:
-\begin{equation}
-\label{main:simulation:equation}
-k_L a=\frac{\text{Flux}}{C_s-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell volume}},
-\end{equation}
-where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
-{\color{red} Do not understand why we need this ratio bubble surface area/unit cell volume. In this
-case the dimensional units do not coincide. In the calculations I will avoid it until further
-clearance.} The overall concentration in the lattice Boltzmann system is prescribed as:
-\begin{equation}
-C_{overall}=\frac{\sum{c_i}}{N_x \, (N_y-2)}.
-\end{equation}
-
-To properly do
-non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
-inside the lattice Botlzmann system. The time conversion can be easily obtained:
-\begin{equation}
-\begin{aligned}
-&U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
-&\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
-&\Delta t=\frac{1.5\,\mathrm{mm}}{200} \frac{0.0559}{0.902\,\mathrm{m/s}}=4.64\times
-10^{-7}\,\mathrm{s} 
-\end{aligned}
-\end{equation}
-
-The bubble surface length is the perimeter of the bubble in two-dimensional space and it is
-calculated with the extraction of the bubble contour and representing it with the polygon. After
-that the calculated perimeter is the effective summation of line lengths and can be represented as:
-\begin{equation}
-P=\sum_i{\sqrt{(x2_i-x1_i)^2+(y2_i-y1_i)^2}},
-\end{equation}
-where the index $i$ represents the polyline consisting of two points $(x1,y1)$ and $(x2,y2)$.
-%The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
-%Table \ref{table:volumetric:coefficients}.
+The corresponding to Table \ref{table:scaling:peclet} contour profiles for different scalings are
+presented in Fig. \ref{fig:contours:scaling:peclet}.
+\begin{figure}[htb!]
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca026.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca054.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca05.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca097.eps}\\
+\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca14.eps}\\
+\caption{Contours for scaling Peclet number.\label{fig:contours:scaling:peclet}}
+\end{figure}
 
@@
 
-\section{Two unit cells results}
-As far as one needs to restore the continuous picture one needs to make a simulation of a few
-cells. This section provides results for two units. The results are summarized in Table
-\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
-\caption{Overall mass transfer coefficient (top left), first part (top
-right), second part (bottom left).\label{fig:results:double}}
-\end{figure}
-\begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|}
-\hline
-$0.7392$&$1.0564$&$0.4220$\\
-$1.8993$&$2.8301$&$0.9684$\\
-$3.3925$&$4.7522$&$2.0328$\\
-$3.7870$&$4.5615$&$3.0125$\\
-\hline
-\end{tabularx}
-\caption{Simulation results for two units. \label{table:two_units}}
-\end{table}
-
-\section{Three unit cells results}
-Three unit cells results are subdivided into three cells. We calculate the mass transfer
-coefficients over the each cell, Fig. \ref{fig:results:triple}. The averaged coefficients  after
-$3,300,000$ time steps are represented in Table. \ref{table:three_units}. The most important thing
-is to look at the third column of the Table \ref{table:three_units} or for at the Fig.
-\ref{fig:results:triple} (bottom left). The coefficients for capillary numbers $0.026$ and $0.047$
-are almost zero which indicates that the concentration at the first part of the channel is almost
-the same as the second part. Thus, there is not enough time steps to transfer concentrate among
-whole the channel (plug flow). In comparison with the first two values for capillary number $0.080$
-the trend is different and concentrate is spread over the channel. However, the drop coefficients
-are still inconsistents. Though last part and the second part exhibit close values (needed to tell
-what is the real mass transfer coefficient). Overall, more time steps are needed.
-$0.080$
-\begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|}
-\hline
-0.4928&1.0564&2.8472e-05&0.4219\\
-1.2662&2.8301&0.0146&0.9537\\
-2.3110&4.7532&1.0665&1.1133\\
-\hline
-\end{tabularx}
-\caption{Simulation results for three units.\label{table:three_units}}
-\end{table}
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/steady_triple_overall.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_triple_first.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_triple_second.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_triple_third.eps}\\
-\caption{The mass transfer coefficient over time in different locations: overall mass transfer
-coefficient (top left), first part (top right), second part (bottom left), third part (bottom
-right). \label{fig:results:triple}}
-\end{figure}
-
-{\color{red} Probably we can consider that for capillary number less than $0.08$ the mass transfer
-is a plug flow mass transfer, keeping only the impact from caps.}
+\section{Open boundary conditions}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0097.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0254.eps}
+\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0254.eps}\\
+\caption{Open boundary conditions. \label{fig:open:boundary:jos}}
+\end{figure}
+
+\section{Symmetric boundary conditions}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0097.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0254.eps}
+\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0254.eps}\\
+\caption{Symmetric boundary conditions. \label{fig:open:boundary:sym}}
+\end{figure}
 
 \section{Four unit cells results}
-Four unit cells results are subdivided into four cells. The results are presented in Fig.
-\ref{fig:results:quadro}. While we expect certain deviations for the first and the last part, but
-surprisingly the concentration difference over the third segment tends to be zero. That means not
-enough time steps are performed. The results over segments are summarized in Table
-\ref{table:four_units}.
-\begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
-\hline
-$Ca$   &Overall  &I       &II      &III     &IV\\
-$0.080$&$1.7359$ &$4.7533$&$1.0665$&$0.1088$&$1.0150$\\
-$0.065$&$1.9260$ &$4.5620$&$0.9113$&$0.0619$&$2.1689$\\
-\hline
-\end{tabularx}
-\caption{Simulation results for mass transfer coefficients for 4 unit cells
-domain.\label{table:four_units}}
-\end{table}
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_overall.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_first.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_second.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_third.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_fourth.eps}\\
-\caption{The mass transfer coefficient over time in different locations: overall mass transfer
-coefficient (top left), first part (top right), second part (middle left), third part (middle
-right) and fourth part (bottom left). \label{fig:results:quadro}}
-\end{figure}
-
 From Figs. \ref{fig:results:triple} and \ref{fig:results:quadro} one can see that $4,000,000$ time
@@
 \end{table}
-
-\section{Lattice Boltzmann Benchmarks}
-
-\section{Tweaking velocity}
-The reason to tweak velocity is that the velocity field because of the highly nonlinear binary liquid lattice Boltzmann model do not have nice velocity profile, since some streamlines penetrate the bubble in the reference frame of the bubble.
-Therefore there exists a normal to the surface of the bubble velocity component which destroys right away the advection-diffusion results.
-Therefore, a special additional free-surface solver was developed in order to dispose the vertical components.
-
-The solver was through consequent steps. First, we extracted the velocity profiles from the
-original binary-liquid simulations. Then, we imposed walls with velocity of the bubble, so the
-bubble stays still. At the surface of the bubble the free boundary conditions were imposed, see
-\ref{appendix-free-surface}. One of the examples is shown in Fig.
-\ref{fig:streamlines:tweaked:velocity}. Among all the simulations the bulk velocity in film and the
-slug are different of no more than $7$ percent. {\color{red} Add some pictures froms streamlines.py
-if it's required to show more.}
-\begin{figure}
-\includegraphics[angle=90,width=\textwidth]{Figures/original.eps}\\
-\includegraphics[angle=90,width=\textwidth]{Figures/performed.eps}\\
-\caption{The comparison between original velocity fields and velocity fields obtained from free surface solver. \label{fig:streamlines:tweaked:velocity}}
-\end{figure}
-
-\section{Keeping Peclet}
-This section addresses the performance of the simulations. The ulimate goal is to increase
-velocity at least by several orders while keeping dimensionless parameters the same. Increasing
-velocity can result in simulations of a lot of unit cells required for continuous picture
-representation.
-
-Only nondimensional parameter Peclet number governs the advection-diffusion equation:
-\beq
-Pe=\frac{U_{bubble} N_y}{D},
-\feq
-where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
-means one needs to increase the diffusion coefficient as well. The runs were made with
-velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
-its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
-boundary conditions were used and mass transfer coefficient was calculated according to Eq.
-(\ref{main:simulation:equation}).
-\begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|}
-\hline
-Scale&$U_{bubble}$&Time Iterations&$C_{aver}$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.097$}\\
-\hline
-$2$ &$0.011$&$400000$&$0.318$\\
-$4$ &$0.023$&$200000$&$0.319$\\
-$8$ &$0.044$&$100000$&$0.320$\\
-$10$&$0.055$&$80000$ &$0.321$\\
-$20$&$0.11 $&$40000$ &$0.324$\\
-$40$&$0.22 $&$20000$ &$0.328$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.254$}\\
-\hline
-$2$& $0.0286$&$800000$&$0.6533$\\
-$4$& $0.0572$&$400000$&$0.6591$\\
-$8$& $0.1144$&$200000$&$0.6692$\\
-$10$&$0.1430$&$160000$&$0.6734$\\
-$20$&$0.2860$&$80000$ &$0.6894$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.526$}\\
-\hline
-$2$&$0.0594$&$200000$&$0.3271$\\
-$4$&$0.1188$&$100000$&$0.3315$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.750$}\\
-\hline
-$2$&$0.0848$&$200000$&$0.3489$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=1.040$}\\
-\hline
-$2$&$0.1176$&$200000$&$0.3675$\\
-\hline
-\end{tabularx}
-\caption{Scaling Peclet table. One can see that scaling is pretty successful. One can see as well
-that the stability limit is approximately around $U_{bubble}=0.1$. That can give us an idea of
-scale of simulations. \label{table:scaling:peclet}}
-\end{table}
-
-The corresponding to Table \ref{table:scaling:peclet} contour profiles for different scalings are
-presented in Fig. \ref{fig:contours:scaling:peclet}.
-\begin{figure}
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca026.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca054.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca05.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca097.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca14.eps}\\
-\caption{Contours for scaling Peclet number.\label{fig:contours:scaling:peclet}}
-\end{figure}
 
@@
 &C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
-k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
+&k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
 \feqal
@@
 
-\section{Open boundary conditions}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0097.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0254.eps}
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0254.eps}\\
-\caption{Open boundary conditions. \label{fig:open:boundary:jos}}
-\end{figure}
-
-\section{Symmetric boundary conditions}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0097.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0254.eps}
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0254.eps}\\
-\caption{Symmetric boundary conditions. \label{fig:open:boundary:sym}}
-\end{figure}
+\section{Scaling for $Ca=1.040$}
 
@@
 \section{Analytical solution for parabolic profile with zero velocity gradient at $0$}
+\label{appendix:zero:gradient}
 The problem is defined in terms of PDE as follows: 
@@
 \Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
-&C(0,y)=C_0,\, C(x,0)=\cstart,\, \frac{\partial C}{\partial y }(x,H)=0\\
+&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,H)=0\\
 \end{aligned}
@@
 &\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
-&\xi=\frac{y}{H}
-\end{aligned}
-\feq
-, Eq. \ref{diffusion:zero:gradient:start} with boundary conditions becomes as follows:
+&\xi=\frac{y}{H},
+\end{aligned}
+\feq 
+Eq. \ref{diffusion:zero:gradient:start} with boundary conditions becomes as follows:
 \beq
@@
 \beq
-\Theta(0,\xi)=C_0-C_{wall}=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
+\Theta(0,\xi)=C_0-\cstar=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)}\\
@@
 \begin{aligned}
-&\bigl(C_0-C_{wall}\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+&\bigl(C_0-\cstar\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)\mathrm{d}\xi}\\
-&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+&C_m = (C_0-\cstar ) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
@@
 \begin{aligned}
-&C(x,y)=C_{wall}+\sum_{m}{C_m
+&C(x,y)=\cstar+\sum_{m}{C_m
 \sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
 \frac { x }{H}\Bigr)}\\
-&C_m = (C_0-C_{wall}) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+&C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
@@
 \feq
-For the sake of completeness, we list $5$ first coefficients $C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
+For the sake of completeness, we list $5$ first coefficients for a case $C_0=0$ and $\cstar=1$:
+$C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
 \subsection{The Poiseuille parabolic profile}
-The problem can be formulated through the following PDE:
+\label{appendix:poiseuille}
+Close to the previous example but with a different velocity profile, the benchmark can be
+formulated through the following PDE:
 \beq
@@
 &\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
-\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
+&\Theta(\zeta,\xi)=C-\cstar\,\Theta(0,\xi)=-\cstar\,\Theta(0,\pm 1)=0
 \end{aligned}
@@
 \beq
-\label{fourier:separation:variables}
+\label{fourier:separation:variables:parabolic}
 \begin{aligned}
@@
 Taking symmetry conditions in the consideration by leaving only even solution, Eq.
-(\ref{fourier:separation:variables}) has a solution as:
+(\ref{fourier:separation:variables:parabolic}) has a solution as:
 \beq
@@
 \beq
--C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+-\cstar=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
 x^2\Bigr)} 
@@
 One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
+x^2\Bigr)$ and through orthoganality (Stourm-Liouiville theorem) obtain coefficients:
 \beq
 \label{coeff:series:parabolic:profile}
-C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+C_m=-\cstar \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
 {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
@@
 \begin{equation}
-C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
+C=\cstar-\cstar \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
 y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
 \end{equation}
-where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
-between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
-\caption{Comparison between analytical profile and simulations with pressure antibounceback
-conditions. One can see given a low resolution of the profile a nice coincedence.}
-\end{figure}
+where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). For the case
+$\cstar$, first ten coefficients equal to  $1.2008$, $-0.2991$, $0.1608$, $-0.1074$, $0.0796$,
+$-0.0627$, $0.0515$, $-0.0435$, $0.0375$, $-0.0329$.
 
@@
 Because the boundary is the staircase approximation, one can find the normal to the boundary which
-is always located by the angle of multiple of $45$, see Fig. \ref{fig:free:surface}. Imposing the
+is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}. This
+can be done automatically by the` simple coding. Imposing the
 symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{Figures/free_surface.eps}
-\caption{Free-surface boundary condition represented in the lattice Boltzmann. By crosses we outline boundary nodes, by circle the fluid node is outlined. \label{fig:free:surface}}
+\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
+\caption{Free-surface boundary condition represented in the lattice Boltzmann. By crosses we outline
+boundary nodes, by circle the fluid node is outlined. Populations at the corner boundary nodes are
+essentially the population of the fluid node, but in the certain order. \label{fig:free:surface}}
 \end{figure}
@@
 \bibliography{paper}
-
 \end{document}

### 2012-02-02 Python/IncreasingDiffusion/copy_from_bugaboo.py

@@ -1,0 +1,51 @@
+#import numpy
+import os
+import subprocess
+
+def run_simulations(main_dir_name):
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    units=[4,6,8]
+    velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
+    scales=[0.3,0.5,1,2,4,6,8,10,15,20]    
+    scale_str=["03","05","1","2","4","6","8","10","15","20"]
+    scales_diff=[2,5,10,20,40]
+    counter=capillary_str.index(main_dir_name)
+    
+    #for counter,dir_temp in enumerate(capillary_str):
+    os.chdir(main_dir_name)
+    
+    flag=False
+    for scale_counter,scale in enumerate(scales):
+        if velocities[counter]*scale>0.12:
+            scale3=scales[scale_counter-1]
+            scale2=scales[scale_counter-2]
+            scale1=scales[scale_counter-3]
+            flag=True 
+            break
+    if not flag:
+        scale1=scales[-3]
+        scale2=scales[-2]
+        scale3=scales[-1] 
+    print scale1,scale2,scale3,velocities[counter] 
+    for scale in [scale2,scale3]:
+        dir_name=scale_str[scales.index(scale)]
+        subprocess.call(['mkdir','-p',dir_name])
+        os.chdir(dir_name)
+        for scale_diff in scales_diff:
+            subprocess.call(['mkdir','-p',str(scale_diff)])
+            os.chdir(str(scale_diff))
+            
+            for unit in units:
+                subprocess.call(['mkdir','-p',str(unit)])
+                os.chdir(str(unit))            
+                subprocess.call(['scp','shurik@bugaboo.westgrid.ca:/home/shurik/IncreasingDiffusion/'+main_dir_name+"/"+str(scale)+"/"+str(scale_diff)+"/"+str(unit)+"/"+'density*.dat',"."])
+                subprocess.call(['scp','shurik@bugaboo.westgrid.ca:/home/shurik/IncreasingDiffusion/'+main_dir_name+"/"+str(scale)+"/"+str(scale_diff)+"/"+str(unit)+"/"+"concentration.dat","."])
+ 
+                os.chdir("..")
+            os.chdir("..")
+        os.chdir("..")
+    os.chdir("..")
+
+if __name__=="__main__":
+    #modify_file()
+    run_simulations("84")

### 2012-02-02 Python/peclet.py

@@ -398,6 +398,104 @@ def check_average_sym_concentration(dir_name,scales):
     pylab.savefig("sym_aver_conc_scale_ca"+str(capillary)[0:1]+str(capillary)[2:]+".eps",format="EPS",dpi=300)
 
 
+def give_overall_characteristics():
+    capillary_str=["9","21","42","60","84"]
+    
+    capillaries_orig=[]
+    reynolds_orig=[]
+    velocities_orig=[]
+    holdups_orig=[]
+    bubble_lengths_orig=[]
+    slug_lengths_orig=[]
+    widths_orig=[]
+    gas_velocities_orig=[]
+    liq_velocities_orig=[]
+    for dir_name in capillary_str:
+        file_dir="HydroResultsRight/"+dir_name+"/"        
+        phase=numpy.loadtxt(file_dir+"phase300000.dat")
+        velx=numpy.loadtxt(file_dir+"velocityx300000.dat")
+        vely=numpy.loadtxt(file_dir+"velocityy300000.dat")
+        dims=phase.shape
+        center=phase[dims[0]/2,:]
+   
+        z1 = numpy.min(numpy.where(center < 0.0))
+        z2 = numpy.max(numpy.where(center < 0.0))
+        if z1==0:
+            z2=numpy.min(numpy.where(center>0.0))+dims[1]
+            z1=numpy.max(numpy.where(center>0.0))
+        
+        prof=phase[:,((z1+z2)/2)%dims[1]]
+        widths_orig.append(Get_Zero(prof))     
+        bubble_lengths_orig.append((z2-z1)/float(dims[0]-2))
+        slug_lengths_orig.append(15.0-(z2-z1)/float(dims[0]-2))
+        velocities_orig.append(velx[dims[0]/2,z2%dims[1]])
+        holdups_orig.append(float(len(numpy.where(phase<0)[0]))/(dims[1]*(dims[0]-2)))        
+        liq_velocities_orig.append(numpy.sum(velx[1:-1,((z1+z2+dims[1])/2)%dims[1]])/(dims[0]-2))
+        gas_velocities_orig.append(holdups_orig[-1]*velocities_orig[-1])
+        capillaries_orig.append(velocities_orig[-1]*(2.0/3.0)/math.sqrt(8*0.04*0.04/9.0))
+        reynolds_orig.append(velocities_orig[-1]*(dims[0]-2)/(2.0/3.0))
+    
+    print "Bubble velocities=",velocities_orig
+    print "Liquid velocities=",liq_velocities_orig
[…]

### 2012-02-04 Text/introduction.tex
Finished the draft.

@@
 sources to be comparable of the representative unit cell, which accounts for the inhomogenous
-situation. By examining $5$ representative cases taken from microfluidics with the capillary number
-from $Ca=0.1$ to $Ca=1$ the following relationship was established {\color{red} Give main findings
-here}. The work is of use to people performing mass transfer numerical simulations.
+situation. The strategies of how to speed up simulations, what the boundaries conditions are
+thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
+domain concentration is taken as the characteristic concentration. Though more difficult to setup
+simulations with a few unit cells can give additional information about how well the liquid slug is
+mixed. The work is of use to people performing mass transfer numerical simulations within the
+lattice Boltzmann context.
 \end{abstract}
@@
 the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
-numbers there is no vortex and stremalines go around the bubble {\color{red} Give two pictures
-with corresponding streamlines}. Thus, the problem is interesting because of different
+numbers there is no vortex and stremalines go around the bubble, see Fig.
+\ref{fig:streamlines:tweaked:velocity}. Thus, the problem is interesting because of different
 hydrodynamic patterns depending on the capillary number which governs a number of experimental
@@
 \beq
+\label{concentration:domain:coordinate}
 C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
@@
 \beqal
+\label{theor:one:concentration:time}
 &\vol\, t \frac{\ububble}{\ugas+\uliq}=\ln \frac{\cstar}{\cstar-C(t)}\\
@@
 The concentration $C(t)$ required for calculation the volumetric mass transfer coefficient, Eq.
-(\ref{theor:average:concentration:time}), can be taken as the average concentration in the domain:
+\ref{theor:one:concentration:time}, can be taken as the average concentration in the domain:
 \beq
@@
 \beq
-\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(t_2)\mathrm{d}V}-\int_liq{C(t_1)\mathrm{d}V}}{
+\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(t_2)\mathrm{d}V}-\int_{liq}{C(t_1)\mathrm{d}V}}{
 t_2-t_1 } .
@@
 
-\item 
-The approach of the opened boundaries was examined, see Fig. \ref{fig:benchmark:jos}. At the inlet
-and outlet boundaries the diffusion flux was imposed to be zero, $\frac{\partial C}{\partial x}=0$.
-The characteristic concentration was taken as the average concentration in the whole domain.
-\begin{figure}
-\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
-\caption{The numerical mass transfer benchmark with open boundaries. The mass transfer is
-calculated according to Eq. \ref{theor:average:concentration:time} with the characteristic
-concentration accoring to Eq. \ref{average:concentration:definition}. \label{fig:benchmark:jos}}
-\end{figure}
+%\item 
+%The approach of the opened boundaries was examined, see Fig. \ref{fig:benchmark:jos}. At the inlet
+%and outlet boundaries the diffusion flux was imposed to be zero, $\frac{\partial C}{\partial x}=0$.
+%The characteristic concentration was taken as the average concentration in the whole domain.
+%\begin{figure}
+%\includegraphics[width=\textwidth]{Figures/benchmark_jos.eps}
+%\caption{The numerical mass transfer benchmark with open boundaries. The mass transfer is
+%calculated according to Eq. \ref{theor:average:concentration:time} with the characteristic
+%concentration accoring to Eq. \ref{average:concentration:definition}. \label{fig:benchmark:jos}}
+%\end{figure}
 
@@
 The last approach to be examined in this paper is the approach of the simulation of a lot of unit
-volumes, see Fig. \ref{big:benchmar:alot}. This situation corresponds to the simulation of the
+volumes, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
 bubble train head, after injecting to the pipe and travelling along the pipe. The argument here is
@@
 \caption{Comparison with the analytical concentration contours, Eq.
-(\ref{analytical:solution:zero:gradient}), for the diffusion coefficient $D=0.0185$. Simulation was
+\ref{analytical:solution:zero:gradient}, for the diffusion coefficient $D=0.0185$. Simulation was
 performed on grid $80\times 1600$. The constant concentration is imposed with the
-anti bounce-back conditions, Eq.\ref{antibb}. \label{fig:parabolic:zero:gradient}}
+anti bounce-back conditions, Eq. \ref{antibb}. \label{fig:parabolic:zero:gradient}}
 \end{figure}
@@
 \end{equation}
-where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
+where coefficients $C_m$ are taken from Eq. \ref{coeff:series:parabolic:profile}. The comparison
 between contours of analytical and simulation results is presented in Fig.
@@
 \caption{Comparison between the analytical concentration contours and simulations with pressure
-anti bounce-back conditions, Eq. (\ref{antibb}). The parameters were
+anti bounce-back conditions, Eq. \ref{antibb}. The parameters were
 taken as $D=0.0185$ and grid $80\times1600$. \label{fig:parabolic:comparison}}
@@
 bubble. We impose a steady concentration of the trace on the surface
-of the bubble with the anti bounce-back condition, Eq. (\ref{antibb}).
+of the bubble with the anti bounce-back condition, Eq. \ref{antibb}.
  \item[Velocity improvement] Due to necessity to increase velocity one can scale the velocity to
@@
 the capillary number (viscous forces over surface tension), the Schmidt number (viscous diffusion
-rate over mass diffusion rate), the Peclet number (convection over diffusion) and the Sherwood
+rate over mass diffusion rate), the Peclet number (convection over diffusion), the Reynolds number
+(inertia over viscous forces) and the Sherwood
 number (convection mass transfer over diffusion mass transfer):
@@
 \begin{aligned}
-&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
-&Pe=\frac{\ububble L}{D}\\
-&Sh=\frac{K L}{D}\\
-&Sc=\frac{\nu}{D}.
+&Re=\frac{\ububble L}{\nu_{\mathrm{liq}}},&&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
+&Pe=\frac{\ububble L}{D},&&Sh=\frac{K L}{D}\\
+&Sc=\frac{\nu_{\mathrm{liq}}}{D}.&&
 \end{aligned}
@@
 
-\section{Keeping Peclet}
+\section{Results}
+This section covers simulation results. We first examine the possibility to increase the fluid
+velocity while keeping the Peclet number the same. After that we will examine the periodic boundary
+conditions for $5$ capillary cases, open boundary simulations, and finally we will examine many
+cells simulations for two representative cases velocity patterns, as $Ca=0.0907$ and $Ca=1.04$
+(see Fig. \ref{fig:streamlines:tweaked:velocity}).
+
+\subsection{Keeping Peclet}
+\label{section:keeping:peclet}
 This section addresses the performance of the simulations. The ulimate goal is to increase
-velocity at least by several orders while keeping dimensionless parameters the same. Increasing
-velocity can result in simulations of a lot of unit cells required for continuous picture
-representation.
-
-Only nondimensional parameter Peclet number governs the advection-diffusion equation:
-\beq
-Pe=\frac{U_{bubble} N_y}{D},
-\feq
-where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
+velocity at least by several orders while keeping dimensionless parameters the same to speed up
+simulations. Increasing velocity can also help to resolve a lot of unit cells to represent a
+continous picture.
+
+With the given bubble shape and velocity pattern only nondimensional parameter Peclet number governs
+the advection-diffusion equation:
+\beq
+Pe=\frac{\ububble N_y}{D}.
+\feq
+As far as we want to increase velocity, that
 means one needs to increase the diffusion coefficient as well. The runs were made with
@@
 boundary conditions were used and mass transfer coefficient was calculated according to Eq.
-(\ref{main:simulation:equation}).
+\ref{main:simulation:equation}. Table \ref{table:scaling:peclet} shows that the velocity limit
+for  periodic boundary conditions is $0.1$ where $\omegaminus=1.99$ ($D=0.000837$). It gives us the
+preliminary idea to what extent one can scale periodic mass transfer simulations. 
 \begin{table}[htb!]
@@
 \multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.097$}\\
+\multicolumn{4}{c}{$Ca=0.097$,$Pe=1313$}\\
 \hline
@@
 \multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.254$}\\
+\multicolumn{4}{c}{$Ca=0.254$,$Pe=3414$}\\
 \hline
@@
 \multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.526$}\\
+\multicolumn{4}{c}{$Ca=0.526$,$Pe=7092$}\\
 \hline
@@
 \multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.750$}\\
+\multicolumn{4}{c}{$Ca=0.750$,$Pe=10125$}\\
 \hline
@@
 \multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=1.040$}\\
+\multicolumn{4}{c}{$Ca=1.040$,$Pe=14041$}\\
 \hline
@@
 \end{tabularx}
-\caption{Scaling Peclet table. One can see that scaling is pretty successful. One can see as well
-that the stability limit is approximately around $U_{bubble}=0.1$. That can give us an idea of
-scale of simulations. \label{table:scaling:peclet}}
+\caption{Table representing how one can speed up simulations. One iteration in the lattice
+Boltzmann system corresponds to time difference as
+$\Delta t=\frac{U_{\mathrm{bubble,LB}}}{U_{\mathrm{bubble,phys}}} \Delta x$. Therefore the speed up
+of the simulation is proportional to the  $U_{\mathrm{bubble,LB}}$. Thus, the time iterations
+indicated in the table correspond to the one time moment in physical space. One can see that
+scaling produces adequate results.  One can see that the stability limit is approximately around
+$U_{bubble}=0.1$ for the diffusion coefficient
+$D=1/3(1/1.99-0.5)=0.000837$. Average concentrations are in the reasonable agreement. The contour
+profiles for all of these cases are presented in Fig. \ref{fig:contours:scaling:peclet}
+\label{table:scaling:peclet}}
 \end{table}
-
-The corresponding to Table \ref{table:scaling:peclet} contour profiles for different scalings are
-presented in Fig. \ref{fig:contours:scaling:peclet}.
-\begin{figure}[htb!]
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca026.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca054.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca05.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca097.eps}\\
-\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca14.eps}\\
-\caption{Contours for scaling Peclet number.\label{fig:contours:scaling:peclet}}
-\end{figure}
-
-\section{Comparison between different approaches for one unit cell}
-We consequently will examine different approaches to the mass transfer definition, Fig.
-\ref{fig:comparison:one:unit:cell}:
-\begin{description}
-\item[I] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
-is located near the entrance of the computational domain, and the characteristic concentration is
-the inlet/outlet concentration, Fig \ref{fig:benchmark}. 
-\item[II] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
-is located near the entrance of the computational domain, and the characteristic concentration is
-the average concentration, Fig \ref{fig:benchmark}.
-\item[III] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a
-bubble is located in the middle of the computational domain, and the characteristic concentration
-is the inlet/outlet concentration.
-\item[IV] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
-is located in the middle of the computational domain, and the characteristic concentration is the
-average concentration.
-\item[V] Definition with the concentration jump between inlet and outlet over one unit cell.
-\end{description}
-
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_entrance.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_inlet_aver.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_aver.eps}
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_middle_outlet.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/steady_state_jos_inlet_outlet.eps}\\
-\caption{\label{fig:comparison:one:unit:cell}}
-\end{figure}
-All the comparison is summarized in Table \ref{table:one_unit_comparison}.
-\begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
-\hline
-$Ca$&$Fo$&$\vol_{ent},\,\mathrm{s}^{-1}$&$\vol_{aver},\,\mathrm{s}^{-1}$&$\vol_{mid,
-aver},\,\mathrm{s} ^ { -1 }$&$\vol_{mid,out},\,\mathrm{s}^{-1}$&$\vol_{open},\,\mathrm{s}^{-1}$ \\
-\hline
-$0.026$&$0.08493$&$0.2737$&$0.1775$&$0.1692$&$0.2631$&$3.6756$\\
-$0.047$&$0.02160$&$0.3664$&$0.3431$&$0.2852$&$0.4553$&$11.4822$\\
-$0.080$&$0.00588$&$0.4959$&$0.4185$&$0.4079$&$0.6920$&$15.1964$\\
-$0.065$&$0.00862$&$0.4734$&$0.4517$&$0.4303$&$0.8923$&$21.4517$\\
-$0.222$&$0.00103$&$0.8505$&$0.6799$&$0.6109$&$0.8679$&N/A\\
-$0.479$&$0.00034$&$1.1541$&$1.0460$&$0.9884$&$1.2995$&N/A\\
-$0.736$&$0.00018$&$1.1801$&$1.2395$&$1.2199$&$1.1555$&N/A\\
-$0.989$&$0.00012$&$1.2215$&$1.3493$&$1.3400$&$1.0350$&N/A\\
-\hline
-\end{tabularx}
-\caption{Simulation results for different capillary numbers.
-\label{table:one_unit_comparison}}
-\end{table}
-One can see that the only consistent result is for simulations which take into the account average
-concentration. The results come to the steady-state after $1,000,000$ iterations. However, to
-understand properly what is the real mass transfer coefficient one needs to perform a few units
-simultions.
-
-\section{Open boundary conditions}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0097.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0254.eps}
-\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0254.eps}\\
-\caption{Open boundary conditions. \label{fig:open:boundary:jos}}
-\end{figure}
-
-\section{Symmetric boundary conditions}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0097.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0254.eps}
-\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0254.eps}\\
-\caption{Symmetric boundary conditions. \label{fig:open:boundary:sym}}
-\end{figure}
-
-\section{Four unit cells results}
-From Figs. \ref{fig:results:triple} and \ref{fig:results:quadro} one can see that $4,000,000$ time
-steps are enough to saturate the second unit for $Ca=0.080$ number. Let us recall bubble velocities
-and see what are the characteristic lengths for them calculated as time steps multiplied on the
-bubble velocity. From the table one can see that each unit cell is saturated with the timesteps as
-$1.5 \frac{N_x}{U_{bubble}}$ {\color{red}(Pretty important result)}. It's inevitably needs the
-velocity increase.
-\begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
-\hline
-$Ca$ &$U_{bubble}$ &$N_{iter_1}$ &$N_{iter_2}$ &$N_{iter_3}$ &$\frac{L_1}{N_x}$&$\frac{L_2}{N_x}$ 
-&$\frac{L_3}{N_x}$\\
-$0.026$&$0.0014$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$0.4666$ &$0.9333$ &$1.8666 $\\
-$0.047$&$0.0027$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$0.9$    &$1.8$    &$3.6    $\\
-$0.080$&$0.0045$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$1.5$    &$3.0$    &$6.0    $\\
-$0.065$&$0.0037$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$1.2333$ &$2.4666$ &$4.9333 $\\
-$0.222$&$0.0125$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$4.1666$ &$8.3333$ &$16.6666$\\
-$0.479$&$0.0271$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$9.0333$ &$18.0666$&$36.1333$\\
-$0.736$&$0.0416$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$13.8666$&$27.7333$&$55.4666$\\
-$0.989$&$0.0559$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$18.6333$&$37.2666$&$74.5333$\\
-\hline
-\end{tabularx}
-\caption{Table results to understand how many time steps are needed to be performed to reach the
-saturation.\label{table:time:steps}}
-\end{table}
-
-\section{Performing real simulations}
-As it was found earlier one needs to make a few units simulations to obtain a proper volumetric
-mass transfer coefficient. This section studies the quantity of the unit cells on the volumetric
-mass transfer coefficient to be independent of the number of unit cells. The cases we want to
-examine in terms of the capillary number are indicated above. The number of cells we want to
-simulate are $1$,$4$,$6$,$8$,$10$. As it was discussed in the previous section we want to keep
-velocity around $0.05-0.1$. The number of steps for mass to cross whole domain is approximately
-$1.5 \frac{N_x}{U_{bubble}}$, given the bulk velocity. If $U_{bubble}$ is taken as $0.05$ then for
-the domain size $3000$ one can obtain the following number of iteration for mass transfer to be
-stabilize $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ time iterations are enough for system
-to be stabilized.
-
-%For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
-%thumb that for such simulations the velocity shouldn't be more than $0.05$.
-
-%\begin{figure}[htb!]
-%\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
-%\caption{The same Peclet number for $Ca=0.0055$. One can see that
-%the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
-%concentration!!!} \label{fig:ca0055:keeping:peclet}}
-%\end{figure}
-
-\section{Performing average approach}
-One can calculate the average domain concentration over the time. According to the definitions of
-the volumetric mass transfer coefficient one can obtain the following concentration depending on
+The corresponding to Table \ref{table:scaling:peclet} concentration contour profiles for different
+velocity scalings are presented in Fig. \ref{fig:contours:scaling:peclet}. One can see an
+acceptable agreement between all of them. Note, that a few profiles are obtained $10$ to $40$ times
+faster.
+\begin{figure}[htb!]
+\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca097.eps}\\
+\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca054.eps}\\
+\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca026.eps}\\
+\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca05.eps}\\
+\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca14.eps}\\
+\caption{Concentration contour profiles for velocity scalings as identified in Table
+\ref{table:scaling:peclet} (top to bottom:
+$Ca=0.097,0.254,0.526,0.750,1.040$).\label{fig:contours:scaling:peclet}}
+\end{figure}
+
+\subsection{Average concentration}
+\label{main:results:periodic}
+As indicated in Section \ref{section:cases} one can calculate the average domain concentration over
+the time. Eq. \ref{theor:one:concentration:time} shows how 
+the volumetric mass transfer coefficient depends on
 time, i.e. streamwise coordinate:
 \beqal
-&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{C^*}{C^*-C(t)}\\
-&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-C(t)}\\
+&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{\cstar}{\cstar-C(t)}\\
+&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-C(t)},\\
 \feqal
+where $C(t)$ is the average concentrations.
 Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
-\ref{fig:aver:conc:different:capillaries}.
+\ref{fig:aver:conc:different:capillaries:time} for different Peclet numbers and velocity scalings
+indicated in Table \ref{table:scaling:peclet}. Because in the definition of the volumetric mass
+transfer coefficient there is the logarithm function, thus when the average concentration goes
+close to $\cstar=1$ then Eq. \ref{theor:one:concentration:time} gives inadequate results due to
+ accuracy of the logarithmic function. However, the more interesting thing is to put the same plots
+as in Fig. \ref{fig:aver:conc:different:capillaries:time} against the number of unit cells length
+which the bubble passes with the given velocity as $\mathrm{scale}\cdot\frac{\mathrm{\ububble\cdot
+t}}{L}$. Fig. \ref{fig:aver:conc:different:capillaries} shows the volumetric mass transfer
+dependency against the distance in unit cells length. One can see in Table
+\ref{table:steady:state:average} that for different Peclet numbers different time (number of unit
+cells) is required to achieve the steady state. Also, Table \ref{table:steady:state:average} shows
+the achieved steady state volumetric mass transfer coefficient. One can see tendention that for
+larger Peclet number less time steps are required to achieve the steady state condition.
+
+Overall one is guaranteed to obtain the steady state volumetric mass transfer coefficient for
+periodic boundaries simulations if the following conditions are fulfilled:
+\begin{description}
+\item Scaling is performed as $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
+\item The larger Peclet number the less time is required. One can extrapolate data from Table
+\ref{table:steady:state:average}, say $L_{\mathrm{steady}}$ and perform the following number of
+iterations as $\mathrm{scale}\cdot \ububble\cdot N_{\mathrm{iter}}\leq L_{\mathrm{steady}}$. 
+\end{description}
+
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time054.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time026.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time05.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time14.eps}
+\caption{Calculated volumetric mass transfer coefficient for different capillaries and scales
+against time. One can see
+that all curves have the same minimum corresponding to the volumetric mass transfer coefficient.
+Some simulations show the volumetric mass transfer coefficient going up due to the average
+concentration being close to $\cstar$. All of them show excellent agreement. Note, that with the
+scaling one can reduce the amount of calculations drastically. However, one needs to be attentive
+because with the large velocity scaling average concentration can fastly approach $\cstar$, thus
+getting an infinite volumetric mass transfer coefficient.
+\label{fig:aver:conc:different:capillaries:time}}
+\end{figure}
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca054.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca026.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca05.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}
+\caption{Volumetric mass transfer coefficient for different capillaries and scales against the
+bubble traveling distance in the laboratory frame. Table \ref{table:steady:state:average}
+summarizes results.\label{fig:aver:conc:different:capillaries}}
+\end{figure}
+\begin{table}[htb!]
+\begin{tabularx}{\textwidth}{|X|X|X|X|}
+\hline
+$Ca$    &$Pe$     &$L_{\mathrm{steady}}/\lunit$& $\volnondim$ \\
+\hline
+$0.097$ &$1313$  &$7$&$0.21$  \\ 
+$0.254$ &$3414$  &$6$&$0.14$  \\ 
+$0.526$ &$7092$  &$3$&$0.095$ \\
+$0.750$ &$10125$ &$3$&$0.074$ \\
+$1.040$ &$14041$ &$2$&$0.0601$\\
+\hline
+\end{tabularx}
+\caption{The distance which a bubble propagates when the
+steady-state condition is achieved. One can see that increasing
+Peclet number helps to achieve the steady state faster.\label{table:steady:state:average}}
+\end{table}
+
+\subsection{Periodic boundaries with the inlet/outlet characteristic concentration}
+When the characteristic concentration is taken as in the formulation of \citet{vanbaten-circular},
+i.e. the inlet/outlet flux averaged concentration, then the results are quite different. One can
+see in Fig. \ref{fig:volumetric:char:concentration:vanbaten} the calculated volumetric mass transfer
+is different from the domain averaged calculated volumetric mass transfer coefficient. For example,
+for small capillary numbers, i.e. $Ca=0.097,0.254,0.526$ the predicted values are overpredicted
+($\volnondim=0.3,0.25,0.1$). When the pattern is changed, i.e. $Ca=0.75,1.04$ the calculated values
+are underpredicted than in previous case, i.e. $\volnondim=0.06,0.04$.
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca054.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca026.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca05.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca14.eps}
+\caption{The volumetric mass transfer coefficient
+with the characteristic concentration based on
+the inlet/outlet flux averaged concentration as
+in \cite{vanbaten-circular}. One can see that values are either overpredicted or underpredicted
+than values specified in Table \ref{table:steady:state:average} depending on the velocity pattern. 
+\label{fig:volumetric:char:concentration:vanbaten}}
+\end{figure}
+
+\subsection{\citeauthor{vanbaten-circular} formulation}
+The van Baten formulation which is calculated as the change of mass in domain with characteristic
+concentrations to be as the average domain simulation and as the averaged flux input/output
+concentration. One can see them in Fig. \ref{fig:vanbaten} for $Ca=0.097$ and
+$Ca=1.04$. One can see that results are consistent with the simulations in Section
+\ref{main:results:periodic} for the volumetric mass transfer coefficient measured with the domain
+averaged concentration in the whole range of capillary numbers. Note that for $Ca=0.097$ the
+obtained mass transfer coefficient is less than in Section \ref{main:results:periodic}. However, as
+it will be shown later this coefficient coincides with the many units formulation. The inlet/outlet
+flux averaged concentration is shown to be consistent only for velocity patterns related to larger
+Capillary numbers, i.e. $Ca\geq0.7$. 
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca026.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca054.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca05.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca097.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}\\
-\caption{Volumetric mass transfer coefficient for different capillaries and scales. One can see the
-excellent agreement. \label{fig:aver:conc:different:capillaries}}
-\end{figure}
-One of interesting correlations for the mass transfer volumetric coefficient was presented by
-\citet{yue-mass}:
+\includegraphics[width=0.5\textwidth]{Figures/vanbaten_aver_scale_ca097.eps}
+\includegraphics[width=0.5\textwidth]{Figures/vanbaten_full_scale_ca097.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/vanbaten_aver_scale_ca14.eps}
+\includegraphics[width=0.5\textwidth]{Figures/vanbaten_full_scale_ca14.eps}\\
+\caption{The \citet{vanbaten-circular} formulations for $Ca=0.097$ (top) and
+$Ca=1.04$ (bottom) with the characteristic concentration being domain
+averaged (left) and inlet/outlet flux averaged concentration (right). One can
+see that \citet{vanbaten-circular} formulation is good with the average
+characteristic concentration for capillary numbers regimes without
+vortex. Moreover, the values are more close to values obtained with many cells
+simulations, see Fig. \ref{fig:moving:average:ca0097}. However, the characteristic concentration
+being inlet/outlet flux averaged concentration does not produce consistent results.
+\label{fig:vanbaten}}
+\end{figure}
+
+%\section{Open boundary conditions}
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0097.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0097.eps}\\
+%\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0254.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0254.eps}\\
+%\caption{Open boundary conditions. \label{fig:open:boundary:jos}}
+%\end{figure}
+%\section{Symmetric boundary conditions}
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0097.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0097.eps}\\
+%\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0254.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0254.eps}\\
+%\caption{Symmetric boundary conditions. \label{fig:open:boundary:sym}}
+%\end{figure}
+
+\subsection{Performing a number of cell units simulations}
+One needs to examine a few units simulations to obtain a proper volumetric
+mass transfer coefficient. This section studies the quantity of the unit cells on the volumetric
+mass transfer coefficient to be independent of the number of unit cells. We chose two different
+velocity patterns (see Fig. \ref{fig:streamlines:tweaked:velocity} for $Ca=0.097$ and $Ca=1.04$) to
+perform a few number of cells simulations. For $Ca=0.097$ we performed simulations with
+$4$,$6$,$8$,$10$ number of cells, for $Ca=1.040$ - $4$,$6$,$8$ cells to be examined. However,
+simulations with $10$ unit cells domain length produce the same results as $8$ unit cells.
+Thus, it won't be covered here, especially as it requires extensive computational resources (grid is
+$30000\times 200$).
+
+As it was discussed in the previous section we want to keep
+velocity around $0.05-0.1$ to from . The number of steps for mass to cross whole domain is
+limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into the account the bulk
+velocity. If $\ububble$ is taken as $0.05$ then for
+the domain size $\lunit=3000$ one can obtain the following number of iteration for mass transfer to
+cross the unit cell $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ time iterations are enough
+for system consisting of $10$ cell units to be stabilized. For more accurate estimations depending
+on the Peclet number one can refer to Section \ref{section:keeping:peclet}.
+
+\subsection{$Ca=0.097$ results}
+To understand the process happening in unit cells one need to keep a track of a few
+characteristics. We chose following representative characteristics: the average concentration in
+the unit cell with time, the concentration difference between adjacent unit cells. The latter is
+the interesting characteristics which shows how well slug liquid is mixed (to be shown later). The
+argument behind this characteristic is that if the following situation is fulfilled: the continuity
+equation is satisfied then the concentration along the coordinate changes according to Eq.
+\ref{main:mass:transfer:expression}:
+\beq
+C(x)= \cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\uliq+\ugas} \bigr)\Bigr)
+\feq
+%After the transition to the reference frame moving with the velocity $\ububble$, one will have the
+%same continuous picture but the concentration dependency will change since velocity is changed as
+%well:
+%\beq
+%C(x)= \cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\uliq+\ugas-\ububble} \bigr)\Bigr),
+%\feq
+%Thus, the volumetric mass transfer coefficient for two concentrations which are located at the
+%distance $\lunit$ can be found as:
+%\beqal
+%&\vol \frac{\lunit}{\uliq+\ugas-\ububble}=\ln\Bigl(\frac{\cstar-C_1}{\cstar-C_2}\Bigr)\\
+%&\vol
+%\frac{\lunit}{\uliq+\ugas}=\frac{\uliq+\ugas-\ububble}{\uliq+\ugas}\ln\Bigl(\frac{\cstar-C_1}{
+%\cstar-C_2}\Bigr)
+%\feqal
+%Parameters $\frac{\uliq+\ugas-\ububble}{\uliq+\ugas}$ were calculated and for representative
+%Capillary numbers equal to $0.11,0.04,-0.02,-0.06,-0.10$.
+Therefore, the following correlation was examined between adjacent cells:
+\beqal
+\label{volumetric:between:adjacent:cells}
+&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
+&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
+&k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
+\feqal
+Fig. \ref{fig:unit:4} shows one of the examples for velocity scale $20$ and  $4$ unit numbers (all
+scales produce the same results) for the volumetric mass transfer coefficient based on difference
+between two adjacent cells concentration averages. One can see that this number is different in
+comparison with the number used for periodic boundary
+conditions. Moreover, it is changed from segment to segment. The same dependencies can be found for
+$6$ and $8$ unit cells simulations but we do not present them here.
+
+However, if one wants to examine how the average concentration changes in time according to Eq.
+\ref{theor:continuous:mass:transfer} for different unit cells then one will see interesting
+thing for the volumetric mass transfer correlation, see Fig. \ref{fig:moving:average:ca0097}:
+\beq
+\label{moving:average}
+\vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
+-t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
+\feq
+\begin{figure}[htb!]
+%\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale10.eps}\hfill
+%\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale10.eps}\\
+%\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale15.eps}\hfill
+%\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
+\caption{Average concentrations and volumetric coefficients for $4$ units cells. The volumetric
+mass transfer coefficient is calculated based on the difference between averages for different unit
+cells.
+\label{fig:unit:4}}
+\end{figure}
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window4scale10.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window8scale10.eps}
+\caption{The non-dimensional volumetric mass transfer coefficient defined in Eq.
+\ref{moving:average} for $4$ (top left),$6$ (top right),$8$ cell units (bottom). Only scale
+$10$ is presented since all other simulations produce the same results. One can see that $4$ unit
+cells is not enough to see avoid the influence of boundaries. However, the results for $6$ and $8$
+unit cells are consistent and show that beginning from third unit cell the results and ending with
+prelast cell results are consistent with periodic boundary simulations and
+\citet{vanbaten-circular} formulations.
+\label{fig:moving:average:ca0097}}
+\end{figure}
+
+\subsection{$Ca=1.040$ results}
+The same correlations were examined for the different velocity pattern $Ca=1.040$ and initial
+velocity $\ububble=0.055$ and initial diffusion $D=0.0008375$. A few unit cells simulation for this
+capillary number are unstable. To improve stability we changed original Peclet number by increasing
+diffusion to reveal all the correlations. The results for unit cells are the same as for $Ca=0.097$:
+at least $6$ unit cells are required to be simulated to avoid the influence of boundaries. Thus,
+only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040}.One can see that the
+volumetric mass transfer coefficient based
+on the difference between unit cells averages is constant for internal
+unit cells. This case is different from the previous case where those coefficients were not equal
+to each other. The average concentration being constant means that there is no backward convection
+flux and there is no slug tracer mixing. This test is a good example to indicate whether there is
+mixing in the liquid slug or not.
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_units6scaleu2scaled5.eps}
+\includegraphics[width=0.5\textwidth]{Figures/novortex6scaleu2scaled5.eps}\\
+\caption{Results for 6 unit cells. The Peclet number equals to $Pe=2644$.
+One can see that average concentrations reach certain number and stay.
+That means whatever was generated by medium is transfered through
+boundary. One can see that the volumetric mass transfer coefficient based
+on the difference between unit cells averages is constant for internal
+unit cells. This is the indication that the tracer in the slug is not
+mixed.\label{fig:6:units:ca1040}}
+\end{figure}
+The volumetric mass transfer coefficient with periodic boundary simulations for $Pe=2644$ (velocity
+scale $2$, diffusion scale $10$) and time dependent, Eq. \ref{theor:continuous:mass:transfer},
+average volumetric mass transfer coefficient are presented in Fig. \ref{fig:periodic:ca1040}. Note
+that they coincide but are different from calculated coefficients based on spatial location.
+Therefore, the time based simulations do not readily convert to spatial based simulations.
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/volume_ca_104_scaleu2scaled5.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scaleu2scaled5.eps}\\
+\caption{The periodic (left) and time unit cells averaging volumetric mass transfer coefficients.
+One can see that they coincide, but are different from spatial based volumetric mass transfer
+coefficient, see Fig. \ref{fig:6:units:ca1040} \label{fig:periodic:ca1040}}
+\end{figure}
+
+\subsection{Experiment comparison}
+The goal of this paper is not to compare with the experiment correlations, but give the
+procedure to perform numerical simulations in the lattice Boltzmann framework. However, the small
+comparison is performed. 
+Unfortunately the experiments to the best authors' knowledge measuring the mass flux for infinite
+width  bubbles flowing between parallel plates are absent. However, one of interesting
+correlations for the mass transfer volumetric coefficient was presented by
+\citet{yue-mass} for three-dimensional microchannel geometries:
 \beqal
@@
 \feqal
-\begin{figure}
-\includegraphics[width=\textwidth]{Figures/volumetric_mass_peclet.eps}
-\end{figure}
-
-\section{Real calculations}
-This section examines different cells for the capillary $Ca=0.097$. The coefficient is
-non-dimensionalized in the following manner $\vol \frac{\lunit}{\ugas+\uliq}$. Therefore, we
-examined the average concentrations in different units and for different scalings. Therefore the
-average concentration between two different cells have to be of the following value:
-\beqal
-&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
-&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
-&k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
-\feqal
-One can see that this number is different in comparison with the number used for periodic boundary
-conditions. Thus, the domain transformation from time domain to the coordinate domain is not
-straightforward and require other definitions. For example by definition we took $C_1$ and $C_2$ to
-be average concentrations over different units. One can see Fig. \ref{fig:unit:8} for
-average coefficients and corresponding volumetric mass transfer coefficients.
-\subsection{4 units}
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale10.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale10.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale15.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
-\caption{Average concentrations and volumetric coefficients for $4$ units.
-\label{fig:unit:4}}
-\end{figure}
-The more interesting picture is actually moving window average which is calculated as:
-\beq
-\label{moving:average}
-\vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
--t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
-\feq
-One can see those moving averages in Fig. \ref{window4}.
-\begin{figure}[htb!]
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale10.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale15.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale20.eps}\\
-\caption{Moving averages defined in Eq. \ref{moving:average} for 4 units
-\label{fig:moving:average:window4}}
-\end{figure}
-
-\subsection{6 units} 
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale10.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale10.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale15.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale15.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale20.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale20.eps}\\
-\caption{Average concentrations and volumetric coefficients for $8$ units.
-\label{fig:unit:10}}
-\end{figure}
-
-Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window6}.
-\begin{figure}[htb!]
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale10.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale15.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale20.eps}\\
-\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
-\label{fig:moving:average:window6}}
-\end{figure}
-
-\subsection{8 units} 
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale10.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale10.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale15.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale15.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units8scale20.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units8scale20.eps}\\
-\caption{Average concentrations and volumetric coefficients for $8$ units.
-\label{fig:unit:8}}
-\end{figure}
-
-Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window8}.
-\begin{figure}[htb!]
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale10.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale15.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale20.eps}\\
-\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
-\label{fig:moving:average:window8}}
-\end{figure}
-
-\subsection{10 units} 
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale10.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale10.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale15.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale15.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units10scale20.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units10scale20.eps}\\
-\caption{Average concentrations and volumetric coefficients for $8$ units.
-\label{fig:unit:10}}
-\end{figure}
-
-Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window10}.
-\begin{figure}[htb!]
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale10.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale15.eps}\\
-\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale20.eps}\\
-\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
-\label{fig:moving:average:window10}}
-\end{figure}
-
-\section{Scaling for $Ca=1.040$}
-
+One can see that approximately the volumetric mass transfer correlation should be proportional to
+$Pe^{-0.5}$. Fig. \ref{fig:volume:mass:coefficient} shows a comparison between corelation by
+\citet{yue-mass} and the current simulations coefficients presented in Table
+\ref{table:steady:state:average}. The coefficients are not far from each other, given the difference
+between two-dimensional and three-dimensional cases. The fitting procedure showed that the power of
+the Peclet number $Pe$ is $-0.50038$ which is close to $-0.5$. 
+\begin{figure}[htb!]
+\includegraphics[width=\textwidth]{Figures/correlations_comparison.eps}
+\caption{Comparison between correlation by \citet{yue-mass} and mass transfer coefficient based
+on periodic boundary conditions. The fitting curve is proportional to $Pe^{-0.5}$ which corresponds
+to the correlation by \citet{yue-mass}.\label{fig:volume:mass:coefficient}}
+\end{figure}
+
+\section{Conclusion}
+This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
+the lattice Boltzmann method. Overall, the recipe is to perform periodic boundary
+conditions simulations and calculate the volumetric mass transfer coefficient based on the averaged
+domain concentration through any formulation as they produce consistent results. Formulation of
+\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
+to be characteristic concentration. A few unit cells simulations are harder to perform, but they
+have indicator of how well the liquid slug is mixed. Finally, a sample of results was
+compared with the experimental correlation of \citet{yue-mass}. 
 \appendix
@@
 Taking symmetry conditions in the consideration by leaving only even solution, Eq.
-(\ref{fourier:separation:variables:parabolic}) has a solution as:
+\ref{fourier:separation:variables:parabolic} has a solution as:
 \beq
@@
 \end{equation}
-where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). For the case
+where coefficients $C_m$ are taken from Eq. \ref{coeff:series:parabolic:profile}. For the case
 $\cstar$, first ten coefficients equal to  $1.2008$, $-0.2991$, $0.1608$, $-0.1074$, $0.0796$,

### 2012-02-04 Python/IncreasingDiffusion/mass_periodic.cpp

@@ -512,7 +512,7 @@ void stream()
 
 void calculate_mass_transfer(int time_counter)
 {
-	static std::ofstream fconc("concentration.dat");
+	static std::ofstream fconc("concentration_periodic.dat");
 	
     double conc=0.0;
     int counter; 	

### 2012-02-04 Python/peclet.py

@@ -174,6 +174,10 @@ def check_average_concentration(dir_name,factor,subtract):
     capillary_str=[str(x) for x in [9,21,42,60,84]]
     capillaries=[0.097,0.254,0.526,0.750,1.040]
     velocities=[0.0055,0.0143,0.0297,0.0424,0.05538]
+    velocities_slug=[0.0046,0.0108,0.0209,0.0293,0.0397]
+    velocities_gas=[0.0016,0.0041,0.0080,0.0101,0.0135]
+    
+
 
     scale=[2,4,8,10,20,40]
     #scale=[8,10,20,40]
@@ -194,7 +198,8 @@ def check_average_concentration(dir_name,factor,subtract):
     for scale_counter in range(0,len(scale_str)-subtract):
         os.chdir(scale_str[scale_counter])
         #exam_point=int(20*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter])
-        exam_point=int(24.0/(velocities[counter]*scale[scale_counter]))        
+        #exam_point=int(24.0/(velocities[counter]*scale[scale_counter]))        
+        exam_point=10;        
         #name=str(20000*factor*scale[len(scale_str)-subtract-1]/scale[scale_counter])
         #name="density"+"0"*(7-len(name))+name+".dat"        
         #print "Filename=",name
@@ -213,7 +218,43 @@ def check_average_concentration(dir_name,factor,subtract):
         pylab.figure(1)
         pylab.plot(velocities[counter]*scale[scale_counter]*concentration[1:,0],aver_concentration,styles[scale_counter])
         pylab.figure(2)
-        pylab.plot(velocities[counter]*scale[scale_counter]*concentration[1:,0]/3000.0,3000.0/(velocities[counter]*scale[scale_counter]*concentration[1:,0])*numpy.log(1.0/(1.0-aver_concentration)),styles[scale_counter],linewidth=2)                
+        
+        #this plot is in terms of unit cells        
[…]

### 2012-02-06 Text/introduction.tex
Started doing showcases for the second part of the paper.

@@
 \beq
+\label{eq:main:definition}
 k_L=\frac{\dot{m}}{P \Delta C},
@@
 %Capillary numbers equal to $0.11,0.04,-0.02,-0.06,-0.10$.
-Therefore, the following correlation was examined between adjacent cells:
+In the case of present simulations the situation is different as the reference frame is moving with
+the bubble. Thus, the correlation between adjacent cells as follows:
 \beqal
 \label{volumetric:between:adjacent:cells}
-&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
-&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
-&k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
+&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq-\ububble}}\Bigr)\\
+&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq-\ububble}}\Bigr)\\
+&k_L\frac{L}{\ugas+\uliq-\ububble}=\frac{C^*-C_1}{C^{*}-C_2}\\
+&k_L\frac{L}{U}=\frac{C^*-C_1}{C^*-C_2},
 \feqal
-Fig. \ref{fig:unit:4} shows one of the examples for velocity scale $20$ and  $4$ unit numbers (all
-scales produce the same results) for the volumetric mass transfer coefficient based on difference
-between two adjacent cells concentration averages. One can see that this number is different in
-comparison with the number used for periodic boundary
-conditions. Moreover, it is changed from segment to segment. The same dependencies can be found for
+where $U=\ugas+\uliq-\ububble$. We will see later that this characteristic is really important to
+see whether the liquid slug is mixed. Fig. \ref{fig:unit:4} shows one of the examples for velocity
+scale $20$ and  $4$ unit numbers (all
+scales produce the same results) for the volumetric mass transfer coefficient $k_L \frac{L}{U}$
+(different from $\volnondim$) based on difference
+between two adjacent cells concentration averages. One can see that this number is changed from
+segment to segment. The same dependencies can be found for
 $6$ and $8$ unit cells simulations but we do not present them here.
@@
 \includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
-\caption{Average concentrations and volumetric coefficients for $4$ units cells. The volumetric
+\caption{Average concentrations (left) and volumetric coefficients (right) $\vol \frac{L}{U}$ (
+different from $\volnondim$) for $4$ units cells. The volumetric
 mass transfer coefficient is calculated based on the difference between averages for different unit
-cells.
+cells. One can see that the numbers for the volumetric mass transfer coefficient are different for
+different unit cells. This is the indication that the liquid slug is mixed and the spatial location
+does not easily transfers to time domain. 
 \label{fig:unit:4}}
@@
 $10$ is presented since all other simulations produce the same results. One can see that $4$ unit
-cells is not enough to see avoid the influence of boundaries. However, the results for $6$ and $8$
+cells is not enough to avoid the influence of boundaries. However, the results for $6$ and $8$
 unit cells are consistent and show that beginning from third unit cell the results and ending with
@@
 The same correlations were examined for the different velocity pattern $Ca=1.040$ and initial
-velocity $\ububble=0.055$ and initial diffusion $D=0.0008375$. A few unit cells simulation for this
+velocity $\ububble=0.055$ and initial diffusion $D=0.0008375$. A few unit cells simulation for
+this
 capillary number are unstable. To improve stability we changed original Peclet number by increasing
@@
 at least $6$ unit cells are required to be simulated to avoid the influence of boundaries. Thus,
-only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040}.One can see that the
-volumetric mass transfer coefficient based
-on the difference between unit cells averages is constant for internal
-unit cells. This case is different from the previous case where those coefficients were not equal
-to each other. The average concentration being constant means that there is no backward convection
-flux and there is no slug tracer mixing. This test is a good example to indicate whether there is
-mixing in the liquid slug or not.
+only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040}. As well the volumetric
+mass transfer coefficient, Eq. \ref{volumetric:between:adjacent:cells}, is shown in Fig.
+\ref{fig:6:units:ca1040}. One can see that the average volume concentration, as well the volumetric
+mass transfer coefficients, come to the constant and are not increasing with time. Thus, all the
+mass generated with medium is transfered through the boundaries. This is the indication that the
+liquid slug is not mixed. Thus, the volumetric mass transfer coefficient $\volnondim$ can be
+calculated according to the definition, Eq. \ref{eq:main:definition}:
+\beq
+\label{inlet:outlet:spatial:location}
+\vol = \frac{\dot{m}}{V \Delta C},
+\feq 
+where $V$ is the unit cell volume, $\Delta C$ is the concentration difference between the bubble
+surface concentration $\cstar$ and the average medium concentration $C_{aver}$. Note that in this
+case one can calculate the mass generation as:
+\beq
+\dot{m}=(\coutlet-\cinlet)\uoutlet,
+\feq
+where $\coutlet$ and $\cinlet$ are taken for the current unit. Fig. \ref{fig:periodic:ca1040}
+(bottom) shows the volumetric mass transfer coefficient, based on spatial calculations of
+inlet/outlet concentrations. One can see that the volumetric mass transfer coefficient is close to
+the calculated volumetric mass transfer coefficient using the time averaged approach and periodic
+boundaries one unit cells simulations. 
 \begin{figure}[htb!]
@@
 One can see that average concentrations reach certain number and stay.
-That means whatever was generated by medium is transfered through
+That means whatever was
+generated by medium is transfered through the outlet
 boundary. One can see that the volumetric mass transfer coefficient based
-on the difference between unit cells averages is constant for internal
+on the difference between unit cells averages, Eq. \ref{volumetric:between:adjacent:cells}, is
+constant for internal
 unit cells. This is the indication that the tracer in the slug is not
-mixed.\label{fig:6:units:ca1040}}
+mixed and the volumetric mass transfer coefficient, $\volnondim$, can be
+calculated using the spatial approach, see Fig.
+\ref{fig:periodic:ca1040}.\label{fig:6:units:ca1040}}
 \end{figure}
@@
 \includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scaleu2scaled5.eps}\\
-\caption{The periodic (left) and time unit cells averaging volumetric mass transfer coefficients.
-One can see that they coincide, but are different from spatial based volumetric mass transfer
-coefficient, see Fig. \ref{fig:6:units:ca1040} \label{fig:periodic:ca1040}}
+\includegraphics[width=0.5\textwidth]{Figures/flux_moving_window6scaleu2scaled5.eps}\\
+\caption{The periodic (top left), time unit cells averaging (top right), and spatial location
+(bottom), Eq. \ref{inlet:outlet:spatial:location}, calculated  volumetric mass transfer
+coefficients. One can see that they all coincide. However, the periodic boundary conditions based
+calculations produce the overestimated volumetric mass transfer
+coefficient. \label{fig:periodic:ca1040}}
 \end{figure}
@@
 conditions simulations and calculate the volumetric mass transfer coefficient based on the averaged
-domain concentration through any formulation as they produce consistent results. Formulation of
+domain concentration through any formulation as they produce consistent results. However, the
+result is the volumetric mass transfer coefficient will be overestimated using this
+approach. Formulation of
 \citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
 to be characteristic concentration. A few unit cells simulations are harder to perform, but they
-have indicator of how well the liquid slug is mixed. Finally, a sample of results was
+have indicator of how well the liquid slug is mixed. As well, for velocity patterns for $Ca\geq
+0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
+coefficient based on the spatial location, not time averaged values used in all other
+approaches. Finally, a sample of results was
 compared with the experimental correlation of \citet{yue-mass}. 

### 2012-02-06 Text/paper.tex
Started a new document about definition of the mass transfer.
Need to keep the same Peclet number either with periodic boundary conditions (easiest case). Calculate critical velocities.
Started doing showcases for the second part of the paper.

@@
 \newcommand{\vol}{k_L\,a}
+\newcommand{\lbubble}{L_{\mathrm{bubble}}}
+\newcommand{\lunit}{L_{\mathrm{unit}}}
+\newcommand{\lslug}{L_{\mathrm{slug}}}
+\newcommand{\ububble}{U_{\mathrm{bubble}}}
+\newcommand{\uliq}{U_{\mathrm{liq}}}
+\newcommand{\ugas}{U_{\mathrm{gas}}}
+\newcommand{\uoutlet}{U_{\mathrm{outlet}}}
+\newcommand{\cbubble}{C_{\mathrm{bubble}}}
+\newcommand{\cinlet}{C_{\mathrm{inlet}}}
+\newcommand{\coutlet}{C_{\mathrm{outlet}}}
+\newcommand{\coverall}{C_{\mathrm{overall}}}
+\newcommand{\cstar}{C^{*}}
+\newcommand{\cmedium}{C_{\mathrm{medium}}}
+\newcommand{\volnondim}{\vol \frac{\lunit}{\ububble+\ugas}}
+\newcommand{\omegaplus}{\omega_{+}}
+\newcommand{\omegaminus}{\omega_{-}}
+\newcommand{\holdup}{\varepsilon_{\mathrm{gas}}}
 
@@
 \subsection{Comparison between different boundary conditions}
-The mass transfer coefficient by the definition of used in the paper of \citet{vanbaten} is as
+The mass transfer coefficient by the definition of used in the paper of \citet{vanbaten-circular} is
+as
 follows:
+\begin{equation}
+dd
+\end{equation}
 

### 2012-02-06 ShowCases/binary.cpp

@@ -1,0 +1,432 @@
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+#include <limits>
+//Domain size
+const int NY=202;
+const int NX=3000;
+
+int width=10;
+int len=500;
+//Time steps
+int N=300000;
+int NOUTPUT=50000;
+int NSIGNAL=100;
+
+
+//Fields and populations
+double f[NX][NY][9], f2[NX][NY][9], g[NX][NY][9], g2[NX][NY][9];
+double rho[NX][NY],ux[NX][NY],uy[NX][NY],phase[NX][NY];
+
+double force_x=0.000006;
+double force_y=0.0;
+
+//Binary-liquid parameters
+double aconst=0.04;
+double kconst=0.04;
+double gammaconst=1.0;
+double wall_gradient=0.0;
+
+double tau_gas=0.7;
+double tau_liq=2.5;
+
+//BGK relaxation parameter
+double omega_rho=1.0;
+double omega_phi=1.0;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+double wxx[] = {0.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+double wyy[] = {0.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+double wxy[] = {0.0, 0.0, 0.0, 0.0, 0.0, 1.0/4.0, -1.0/4.0, 1.0/4.0, -1.0/4.0};
+
+double gradstencilx[9]={0.0,4.0/12.0,0.0,-4.0/12.0,0.0,
+			          1.0/12.0,-1.0/12.0,-1.0/12.0,1.0/12.0};
+
[…]

### 2012-02-06 ShowCases/govern.py

@@ -1,0 +1,39 @@
+import numpy
+import os
+import subprocess
+def modify_file(length,width_value,force):
+    f=open("binary.pbs","r+")
+    f2=open("binary_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE1",str(length))
+            line=line.replace("TOCHANGE2",str(width_value))
+            line=line.replace("TOCHANGE3",str(force))
+        f2.write(line)
+            
+            
+    f.close()
+    f2.close()
+def run_simulations():
+    capillary=numpy.linspace(0.03,0.9,30)
+    capillary_str=[str(x) for x in range(3,93,3)]
+    force_init=6e-6/16;
+    width=0.1
+    for i in range(0, len(capillary)):
+        dir_temp=capillary_str[i]
+        os.mkdir(dir_temp)
+        subprocess.call(['cp','main.out',dir_temp+"/"])
+        subprocess.call(['cp','binary.pbs',dir_temp+"/"])
+        os.chdir(dir_temp)
+        os.mkdir("tmp")
+        ratio=capillary[i]/0.05
+        force=force_init*ratio
+        width_value=int(width[i]*200)
+        modify_file(length,width_value,force)
+        subprocess.call(['qsub','binary_new.pbs'])
+        
+        os.chdir("..")
+
+if __name__=="__main__":
+    #modify_file()
+    run_simulations()

### 2012-02-07 ShowCases/binary.cpp
Started doing showcases.

@@ -12,7 +12,7 @@ const int NY=202;
 const int NX=3000;
 
 int width=10;
-int len=500;
+int length=500;
 //Time steps
 int N=300000;
 int NOUTPUT=50000;
@@ -394,7 +394,7 @@ int main(int argc, char* argv[])
 		//Writing files
 		if (counter%NOUTPUT==0)
 		{
-			if (if phase[NX/2][NY/2]!=phase[NX/2][NY/2])
+			if (phase[NX/2][NY/2]!=phase[NX/2][NY/2])
 			{
 				std::cout<<"There were some NaN values.\n";
 				return 0;

### 2012-02-07 ShowCases/copy_to_bugaboo.py

@@ -1,0 +1,11 @@
+import numpy
+import os
+import subprocess
+
+def copy_files(server):
+    subprocess.call(['scp','binary.cpp',server+".westgrid.ca:/home/shurik/ShowCases/"]) 
+    #subprocess.call(['scp','binary.pbs',server+".westgrid.ca:/home/shurik/ShowCases/"]) 
+    subprocess.call(['scp','govern.py',server+".westgrid.ca:/home/shurik/ShowCases/"]) 
+
+if __name__=="__main__":
+    copy_files("bugaboo")

### 2012-02-07 ShowCases/govern.py

@@ -1,4 +1,4 @@
-import numpy
+#import numpy
 import os
 import subprocess
 def modify_file(length,width_value,force):
@@ -15,23 +15,29 @@ def modify_file(length,width_value,force):
     f.close()
     f2.close()
 def run_simulations():
-    capillary=numpy.linspace(0.03,0.9,30)
-    capillary_str=[str(x) for x in range(3,93,3)]
+    capillary=[0.01*x for x in range(9,93,10)]
+    capillary_str=[str(x) for x in range(9,93,10)]
     force_init=6e-6/16;
     width=0.1
-    for i in range(0, len(capillary)):
-        dir_temp=capillary_str[i]
-        os.mkdir(dir_temp)
-        subprocess.call(['cp','main.out',dir_temp+"/"])
-        subprocess.call(['cp','binary.pbs',dir_temp+"/"])
-        os.chdir(dir_temp)
-        os.mkdir("tmp")
-        ratio=capillary[i]/0.05
-        force=force_init*ratio
-        width_value=int(width[i]*200)
-        modify_file(length,width_value,force)
-        subprocess.call(['qsub','binary_new.pbs'])
+    for length in range(200,1400,150):
+        subprocess.call(['mkdir','-p',str(length)])
+        subprocess.call(['cp','main.out',str(length)+"/"])
+        subprocess.call(['cp','binary.pbs',str(length)+"/"])
+        os.chdir(str(length))
+        for i in range(0, len(capillary)):
+            dir_temp=capillary_str[i]
+            subprocess.call(['mkdir','-p',dir_temp])
+            subprocess.call(['cp','main.out',dir_temp+"/"])
+            subprocess.call(['cp','binary.pbs',dir_temp+"/"])
+            os.chdir(dir_temp)
+            subprocess.call(["mkdir","-p","tmp"])
+            ratio=capillary[i]/0.05
+            force=force_init*ratio
+            width_value=int(width*200)
+            modify_file(length,width_value,force)
+            subprocess.call(['qsub','binary_new.pbs'])
         
+            os.chdir("..")
         os.chdir("..")
 
 if __name__=="__main__":

### 2012-02-09 Python/peclet.py
Van Baten works :)

@@ -726,7 +726,27 @@ def check_yue_dependance():
         #pylab.legend(["Simulations","Correlation"])
     #pylab.text(2000,10,r'''$'''+str(p1[0])+r'''Pe^'''+str(p1[1])+r'''$''',bbox=True)
     #pylab.savefig("volumetric_mass_peclet.eps",format="EPS",dpi=300)    
+
+def check_vanbaten_dependance():
+    aver_coefficients=numpy.array([0.21,0.14,0.095,0.074,0.0601])
+    holdups=numpy.array([0.302466666667,0.288423333333,0.271146666667,0.252866666667,0.229446666667])
+    widths=numpy.array([0.092,0.132,0.157,0.167,0.177])
+    velocities=numpy.array([0.0055,0.0143,0.0297,0.0424,0.05538])
+    velocities_liq=numpy.array([ 0.00459266431535,0.0107317293541,0.0208964048893,0.0292353942998,0.0362306511905])    
+    velocities_gas=holdups*velocities    
+    bubble_lengths=numpy.array([1159,1224,1238,1193,1118])
+    omega=1.99
+    diffusion=1.0/3.0*(1.0/omega-0.5)
+
+
+    peclets=velocities*200.0/diffusion
     
+    vanbaten=3000.0/(velocities_liq+velocities_gas)*4.0*numpy.sqrt(diffusion*velocities/numpy.pi)\
+             *numpy.sqrt(bubble_lengths-200.0*(1.0-2.0*widths))/(3000.0*200.0)\
+             +3000.0/(velocities_liq+velocities_gas)*2.0*numpy.sqrt(2.0)*numpy.sqrt(diffusion*velocities)\
+             *numpy.sqrt(200.0*(1.0-2.0*widths))/(3000.0*200.0)
+    pylab.plot(peclets,aver_coefficients,"+-")
+    pylab.plot(peclets,vanbaten)
     
 if __name__=="__main__":
     #modify_file()
@@ -751,7 +771,8 @@ if __name__=="__main__":
     #check_average_sym_concentration("21",["15","20"])
     
     #check_dependance()
-    check_yue_dependance()    
+    #check_yue_dependance()    
+    check_vanbaten_dependance()
     #give_overall_characteristics()     
      
     pylab.show()

### 2012-02-10 Text/paper.tex
Minor changes.
Started doing the Same Peclet simulations.

@@
 \newcommand{\lslug}{L_{\mathrm{slug}}}
+\newcommand{\lfilm}{L_{\mathrm{film}}}
 \newcommand{\ububble}{U_{\mathrm{bubble}}}
@@
 \newcommand{\holdup}{\varepsilon_{\mathrm{gas}}}
+\newcommand{\volfilm}{k_L\, a_{\mathrm{film}}}
+\newcommand{\volcap}{k_L\, a_{\mathrm{cap}}}
+\newcommand{\tfilm}{t_{\mathrm{film}}}
+\newcommand{\tcap}{t_{\mathrm{cap}}}
 
@@
 
+One can see in Appendix that for the two-dimensional geometry one can estimate the impact to the volumetric mass transfer coefficient:
+\beq
+\vol=\volfilm+\volcap,
+\feq
+where $\volfilm$ can be calculated as in Appendix {\color{red} give appendix number here}. For
+example, for the unsaturated film the expression for the volumetric mass transfer coefficient is as:
+\beq
+k_L=2\sqrt{\frac{D}{\pi \tfilm}},
+\feq
+where $\tfilm$ is the contact time of the bubble with the film:
+\beq
+\tfilm=\frac{\lfilm}{\ububble}=\frac{\lbubble-H(1-2\delta)}{\ububble}
+\feq
+Therefore the volumetric mass transfer coefficient can be calculated as (considering that there are
+two films):
+\beqal
+\volfilm&=2\sqrt{\frac{D \ububble}{\pi (\lbubble-H(1-2\delta))}} 2 \frac{
+\lbubble-H(1-2\delta)}{\lunit\,H}\\
+&=4\sqrt{\frac{D \ububble}{\pi}} \frac{
+\sqrt{\lbubble-H(1-2\delta)}}{\lunit\,H}
+\feqal
+The same expression for the coefficient $k_L$ can be used to calculate mass transfer from the caps:
+\beq
+k_L=2\sqrt{\frac{D}{\pi \tcap}},
+\feq
+where $\tcap$ is the time when the fluid interacts with bubble caps. It can be estimated due to
+following explanations: if there is a vortex in front of the bubble then the fluid packet travels
+the distance as half of the circumference and then is leaving with the bubble velocity from the
+bubble surface. Therefore, $\tcap$ can be estimated as:
+\beq
+\tcap=\frac{\pi H(1-2\delta)}{2 \ububble}.
+\feq
 \end{description}
-
-Overall work goal is to compare numerical simulations with given correlations and to establish a
-new one.
+Therefore, the cap volumetric mass transfer coefficient is the following (considering that two rear
+and front bubble caps form a whole circle):
+\beqal
+\volcap&=2 \sqrt{\frac{2 D \ububble}{\pi^2 H(1-2\delta) }} \frac{\pi H(1-2\delta)}{\lunit
+H}=2\sqrt{2} \sqrt{D \ububble}\frac{\sqrt{H (1-2\delta)}}{\lunit H}
+\feqal
+Therefore, the whole volumetric mass transfer correlation is the sum of contributions from film and
+width:
+%\beq
+\begin{multline}
+\volnondim=\\
+\frac{\lunit}{\ububble+\ugas}\Bigl(4\sqrt{\frac{D \ububble}{\pi}} \frac{
+\sqrt{\lbubble-H(1-2\delta)}}{\lunit\,H}+2\sqrt{2} \sqrt{D \ububble}\frac{\sqrt{H
+(1-2\delta)}}{\lunit H}\Bigr)
+\end{multline}
+%\feq
+
+Some results:
+200
+Bubble velocities= [0.0041703652250000001, 0.0097256202740000006, 0.01588329539, 0.02169746379,
+0.028008169950000002, 0.034069223429999997, 0.040563539609999998, 0.047033809750000002,
+0.053112798260000003]
+Liquid velocities= [0.003537420725238904, 0.007658332369944002, 0.011807274133101,
+0.01596516025341501, 0.020125845424484007, 0.024289948286241009, 0.028452175441002994,
+0.03260953169443101, 0.036767336801079013]
+Gas velocities= [0.00045059406134383335, 0.0010532846756742, 0.0017299026452428667,
+0.0023709541932125998, 0.0030704423110520002, 0.0037603337540471999, 0.0044949810359827995,
+0.005218714750494167, 0.0059203065793813339]
+Holdups= [0.10804666666666667, 0.10829999999999999, 0.10891333333333333, 0.10927333333333333,
+0.10962666666666666, 0.11037333333333334, 0.11081333333333333, 0.11095666666666666,
+0.11146666666666667]
+Widths= [0.083691708460646039, 0.11453052579506764, 0.13337291846007834, 0.14494545818883292,
+0.15412449600357994, 0.16018690601288671, 0.16531042826765582, 0.16967458296893251,
+0.17344750155827895]
+Capillaries= [0.073722338265551551, 0.1719263011747692, 0.28077964694645074, 0.38356059451146424,
+0.49511917250675719, 0.60226447292781515, 0.71706884817900307, 0.83144814548157386,
+0.9389104954359766]
+Reynolds= [1.2511095675000001, 2.9176860822000004, 4.7649886170000002, 6.5092391369999998,
+8.4024509850000015, 10.220767028999999, 12.169061883000001, 14.110142925, 15.933839478000003]
+Bubble lengths= [2.1349999999999998, 2.2999999999999998, 2.4300000000000002, 2.5049999999999999,
+2.5750000000000002, 2.6400000000000001, 2.6899999999999999, 2.7349999999999999, 2.7599999999999998]
+Slug lengths= [12.865, 12.699999999999999, 12.57, 12.495000000000001, 12.425000000000001,
+12.359999999999999, 12.31, 12.265000000000001, 12.24]
+350
+Bubble velocities= [0.0046341367029999999, 0.01080052902, 0.017377746239999999,
+0.024331842780000001, 0.031265874229999997, 0.038061554249999997, 0.045243732449999997,
+0.052329724549999998, 0.059326526419999998]
+Liquid velocities= [0.0038803812007794009, 0.0084385532971600029, 0.013036803534905009,
+0.017645755902851005, 0.02225813959945698, 0.026865244181491992, 0.031470323329384015,
+0.03607200072948101, 0.040659019252402999]
+Gas velocities= [0.00087688679406400325, 0.0020412639830166002, 0.0033112716202111999,
+0.0046254022063354, 0.0060081546116175655, 0.0073038853887274994, 0.0087113790583645007,
+0.010121615322460999, 0.011433012661486266]
+Holdups= [0.18922333333333333, 0.18899666666666667, 0.19054666666666667, 0.19009666666666666,
+0.19216333333333332, 0.19189666666666666, 0.19254333333333334, 0.19342000000000001,
+0.19271333333333332]
+Widths= [0.085334881242557656, 0.11754777714799797, 0.13562130389756313, 0.14771657697902627,
+0.1559458293070895, 0.16216161772762192, 0.16690218748145516, 0.17071829922107651,
+0.17395151438539647]
+Capillaries= [0.081920737190919246, 0.19092818276110241, 0.30719805520107568, 0.4301302757125734,
+0.55270779219396804, 0.67283957781686643, 0.79980375053962127, 0.92506757717322885,
+1.0487547283956218]
+Reynolds= [1.3902410109000001, 3.2401587060000003, 5.2133238720000001, 7.2995528340000009,
+9.3797622690000004, 11.418466275, 13.573119734999999, 15.698917365, 17.797957926000002]
+Bubble lengths= [3.625, 3.9100000000000001, 4.1200000000000001, 4.2649999999999997,
+4.3899999999999997, 4.4749999999999996, 4.5549999999999997, 4.6200000000000001, 4.6550000000000002]
+Slug lengths= [11.375, 11.09, 10.879999999999999, 10.734999999999999, 10.609999999999999, 10.525,
+10.445, 10.379999999999999, 10.344999999999999]
+500
+Bubble velocities= [0.0052657317470000001, 0.01217878658, 0.01962143069, 0.027579066659999998,
+0.03530242384, 0.042899137660000003, 0.050761276039999997, 0.064964573319999996,
+0.080310501160000006]
+Liquid velocities= [0.0043048060885056008, 0.0094048376047090026, 0.014562819556581999,
+0.019728073069401001, 0.024892914265017, 0.030049067027628981, 0.035198125742582999,
+0.044643609849748973, 0.054620418463494469]
+Gas velocities= [0.0014211507887586733, 0.0033086109501886001, 0.0053329740520040667,
+0.0075300964306241995, 0.0096365026356047996, 0.011760655592363467, 0.013922125975237332,
+0.017439956256331733, 0.021556677019696671]
+Holdups= [0.26988666666666666, 0.27167000000000002, 0.27179333333333333, 0.27303666666666665,
+0.27296999999999999, 0.27414666666666665, 0.27426666666666666, 0.26845333333333332,
+0.26841666666666669]
+Widths= [0.089396777499460164, 0.12189600121336229, 0.14008376507935255, 0.15155603520007516,
+0.15974866664944226, 0.16554914994206618, 0.17007608573781216, 0.30999461831205144,
+0.22732300823418256]
+Capillaries= [0.093085865655324646, 0.21529256443354303, 0.34686116743702095, 0.48753362635204572,
+0.6240645822396409, 0.75835677866103002, 0.89734106273915526, 1.1484222582865664,
+1.4197024992681524]
+Reynolds= [1.5797195240999999, 3.6536359740000002, 5.8864292070000008, 8.2737199980000007,
+10.590727152000001, 12.869741298000003, 15.228382812, 19.489371995999999, 24.093150348000005]
+Bubble lengths= [5.1399999999999997, 5.5750000000000002, 5.8650000000000002, 6.085,
+6.2400000000000002, 6.3550000000000004, 6.4500000000000002, 0.38500000000000001, 1.03]
+Slug lengths= [9.8599999999999994, 9.4250000000000007, 9.1349999999999998, 8.9149999999999991,
+8.7599999999999998, 8.6449999999999996, 8.5500000000000007, 14.615, 13.970000000000001]
+
+650
+Bubble velocities= [0.0058695922599999997, 0.014085166979999999, 0.022472028200000001,
+0.031304453740000002, 0.04025350363, 0.049387996580000003, 0.1094018549, 0.15286911380000001,
+0.099952447360000002]
+Liquid velocities= [0.0048267119263748015, 0.010635775511508006, 0.016503260202420003,
+0.022370510614027995, 0.028237291072309011, 0.034083362994406008, 0.046219448474894988,
+0.067168537760430982, 0.067247061842290498]
+Gas velocities= [0.0020611073220990002, 0.0049701389711193991, 0.0079327008613606677,
+0.011103168000682334, 0.0142102918514626, 0.017489606602220133, 0.0380718455052,
+0.053700371859376671, 0.035093637442920531]
+Holdups= [0.35115000000000002, 0.35286333333333331, 0.35300333333333334, 0.35468333333333335,
+0.35302, 0.35412666666666665, 0.34799999999999998, 0.35128333333333334, 0.35110333333333332]
+Widths= [0.095686850123114092, 0.12704971860959374, 0.14492911134976988, 0.155909577069202,
+0.16366636791645661, 0.16914779849407549, 0.1413349338842142, 0.18097719638547718,
+0.25542130684882919]
+Capillaries= [0.10376071224615181, 0.24899292714257107, 0.39725308818088317, 0.55338978802236449,
+0.71158813458225767, 0.87306468227340051, 1.933969836854418, 2.702369675048951, 1.7669263331111857]
+Reynolds= [1.7608776779999999, 4.2255500939999999, 6.7416084600000001, 9.391336122000002,
+12.076051089000002, 14.816398974000002, 32.82055647, 45.860734140000005, 29.985734208]
+Bubble lengths= [6.6900000000000004, 7.29, 7.6600000000000001, 7.9249999999999998,
+8.1099999999999994, 8.2699999999999996, 0.53500000000000003, 1.645, 0.81000000000000005]
+Slug lengths= [8.3099999999999987, 7.71, 7.3399999999999999, 7.0750000000000002, 6.8900000000000006,
+6.7300000000000004, 14.465, 13.355, 14.19]
+
+800
+Bubble velocities= [0.0068458110670000004, 0.01639621631, 0.026605047409999999,
+0.036840145929999998, 0.047125554479999998, 0.098226389829999997, 0.088886650849999999, 0.155738557,
+0.1598356065]
+Liquid velocities= [0.0054993290778350004, 0.012256252057892001, 0.019051401038488,
+0.025834965312065014, 0.032605613362688031, 0.054062078686480969, 0.059582587094709517,
+0.077607375795613484, 0.084522484007136495]
+Gas velocities= [0.0029579152264591368, 0.0070805967053647672, 0.011559094948222701,
+0.016054075992888966, 0.020507156287516797, 0.042450171471531663, 0.038447624536331333,
+0.067548224763348333, 0.06939502609607251]
+Holdups= [0.43207666666666666, 0.43184333333333336, 0.43447000000000002, 0.43577666666666665,
+0.43515999999999999, 0.43216666666666664, 0.43254666666666669, 0.43372833333333333,
+0.43416500000000002]
+Widths= [0.10003982925931058, 0.13317387670353664, 0.15015330462158188, 0.16056724856591476,
+0.16754248421583459, 0.17575649947662744, 0.091940069806373592, 0.18678182336855095,
+0.10494658358534029]
+Capillaries= [0.12101798570494038, 0.28984689346506176, 0.47031523593501479, 0.65124792517512475,
+0.83306997849960196, 1.7364136585066581, 1.5713088393249, 2.7530947436726914, 2.8255210307803655]
+Reynolds= [2.0537433201000002, 4.9188648930000003, 7.9815142230000005, 11.052043779,
+14.137666343999999, 29.467916948999999, 26.665995254999999, 46.721567100000001, 47.950681950000003]
+Bubble lengths= [8.2899999999999991, 9.0649999999999995, 9.5299999999999994, 9.8399999999999999,
+10.055, 7.1200000000000001, 5.9649999999999999, 3.585, 5.4699999999999998]
+Slug lengths= [6.7100000000000009, 5.9350000000000005, 5.4700000000000006, 5.1600000000000001,
+4.9450000000000003, 7.8799999999999999, 9.0350000000000001, 11.414999999999999, 9.5300000000000011]
+
+950
+Bubble velocities= [0.0081105889820000006, 0.01968896174, 0.031648192290000002,
+0.043746032820000003, 0.056154315660000002, 0.09110329466, 0.12485531280000001, 0.13740875180000001,
+0.20420121150000001]
+Liquid velocities= [0.0064009034784269989, 0.014478691581925994, 0.022535789859960999,
+0.030564372867634991, 0.038537555847714004, 0.053671674539171009, 0.072182391854489547,
+0.079464538286806011, 0.11495232139103347]
+Gas velocities= [0.0041692753014937068, 0.0101189449966556, 0.016351882498422902,
+0.022612178544548601, 0.029043012059352002, 0.046834078041163928, 0.064378728754688003,
+0.07078199622721601, 0.10522080026172]
+Holdups= [0.51405333333333336, 0.51393999999999995, 0.51667666666666667, 0.51689666666666667,
+0.51719999999999999, 0.51407666666666663, 0.51562666666666668, 0.51512000000000002,
+0.51527999999999996]
+Widths= [0.10534960942798749, 0.13968846394555789, 0.15578372184740735, 0.16543619956323713,
+0.17153030593666954, 0.19424048762229987, 0.19865767560879785, 0.17950947813380666,
+0.12066555457759411]
+Capillaries= [0.14337631171472745, 0.34805495902191214, 0.55946628451387026, 0.77332791142578172,
+0.99267743490189853, 1.6104939360630546, 2.207150958701189, 2.4290665048039806, 3.6098015344539602]
+Reynolds= [2.4331766946000006, 5.9066885220000005, 9.4944576870000024, 13.123809846000002,
+16.846294698000001, 27.330988397999999, 37.456593840000004, 41.222625540000003, 61.26036345]
+Bubble lengths= [9.9499999999999993, 10.914999999999999, 11.449999999999999, 11.789999999999999,
+12.035, 8.9499999999999993, 9.1750000000000007, 6.2800000000000002, 4.6050000000000004]
+Slug lengths= [5.0500000000000007, 4.0850000000000009, 3.5500000000000007, 3.2100000000000009,
+2.9649999999999999, 6.0500000000000007, 5.8249999999999993, 8.7199999999999989, 10.395]
+
+1100
+Bubble velocities= [0.0097824175900000001, 0.024498111669999999, 0.039400354679999999,
+0.054303837889999998, 0.09376646777, 0.11965875519999999, 0.1483564782, 0.17728152890000001,
+0.225203454]
+Liquid velocities= [0.0077186053895769999, 0.01770605859890001, 0.027603204679605003,
+0.037367546771407988, 0.055859605054054476, 0.071491609706563986, 0.087203948180378035,
+0.099228457857510055, 0.12788810850038299]
+Gas velocities= [0.005819331967880567, 0.014661466551517132, 0.023538559892925599,
+0.032476410250114496, 0.05588731523006054, 0.071375450320506656, 0.088544833188091004,
+0.10585273262168618, 0.13442619372714001]
+Holdups= [0.59487666666666672, 0.5984733333333333, 0.59741999999999995, 0.59804999999999997,
+0.5960266666666667, 0.59649166666666664, 0.59683833333333336, 0.59708833333333333,
+0.59691000000000005]
+Widths= [0.11146768101104691, 0.14705522853564731, 0.16189749306607318, 0.17031901280973424,
+0.22743073870670458, 0.14494577386922328, 0.15532348617470038, 0.19125412329860453,
+0.089789110604593075]
+Capillaries= [0.1729303453571891, 0.43306952220305733, 0.69650644938457806, 0.95996530041184946,
+1.6575726302019211, 2.1152879307565264, 2.6225967942043553, 3.1339242816077229, 3.9810722367508178]
+Reynolds= [2.9347252770000001, 7.349433501, 11.820106404000001, 16.291151367000001, 28.129940331,
+35.897626559999999, 44.506943460000002, 53.184458670000005, 67.561036200000004]
+Bubble lengths= [11.699999999999999, 12.875, 13.465, 13.82, 12.51, 11.305, 10.44,
+9.6199999999999992, 14.234999999999999]
+Slug lengths= [3.3000000000000007, 2.125, 1.5350000000000001, 1.1799999999999997,
+2.4900000000000002, 3.6950000000000003, 4.5600000000000005, 5.3800000000000008, 0.76500000000000057]
 

### 2012-02-10 Python/SamePeclet/copy_to_checkers.py

@@ -1,0 +1,23 @@
+import numpy
+import os
+import subprocess
+
+def copy_files():
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+    #subprocess.call(['scp','mass_periodic.cpp','shurik@checkers.westgrid.ca:/home/shurik/SamePeclet'])
+    #subprocess.call(['scp','govern.py','shurik@checkers.westgrid.ca:/home/shurik/SamePeclet/'])
+    #subprocess.call(['scp','binary.pbs','shurik@checkers.westgrid.ca:/home/shurik/SamePeclet/'])
+    for counter,dir_temp in enumerate(capillary_str):
+        os.chdir(dir_temp)
+        subprocess.call(['scp','geometry.dat','shurik@checkers.westgrid.ca:/home/shurik/SamePeclet/'+dir_temp+"/"])
+        subprocess.call(['scp','velx0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/SamePeclet/'+dir_temp+"/"])
+        subprocess.call(['scp','vely0200000.dat','shurik@checkers.westgrid.ca:/home/shurik/SamePeclet/'+dir_temp+"/"])
+        print "Done with ",dir_temp 
+        os.chdir("..")
+
+if __name__=="__main__":
+    #modify_file()
+    #run_simulations()
+    #copy_files("42",5,4)
+    #copy_files("60",10,5)
+    copy_files()

### 2012-02-10 Python/SamePeclet/govern.py

@@ -1,0 +1,42 @@
+#import numpy
+import os
+import subprocess
+def modify_file(peclet_str):
+    f=open("binary.pbs","r+")
+    f2=open("binary_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE",peclet_str)
+
+        f2.write(line)
+            
+    f.close()
+    f2.close()
+
+
+def run_simulations():
+    capillary_str=[str(x) for x in [9,21,42,60,84]]
+
+    for capillary in capillary_str:
+        dir_capillary_name=str(capillary)
+        subprocess.call(['cp','main.out',dir_capillary_name+"/"])
+        subprocess.call(['cp','binary.pbs',dir_capillary_name+"/"])
+        os.chdir(dir_capillary_name)
+        for peclet in range(2000,18000,2000):
+            dir_name=str(peclet)
+            subprocess.call(['mkdir','-p',dir_name])
+            subprocess.call(['cp','main.out',dir_name+"/"])
+            subprocess.call(['cp','binary.pbs',dir_name+"/"])
+            subprocess.call(['cp','geometry.dat',dir_name+"/"])
+            subprocess.call(['cp','velx0200000.dat',dir_name+"/"])
+            subprocess.call(['cp','vely0200000.dat',dir_name+"/"])
+            os.chdir(dir_name)
+            modify_file(str(peclet))
+            #subprocess.call(['qsub','binary_new.pbs'])
+ 
+            os.chdir("..")
+        os.chdir("..")
+
+if __name__=="__main__":
+    #modify_file()
+    run_simulations()

### 2012-02-10 Python/SamePeclet/mass_periodic.cpp

@@ -1,0 +1,614 @@
+//Simple mass transfer
+
+
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+#include <limits>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Overall scaling parameter
+double peclet=1000.0;
+double scale_velocity=1.0;
+double scale_diffusion=1.0;
+
+//Other constants
+const int NPOP=9;
+
+//Time steps
+int N=1000000;
+int NOUTPUT=20000;
+int NSIGNAL=1000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+//Boundary conditions
+double conc_inlet=0.0;
+double conc_bubble=1.0;
+double conc_wall=0.0;
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+int *bottom;
+int *bottom_mid;
+int *top;
+int *top_mid;
+
+//BGK relaxation parameter
+double omega=1.99;
+double omega_plus=2.0-omega;
+double omega_minus=omega;
+
+//Diffusion parameter
+double ce=1.0/3.0;
+
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+double weights_trt[]={0.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/3.0,1.0/12.0,1.0/12.0,1.0/12.0,1.0/12.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int pxx[]={0, 1, -1, 1, -1, 0, 0, 0, 0};
+int pxy[]={0, 0, 0, 0, 0, 1, -1, 1, -1};
+
+void writedensity(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iX=0; iX<NX; ++iX)
+	{
[…]

### 2012-02-10 Python/peclet.py

@@ -747,6 +747,7 @@ def check_vanbaten_dependance():
              *numpy.sqrt(200.0*(1.0-2.0*widths))/(3000.0*200.0)
     pylab.plot(peclets,aver_coefficients,"+-")
     pylab.plot(peclets,vanbaten)
+    pylab.ylim(ymin=0.0)
     
 if __name__=="__main__":
     #modify_file()

### 2012-02-10 ShowCases/analysis.py

@@ -1,0 +1,159 @@
+#!/usr/bin/python
+import numpy
+import os
+import subprocess
+import math
+import pylab
+import scipy
+import scipy.optimize
+
+def Get_Zero(prof):
+    zero=0
+    #pylab.figure()
+    #pylab.plot(prof)
+    for counter in range(0, len(prof)/2):
+        if prof[counter]>=0 and prof[counter+1]<0:
+            zero=-(prof[counter]*(counter+1)-prof[counter+1]*counter)/(prof[counter+1]-prof[counter])
+    return (zero-0.5)/(len(prof)-2)
+
+
+def give_overall_characteristics(flag,length_external):
+    capillary_str=[str(x) for x in range(9,93,10)]
+   
+    #for length in range(200,1400,150):
+    #    if not flag:
+    if not flag:    
+        length=length_external
+        print length
+        capillaries_orig=[]
+        reynolds_orig=[]
+        velocities_orig=[]
+        holdups_orig=[]
+        bubble_lengths_orig=[]
+        slug_lengths_orig=[]
+        widths_orig=[]
+        gas_velocities_orig=[]
+        liq_velocities_orig=[]
+        
+        for dir_name in capillary_str:
+            file_dir=str(length)+"/"+dir_name+"/"        
+            phase=numpy.loadtxt(file_dir+"phase300000.dat")
+            velx=numpy.loadtxt(file_dir+"velocityx300000.dat")
+            vely=numpy.loadtxt(file_dir+"velocityy300000.dat")
+            dims=phase.shape
+            center=phase[dims[0]/2,:]
+	   
+            z1 = numpy.min(numpy.where(center < 0.0))
+            z2 = numpy.max(numpy.where(center < 0.0))
+            if z1==0:
+                z2=numpy.min(numpy.where(center>0.0))+dims[1]
+                z1=numpy.max(numpy.where(center>0.0))
+		    
+            pylab.figure()
+            pylab.imshow(phase)
+            prof=phase[:,((z1+z2)/2)%dims[1]]
+            widths_orig.append(Get_Zero(prof))     
+            bubble_lengths_orig.append((z2-z1)/float(dims[0]-2))
+            slug_lengths_orig.append(15.0-(z2-z1)/float(dims[0]-2))
+            velocities_orig.append(velx[dims[0]/2,z2%dims[1]])
[…]

### 2012-02-10 ShowCases/binary.cpp

@@ -17,7 +17,7 @@ int length=500;
 int N=300000;
 int NOUTPUT=50000;
 int NSIGNAL=100;
-
+int NTHRESHOLD=10000;
 
 //Fields and populations
 double f[NX][NY][9], f2[NX][NY][9], g[NX][NY][9], g2[NX][NY][9];
@@ -368,14 +368,18 @@ int main(int argc, char* argv[])
     std::cout<<"Force="<<force_x<<"\n";
 
     init();
-
-
+    double force_x_init=force_x;
+    
 	for(int counter=0;counter<=N;counter++)
 	{
 
+        if (counter<NTHRESHOLD)
+            force_x=0.3*force_x_init+0.7*force_x_init*double(counter)/double(NTHRESHOLD);
+        else
+            force_x=force_x_init;
         collide_bulk();
         update_bounce_back();
-
+        
 		//Streaming
 		for(int iX=0;iX<NX;iX++)
 			for(int iY=1;iY<NY-1;iY++)

### 2012-02-10 ShowCases/copy_from_bugaboo.py

@@ -1,0 +1,19 @@
+#import numpy
+import os
+import subprocess
+
+def copy_files():
+    capillary_str=[str(x) for x in range(9,93,10)]
+    for length in range(200,1400,150):
+        subprocess.call(['mkdir','-p',str(length)])
+        os.chdir(str(length))
+        for i in range(0, len(capillary_str)):
+            dir_temp=capillary_str[i]
+            subprocess.call(['mkdir','-p',dir_temp])
+            os.chdir(dir_temp)
+            subprocess.call(["scp","shurik@bugaboo.westgrid.ca:/home/shurik/ShowCases/"+str(length)+"/"+capillary_str[i]+"/"+"tmp/*300000.dat","."])
+            os.chdir("..")
+        os.chdir("..")
+
+if __name__=="__main__":
+    copy_files()

### 2012-02-10 ShowCases/copy_to_bugaboo.py

@@ -3,9 +3,9 @@ import os
 import subprocess
 
 def copy_files(server):
-    subprocess.call(['scp','binary.cpp',server+".westgrid.ca:/home/shurik/ShowCases/"]) 
-    #subprocess.call(['scp','binary.pbs',server+".westgrid.ca:/home/shurik/ShowCases/"]) 
-    subprocess.call(['scp','govern.py',server+".westgrid.ca:/home/shurik/ShowCases/"]) 
+    subprocess.call(['scp','binary.cpp',server+".westgrid.ca:/home/shurik/ShowCasesScaled/"]) 
+    subprocess.call(['scp','binary.pbs',server+".westgrid.ca:/home/shurik/ShowCasesScaled/"]) 
+    subprocess.call(['scp','govern.py',server+".westgrid.ca:/home/shurik/ShowCasesScaled/"]) 
 
 if __name__=="__main__":
     copy_files("bugaboo")

### 2012-02-10 ShowCases/govern.py

@@ -32,7 +32,8 @@ def run_simulations():
             os.chdir(dir_temp)
             subprocess.call(["mkdir","-p","tmp"])
             ratio=capillary[i]/0.05
-            force=force_init*ratio
+            ratio2=1.0/(1.0+(length-200.0)*(length-200.0)/(150.0*150.0*26.0))
+            force=force_init*ratio*ratio2
             width_value=int(width*200)
             modify_file(length,width_value,force)
             subprocess.call(['qsub','binary_new.pbs'])

### 2012-02-18 Text/introduction.tex
Van Baten works :)
Need to work on the paper.

@@
 
-\title{Lattice Boltzmann study of mass transfer for complicated geometries}
+\title{Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow}
 
@@
 coefficient
-in the context of lattice Boltzmann simulations. The novelty of this work lies in the establishing
-a thorough procedure of how to measure the volumetric mass transfer coefficient in case of mass
-sources to be comparable of the representative unit cell, which accounts for the inhomogenous
-situation. The strategies of how to speed up simulations, what the boundaries conditions are
+in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
+novelty of this work lies in the establishing
+a thorough procedure of how to measure the volumetric mass transfer coefficient depending on the
+capillary number $Ca$ regime. For example, for $Ca<0.7$ the flow has a vortex in front of the
+bubble, but for the larger capillary number it hasn't. In case of mass
+sources to be comparable of the representative unit cell (inhomogenous
+situation), one cannot estimate  the strategies to measure the volumetric mass transfer coefficient
+are presented. The strategies of how to speed up simulations, what the boundaries conditions are
 thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
@@
 \beq
-\label{concentration:domain:coordinate}
+%\label{concentration:domain:coordinate}
 C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).

### 2012-02-18 Text/introduction.tex
Started editing the text. More stuff in the introduction.

@@
 novelty of this work lies in the establishing
-a thorough procedure of how to measure the volumetric mass transfer coefficient depending on the
-capillary number $Ca$ regime. For example, for $Ca<0.7$ the flow has a vortex in front of the
-bubble, but for the larger capillary number it hasn't. In case of mass
-sources to be comparable of the representative unit cell (inhomogenous
-situation), one cannot estimate  the strategies to measure the volumetric mass transfer coefficient
-are presented. The strategies of how to speed up simulations, what the boundaries conditions are
-thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
-domain concentration is taken as the characteristic concentration. Though more difficult to setup
-simulations with a few unit cells can give additional information about how well the liquid slug is
-mixed. The work is of use to people performing mass transfer numerical simulations within the
+a thorough procedure of how to measure the volumetric mass transfer coefficient addressing the
+following challenges: the flow pattern  depends on the capillary number $Ca$ regime, i.e. for
+$Ca<0.7$ the flow has a vortex in front of the
+bubble, but for the larger capillary number it hasn't;  the mass sources is comparable of the
+representative unit cell size (inhomogenous situation is different from the homogenous well-mixed
+media \cite{jos-mass}); the connection between time and space domains for moving bubbles; the
+definition of the mass transfer coefficient which is defined through the characteristic
+concentration (inlet/outlet concentration, average concentration). The following boundary conditions
+were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
+simulations. It was shown that the time dependent average concentration to be a characteristic
+concentration produce robust results, though a bit overpredicted. The inlet/outlet flux averaged
+concentration to be a characteristic concentration produce unreliable results. In comparison, a few
+unit cells open boundaries conditions resemble physical situation most and are harder to conduct
+but provide the volumetric mass transfer coefficient based only on the spatial information for the
+capillary number $Ca>0.7$. As well, a few unit cells simulations can provide more information about
+mixing in the liquid slug in comparision with the periodic boundary conditions. We show
+that all presented in literature strategies are extreme limits of one equation,
+Eq. {\color{red} give equation number here}. Finally, the correlation for different Peclet numbers
+is compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
+comparison. The work is of use to people performing mass transfer numerical simulations for bubble
+train flow in microchannels and within the
 lattice Boltzmann context.
@@
 \section{Introduction}
-The volumetric mass transfer coefficient is a very important characteristic for microchannels 
-design \cite{kreutzer-overview}. It allows to
-properly manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner. Many chemical microchannel configurations
-\cite{kreutzer-pressure-drop}  The flow for microchannels we focus on is the bubble train
-motion, where bubbles organized in a train are traveling through the liquid media. This
+The monolith reactors during last years are getting more attention as alternative to slurry
+reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. The bubble flow we focus in
+this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
+a liquid medium of equal sized, long in comparison with the height bubbles in microchannels, see
+Fig. \ref{fig:benchmark:hydro}. This flow regime
+is usually characterized by surface tension dominance over inertia and viscous effects and by
+comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
+scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
+in macroscopic counterparts: such as thin films \cite{bretherton} which can remarkably enhance mass
+transfer in the film from gas or wall; the plug flow nature that separates liquid slugs from each
+other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
+the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
+\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
+of Bretherton-Taylor bubble train flow: continous flow analyzers, lung openings, chemical reactions
+as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
+lot of different application references in extensive reviews \cite{kreutzer-overview,
+gupta-review,yue-mass}.
+
+Among different applications of microchannel flows, this work is focused on the mass transfer
+study from gas to liquid. The good understanding of mass transfer and how it depends on the
+parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
+manufacture a microchannel with necessary properties to ensure that chemical
+reactions are performed in the best manner \cite{bercic}. A number 
+  This
 configuration is interesting due to several reasons: hydrodynamic velocity patterns are completely

### 2012-02-21 Text/introduction.tex
Made an abstract and introduction.

@@
 $Ca<0.7$ the flow has a vortex in front of the
-bubble, but for the larger capillary number it hasn't;  the mass sources is comparable of the
+bubble \cite{giavedoni-numerical}, but for the larger capillary number it hasn't;  the mass sources are comparable of the
 representative unit cell size (inhomogenous situation is different from the homogenous well-mixed
@@
 this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
-a liquid medium of equal sized, long in comparison with the height bubbles in microchannels, see
+a liquid medium of equal sized, long in comparison with the channel height bubbles, see
 Fig. \ref{fig:benchmark:hydro}. This flow regime
@@
 scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
-in macroscopic counterparts: such as thin films \cite{bretherton} which can remarkably enhance mass
-transfer in the film from gas or wall; the plug flow nature that separates liquid slugs from each
+in macroscopic counterparts: such as thin films \cite{bretherton} can remarkably enhance mass
+transfer in the film from a gas or from walls; the plug flow nature that separates liquid slugs from each
 other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
@@
 \cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
-of Bretherton-Taylor bubble train flow: continous flow analyzers, lung openings, chemical reactions
+of Bretherton-Taylor bubble train flow: continuous flow analyzers, lung openings, chemical reactions
 as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
@@
 manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner \cite{bercic}. A number 
-  This
-configuration is interesting due to several reasons: hydrodynamic velocity patterns are completely
-different for different capillary numbers, the bubble occupies the significant part of the unit cell
-and the flow can be assumed periodic.
-
-For the bubble train the volumetric mass transfer coefficient correlations are represented as a
-function of the diffusion coefficient, slug and bubble lengths, and bubble velocity. For example,
-\citet{yue-mass} established an experimental correlation for a bubble train as: 
+reactions are performed in the best manner. A lot of experiments \cite{bercic-mass,irandoust,kreutzer-overview} confirm 
+a number of parameters involved in mass transfer. 
+For example,
+\citet{yue-mass} established an experimental correlation for the volumetric mass transfer coefficient for a bubble train as
+a function of the diffusion coefficient, slug and bubble lengths, and bubble velocity.  
 \begin{equation}
@@
 diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
-$\ububble$ is the bubble velocity. This correlation is within $10\%$ accuracy for experimental
-results for the following range of
+$\ububble$ is the bubble velocity, $D$ is the diffusiont coefficient. This correlation is within $10\%$ accuracy for experimental
+results for the microchannels with rectangular/square crossections for the following range of
 parameters: bubble velocity $0.4\,\mathrm{m/s}<\ububble<2\,\mathrm{m/s}$, bubble length
@@
 Other correlations can be found in works of \citet{kreutzer-overview}
-and \citet{bercic-mass}. Among a variety of experimental works extensively covered
-\cite{yue-mass}, the numerical validations to the best authors' knowledge are sparse. One of the
-reasons is that the experimental correlations are established for continous system, i.e. one does
+and \citet{bercic-mass}. However, all of them study only a certain set of parameters but do not provide overall picture. 
+For example, in the work of \citet{bercic-mass} the bubble lengths were comparatively large that makes the film saturated
+with the tracer. Thus, the volumetric mass transfer coefficient accounts only the mass transfer from the bubble caps. 
+One can find other correlations and parameters in  the excellent overview of experimental works \cite{yue-mass}.
+
+The same scarcity for parameters study can be found in numerical simulations. There are a number of reasons, such as 
+the decoupling of the mass transfer from the multiphase simulations. Authors \cite{kreutzer-overview,vanbaten-circular} used
+the approximations of bubble shapes obtained from experiments and numerical simulations, obtained hydrodynamic fields with 
+one-component solver around the approximated bubble shape with the imposed free-slip boundary condition at the surface of the bubble.
+After that the tracer concentration is imposed at the bubble surface, and the mass transfer solver is run with the hydrodynamic fields obtained
+from the previous step. The main assumption here is the bubble shape approximation. The approximation as two hemispheres and cylinder
+\cite{vanbaten-circular} for a bubble shape is good only for small capillary numbers, say $Ca<0.1$ and cannot be used for larger capillary numbers, 
+where the bubble shape resembles a bullet shape \cite{kuzmin-binary2d,kuzmin-binary3d}. Therefore, for larger capillary numbers, i.e. $Ca>0.1$, 
+the numerical estimations do require obtaining of hydrodynamic fields and bubble shape from multiphase simulations without analytical estimations.
+
+Another challenge that can be seen in numerical simulations is the transition between continuous picture of experiments with a lot of bubbles to the simulation
+of one unit cell which is usually performed in mass transfer simulations. The experimental correlations are established for continuous system, i.e. one does
 not distinguish separate bubbles, but looks to the system as a whole measuring mass concentration
-in different places. Thus, numerical simulations require a significant computational
-resources to be able to simulate enough number of the unit cells to mimic the continuous picture.
-There are some works as how to avoid large scale numerical simulations by performing numerical
-simulations for one unit cell. For example, \citet{vanbaten-circular} perform numerical
-simulations for one unit cell using periodic boundary conditions and measure the volumetric mass
+in different places \cite{bercic-mass}. In contrast, numerical simulations avoid a significant computational burden to simulate a number of unit cells 
+to mimic the continuous picture but simulate only one unit cell mass transfer.
+The gap between numerical simulations and experiments results in the inconsistency of the characteristic concentration determination involved in
+the volumetric mass transfer definition, Eq. \ref{eq:main:definition}. In experiments the characteristic concentration is taken as the averaged in time location concentration. 
+In numerical simulations by \citet{vanbaten-circular}, the characteristic concentration is taken as the averaged in space inlet/outlet concentration.
+Authors \cite{vanbaten-circular} performed  numerical
+simulations for one unit cell using periodic boundary conditions and measured the volumetric mass
 transfer coefficient as:
@@
 \label{main:simulation:equation}
-k_L a=\frac{\mathrm{Flux}}{\cbubble-\coutlet} \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\
+\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\coutlet\rangle} \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\
 cell\ volume}},
 \end{equation}
-where $\coutlet=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$. 
-The concentration flux is calculated as the difference between overall
-average concentration in the whole domain ($\coverall=\int_{V} C \mathrm{d}V /V$)
+where $\langle\coutlet(t)\rangle=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the averaged in space outlet concentration used as the characteristic concentration in the definition, Eq.
+\ref{eq:main:definition}.
+The averaged in time concentration flux is calculated as the difference between overall
+average concentration in the whole domain ($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$)
 at time
 $t_1$ and at time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
-simulations and correlations of \citet{bercic-mass} was good. However, the numerical model only
+simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass} was good. However, the numerical model only
 accounts for circular capillaries and short contact times when the
 bubble film is not saturated with tracer. As well, authors took the
-approximation of bubble shapes for small capillary numbers $Ca<0.01$ and then derived the
-hydrodynamics fields by imposing a free-slip condition at the bubble surface. {\color{red} Give
-another numerical work by Kreutzer.}
-
-This work aims at the establishing numerical procedures as to how properly obtain the volumetric
-mass transfer coefficient in the range of capillary number $0.1\leq Ca\leq 1.0$, where the
-hydrodynamic velocity pattern changes. The details to obtain velocities and bubble shapes can be
-found in \cite{kuzmin-binary2d}. Fig. \ref{fig:benchmark:hydro} gives the simplified picture for the
-bubble train. Different boundary conditions, i.e. the periodic boundary
-conditions, open boundaries conditions will be examined to determine the volumetric mass transfer
-coefficient. As well, large scale simulations are performed, which simulate from $4$ to $10$ unit
-cells.
+approximation of bubble shapes for small capillary numbers $Ca<0.01$ and then obtained
+hydrodynamics fields by imposing a free-slip condition at the bubble surface. However, it will be shown later that this strategy is good only for small capillary numbers $Ca<0.1$
+where the shape of the bubble is simple. Moreover, the characteristic concentration to be averaged outlet concentration underpredicts the volumetric transfer coefficient for small capillary
+numbers $Ca<0.1$ and overpredicts for larger capillary numbers $Ca>0.7$.
+
+Addressing situations for a rich number of hydrodynamic patterns, shapes, effects for a bubble train authors feel that they need to examine more carefully the strategies and assumptions which stay behind the mass transfer coefficient numerical simulations measurements.
+We aim at establishing numerical simulations procedures as to how properly obtain the volumetric
+mass transfer coefficient via a study of different boundary conditions, different characteristic concentration definitions, and address the following situations:
+\begin{description}
+\item[I] In numerical simulations \cite{vanbaten-circular,kreutzer-overview}, the bubble shape is approximated by two hemispheres and a cylinder which is valid only for the capillary number $Ca\leq 0.1$.
+It is known \cite{kreutzer-overview} that the liquid slug is well mixed with the concentrator.
+Due to homogeneity periodic boundary conditions were used, and the averaged in space inlet/outlet concentration as the characteristic concentration was used \cite{vanbaten-circular}.
+In comparison, we obtain bubble shapes and hydrodynamic fields from multiphase simulations \cite{kuzmin-binary2d,kuzmin-binary3d} and examine different boundary conditions with a few unit cells ($1$ to $10$ unit cells).
+\item[II] The gas holdup, i.e. the ratio of volume occupied by a bubble to an unit cell volume, is
+non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
+to the homogenous advection-diffusion equation with the mass source \cite{jos-mass}.  Therefore, there is a logical
+mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
+all velocity pattern details, on the other hand one needs to mimic the continuous picture which is
+seen in experiments. Thus, a few unit cells simulations are performed and compared with one unit cell simulations to bridge different scales.
+\item[III] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
+the reference frame moving with
+the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
+numbers there is no vortex and streamlines go around the bubble, see Fig.
+\ref{fig:streamlines:tweaked:velocity}.
+Literature results of numerical simulations \cite{kreutzer-overview,vanbaten-circular} are all for $Ca<0.01$.
+For non-homogenous situation, i.e.
+$Ca\geq 0.7$, we want to examine particular questions: whether periodic boundary conditions are valid to calculate the volumetric mass transfer coefficients, whether the change of hydrodynamic pattern significantly changes the way we measure the volumetric mass transfer coefficient (the inlet/outlet averaged in space concentration to be the characteristic concentration).
+There is the indication in literature \cite{bercic-mass,yue-mass} of a number of parameters influencing mass transfer, as the slug length, the film thickness.
+However, to the best authors' knowledge it is not indicated of how the change of the hydrodynamic pattern (capillary number $Ca$ dependency) influence mass transfer.
+\end{description}
 \begin{figure}[htb!]
@@
 \end{figure}
-
-The comparison of volumetric mass transfer coefficient
-correlations with experimental correlations and establishing the Sherwood number as a function of
-other non-dimensional parameters is the goal of the future work. However, as an example we will
-show that one of the most recent correlations for the volumetric mass transfer coefficient by
-\citet{yue-mass} resembles current simulations.
-
-We chose to simulate mass transfer of the bubble train due to different reasons:
-\begin{description}
-\item[I] The gas holdup, i.e. the ratio of volume occupied by bubble to unit cell volume, is
-non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
-to the homogenous advection-diffusion equation with the mass source.  Therefore, there is a logical
-mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
-all velocity pattern details, on the other hand one needs to mimic the continous picture which is
-seen in experiments. One of the goals of this work is to establish certain criteria as how to
-simulate such problems numerically with the help of the lattice Boltzmann method.
-\item[II] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
-the reference frame moving with
-the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
-numbers there is no vortex and stremalines go around the bubble, see Fig.
-\ref{fig:streamlines:tweaked:velocity}. Thus, the problem is interesting because of different
-hydrodynamic patterns depending on the capillary number which governs a number of experimental
-parameters as the slug length, the film thickness and the existence of the vortex in front of the
-bubble. There are some available
-correlations in literature \cite{bercic-mass,kreutzer-overview}. One of the particular goal of
-this work is to study mass transfer dependence on the completely different velocity patterns
-depending on the capillary number $Ca$. 
-\end{description}
+Note that the goal of this paper is to establish procedures and boundary conditions used for the volumetric mass transfer coefficient.
+Though at the end of the manuscript we present comparison of the volumetric mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations \cite{yue-mass}, the thorough
+determination of the Sherwood number as a function of
+other non-dimensional parameters as gas holdup, bubble/slug lenghts, the capillary number is the goal of the future work.
 
@@
 are of general nature to simulate the advection-diffusion equation via the lattice Boltzmann
-framework. In comparison, this work aims to establish the procedure of how to obtain the
+framework. In comparison, this work focuses on the application side as to establish the procedure of how to obtain the
 volumetric mass transfer coefficients for bubble train flow. One should mention the work of
-\citet{inamuro-scalar-boundary} simulates heat and mass transfers in the porous media and the work
+\citet{inamuro-scalar-boundary} about heat and mass transfers in the porous media and the work
 of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While two last works are focused
-at the particular mass transfer problems, both problems are of homogenuous nature and do not
+at the particular mass transfer problems, both problems are of homogeneous nature and do not
 guide as how to simulate the non-homogenous problems.
 
-The overall goal of this paper is to address the questions arised and to establish the numerical
-procedure suitable to measure the volumetric mass transfer coefficient in the context of the
-lattice Boltzmann method. We will utilize the results of numerical simulations of bubble flow
-obtained
-before \cite{kuzmin-binary2d,kuzmin-binary3d}.
-
-The paper is organized as follows. The mass transfer coefficients and volumetric mass transfer
-coefficients definitions are covered. The limiting cases from the continuos representation and their
-application to present simulations are given. The mass transfer simulations benchmarks are
-presented. Finally, numerical simulations of different boundary conditions and large scale
-simulations and comparison between them are presented.
+The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
+for the bubble train to derive expressions to connect space and time domain.
+Then the lattice Boltzmann model used to simulate mass transfer is presented followed by benchmarks.
+Finally, numerical simulations of different boundary conditions and a few unit cells simulations for different hydrodynamic patterns are presented to establish the thorough procedure to determine the volumetric mass transfer coefficient.
 
@@
 from the bubble. However, in the case of complicated geometries and non-homogeneous concentrations, 
-the medium concentration can be the average concentration in the domain, the flux averaged
-concentration at the inlet or outlet. Thus, one needs to establish a thorough definition of the volumetric
+the medium concentration can be the average concentration in the domain or the flux averaged
+concentration at the inlet or outlet, etc. Thus, one needs to establish a thorough definition of the volumetric
 mass transfer coefficient in the case of complex geometries and non-trivial hydrodynamic velocity patterns.
@@
 C(t)$, where $\cstar$ is the imposed point source concentration, $C(t)$ is
-the time dependent average concentration. Therefore one can write the time dependent ODE for the
-average concentration in the domain:
+the time dependent concentration, which do not depend on the location due to homogeneity. Therefore, one can write the time dependent ODE for the
+concentration in the domain:
 \beq

### 2012-02-21 Text/introduction.tex
Finished another iteration.

@@
 that all presented in literature strategies are extreme limits of one equation,
-Eq. {\color{red} give equation number here}. Finally, the correlation for different Peclet numbers
+Eq. \ref{main:main:main}. Finally, the correlation for different Peclet numbers
 is compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
@@
 \section{Introduction}
+\label{intro}
 The monolith reactors during last years are getting more attention as alternative to slurry
@@
 
-Addressing situations for a rich number of hydrodynamic patterns, shapes, effects for a bubble train authors feel that they need to examine more carefully the strategies and assumptions which stay behind the mass transfer coefficient numerical simulations measurements.
-We aim at establishing numerical simulations procedures as to how properly obtain the volumetric
+Addressing situations for a rich number of hydrodynamic patterns, shapes, effects for a bubble
+train authors feel that they need to examine more carefully the strategies and assumptions which
+stay behind the mass transfer coefficient numerical simulations measurements. We aim at establishing
+numerical simulations procedures as to how properly obtain the volumetric
 mass transfer coefficient via a study of different boundary conditions, different characteristic concentration definitions, and address the following situations:
@@
 The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
-for the bubble train to derive expressions to connect space and time domain.
-Then the lattice Boltzmann model used to simulate mass transfer is presented followed by benchmarks.
-Finally, numerical simulations of different boundary conditions and a few unit cells simulations for different hydrodynamic patterns are presented to establish the thorough procedure to determine the volumetric mass transfer coefficient.
+for the bubble train to derive expressions to connect space and time domain. Then the lattice
+Boltzmann model used to simulate mass transfer is presented followed by benchmarks. Finally,
+numerical simulations of different boundary conditions and a few unit cells simulations for
+different hydrodynamic patterns are presented to establish the thorough procedure to determine the
+volumetric mass transfer coefficient.
 
@@
 \item
-The previous consideration is able to predict mass transfer happening in moving with the velocity
+Let us predict mass transfer happening in moving with the velocity
 $U$ liquid, see Fig. \ref{fig:moving:frame}. 
@@
 \feq
+Note that the concentration $C(x)$ does not depend on time.
 
@@
 \subsection{Bubble train}
-In the application to the bubble train flow, if one can think of one bubble to be a point source,
-then all considerations above are valid. For example, the expression
+In the application to the bubble train flow, it is useful to think of one bubble to be a point
+source to make all considerations above valid. For example, the expression
 (\ref{main:mass:transfer:expression}) was used in the experiments by
@@
 
-Though the experimental measurements are straightforward as measuring concentrations at different
+Thus, the experimental measurements are straightforward as measuring concentrations at
+different
 locations and calculating the volumetric mass transfer coefficient through the logarithmic
@@
 geometry. Phases can have different mixing patterns
-from film to slug and from slug to film. As it was mentioned before depending on the capillary
+from film to slug and from slug to film. Also, as it was mentioned before depending on the capillary
 number the mixing velocity pattern is different. Analytical approaches
@@
 such 
-an assumption for bubble caps (slug well mixed and the concentration is uniformly distributed over
+an assumption (slug well mixed and the concentration is uniformly distributed over
 the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
 concentration from film is mixed with the slug and changes the overall concentration in the slug.
-Thus, all estimations for the analytical mass as well do not account mutual mass transfer from
+Thus, all estimations for analytical mass trass calculation  do not account for mutual mass
+transfer from
 neighbouring bubbles.
@@
 Another issue is that if the slug is long enough then the film saturates with the tracer
-concentration and its influence on the mass transfer can be negligible \cite{vanbaten-circular}.
-Mixing patterns of the film and the liquid slugs are of great importance for the analytical
+concentration and its influence on mass transfer can be negligible \cite{vanbaten-circular}.
+Mixing patterns of the film and liquid slugs are of great importance for the analytical
 estimation of the mass transfer \cite{yue-mass}. However, the assumptions usually taken for the
@@
 
-The numerical approach can take into the account the complicated mixing patterns and geometries.
-However, there is a  challenge to restore the continous approach as it is seen in experiments. Next
+In comparison with analytical calculations and simplifications, the numerical approach can take into
+the account the complicated mixing patterns and geometries. However, there are challenges as to
+mimic the continuous picture like moving with bulk velocity $U$ reacting medium as it is seen in
+experiments. Thus, the questions indicated in Section \ref{intro}, as the choice of the
+characteristic concentration, the choice of boundary conditions, arise. Next
 section gives more details about numerical simulations.
@@
 \label{section:cases}
-To restore the continuous picture one needs to perform a number of bubbles simulations. As we saw
-before there are two approaches towards it - either to simulate
+Ideally one needs to mimic the continuous picture as it is seen in experiments. Thus, one needs to
+perform mass transfer simulations for a number of unit cells. As it was indicated above there are
+two approaches towards it - either to simulate
 the bubble train and then to measure concentration along the pipe, Eq.
@@
 moving bubbles which is complicated from the numerical point of view. Therefore, one needs to come
-up with the simple smaller domain calculations of the mass transfer coefficient, which mimic the
+up with simple smaller domain calculations of the mass transfer coefficient, which mimic the
 continuous picture with infinite numbers of the bubbles closely.
@@
 $\ububble$), that the bubble position stands steady. The bubble velocity $\ububble$ is
-different from the bulk velocity $\ugas+\uliq$. In this case we need to perform a coordinate $x$
+different from the bulk velocity $\ugas+\uliq$. In this case one needs to perform a coordinate $x$
 variable change:
@@
 &C(x)=\cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\ugas+\uliq}\bigr)\Bigr)\\
-&C(t)=\cstar \Bigl(1-\exp\bigl(-\vol\, t \frac{\ububble}{\ugas+\uliq}\bigr)\Bigr).
+&\langle C(t)\rangle=\cstar \Bigl(1-\exp\bigl(-\vol\, t \frac{\ububble}{\ugas+\uliq}\bigr)\Bigr),
 \feqal
+where $\langle C(t)\rangle$ is the characteristic concentration averaged in space
+concentration. The geometry is not one-dimensional and one needs the characteristic concentration
+to be only as a function of time. One can have different choices of
+$\langle C(t) \rangle$ as the averaged in whole domain concentration or inlet/outlet averaged in
+space concentrations.  Note that $C(x)$ is not averaged in time as $\overline{C(x)}$ since $C(x)$
+ideally should not depend on time. 
 Therefore, one can obtain the volumetric mass transfer coefficient through the concentration:
@@
 \label{theor:one:concentration:time}
-&\vol\, t \frac{\ububble}{\ugas+\uliq}=\ln \frac{\cstar}{\cstar-C(t)}\\
-&\volnondim=\frac{\lunit}{\ububble t}\ln \frac{\cstar}{\cstar-C(t)},
+&\vol\, t \frac{\ububble}{\ugas+\uliq}=\ln \frac{\cstar}{\cstar-\langle C(t)\rangle}\\
+&\volnondim=\frac{\lunit}{\ububble t}\ln \frac{\cstar}{\cstar-\langle C(t) \rangle},
 \feqal
@@
 \volnondim=\frac{\lunit}{\ububble
-(t_2-t_1)}\ln\frac{C^{*}-C(t_1)}{C^{*}-C(t_2)}.
+(t_2-t_1)}\ln\frac{C^{*}-\langle C(t_1) \rangle}{C^{*}-\langle C(t_2) \rangle}.
 \feq
 Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are
-the cornerstones of the present work. The main questions arisen in the present work are to define
-$C(t)$ and  the boundary conditions to produce a proper volumetric mass transfer coefficient
+cornerstones of the present work. The main questions arisen in the present work are to define the
+characteristic concentration $\langle C(t) \rangle$ and  boundary conditions to calculate a proper
+volumetric mass transfer coefficient
 $\vol$.
 
-Three possible scenarios of conducting numerical simulations are possible: 
+Three possible scenarios of conducting numerical simulations are examined in this work: 
 \begin{enumerate}
-\item As far as the hydrodynamic flow is periodic, one can make an assumption of the same boundary
-conditions applied to the tracer concentration. Therefore, only one unit cell is simulated with
+\item The bubble train multiphase simulations are conducted by applying periodic boundary
+conditions \cite{kuzmin-binary2d,kuzmin-binary3d}. One
+can make an assumption of same boundary
+conditions applied to the tracer concentration to simulate mass transfer. Therefore, only one unit
+cell is simulated with
 periodic boundary conditions, see Fig. \ref{fig:benchmark}. As well, no tracer leaves a
 domain. The situation resembles a situation for the plug flow, where no tracer can leave a unit
-domain. We expect such a situation happening for small Capillary numbers $Ca<0.1$, where the film
-is thin and saturates fast with the tracer. Though easier to implement, it rises certain critisism
-towards the inlet concentration to be equal to the outlet concentration. In the continuous
-formulation there is the concentration difference between inlet and outlet involving the volumetric
-mass transfer coefficient:
-\beq
-\volnondim=\ln\frac{\cstar-\cinlet}{\cstar-\coutlet}.
-\feq
-The concentration $C(t)$ required for calculation the volumetric mass transfer coefficient, Eq.
+domain. We expect such a situation resembles most the mass transfer for small Capillary numbers
+$Ca<0.1$, where the liquid slug is well mixed and one have a homogenuous concentration in the unit
+cell. Though easier to implement, it rises certain critisism
+about the inlet concentration to be equal to the outlet concentration. In the continuous
+formulation as it is seen in experiments there is the concentration difference between inlet and
+outlet involving the volumetric
+mass transfer coefficient, see second equation in system \ref{theor:one:concentration:time}.
+
+One needs also address the choice of the characteristic concentration. For example, the
+characteristic concentration $\langle C(t) \rangle$ required for calculation the volumetric mass
+transfer coefficient, Eq.
 \ref{theor:one:concentration:time}, can be taken as the average concentration in the domain:
@@
 \end{figure}
-\item The second approach is the same as the first one but the concentration is taken as in
+\item The second approach is the same as the first one but the characteristic concentration is taken
+as in
 \cite{vanbaten-circular}. The characteristic concentration is taken as the inlet/outlet
-concentration:
+concentration. For the two-dimensional flow between plates inlet/outlet concentrations can be found
+as:
 \beqal
-&\cinlet=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
-&\coutlet=\frac{\int{U(y) C(\lunit,y,t) \mathrm{d}y}}{\int{U(\lunit,y) \mathrm{d}y}}\\
-&\cinlet=\coutlet.
+&\langle \cinlet(t) \rangle=\frac{\int{U(y) C(0,y,t) \mathrm{d}y}}{\int{U(0,y) \mathrm{d}y}}\\
+&\langle \coutlet(t) \rangle=\frac{\int{U(y) C(\lunit,y,t) \mathrm{d}y}}{\int{U(\lunit,y)
+\mathrm{d}y}}\\
+&\cinlet(\bm{x},t)=\coutlet(\bm{x},t),\,\text{due to periodicity}.
 \feqal
-Therefore the assumptions  of this approach is that the difference between inlet and outlet is not
-considerably large and the tracer is well mixed in the slug.
+Therefore, the assumptions  of this approach is
+that the difference between inlet and outlet is not
+considerably large and the tracer is well mixed in the slug, so that the inlet or outlet
+concentrations equal to the average concentration.
 
 \item
-The approach of \citet{vanbaten-circular} is taken. Periodic boundary conditions were used. By the
-definition the mass transfer coefficient is
-proportional to the gain of the mass in the system divided by the concentration difference
+The approach of \citet{vanbaten-circular} is examined. Periodic boundary conditions were used. We
+used the
+definition of the mass transfer coefficient to be proportional to the gain of the mass in the system
+divided by the concentration difference
 multiplied on the surface area:
 \beq
-\vol=\frac{\dot{m}}{P \Delta C}\frac{P}{V}=\frac{\dot{m}}{V (\cstar-C(t))},
+\vol=\frac{\dot{m}}{P \Delta C}\frac{P}{V}=\frac{\dot{m}}{V (\cstar-\langle C(t) \rangle)},
 \feq
@@
 \beq
-\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(t_2)\mathrm{d}V}-\int_{liq}{C(t_1)\mathrm{d}V}}{
-t_2-t_1 } .
-\feq
+\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(\bm{x},t_2)\mathrm{d}V}-\int_{liq}{
+C(\bm{x},t_1)\mathrm { d } V} } {
+t_2-t_1 },
+\feq
+where the integration element $\mathrm{d}V=\mathrm{d}x\mathrm{d}y=\mathrm{d}\bm{x}$.
 In the approach of \citet{vanbaten-circular} the inlet and outlet concentrations were taken as the
-characteristic concentration $C(t)$.
+characteristic concentration $\langle C(t) \rangle $.
 
@@
 %\end{figure}
-
 \item 
@@
 volumes, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
-bubble train head, after injecting to the pipe and travelling along the pipe. The argument here is
-that behind a certain number of the bubble train head, the influence of the boundaries will be
-diminished. Thus, the average concentration in time will be governed by Eq.
+bubble train head, after injecting to the pipe and travelling along the pipe. One can see that this
+situation corresponds most to the experimental picture. By simulation of a certain number of the
+bubble train head, the influence of the boundaries can be
+diminished. In this case, there is no ambiguity in the choice of the
+characteristic concentration in this case. The average concentration in time will be governed
+by Eq.
 \ref{theor:continuous:mass:transfer}. This simulation statement is of most correspondence to
 experiments and should give right answer. However, one of the
-disadvantages is to simulate a certain number of unit cells, thus increasing a computational
+disadvantages is to simulate a certain number of unit cells ($1$ to $10$ in this case), thus
+increasing a computational
 complexity.
@@
 
-Before all the approaches will be examined we will perform benchmarks of parts of geometries that
-form a problem.
+One can notice that all the examined cases are extreme cases of one equation. The choice of boundary
+conditions to use  or how many unit cells to simulate are not of importance but one needs only to
+understand a proper mass balance for medium, which states:
+\beq
+\label{main:main:main}
+\vol=\frac{\dot{m}-\int{\coutlet(t) u(\lunit,y)\mathrm{d}y}+\int{\cinlet(t) u(0,y)\mathrm{d}y}}{V
+\Delta C}, 
+\feq
+where $\Delta C=\cstar-\langle C(t) \rangle$ with $\langle C(t) \rangle$ to be the average
+concentration in whole liquid domain. Eq. \ref{main:main:main} is nothing else but a proper mass
+balance: whatever was generated by the bubble surface equals to the mass domain change minus
+whatever left domain plus whatever entered domain. Periodic boundary condition is the extreme
+limiting case of Eq. \ref{main:main:main} as $\int{\coutlet(t)
+u(\lunit,y)\mathrm{d}y}=\int{\cinlet(t) u(0,y)\mathrm{d}y}$. Thus, the mass change in the domain is
+only because of the generating bubble surface. In this case, to calculate the volumetric mass
+transfer coefficient one needs to track not only spatial information to calculate the averaged over
+domain characteristic concentration  $\langle C(t) \rangle$ but as well time information to
+calculate the mass change in the domain. It will be shown later, that for $Ca>0.7$ where velocity
+pattern is changed, one can use only spatial information to calculate $\int{\cinlet(t) u(0,y)
+\mathrm{d}y}$ and $\int{\coutlet(t) u(\lunit,y)\mathrm{d}y}$ as far as mass change in the domain is
+zero, i.e. $\dot{m}=0$.
+
+Before we examine all the test cases above, the lattice Boltzmann mass transfer
+benchmarks will be presented.
 
 \section{Validation}
-As for analytical expressions the problem of the mass transfer can be decomposed to the following
-parts: the mass transfer from two hemispheres and the mass transfer from the film. We will examine
+For analytical expressions the problem of the mass transfer can be decomposed to the following
+parts: the mass transfer from two circumferences and the mass transfer from the film. We will
+examine
 these problems with the help of the lattice Boltzmann method and compare them against analytical
@@
 \subsection{TRT $D2Q9$ model}
-The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
+The lattice Boltzmann equation (LBE) operates on a square/cubic grid representing the
 physical domain. It utilizes
@@
 \begin{aligned}
-&f_i^{*}(\bm{x},t)= f_i(\bm{x},t)-\omega \bigl(f_i(\bm{x},t)-f_i^{eq}(\bm{x},t)\bigr),&&\text{
+&f_i^{*}(\bm{x},t)= f_i(\bm{x},t)-\omega \bigl(f_i(\bm{x},t)-eq_i(\bm{x},t)\bigr),&&\text{
 collision step}\\
@@
 (two-relaxation-times) collision operator \cite{ginzburg-main,ginzburg-saturated-flow}. In
-comparison with the widely used BGK collision operator, TRT collision operator have better accuracy
-for diffusion and convection fluxes, larger range of parameters where the LBM scheme is stable.
+comparison with the widely used BGK collision operator, TRT collision operator has better accuracy
+for diffusion and convection fluxes, and larger range of parameters where the LBM scheme is stable.
 
@@
 introduces
-so-called magic (free) parameter
+the free parameter
 $\Lambda=\Bigl(\frac{1}{\omegaplus}-\frac{1}{2}\Bigr)\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}
@@
 
-The parameters $\omegaplus$, $\omegaminus$ and $f_i^{eq}$ fully define the lattice Boltzmann
-procedure. The two-dimensional nine velocities LBM $D2Q9$ is defined on the set of lattice
+The parameters $\omegaplus$, $\omegaminus$ and $eq_i$ fully define the lattice Boltzmann
+procedure. The two-dimensional nine velocities LBM $D2Q9$ we used in this work is defined on the set
+of lattice
 velocities with coordinates:
@@
 u_y}{4} p_i^{xy}\\
-&eq_i^{(a)}=\frac{D_{xx}-D_{yy}}{4} p_i^{xx}+\frac{D_{xy}}{4} p_i^{(xy)},
+&eq_i^{(a)}=\frac{K_{xx}-K_{yy}}{4} p_i^{xx}+\frac{D_{xy}}{4} p_i^{(xy)},
 \end{aligned}
 \end{equation}
-where $D_{xx,yy,xy}$ are components of the diffusion tensor, $c_e=\frac{D_{xx}+D_{yy}}{2}$, the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor  $p_i^{(xy)}=c_{ix} c_{iy}$, the weights
+where $K_{xx,yy,xy}$ are proportional to components of the diffusion tensor,
+$c_e=\frac{K_{xx}+K_{yy}}{2}$, parameters $g^{(u)}$ and $g^{u}_{xy}$ are either zero or one (see
+below), the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor $p_i^{(xy)}=c_{ix} c_{iy}$, the
+weights
 $t_i^{(u,m,a)}$ can be chosen based on stability criteria. Though not the best set of weights for
-stability, but the most spread set of weights, so called ``hydrodynamic`` weights, was chosen:
+stability \cite{kuzmin-stability-optimal}, but the most spread set of weights, so called
+``hydrodynamic`` weights, was chosen:
 \begin{equation}
@@
 \beq
-\partial_t C+ \partial_{\alpha} C u_{\alpha}=\partial_{\alpha\beta} K_{\alpha\beta} C,
-\feq
-where $K_{\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)D_{\alpha\beta}$
+\partial_t C+ \partial_{\alpha} C u_{\alpha}=\partial_{\alpha\beta} D_{\alpha\beta} C,
+\feq
+where $D_{\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)K_{\alpha\beta}$
 with the
@@
 \begin{pmatrix}
-D_{xx} + (g^{(u)}-1) u_x^2 & D_{xy}+(g_{xy}^{(u)}-1)u_x u_y\\
-D_{xy} + (g_{xy}^{(u)}-1) u_x u_y& D_{yy}+(g^{(u)}-1) u_y^2 
+D_{xx} + \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g^{(u)}-1) u_x^2 &
+D_{xy}+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g_{xy}^{(u)}-1)u_x u_y\\
+D_{xy} + \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g_{xy}^{(u)}-1) u_x u_y&
+D_{yy}+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g^{(u)}-1) u_y^2. 
 \end{pmatrix}
 \end{equation}
-We want to resolve the isotropic advection-diffusion equation, $D=D_{xx}=D_{yy}$ or $K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components to be zero $D_{xy}=0$.
-In comparison with the $D2Q5$ model, with the $D2Q9$ it is
+We want to resolve the isotropic advection-diffusion equation, $D=D_{xx}=D_{yy}$ or
+$K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components to be zero $D_{xy}=0$. In
+comparison with the $D2Q5$ model, with the $D2Q9$ it is
 possible to cancel the numerical diffusion by the proper choice
 of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$.  The particular choice of parameters
-used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$. Thus, the diffusion coefficient $K$
-is matched through $\omegaminus$, i.e. $K=c_e
+used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$. Thus, the diffusion coefficient $D$
+is matched through $\omegaminus$, i.e. $D=c_e
 \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
-From hereon, without a loss of generality we refer to diffusion coefficient 
-$K$ as $D$.  Free relaxation parameter $\omegaplus$ can be found through $\Lambda$. For particular
+ Free relaxation parameter $\omegaplus$ can be found through $\Lambda$. For particular
 choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as
-$\omegaplus=2-\omegaminus$.  Fig. \ref{stability:d2q9} shows the stability limits for the $D2Q9$
-model $c_e$ against $U^2=u_x^2+u_y^2$ for two particular choices.
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
-\caption{The stable sub-domains of the $D2Q9$ schemes ($\Lambda=\frac{1}{4}$)
-are plotted for standard (hydrodynamic) weights (left) and uniform weights (right, not mentioned here) when the
-numerical diffusion is removed, partially or completely.
-For particular choice used in this work (hydrodynamic weights, $c_e=\frac{1}{3}$, left picture), the achieved stable velocity is $u_x^2+u_y^2\leq\frac{2}{3}$.
-The non-negativity of populations (green+yellow) is for BGK stability.
-One can see that the achieved maximum stable velocity is twice smaller $u_x^2+u_y^2\leq \frac{1}{3}$ for the BGK collision operator.The proper choice of weights can
-allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1- c_e$ (the
-uniform weights only).
-\label{stability:d2q9}}
-\end{figure}
+ $\omegaplus=2-\omegaminus$.
+
+%Fig. \ref{stability:d2q9} shows the stability limits for the $D2Q9$
+% model $c_e$ against $U^2=u_x^2+u_y^2$ for two particular choices.
+% \begin{figure}[htb!]
+% \includegraphics[width=\textwidth]{Figures/d2q9_stability.eps}
+% \caption{The stable sub-domains of the $D2Q9$ schemes ($\Lambda=\frac{1}{4}$)
+% are plotted for standard (hydrodynamic) weights (left) and uniform weights (right, not mentioned
+%here) when the
+% numerical diffusion is removed, partially or completely. For particular choice used in this work
+%(hydrodynamic weights, $c_e=\frac{1}{3}$, left picture), the achieved stable velocity is
+%$u_x^2+u_y^2\leq\frac{2}{3}$. The non-negativity of populations (green+yellow) is for BGK
+%stability. One can see that the achieved maximum stable velocity is twice smaller $u_x^2+u_y^2\leq
+%\frac{1}{3}$ for the BGK collision operator.The proper choice of weights can
+% allow to obtain  total triangle $0 \leq u_x^2+u_y^2 \leq 1- c_e$ (the
+% uniform weights only).
+% \label{stability:d2q9}}
+% \end{figure}
+
 Boundary conditions for the mass transfer used in this work are all of Dirichlet type. We validated
 two types of boundary conditions: Inamuro boundary conditions \cite{inamuro-scalar-boundary} and
-Pressure anti bounce-back boundary conditions \cite{ginzburg-multireflection}. However, the
+pressure anti bounce-back boundary conditions \cite{ginzburg-multireflection}. However, the
 simulation results presented in this work are only pressure anti bounce-back due to its simplicity
@@
 Note that the parameters of the lattice
-Boltzmann are connected with the physical parameters only through the non-dimensional
+Boltzmann scheme are connected with the physical parameters only through the non-dimensional
 numbers governing the physics of the problem. In our case, this number is the Peclet number, $Pe=\frac{\ububble L}{D}$.
@@
 $\ububble$ in the lattice Boltzmann units as soon as the
-Peclet number is the matched in physical space and numerical simulations.
-This fact that $\ububble$ can be chosen arbitrarily is extremely useful in the context of numerical simulations, since can increase the time step, or decrease the computational demand by order of magnitude to obtain meaningful results.
-This point will be extensively covered later.
-
-Next section will cover LBM benchmarks for problems that form the mass transfer problem, as mass transfer from the film  and hemispheres.
+Peclet number is the matched in physical space and numerical simulations. This fact that $\ububble$
+can be chosen arbitrarily is extremely useful in the context of numerical simulations, since it can
+increase the time step, or decrease the computational demand by order of magnitude to obtain
+meaningful results. This point will be extensively covered later.
+
+Next section will cover LBM benchmarks that resemble the mass transfer problem from a bubble, as as
+mass transfer from the film  and circumferences.
 
@@
 \includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
-\caption{Profiles for different diffusion parameters varied with $\omegaminus$. One can see that the diffusion from the non-linear boundaries is captured
-accurately \label{fig:cylinder:benchmark}.}
+\caption{Profiles for different diffusion parameters varied with $\omegaminus$. One can see that the
+diffusion from curved boundaries is captured
+accurately \label{fig:cylinder:benchmark}. $x$ is the distance from the center.}
 \end{figure}
@@
 &C(x,y)=\cstar+\sum_{m}{C_m
-\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
-\frac { x }{H}\Bigr)}\\
-&C_m = (C_0-\cstar \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+\sqrt{\frac{y}{\delta}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{\delta^2}\Bigr)\exp\Bigl(-\frac{
+m^4 } { Pe }
+\frac { x }{\delta}\Bigr)}\\
+&C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
 \xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
@@
 performed on grid $80\times 1600$. The constant concentration is imposed with the
-anti bounce-back conditions, Eq. \ref{antibb}. \label{fig:parabolic:zero:gradient}}
+anti bounce-back conditions, Eq. \ref{antibb}. Coordinate $x$ and $y$ are non-dimensionalized on
+the height of the channel. $\delta=H/2$ is the half of the channel height
+\label{fig:parabolic:zero:gradient}}
 \end{figure}
@@
 \label{sec:numerics}
-The code was utilized to obtain the flow patterns for different capillary numbers
+The multiphase code was utilized to obtain the flow patterns for different capillary numbers
 \cite{kuzmin-binary2d}. Five particular cases were chosen to examine, their results are summarized
@@
 
-Given all the considerations above, one needs to approach the mass transfer in the following
-steps:
+Given all the considerations above, the approach we take for mass transfer is:
 \begin{description}
@@
 $202\times 3000$ which corresponds to fluid domain size $200\times3000$. The grid resolution is
-taken to insure grid
-independency of results.  
+taken to ensure grid
+independency of results \cite{kuzmin-binary2d}.  
  \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
-are conducted in the moving reference frame with the bubble. Then the bubble stands still and the
+are conducted in the reference frame moving with the bubble. Then the bubble stands still and the
 flow is coming around the
-bubble. We impose a steady concentration of the trace on the surface
+bubble. We impose a steady concentration on the surface
 of the bubble with the anti bounce-back condition, Eq. \ref{antibb}.
@@
 perform fast simulations, one needs to improve velocity. This issue arises because of the
-multiphase model used in simulations.The binary liquid lattice Boltzmann model is the diffusive
+multiphase model used in simulations. The binary liquid lattice Boltzmann model is the diffusive
 interface model. Thus, the
@@
 
-Thus, before performing the mass transfer simulations one additional one-component hydrodynamic
-simulation is performed. A special additional free-surface solver was developed in order to dispose
-the normal to surface velocity components. We take results from the multiphase simulations, extract
+Thus, before performing the mass transfer simulations one additional single phase hydrodynamic
+simulation is performed. An additional free-surface solver was developed in order to obtain
+consistent with the advection-diffusion equation velocity field. We take results from the
+multiphase simulations, extract a
 bubble shape using the phase indicator $\phi<0$, approximate the bubble shape by the stair-case
@@
 condition on the bubble surface is imposed. Appendix \ref{appendix-free-surface} covers the simple
-free-slip boundary conditions drastically improving velocity patterns. The system is tterate until a
+free-slip boundary conditions implementation drastically improving velocity patterns. The system is
+iterated until a
 steady state is reached. Note, that these type of simulations are much faster than original
 multiphase simulations. As the output all the non-zero velocity components perpendicular to the
-bubble surface are completely illuminated. We compared original multiphase simulations with
+bubble surface are completely eliminated. We compared original multiphase simulations with
 one-component free-slip simulations. All quantities as superficial slug and bubble velocities are
-within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. This small trick helps to
-make mass transfer simulations stable and faster, since the velocity scaling can be done easier. One
+within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. This simulation helps to
+make mass transfer simulations stable and faster, since the velocity scaling can be done easier and
+streamlines are non-penetrating through the interface. One
 can see in Fig. \ref{fig:free:surface} two streamlines profiles for $Ca=0.097$  and $Ca=1.040$.
@@
 rate over mass diffusion rate), the Peclet number (convection over diffusion), the Reynolds number
-(inertia over viscous forces) and the Sherwood
-number (convection mass transfer over diffusion mass transfer):
+(inertia over viscous forces). As the output one can obtain the Sherwood number dependancy on other
+parameter (convection mass transfer over diffusion mass transfer):
 \begin{equation}
@@
 velocity while keeping the Peclet number the same. After that we will examine the periodic boundary
-conditions for $5$ capillary cases, open boundary simulations, and finally we will examine many
+conditions for $5$ capillary number cases,  and finally we will examine
+many
 cells simulations for two representative cases velocity patterns, as $Ca=0.0907$ and $Ca=1.04$
@@
 This section addresses the performance of the simulations. The ulimate goal is to increase
-velocity at least by several orders while keeping dimensionless parameters the same to speed up
+velocity at least by several orders of magnitude while keeping dimensionless parameters the same to
+speed up                                      
 simulations. Increasing velocity can also help to resolve a lot of unit cells to represent a
@@
 With the given bubble shape and velocity pattern only nondimensional parameter Peclet number governs
-the advection-diffusion equation:
+the advection-diffusion equation represented in the lattice Boltzmann system as:
 \beq
@@
 \end{tabularx}
-\caption{Table representing how one can speed up simulations. One iteration in the lattice
+\caption{This table presents the achievable stable velocity $\ububble$ when one scales velocity. One
+iteration in the lattice
 Boltzmann system corresponds to time difference as
 $\Delta t=\frac{U_{\mathrm{bubble,LB}}}{U_{\mathrm{bubble,phys}}} \Delta x$. Therefore the speed up
-of the simulation is proportional to the  $U_{\mathrm{bubble,LB}}$. Thus, the time iterations
+of the simulation is proportional to the  $U_{\mathrm{bubble,LB}}$. Note that all time
+iterations
 indicated in the table correspond to the one time moment in physical space. One can see that
-scaling produces adequate results.  One can see that the stability limit is approximately around
-$U_{bubble}=0.1$ for the diffusion coefficient
+scaling produces adequate results.  The achievable stable velocity is around $U_{bubble}=0.1$ for
+the diffusion coefficient
 $D=1/3(1/1.99-0.5)=0.000837$. Average concentrations are in the reasonable agreement. The contour
-profiles for all of these cases are presented in Fig. \ref{fig:contours:scaling:peclet}
+profiles for all of these cases (capillary number $Ca$ and all scales) are presented in Fig.
+\ref{fig:contours:scaling:peclet}.
 \label{table:scaling:peclet}}
@@
 \ref{table:scaling:peclet} (top to bottom:
-$Ca=0.097,0.254,0.526,0.750,1.040$).\label{fig:contours:scaling:peclet}}
+$Ca=0.097,0.254,0.526,0.750,1.040$). Thick lines correspond to
+all different scales indicated in Table
+\ref{table:scaling:peclet}. Agreement is reasonable. \label{fig:contours:scaling:peclet}}
 \end{figure}
@@
 \beqal
-&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{\cstar}{\cstar-C(t)}\\
-&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-C(t)},\\
+&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{\cstar}{\cstar-\langle C(t) \rangle}\\
+&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-\langle C(t)
+\rangle},\\
 \feqal
-where $C(t)$ is the average concentrations.
+where $\langle C(t) \rangle$ is the average concentration in the whole liquid domain.
 Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
@@
 close to $\cstar=1$ then Eq. \ref{theor:one:concentration:time} gives inadequate results due to
- accuracy of the logarithmic function. However, the more interesting thing is to put the same plots
-as in Fig. \ref{fig:aver:conc:different:capillaries:time} against the number of unit cells length
-which the bubble passes with the given velocity as $\mathrm{scale}\cdot\frac{\mathrm{\ububble\cdot
-t}}{L}$. Fig. \ref{fig:aver:conc:different:capillaries} shows the volumetric mass transfer
+ accuracy of the logarithmic function. Fig. \ref{fig:aver:conc:different:capillaries:time} presents
+the volumetric mass transfer coefficient against number of time iterations. However, due to scaling
+each simulation has a different physical time step. We scaled curves against number of cell
+units which tracer will pass with the given bubble velocity, i.e. 
+$N_{\text{cell\,units}}=\frac{\text{scale} \ububble t}{\lunit}$.  Fig.
+\ref{fig:aver:conc:different:capillaries} shows the volumetric mass transfer
 dependency against the distance in unit cells length. One can see in Table
 \ref{table:steady:state:average} that for different Peclet numbers different time (number of unit
-cells) is required to achieve the steady state. Also, Table \ref{table:steady:state:average} shows
-the achieved steady state volumetric mass transfer coefficient. One can see tendention that for
+cells) is required to achieve the steady state. For example, for
 larger Peclet number less time steps are required to achieve the steady state condition.
@@
 \begin{description}
-\item Scaling is performed as $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
-\item The larger Peclet number the less time is required. One can extrapolate data from Table
+\item[I] Scaling is performed as $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
+\item[II] The larger Peclet number the less time is required. One can extrapolate data from Table
 \ref{table:steady:state:average}, say $L_{\mathrm{steady}}$ and perform the following number of
@@
 \end{description}
-
+Also, Table \ref{table:steady:state:average} shows
+the achieved steady state volumetric mass transfer coefficient. 
 \begin{figure}[htb!]
@@
 Some simulations show the volumetric mass transfer coefficient going up due to the average
-concentration being close to $\cstar$. All of them show excellent agreement. Note, that with the
+concentration being close to $\cstar$. All of them show an excellent agreement. Note, that with the
 scaling one can reduce the amount of calculations drastically. However, one needs to be attentive
-because with the large velocity scaling average concentration can fastly approach $\cstar$, thus
+because with the large velocity scaling average concentration can quickly approach $\cstar$, thus
 getting an infinite volumetric mass transfer coefficient.
@@
 \caption{Volumetric mass transfer coefficient for different capillaries and scales against the
-bubble traveling distance in the laboratory frame. Table \ref{table:steady:state:average}
+bubble traveling distance in the laboratory frame. ''Cell Units`` axis is refered to the physical
+distance of how many unit cells the bubble passes until the steady state is reached. Table
+\ref{table:steady:state:average}
 summarizes results.\label{fig:aver:conc:different:capillaries}}
@@
 \subsection{Periodic boundaries with the inlet/outlet characteristic concentration}
+\label{results:periodic:inlet:outlet}
 When the characteristic concentration is taken as in the formulation of \citet{vanbaten-circular},
@@
 for small capillary numbers, i.e. $Ca=0.097,0.254,0.526$ the predicted values are overpredicted
-($\volnondim=0.3,0.25,0.1$). When the pattern is changed, i.e. $Ca=0.75,1.04$ the calculated values
-are underpredicted than in previous case, i.e. $\volnondim=0.06,0.04$.
+($\volnondim=0.3,0.25,0.1$). When the velocity pattern is changed from having vortex in front of
+the bubble to not having it,  i.e. $Ca=0.75,1.04$ the calculated values
+are underpredicted than in the previous case, i.e. $\volnondim=0.06,0.04$.
 \begin{figure}[htb!]
@@
 \subsection{\citeauthor{vanbaten-circular} formulation}
+\label{results:vanbaten}
 The van Baten formulation which is calculated as the change of mass in domain with characteristic
@@
 obtained mass transfer coefficient is less than in Section \ref{main:results:periodic}. However, as
-it will be shown later this coefficient coincides with the many units formulation. The inlet/outlet
+it will be shown later the obtained volumetric mass transfer coefficient for $Ca=0.0097$ has the
+same value as for the simulations of a few unit cells. The
+inlet/outlet
 flux averaged concentration is shown to be consistent only for velocity patterns related to larger
@@
 averaged (left) and inlet/outlet flux averaged concentration (right). One can
-see that \citet{vanbaten-circular} formulation is good with the average
-characteristic concentration for capillary numbers regimes without
-vortex. Moreover, the values are more close to values obtained with many cells
-simulations, see Fig. \ref{fig:moving:average:ca0097}. However, the characteristic concentration
-being inlet/outlet flux averaged concentration does not produce consistent results.
+see that \citet{vanbaten-circular} formulation is good with the characteristic concentration being
+the average concentration. Moreover, the values are more close to values obtained with many cells
+simulations, see Fig. \ref{fig:moving:average:ca0097}, than in comparison with periodic boundary
+simulations in Section \ref{main:results:periodic}. However, the characteristic concentration
+being inlet/outlet flux averaged concentration does not produce consistent results as in Section
+\ref{results:periodic:inlet:outlet}.
 \label{fig:vanbaten}}
@@
 \subsection{Performing a number of cell units simulations}
-One needs to examine a few units simulations to obtain a proper volumetric
-mass transfer coefficient. This section studies the quantity of the unit cells on the volumetric
-mass transfer coefficient to be independent of the number of unit cells. We chose two different
+A few unit cells simulations naturally resemble the real experiments picture.  The idea here is
+that if one have enough number of unit cells then results of internal unit cells should be
+independent of boundaries and correspond to experiments. A few unit cells simulations physically
+correspond to the simulation of bubble train head. If boundaries are eliminated then the average
+domain characteristic should be changed in time according to Eq.
+\ref{theor:continuous:mass:transfer}. It means that there is no ambiguity to choose the
+characteristic concentration. The characteristic concentration is the averaged domain concentration
+as it is seen in experiments.
+
+This section studies a number of the unit cells required for the volumetric
+mass transfer coefficient to be independent of boundaries. We chose two
+different
 velocity patterns (see Fig. \ref{fig:streamlines:tweaked:velocity} for $Ca=0.097$ and $Ca=1.04$) to
 perform a few number of cells simulations. For $Ca=0.097$ we performed simulations with
-$4$,$6$,$8$,$10$ number of cells, for $Ca=1.040$ - $4$,$6$,$8$ cells to be examined. However,
+$4$,$6$,$8$,$10$ number of cells, for $Ca=1.040$ only $4$,$6$,$8$ unit cells simulations.
+However,
 simulations with $10$ unit cells domain length produce the same results as $8$ unit cells.
@@
 As it was discussed in the previous section we want to keep
-velocity around $0.05-0.1$ to from . The number of steps for mass to cross whole domain is
+velocity around $0.05-0.1$. The number of steps for mass to cross whole domain is
 limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into the account the bulk
@@
 cross the unit cell $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ time iterations are enough
-for system consisting of $10$ cell units to be stabilized. For more accurate estimations depending
+for system consisting of $10$ cell units. For more accurate estimations of number of time
+iterations depending
 on the Peclet number one can refer to Section \ref{section:keeping:peclet}.
@@
 \subsection{$Ca=0.097$ results}
-To understand the process happening in unit cells one need to keep a track of a few
-characteristics. We chose following representative characteristics: the average concentration in
-the unit cell with time, the concentration difference between adjacent unit cells. The latter is
-the interesting characteristics which shows how well slug liquid is mixed (to be shown later). The
-argument behind this characteristic is that if the following situation is fulfilled: the continuity
-equation is satisfied then the concentration along the coordinate changes according to Eq.
-\ref{main:mass:transfer:expression}:
-\beq
-C(x)= \cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\uliq+\ugas} \bigr)\Bigr)
-\feq
+There are two characteristics we want to track for a few unit cells simulations: the average
+concentration in
+the unit cell with time (see Eq. \ref{theor:continuous:mass:transfer}), and the accumulated mass
+rate in the domain adjusted with inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
+resembles the experimental picture: if one have enough unit cells then the average domain
+concentration should change in time according to Eq. \ref{theor:continuous:mass:transfer}: 
+\beq
+\label{moving:average}
+\vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
+-t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
+\feq
+The
+latter is the main equation that can help to obtain the volumetric mass transfer coefficient from
+mass transfer simulations with any bounary conditions (periodic boundary conditions, open
+boundaries). Eq.\ref{main:main:main} can be rewritten as:
+\beq
+\begin{aligned}
+\volnondim=\frac{\lunit}{\ugas+\ububble} \frac{V \frac{(\langle C(t_2)\rangle - \langle C(t_1)
+\rangle)}{t_2-t-1}}{\dots}\\
+\frac{-\int{\coutlet(\lunit,y,t^*) u(\lunit,y) \mathrm{d} y}+\int{\cinlet(0,y,t^*)
+u(0,y)\mathrm{d} y}}{V (\cstar - \langle C(t^*) \rangle)},
+\end{aligned}
+\feq
+where $t^*$ is medium time between $t_1$ and $t_2$.
+%The
+%argument behind this characteristic is that if the following situation is fulfilled: the continuity
+%equation is satisfied then the concentration along the coordinate changes according to Eq.
+%\ref{main:mass:transfer:expression}:
+%\beq
+%C(x)= \cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\uliq+\ugas} \bigr)\Bigr)
+%\feq
 %After the transition to the reference frame moving with the velocity $\ububble$, one will have the
@@
 %Capillary numbers equal to $0.11,0.04,-0.02,-0.06,-0.10$.
-In the case of present simulations the situation is different as the reference frame is moving with
-the bubble. Thus, the correlation between adjacent cells as follows:
-\beqal
-\label{volumetric:between:adjacent:cells}
-&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq-\ububble}}\Bigr)\\
-&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq-\ububble}}\Bigr)\\
-&k_L\frac{L}{\ugas+\uliq-\ububble}=\frac{C^*-C_1}{C^{*}-C_2}\\
-&k_L\frac{L}{U}=\frac{C^*-C_1}{C^*-C_2},
-\feqal
-where $U=\ugas+\uliq-\ububble$. We will see later that this characteristic is really important to
-see whether the liquid slug is mixed. Fig. \ref{fig:unit:4} shows one of the examples for velocity
-scale $20$ and  $4$ unit numbers (all
-scales produce the same results) for the volumetric mass transfer coefficient $k_L \frac{L}{U}$
-(different from $\volnondim$) based on difference
-between two adjacent cells concentration averages. One can see that this number is changed from
-segment to segment. The same dependencies can be found for
-$6$ and $8$ unit cells simulations but we do not present them here.
-
-However, if one wants to examine how the average concentration changes in time according to Eq.
-\ref{theor:continuous:mass:transfer} for different unit cells then one will see interesting
-thing for the volumetric mass transfer correlation, see Fig. \ref{fig:moving:average:ca0097}:
-\beq
-\label{moving:average}
-\vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
--t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
-\feq
+%In the case of present simulations the situation is different as the reference frame is moving with
+%the bubble. Thus, the correlation between adjacent cells as follows:
+%\beqal
+%\label{volumetric:between:adjacent:cells}
+%&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq-\ububble}}\Bigr)\\
+%&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq-\ububble}}\Bigr)\\
+%&k_L\frac{L}{\ugas+\uliq-\ububble}=\frac{C^*-C_1}{C^{*}-C_2}\\
+%&k_L\frac{L}{U}=\frac{C^*-C_1}{C^*-C_2},
+%\feqal
+%where $U=\ugas+\uliq-\ububble$. We will see later that this characteristic is really important to
+%see whether the liquid slug is mixed. 
+Fig. \ref{fig:unit:6} shows average concentrations in different units and $\volnondim$ based on Eq.
+\ref{main:main:main} calculated for each unit for velocity
+scale $10$ and  $6$ unit cells (all velocity scales produce same results). One can see that the
+volumetric mass transfer cofficient is consistent for internal segments, i.e. $3-5$. One can see
+that Eq. \ref{main:main:main} for a few unit cells produce the same results as periodic boundary
+conditions in Section \ref{main:results:periodic}. The same dependencies
+can be found for
+$8$ and $10$ unit cells simulations but we do not present them here. As well we do not present $4$
+units cells simulation results which are influenced by inlet and outlet boundaries.
+
+The non-dimensional volumetric mass transfer coefficient calculated based on Eq.
+\ref{theor:continuous:mass:transfer} (averaged domain concentration changes in times) is
+represented in Fig. \ref{fig:moving:average:ca0097} for different unit cells. One can see that the
+results are less than the volumetric mass transfer coefficient , but consistent with the mass flux
+concentration based on \citeauthor{vanbaten-circular} formulation with the characteristic
+concentration being averaged domain concentration (see Section \ref{results:vanbaten}).
 \begin{figure}[htb!]
@@
 %\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
-\caption{Average concentrations (left) and volumetric coefficients (right) $\vol \frac{L}{U}$ (
-different from $\volnondim$) for $4$ units cells. The volumetric
-mass transfer coefficient is calculated based on the difference between averages for different unit
-cells. One can see that the numbers for the volumetric mass transfer coefficient are different for
-different unit cells. This is the indication that the liquid slug is mixed and the spatial location
-does not easily transfers to time domain. 
-\label{fig:unit:4}}
+\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale10.eps}\hfill
+\includegraphics[width=0.5\textwidth]{Figures/right_def_6scale10.eps}\\
+%\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
+\caption{Average concentrations (left) and volumetric coefficients (right) for $6$ units cells. The
+volumetric
+mass transfer coefficient is calculated based on Eq. \ref{main:main:main} and accounts for inlet
+and outlet fluxes. \label{fig:unit:6}}
 \end{figure}
@@
 The same correlations were examined for the different velocity pattern $Ca=1.040$ and initial
-velocity $\ububble=0.055$ and initial diffusion $D=0.0008375$. A few unit cells simulation for
-this
-capillary number are unstable. To improve stability we changed original Peclet number by increasing
-diffusion to reveal all the correlations. The results for unit cells are the same as for $Ca=0.097$:
+velocity $\ububble=0.055$ and initial diffusion $D=0.0008375$. If only velocity scaling is
+performed then a few unit cells simulations for
+this capillary number  are unstable. To improve stability we changed original Peclet number by
+increasing
+diffusion. The results for unit cells are the same as for $Ca=0.097$:
 at least $6$ unit cells are required to be simulated to avoid the influence of boundaries. Thus,
-only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040}. As well the volumetric
-mass transfer coefficient, Eq. \ref{volumetric:between:adjacent:cells}, is shown in Fig.
-\ref{fig:6:units:ca1040}. One can see that the average volume concentration, as well the volumetric
-mass transfer coefficients, come to the constant and are not increasing with time. Thus, all the
+only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040}, that show only the
+average concentration for each unit cell. One can see that the average volume concentration come to
+constant values and are not increasing with time. Thus, all the
 mass generated with medium is transfered through the boundaries. This is the indication that the
-liquid slug is not mixed. Thus, the volumetric mass transfer coefficient $\volnondim$ can be
-calculated according to the definition, Eq. \ref{eq:main:definition}:
+liquid slug is not mixed. Note that the periodic boundary conditions can not show whether the
+liquid slug is mixed or not, since the averaged domain concentration is always increasing in time. 
+Thus, the volumetric mass transfer coefficient $\volnondim$ can be calculated according to the
+definition, Eq. \ref{main:main:main}:
 \beq
 \label{inlet:outlet:spatial:location}
-\vol = \frac{\dot{m}}{V \Delta C},
+\vol =
+\frac{\dot{m}-\int{\coutlet(y)u(\lunit,y)\mathrm{d}y}+\int{\cinlet(y)u(\lunit,y)\mathrm{d}y}}{V
+\Delta C},
 \feq 
 where $V$ is the unit cell volume, $\Delta C$ is the concentration difference between the bubble
-surface concentration $\cstar$ and the average medium concentration $C_{aver}$. Note that in this
-case one can calculate the mass generation as:
-\beq
-\dot{m}=(\coutlet-\cinlet)\uoutlet,
-\feq
-where $\coutlet$ and $\cinlet$ are taken for the current unit. Fig. \ref{fig:periodic:ca1040}
+surface concentration $\cstar$ and the averaged liquid domain concentration $\langle
+C(t)\rangle$. There is no accumulated mass in the domain. Thus, $\dot{m}=0$. As periodic boundary
+conditions this case is another extreme limit of Eq. \ref{main:main:main}. Note that to calculate
+the volumetric mass transfer coefficient one needs only the spatial information and does not
+require the knowledge of how concentration is changed in time.
+
+Fig. \ref{fig:periodic:ca1040}
 (bottom) shows the volumetric mass transfer coefficient, based on spatial calculations of
@@
 \begin{figure}[htb!]
+\begin{center}
 \includegraphics[width=0.5\textwidth]{Figures/aver_units6scaleu2scaled5.eps}
-\includegraphics[width=0.5\textwidth]{Figures/novortex6scaleu2scaled5.eps}\\
-\caption{Results for 6 unit cells. The Peclet number equals to $Pe=2644$.
+\end{center}
+%\includegraphics[width=0.5\textwidth]{Figures/novortex6scaleu2scaled5.eps}\\
+\caption{Results for $6$ unit cells. The Peclet number equals to $Pe=2644$.
 One can see that average concentrations reach certain number and stay.
@@
 generated by medium is transfered through the outlet
-boundary. One can see that the volumetric mass transfer coefficient based
-on the difference between unit cells averages, Eq. \ref{volumetric:between:adjacent:cells}, is
-constant for internal
-unit cells. This is the indication that the tracer in the slug is not
+boundary. O This is the indication that the tracer in the slug is not
 mixed and the volumetric mass transfer coefficient, $\volnondim$, can be
@@
 average volumetric mass transfer coefficient are presented in Fig. \ref{fig:periodic:ca1040}. Note
-that they coincide but are different from calculated coefficients based on spatial location.
-Therefore, the time based simulations do not readily convert to spatial based simulations.
+that they coincide. Therefore, for certain hydrodynamic patterns one can easily convert time
+domain to the spatial domain calculations.
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{Figures/flux_moving_window6scaleu2scaled5.eps}\\
-\caption{The periodic (top left), time unit cells averaging (top right), and spatial location
-(bottom), Eq. \ref{inlet:outlet:spatial:location}, calculated  volumetric mass transfer
+\caption{The periodic (top left, $1$ unit cell, Eq. \ref{theor:continuous:mass:transfer}), unit
+cells averaged domain concentrations in time (top right, $6$ unit cells, Eq.
+\ref{theor:continuous:mass:transfer}), and spatial location
+(bottom, $6$ unit cells, Eq. \ref{inlet:outlet:spatial:location}) calculated  volumetric mass
+transfer
 coefficients. One can see that they all coincide. However, the periodic boundary conditions based
-calculations produce the overestimated volumetric mass transfer
-coefficient. \label{fig:periodic:ca1040}}
-\end{figure}
-
-\subsection{Experiment comparison}
+calculations produce a bit overestimated volumetric mass transfer
+coefficient. As well one can see that the averaged domain concentration simulations (top right)
+reach the steady volumetric concentrations fast and after that start decaying. It is not convenient
+to use them in practical cases for not mixed slug, i.e. $Ca>0.7$. \label{fig:periodic:ca1040}}
+\end{figure}
+
+\subsection{Experiment and Analytical correlations comparison}
 The goal of this paper is not to compare with the experiment correlations, but give the
-procedure to perform numerical simulations in the lattice Boltzmann framework. However, the small
-comparison is performed. 
+procedure to perform numerical simulationsrof  in the lattice Boltzmann framework. However, the
+small comparison is performed.
 Unfortunately the experiments to the best authors' knowledge measuring the mass flux for infinite
@@
 One can see that approximately the volumetric mass transfer correlation should be proportional to
-$Pe^{-0.5}$. Fig. \ref{fig:volume:mass:coefficient} shows a comparison between corelation by
-\citet{yue-mass} and the current simulations coefficients presented in Table
-\ref{table:steady:state:average}. The coefficients are not far from each other, given the difference
-between two-dimensional and three-dimensional cases. The fitting procedure showed that the power of
+$Pe^{-0.5}$. As well one can use analytical estimations for the volumetric mass transfer
+coefficient calculated using Higbie penetration theory \cite{higbie}. One can show following works
+\cite{irandoust,vanbaten-circular} that the analytical expression for the flow between plats has
+the following form:
+\beq
+\label{vanbaten:analytical:expresssion}
+\begin{aligned}
+\volnondim=&\frac{\lunit}{\ugas+\uliq}\Bigl(4 \sqrt{D \ububble}{\pi}
+\frac{\sqrt{\lbubble-H (1-2\delta)}}{\lunit H}\\
+&+2 \sqrt{2} \sqrt{D \ububble} \frac{\sqrt{H
+(1-2\delta)}}{\lunit H}\Bigr),
+\end{aligned}
+\feq
+where $H$ is the channel height, $\delta$ is the film thickness.
+
+Fig. \ref{fig:volume:mass:coefficient} shows a comparison between corelation by
+\citet{yue-mass}, analitical expression, Eq. \ref{vanbaten:analytical:expresssion} and the current
+simulations coefficients presented in Table
+\ref{table:steady:state:average}. The coefficients are close to each other, especially given that
+the correlation by \citet{yue-mass} is for three-dimensional cases. The fitting procedure showed
+that the power of
 the Peclet number $Pe$ is $-0.50038$ which is close to $-0.5$. 
@@
 \includegraphics[width=\textwidth]{Figures/correlations_comparison.eps}
-\caption{Comparison between correlation by \citet{yue-mass} and mass transfer coefficient based
+\caption{Comparison between correlation by \citet{yue-mass}, analytical correlation following work
+\cite{irandoust} and mass transfer coefficient based
 on periodic boundary conditions. The fitting curve is proportional to $Pe^{-0.5}$ which corresponds
-to the correlation by \citet{yue-mass}.\label{fig:volume:mass:coefficient}}
+to all correlations. As well one can see that the deviation from the analytical expression becomes
+larger because the analytical expression does not account for the velocity pattern and a bubble
+shape change.\label{fig:volume:mass:coefficient}}
 \end{figure}
@@
 This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
-the lattice Boltzmann method. Overall, the recipe is to perform periodic boundary
+the lattice Boltzmann method. Overall, the easiest recipe is to perform periodic boundary
 conditions simulations and calculate the volumetric mass transfer coefficient based on the averaged
-domain concentration through any formulation as they produce consistent results. However, the
-result is the volumetric mass transfer coefficient will be overestimated using this
-approach. Formulation of
+domain concentration through any formulation as they produce consistent results. The best accuracy
+is achieved with formulations based on the mass difference or on the averaged domain concentrations
+taken in different times, Eq. \ref{theor:continuous:mass:transfer}. Eq.
+\ref{theor:average:concentration:time} gives a bit overestimated volumetric mass transfer
+coefficient. Formulation of
 \citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
@@
 approaches. Finally, a sample of results was
-compared with the experimental correlation of \citet{yue-mass}. 
+compared with the experimental correlation of \citet{yue-mass} and shows a good agreement. 
 \appendix
@@
 \begin{aligned}
-&\frac{\partial C}{\partial \frac{x}{H}} \frac{U_0}{H}
-\Bigl(\frac{y}{H}\Bigr)^2=\frac{D}{H^2}\frac{\partial^2 C}{\partial \frac{y^2}{H^2}}\\
-&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,H)=0\\
+&\frac{\partial C}{\partial \frac{x}{\delta}} \frac{U_0}{\delta}
+\Bigl(\frac{y}{\delta}\Bigr)^2=\frac{D}{\delta^2}\frac{\partial^2 C}{\partial
+\frac{y^2}{\delta^2}}\\
+&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
 \end{aligned}
@@
 \begin{aligned}
-&\zeta=\frac{x}{H} \frac{D}{U_0 H}=\frac{1}{Pe}\frac{x}{H}\\
-&\xi=\frac{y}{H},
+&\zeta=\frac{x}{\delta} \frac{D}{U_0 \delta}=\frac{1}{Pe}\frac{x}{\delta}\\
+&\xi=\frac{y}{\delta},
 \end{aligned}
@@
 &C(x,y)=\cstar+\sum_{m}{C_m
-\sqrt{\frac{y}{H}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{H^2}\Bigr)\exp\Bigl(-\frac{m^4}{Pe}
-\frac { x }{H}\Bigr)}\\
+\sqrt{\frac{y}{\delta}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{\delta^2}\Bigr)\exp\Bigl(-\frac{
+m^4 } { Pe }
+\frac { x }{\delta}\Bigr)}\\
 &C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2

### 2012-02-21 Benchmarks/cylinder.cpp

@@ -19,7 +19,7 @@ const int NPOP=9;
 
 //Time steps
 int N=64000;
-int NOUTPUT=1600;
+int NOUTPUT=200;
 
 //Fields and populations
 double *f;
@@ -37,7 +37,7 @@ int *bottom;
 int *top;
 
 //BGK relaxation parameter
-double omega=1.0/(0.5+0.5/32.0); ///1.99;
+double omega=1.0/(0.5+0.5/1.0); ///1.99;
 double omega_plus=2.0-omega;
 double omega_minus=omega;
 

### 2012-02-21 Python/benchmarks.py

@@ -5,7 +5,7 @@ import scipy.special
 import math
 #import matplotlib.tri as tri
 
-coeff=32
+coeff=1
 omega=1.0/(0.5+0.5/coeff)
 radius=39
 diffusion=1.0/3.0*(1.0/omega-0.5)
@@ -50,7 +50,7 @@ def read_files(file_dir):
     legs=numpy.ravel(legs)   
     pylab.title(r'''$D='''+str(diffusion)[0:6]+'''$''',fontsize=30)
     pylab.legend(legs,fancybox=True,loc=2)
-    pylab.xlabel(r'''$x$''',fontsize=20)
+    pylab.xlabel(r'''$r$''',fontsize=20)
     pylab.ylabel(r'''$C$''',fontsize=20)
     #pylab.legend(legs,fancybox=True,labelspacing=0.1)
     pylab.savefig("cylinder"+str(diffusion)[2:6]+".eps",dpi=300)        
@@ -1096,7 +1096,7 @@ if __name__=="__main__":
 
     #read_file(file_name)
     
-    #read_files(file_dir)
+    read_files(file_dir)
     #show_bessel()    
     #read_film(file_dir)    
     #film_analytical()    
@@ -1110,5 +1110,5 @@ if __name__=="__main__":
     #comparison_two_analytics(file_dir)    
     #irandoust_construction(file_dir)    
     #final_comparison()
-    final_comparison_zero_gradient()    
+    #final_comparison_zero_gradient()    
     pylab.show()

### 2012-02-21 Python/peclet.py

@@ -670,6 +670,7 @@ def check_dependance():
 def check_yue_dependance():
     aver_coefficients=numpy.array([0.21,0.14,0.095,0.074,0.0601])
     holdups=numpy.array([0.302466666667,0.288423333333,0.271146666667,0.252866666667,0.229446666667])
+    widths=numpy.array([0.092,0.132,0.157,0.167,0.177])
 
     velocities=numpy.array([0.0055,0.0143,0.0297,0.0424,0.05538])
     velocities_liq=numpy.array([ 0.00459266431535,0.0107317293541,0.0208964048893,0.0292353942998,0.0362306511905])    
@@ -728,16 +729,22 @@ def check_yue_dependance():
     
     fig=pylab.figure()
     pylab.plot(peclets_range,p1[0]*numpy.power(peclets_range,p1[1]),"k--")
-
-
+    vanbaten=3000.0/(velocities_liq+velocities_gas)*4.0*numpy.sqrt(diffusion*velocities/numpy.pi)\
+             *numpy.sqrt(bubble_lengths-200.0*(1.0-2.0*widths))/(3000.0*200.0)\
+             +3000.0/(velocities_liq+velocities_gas)*2.0*numpy.sqrt(2.0)*numpy.sqrt(diffusion*velocities)\
+             *numpy.sqrt(200.0*(1.0-2.0*widths))/(3000.0*200.0)
+    #pylab.plot(peclets,aver_coefficients,"+-")
+    
     pylab.xticks(fontsize=16)
     pylab.yticks(fontsize=16)
     pylab.plot(peclets,aver_coefficients,"ko-",markersize=6)
     pylab.plot(peclets,yue_correlation,"ks-",markersize=6)
+    pylab.plot(peclets,vanbaten,"kv-",markersize=6)
     pylab.xlabel(r'''$\mathrm{Peclet}$''',fontsize=30)
     pylab.ylabel(r'''$k_L a\frac{L}{U_{\mathrm{gas}}+U_{\mathrm{liq}}}$''',fontsize=30)
-    pylab.legend(["Fitting","Simulations","Yue correlation"],fancybox=True)
+    pylab.legend(["Fitting","Simulations","Yue correlation","Analytical correlation"],fancybox=True)
     fig.subplots_adjust(left=0.2,bottom=0.15)    
+    pylab.ylim(ymin=0.0)    
     pylab.savefig("correlations_comparison.eps",format="EPS",dpi=300)
     
 
[…]

### 2012-03-05 Text/introduction.tex
Small modifications.

@@
 \label{intro}
-The monolith reactors during last years are getting more attention as alternative to slurry
-reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. The bubble flow we focus in
-this work, so-called Bretherton-Taylor flow \cite{bretherton,taylor}, describes the flow through
-a liquid medium of equal sized, long in comparison with the channel height bubbles, see
+The monolith reactors during last years are getting more attention as a promising alternative to slurry
+reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Monolith reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
+a liquid medium of equally sized, long bubbles, see
 Fig. \ref{fig:benchmark:hydro}. This flow regime
-is usually characterized by surface tension dominance over inertia and viscous effects and by
+is characterized by surface tension dominance over inertia and viscous effects and by
 comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
 scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
-in macroscopic counterparts: such as thin films \cite{bretherton} can remarkably enhance mass
-transfer in the film from a gas or from walls; the plug flow nature that separates liquid slugs from each
+in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
+transfer from gas and walls to liquid; the plug flow nature that separates liquid slugs from each
 other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of

### 2012-04-16 Text/introduction.tex
Rewriting the introduction.

@@
 \newcommand{\feqalstar}{\end{aligned}\end{equation*}}
+\newcommand{\kl}{k_L}
 \newcommand{\vol}{k_L\,a}
@@
 The monolith reactors during last years are getting more attention as a promising alternative to slurry
-reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Monolith reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
+reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
 a liquid medium of equally sized, long bubbles, see
 Fig. \ref{fig:benchmark:hydro}. This flow regime
-is characterized by surface tension dominance over inertia and viscous effects and by
-comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
-scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
+is characterized by surface tension dominance over inertia and viscous effects, and by
+comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance bubble train flow exhibit advantageous properties which can not be achieved
 in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
-transfer from gas and walls to liquid; the plug flow nature that separates liquid slugs from each
-other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
-the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
-\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
-of Bretherton-Taylor bubble train flow: continuous flow analyzers, lung openings, chemical reactions
-as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
-lot of different application references in extensive reviews \cite{kreutzer-overview,
-gupta-review,yue-mass}.
-
-Among different applications of microchannel flows, this work is focused on the mass transfer
-study from gas to liquid. The good understanding of mass transfer and how it depends on the
+transfer from gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.
+Moreover, the low slip velocity between gas and liquid is utilized in the experiments to measure liquid velocity \cite{taylor}:  bubbles travelling with approximately the same velocity as liquid can be captured with a camera.
+Overall, nowadays one can find a large number of applications
+of the Bretherton-Taylor bubble train flow: continuous flow analyzers to measure liquid velocity, lung openings, chemical reactions
+as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. Extensive reviews of \citet{kreutzer-overview,
+gupta-review,yue-mass} cover a significant number of applications.
+
+This work is focused on the mass transfer 
+study from gas to liquid for the Bretherton/Taylor flow. The good understanding of mass transfer and how it depends on the
 parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
 manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner. A lot of experiments \cite{bercic-mass,irandoust,kreutzer-overview} confirm 
-a number of parameters involved in mass transfer. 
+reactions are performed in the best manner.
+Experimental studies \cite{yue-mass,bercic} show a complex dependency of the mass transfer coefficient on flow parameters: bubble and slug lengths, bubble velocity, which are in the turn depend on the capillary number $Ca$ and the Reynolds number $Re$.
 For example,
@@
 
+Thus, the understanding of mass transfer for the bubble train flow is not possible without deep understanding of the hydrodynamic patterns.
+There are a number of studies available for the hydrodynamic study of the bubble train flow: experimental \citet{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \citet{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
+For the flow of long bubbles between parallel plates  It is indicated that  there exists a vortex in front of the bubble for $Ca<0.7$ , see Fig.
+\ref{fig:streamlines:tweaked:velocity}.
+However, for $Ca>0.7$ the vortex in front of the bubble does not exist.
+As well the bubble shape for low capillary numbers ($Ca<0.1$ \cite{cerro-bubble-train}) is symmetric and can be represented as two hemispheres and the cylinder for the cylindrical case.
+This is heavily utilized for the mass transfer analytical estimations.
+
+The mass transfer coefficient is defined as the mass flux from certain area divided by concentration difference between the surface and the surrounding medium.
+Thus, analytical estimations \cite{kreutzer-overview,irandoust} are  based on decomposition of the bubble shape.
+The mass transfer coefficient is calculated through two separate contributions from the film and two hemispheres.
+For both contributions the Higbie penetration theory \cite{higbie} is utilized, which states that the mass transfer coefficient  for simple geometry flow depends on the average time of liquid packet interaction with geometrical feature.
+It can be calculated as $\sqrt{\frac{\pi D}{t_{\mathrm{char}}}}$, where $t_{\mathrm{char}}$ is the characteristic time of the interaction, $D$ is the diffusion coefficient.
+As the example for the Higbie penetration theory, the mass  transfer coefficient for the flow of bubbles in cylindrical channel is calculated as:
+\beq
+k_L=\sqrt{\frac{\pi D}{t_{\mathrm{film}}}}+\sqrt{\frac{\pi D}{t_{\mathrm{hemisphere}}}},
+\feq
+where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through cylinder length with the bubble velocity, $t_{\mathrm{hemisphere}}=\frac{\pi R_{\mathrm{hemisphere}}}{\ububble}$ is the time which liquid in the slug goes the distance of half circumference.
+
+Despite the simplicity, analytical expressions work perfectly for flows with low capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape can be nicely approximated by hemispheres and cylinder.
+Moreover, because of the hydrodynamic pattern in the slug, i.e.
+there is a vortex in slug, one can estimate the time for fluid batch to travel whole circumference (Fig.
+\ref{fig:streamlines:tweaked:velocity}).
+However, with the change of the capillary number the situation drastically changes.
+The symmetrical bubble shape changes and resembles a bullet.
+With the change of the shape for $Ca>0.7$ there is no vortex in front of the bubble and the Higbie theory fails to estimate contribution from bubble caps.
+Thus, the need of numerical simulations where all hydrodynamics fields and complicated bubble shapes are taken in the account is obvious.
+
+However, available numerical studies of mass transfer \cite{kreutzer-overview,vanbaten-circular} are lacking the calculation of  bubble shapes as well.
+The mass transfer simulations are made as follows: first the bubble shape is calculated either through analytical correlations \cite{bretherton} or experimental correlations \cite{cerro-bubble-train} without directly resolving bubbles shapes through multiphase simulations.
+Then the mass .
+The approximations of bubble shapes work well for flows with low capillary numbers, i.e.
+$Ca<0.1$, where the bubble shape is symmetrical.
+However, for flows with larger capillary numbers the correlations are not satisfactory.
+In addition to the bubble shape approximation, numerical simulations are performed with periodic boundary conditions.
+Hydrodynamic boundary conditions are obvious, but what boundary conditions to use for the mass transfer calculations is not obvious.
+and can
+the approximations of bubble shapes obtained from experiments and numerical simulations, obtained hydrodynamic fields with 
+one-component solver around the approximated bubble shape with the imposed free-slip boundary condition at the surface of the bubble.
+
+There are a number of reasons, such as 
+the decoupling of the mass transfer from the multiphase simulations.
+Authors \cite{kreutzer-overview,vanbaten-circular} uAfter that the tracer concentration is imposed at the bubble surface, and the mass transfer solver is run with the hydrodynamic fields obtained
+from the previous step. The main assumption here is the bubble shape approximation. The approximation as two hemispheres and cylinder
+\cite{vanbaten-circular} for a bubble shape is good only for small capillary numbers, say $Ca<0.1$ and cannot be used for larger capillary numbers, 
+where the bubble shape resembles a bullet shape \cite{kuzmin-binary2d,kuzmin-binary3d}. Therefore, for larger capillary numbers, i.e. $Ca>0.1$, 
+the numerical estimations do require obtaining of hydrodynamic fields and bubble shape from multiphase simulations without analytical estimations.
+
 Other correlations can be found in works of \citet{kreutzer-overview}
@@
 One can find other correlations and parameters in  the excellent overview of experimental works \cite{yue-mass}.
-
-The same scarcity for parameters study can be found in numerical simulations. There are a number of reasons, such as 
-the decoupling of the mass transfer from the multiphase simulations. Authors \cite{kreutzer-overview,vanbaten-circular} used
-the approximations of bubble shapes obtained from experiments and numerical simulations, obtained hydrodynamic fields with 
-one-component solver around the approximated bubble shape with the imposed free-slip boundary condition at the surface of the bubble.
-After that the tracer concentration is imposed at the bubble surface, and the mass transfer solver is run with the hydrodynamic fields obtained
-from the previous step. The main assumption here is the bubble shape approximation. The approximation as two hemispheres and cylinder
-\cite{vanbaten-circular} for a bubble shape is good only for small capillary numbers, say $Ca<0.1$ and cannot be used for larger capillary numbers, 
-where the bubble shape resembles a bullet shape \cite{kuzmin-binary2d,kuzmin-binary3d}. Therefore, for larger capillary numbers, i.e. $Ca>0.1$, 
-the numerical estimations do require obtaining of hydrodynamic fields and bubble shape from multiphase simulations without analytical estimations.
 

### 2012-04-23 Text/introduction.tex
Changed introduction considerably.

--- 2012-03-05 Text/introduction.tex
@@
 coefficient
-in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
-novelty of this work lies in the establishing
-a thorough procedure of how to measure the volumetric mass transfer coefficient addressing the
-following challenges: the flow pattern  depends on the capillary number $Ca$ regime, i.e. for
-$Ca<0.7$ the flow has a vortex in front of the
-bubble \cite{giavedoni-numerical}, but for the larger capillary number it hasn't;  the mass sources are comparable of the
-representative unit cell size (inhomogenous situation is different from the homogenous well-mixed
-media \cite{jos-mass}); the connection between time and space domains for moving bubbles; the
-definition of the mass transfer coefficient which is defined through the characteristic
-concentration (inlet/outlet concentration, average concentration). The following boundary conditions
-were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
+in the context of lattice Boltzmann simulations for the Bretherton/Taylor bubble train flow.
+In this work we address the situation when the hydrodynamic pattern changes from having a vortex in slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.
+For the latter case the bubble shape is not symmetric and cannot be approximated through flat surfaces and circumferences as it is done in literature \cite{vanbaten-circular,kreutzer-overview}.
+Moreover, with a vortex in the slug the tracer is well mixed.
+Thus, it is common to  use periodic boundary conditions  and inlet/outlet averaged concentration as the characteristic concentration, Eq.
+\ref{eq:main:definition}.
+The later is not valid for flows where tracer is not well mixed.
+This work through examination of different boundary conditions and different characteristic concentration definitions establishes the procedure to determine the volumetric mass transfer coefficient for flows with the capillary number $0.1<Ca<1.0$.
+With simulations of a few unit cells the connection between time (used in simulations) and space (used in experiments) domains was established.
+The following boundary conditions were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
 simulations. It was shown that the time dependent average concentration to be a characteristic
 concentration produce robust results, though a bit overpredicted. The inlet/outlet flux averaged
-concentration to be a characteristic concentration produce unreliable results. In comparison, a few
-unit cells open boundaries conditions resemble physical situation most and are harder to conduct
+concentration \cite{vanbaten-circular} to be a characteristic concentration produce unreliable results in the range of capillary numbers specified.
+In comparison with works \cite{vanbaten-circular,kreutzer-overview} where only one unit cell was simulated, a few
+unit cells open boundaries conditions resemble physical situation most closely and are harder to conduct
 but provide the volumetric mass transfer coefficient based only on the spatial information for the
-capillary number $Ca>0.7$. As well, a few unit cells simulations can provide more information about
-mixing in the liquid slug in comparision with the periodic boundary conditions. We show
+capillary number $Ca>0.7$. 
+%As well, a few unit cells simulations can provide more information about
+%mixing in the liquid slug in comparison with the periodic boundary conditions. 
+We show
 that all presented in literature strategies are extreme limits of one equation,
-Eq. \ref{main:main:main}. Finally, the correlation for different Peclet numbers
-is compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
-comparison. The work is of use to people performing mass transfer numerical simulations for bubble
-train flow in microchannels and within the
+Eq. \ref{main:main:main}. Finally, simulation results for different Peclet numbers
+are compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
+agreement. The work is of use to people performing mass transfer numerical simulations for bubble
+train flow in microchannels and/or within the
 lattice Boltzmann context.
@@
 The monolith reactors during last years are getting more attention as a promising alternative to slurry
-reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Monolith reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
+reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
 a liquid medium of equally sized, long bubbles, see
 Fig. \ref{fig:benchmark:hydro}. This flow regime
-is characterized by surface tension dominance over inertia and viscous effects and by
-comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance and small
-scales of microchannels, bubble train flow exhibit advantageous properties which can not be achieved
+is characterized by surface tension dominance over inertia and viscous effects, and by
+comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance bubble train flow exhibit advantageous properties which can not be achieved
 in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
-transfer from gas and walls to liquid; the plug flow nature that separates liquid slugs from each
-other allowing to perform chemical reactions in slugs \cite{kreutzer-overview} or be an indicator of
-the liquid velocity \cite{taylor}; the flow pattern depending on the capillary number $Ca$
-\cite{heil-bretherton,heil-threedim}.  Overall, nowadays one can find a large number of applications
-of Bretherton-Taylor bubble train flow: continuous flow analyzers, lung openings, chemical reactions
-as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. One can find a
-lot of different application references in extensive reviews \cite{kreutzer-overview,
-gupta-review,yue-mass}.
-
-Among different applications of microchannel flows, this work is focused on the mass transfer
-study from gas to liquid. The good understanding of mass transfer and how it depends on the
+transfer from a gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.
+Moreover, the low slip velocity between gas and liquid is utilized in the experiments to measure liquid velocity \cite{taylor}:  bubbles travelling with approximately the same velocity as liquid can be captured with a camera.
+Overall, nowadays one can find a large number of applications
+of the Bretherton-Taylor bubble train flow: continuous flow analyzers to measure liquid velocity, lung openings, chemical reactions
+as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. Extensive reviews of \citet{kreutzer-overview,
+gupta-review,yue-mass} cover a significant number of applications.
+
+This work is focused on the gas to liquid mass transfer 
+study for the Bretherton/Taylor flow. The good understanding of mass transfer and how it depends on the
 parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
 manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner. A lot of experiments \cite{bercic-mass,irandoust,kreutzer-overview} confirm 
-a number of parameters involved in mass transfer. 
-For example,
+reactions are performed in the best manner.
+The mass transfer coefficient characterizing mass transfer is defined as the flux from the surface divided on the concentration difference between the concentration imposed on the body and the characteristic concentration in the domain.
+The characteristic concentration in the domain depends largely on underlying hydrodynamics fields.
+For example, experimental studies \cite{yue-mass,bercic-mass} show a complex dependency of the mass transfer coefficient on flow parameters: bubble and slug lengths, bubble velocity, which are in turn depend on the capillary number $Ca$ and the Reynolds number $Re$.
 \citet{yue-mass} established an experimental correlation for the volumetric mass transfer coefficient for a bubble train as
-a function of the diffusion coefficient, slug and bubble lengths, and bubble velocity.  
+a function of the diffusion coefficient, slug and bubble lengths, and bubble velocity: 
 \begin{equation}
@@
 diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
-$\ububble$ is the bubble velocity, $D$ is the diffusiont coefficient. This correlation is within $10\%$ accuracy for experimental
-results for the microchannels with rectangular/square crossections for the following range of
-parameters: bubble velocity $0.4\,\mathrm{m/s}<\ububble<2\,\mathrm{m/s}$, bubble length
-$1.4<\frac{\lbubble}{d_h}<6.3$, slug length $1<\frac{\lslug}{d_h}<3.2$,
-hydrodynamic diameter $d_h = 400 \mathrm{\mu m}$.
-
-Other correlations can be found in works of \citet{kreutzer-overview}
-and \citet{bercic-mass}. However, all of them study only a certain set of parameters but do not provide overall picture. 
-For example, in the work of \citet{bercic-mass} the bubble lengths were comparatively large that makes the film saturated
-with the tracer. Thus, the volumetric mass transfer coefficient accounts only the mass transfer from the bubble caps. 
-One can find other correlations and parameters in  the excellent overview of experimental works \cite{yue-mass}.
-
-The same scarcity for parameters study can be found in numerical simulations. There are a number of reasons, such as 
-the decoupling of the mass transfer from the multiphase simulations. Authors \cite{kreutzer-overview,vanbaten-circular} used
-the approximations of bubble shapes obtained from experiments and numerical simulations, obtained hydrodynamic fields with 
-one-component solver around the approximated bubble shape with the imposed free-slip boundary condition at the surface of the bubble.
-After that the tracer concentration is imposed at the bubble surface, and the mass transfer solver is run with the hydrodynamic fields obtained
-from the previous step. The main assumption here is the bubble shape approximation. The approximation as two hemispheres and cylinder
-\cite{vanbaten-circular} for a bubble shape is good only for small capillary numbers, say $Ca<0.1$ and cannot be used for larger capillary numbers, 
-where the bubble shape resembles a bullet shape \cite{kuzmin-binary2d,kuzmin-binary3d}. Therefore, for larger capillary numbers, i.e. $Ca>0.1$, 
-the numerical estimations do require obtaining of hydrodynamic fields and bubble shape from multiphase simulations without analytical estimations.
-
-Another challenge that can be seen in numerical simulations is the transition between continuous picture of experiments with a lot of bubbles to the simulation
-of one unit cell which is usually performed in mass transfer simulations. The experimental correlations are established for continuous system, i.e. one does
-not distinguish separate bubbles, but looks to the system as a whole measuring mass concentration
-in different places \cite{bercic-mass}. In contrast, numerical simulations avoid a significant computational burden to simulate a number of unit cells 
-to mimic the continuous picture but simulate only one unit cell mass transfer.
-The gap between numerical simulations and experiments results in the inconsistency of the characteristic concentration determination involved in
-the volumetric mass transfer definition, Eq. \ref{eq:main:definition}. In experiments the characteristic concentration is taken as the averaged in time location concentration. 
-In numerical simulations by \citet{vanbaten-circular}, the characteristic concentration is taken as the averaged in space inlet/outlet concentration.
-Authors \cite{vanbaten-circular} performed  numerical
-simulations for one unit cell using periodic boundary conditions and measured the volumetric mass
-transfer coefficient as:
+$\ububble$ is the bubble velocity, $D$ is the diffusion coefficient. 
+%This correlation is within $10\%$ accuracy for experimental
+%results for the microchannels with rectangular/square crosssections for the following range of
+%parameters: bubble velocity $0.4\,\mathrm{m/s}<\ububble<2\,\mathrm{m/s}$, bubble length
+%$1.4<\frac{\lbubble}{d_h}<6.3$, slug length $1<\frac{\lslug}{d_h}<3.2$,
+%hydrodynamic diameter $d_h = 400 \mathrm{\mu m}$.
+
+Thus, the understanding of mass transfer for the bubble train flow is not possible without deep understanding of hydrodynamic patterns.
+There are a number of studies available for the hydrodynamic study of the bubble train flow: experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
+For the flow of long bubbles between parallel plates as the study case it is indicated that  there exists a vortex in the liquid slug for $Ca<0.7$ , see Fig.
+\ref{fig:streamlines:tweaked:velocity}.
+However, for $Ca>0.7$ the vortex in the liquid slug does not exist.
+As well the bubble shape for low capillary numbers ($Ca<0.1$ \cite{cerro-bubble-train}) is symmetric.
+Thus, in the case of flow between plates the bubble shape can be represented as two hemicircles and two planar interfaces.
+This is heavily utilized for mass transfer analytical estimations.
+
+As mentioned before the mass transfer coefficient is defined as the mass flux from certain area, Eq.
+\ref{eq:main:definition}.
+Thus, analytical estimations \cite{kreutzer-overview,irandoust} are  based on decomposition of the bubble shape.
+The mass transfer coefficient is calculated through two separate contributions from two films and two hemicircles.
+For both contributions the Higbie penetration theory \cite{higbie} is utilized, which states that the mass transfer coefficient  for simple geometry flow depends on the average time of liquid packet interaction with a geometrical feature.
+It can be calculated as $\sqrt{\frac{\pi D}{t_{\mathrm{char}}}}$, where $t_{\mathrm{char}}$ is the interaction characteristic time, $D$ is the diffusion coefficient.
+As the example for the Higbie penetration theory, the mass  transfer coefficient for the flow of bubbles between parallel plates  is calculated as (similarly to work of \citet{vanbaten-circular}):
+\beq
+k_L=2 \sqrt{\frac{\pi D}{t_{\mathrm{film}}}}+2 \sqrt{\frac{\pi D}{t_{\mathrm{circle}}}},
+\feq
+where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through planar part of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time which liquid in the slug travels the distance of half circumference.
+
+Despite the simplicity, analytical expressions work well for flows with low capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape is symmetrical and can be nicely approximated.
+Moreover, because of the hydrodynamic pattern in the slug, i.e.
+there is a vortex in slug, one can estimate the time for fluid batch to travel whole circumference.
+However, with the change of the capillary number the situation drastically changes.
+The symmetrical bubble shape changes and resembles a bullet \cite{kuzmin-binary2d}.
+With the change of the shape and for flows with $Ca>0.7$ there is no vortex in the liquid slug.
+In this case the Higbie theory fails to estimate contribution from bubble caps.
+Thus, the need of numerical simulations where all hydrodynamics fields and complicated bubble shapes are taken in the account is obvious.
+
+However, available numerical studies of mass transfer \cite{kreutzer-overview,vanbaten-circular} are lacking the simulation of  bubble shapes.
+The usual simulation of the mass transfer  is performed as follows:
+\begin{description}
+\item[I] The bubble shape is calculated either through analytical correlations \cite{bretherton} or experimental correlations \cite{cerro-bubble-train} without directly resolving bubbles shapes through multiphase simulations.
+\item[II] Hydrodynamics fields are then obtained by performing simulations of one-component flow around the droplet by imposing the bubble velocity on the walls.
+Thus, the simulations are performed in the reference frame moving with the bubble.
+The stress free condition is imposed at the bubble surface.
+\item[III]  The mass transfer simulations are  performed in the reference frame moving with the bubble.
+The saturation concentration is imposed at the bubble surface.
+Only one unit cell with one bubble in it is used for simulations.
+Periodic boundary conditions are utilized to determine the volumetric mass transfer coefficient, which is calculated through the following equation \cite{vanbaten-circular}:
 \begin{equation}
@@
 \end{equation}
-where $\langle\coutlet(t)\rangle=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the averaged in space outlet concentration used as the characteristic concentration in the definition, Eq.
+where $\langle\coutlet(t)\rangle=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the averaged in space outlet concentration as the function of time used as the characteristic concentration in the definition, Eq.
 \ref{eq:main:definition}.
-The averaged in time concentration flux is calculated as the difference between overall
+The averaged in time concentration flux ($\mathrm{\overline{Flux}}$) is calculated as the difference between the overall
 average concentration in the whole domain ($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$)
@@
 $t_1$ and at time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
-simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass} was good. However, the numerical model only
-accounts for circular capillaries and short contact times when the
-bubble film is not saturated with tracer. As well, authors took the
-approximation of bubble shapes for small capillary numbers $Ca<0.01$ and then obtained
-hydrodynamics fields by imposing a free-slip condition at the bubble surface. However, it will be shown later that this strategy is good only for small capillary numbers $Ca<0.1$
-where the shape of the bubble is simple. Moreover, the characteristic concentration to be averaged outlet concentration underpredicts the volumetric transfer coefficient for small capillary
-numbers $Ca<0.1$ and overpredicts for larger capillary numbers $Ca>0.7$.
+simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass} was good. 
+\end{description}
+There is a certain critics towards the presented numerical approaches \cite{vanbaten-circular,kreutzer-overview}.
+They mainly originate from the bubble shape approximation.
+It is taken symmetric, i.e.
+consisting from hemispheres and cylinder film for the case of flow in circular capillaries.
+This is valid  for small capillary numbers $Ca<0.1$.
+As it was discussed, for such capillary numbers in the reference frame moving with the bubble there is a vortex in slug.
+Thus, the tracer is well mixed in slug.The choice of the characteristic concentration needed for the mass transfer coefficient, Eq.
+\ref{eq:main:definition}, in this case  is obvious.
+With small differences in results it can be either averaged in the liquid slug concentration or the outlet space averaged concentration as used in formulation of \citet{vanbaten-circular}.
+Another critics is towards periodic boundary conditions to calculate the mass transfer coefficient.
+While it is clear to use periodic boundary conditions for the calculation of hydrodynamics fields for  long bubbles motion in the microchannel, it is not the case for mass transfer simulations.
+Experimental correlations \cite{bercic-mass} show that the concentration needed for the mass transfer calculations along the streamwise direction changes as the exponential function.
+However, mass transfer simulations are made only for one unit cell using the periodic boundary conditions with the same concentration at the inlet and at the outlet.
+The question how  one unit cell simulation corresponds to experimental measurements arises where concentration difference is measured at the distances of at least of a few unit cells difference \cite{bercic-mass}.
+In other words one needs to understand how the discrete one unit cell simulation corresponds to the continuous picture in experiments where one does not distinguish bubbles but takes measurements of concentration at different locations.
 
 Addressing situations for a rich number of hydrodynamic patterns, shapes, effects for a bubble
-train authors feel that they need to examine more carefully the strategies and assumptions which
-stay behind the mass transfer coefficient numerical simulations measurements. We aim at establishing
-numerical simulations procedures as to how properly obtain the volumetric
-mass transfer coefficient via a study of different boundary conditions, different characteristic concentration definitions, and address the following situations:
+train we feel that there is a need to examine more carefully the strategies and assumptions which
+stay behind the mass transfer coefficient numerical simulations. We aim at establishing
+numerical simulations procedures as to how properly obtain the mass transfer coefficient via a study of different boundary conditions, different characteristic concentration definitions.
+The case we want to examine is the two-dimensional case of the bubble train flow between parallel plates.
+The following issues will be addressed:
 \begin{description}
-\item[I] In numerical simulations \cite{vanbaten-circular,kreutzer-overview}, the bubble shape is approximated by two hemispheres and a cylinder which is valid only for the capillary number $Ca\leq 0.1$.
-It is known \cite{kreutzer-overview} that the liquid slug is well mixed with the concentrator.
-Due to homogeneity periodic boundary conditions were used, and the averaged in space inlet/outlet concentration as the characteristic concentration was used \cite{vanbaten-circular}.
-In comparison, we obtain bubble shapes and hydrodynamic fields from multiphase simulations \cite{kuzmin-binary2d,kuzmin-binary3d} and examine different boundary conditions with a few unit cells ($1$ to $10$ unit cells).
-\item[II] The gas holdup, i.e. the ratio of volume occupied by a bubble to an unit cell volume, is
-non-negligible. Therefore, one cannot assume that the mass source is a point source which accounts
-to the homogenous advection-diffusion equation with the mass source \cite{jos-mass}.  Therefore, there is a logical
-mismatch: on one hand one needs to account the complicated geometry of the bubble and account for
-all velocity pattern details, on the other hand one needs to mimic the continuous picture which is
-seen in experiments. Thus, a few unit cells simulations are performed and compared with one unit cell simulations to bridge different scales.
-\item[III] For small capillary numbers as $Ca<0.7$ \cite{giavedoni-numerical} there is a vortex in
-the reference frame moving with
-the bubble, which  influences and improves the corresponding mass transfer.  For larger capillary
-numbers there is no vortex and streamlines go around the bubble, see Fig.
-\ref{fig:streamlines:tweaked:velocity}.
-Literature results of numerical simulations \cite{kreutzer-overview,vanbaten-circular} are all for $Ca<0.01$.
-For non-homogenous situation, i.e.
-$Ca\geq 0.7$, we want to examine particular questions: whether periodic boundary conditions are valid to calculate the volumetric mass transfer coefficients, whether the change of hydrodynamic pattern significantly changes the way we measure the volumetric mass transfer coefficient (the inlet/outlet averaged in space concentration to be the characteristic concentration).
-There is the indication in literature \cite{bercic-mass,yue-mass} of a number of parameters influencing mass transfer, as the slug length, the film thickness.
-However, to the best authors' knowledge it is not indicated of how the change of the hydrodynamic pattern (capillary number $Ca$ dependency) influence mass transfer.
+\item[I] Applicability of periodic boundary conditions to determine the mass transfer coefficient when there is a change of pattern from having vortex in the slug to not having it. 
+\item[II] Validity to use the inlet/outlet averaged or domain averaged concentrations as characteristic concentrations in the definition of the mass transfer coefficient.
+\item[III] Transition of the continuous experimental picture to numerical simulations of a few unit cells mass transfer.
+This is the question about connection between time and space domains.
+In experiments the characteristic concentration is taken as an average in time, but in numerical simulations \cite{vanbaten-circular} the characteristic concentration is taken as an average in space.
+\item[IV] How the change of the hydrodynamic pattern ($Ca>0.7$) influences mass transfer.
 \end{description}
+Note that the goal of this paper is to establish procedures and boundary conditions used for the mass transfer coefficient determination.
+Though at the end of the manuscript we present a comparison of the volumetric mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations \cite{yue-mass}, the thorough
+determination of the Sherwood number as a function of
+other non-dimensional parameters as gas holdup, bubble/slug lenghts, the capillary number is the goal of the future work.
 \begin{figure}[htb!]
@@
 \end{figure}
-Note that the goal of this paper is to establish procedures and boundary conditions used for the volumetric mass transfer coefficient.
-Though at the end of the manuscript we present comparison of the volumetric mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations \cite{yue-mass}, the thorough
-determination of the Sherwood number as a function of
-other non-dimensional parameters as gas holdup, bubble/slug lenghts, the capillary number is the goal of the future work.
-
+
+To establish numerical procedures we performed multiphase simulations \cite{kuzmin-binary2d,kuzmin-binary3d} for the range of capillary numbers $Ca=0.1\div 1.0$ to extract bubble shapes.
+For this range of capillary numbers we are able to capture the bubble shape change and the change of hydrodynamic patterns.
+The mass transfer simulations were performed with different boundary conditions (open, periodic) and with a few unit cells ($1$ to $10$ unit cells).
 The numerical approach we take is the lattice Boltzmann method, a relatively new CFD
@@
 The mass transfer problems in the lattice Boltzmann framework were mainly addressed in series of
-works of Dr. Ginzburg and co-authors
+works of Ginzburg and co-authors
 \cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}. However, all these works
@@
 at the particular mass transfer problems, both problems are of homogeneous nature and do not
-guide as how to simulate the non-homogenous problems.
+guide as how to obtain the mass transfer coefficient for non-homogenous problems.
 
 The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
-for the bubble train to derive expressions to connect space and time domain. Then the lattice
+for the bubble train flow to derive expressions to connect space and time domains. Then the lattice
 Boltzmann model used to simulate mass transfer is presented followed by benchmarks. Finally,
@@
 different hydrodynamic patterns are presented to establish the thorough procedure to determine the
-volumetric mass transfer coefficient.
+volumetric mass transfer coefficient. The comparison with analytical correlations is also presented.
 
@@
 In what follows we will present three approaches to calculate point  mass transfer
-coefficients:
+coefficients (by point source we assume the source with the infinitesimally small surface area $P$):
 \begin{enumerate}
@@
 \beq
-\vol=k_L \frac{P}{V},
+\vol=k_L \frac{P}{A \Delta x}=k_L \frac{P}{V},
 \feq
@@
 If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
-mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
-source is a point source with the effective perimeter (area) $P$. The accumulated mass should be proportional
+mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. The accumulated mass should be proportional
 to the mass transfer coefficient:
@@
 locations and calculating the volumetric mass transfer coefficient through the logarithmic
-function. However, if one wants to analytically estimate the mass transfer coefficients, the
+function. However, if one wants to analytically or numerically calculate the mass transfer coefficients, the
 situation is much more complicated because of two phases presence and complicated bubble
-geometry. Phases can have different mixing patterns
-from film to slug and from slug to film. Also, as it was mentioned before depending on the capillary
+geometry. As it was mentioned before depending on the capillary
 number the mixing velocity pattern is different. Analytical approaches
@@
 the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
-concentration from film is mixed with the slug and changes the overall concentration in the slug.
-Thus, all estimations for analytical mass trass calculation  do not account for mutual mass
+concentration from film is mixed with the slug and increases the overall concentration in the slug. Thus, it decreases the mass transfer from bubble caps.
+Therefore, all estimations for the analytical mass transfer coefficient calculation  do not account for mutual mass
 transfer from
@@
 
-Another issue is that if the slug is long enough then the film saturates with the tracer
+Another issue is that if the bubble is long enough then the film saturates with the tracer
 concentration and its influence on mass transfer can be negligible \cite{vanbaten-circular}.
 Mixing patterns of the film and liquid slugs are of great importance for the analytical
-estimation of the mass transfer \cite{yue-mass}. However, the assumptions usually taken for the
+estimation of mass transfer \cite{yue-mass}. However, the assumptions usually taken for the
 mass transfer calculation are small capillary number and certain mixing patterns which help to
@@
 the account the complicated mixing patterns and geometries. However, there are challenges as to
-mimic the continuous picture like moving with bulk velocity $U$ reacting medium as it is seen in
+mimic the continuous picture like moving with bulk velocity $U=\ugas+\uliq$ reacting medium as it is seen in
 experiments. Thus, the questions indicated in Section \ref{intro}, as the choice of the
@@
 \label{section:cases}
-Ideally one needs to mimic the continuous picture as it is seen in experiments. Thus, one needs to
-perform mass transfer simulations for a number of unit cells. As it was indicated above there are
+Ideally one needs to mimic the continuous picture as it is seen in experiments. Thus, mass transfer simulations for a number of unit cells is needed. As it was indicated above there are
 two approaches towards it - either to simulate
@@
 approach is to simulate mass transfer in the reference frame moving with the bubble. Therefore, one
-needs to examine the equation for the continuous approach, Eq.
-\ref{main:mass:transfer:expression}.
+needs to examine  Eq.
+\ref{main:mass:transfer:expression} more closely.
 
@@
 $\ububble$), that the bubble position stands steady. The bubble velocity $\ububble$ is
-different from the bulk velocity $\ugas+\uliq$. In this case one needs to perform a coordinate $x$
+different from the bulk velocity $U=\ugas+\uliq$. In this case one needs to perform a coordinate $x$
 variable change:
@@
 &x(t)=\ububble t\\
-&C(x)=\cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\ugas+\uliq}\bigr)\Bigr)\\
+&\overline{C(x)}=\cstar \Bigl(1-\exp\bigl(-\vol \frac{x}{\ugas+\uliq}\bigr)\Bigr)\\
 &\langle C(t)\rangle=\cstar \Bigl(1-\exp\bigl(-\vol\, t \frac{\ububble}{\ugas+\uliq}\bigr)\Bigr),
 \feqal
-where $\langle C(t)\rangle$ is the characteristic concentration averaged in space
-concentration. The geometry is not one-dimensional and one needs the characteristic concentration
-to be only as a function of time. One can have different choices of
+where $\langle C(t)\rangle$ is the characteristic concentration averaged in space, $\overline{C(x)}$ is averaged in time concentration at location $x$. 
+%The geometry is not one-dimensional and one needs the characteristic concentration
+%to be only as a function of time. 
+One can have different choices of
 $\langle C(t) \rangle$ as the averaged in whole domain concentration or inlet/outlet averaged in
-space concentrations.  Note that $C(x)$ is not averaged in time as $\overline{C(x)}$ since $C(x)$
-ideally should not depend on time. 
-Therefore, one can obtain the volumetric mass transfer coefficient through the concentration:
+space concentrations used in works \cite{vanbaten-circular,kreutzer-overview}.  
+%Note that $C(x)$ is not averaged in time as $\overline{C(x)}$ since $C(x)$
+%ideally should not depend on time. 
+Therefore, one can obtain the volumetric mass transfer coefficient through the concentration averaged in space:
 \beqal
@@
 \item The bubble train multiphase simulations are conducted by applying periodic boundary
-conditions \cite{kuzmin-binary2d,kuzmin-binary3d}. One
-can make an assumption of same boundary
-conditions applied to the tracer concentration to simulate mass transfer. Therefore, only one unit
+conditions \cite{kuzmin-binary2d,kuzmin-binary3d}. 
+%One
+%can make an assumption of same boundary
+%conditions applied to the tracer concentration to simulate mass transfer. 
+Therefore, only one unit
 cell is simulated with
 periodic boundary conditions, see Fig. \ref{fig:benchmark}. As well, no tracer leaves a
-domain. The situation resembles a situation for the plug flow, where no tracer can leave a unit
-domain. We expect such a situation resembles most the mass transfer for small Capillary numbers
-$Ca<0.1$, where the liquid slug is well mixed and one have a homogenuous concentration in the unit
-cell. Though easier to implement, it rises certain critisism
+domain. The situation resembles the plug flow situation, where no tracer can leave a unit
+domain. From the physical point of view this case resembles most the mass transfer for small Capillary numbers
+$Ca<0.1$.  The liquid slug is well mixed and one have a homogenuous concentration in the unit
+cell, i.e. the outlet and the inlet concentrations are close. Though easier to implement, it rises certain criticism
 about the inlet concentration to be equal to the outlet concentration. In the continuous
@@
 outlet involving the volumetric
-mass transfer coefficient, see second equation in system \ref{theor:one:concentration:time}.
+mass transfer coefficient, see second equation in the system \ref{theor:one:concentration:time}.
 

### 2012-04-24 Text/introduction.tex
Finished till validation part.

@@
 
-Three possible scenarios of conducting numerical simulations are examined in this work: 
+Four possible scenarios of  numerical simulations are examined in this work: 
 \begin{enumerate}
-\item The bubble train multiphase simulations are conducted by applying periodic boundary
-conditions \cite{kuzmin-binary2d,kuzmin-binary3d}. 
+\item % The bubble train multiphase simulations are conducted by applying periodic boundary
+%conditions \cite{kuzmin-binary2d,kuzmin-binary3d}. 
 %One
@@
 %conditions applied to the tracer concentration to simulate mass transfer. 
-Therefore, only one unit
+One unit
 cell is simulated with
-periodic boundary conditions, see Fig. \ref{fig:benchmark}. As well, no tracer leaves a
-domain. The situation resembles the plug flow situation, where no tracer can leave a unit
-domain. From the physical point of view this case resembles most the mass transfer for small Capillary numbers
-$Ca<0.1$.  The liquid slug is well mixed and one have a homogenuous concentration in the unit
-cell, i.e. the outlet and the inlet concentrations are close. Though easier to implement, it rises certain criticism
-about the inlet concentration to be equal to the outlet concentration. In the continuous
-formulation as it is seen in experiments there is the concentration difference between inlet and
-outlet involving the volumetric
-mass transfer coefficient, see second equation in the system \ref{theor:one:concentration:time}.
-
-One needs also address the choice of the characteristic concentration. For example, the
-characteristic concentration $\langle C(t) \rangle$ required for calculation the volumetric mass
+periodic boundary conditions, see Fig. \ref{fig:benchmark}. 
+Thus, no tracer leaves a
+domain like for the plug flow. 
+%From the physical point of view this case resembles the mass transfer for small Capillary numbers
+%$Ca<0.1$.  The liquid slug is well mixed and one have a homogeneous concentration in the unit
+%cell, i.e. the outlet and the inlet concentrations are close. 
+Though easier to implement, it rises certain criticism
+about the inlet concentration to be equal to the outlet concentration. As it was discussed, in experiments there is the concentration difference between the inlet and
+ the outlet.
+
+The volumetric mass transfer coefficient is calculated by Eq. \ref{theor:one:concentration:time}.
+The
+characteristic concentration $\langle C(t) \rangle$ required for the volumetric mass
 transfer coefficient, Eq.
-\ref{theor:one:concentration:time}, can be taken as the average concentration in the domain:
+\ref{theor:one:concentration:time}, is taken as the average concentration in the domain:
 \beq
@@
 \end{figure}
-\item The second approach is the same as the first one but the characteristic concentration is taken
-as in
-\cite{vanbaten-circular}. The characteristic concentration is taken as the inlet/outlet
-concentration. For the two-dimensional flow between plates inlet/outlet concentrations can be found
-as:
+\item The second approach is to apply periodic boundary conditions as in the first case but the characteristic concentration is taken as the inlet/outlet
+concentration \cite{vanbaten-circular}:
 \beqal
@@
 that the difference between inlet and outlet is not
-considerably large and the tracer is well mixed in the slug, so that the inlet or outlet
+considerably large and the tracer is well mixed in the slug. Thus, the inlet or outlet
 concentrations equal to the average concentration.
@@
 \item
-The approach of \citet{vanbaten-circular} is examined. Periodic boundary conditions were used. We
-used the
-definition of the mass transfer coefficient to be proportional to the gain of the mass in the system
+The approach of \citet{vanbaten-circular} is examined. Periodic boundary conditions were used. The work \cite{vanbaten-circular}
+calculates the mass transfer coefficient as the gain of the mass in the system
 divided by the concentration difference
@@
 \dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(\bm{x},t_2)\mathrm{d}V}-\int_{liq}{
-C(\bm{x},t_1)\mathrm { d } V} } {
-t_2-t_1 },
-\feq
-where the integration element $\mathrm{d}V=\mathrm{d}x\mathrm{d}y=\mathrm{d}\bm{x}$.
-In the approach of \citet{vanbaten-circular} the inlet and outlet concentrations were taken as the
+C(\bm{x},t_1)\mathrm { d } \bm{x}} } {
+t_2-t_1 }.
+\feq
+In the approach of \citeauthor{vanbaten-circular} the inlet and outlet concentrations were taken as the
 characteristic concentration $\langle C(t) \rangle $.
@@
 \item 
-The last approach to be examined in this paper is the approach of the simulation of a lot of unit
-volumes, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
+The last approach to be examined in this paper is the simulation of a few unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
 bubble train head, after injecting to the pipe and travelling along the pipe. One can see that this
@@
 diminished. In this case, there is no ambiguity in the choice of the
-characteristic concentration in this case. The average concentration in time will be governed
+characteristic concentration. The average concentration of any unit cell far away from boundaries will be governed
 by Eq.
@@
 increasing a computational
-complexity.
+burden.
 \begin{figure}[htb!]
@@
 
-One can notice that all the examined cases are extreme cases of one equation. The choice of boundary
-conditions to use  or how many unit cells to simulate are not of importance but one needs only to
-understand a proper mass balance for medium, which states:
+One can notice that all examined cases are extreme cases of one equation:
 \beq
@@
 where $\Delta C=\cstar-\langle C(t) \rangle$ with $\langle C(t) \rangle$ to be the average
-concentration in whole liquid domain. Eq. \ref{main:main:main} is nothing else but a proper mass
+concentration in whole liquid domain, $\dot{m}$ is the mass gain in the domain,$\int{\cinlet u(0,y) \mathrm{d}y}$ and $\int{\coutlet u(\lunit,y)\mathrm{d}y}$ are inlet/outlet mass fluxes.
+Eq.
+\ref{main:main:main} describes the mass
 balance: whatever was generated by the bubble surface equals to the mass domain change minus
-whatever left domain plus whatever entered domain. Periodic boundary condition is the extreme
-limiting case of Eq. \ref{main:main:main} as $\int{\coutlet(t)
-u(\lunit,y)\mathrm{d}y}=\int{\cinlet(t) u(0,y)\mathrm{d}y}$. Thus, the mass change in the domain is
-only because of the generating bubble surface. In this case, to calculate the volumetric mass
-transfer coefficient one needs to track not only spatial information to calculate the averaged over
-domain characteristic concentration  $\langle C(t) \rangle$ but as well time information to
-calculate the mass change in the domain. It will be shown later, that for $Ca>0.7$ where velocity
-pattern is changed, one can use only spatial information to calculate $\int{\cinlet(t) u(0,y)
-\mathrm{d}y}$ and $\int{\coutlet(t) u(\lunit,y)\mathrm{d}y}$ as far as mass change in the domain is
-zero, i.e. $\dot{m}=0$.
+whatever left domain plus whatever entered domain.
+
+Periodic boundary condition is the extreme
+limiting case of Eq. \ref{main:main:main}: 
+\beqstar
+\int{\coutlet(t)
+u(\lunit,y)\mathrm{d}y}=\int{\cinlet(t) u(0,y)\mathrm{d}y}. 
+\feqstar
+Then the mass change in the domain is
+only because of the generating bubble surface.
+However, to calculate the mass transfer coefficient one needs to have characteristic concentration  $\langle C(t) \rangle$ and mass gain $\dot{m}$ which do require the storage of time and space information.
+
+Another limiting case (will be shown later) is hydrodynamic pattern change $Ca>0.7$.
+The mass accumulation rate equals zero in this case, $\dot{m}=0$.
+One can use only spatial information to calculate the mass transfer coefficient, i.e.
+$\int{\cinlet(t) u(0,y)
+\mathrm{d}y}$ and $\int{\coutlet(t) u(\lunit,y)\mathrm{d}y}$ require only space information.
 

### 2012-04-30 Text/introduction.tex
The iteration from my side is finished.

@@
 For the latter case the bubble shape is not symmetric and cannot be approximated through flat surfaces and circumferences as it is done in literature \cite{vanbaten-circular,kreutzer-overview}.
-Moreover, with a vortex in the slug the tracer is well mixed.
-Thus, it is common to  use periodic boundary conditions  and inlet/outlet averaged concentration as the characteristic concentration, Eq.
+For $Ca<0.7$ where there is a vortex in the slug the tracer is well mixed.
+Thus, it is common to  use periodic boundary conditions  and the inlet/outlet averaged concentration as the characteristic concentration, Eq.
 \ref{eq:main:definition}.
-The later is not valid for flows where tracer is not well mixed.
+The later is not valid for flows where tracer is not well mixed, i.e.
+$Ca>0.7$.
 This work through examination of different boundary conditions and different characteristic concentration definitions establishes the procedure to determine the volumetric mass transfer coefficient for flows with the capillary number $0.1<Ca<1.0$.
-With simulations of a few unit cells the connection between time (used in simulations) and space (used in experiments) domains was established.
+With simulations of a few unit cells the connection between time (used in simulations) and space (used in experiments) domains is established.
 The following boundary conditions were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
@@
 In comparison with works \cite{vanbaten-circular,kreutzer-overview} where only one unit cell was simulated, a few
-unit cells open boundaries conditions resemble physical situation most closely and are harder to conduct
+unit cells open boundaries conditions resemble physical situation most closely. However, they  are harder to be conducted 
 but provide the volumetric mass transfer coefficient based only on the spatial information for the
@@
 train flow in microchannels and/or within the
-lattice Boltzmann context.
+lattice Boltzmann model context.
 \end{abstract}
@@
 The monolith reactors during last years are getting more attention as a promising alternative to slurry
-reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Reactors usually operate in Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
-a liquid medium of equally sized, long bubbles, see
+reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Reactors usually operate in the Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
+a liquid medium of equally sized, long air bubbles, see
 Fig. \ref{fig:benchmark:hydro}. This flow regime
@@
 The mass transfer coefficient characterizing mass transfer is defined as the flux from the surface divided on the concentration difference between the concentration imposed on the body and the characteristic concentration in the domain.
-The characteristic concentration in the domain depends largely on underlying hydrodynamics fields.
+The characteristic concentration in the domain significantly depends on underlying hydrodynamics fields.
 For example, experimental studies \cite{yue-mass,bercic-mass} show a complex dependency of the mass transfer coefficient on flow parameters: bubble and slug lengths, bubble velocity, which are in turn depend on the capillary number $Ca$ and the Reynolds number $Re$.
@@
 There are a number of studies available for the hydrodynamic study of the bubble train flow: experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
-For the flow of long bubbles between parallel plates as the study case it is indicated that  there exists a vortex in the liquid slug for $Ca<0.7$ , see Fig.
+For the flow of long bubbles between parallel plates chosen here as the study case it is indicated that  there exists a vortex in the liquid slug for $Ca<0.7$ , see Fig.
 \ref{fig:streamlines:tweaked:velocity}.
-However, for $Ca>0.7$ the vortex in the liquid slug does not exist.
-As well the bubble shape for low capillary numbers ($Ca<0.1$ \cite{cerro-bubble-train}) is symmetric.
-Thus, in the case of flow between plates the bubble shape can be represented as two hemicircles and two planar interfaces.
+As well, the bubble shape for low capillary numbers ($Ca<0.1$ \cite{cerro-bubble-train}) is symmetric.
+Thus, in the case of flow between plates for $Ca<0.1\div0.7$ the bubble shape can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug.
 This is heavily utilized for mass transfer analytical estimations.
 
-As mentioned before the mass transfer coefficient is defined as the mass flux from certain area, Eq.
+As mentioned  the mass transfer coefficient is defined as the mass flux from certain area, Eq.
 \ref{eq:main:definition}.
@@
 \feq
-where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through planar part of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time which liquid in the slug travels the distance of half circumference.
+where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through planar part of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time which liquid in the slug travels the distance of half bubble circumference.
 
@@
 \item[I] The bubble shape is calculated either through analytical correlations \cite{bretherton} or experimental correlations \cite{cerro-bubble-train} without directly resolving bubbles shapes through multiphase simulations.
+The expressions for bubble shapes are available only for flows with the capillary number $Ca<0.1$.
 \item[II] Hydrodynamics fields are then obtained by performing simulations of one-component flow around the droplet by imposing the bubble velocity on the walls.
@@
 They mainly originate from the bubble shape approximation.
-It is taken symmetric, i.e.
+It is taken symmetrical, i.e.
 consisting from hemispheres and cylinder film for the case of flow in circular capillaries.
@@
 While it is clear to use periodic boundary conditions for the calculation of hydrodynamics fields for  long bubbles motion in the microchannel, it is not the case for mass transfer simulations.
-Experimental correlations \cite{bercic-mass} show that the concentration needed for the mass transfer calculations along the streamwise direction changes as the exponential function.
+Experimental correlations \cite{bercic-mass} show that the concentration along the streamwise direction changes as the exponential function.
 However, mass transfer simulations are made only for one unit cell using the periodic boundary conditions with the same concentration at the inlet and at the outlet.
@@
 \beq
+\label{eq:vanbaten:formulation}
 \vol=\frac{\dot{m}}{P \Delta C}\frac{P}{V}=\frac{\dot{m}}{V (\cstar-\langle C(t) \rangle)},
@@
 \section{Validation}
-For analytical expressions the problem of the mass transfer can be decomposed to the following
-parts: the mass transfer from two circumferences and the mass transfer from the film. We will
+As it was discussed analytical correlations for the mass transfer coefficient are derived  as two separate contributions: the mass transfer from two circumferences and the mass transfer from the film.
+We will
 examine
-these problems with the help of the lattice Boltzmann method and compare them against analytical
-solutions. The next sections will present the lattice Boltzmann method and a few benchmarks.
+these problems closely with the help of the lattice Boltzmann method and compare them against analytical
+solutions. The next sections will give a short introduction on the lattice Boltzmann method and present a few benchmarks.
 
@@
 $\omegaplus=\omegaminus$. In comparison with the BGK collision operator,
-the TRT collision operator has the additional degree of freedom. Thus, the TRT operator then
+the TRT collision operator has the additional degree of freedom. Thus, the TRT operator 
 introduces
@@
 u_y}{4} p_i^{xy}\\
-&eq_i^{(a)}=\frac{K_{xx}-K_{yy}}{4} p_i^{xx}+\frac{D_{xy}}{4} p_i^{(xy)},
+&eq_i^{(a)}=\frac{K_{xx}-K_{yy}}{4} p_i^{xx}+\frac{K_{xy}}{4} p_i^{(xy)},
 \end{aligned}
@@
 weights
-$t_i^{(u,m,a)}$ can be chosen based on stability criteria. Though not the best set of weights for
-stability \cite{kuzmin-stability-optimal}, but the most spread set of weights, so called
+$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most spread set of weights, so called
 ``hydrodynamic`` weights, was chosen:
@@
 $\bar{i}$ is the direction number opposite to $i$ and is located at the fluid $F$ specifically that
-$B$ is located at the location $F+c_i$.
+$B$ is located at the location $F+\bm{c_i}$.
 
 Note that the parameters of the lattice
-Boltzmann scheme are connected with the physical parameters only through the non-dimensional
+Boltzmann scheme are connected with  physical parameters only through  non-dimensional
 numbers governing the physics of the problem. In our case, this number is the Peclet number, $Pe=\frac{\ububble L}{D}$.
@@
 $\ububble$ in the lattice Boltzmann units as soon as the
-Peclet number is the matched in physical space and numerical simulations. This fact that $\ububble$
+Peclet number is  matched in physical space and numerical simulations. This fact that $\ububble$
 can be chosen arbitrarily is extremely useful in the context of numerical simulations, since it can
 increase the time step, or decrease the computational demand by order of magnitude to obtain
-meaningful results. This point will be extensively covered later.
-
-Next section will cover LBM benchmarks that resemble the mass transfer problem from a bubble, as as
+meaningful results. This point will be used in simulations and covered later.
+
+Next section will cover LBM benchmarks that resemble the mass transfer problem from a bubble, as 
 mass transfer from the film  and circumferences.
@@
 \subsection{The radial case}
-The case to be examined here is the mass transfer from the stair-case boundary forming a circle. It
+The case to be examined  is the mass transfer from the stair-case boundary forming a circle. It
 can be
@@
 diffusion from curved boundaries is captured
-accurately \label{fig:cylinder:benchmark}. $x$ is the distance from the center.}
-\end{figure}
-
-\subsection{Parabolic profile with the velocity zero gradient at the wall}
+accurately \label{fig:cylinder:benchmark}. $r$ is the distance from the center.}
+\end{figure}
+
+\subsection{Parabolic velocity profile with the velocity zero gradient at the wall}
 The problem is defined in terms of PDE as follows: 
@@
 Fig. \ref{fig:parabolic:zero:gradient} shows the steady-state contours comparison between the
-analytical and the simulation with the Anti Bounce-Back conditions used to impose constant
-concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The grid used in the simulation is
+analytical solution and the simulation with the anti bounce-back boundary conditions used to impose constant
+concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The simulation grid is
 $80\times1600$. Parameter $\omegaminus=1.8$ implies the diffusion coefficient to be
@@
 \includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
-\caption{Comparison with the analytical concentration contours, Eq.
-\ref{analytical:solution:zero:gradient}, for the diffusion coefficient $D=0.0185$. Simulation was
-performed on grid $80\times 1600$. The constant concentration is imposed with the
+\caption{Concentration contour levels comparison between the analytical solution, Eq.
+\ref{analytical:solution:zero:gradient}, and simulation for the diffusion coefficient $D=0.0185$. Simulation was
+performed on the grid size of $80\times 1600$. The constant concentration is imposed with the
 anti bounce-back conditions, Eq. \ref{antibb}. Coordinate $x$ and $y$ are non-dimensionalized on
-the height of the channel. $\delta=H/2$ is the half of the channel height
+the height of the channel. $\delta=H/2$ is the half of the channel height.
 \label{fig:parabolic:zero:gradient}}
@@
 between contours of analytical and simulation results is presented in Fig.
-\ref{fig:parabolic:comparison}. Parameters were taken the same as in the previous case: the
+\ref{fig:parabolic:comparison}. Parameters were taken  same as in the previous case: the
 diffusion $D=0.0185$, the grid dimension is $80\times1600$. 
@@
 After the LBM is validated against the benchmarks relevant for the flow around bubbles, one can
-examine all the cases to calculate the volumetric mass transfer coefficient, Section
-\ref{section:cases}.
+examine all cases mentioned in Section
+\ref{section:cases} to calculate the volumetric mass transfer coefficient.
 
@@
 \label{sec:numerics}
-The multiphase code was utilized to obtain the flow patterns for different capillary numbers
-\cite{kuzmin-binary2d}. Five particular cases were chosen to examine, their results are summarized
+The multiphase code was utilized to obtain the flow patterns and bubble shapes for different capillary numbers
+\cite{kuzmin-binary2d}. Five particular cases were chosen to be examined, their results are summarized
 in Table \ref{table:capillary:cases}. 
@@
 \caption{Sample results with the binary liquid lattice Boltzmann model \cite{kuzmin-binary2d}. The
-following notations are used: the capillary number $Ca=\frac{\ububble L}{\rho \nu}$, $\delta$ is the
+following notations are used: the capillary number $Ca=\frac{\ububble L}{\rho \nu_{\mathrm{liq}}}$, $\delta$ is the
 non-dimensional film thickness, $\uliq$ is the superficial liquid velocity, $\ugas$ is the
-superficial gas velocity. One can see the sketch of the simulation in Fig.
+superficial gas velocity. The simulation sketch is presented in Fig.
 \ref{fig:benchmark:hydro}. \label{table:capillary:cases}}
 \end{table}
-One can check that velocities in Table \ref{table:capillary:cases} are small. It means that to
-match large Peclet numbers, $Pe=\frac{\ububble L}{D}$, usually seen in experiments to measure
-the mass transfer coefficient, one needs to decrease
-$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. However, for parameters
-$\omegaminus \approx 0.5$ the stability of the lattice Boltzmann method drastically decreases
+Note that velocities in Table \ref{table:capillary:cases} are small. It means that to
+match large Peclet numbers, $Pe=\frac{\ububble L}{D}$, usually used in experiments, one needs to decrease the diffusion coefficient
+$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. Thus, parameter $\omegaminus\approx 0.5$. However, for such parameters
+$\omegaminus$ the stability of the lattice Boltzmann method drastically decreases
 \cite{kuzmin-d1q3}. On the other hand, one iteration in the lattice Boltzmann system corresponds
-to the time in the physical domain as $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
-x}{U_{\mathrm{bubble,phys}}}$. This time is proportional to the velocity of the $U_{\mathrm{LB}}$
-and the typical number of simulation steps to obtain necessary number with given velocities for
-$Ca<0.2$ is of the order of a few millions. Thus, one wants to increase the available velocity
-while keeping the Peclet number the same. This helps to stability of the method as well, since
-$\omegaminus$ is not close to its stability limit $\omegaminus=0.5$.
-
-Given all the considerations above, the approach we take for mass transfer is:
+to the time step in the physical domain  $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
+x}{U_{\mathrm{bubble,phys}}}$. One iteration time is proportional to the velocity $U_{\mathrm{LB}}$
+and the typical number of simulation steps to obtain the steady-state mass transfer coefficient for
+$Ca<0.2$ is of the order of a few millions. Therefore, it is desirable to increase  velocity  $U_{\mathrm{LB}}$
+while keeping the Peclet number the same.
+If one increases velocity, then $\omegaminus$ increases as well.
+Thus, the increase of the velocity impacts positively on stability of the LBM as $\omegaminus$ is not close to its stability limit $0.5$.
+
+Given all the considerations above, mass transfer simulations are performed as:
 \begin{description}
  \item[Flow field] Given the capillary number $Ca$, one needs to obtain hydrodynamic fields around
-the bubble using the binary liquid lattice Boltzmann model according to work
+the bubble using the multiphase binary liquid lattice Boltzmann model according to work
 \cite{kuzmin-binary2d}. Periodic boundary conditions are used. The grid used in this work is
-$202\times 3000$ which corresponds to fluid domain size $200\times3000$. The grid resolution is
+$202\times 3000$ which corresponds to the fluid domain  of size $200\times3000$. The grid resolution is
 taken to ensure grid
-independency of results \cite{kuzmin-binary2d}.  
+independency of results \cite{kuzmin-binary2d}. Note that we do not approximate bubble shapes by correlations, but we directly resolve them by using the multiphase solver. 
  \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
 are conducted in the reference frame moving with the bubble. Then the bubble stands still and the
-flow is coming around the
+flow is  happening around the
 bubble. We impose a steady concentration on the surface
 of the bubble with the anti bounce-back condition, Eq. \ref{antibb}.
- \item[Velocity improvement] Due to necessity to increase velocity one can scale the velocity to
-perform fast simulations, one needs to improve velocity. This issue arises because of the
+ \item[Velocity improvement] One can scale the velocity to
+perform faster simulations. However, before doing it one needs to improve velocity. This issue arises because of the
 multiphase model used in simulations. The binary liquid lattice Boltzmann model is the diffusive
@@
 transition between gas and liquid is the continuous function. We obtain the bubble shape according
-to the phase indicator $\phi$ as used in \cite{kuzmin-binary2d}, say $\phi<0$. The velocity of the
-bubble is calculated as the bubble tip velocity. Because of the highly non-linear diffusive
-interface model the shape of the bubble is determined within accuracy of one grid node, as well
-there is the error in determination in the bubble velocity. Though these errors are small, however
-there is small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
+to the phase indicator $\phi$ as used in \cite{kuzmin-binary2d}, say $\phi\leq0$. The velocity of the
+bubble is calculated as the bubble tip velocity. Because of the square grid the shape of the bubble is determined within accuracy of one grid node. Thus,
+there is the error in determination of the bubble velocity. Though these errors are small, however
+there is a small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
 \cite{kuzmin-binary2d} where some streamlines are penetrating a bubble surface a bit.
 This small velocity is amplified upon the velocity scaling and is inconsistent with the
-advection-diffusion equation.
+advection-diffusion equation leading to the instability after many iterations.
 
 Thus, before performing the mass transfer simulations one additional single phase hydrodynamic
-simulation is performed. An additional free-surface solver was developed in order to obtain
-consistent with the advection-diffusion equation velocity field. We take results from the
+simulation is performed. An additional free-surface solver was developed in order to obtain velocity field
+consistency with the advection-diffusion equation. We take results from the
 multiphase simulations, extract a
-bubble shape using the phase indicator $\phi<0$, approximate the bubble shape by the stair-case
-line. Then,the obtained bubble velocity is imposed on walls. This corresponds to conducting
+bubble shape using the phase indicator $\phi\leq0$, approximate the bubble shape by the stair-case
+line. Then, the obtained bubble velocity is imposed on walls. This corresponds to conducting
 simulation in the reference frame moving with the bubble. In addition, the free-slip boundary
@@
 bubble surface are completely eliminated. We compared original multiphase simulations with
-one-component free-slip simulations. All quantities as superficial slug and bubble velocities are
+one-component free-slip simulations. All quantities as superficial slug and liquid velocities are
 within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. This simulation helps to
-make mass transfer simulations stable and faster, since the velocity scaling can be done easier and
-streamlines are non-penetrating through the interface. One
+make mass transfer simulations stable and faster.%, since the velocity scaling can be done easier and
+%streamlines are non-penetrating through the interface. 
+One
 can see in Fig. \ref{fig:free:surface} two streamlines profiles for $Ca=0.097$  and $Ca=1.040$.
 \begin{figure}[htb!]
-\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca0097.eps}\\
-\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca1040.eps}
+\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca0097_out.eps}\\
+\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca1040_out.eps}
 \caption{The streamlines patterns produced by the free-surface solver with simplistic approximation
@@
 transfer simulations with different boundary conditions as covered in Section \ref{section:cases}.
-For this purpose one needs to match the Peclet number $Pe$ from experiments. Note that we
-specifically separated the hydrodynamic problem from the mass transfer problem. When one wants to
-solve these simultaneous problems, then one needs to match all the non-dimensional parameters, as
-the capillary number (viscous forces over surface tension), the Schmidt number (viscous diffusion
-rate over mass diffusion rate), the Peclet number (convection over diffusion), the Reynolds number
-(inertia over viscous forces). As the output one can obtain the Sherwood number dependancy on other
-parameter (convection mass transfer over diffusion mass transfer):
-\begin{equation}
-\begin{aligned}
-&Re=\frac{\ububble L}{\nu_{\mathrm{liq}}},&&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
-&Pe=\frac{\ububble L}{D},&&Sh=\frac{K L}{D}\\
-&Sc=\frac{\nu_{\mathrm{liq}}}{D}.&&
-\end{aligned}
-\end{equation}
+For this purpose one needs to match the Peclet number $Pe$ taken from experiments. Note that we
+specifically separated the hydrodynamic problem from the mass transfer problem. 
 \end{description}
+%When one wants to
+%solve these simultaneous problems, then one needs to match all the non-dimensional parameters, as
+%the capillary number (viscous forces over surface tension), the Schmidt number (viscous diffusion
+%rate over mass diffusion rate), the Peclet number (convection over diffusion), the Reynolds number
+%(inertia over viscous forces). As the output one can obtain the Sherwood number  (convection mass transfer over diffusion mass transfer) dependancy on other
+%parameters:
+%\begin{equation}
+%\begin{aligned}
+%&Re=\frac{\ububble L}{\nu_{\mathrm{liq}}},&&Ca=\frac{\ububble \mu_{\mathrm{liq}}}{\gamma}\\
+%&Pe=\frac{\ububble L}{D},&&Sh=\frac{K L}{D}\\
+%&Sc=\frac{\nu_{\mathrm{liq}}}{D}.&&
+%\end{aligned}
+%\end{equation}
+%\end{description}
+%Note that in this work we do not establish the Sherwood number dependancy on other parameters in this work.
+The purpose of this work is to establish procedures of simulation mass transfer problems for the Bretherton/Taylor bubble flow in the context of the lattice Boltzmann simulations.
 
@@
 This section covers simulation results. We first examine the possibility to increase the fluid
-velocity while keeping the Peclet number the same. After that we will examine the periodic boundary
-conditions for $5$ capillary number cases,  and finally we will examine
+velocity while keeping the Peclet number the same. After the periodic boundary
+conditions for $5$ capillary number cases will be presented. Finally, we will examine
 many
@@
 
-\subsection{Keeping Peclet}
+\subsection{Keeping the Peclet number}
 \label{section:keeping:peclet}
-This section addresses the performance of the simulations. The ulimate goal is to increase
-velocity at least by several orders of magnitude while keeping dimensionless parameters the same to
+This section addresses the simulations performance. The ultimate goal is to increase
+velocity magnitude significantly while keeping dimensionless parameters the same to
 speed up                                      
-simulations. Increasing velocity can also help to resolve a lot of unit cells to represent a
-continous picture.
-
-With the given bubble shape and velocity pattern only nondimensional parameter Peclet number governs
-the advection-diffusion equation represented in the lattice Boltzmann system as:
+simulations. This is especially important to be able to simulate a few unit cells simulations. For example, ten unit cells simulations require a grid of $30000\times202$ nodes.
+%Increasing velocity can also help to resolve a lot of unit cells to represent a
+%continous picture.
+As it was discussed above, only the Peclet number governs 
+the advection-diffusion equation. In the lattice Boltzmann system it is represented as:
 \beq
@@
 \feq
-As far as we want to increase velocity, that
-means one needs to increase the diffusion coefficient as well. The runs were made with
-velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
+As far as we want to increase velocity, one needs to increase the diffusion coefficient as well. The runs were made with
+velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities and
 its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
@@
 \ref{main:simulation:equation}. Table \ref{table:scaling:peclet} shows that the velocity limit
-for  periodic boundary conditions is $0.1$ where $\omegaminus=1.99$ ($D=0.000837$). It gives us the
+for  periodic boundary conditions is $0.1$. %if  when $\omegaminus=1.99$ ($D=0.000837$). 
+It gives us the
 preliminary idea to what extent one can scale periodic mass transfer simulations. 
 \begin{table}[htb!]
-\begin{tabularx}{\textwidth}{|X|X|X|X|}
-\hline
-Scale&$U_{bubble}$&Time Iterations&$C_{aver}$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.097$,$Pe=1313$}\\
-\hline
-$2$ &$0.011$&$400000$&$0.318$\\
-$4$ &$0.023$&$200000$&$0.319$\\
-$8$ &$0.044$&$100000$&$0.320$\\
-$10$&$0.055$&$80000$ &$0.321$\\
-$20$&$0.11 $&$40000$ &$0.324$\\
-$40$&$0.22 $&$20000$ &$0.328$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.254$,$Pe=3414$}\\
-\hline
-$2$& $0.0286$&$800000$&$0.6533$\\
-$4$& $0.0572$&$400000$&$0.6591$\\
-$8$& $0.1144$&$200000$&$0.6692$\\
-$10$&$0.1430$&$160000$&$0.6734$\\
-$20$&$0.2860$&$80000$ &$0.6894$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.526$,$Pe=7092$}\\
-\hline
-$2$&$0.0594$&$200000$&$0.3271$\\
-$4$&$0.1188$&$100000$&$0.3315$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=0.750$,$Pe=10125$}\\
-\hline
-$2$&$0.0848$&$200000$&$0.3489$\\
-\hline
-\multicolumn{4}{c}{}\\
-\multicolumn{4}{c}{$Ca=1.040$,$Pe=14041$}\\
-\hline
-$2$&$0.1176$&$200000$&$0.3675$\\
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
+\hline
+Scale&$U_{bubble}$&$\omegaminus$&Time Iterations&$C_{aver}$\\
+\hline
+\multicolumn{5}{c}{}\\
+\multicolumn{5}{c}{$Ca=0.097$,$Pe=1313$}\\
+\hline
+$2$ &$0.011$&$1.98$&$400000$&$0.318$\\
+$4$ &$0.023$&$1.96$&$200000$&$0.319$\\
+$8$ &$0.044$&$1.92$&$100000$&$0.320$\\
+$10$&$0.055$&$1.90$&$80000$ &$0.321$\\
+$20$&$0.11 $&$1.81$&$40000$ &$0.324$\\
+$40$&$0.22 $&$1.66$&$20000$ &$0.328$\\
+\hline
+\multicolumn{5}{c}{}\\
+\multicolumn{5}{c}{$Ca=0.254$,$Pe=3414$}\\
+\hline
+$2$& $0.0286$&$1.98$&$800000$&$0.6533$\\
+$4$& $0.0572$&$1.96$&$400000$&$0.6591$\\
+$8$& $0.1144$&$1.92$&$200000$&$0.6692$\\
+$10$&$0.1430$&$1.90$&$160000$&$0.6734$\\
+$20$&$0.2860$&$1.81$&$80000$ &$0.6894$\\
+\hline
+\multicolumn{5}{c}{}\\
+\multicolumn{5}{c}{$Ca=0.526$,$Pe=7092$}\\
+\hline
+$2$&$0.0594$&$1.98$&$200000$&$0.3271$\\
+$4$&$0.1188$&$1.96$&$100000$&$0.3315$\\
+\hline
+\multicolumn{5}{c}{}\\
+\multicolumn{5}{c}{$Ca=0.750$,$Pe=10125$}\\
+\hline
+$2$&$0.0848$&$1.98$&$200000$&$0.3489$\\
+\hline
+\multicolumn{5}{c}{}\\
+\multicolumn{5}{c}{$Ca=1.040$,$Pe=14041$}\\
+\hline
+$2$&$0.1176$&$1.98$&$200000$&$0.3675$\\
 \hline
@@
 $\Delta t=\frac{U_{\mathrm{bubble,LB}}}{U_{\mathrm{bubble,phys}}} \Delta x$. Therefore the speed up
-of the simulation is proportional to the  $U_{\mathrm{bubble,LB}}$. Note that all time
+of the simulation is proportional to the  $U_{\mathrm{bubble,LB}}$. Note that time
 iterations
-indicated in the table correspond to the one time moment in physical space. One can see that
-scaling produces adequate results.  The achievable stable velocity is around $U_{bubble}=0.1$ for
-the diffusion coefficient
-$D=1/3(1/1.99-0.5)=0.000837$. Average concentrations are in the reasonable agreement. The contour
+indicated in the table correspond to the one time moment in the physical space. One can see that
+scaling produces adequate results.  The achievable stable velocity is around $U_{bubble}=0.1$. Average concentrations are in the reasonable agreement. The contour
 profiles for all of these cases (capillary number $Ca$ and all scales) are presented in Fig.
@@
 velocity scalings are presented in Fig. \ref{fig:contours:scaling:peclet}. One can see an
-acceptable agreement between all of them. Note, that a few profiles are obtained $10$ to $40$ times
+acceptable agreement between all of them. Note, that the speedup can be upto $10$ to $40$ times
 faster.
@@
 \ref{table:scaling:peclet} (top to bottom:
-$Ca=0.097,0.254,0.526,0.750,1.040$). Thick lines correspond to
+$Ca=0.097,0.254,0.526,0.750,1.040$). Lines correspond to
 all different scales indicated in Table
@@
 \feqal
-where $\langle C(t) \rangle$ is the average concentration in the whole liquid domain.
+where $\langle C(t) \rangle$ is the average concentration in the liquid domain.
 Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
 \ref{fig:aver:conc:different:capillaries:time} for different Peclet numbers and velocity scalings
-indicated in Table \ref{table:scaling:peclet}. Because in the definition of the volumetric mass
-transfer coefficient there is the logarithm function, thus when the average concentration goes
+indicated in Table \ref{table:scaling:peclet}. When the average concentration goes
 close to $\cstar=1$ then Eq. \ref{theor:one:concentration:time} gives inadequate results due to
  accuracy of the logarithmic function. Fig. \ref{fig:aver:conc:different:capillaries:time} presents
-the volumetric mass transfer coefficient against number of time iterations. However, due to scaling
+the volumetric mass transfer coefficient against number of iterations. However, due to scaling
 each simulation has a different physical time step. We scaled curves against number of cell
 units which tracer will pass with the given bubble velocity, i.e. 
-$N_{\text{cell\,units}}=\frac{\text{scale} \ububble t}{\lunit}$.  Fig.
+$N_{\text{cell\,units}}=\frac{\text{scale}\cdot \ububble\cdot N_{\mathrm{iter}}}{\lunit}$.  Fig.
 \ref{fig:aver:conc:different:capillaries} shows the volumetric mass transfer
@@
 cells) is required to achieve the steady state. For example, for
-larger Peclet number less time steps are required to achieve the steady state condition.
+larger Peclet number less number of iterations are required to achieve the steady state condition.
 
@@
 \item[I] Scaling is performed as $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
-\item[II] The larger Peclet number the less time is required. One can extrapolate data from Table
-\ref{table:steady:state:average}, say $L_{\mathrm{steady}}$ and perform the following number of
-iterations as $\mathrm{scale}\cdot \ububble\cdot N_{\mathrm{iter}}\leq L_{\mathrm{steady}}$. 
+\item[II] The larger Peclet number the less number of iterations is required. One can extrapolate data from Table
+\ref{table:steady:state:average}, say $L_{\mathrm{steady}}$ and estimate the  number of
+iterations to reach the steady-state as $\mathrm{scale}\cdot \ububble\cdot N_{\mathrm{iter}}\leq L_{\mathrm{steady}}$. 
 \end{description}
@@
 \label{results:periodic:inlet:outlet}
-When the characteristic concentration is taken as in the formulation of \citet{vanbaten-circular},
-i.e. the inlet/outlet flux averaged concentration, then the results are quite different. One can
-see in Fig. \ref{fig:volumetric:char:concentration:vanbaten} the calculated volumetric mass transfer
-is different from the domain averaged calculated volumetric mass transfer coefficient. For example,
+The volumetric mass transfer coefficient was calculated using Eq.
+\ref{theor:one:concentration:time} with the characteristic concentration being the inlet/outlet flux averaged concentration as used by \citet{vanbaten-circular}.
+One can
+see in Fig. \ref{fig:volumetric:char:concentration:vanbaten} the calculated volumetric mass transfer is different from the domain averaged calculated volumetric mass transfer coefficient. For example,
 for small capillary numbers, i.e. $Ca=0.097,0.254,0.526$ the predicted values are overpredicted
@@
 the bubble to not having it,  i.e. $Ca=0.75,1.04$ the calculated values
-are underpredicted than in the previous case, i.e. $\volnondim=0.06,0.04$.
+are underpredicted than in the previous case, i.e. $\volnondim=0.06,0.04$. As we will see later the domain averaged characteristic concentration produces proper results. 
 \begin{figure}[htb!]
@@
 \label{results:vanbaten}
-The van Baten formulation which is calculated as the change of mass in domain with characteristic
-concentrations to be as the average domain simulation and as the averaged flux input/output
-concentration. One can see them in Fig. \ref{fig:vanbaten} for $Ca=0.097$ and
-$Ca=1.04$. One can see that results are consistent with the simulations in Section
-\ref{main:results:periodic} for the volumetric mass transfer coefficient measured with the domain
-averaged concentration in the whole range of capillary numbers. Note that for $Ca=0.097$ the
-obtained mass transfer coefficient is less than in Section \ref{main:results:periodic}. However, as
+The van Baten formulation, Eq.
+\ref{eq:vanbaten:formulation}, is calculated as the change of mass in domain divided on the time difference.
+We examined two approaches:  the characteristic concentration to be as the average domain simulation and as the averaged flux input/output
+concentration. The latter case corresponds to the work \cite{vanbaten-circular}. The results are presented in Fig. \ref{fig:vanbaten} for $Ca=0.097$ and
+$Ca=1.04$. One can see that the
+inlet/outlet
+flux averaged concentration is shown to be inconsistent.
+The reason that \citet{vanbaten-circular} obtained the mass transfer coefficient close to the analytical estimation is that the liquid slug is well mixed that the averaged concentration is close to the inlet/outlet concentration.
+
+However, results for the domain averaged concentration using the approach of \citeauthor{vanbaten-circular} is close to simulation results in Section
+\ref{main:results:periodic}. %for the volumetric mass transfer coefficient measured with the domain
+%averaged concentration in the whole range of capillary numbers. 
+Note that for $Ca=0.097$ the
+obtained mass transfer coefficient value is a bit less than the value in Section \ref{main:results:periodic}. However, as
 it will be shown later the obtained volumetric mass transfer coefficient for $Ca=0.0097$ has the
-same value as for the simulations of a few unit cells. The
-inlet/outlet
-flux averaged concentration is shown to be consistent only for velocity patterns related to larger
-Capillary numbers, i.e. $Ca\geq0.7$. 
+same value as for the simulations of a few unit cells.
+Therefore this approach produces most accurate results but requires the results in time and space to calculate the mass change in time and the averaged domain characteristic concentration.
+% only for velocity patterns related to larger
+%Capillary numbers, i.e. $Ca\geq0.7$. 
 \begin{figure}
@@
 averaged (left) and inlet/outlet flux averaged concentration (right). One can
-see that \citet{vanbaten-circular} formulation is good with the characteristic concentration being
+see that \citet{vanbaten-circular} formulation produces good results with the characteristic concentration being
 the average concentration. Moreover, the values are more close to values obtained with many cells
@@
 Thus, it won't be covered here, especially as it requires extensive computational resources (grid is
-$30000\times 200$).
+$30000\times 202$ nodes).
 
 As it was discussed in the previous section we want to keep
-velocity around $0.05-0.1$. The number of steps for mass to cross whole domain is
+velocity around $0.05-0.1$ to avoid computational burden. The number of steps for mass to cross whole domain is
 limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into the account the bulk
@@
 rate in the domain adjusted with inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
-resembles the experimental picture: if one have enough unit cells then the average domain
+resembles the experimental picture: if one have enough unit cells then the averaged domain
 concentration should change in time according to Eq. \ref{theor:continuous:mass:transfer}: 
@@
 \vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
--t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
-\feq
-The
-latter is the main equation that can help to obtain the volumetric mass transfer coefficient from
-mass transfer simulations with any bounary conditions (periodic boundary conditions, open
-boundaries). Eq.\ref{main:main:main} can be rewritten as:
-\beq
-\begin{aligned}
-\volnondim=\frac{\lunit}{\ugas+\ububble} \frac{V \frac{(\langle C(t_2)\rangle - \langle C(t_1)
-\rangle)}{t_2-t-1}}{\dots}\\
+-t_1)}\ln\biggl(\frac{C^*-\langle C(t_1) \rangle}{C^*-\langle C(t_2)\rangle}\biggr)
+\feq
+The non-dimensional volumetric mass transfer coefficient calculated based on Eq.
+\ref{moving:average} (averaged domain concentration changes in times) is
+represented in Fig. \ref{fig:moving:average:ca0097} for different unit cells. One can see that the
+results are consistent with the mass flux
+concentration based on \citeauthor{vanbaten-circular} formulation with the characteristic
+concentration being averaged domain concentration (see Section \ref{results:vanbaten}).
+That proves two things:  the domain averaged concentration is the only choice for the characteristic concentration, and periodic boundary conditions for one unit cell produce good results.
+
+%The
+%latter is the main equation that can help to obtain the volumetric mass transfer coefficient from
+%mass transfer simulations with any bounary conditions (periodic boundary conditions, open
+%boundaries). 
+In comparison with periodic boundary conditions Eq.\ref{main:main:main} allows to calculate the mass transfer coefficient differently. Eq. \ref{main:main:main}  can be rewritten as:
+\beq
+\label{main:main:main:thorough}
+\begin{aligned}
+\volnondim=\frac{\lunit}{\ugas+\ububble} \frac{V \frac{\langle C(t_2)\rangle - \langle C(t_1)
+\rangle}{t_2-t_1}}{\dots}\\
 \frac{-\int{\coutlet(\lunit,y,t^*) u(\lunit,y) \mathrm{d} y}+\int{\cinlet(0,y,t^*)
@@
 Fig. \ref{fig:unit:6} shows average concentrations in different units and $\volnondim$ based on Eq.
-\ref{main:main:main} calculated for each unit for velocity
-scale $10$ and  $6$ unit cells (all velocity scales produce same results). One can see that the
-volumetric mass transfer cofficient is consistent for internal segments, i.e. $3-5$. One can see
-that Eq. \ref{main:main:main} for a few unit cells produce the same results as periodic boundary
-conditions in Section \ref{main:results:periodic}. The same dependencies
+\ref{main:main:main:thorough} calculated for each unit for velocity
+scale $10$ and  $6$ unit cells (all velocity scales produce same results). It is shown that the
+volumetric mass transfer cofficient is consistent for internal segments, i.e.
+$3-5$ unit cells numbers.
+The results for the volumetric mass transfer coefficient calculated by Eq.
+\ref{main:main:main} for a few unit cells  are close to results for periodic boundary
+conditions in Section \ref{main:results:periodic}. 
+%However, they are even closer to results calculated by approach of \citeauthor{vanbaten-circular} with the domain averaged characteristic concentration. 
+The same dependencies
 can be found for
@@
 
-The non-dimensional volumetric mass transfer coefficient calculated based on Eq.
-\ref{theor:continuous:mass:transfer} (averaged domain concentration changes in times) is
-represented in Fig. \ref{fig:moving:average:ca0097} for different unit cells. One can see that the
-results are less than the volumetric mass transfer coefficient , but consistent with the mass flux
-concentration based on \citeauthor{vanbaten-circular} formulation with the characteristic
-concentration being averaged domain concentration (see Section \ref{results:vanbaten}).
+Though the calculation of the  volumetric mass transfer coefficient is harder using Eq.
+\ref{main:main:main:thorough}.
+However, it will be shown below that this equation can be significantly simplified in case of larger capillary numbers $Ca>0.7$.
+
 \begin{figure}[htb!]
@@
 volumetric
-mass transfer coefficient is calculated based on Eq. \ref{main:main:main} and accounts for inlet
+mass transfer coefficient is calculated based on Eq. \ref{main:main:main:thorough} and accounts for inlet
 and outlet fluxes. \label{fig:unit:6}}
@@
 \subsection{$Ca=1.040$ results}
-The same correlations were examined for the different velocity pattern $Ca=1.040$ and initial
-velocity $\ububble=0.055$ and initial diffusion $D=0.0008375$. If only velocity scaling is
-performed then a few unit cells simulations for
-this capillary number  are unstable. To improve stability we changed original Peclet number by
+The same correlations were examined for the different velocity pattern $Ca=1.040$.%, initial
+%velocity $\ububble=0.055$, initial diffusion $D=0.0008375$. If only velocity scaling is
+%performed then a few unit cells simulations for
+%this capillary number  are unstable. 
+A few unit cells simulations with the original Peclet number $Pe=14041$.To improve stability we changed the original Peclet number by
 increasing
-diffusion. The results for unit cells are the same as for $Ca=0.097$:
+diffusion to $Pe=2644$. The results for unit cells are the same as for $Ca=0.097$:
 at least $6$ unit cells are required to be simulated to avoid the influence of boundaries. Thus,
-only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040}, that show only the
-average concentration for each unit cell. One can see that the average volume concentration come to
+only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040} which shows only the
+average concentration for each unit cell. One can see that the average volume concentration for each unit cell come to
 constant values and are not increasing with time. Thus, all the
-mass generated with medium is transfered through the boundaries. This is the indication that the
+mass generated with medium is transferred through the boundaries. This is the indication that the
 liquid slug is not mixed. Note that the periodic boundary conditions can not show whether the
-liquid slug is mixed or not, since the averaged domain concentration is always increasing in time. 
+liquid slug is mixed or not due to the fact that the averaged domain concentration always increases in time. 
 Thus, the volumetric mass transfer coefficient $\volnondim$ can be calculated according to the
@@
 \frac{\dot{m}-\int{\coutlet(y)u(\lunit,y)\mathrm{d}y}+\int{\cinlet(y)u(\lunit,y)\mathrm{d}y}}{V
-\Delta C},
-\feq 
-where $V$ is the unit cell volume, $\Delta C$ is the concentration difference between the bubble
-surface concentration $\cstar$ and the averaged liquid domain concentration $\langle
-C(t)\rangle$. There is no accumulated mass in the domain. Thus, $\dot{m}=0$. As periodic boundary
+(\cstar - \langle C(t) \rangle},
+\feq 
+where $V$ is the unit cell volume. There is no accumulated mass in the domain. Thus, $\dot{m}=0$. As periodic boundary
 conditions this case is another extreme limit of Eq. \ref{main:main:main}. Note that to calculate
 the volumetric mass transfer coefficient one needs only the spatial information and does not
-require the knowledge of how concentration is changed in time.
+require the knowledge of how the averaged concentration is changed in time.
+This approach is the file storage saving computational approach for the Bretherton/Taylor phenomenon flow with $Ca>0.7$ where there is no vortex in the liquid slug.
 
 Fig. \ref{fig:periodic:ca1040}
-(bottom) shows the volumetric mass transfer coefficient, based on spatial calculations of
+(bottom) shows the volumetric mass transfer coefficient based on spatial calculations of
 inlet/outlet concentrations. One can see that the volumetric mass transfer coefficient is close to
 the calculated volumetric mass transfer coefficient using the time averaged approach and periodic
-boundaries one unit cells simulations. 
+boundaries one unit cells simulations presented in the same figure for comparison reasons. 
 \begin{figure}[htb!]
@@
 That means whatever was
-generated by medium is transfered through the outlet
-boundary. O This is the indication that the tracer in the slug is not
+generated by medium is transferred through the outlet
+boundary. This is the indication that the tracer in the slug is not
 mixed and the volumetric mass transfer coefficient, $\volnondim$, can be
@@
 \end{figure}
-The volumetric mass transfer coefficient with periodic boundary simulations for $Pe=2644$ (velocity
-scale $2$, diffusion scale $10$) and time dependent, Eq. \ref{theor:continuous:mass:transfer},
-average volumetric mass transfer coefficient are presented in Fig. \ref{fig:periodic:ca1040}. Note
-that they coincide. Therefore, for certain hydrodynamic patterns one can easily convert time
+%The volumetric mass transfer coefficient with periodic boundary simulations for $Pe=2644$ (velocity
+%scale $2$, diffusion scale $10$) and time dependent, Eq. \ref{theor:continuous:mass:transfer},
+%average volumetric mass transfer coefficient are presented in Fig. \ref{fig:periodic:ca1040}. 
+Note
+that all approaches coincide. Therefore, for certain hydrodynamic patterns ($Ca>0.7$) one can easily convert time
 domain to the spatial domain calculations.
@@
 \subsection{Experiment and Analytical correlations comparison}
-The goal of this paper is not to compare with the experiment correlations, but give the
-procedure to perform numerical simulationsrof  in the lattice Boltzmann framework. However, the
+The goal of this paper is not to compare simulation results with the experiment correlations, but give the
+procedure to perform numerical simulations  in the lattice Boltzmann framework. However, the
 small comparison is performed.
-Unfortunately the experiments to the best authors' knowledge measuring the mass flux for infinite
-width  bubbles flowing between parallel plates are absent. However, one of interesting
+Unfortunately the experiments to the best authors' knowledge measuring the mass flux for  bubbles flowing between parallel plates are absent. However, one of interesting
 correlations for the mass transfer volumetric coefficient was presented by
@@
 $Pe^{-0.5}$. As well one can use analytical estimations for the volumetric mass transfer
-coefficient calculated using Higbie penetration theory \cite{higbie}. One can show following works
-\cite{irandoust,vanbaten-circular} that the analytical expression for the flow between plats has
+coefficient calculated using the Higbie penetration theory \cite{higbie}. One can derive by following works
+\cite{irandoust,vanbaten-circular} that the analytical expression for the flow between plates has
 the following form:
@@
 
-Fig. \ref{fig:volume:mass:coefficient} shows a comparison between corelation by
-\citet{yue-mass}, analitical expression, Eq. \ref{vanbaten:analytical:expresssion} and the current
-simulations coefficients presented in Table
+Fig. \ref{fig:volume:mass:coefficient} shows a comparison between correlation by
+\citet{yue-mass}, analytical expression, Eq. \ref{vanbaten:analytical:expresssion}, and the current
+simulation coefficients presented in Table
 \ref{table:steady:state:average}. The coefficients are close to each other, especially given that
@@
 \includegraphics[width=\textwidth]{Figures/correlations_comparison.eps}
-\caption{Comparison between correlation by \citet{yue-mass}, analytical correlation following work
-\cite{irandoust} and mass transfer coefficient based
+\caption{Comparison between the correlation by \citet{yue-mass}, the analytical correlation derived by following the work
+\cite{irandoust} and the mass transfer coefficient based
 on periodic boundary conditions. The fitting curve is proportional to $Pe^{-0.5}$ which corresponds
 to all correlations. As well one can see that the deviation from the analytical expression becomes
-larger because the analytical expression does not account for the velocity pattern and a bubble
+larger with the Peclet number increasing $Pe$. It is because the analytical expression does not account for the velocity pattern and a bubble
 shape change.\label{fig:volume:mass:coefficient}}
@@
 \ref{theor:average:concentration:time} gives a bit overestimated volumetric mass transfer
-coefficient. Formulation of
+coefficient. The original formulation of
 \citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
 to be characteristic concentration. A few unit cells simulations are harder to perform, but they
-have indicator of how well the liquid slug is mixed. As well, for velocity patterns for $Ca\geq
+have indicator of how well the liquid slug is mixed. As well, for velocity patterns of $Ca\geq
 0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
-coefficient based on the spatial location, not time averaged values used in all other
+coefficient only based on the spatial location, not time snapshots of domain concentration values used in all other
 approaches. Finally, a sample of results was
@@
 $C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
-\subsection{The Poiseuille parabolic profile}
+\section{The Poiseuille parabolic profile}
 \label{appendix:poiseuille}

### 2012-05-06 Text/introduction.tex
Style fixes in the first 20% of the paper. Also reformat the whole text so that it does not require wrapping and is easier to read.

@@
 \begin{abstract}
-This work presents a thorough procedure of how to determine the volumetric mass transfer
-coefficient
-in the context of lattice Boltzmann simulations for the Bretherton/Taylor bubble train flow.
-In this work we address the situation when the hydrodynamic pattern changes from having a vortex in slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.
-For the latter case the bubble shape is not symmetric and cannot be approximated through flat surfaces and circumferences as it is done in literature \cite{vanbaten-circular,kreutzer-overview}.
-For $Ca<0.7$ where there is a vortex in the slug the tracer is well mixed.
-Thus, it is common to  use periodic boundary conditions  and the inlet/outlet averaged concentration as the characteristic concentration, Eq.
-\ref{eq:main:definition}.
-The later is not valid for flows where tracer is not well mixed, i.e.
-$Ca>0.7$.
-This work through examination of different boundary conditions and different characteristic concentration definitions establishes the procedure to determine the volumetric mass transfer coefficient for flows with the capillary number $0.1<Ca<1.0$.
-With simulations of a few unit cells the connection between time (used in simulations) and space (used in experiments) domains is established.
-The following boundary conditions were examined: periodic boundary conditions, open boundaries, and a few unit cells open boundary
-simulations. It was shown that the time dependent average concentration to be a characteristic
-concentration produce robust results, though a bit overpredicted. The inlet/outlet flux averaged
-concentration \cite{vanbaten-circular} to be a characteristic concentration produce unreliable results in the range of capillary numbers specified.
-In comparison with works \cite{vanbaten-circular,kreutzer-overview} where only one unit cell was simulated, a few
-unit cells open boundaries conditions resemble physical situation most closely. However, they  are harder to be conducted 
-but provide the volumetric mass transfer coefficient based only on the spatial information for the
-capillary number $Ca>0.7$. 
-%As well, a few unit cells simulations can provide more information about
-%mixing in the liquid slug in comparison with the periodic boundary conditions. 
-We show
-that all presented in literature strategies are extreme limits of one equation,
-Eq. \ref{main:main:main}. Finally, simulation results for different Peclet numbers
-are compared with analytical predictions presented by \citet{vanbaten-circular} and shows a good
-agreement. The work is of use to people performing mass transfer numerical simulations for bubble
-train flow in microchannels and/or within the
-lattice Boltzmann model context.
+This work presents a procedure for the determination of the volumetric mass transfer
+coefficient in the context of lattice Boltzmann simulations for the Bretherton/Taylor bubble train
+flow for capillary numbers $0.1 < Ca < 1.0$. We address the case where the hydrodynamic pattern changes from having a
+vortex in slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.  In the latter case
+the bubble shape is asymmetric and cannot be approximated through flat surfaces and circumferences as
+is often done in literature \cite{vanbaten-circular,kreutzer-overview}.  When the vortex is present
+in the slug, the tracer is well mixed and it is common to use periodic boundary conditions and the inlet/outlet-averaged concentration
+% Do we really want equation references in the abstract?
+as the characteristic concentration, Eq. \ref{eq:main:definition}.
+The latter is not valid for flows where tracer is not well mixed, i.e. $Ca>0.7$.  We therefore
+examine various boundary conditions (periodic, open, open with more than 1 unit cell) and definitions of the characteristic concentration.
+We show that the time-dependent average concentration produces the most robust results and
+that all strategies presented in the literature are extreme limits of one equation,
+% Same question applies.
+Eq. \ref{main:main:main}. Finally, we show good agreement of simulation results for different Peclet numbers
+with analytical predictions \citet{vanbaten-circular}.
 \end{abstract}
@@
 \label{intro}
-The monolith reactors during last years are getting more attention as a promising alternative to slurry
-reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}. Reactors usually operate in the Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
+Monolith reactors have recently been getting more and more attention as a promising alternative to slurry
+reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}.  These reactors usually operate in
+ the Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
 a liquid medium of equally sized, long air bubbles, see
@@
 is characterized by surface tension dominance over inertia and viscous effects, and by
-comparatively small gas flow velocities \cite{yue-mass}. Due to surface tension dominance bubble train flow exhibit advantageous properties which can not be achieved
+comparatively small gas flow velocities \cite{yue-mass}. Due to the dominance of surface tension, the bubble train flow exhibits advantageous
+ properties which can not be achieved
 in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
-transfer from a gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.
-Moreover, the low slip velocity between gas and liquid is utilized in the experiments to measure liquid velocity \cite{taylor}:  bubbles travelling with approximately the same velocity as liquid can be captured with a camera.
-Overall, nowadays one can find a large number of applications
+transfer from gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.
+ Moreover, the low slip velocity between gas and liquid is utilized in the experiments to measure liquid velocity \cite{taylor}:  bubbles
+ travelling with approximately the same velocity as liquid can be captured with a camera. These properties explain why nowadays one can find a large number of applications
 of the Bretherton-Taylor bubble train flow: continuous flow analyzers to measure liquid velocity, lung openings, chemical reactions
-as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. Extensive reviews of \citet{kreutzer-overview,
+such as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. The extensive reviews of \citet{kreutzer-overview,
 gupta-review,yue-mass} cover a significant number of applications.
@@
 This work is focused on the gas to liquid mass transfer 
-study for the Bretherton/Taylor flow. The good understanding of mass transfer and how it depends on the
-parameters as the capillary number, the Reynolds number, slug and bubble lengths allows to properly
-manufacture a microchannel with necessary properties to ensure that chemical
-reactions are performed in the best manner.
-The mass transfer coefficient characterizing mass transfer is defined as the flux from the surface divided on the concentration difference between the concentration imposed on the body and the characteristic concentration in the domain.
+study for the Bretherton/Taylor flow. A good understanding of mass transfer and how it depends on the
+parameters such as the capillary number, the Reynolds number, and slug and bubble lengths allows to properly
+manufacture a microchannel with properties necessary to ensure that chemical
+reactions are performed in the best possible manner. The mass transfer coefficient is defined as the flux from the 
+surface divided by the concentration difference between the concentration imposed on the body and the characteristic concentration in the domain.
  The characteristic concentration in the domain significantly depends on underlying hydrodynamics fields. 
-For example, experimental studies \cite{yue-mass,bercic-mass} show a complex dependency of the mass transfer coefficient on flow parameters: bubble and slug lengths, bubble velocity, which are in turn depend on the capillary number $Ca$ and the Reynolds number $Re$.
+ For example, experimental studies \cite{yue-mass,bercic-mass} show a complex dependency of the mass transfer coefficient on flow parameters:
+ bubble and slug lengths, and bubble velocity, which are in turn dependent on the capillary number $Ca$ and the Reynolds number $Re$. 
 \citet{yue-mass} established an experimental correlation for the volumetric mass transfer coefficient for a bubble train as
@@
 Thus, the understanding of mass transfer for the bubble train flow is not possible without deep understanding of hydrodynamic patterns.
-There are a number of studies available for the hydrodynamic study of the bubble train flow: experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
-For the flow of long bubbles between parallel plates chosen here as the study case it is indicated that  there exists a vortex in the liquid slug for $Ca<0.7$ , see Fig.
-\ref{fig:streamlines:tweaked:velocity}.
-As well, the bubble shape for low capillary numbers ($Ca<0.1$ \cite{cerro-bubble-train}) is symmetric.
-Thus, in the case of flow between plates for $Ca<0.1\div0.7$ the bubble shape can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug.
-This is heavily utilized for mass transfer analytical estimations.
-
-As mentioned  the mass transfer coefficient is defined as the mass flux from certain area, Eq.
-\ref{eq:main:definition}.
-Thus, analytical estimations \cite{kreutzer-overview,irandoust} are  based on decomposition of the bubble shape.
-The mass transfer coefficient is calculated through two separate contributions from two films and two hemicircles.
-For both contributions the Higbie penetration theory \cite{higbie} is utilized, which states that the mass transfer coefficient  for simple geometry flow depends on the average time of liquid packet interaction with a geometrical feature.
-It can be calculated as $\sqrt{\frac{\pi D}{t_{\mathrm{char}}}}$, where $t_{\mathrm{char}}$ is the interaction characteristic time, $D$ is the diffusion coefficient.
-As the example for the Higbie penetration theory, the mass  transfer coefficient for the flow of bubbles between parallel plates  is calculated as (similarly to work of \citet{vanbaten-circular}):
+There are several works studying the hydrodynamic properties of the bubble train flow: 
+experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
+ For the flow of long bubbles between parallel plates chosen here as the study case it is indicated that  there exists a vortex 
+in the liquid slug for $Ca<0.7$ , see Fig. \ref{fig:streamlines:tweaked:velocity}, and that the bubble shape is symmetric for low capillary 
+numbers ($Ca<0.1$ \cite{cerro-bubble-train}).  In the case of flow between plates for $Ca<0.1\div0.7$ the bubble
+ shape can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug. This is heavily 
+utilized for analytical estimations of mass transfer properties.
+
+Since mass transfer coefficient is defined in terms of a mass flux from a certain area, Eq. \ref{eq:main:definition},
+analytical estimations \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble shape. The mass
+ transfer coefficient is calculated through two separate contributions from two films and two hemicircles. For both 
+contributions the Higbie penetration theory \cite{higbie} is utilized, which states that the mass transfer coefficient
+ for a simple flow geometry depends on the average time of liquid packet interaction with a geometrical feature. It 
+can be calculated as $\sqrt{\frac{\pi D}{t_{\mathrm{char}}}}$, where $t_{\mathrm{char}}$ is the characteristic 
+time of the interaction, and $D$ is the diffusion coefficient. As an example of the application of the Higbie penetration theory,
+ the mass  transfer coefficient 
+for the flow of bubbles between parallel plates  is calculated as (similarly to the work of \citet{vanbaten-circular}):
 \beq
@@
 \feq
-where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through planar part of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time which liquid in the slug travels the distance of half bubble circumference.
-
-Despite the simplicity, analytical expressions work well for flows with low capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape is symmetrical and can be nicely approximated.
-Moreover, because of the hydrodynamic pattern in the slug, i.e.
-there is a vortex in slug, one can estimate the time for fluid batch to travel whole circumference.
-However, with the change of the capillary number the situation drastically changes.
-The symmetrical bubble shape changes and resembles a bullet \cite{kuzmin-binary2d}.
-With the change of the shape and for flows with $Ca>0.7$ there is no vortex in the liquid slug.
-In this case the Higbie theory fails to estimate contribution from bubble caps.
-Thus, the need of numerical simulations where all hydrodynamics fields and complicated bubble shapes are taken in the account is obvious.
-
-However, available numerical studies of mass transfer \cite{kreutzer-overview,vanbaten-circular} are lacking the simulation of  bubble shapes.
-The usual simulation of the mass transfer  is performed as follows:
+where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through the planar part
+ of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time in which liquid in the slug travels the distance of half bubble circumference.
+
+Despite their simplicity, analytical expressions work well for flows with low
+capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape is
+symmetrical and can approximated with good precision. Moreover, because of the
+hydrodynamic pattern in the slug (i.e. presence of a vortex in slug), one can
+estimate the time for a fluid batch to travel whole circumference.   However,
+with the increase of the capillary number the situation drastically changes -- the
+symmetrical bubble shape is lost and the bubble shape resembles a bullet \cite{kuzmin-binary2d}.
+For flows with $Ca>0.7$ there is also no vortex in the liquid slug. In this case the Higbie theory fails
+to estimate the contribution from bubble caps, which explains the need to turn to numerical simulations where all
+hydrodynamics fields and complicated bubble shapes are taken into account.
+
+Available numerical studies of mass transfer
+\cite{kreutzer-overview,vanbaten-circular} lack the simulation of
+bubble shapes. The usual simulation of mass transfer is performed as
+follows: \begin{description}
+ \item[I] The bubble shape is calculated either
+through analytical correlations \cite{bretherton} or experimental correlations
+\cite{cerro-bubble-train} without directly resolving bubbles shapes through
+multiphase simulations.  The expressions for bubble shapes are available only
+for flows with the capillary number $Ca<0.1$.
+  \item[II] Hydrodynamic fields
+are then obtained by performing simulations of one-component flow around the
+droplet by imposing the bubble velocity on the walls. Thus, the simulations are
+performed in the reference frame moving with the bubble. The stress-free
+condition is imposed at the bubble surface.
+  \item[III]  The mass transfer
+simulations are performed in the reference frame moving with the bubble. The
+saturation concentration is imposed at the bubble surface. Only one unit cell
+with one bubble in it is used for simulations. Periodic boundary conditions are
+utilized to determine the volumetric mass transfer coefficient, which is
+calculated through the following equation \cite{vanbaten-circular}:
+\begin{equation} \label{main:simulation:equation}
+\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\coutlet\rangle}
+\frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\ cell\ volume}},
+\end{equation}
+ where $\langle\coutlet(t)\rangle=\int{C \uoutlet
+\mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the space-averaged outlet
+concentration as a function of time used as the characteristic concentration
+in the definition, Eq. \ref{eq:main:definition}.  The time-averaged
+concentration flux ($\mathrm{\overline{Flux}}$) is calculated as the difference
+between the overall average concentration in the whole domain
+($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$) at time $t_1$ and at time
+$t_2$ divided by the time difference $t_2-t_1$. The agreement between numerical
+simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass}
+was good.  \end{description}
+
+The presented numerical approaches \cite{vanbaten-circular,kreutzer-overview}.
+can be critized on a number of points. They mainly
+originate from the bubble shape approximation, which is taken to be symmetrical, i.e.
+consisting of hemispheres and cylinder film for the case of flow in circular
+capillaries. This is valid  for small capillary numbers $Ca<0.1$. As previously
+discussed, for such capillary numbers the tracer is well mixed in the slug and 
+the choice of the characteristic concentration needed for the mass transfer
+coefficient, Eq. \ref{eq:main:definition} is obvious. With small
+differences in results it can be either averaged in the liquid slug
+concentration or the outlet space-averaged concentration as used in the formulation
+of \citet{vanbaten-circular}.
+
+While it clear that periodic boundary conditions can be employed for the calculation
+ of hydrodynamic fields, the same does not apply to the mass transfer coefficient.
+simulations. Experimental correlations \cite{bercic-mass} show that the
+concentration along the streamwise direction changes exponentially with distance.
+Mass transfer simulations however, are made only for one unit cell
+using the periodic boundary conditions with the same concentration at the inlet
+and at the outlet. The question how one unit cell simulation corresponds to
+experimental measurements arises where concentration difference is measured at
+the distances of at least of a few unit cells \cite{bercic-mass}. In
+other words one needs to understand how the discrete one unit cell simulation
+corresponds to the continuous picture in experiments where one does not
+distinguish bubbles but takes measurements of concentration at different
+locations.
+
+Addressing situations for a rich number of hydrodynamic patterns, shapes, and
+effects for a bubble train, we feel that there is a need to examine more
+carefully the strategies and assumptions behind the numerical calculations
+of the mass transfer coefficient. We aim at establishing clear
+procedures as to how properly obtain the mass transfer coefficient via a study
+of different boundary conditions and different definitions of characteristic concentration
+The case we want to examine is a two-dimensionalbubble train flow between parallel plates.
+We address the following issues:
  \begin{description}
-\item[I] The bubble shape is calculated either through analytical correlations \cite{bretherton} or experimental correlations \cite{cerro-bubble-train} without directly resolving bubbles shapes through multiphase simulations.
-The expressions for bubble shapes are available only for flows with the capillary number $Ca<0.1$.
-\item[II] Hydrodynamics fields are then obtained by performing simulations of one-component flow around the droplet by imposing the bubble velocity on the walls.
-Thus, the simulations are performed in the reference frame moving with the bubble.
-The stress free condition is imposed at the bubble surface.
-\item[III]  The mass transfer simulations are  performed in the reference frame moving with the bubble.
-The saturation concentration is imposed at the bubble surface.
-Only one unit cell with one bubble in it is used for simulations.
-Periodic boundary conditions are utilized to determine the volumetric mass transfer coefficient, which is calculated through the following equation \cite{vanbaten-circular}:
-\begin{equation}
-\label{main:simulation:equation}
-\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\coutlet\rangle} \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\
-cell\ volume}},
-\end{equation}
-where $\langle\coutlet(t)\rangle=\int{C \uoutlet \mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the averaged in space outlet concentration as the function of time used as the characteristic concentration in the definition, Eq.
-\ref{eq:main:definition}.
-The averaged in time concentration flux ($\mathrm{\overline{Flux}}$) is calculated as the difference between the overall
-average concentration in the whole domain ($\langle\coverall\rangle=\int_{V} C \mathrm{d}V /V$)
-at time
-$t_1$ and at time $t_2$ divided on the time difference $t_2-t_1$. The agreement between numerical
-simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass} was good. 
+ \item[I] Applicability of periodic boundary
+conditions to determine the mass transfer coefficient when the vortex in the slug
+disappears.
+ \item[II] Validity of the inlet/outlet-averaged or domain-averaged concentrations as
+characteristic concentrations in the definition of the mass transfer
+coefficient.
+ \item[III] Transition of the continuous experimental picture to
+numerical simulations of a few unit cells, the issue of correspondence
+between space averages (simulations \cite{vanbaten-circular}) and time averages (experiment).
+ \item[IV] Influence of the hydrodynamic pattern in flows with $Ca>0.7$ on the mass transfer.
 \end{description}
-There is a certain critics towards the presented numerical approaches \cite{vanbaten-circular,kreutzer-overview}.
-They mainly originate from the bubble shape approximation.
-It is taken symmetrical, i.e.
-consisting from hemispheres and cylinder film for the case of flow in circular capillaries.
-This is valid  for small capillary numbers $Ca<0.1$.
-As it was discussed, for such capillary numbers in the reference frame moving with the bubble there is a vortex in slug.
-Thus, the tracer is well mixed in slug.The choice of the characteristic concentration needed for the mass transfer coefficient, Eq.
-\ref{eq:main:definition}, in this case  is obvious.
-With small differences in results it can be either averaged in the liquid slug concentration or the outlet space averaged concentration as used in formulation of \citet{vanbaten-circular}.
-Another critics is towards periodic boundary conditions to calculate the mass transfer coefficient.
-While it is clear to use periodic boundary conditions for the calculation of hydrodynamics fields for  long bubbles motion in the microchannel, it is not the case for mass transfer simulations.
-Experimental correlations \cite{bercic-mass} show that the concentration along the streamwise direction changes as the exponential function.
-However, mass transfer simulations are made only for one unit cell using the periodic boundary conditions with the same concentration at the inlet and at the outlet.
-The question how  one unit cell simulation corresponds to experimental measurements arises where concentration difference is measured at the distances of at least of a few unit cells difference \cite{bercic-mass}.
-In other words one needs to understand how the discrete one unit cell simulation corresponds to the continuous picture in experiments where one does not distinguish bubbles but takes measurements of concentration at different locations.
-
-Addressing situations for a rich number of hydrodynamic patterns, shapes, effects for a bubble
-train we feel that there is a need to examine more carefully the strategies and assumptions which
-stay behind the mass transfer coefficient numerical simulations. We aim at establishing
-numerical simulations procedures as to how properly obtain the mass transfer coefficient via a study of different boundary conditions, different characteristic concentration definitions.
-The case we want to examine is the two-dimensional case of the bubble train flow between parallel plates.
-The following issues will be addressed:
-\begin{description}
-\item[I] Applicability of periodic boundary conditions to determine the mass transfer coefficient when there is a change of pattern from having vortex in the slug to not having it. 
-\item[II] Validity to use the inlet/outlet averaged or domain averaged concentrations as characteristic concentrations in the definition of the mass transfer coefficient.
-\item[III] Transition of the continuous experimental picture to numerical simulations of a few unit cells mass transfer.
-This is the question about connection between time and space domains.
-In experiments the characteristic concentration is taken as an average in time, but in numerical simulations \cite{vanbaten-circular} the characteristic concentration is taken as an average in space.
-\item[IV] How the change of the hydrodynamic pattern ($Ca>0.7$) influences mass transfer.
-\end{description}
-Note that the goal of this paper is to establish procedures and boundary conditions used for the mass transfer coefficient determination.
-Though at the end of the manuscript we present a comparison of the volumetric mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations \cite{yue-mass}, the thorough
-determination of the Sherwood number as a function of
-other non-dimensional parameters as gas holdup, bubble/slug lenghts, the capillary number is the goal of the future work.
+In addition, at the end of the manuscript we present a comparison of dependence the volumetric
+mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations
+\cite{yue-mass}.  The thorough determination of the Sherwood number as a
+function of other non-dimensional parameters such as gas holdup, bubble/slug
+lenghts, the capillary number is the goal of future work.
 \begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/benchmark_hydro.eps}
-\caption{Simplified sketch of the bubble train motion. Using periodic conditions for the velocity
-field is natural, but needs validation for the mass transfer. \label{fig:benchmark:hydro}}
-\end{figure}
-
-To establish numerical procedures we performed multiphase simulations \cite{kuzmin-binary2d,kuzmin-binary3d} for the range of capillary numbers $Ca=0.1\div 1.0$ to extract bubble shapes.
-For this range of capillary numbers we are able to capture the bubble shape change and the change of hydrodynamic patterns.
-The mass transfer simulations were performed with different boundary conditions (open, periodic) and with a few unit cells ($1$ to $10$ unit cells).
-The numerical approach we take is the lattice Boltzmann method, a relatively new CFD
-competitor emerged during last $20$ years \cite{frisch,mcnamara,HJ,HSB}. During years the
-method was applied to simulate not only hydrodynamic problems \cite{yu}, but as well multiphase
+\caption{Simplified sketch of the bubble train motion. Using periodic
+conditions for the velocity field is natural, but needs validation for the mass
+transfer.
+\label{fig:benchmark:hydro}}
+\end{figure}
+
+To establish numerical procedures we performed multiphase simulations
+\cite{kuzmin-binary2d,kuzmin-binary3d} for the range of capillary numbers
+$Ca=0.1\div 1.0$ to extract bubble shapes. For this range of capillary numbers
+we are able to capture the bubble shape change and the change of hydrodynamic
+patterns. The mass transfer simulations were performed with different boundary
+conditions (open, periodic) and with a few unit cells ($1$ to $10$ unit cells).
+As our numerical approach we take the lattice Boltzmann method, a relatively
+new CFD competitor developed during last $20$ years
+\cite{frisch,mcnamara,HJ,HSB}. This method was successfully applied to simulate
+not only simple hydrodynamic problems \cite{yu}, but also multiphase
 flows \cite{Shan-chen:extended,swift,gunstensen}, heat transfer
-\cite{yuan-thermal,zhang-thermal}, ferrofluids \cite{dellar-ferro,kuzmin-aniso}.
-
-The mass transfer problems in the lattice Boltzmann framework were mainly addressed in series of
-works of Ginzburg and co-authors
-\cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}. However, all these works
-are of general nature to simulate the advection-diffusion equation via the lattice Boltzmann
-framework. In comparison, this work focuses on the application side as to establish the procedure of how to obtain the
-volumetric mass transfer coefficients for bubble train flow. One should mention the work of
-\citet{inamuro-scalar-boundary} about heat and mass transfers in the porous media and the work
-of \citet{jos-mass} simulates lateral mixing in cross-channel flow. While two last works are focused
-at the particular mass transfer problems, both problems are of homogeneous nature and do not
-guide as how to obtain the mass transfer coefficient for non-homogenous problems.
+\cite{yuan-thermal,zhang-thermal}, and ferrofluids \cite{dellar-ferro,kuzmin-aniso}.
+
+The mass transfer problems in the lattice Boltzmann framework were mainly
+addressed in series of works of Ginzburg and co-authors
+\cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}.
+In contrast to these works whose focus was on simulating the
+advection-diffusion equation via the lattice Boltzmann framework, we concentrate
+on the application side.  One should also mention the work of \citet{inamuro-scalar-boundary}
+about heat and mass transfers in porous media and the work of
+\citet{jos-mass} simulating lateral mixing in cross-channel flow.  The last two
+works are focused on problems of homogeneous nature and do not provide
+guidance as how to obtain the mass transfer coefficient for non-homogenous cases.
 
 The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
-for the bubble train flow to derive expressions to connect space and time domains. Then the lattice
-Boltzmann model used to simulate mass transfer is presented followed by benchmarks. Finally,
-numerical simulations of different boundary conditions and a few unit cells simulations for
-different hydrodynamic patterns are presented to establish the thorough procedure to determine the
+for the bubble train flow to derive expressions to connect the space- and time-averages.  Then, the lattice
+Boltzmann model used to simulate mass transfer is presented, and followed by benchmarks. Finally,
+numerical simulations of different boundary conditions and simulations spanning a few unit cells for
+different hydrodynamic patterns are presented to establish the procedure to determine the
 volumetric mass transfer coefficient. The comparison with analytical correlations is also presented.
@@
 \section{Mass transfer definitions}
-By the definition the mass transfer coefficient from the surface with the imposed constant
+By definition, the mass transfer coefficient from the surface with the imposed constant
 concentration $\cbubble$ is the following:
@@
 where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
-$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference between the surface and the surrounding medium
+$\Bigl[m^2\Bigr]$, and $\Delta C$ is the concentration difference between the surface and the surrounding medium
 $\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of velocity
@@
 
-There are different methods to estimate the mass transfer coefficient $k_L$. We first examine the
-theoretical definitions of the mass transfer in case of point mass sources.
+There exist a number of methods to estimate the mass transfer coefficient $k_L$. We first examine the
+theoretical definitions of the mass transfer in the case of point mass sources.
 \subsection{Point mass sources}
 In what follows we will present three approaches to calculate point  mass transfer
-coefficients (by point source we assume the source with the infinitesimally small surface area $P$):
+coefficients (by point source we assume the source with an infinitesimally small surface area $P$):
 \begin{enumerate}
 \item
-Let us look at the infinitesimal small domain of the volume $A \Delta x$ not
-moving and with the point mass source.  Then the concentration difference can be found as $\Delta C =
+Let us look at the infinitesimal small domain of volume $A \Delta x$, not
+moving and with a point mass source.  The concentration difference can be then found as $\Delta C =
 \cstar -
-C(t)$, where $\cstar$ is the imposed point source concentration, $C(t)$ is
-the time dependent concentration, which do not depend on the location due to homogeneity. Therefore, one can write the time dependent ODE for the
+C(t)$, where $\cstar$ is the imposed point source concentration, and $C(t)$ is
+the time-dependent concentration, which does not depend on the location due to the assumption of
+homogeneity. One can therefore write a time-dependent ordinary differential equation for the
 concentration in the domain:
@@
 with the initial condition $C(0)=0$
-The solution can be found by solving ODE:
+The solution can be found as:
 \beq
@@
 \item
-Let us predict mass transfer happening in moving with the velocity
-$U$ liquid, see Fig. \ref{fig:moving:frame}. 
+Let us predict mass transfer in a liquid moving with the velocity
+$U$, see Fig. \ref{fig:moving:frame}. 
 \begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
-\caption{The mass transfer in the moving liquid. \label{fig:moving:frame}}
-\end{figure}
-
-If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
-mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. The accumulated mass should be proportional
-to the mass transfer coefficient:
+\caption{The mass transfer in a moving liquid. \label{fig:moving:frame}}
+\end{figure}
+
+If one can assume that the point mass sources are distributed in the whole
+medium, the mass accumulated in the unit volume $V=A \Delta x$ can be
+calculated as the difference of mass fluxes entering and leaving domain $U
+\bigl(C(x+\Delta x)-C(x)\bigr)$. The accumulated mass should be proportional to
+the mass transfer coefficient:
 \beq
@@
 
-\item If one transfers to the frame moving with the liquid velocity $U$, then the situation will be
+\item If one transfers to the frame moving with the liquid velocity $U$, the situation will be
 the same as in the first case. However, one can connect the time and spatial location with the
@@
 \subsection{Bubble train}
-In the application to the bubble train flow, it is useful to think of one bubble to be a point
+In the application to the bubble train flow it is useful to think of one bubble to be a point
 source to make all considerations above valid. For example, the expression
@@
 \citet{bercic-mass}. However, one should be accurate with the definition of velocities because two
-different phases co-exist in the bubble train flow. Usually, one can take the velocity $U$ to be as
+different phases co-exist in the bubble train flow. Usually, one can take the velocity $U$ to be
 a bulk velocity or $U=\ugas+\uliq$, where $\ugas$ and $\uliq$ are liquid and gas
-superficial velocities correspondingly.
-
-Thus, the experimental measurements are straightforward as measuring concentrations at
-different
-locations and calculating the volumetric mass transfer coefficient through the logarithmic
-function. However, if one wants to analytically or numerically calculate the mass transfer coefficients, the
-situation is much more complicated because of two phases presence and complicated bubble
-geometry. As it was mentioned before depending on the capillary
+superficial velocities, correspondingly.
+
+With experimental measurements of concentration at different locations, the calculation
+of the mass transfer coefficient using the logarithmic function is straightforward.
+However, if one wants to analytically or numerically calculate the mass transfer coefficients, the
+situation is much more complicated because of the presence of two phases and complicated bubble
+geometry. As was mentioned before, depending on the capillary
 number the mixing velocity pattern is different. Analytical approaches
@@
 such 
-an assumption (slug well mixed and the concentration is uniformly distributed over
+an assumption (slug well mixed and the concentration uniformly distributed over
 the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
-concentration from film is mixed with the slug and increases the overall concentration in the slug. Thus, it decreases the mass transfer from bubble caps.
+concentration from film is mixed with the slug and increases the overall concentration in the slug, thereby decreasing
+the mass transfer from bubble caps.
 Therefore, all estimations for the analytical mass transfer coefficient calculation  do not account for mutual mass
-transfer from
-neighbouring bubbles.
+transfer from neighbouring bubbles.
 
@@
 In comparison with analytical calculations and simplifications, the numerical approach can take into
-the account the complicated mixing patterns and geometries. However, there are challenges as to
-mimic the continuous picture like moving with bulk velocity $U=\ugas+\uliq$ reacting medium as it is seen in
-experiments. Thus, the questions indicated in Section \ref{intro}, as the choice of the
-characteristic concentration, the choice of boundary conditions, arise. Next
-section gives more details about numerical simulations.
+the account the complicated mixing patterns and geometries. However, there are challenges as to how to
+mimic the continuous picture like moving with bulk velocity $U=\ugas+\uliq$ reacting medium as seen in
+experiments. Thus, the questions indicated in Section \ref{intro} arise.  The next section gives more
+ details about numerical simulations.
 
@@
 \label{section:cases}
-Ideally one needs to mimic the continuous picture as it is seen in experiments. Thus, mass transfer simulations for a number of unit cells is needed. As it was indicated above there are
-two approaches towards it - either to simulate
-the bubble train and then to measure concentration along the pipe, Eq.
+Ideally one needs to mimic the continuous picture as it is seen in experiments.
+Thus, mass transfer simulations for a number of unit cells is needed. As it was
+indicated above there are two approaches towards it - either to simulate the
+bubble train and then to measure concentration along the pipe, Eq.
 \ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with the bulk
@@
 \feq
-where $\Delta C=\cstar-\langle C(t) \rangle$ with $\langle C(t) \rangle$ to be the average
-concentration in whole liquid domain, $\dot{m}$ is the mass gain in the domain,$\int{\cinlet u(0,y) \mathrm{d}y}$ and $\int{\coutlet u(\lunit,y)\mathrm{d}y}$ are inlet/outlet mass fluxes.
-Eq.
-\ref{main:main:main} describes the mass
-balance: whatever was generated by the bubble surface equals to the mass domain change minus
-whatever left domain plus whatever entered domain.
+where $\Delta C=\cstar-\langle C(t) \rangle$ with $\langle C(t) \rangle$ to be
+the average concentration in whole liquid domain, $\dot{m}$ is the mass gain in
+the domain,$\int{\cinlet u(0,y) \mathrm{d}y}$ and $\int{\coutlet
+u(\lunit,y)\mathrm{d}y}$ are inlet/outlet mass fluxes. Eq. \ref{main:main:main}
+describes the mass balance: whatever was generated by the bubble surface equals
+to the mass domain change minus whatever left domain plus whatever entered
+domain.
 
@@
 \feqstar
-Then the mass change in the domain is
-only because of the generating bubble surface.
-However, to calculate the mass transfer coefficient one needs to have characteristic concentration  $\langle C(t) \rangle$ and mass gain $\dot{m}$ which do require the storage of time and space information.
-
-Another limiting case (will be shown later) is hydrodynamic pattern change $Ca>0.7$.
-The mass accumulation rate equals zero in this case, $\dot{m}=0$.
-One can use only spatial information to calculate the mass transfer coefficient, i.e.
-$\int{\cinlet(t) u(0,y)
-\mathrm{d}y}$ and $\int{\coutlet(t) u(\lunit,y)\mathrm{d}y}$ require only space information.
+Then the mass change in the domain is only because of the generating bubble
+surface. However, to calculate the mass transfer coefficient one needs to have
+characteristic concentration  $\langle C(t) \rangle$ and mass gain $\dot{m}$
+which do require the storage of time and space information.
+
+Another limiting case (will be shown later) is hydrodynamic pattern change
+$Ca>0.7$. The mass accumulation rate equals zero in this case, $\dot{m}=0$. One
+can use only spatial information to calculate the mass transfer coefficient,
+i.e. $\int{\cinlet(t) u(0,y) \mathrm{d}y}$ and $\int{\coutlet(t)
+u(\lunit,y)\mathrm{d}y}$ require only space information.
 
@@
 \section{Validation}
-As it was discussed analytical correlations for the mass transfer coefficient are derived  as two separate contributions: the mass transfer from two circumferences and the mass transfer from the film.
-We will
-examine
-these problems closely with the help of the lattice Boltzmann method and compare them against analytical
+As it was discussed analytical correlations for the mass transfer coefficient
+are derived  as two separate contributions: the mass transfer from two
+circumferences and the mass transfer from the film. We will examine these
+problems closely with the help of the lattice Boltzmann method and compare them
+against analytical
 solutions. The next sections will give a short introduction on the lattice Boltzmann method and present a few benchmarks.
@@
 $Ca<0.2$ is of the order of a few millions. Therefore, it is desirable to increase  velocity  $U_{\mathrm{LB}}$
-while keeping the Peclet number the same.
-If one increases velocity, then $\omegaminus$ increases as well.
-Thus, the increase of the velocity impacts positively on stability of the LBM as $\omegaminus$ is not close to its stability limit $0.5$.
+while keeping the Peclet number the same. If one increases velocity, then
+$\omegaminus$ increases as well. Thus, the increase of the velocity impacts
+positively on stability of the LBM as $\omegaminus$ is not close to its
+stability limit $0.5$.
 
@@
 \subsection{Periodic boundaries with the inlet/outlet characteristic concentration}
-\label{results:periodic:inlet:outlet}
-The volumetric mass transfer coefficient was calculated using Eq.
-\ref{theor:one:concentration:time} with the characteristic concentration being the inlet/outlet flux averaged concentration as used by \citet{vanbaten-circular}.
-One can
-see in Fig. \ref{fig:volumetric:char:concentration:vanbaten} the calculated volumetric mass transfer is different from the domain averaged calculated volumetric mass transfer coefficient. For example,
-for small capillary numbers, i.e. $Ca=0.097,0.254,0.526$ the predicted values are overpredicted
-($\volnondim=0.3,0.25,0.1$). When the velocity pattern is changed from having vortex in front of
+\label{results:periodic:inlet:outlet} The volumetric mass transfer coefficient
+was calculated using Eq. \ref{theor:one:concentration:time} with the
+characteristic concentration being the inlet/outlet flux averaged concentration
+as used by \citet{vanbaten-circular}. One can see in Fig.
+\ref{fig:volumetric:char:concentration:vanbaten} the calculated volumetric mass
+transfer is different from the domain averaged calculated volumetric mass
+transfer coefficient. For example, for small capillary numbers, i.e.
+$Ca=0.097,0.254,0.526$ the predicted values are overpredicted
+($\volnondim=0.3,0.25,0.1$). When the velocity pattern is changed from having
+vortex in front of
 the bubble to not having it,  i.e. $Ca=0.75,1.04$ the calculated values
@@
 \label{results:vanbaten}
-The van Baten formulation, Eq.
-\ref{eq:vanbaten:formulation}, is calculated as the change of mass in domain divided on the time difference.
-We examined two approaches:  the characteristic concentration to be as the average domain simulation and as the averaged flux input/output
-concentration. The latter case corresponds to the work \cite{vanbaten-circular}. The results are presented in Fig. \ref{fig:vanbaten} for $Ca=0.097$ and
-$Ca=1.04$. One can see that the
-inlet/outlet
-flux averaged concentration is shown to be inconsistent.
-The reason that \citet{vanbaten-circular} obtained the mass transfer coefficient close to the analytical estimation is that the liquid slug is well mixed that the averaged concentration is close to the inlet/outlet concentration.
+The van Baten formulation, Eq. \ref{eq:vanbaten:formulation}, is calculated as
+the change of mass in domain divided on the time difference. We examined two
+approaches:  the characteristic concentration to be as the average domain
+simulation and as the averaged flux input/output concentration. The latter case
+corresponds to the work \cite{vanbaten-circular}. The results are presented in
+Fig. \ref{fig:vanbaten} for $Ca=0.097$ and $Ca=1.04$. One can see that the
+inlet/outlet flux averaged concentration is shown to be inconsistent. The
+reason that \citet{vanbaten-circular} obtained the mass transfer coefficient
+close to the analytical estimation is that the liquid slug is well mixed that
+the averaged concentration is close to the inlet/outlet concentration.
 
@@
 %averaged concentration in the whole range of capillary numbers. 
-Note that for $Ca=0.097$ the
-obtained mass transfer coefficient value is a bit less than the value in Section \ref{main:results:periodic}. However, as
-it will be shown later the obtained volumetric mass transfer coefficient for $Ca=0.0097$ has the
-same value as for the simulations of a few unit cells.
-Therefore this approach produces most accurate results but requires the results in time and space to calculate the mass change in time and the averaged domain characteristic concentration.
+Note that for $Ca=0.097$ the obtained mass transfer coefficient value is a bit
+less than the value in Section \ref{main:results:periodic}. However, as it will
+be shown later the obtained volumetric mass transfer coefficient for
+$Ca=0.0097$ has the same value as for the simulations of a few unit cells.
+Therefore this approach produces most accurate results but requires the results
+in time and space to calculate the mass change in time and the averaged domain
+characteristic concentration.
 % only for velocity patterns related to larger
@@
 concentration based on \citeauthor{vanbaten-circular} formulation with the characteristic
-concentration being averaged domain concentration (see Section \ref{results:vanbaten}).
-That proves two things:  the domain averaged concentration is the only choice for the characteristic concentration, and periodic boundary conditions for one unit cell produce good results.
+concentration being averaged domain concentration (see Section
+\ref{results:vanbaten}). That proves two things:  the domain averaged
+concentration is the only choice for the characteristic concentration, and
+periodic boundary conditions for one unit cell produce good results.
 
@@
 %boundaries). 
-In comparison with periodic boundary conditions Eq.\ref{main:main:main} allows to calculate the mass transfer coefficient differently. Eq. \ref{main:main:main}  can be rewritten as:
-\beq
+In comparison with periodic boundary conditions Eq.\ref{main:main:main} allows
+to calculate the mass transfer coefficient differently. Eq.
+\ref{main:main:main}  can be rewritten as: \beq
 \label{main:main:main:thorough}
@@
 volumetric mass transfer cofficient is consistent for internal segments, i.e.
-$3-5$ unit cells numbers.
-The results for the volumetric mass transfer coefficient calculated by Eq.
-\ref{main:main:main} for a few unit cells  are close to results for periodic boundary
-conditions in Section \ref{main:results:periodic}. 
+$3-5$ unit cells numbers.  The results for the volumetric mass transfer
+coefficient calculated by Eq. \ref{main:main:main} for a few unit cells  are
+close to results for periodic boundary conditions in Section
+\ref{main:results:periodic}. 
 %However, they are even closer to results calculated by approach of \citeauthor{vanbaten-circular} with the domain averaged characteristic concentration. 
@@
 
-Though the calculation of the  volumetric mass transfer coefficient is harder using Eq.
-\ref{main:main:main:thorough}.
-However, it will be shown below that this equation can be significantly simplified in case of larger capillary numbers $Ca>0.7$.
+Though the calculation of the  volumetric mass transfer coefficient is harder
+using Eq. \ref{main:main:main:thorough}. However, it will be shown below that
+this equation can be significantly simplified in case of larger capillary
+numbers $Ca>0.7$.
 
@@
 require the knowledge of how the averaged concentration is changed in time.
-This approach is the file storage saving computational approach for the Bretherton/Taylor phenomenon flow with $Ca>0.7$ where there is no vortex in the liquid slug.
+This approach is the file storage saving computational approach for the
+Bretherton/Taylor phenomenon flow with $Ca>0.7$ where there is no vortex in the
+liquid slug.
 

### 2012-05-27 Text/introduction.tex
More style fixes (30%).

@@
 the bubble shape is asymmetric and cannot be approximated through flat surfaces and circumferences as
-is often done in literature \cite{vanbaten-circular,kreutzer-overview}.  When the vortex is present
+is often done in the literature \cite{vanbaten-circular,kreutzer-overview}.  When the vortex is present
 in the slug, the tracer is well mixed and it is common to use periodic boundary conditions and the inlet/outlet-averaged concentration
@@
 reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}.  These reactors usually operate in
- the Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow through
-a liquid medium of equally sized, long air bubbles, see
+ the Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow
+ of equally sized, long air bubbles through a liquid medium, see
 Fig. \ref{fig:benchmark:hydro}. This flow regime
-is characterized by surface tension dominance over inertia and viscous effects, and by
+is characterized by the dominance of surface tension over inertia and viscous effects, and by
 comparatively small gas flow velocities \cite{yue-mass}. Due to the dominance of surface tension, the bubble train flow exhibits advantageous
- properties which can not be achieved
+ properties which cannot be achieved
 in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
@@
 diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
-$\ububble$ is the bubble velocity, $D$ is the diffusion coefficient. 
+$\ububble$ is the bubble velocity, and $D$ is the diffusion coefficient. 
 %This correlation is within $10\%$ accuracy for experimental
@@
 
-Thus, the understanding of mass transfer for the bubble train flow is not possible without deep understanding of hydrodynamic patterns.
-There are several works studying the hydrodynamic properties of the bubble train flow: 
+The understanding of mass transfer for the bubble train flow is not possible without deep understanding of hydrodynamic patterns.
+There are several works studying the hydrodynamic properties of the bubble train flow, both
 experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
  For the flow of long bubbles between parallel plates chosen here as the study case it is indicated that  there exists a vortex 
-in the liquid slug for $Ca<0.7$ , see Fig. \ref{fig:streamlines:tweaked:velocity}, and that the bubble shape is symmetric for low capillary 
+in the liquid slug for $Ca<0.7$, see Fig. \ref{fig:streamlines:tweaked:velocity}, and that the bubble shape is symmetric for low capillary 
 numbers ($Ca<0.1$ \cite{cerro-bubble-train}).  In the case of flow between plates for $Ca<0.1\div0.7$ the bubble
@@
 
-Since mass transfer coefficient is defined in terms of a mass flux from a certain area, Eq. \ref{eq:main:definition},
+% TODO: move this later so that there is no forward reference to eq.4?
+Since the mass transfer coefficient is defined in terms of a mass flux from a certain area, Eq. \ref{eq:main:definition},
 analytical estimations \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble shape. The mass
@@
 hydrodynamic pattern in the slug (i.e. presence of a vortex in slug), one can
-estimate the time for a fluid batch to travel whole circumference.   However,
+estimate the time for a fluid batch to travel the whole circumference.   However,
 with the increase of the capillary number the situation drastically changes -- the
@@
 to estimate the contribution from bubble caps, which explains the need to turn to numerical simulations where all
-hydrodynamics fields and complicated bubble shapes are taken into account.
+hydrodynamics fields as well as complex bubble shapes are taken into account.
 
@@
 saturation concentration is imposed at the bubble surface. Only one unit cell
-with one bubble in it is used for simulations. Periodic boundary conditions are
+containing a single bubble is used for simulations. Periodic boundary conditions are
 utilized to determine the volumetric mass transfer coefficient, which is
@@
 simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass}
+% TODO: was good where?
 was good.  \end{description}
 
-The presented numerical approaches \cite{vanbaten-circular,kreutzer-overview}.
+The presented numerical approaches \cite{vanbaten-circular,kreutzer-overview}
 can be critized on a number of points. They mainly
@@
 the choice of the characteristic concentration needed for the mass transfer
-coefficient, Eq. \ref{eq:main:definition} is obvious. With small
-differences in results it can be either averaged in the liquid slug
+coefficient, Eq. \ref{eq:main:definition} is obvious. With minimal
+differences in the results, it can either be averaged in the liquid slug
 concentration or the outlet space-averaged concentration as used in the formulation
@@
 
-While it clear that periodic boundary conditions can be employed for the calculation
- of hydrodynamic fields, the same does not apply to the mass transfer coefficient.
+While it is clear that periodic boundary conditions can be employed for the calculation
+ of hydrodynamic fields, the same does not apply to the mass transfer coefficient
 simulations. Experimental correlations \cite{bercic-mass} show that the
@@
 Mass transfer simulations however, are made only for one unit cell
-using the periodic boundary conditions with the same concentration at the inlet
+using periodic boundary conditions with the same concentration at the inlet
 and at the outlet. The question how one unit cell simulation corresponds to
@@
 procedures as to how properly obtain the mass transfer coefficient via a study
-of different boundary conditions and different definitions of characteristic concentration
-The case we want to examine is a two-dimensionalbubble train flow between parallel plates.
+of different boundary conditions and different definitions of characteristic concentration.
+The case we want to examine is a two-dimensional bubble train flow between parallel plates.
 We address the following issues:
@@
 \end{description}
-In addition, at the end of the manuscript we present a comparison of dependence the volumetric
+In addition, at the end of the manuscript we present a comparison of the dependence of the volumetric
 mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations
@@
 function of other non-dimensional parameters such as gas holdup, bubble/slug
-lenghts, the capillary number is the goal of future work.
+lenghts, and the capillary number is the goal of future work.
 \begin{figure}[htb!]
@@
 \citet{jos-mass} simulating lateral mixing in cross-channel flow.  The last two
-works are focused on problems of homogeneous nature and do not provide
-guidance as how to obtain the mass transfer coefficient for non-homogenous cases.
+works focused on problems of homogeneous nature and do not provide
+guidance as to how to obtain the mass transfer coefficient for heterogeneous cases.
 
@@
 for the bubble train flow to derive expressions to connect the space- and time-averages.  Then, the lattice
-Boltzmann model used to simulate mass transfer is presented, and followed by benchmarks. Finally,
+Boltzmann model used to simulate mass transfer is presented and followed by benchmarks. Finally,
 numerical simulations of different boundary conditions and simulations spanning a few unit cells for
@@
 from the bubble. However, in the case of complicated geometries and non-homogeneous concentrations, 
-the medium concentration can be the average concentration in the domain or the flux averaged
+the medium concentration can be the average concentration in the domain or the flux-averaged
 concentration at the inlet or outlet, etc. Thus, one needs to establish a thorough definition of the volumetric
@@
 \subsection{Bubble train}
-In the application to the bubble train flow it is useful to think of one bubble to be a point
+In the application to the bubble train flow it is useful to think of one bubble as a point
 source to make all considerations above valid. For example, the expression
@@
 However, if one wants to analytically or numerically calculate the mass transfer coefficients, the
-situation is much more complicated because of the presence of two phases and complicated bubble
+situation is much more complicated because of the presence of two phases and complex bubble
 geometry. As was mentioned before, depending on the capillary
@@
 In comparison with analytical calculations and simplifications, the numerical approach can take into
-the account the complicated mixing patterns and geometries. However, there are challenges as to how to
+account the complex mixing patterns and geometries. However, there are challenges as to how to
 mimic the continuous picture like moving with bulk velocity $U=\ugas+\uliq$ reacting medium as seen in
@@
 Ideally one needs to mimic the continuous picture as it is seen in experiments.
-Thus, mass transfer simulations for a number of unit cells is needed. As it was
-indicated above there are two approaches towards it - either to simulate the
-bubble train and then to measure concentration along the pipe, Eq.
-\ref{main:mass:transfer:expression}, or to transfer to the reference frame moving with the bulk
-velocity $U$ and conduct same measurements. However, both methods do require a tracking of
+Thus, mass transfer simulations for a number of unit cells are needed. As was
+indicated above there are two approaches towards it -- either to simulate the
+bubble train and then to measure concentration along the pipe, Eq.~\ref{main:mass:transfer:expression},
+or to transfer to the reference frame moving with the bulk
+velocity $U$ and conduct same measurements. However, both methods require tracking of
 moving bubbles which is complicated from the numerical point of view. Therefore, one needs to come
-up with simple smaller domain calculations of the mass transfer coefficient, which mimic the
-continuous picture with infinite numbers of the bubbles closely.
+up with simple smaller domain calculations of the mass transfer coefficient, which mimics the
+continuous picture by an infinite number of closely separated bubbles.
 
@@
 approach is to simulate mass transfer in the reference frame moving with the bubble. Therefore, one
-needs to examine  Eq.
-\ref{main:mass:transfer:expression} more closely.
-
-We perform simulations in the frame moving with the bubble (velocity
-$\ububble$), that the bubble position stands steady. The bubble velocity $\ububble$ is
-different from the bulk velocity $U=\ugas+\uliq$. In this case one needs to perform a coordinate $x$
+needs to examine  Eq.~\ref{main:mass:transfer:expression} more closely.
+
+We perform simulations in the frame co-moving with the bubble
+in which the bubble position stays constant. The bubble velocity $\ububble$ is
+different from the bulk velocity $U=\ugas+\uliq$, and one thus needs to perform a $x$ coordinate
 variable change:
@@
 \feqal
-where $\langle C(t)\rangle$ is the characteristic concentration averaged in space, $\overline{C(x)}$ is averaged in time concentration at location $x$. 
+where $\langle C(t)\rangle$ is the space-averaged characteristic concentration,
+and $\overline{C(x)}$ is the time-averaged concentration at location $x$. 
 %The geometry is not one-dimensional and one needs the characteristic concentration
 %to be only as a function of time. 
-One can have different choices of
-$\langle C(t) \rangle$ as the averaged in whole domain concentration or inlet/outlet averaged in
-space concentrations used in works \cite{vanbaten-circular,kreutzer-overview}.  
+One can make different choices of
+$\langle C(t) \rangle$ such as the concentration averaged over the whole domain or inlet/outlet space-averaged
+concentrations used in works \cite{vanbaten-circular,kreutzer-overview}.  
 %Note that $C(x)$ is not averaged in time as $\overline{C(x)}$ since $C(x)$
 %ideally should not depend on time. 
-Therefore, one can obtain the volumetric mass transfer coefficient through the concentration averaged in space:
+The volumetric mass transfer coefficient can be obtained through the space-averaged concentration:
 \beqal
@@
 Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are
-cornerstones of the present work. The main questions arisen in the present work are to define the
-characteristic concentration $\langle C(t) \rangle$ and  boundary conditions to calculate a proper
-volumetric mass transfer coefficient
-$\vol$.
-
-Four possible scenarios of  numerical simulations are examined in this work: 
+cornerstones of the present work  Four possible scenarios of numerical simulations are examined: 
 \begin{enumerate}
@@
 cell is simulated with
-periodic boundary conditions, see Fig. \ref{fig:benchmark}. 
-Thus, no tracer leaves a
+periodic boundary conditions, see Fig. \ref{fig:benchmark} so that no tracer leaves the
 domain like for the plug flow. 
@@
 %cell, i.e. the outlet and the inlet concentrations are close. 
-Though easier to implement, it rises certain criticism
-about the inlet concentration to be equal to the outlet concentration. As it was discussed, in experiments there is the concentration difference between the inlet and
- the outlet.
+Though easier to implement, it rises certain criticisms
+about requiring the inlet concentration to be equal to the outlet one. As was
+discussed, in experiments there is a concentration difference between the
+inlet and the outlet.
 
@@
 \end{figure}
-\item The second approach is to apply periodic boundary conditions as in the first case but the characteristic concentration is taken as the inlet/outlet
+\item Periodic boundary conditions are applied as in the first case but the characteristic concentration is taken as the inlet/outlet
 concentration \cite{vanbaten-circular}:
@@
 \feqal
-Therefore, the assumptions  of this approach is
-that the difference between inlet and outlet is not
-considerably large and the tracer is well mixed in the slug. Thus, the inlet or outlet
-concentrations equal to the average concentration.
-
+The assumptions of this approach are
+that the difference between inlet and outlet is not significant (so that they can be taken to have average
+concentration) and that the tracer is well mixed in the slug.
 \item
-The approach of \citet{vanbaten-circular} is examined. Periodic boundary conditions were used. The work \cite{vanbaten-circular}
-calculates the mass transfer coefficient as the gain of the mass in the system
+The approach of \citet{vanbaten-circular}, where [eriodic boundary conditions are used and
+the mass transfer coefficient is calculated as the gain of the mass in the system
 divided by the concentration difference
-multiplied on the surface area:
+multiplied by the surface area:
 \beq
@@
 \feq
-where mass difference in the domain can be calculated as:
+where the mass difference in the domain can be calculated as:
 \beq
@@
 \item 
-The last approach to be examined in this paper is the simulation of a few unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
-bubble train head, after injecting to the pipe and travelling along the pipe. One can see that this
-situation corresponds most to the experimental picture. By simulation of a certain number of the
-bubble train head, the influence of the boundaries can be
+Simulation of a few unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
+bubble train head, after injection to the pipe and travelling along the pipe. One can see that this
+situation corresponds most closely to the experimental picture, but also requires larger computational
+resources. By simulating a certain number of the
+bubbles in the train head, the influence of the boundaries can be
 diminished. In this case, there is no ambiguity in the choice of the
@@
 by Eq.
-\ref{theor:continuous:mass:transfer}. This simulation statement is of most correspondence to
-experiments and should give right answer. However, one of the
-disadvantages is to simulate a certain number of unit cells ($1$ to $10$ in this case), thus
-increasing a computational
-burden.
-\begin{figure}[htb!]
+\ref{theor:continuous:mass:transfer}. \begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/benchmark_alot.eps}\\
-\caption{Benchmark for a lot of units. \label{fig:benchmark:alot}}
+\caption{Benchmark for multiple unit cells. \label{fig:benchmark:alot}}
 \end{figure}
@@
 
-One can notice that all examined cases are extreme cases of one equation:
+One can notice that all examined cases are the extreme limits of one equation:
 \beq
@@
 \feq
-where $\Delta C=\cstar-\langle C(t) \rangle$ with $\langle C(t) \rangle$ to be
-the average concentration in whole liquid domain, $\dot{m}$ is the mass gain in
+where $\Delta C=\cstar-\langle C(t) \rangle$ with $\langle C(t) \rangle$ taken to be
+the average concentration in the whole liquid domain, $\dot{m}$ is the mass gain in
 the domain,$\int{\cinlet u(0,y) \mathrm{d}y}$ and $\int{\coutlet
@@
 describes the mass balance: whatever was generated by the bubble surface equals
-to the mass domain change minus whatever left domain plus whatever entered
-domain.
+to the domain mass change minus whatever left the domain plus whatever entered it.
 
@@
 \feqstar
-Then the mass change in the domain is only because of the generating bubble
+Then the mass change in the domain arises only because of the bubble
 surface. However, to calculate the mass transfer coefficient one needs to have
-characteristic concentration  $\langle C(t) \rangle$ and mass gain $\dot{m}$
-which do require the storage of time and space information.
-
-Another limiting case (will be shown later) is hydrodynamic pattern change
+the characteristic concentration  $\langle C(t) \rangle$ and mass gain $\dot{m}$
+which do require the storage of both temporal and spatial information.
+
+Another limiting case (will be shown later) is the hydrodynamic pattern change
 $Ca>0.7$. The mass accumulation rate equals zero in this case, $\dot{m}=0$. One
@@
 \section{Validation}
-As it was discussed analytical correlations for the mass transfer coefficient
+As was discussed earlier, analytical correlations for the mass transfer coefficient
 are derived  as two separate contributions: the mass transfer from two
@@
 relaxation parameter. Collision operator, $-\omega \bigl(f_i- f_i^{eq}\bigr)$ is so-called BGK
-collision operator \cite{bgk}. However, the approach to be used here is the TRT
+collision operator \cite{bgk}. However, the approach used here is the TRT
 (two-relaxation-times) collision operator \cite{ginzburg-main,ginzburg-saturated-flow}. In
-comparison with the widely used BGK collision operator, TRT collision operator has better accuracy
-for diffusion and convection fluxes, and larger range of parameters where the LBM scheme is stable.
+comparison with the widely used BGK collision operator, the TRT collision operator has better accuracy
+for diffusion and convection fluxes, as well as a larger range of parameters where the LBM scheme is stable.
 
@@
 weights
-$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most spread set of weights, so called
+$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most spread set of weights, the so called
 ``hydrodynamic`` weights, was chosen:
@@
 We want to resolve the isotropic advection-diffusion equation, $D=D_{xx}=D_{yy}$ or
-$K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components to be zero $D_{xy}=0$. In
-comparison with the $D2Q5$ model, with the $D2Q9$ it is
+$K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components set to zero $D_{xy}=0$. In
+contrast to the $D2Q5$ model, with $D2Q9$ it is
 possible to cancel the numerical diffusion by the proper choice
@@
 \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
- Free relaxation parameter $\omegaplus$ can be found through $\Lambda$. For particular
-choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as
+For a particular choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as
  $\omegaplus=2-\omegaminus$.
@@
 pressure anti bounce-back boundary conditions \cite{ginzburg-multireflection}. However, the
-simulation results presented in this work are only pressure anti bounce-back due to its simplicity
-to handle any complicated type of boundary:
+simulation results presented in this work are only pressure anti bounce-back due to their ability
+to handle complex boundaries in a simple way:
 \beq
@@
 $i$ is the direction number pointing to the domain (unknown) located at the boundary surface $B$,
-$\bar{i}$ is the direction number opposite to $i$ and is located at the fluid $F$ specifically that
-$B$ is located at the location $F+\bm{c_i}$.
+$\bar{i}$ is the direction number opposite to $i$ and is located at the fluid node $F$ specifically
+so that node $B$ is located at the location $F+\bm{c_i}$.
 
@@
 \frac{C(r,t)-C_{0}}{C_{init}-C_{0}}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
-J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})},
+J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0\left(\mu_n \frac{r}{a}\right)},
 \feq
 where $\mu_n$ is the $n$-th zero root of the $0$th order Bessel polynomial $J_0(\mu_n)=0$. Some of
-the corresponding roots are as follows: $\mu_1=2.4048$,$\mu_2=5.5201$,$\mu_3=8.6537$,
-$\mu_4=11.7915$,$\mu_5=14.9309$.
+the corresponding roots are as follows: $\mu_1=2.4048$, $\mu_2=5.5201$, $\mu_3=8.6537$,
+$\mu_4=11.7915$, $\mu_5=14.9309$.
 By taking initial concentration to be $0$, one can obtain the following solution:
@@
 \subsection{Parabolic velocity profile with the velocity zero gradient at the wall}
-The problem is defined in terms of PDE as follows: 
+The problem is defined in terms of PDEs as follows: 
 \beq
@@
 velocity around $0.05-0.1$ to avoid computational burden. The number of steps for mass to cross whole domain is
-limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into the account the bulk
+limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into account the bulk
 velocity. If $\ububble$ is taken as $0.05$ then for

### 2012-05-28 Text/introduction.tex
Final fixes.

@@
 $\ububble$ in the lattice Boltzmann units as soon as the
-Peclet number is  matched in physical space and numerical simulations. This fact that $\ububble$
-can be chosen arbitrarily is extremely useful in the context of numerical simulations, since it can
-increase the time step, or decrease the computational demand by order of magnitude to obtain
-meaningful results. This point will be used in simulations and covered later.
-
+Peclet number is  matched in physical space and numerical simulations. The fact that $\ububble$
+can be chosen arbitrarily is extremely useful in the context of numerical simulations, since one can
+increase the time step and decrease the computational demand by an order of magnitude while still
+obtaining meaningful results. This point will be used in simulations and covered later.
+
+% TODO: I'm not sure I understand this sentence.  Does it say that we use the cap + film simplification
+% for the simulations, or that the simulation results are compared to results obtained via this simplification?
 Next section will cover LBM benchmarks that resemble the mass transfer problem from a bubble, as 
@@
 \subsection{The radial case}
-The case to be examined  is the mass transfer from the stair-case boundary forming a circle. It
-can be
-prescribed by the following system of equations:
+The case to be examined  is the mass transfer from a stair-case boundary forming a circle. It
+can be described by the following system of equations:
 \beq
@@
 \feq
-Fig. \ref{fig:parabolic:zero:gradient} shows the steady-state contours comparison between the
-analytical solution and the simulation with the anti bounce-back boundary conditions used to impose constant
+Fig. \ref{fig:parabolic:zero:gradient} shows a comparison of the steady-state contours between the
+analytical solution and the simulation with anti bounce-back boundary conditions used to impose constant
 concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The simulation grid is
@@
 \includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
-\caption{Concentration contour levels comparison between the analytical solution, Eq.
-\ref{analytical:solution:zero:gradient}, and simulation for the diffusion coefficient $D=0.0185$. Simulation was
+\caption{Comparison of the concentration contour levels between the analytical solution, Eq.
+\ref{analytical:solution:zero:gradient}, and simulation for the diffusion coefficient $D=0.0185$. The simulation was
 performed on the grid size of $80\times 1600$. The constant concentration is imposed with the
 anti bounce-back conditions, Eq. \ref{antibb}. Coordinate $x$ and $y$ are non-dimensionalized on
-the height of the channel. $\delta=H/2$ is the half of the channel height.
+the height of the channel. $\delta=H/2$ is half of the channel height.
 \label{fig:parabolic:zero:gradient}}
@@
 \ref{fig:parabolic:comparison}. Parameters were taken  same as in the previous case: the
-diffusion $D=0.0185$, the grid dimension is $80\times1600$. 
+diffusion coefficient is $D=0.0185$, the grid dimension is $80\times1600$. 
 \begin{figure}[htb!]
@@
 \caption{Comparison between the analytical concentration contours and simulations with pressure
-anti bounce-back conditions, Eq. \ref{antibb}. The parameters were
-taken as $D=0.0185$ and grid $80\times1600$. \label{fig:parabolic:comparison}}
+anti bounce-back conditions, Eq. \ref{antibb}. The simulation was done for $D=0.0185$ with a
+$80\times1600$ grid. \label{fig:parabolic:comparison}}
 \end{figure}
@@
 \cite{kuzmin-d1q3}. On the other hand, one iteration in the lattice Boltzmann system corresponds
-to the time step in the physical domain  $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
-x}{U_{\mathrm{bubble,phys}}}$. One iteration time is proportional to the velocity $U_{\mathrm{LB}}$
+to the physical time step  $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
+x}{U_{\mathrm{bubble,phys}}}$. The iteration time is proportional to the velocity $U_{\mathrm{LB}}$
 and the typical number of simulation steps to obtain the steady-state mass transfer coefficient for
 $Ca<0.2$ is of the order of a few millions. Therefore, it is desirable to increase  velocity  $U_{\mathrm{LB}}$
-while keeping the Peclet number the same. If one increases velocity, then
-$\omegaminus$ increases as well. Thus, the increase of the velocity impacts
-positively on stability of the LBM as $\omegaminus$ is not close to its
-stability limit $0.5$.
-
-Given all the considerations above, mass transfer simulations are performed as:
+while keeping the Peclet number the same. If one increases the velocity, then
+$\omegaminus$ increases as well, moving away from the stability limit $0.5$ and therefore
+stabilizing the simulation.
+
+Given all the considerations above, mass transfer simulations are performed as follows:
 \begin{description}
@@
 taken to ensure grid
-independency of results \cite{kuzmin-binary2d}. Note that we do not approximate bubble shapes by correlations, but we directly resolve them by using the multiphase solver. 
+independency of the results \cite{kuzmin-binary2d}. Note that we do not approximate bubble shapes by correlations, but we directly resolve them by using the multiphase solver. 
  \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
-are conducted in the reference frame moving with the bubble. Then the bubble stands still and the
+are conducted in the reference frame moving with the bubble, where the bubble stands still and the
 flow is happening around the
@@
  \item[Velocity improvement] One can scale the velocity to
-perform faster simulations. However, before doing it one needs to improve velocity. This issue arises because of the
-multiphase model used in simulations. The binary liquid lattice Boltzmann model is the diffusive
-interface model. Thus, the
-transition between gas and liquid is the continuous function. We obtain the bubble shape according
-to the phase indicator $\phi$ as used in \cite{kuzmin-binary2d}, say $\phi\leq0$. The velocity of the
+perform faster simulations. However, before doing it one needs to improve the velocity field.
+This issue arises because of the
+multiphase model used in simulations. The binary liquid lattice Boltzmann model is a diffusive
+interface model where no clear boundary between gas and liquid exists.
+% TODO: Is this only a problem of how we determine the bubble shape or also a problem of
+% spurious velocities within the model itself?
+We obtain the bubble shape by imposing a condition on the order parameter field $\phi$ as in \cite{kuzmin-binary2d}, say $\phi\leq0$. The velocity of the
 bubble is calculated as the bubble tip velocity. Because of the square grid the shape of the bubble is determined within accuracy of one grid node. Thus,
-there is the error in determination of the bubble velocity. Though these errors are small, however
-there is a small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
-\cite{kuzmin-binary2d} where some streamlines are penetrating a bubble surface a bit.
+there is the error in determination of the bubble velocity. Though these errors are small,
+there is still a small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
+\cite{kuzmin-binary2d} where some streamlines are penetrating the bubble surface a bit.
 This small velocity is amplified upon the velocity scaling and is inconsistent with the
@@
 simulation is performed. An additional free-surface solver was developed in order to obtain velocity field
-consistency with the advection-diffusion equation. We take results from the
+consistent with the advection-diffusion equation. We take results from the
 multiphase simulations, extract a
-bubble shape using the phase indicator $\phi\leq0$, approximate the bubble shape by the stair-case
-line. Then, the obtained bubble velocity is imposed on walls. This corresponds to conducting
+bubble shape using the phase indicator $\phi\leq0$, and approximate the bubble shape by the stair-case
+line. The obtained bubble velocity is then imposed on the walls. This corresponds to conducting the
 simulation in the reference frame moving with the bubble. In addition, the free-slip boundary
 condition on the bubble surface is imposed. Appendix \ref{appendix-free-surface} covers the simple
-free-slip boundary conditions implementation drastically improving velocity patterns. The system is
+free-slip boundary condition implementation drastically improving velocity patterns. The system is
 iterated until a
@@
 bubble surface are completely eliminated. We compared original multiphase simulations with
-one-component free-slip simulations. All quantities as superficial slug and liquid velocities are
-within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. This simulation helps to
-make mass transfer simulations stable and faster.%, since the velocity scaling can be done easier and
-%streamlines are non-penetrating through the interface. 
-One
-can see in Fig. \ref{fig:free:surface} two streamlines profiles for $Ca=0.097$  and $Ca=1.040$.
+one-component free-slip simulations. All quantities such as superficial slug and liquid velocities are
+within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. 
+One can see in Fig. \ref{fig:free:surface} two streamline profiles for $Ca=0.097$  and $Ca=1.040$.
 \begin{figure}[htb!]
@@
 many
-cells simulations for two representative cases velocity patterns, as $Ca=0.0907$ and $Ca=1.04$
+cell simulations for two representative cases of velocity patterns, $Ca=0.0907$ and $Ca=1.04$
 (see Fig. \ref{fig:streamlines:tweaked:velocity}).
 
-\subsection{Keeping the Peclet number}
+\subsection{Keeping the Peclet number constant}
 \label{section:keeping:peclet}
-This section addresses the simulations performance. The ultimate goal is to increase
-velocity magnitude significantly while keeping dimensionless parameters the same to
+This section addresses the process of significantly increasing the
+velocity magnitude while keeping dimensionless parameters the same to
 speed up                                      
-simulations. This is especially important to be able to simulate a few unit cells simulations. For example, ten unit cells simulations require a grid of $30000\times202$ nodes.
+simulations. This is especially important to be able to simulate a few unit cells in a reasonable time.
+For example, ten unit cell simulations require a grid of $30000\times202$ nodes.
 %Increasing velocity can also help to resolve a lot of unit cells to represent a
 %continous picture.
-As it was discussed above, only the Peclet number governs 
-the advection-diffusion equation. In the lattice Boltzmann system it is represented as:
+Since the Peclet number is the only dimensionless quantity governing
+the advection-diffusion equation:
 \beq
@@
 \feq
-As far as we want to increase velocity, one needs to increase the diffusion coefficient as well. The runs were made with
+one needs to increase the diffusion coefficient when the velocity is increased. Simulation runs were made with
 velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities and
-its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
+their corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
 boundary conditions were used and mass transfer coefficient was calculated according to Eq.
@@
 \end{tabularx}
-\caption{This table presents the achievable stable velocity $\ububble$ when one scales velocity. One
-iteration in the lattice
-Boltzmann system corresponds to time difference as
-$\Delta t=\frac{U_{\mathrm{bubble,LB}}}{U_{\mathrm{bubble,phys}}} \Delta x$. Therefore the speed up
-of the simulation is proportional to the  $U_{\mathrm{bubble,LB}}$. Note that time
-iterations
-indicated in the table correspond to the one time moment in the physical space. One can see that
-scaling produces adequate results.  The achievable stable velocity is around $U_{bubble}=0.1$. Average concentrations are in the reasonable agreement. The contour
+\caption{This table presents the achievable stable velocity $\ububble$ when one scales velocity. Since
+the physical time step represented by a single iteration of the simulation is directly proportional
+$U_{\mathrm{bubble,LB}}$, scaling the velocity directly translates to an effective speed-up of the simulation.
+Note that time iterations
+indicated in the table correspond to physical time. One can see that
+scaling produces adequate results.  The achievable stable velocity is around $U_{bubble}=0.1$. Average concentrations are in reasonable agreement. The contour
 profiles for all of these cases (capillary number $Ca$ and all scales) are presented in Fig.
@@
 \end{table}
-The corresponding to Table \ref{table:scaling:peclet} concentration contour profiles for different
+The concentration contour profiles corresponding to Table \ref{table:scaling:peclet} for different
 velocity scalings are presented in Fig. \ref{fig:contours:scaling:peclet}. One can see an
-acceptable agreement between all of them. Note, that the speedup can be upto $10$ to $40$ times
-faster.
+acceptable agreement between all of them. Note, that the speedup can be up to $10$ to $40$ times
+higher.
 \begin{figure}[htb!]
@@
 \ref{fig:aver:conc:different:capillaries} shows the volumetric mass transfer
-dependency against the distance in unit cells length. One can see in Table
+dependency against the distance in unit cell length. One can see in Table
 \ref{table:steady:state:average} that for different Peclet numbers different time (number of unit
 cells) is required to achieve the steady state. For example, for
-larger Peclet number less number of iterations are required to achieve the steady state condition.
+larger Peclet numbers fewer iterations are required to achieve the steady state condition.
 
@@
 \item[I] Scaling is performed as $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
-\item[II] The larger Peclet number the less number of iterations is required. One can extrapolate data from Table
+\item[II] The larger the Peclet number, the fewer iterations are required. One can extrapolate data from Table
 \ref{table:steady:state:average}, say $L_{\mathrm{steady}}$ and estimate the  number of
@@
 concentration being close to $\cstar$. All of them show an excellent agreement. Note, that with the
-scaling one can reduce the amount of calculations drastically. However, one needs to be attentive
-because with the large velocity scaling average concentration can quickly approach $\cstar$, thus
+velocity scaling one can reduce the amount of calculations drastically. However, one needs to be attentive
+because with large velocity scaling average concentration can quickly approach $\cstar$, thus
 getting an infinite volumetric mass transfer coefficient.
@@
 \caption{Volumetric mass transfer coefficient for different capillaries and scales against the
-bubble traveling distance in the laboratory frame. ''Cell Units`` axis is refered to the physical
+bubble travel distance in the laboratory frame. ''Cell Units`` axis refers to the physical
 distance of how many unit cells the bubble passes until the steady state is reached. Table
@@
 ($\volnondim=0.3,0.25,0.1$). When the velocity pattern is changed from having
-vortex in front of
+a vortex in front of
 the bubble to not having it,  i.e. $Ca=0.75,1.04$ the calculated values
-are underpredicted than in the previous case, i.e. $\volnondim=0.06,0.04$. As we will see later the domain averaged characteristic concentration produces proper results. 
+are underpredicted in contrast to the previous case, i.e. $\volnondim=0.06,0.04$. As we will see later, the domain-averaged characteristic concentration produces proper results. 
 \begin{figure}[htb!]
@@
 the inlet/outlet flux averaged concentration as
-in \cite{vanbaten-circular}. One can see that values are either overpredicted or underpredicted
-than values specified in Table \ref{table:steady:state:average} depending on the velocity pattern. 
+in \cite{vanbaten-circular}. One can see that depending on the velocity pattern,
+ the values are either overpredicted or underpredicted
+in comparison to values specified in Table \ref{table:steady:state:average} 
 \label{fig:volumetric:char:concentration:vanbaten}}
@@
 The van Baten formulation, Eq. \ref{eq:vanbaten:formulation}, is calculated as
-the change of mass in domain divided on the time difference. We examined two
-approaches:  the characteristic concentration to be as the average domain
-simulation and as the averaged flux input/output concentration. The latter case
+the change of mass in domain divided by the time difference. We examined two
+approaches:  the characteristic concentration taken to be as the domain average
+and as the flux-averaged input/output concentration. The latter case
 corresponds to the work \cite{vanbaten-circular}. The results are presented in
@@
 reason that \citet{vanbaten-circular} obtained the mass transfer coefficient
-close to the analytical estimation is that the liquid slug is well mixed that
+close to the analytical estimation is that the liquid slug is well mixed so that
 the averaged concentration is close to the inlet/outlet concentration.
 
-However, results for the domain averaged concentration using the approach of \citeauthor{vanbaten-circular} is close to simulation results in Section
+However, results for the domain-averaged concentration using the approach of \citeauthor{vanbaten-circular} are close to simulation results in Section
 \ref{main:results:periodic}. %for the volumetric mass transfer coefficient measured with the domain
@@
 Note that for $Ca=0.097$ the obtained mass transfer coefficient value is a bit
-less than the value in Section \ref{main:results:periodic}. However, as it will
+lower than the value in Section \ref{main:results:periodic}. However, as will
 be shown later the obtained volumetric mass transfer coefficient for
@@
 \caption{The \citet{vanbaten-circular} formulations for $Ca=0.097$ (top) and
-$Ca=1.04$ (bottom) with the characteristic concentration being domain
-averaged (left) and inlet/outlet flux averaged concentration (right). One can
-see that \citet{vanbaten-circular} formulation produces good results with the characteristic concentration being
-the average concentration. Moreover, the values are more close to values obtained with many cells
+$Ca=1.04$ (bottom) with the characteristic concentration being domain-averaged (left)
+ and inlet/outlet flux-averaged (right). One can
+see that the \citet{vanbaten-circular} formulation produces good results with the characteristic concentration being
+the average concentration. Moreover, the values are closer to values obtained with many cell
 simulations, see Fig. \ref{fig:moving:average:ca0097}, than in comparison with periodic boundary
 simulations in Section \ref{main:results:periodic}. However, the characteristic concentration
-being inlet/outlet flux averaged concentration does not produce consistent results as in Section
+being inlet/outlet flux-averaged does not produce consistent results as in Section
 \ref{results:periodic:inlet:outlet}.
@@
 
-\subsection{Performing a number of cell units simulations}
-A few unit cells simulations naturally resemble the real experiments picture.  The idea here is
-that if one have enough number of unit cells then results of internal unit cells should be
-independent of boundaries and correspond to experiments. A few unit cells simulations physically
-correspond to the simulation of bubble train head. If boundaries are eliminated then the average
-domain characteristic should be changed in time according to Eq.
-\ref{theor:continuous:mass:transfer}. It means that there is no ambiguity to choose the
-characteristic concentration. The characteristic concentration is the averaged domain concentration
-as it is seen in experiments.
-
-This section studies a number of the unit cells required for the volumetric
+\subsection{Simulations for several unit cells}
+In order to achieve independence from the boundary conditions and a closer match with
+the physical system being modeled, one can simulate several unit cells, corresponding
+to a bubble train head.  If boundaries are eliminated then the average
+domain characteristic should change in time according to Eq.
+\ref{theor:continuous:mass:transfer}. This eliminates the ambiguity inherent in choosing a definition
+of the characteristic concentration, which now becomes the same domain-averaged concentration
+as the one measured in experiments.
+
+This section studies the number of unit cells required for the volumetric
 mass transfer coefficient to be independent of boundaries. We chose two
@@
 velocity patterns (see Fig. \ref{fig:streamlines:tweaked:velocity} for $Ca=0.097$ and $Ca=1.04$) to
-perform a few number of cells simulations. For $Ca=0.097$ we performed simulations with
-$4$,$6$,$8$,$10$ number of cells, for $Ca=1.040$ only $4$,$6$,$8$ unit cells simulations.
-However,
-simulations with $10$ unit cells domain length produce the same results as $8$ unit cells.
-Thus, it won't be covered here, especially as it requires extensive computational resources (grid is
-$30000\times 202$ nodes).
-
-As it was discussed in the previous section we want to keep
-velocity around $0.05-0.1$ to avoid computational burden. The number of steps for mass to cross whole domain is
+perform the simulations. For $Ca=0.097$ we performed simulations with
+$4$, $6$, $8$, $10$ cells, and for $Ca=1.040$ only with $4$, $6$, $8$ cells.
+The final run for 10 cells was skipped due to limited computational resources.
+% TODO: how do we know that this holds true regardless of the Ca number?
+We observed however that simulations with a domain length of $10$ unit cells produce the same results as those with $8$ unit cells.
+
+We keep velocity in the range $0.05-0.1$ to avoid excessively long simulation times.
+The number of steps for mass to cross the whole domain is
 limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into account the bulk
 velocity. If $\ububble$ is taken as $0.05$ then for
-the domain size $\lunit=3000$ one can obtain the following number of iteration for mass transfer to
-cross the unit cell $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ time iterations are enough
-for system consisting of $10$ cell units. For more accurate estimations of number of time
-iterations depending
-on the Peclet number one can refer to Section \ref{section:keeping:peclet}.
+the domain size $\lunit=3000$ one can obtain the following number of iterations for the mass to
+cross the unit cell $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ iterations are enough
+for a system consisting of $10$ unit cells. For more accurate estimations of number of time
+iterations depending on the Peclet number one can refer to Section \ref{section:keeping:peclet}.
 
 \subsection{$Ca=0.097$ results}
-There are two characteristics we want to track for a few unit cells simulations: the average
+There are two characteristics we want to track in the simulations: the average
 concentration in
@@
 rate in the domain adjusted with inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
-resembles the experimental picture: if one have enough unit cells then the averaged domain
+resembles the experimental picture: if one has enough unit cells, then the averaged domain
 concentration should change in time according to Eq. \ref{theor:continuous:mass:transfer}: 
@@
 The non-dimensional volumetric mass transfer coefficient calculated based on Eq.
-\ref{moving:average} (averaged domain concentration changes in times) is
+\ref{moving:average} (domain-averaged concentration changes in time) is
 represented in Fig. \ref{fig:moving:average:ca0097} for different unit cells. One can see that the
@@
 concentration based on \citeauthor{vanbaten-circular} formulation with the characteristic
-concentration being averaged domain concentration (see Section
-\ref{results:vanbaten}). That proves two things:  the domain averaged
+concentration being domain-averaged concentration (see Section
+\ref{results:vanbaten}). This proves two things:  the domain-averaged
 concentration is the only choice for the characteristic concentration, and
@@
 %boundaries). 
-In comparison with periodic boundary conditions Eq.\ref{main:main:main} allows
+In comparison with periodic boundary conditions Eq.~\ref{main:main:main} allows
 to calculate the mass transfer coefficient differently. Eq.
@@
 \feq
-where $t^*$ is medium time between $t_1$ and $t_2$.
+where $t^*$ is the medium time between $t_1$ and $t_2$.
+%TODO: what is a medium time?  is it just the mean of the two times?
+
 %The
@@
 %see whether the liquid slug is mixed. 
-Fig. \ref{fig:unit:6} shows average concentrations in different units and $\volnondim$ based on Eq.
-\ref{main:main:main:thorough} calculated for each unit for velocity
+Fig.~\ref{fig:unit:6} shows average concentrations in different units and $\volnondim$ based on
+Eq.~\ref{main:main:main:thorough} calculated for each unit for velocity
 scale $10$ and  $6$ unit cells (all velocity scales produce same results). It is shown that the
 volumetric mass transfer cofficient is consistent for internal segments, i.e.
-$3-5$ unit cells numbers.  The results for the volumetric mass transfer
-coefficient calculated by Eq. \ref{main:main:main} for a few unit cells  are
+unit cells $3-5$.  The results for the volumetric mass transfer
+coefficient calculated by Eq. \ref{main:main:main} for a multiple unit cells are
 close to results for periodic boundary conditions in Section
@@
 can be found for
-$8$ and $10$ unit cells simulations but we do not present them here. As well we do not present $4$
+$8$ and $10$ unit cells simulations but we do not present them here. We also do not present $4$
 units cells simulation results which are influenced by inlet and outlet boundaries.
 
-Though the calculation of the  volumetric mass transfer coefficient is harder
+The calculation of the  volumetric mass transfer coefficient is more difficult
 using Eq. \ref{main:main:main:thorough}. However, it will be shown below that
@@
 %\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
-\caption{Average concentrations (left) and volumetric coefficients (right) for $6$ units cells. The
+\caption{Average concentrations (left) and volumetric coefficients (right) for $6$ unit cells. The
 volumetric
@@
 \caption{The non-dimensional volumetric mass transfer coefficient defined in Eq.
-\ref{moving:average} for $4$ (top left),$6$ (top right),$8$ cell units (bottom). Only scale
+\ref{moving:average} for $4$ (top left), $6$ (top right), $8$ unit cells (bottom). Only scale
 $10$ is presented since all other simulations produce the same results. One can see that $4$ unit
@@
 unit cells are consistent and show that beginning from third unit cell the results and ending with
-prelast cell results are consistent with periodic boundary simulations and
+the penultimate cell results are consistent with periodic boundary simulations and
 \citet{vanbaten-circular} formulations.
@@
 \subsection{$Ca=1.040$ results}
-The same correlations were examined for the different velocity pattern $Ca=1.040$.%, initial
+The same correlations were examined for a different velocity pattern $Ca=1.040$.%, initial
 %velocity $\ububble=0.055$, initial diffusion $D=0.0008375$. If only velocity scaling is
@@
 %this capillary number  are unstable.
-A few unit cells simulations with the original Peclet number $Pe=14041$.To improve stability we changed the original Peclet number by
-increasing
+
+%TODO: I'm not sure what this sentence means here on its own..
+A few unit cells simulations with the original Peclet number $Pe=14041$.
+To improve stability we changed the original Peclet number by increasing
 diffusion to $Pe=2644$. The results for unit cells are the same as for $Ca=0.097$:
 at least $6$ unit cells are required to be simulated to avoid the influence of boundaries. Thus,
-only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040} which shows only the
-average concentration for each unit cell. One can see that the average volume concentration for each unit cell come to
-constant values and are not increasing with time. Thus, all the
-mass generated with medium is transferred through the boundaries. This is the indication that the
-liquid slug is not mixed. Note that the periodic boundary conditions can not show whether the
+only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040} which shows the
+average concentration for each unit cell. One can see that the average volume concentration for each unit cell comes to
+a constant value and is not increasing with time. Thus, all the
+mass generated with medium is transferred through the boundaries. This indicates that the
+liquid slug is unmixed. Note that the periodic boundary conditions cannot show whether the
 liquid slug is mixed or not due to the fact that the averaged domain concentration always increases in time. 
-Thus, the volumetric mass transfer coefficient $\volnondim$ can be calculated according to the
+Thus, the volumetric mass tranun coefficient $\volnondim$ can be calculated according to the
 definition, Eq. \ref{main:main:main}:
@@
 \feq 
-where $V$ is the unit cell volume. There is no accumulated mass in the domain. Thus, $\dot{m}=0$. As periodic boundary
-conditions this case is another extreme limit of Eq. \ref{main:main:main}. Note that to calculate
+where $V$ is the unit cell volume. There is no accumulated mass in the domain, so $\dot{m}=0$. Like periodic boundary
+conditions, this case is another extreme limit of Eq. \ref{main:main:main}. Note that to calculate
 the volumetric mass transfer coefficient one needs only the spatial information and does not
-require the knowledge of how the averaged concentration is changed in time.
-This approach is the file storage saving computational approach for the
-Bretherton/Taylor phenomenon flow with $Ca>0.7$ where there is no vortex in the
+require the knowledge of how the averaged concentration changes in time, which significantly
+lowers storage requirements for the simulations with $Ca>0.7$ where there is no vortex in the
 liquid slug.
@@
 the calculated volumetric mass transfer coefficient using the time averaged approach and periodic
-boundaries one unit cells simulations presented in the same figure for comparison reasons. 
+boundaries one unit cell simulations presented in the same figure for comparison.
 \begin{figure}[htb!]
@@
 \caption{Results for $6$ unit cells. The Peclet number equals to $Pe=2644$.
-One can see that average concentrations reach certain number and stay.
+One can see that average concentrations reach certain value and stay constant.
 That means whatever was
 generated by medium is transferred through the outlet
-boundary. This is the indication that the tracer in the slug is not
+boundary. This indicates that the tracer in the slug is not
 mixed and the volumetric mass transfer coefficient, $\volnondim$, can be
@@
 Note
-that all approaches coincide. Therefore, for certain hydrodynamic patterns ($Ca>0.7$) one can easily convert time
-domain to the spatial domain calculations.
+that all approaches coincide and therefore, for certain hydrodynamic patterns ($Ca>0.7$), one can
+easily convert time domain to spatial domain calculations.
 \begin{figure}
@@
 \caption{The periodic (top left, $1$ unit cell, Eq. \ref{theor:continuous:mass:transfer}), unit
-cells averaged domain concentrations in time (top right, $6$ unit cells, Eq.
+cells domain-averaged concentrations as a function of time (top right, $6$ unit cells, Eq.
 \ref{theor:continuous:mass:transfer}), and spatial location
@@
 transfer
-coefficients. One can see that they all coincide. However, the periodic boundary conditions based
-calculations produce a bit overestimated volumetric mass transfer
-coefficient. As well one can see that the averaged domain concentration simulations (top right)
-reach the steady volumetric concentrations fast and after that start decaying. It is not convenient
-to use them in practical cases for not mixed slug, i.e. $Ca>0.7$. \label{fig:periodic:ca1040}}
-\end{figure}
-
-\subsection{Experiment and Analytical correlations comparison}
-The goal of this paper is not to compare simulation results with the experiment correlations, but give the
-procedure to perform numerical simulations  in the lattice Boltzmann framework. However, the
-small comparison is performed.
-Unfortunately the experiments to the best authors' knowledge measuring the mass flux for  bubbles flowing between parallel plates are absent. However, one of interesting
-correlations for the mass transfer volumetric coefficient was presented by
+coefficients. One can see that they all coincide. However, the calculations based on periodic boundary conditions
+produce a slightly overestimated volumetric mass transfer
+coefficient. One can as well see that the domain-averaged concentration simulations (top right)
+reach the steady volumetric concentration fast and start decaying after that. It is not convenient
+to use them in practical cases for unmixed slug, i.e. $Ca>0.7$. \label{fig:periodic:ca1040}}
+\end{figure}
+
+\subsection{Comparison of experimental and analytical correlations}
+While the goal of this paper is not to compare simulation results with the experimental measurements, but to give the
+procedure to perform numerical simulations  in the lattice Boltzmann framework, we felt that a
+short note about such comparison will be beneficial.
+Unfortunately, to the best authors' knowledge, there are no reported experimental results measuring the mass flux for
+  bubbles flowing between parallel plates. However, an interesting
+correlation for the mass transfer volumetric coefficient was presented by
 \citet{yue-mass} for three-dimensional microchannel geometries:
@@
 One can see that approximately the volumetric mass transfer correlation should be proportional to
-$Pe^{-0.5}$. As well one can use analytical estimations for the volumetric mass transfer
-coefficient calculated using the Higbie penetration theory \cite{higbie}. One can derive by following works
+$Pe^{-0.5}$.  One can also use analytical estimates of the volumetric mass transfer
+coefficient calculated using the Higbie penetration theory \cite{higbie}. One can derive by following the works
 \cite{irandoust,vanbaten-circular} that the analytical expression for the flow between plates has
@@
 \feq
-where $H$ is the channel height, $\delta$ is the film thickness.
-
-Fig. \ref{fig:volume:mass:coefficient} shows a comparison between correlation by
-\citet{yue-mass}, analytical expression, Eq. \ref{vanbaten:analytical:expresssion}, and the current
+where $H$ is the channel height, and $\delta$ is the film thickness.
+
+Fig. \ref{fig:volume:mass:coefficient} shows a comparison between a correlation by
+\citet{yue-mass}, the analytical expression, Eq. \ref{vanbaten:analytical:expresssion}, and the current
 simulation coefficients presented in Table
@@
 on periodic boundary conditions. The fitting curve is proportional to $Pe^{-0.5}$ which corresponds
-to all correlations. As well one can see that the deviation from the analytical expression becomes
-larger with the Peclet number increasing $Pe$. It is because the analytical expression does not account for the velocity pattern and a bubble
-shape change.\label{fig:volume:mass:coefficient}}
+to all correlations. One can as well see that the deviation from the analytical expression becomes
+larger with the increasing Peclet number $Pe$, which happens because the analytical expression does
+ not account for the velocity pattern and the bubble shape change.\label{fig:volume:mass:coefficient}}
 \end{figure}
@@
 taken in different times, Eq. \ref{theor:continuous:mass:transfer}. Eq.
-\ref{theor:average:concentration:time} gives a bit overestimated volumetric mass transfer
+\ref{theor:average:concentration:time} gives a slightly overestimated volumetric mass transfer
 coefficient. The original formulation of
 \citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
-to be characteristic concentration. A few unit cells simulations are harder to perform, but they
-have indicator of how well the liquid slug is mixed. As well, for velocity patterns of $Ca\geq
+to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
+have indicator of how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
 0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
-coefficient only based on the spatial location, not time snapshots of domain concentration values used in all other
+coefficient based on the spatial location only, without requiring the time snapshots of domain concentration values used in all other
 approaches. Finally, a sample of results was
-compared with the experimental correlation of \citet{yue-mass} and shows a good agreement. 
+compared with the experimental correlation of \citet{yue-mass} and shown to be in good agreement. 
 \appendix
@@
 Still Eq. \ref{diffusion:zero:gradient:middle} cannot be solved with the separation of variables as it requires homogenous
-boundary conditions. Thus, let us introduce the new variable, $\Theta=C-\cstar$, which makes the system to be with homogenous boundary conditions:
+boundary conditions. Thus, let us introduce the new variable, $\Theta=C-\cstar$, which makes the system have homogenous boundary conditions:
 \beq
@@
 \feq 
-This equation can be solved by separation of variables if the solutions is represented as the
-multiplication of two functions $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$:
+This equation can be solved by separation of variables if the solutions are assumed to factorize as
+$\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$:
 \beq
@@
 The left and right parts depend on different variables. Therefore to be equal to each other both
-parts shall equal to constant, say $-m^4$. Thus, the separation of the variables leads to two ODEs:
+parts shall equal to a constant, say $-m^4$. The separation of variables leads to two ODEs:
 \begin{equation*}
@@
 \label{appendix:poiseuille}
-Close to the previous example but with a different velocity profile, the benchmark can be
+Close to the previous example but with a different velocity profile, the problem can be
 formulated through the following PDE:
@@
 \feq 
-Taking symmetry conditions in the consideration by leaving only even solution, Eq.
-\ref{fourier:separation:variables:parabolic} has a solution as:
+Taking symmetry conditions into consideration by leaving only the even solution, Eq.
+\ref{fourier:separation:variables:parabolic} has the following solution:
 \beq
@@
 \feq
-To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
+To satisfy the boundary condition we need to find zeros of the hypergeometric function, i.e.
 ${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
-found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
+found using numerical methods: $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
 $5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
@@
 One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)$ and through orthoganality (Stourm-Liouiville theorem) obtain coefficients:
+x^2\Bigr)$ and through orthogonality (Stourm-Liouiville theorem) obtain coefficients:
 \beq
@@
 \feq
-Therefore a whole solution can be written as:
+Therefore the complete solution can be written as:
 \begin{equation}
@@
 where coefficients $C_m$ are taken from Eq. \ref{coeff:series:parabolic:profile}. For the case
-$\cstar$, first ten coefficients equal to  $1.2008$, $-0.2991$, $0.1608$, $-0.1074$, $0.0796$,
+$\cstar$, the first ten coefficients are: $1.2008$, $-0.2991$, $0.1608$, $-0.1074$, $0.0796$,
 $-0.0627$, $0.0515$, $-0.0435$, $0.0375$, $-0.0329$.
@@
 complicated surface of the bubble. The reason is to impose the symmetric boundary conditions.
-Because the boundary is the staircase approximation, one can find the normal to the boundary which
+Because the boundary is a staircase approximation, one can find the normal to the boundary which
 is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}. This
-can be done automatically by the` simple coding. Imposing the
+can be done automatically by the simple coding. Imposing the
 symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
@@
 
+% TOOD: for completeness, this picture shoudl probably include other fluid nodes as well?
 \begin{figure}
 \includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
-\caption{Free-surface boundary condition represented in the lattice Boltzmann. By crosses we outline
-boundary nodes, by circle the fluid node is outlined. Populations at the corner boundary nodes are
-essentially the population of the fluid node, but in the certain order. \label{fig:free:surface}}
+\caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
+Boundary nodes are depicted by crosses, and fluid nodes are represented by circles.
+The populations at the corner boundary nodes are 
+essentially the populations of the fluid node, but in a different order. \label{fig:free:surface}}
 \end{figure}

### 2012-07-16 Text/introduction.tex
Almost final corrections.

@@
 \newcommand{\uoutlet}{U_{\mathrm{outlet}}}
+\newcommand{\uinoutlet}{U_{\mathrm{in/outlet}}}
 \newcommand{\cbubble}{C_{\mathrm{bubble}}}
@@
 \newcommand{\coutlet}{C_{\mathrm{outlet}}}
+\newcommand{\cinoutlet}{C_{\mathrm{in/outlet}}}
 \newcommand{\coverall}{C_{\mathrm{overall}}}
@@
 
-\title{Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow}
+\title{Lattice Boltzmann study of mass transfer for two-dimensional Bretherton/Taylor bubble train flow}
 
@@
 flow for capillary numbers $0.1 < Ca < 1.0$. We address the case where the hydrodynamic pattern changes from having a
-vortex in slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.  In the latter case
-the bubble shape is asymmetric and cannot be approximated through flat surfaces and circumferences as
+vortex in a slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.  In the latter case
+the bubble shape is asymmetric and cannot be approximated through flat surfaces and circular circumferences as
 is often done in the literature \cite{vanbaten-circular,kreutzer-overview}.  When the vortex is present
-in the slug, the tracer is well mixed and it is common to use periodic boundary conditions and the inlet/outlet-averaged concentration
+in the slug, the scalar concentration is well mixed and it is common to use periodic boundary conditions and the inlet/outlet-averaged concentration
 % Do we really want equation references in the abstract?
-as the characteristic concentration, Eq. \ref{eq:main:definition}.
+as the characteristic concentration. %, Eq. \ref{eq:main:definition}.
 The latter is not valid for flows where tracer is not well mixed, i.e. $Ca>0.7$.  We therefore
-examine various boundary conditions (periodic, open, open with more than 1 unit cell) and definitions of the characteristic concentration.
+examine various boundary conditions (periodic, open, open with more than 1 unit cell) and definitions of the characteristic concentration for the range of capillary numbers $0.1<Ca<1.0$.
 We show that the time-dependent average concentration produces the most robust results and
-that all strategies presented in the literature are extreme limits of one equation,
+that all strategies presented in the literature are extreme limits of one unified equation. %,
 % Same question applies.
-Eq. \ref{main:main:main}. Finally, we show good agreement of simulation results for different Peclet numbers
-with analytical predictions \citet{vanbaten-circular}.
+%Eq. \ref{main:main:main}. 
+Finally, we show good agreement of simulation results for different Peclet numbers
+with analytical predictions of \citet{vanbaten-circular}.
+%The work is of use to people performing mass transfer numerical simulations for bubble train flow in microchannels within the lattice Boltzmann context.
 \end{abstract}
@@
 \label{intro}
-Monolith reactors have recently been getting more and more attention as a promising alternative to slurry
+Monolith reactors have recently been getting more attention as a promising alternative to slurry
 reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}.  These reactors usually operate in
@@
 is characterized by the dominance of surface tension over inertia and viscous effects, and by
-comparatively small gas flow velocities \cite{yue-mass}. Due to the dominance of surface tension, the bubble train flow exhibits advantageous
+comparatively small gas flow velocities \cite{yue-mass}. Due to the dominance of surface tension, the flow exhibits advantageous
  properties which cannot be achieved
-in macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls remarkably enhance mass
+in its macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls strongly enhance mass
 transfer from gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.
@@
  travelling with approximately the same velocity as liquid can be captured with a camera. These properties explain why nowadays one can find a large number of applications
-of the Bretherton-Taylor bubble train flow: continuous flow analyzers to measure liquid velocity, lung openings, chemical reactions
-such as hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc. The extensive reviews of \citet{kreutzer-overview,
+of the Bretherton-Taylor bubble train flow: continuous flow analyzers to measure liquid velocity, chemical reactors for hydrogenation of nitroaromatics, 2-ethyl-hexenal, Fischer-Tropsch synthesis, etc.
+The extensive reviews of \citet{kreutzer-overview,
 gupta-review,yue-mass} cover a significant number of applications.
 
-This work is focused on the gas to liquid mass transfer 
-study for the Bretherton/Taylor flow. A good understanding of mass transfer and how it depends on the
+This work is focused on  gas to liquid mass transfer  for the two-dimensional Bretherton/Taylor flow. A good understanding of mass transfer and how it depends on 
 parameters such as the capillary number, the Reynolds number, and slug and bubble lengths allows to properly
@@
 reactions are performed in the best possible manner. The mass transfer coefficient is defined as the flux from the 
-surface divided by the concentration difference between the concentration imposed on the body and the characteristic concentration in the domain.
- The characteristic concentration in the domain significantly depends on underlying hydrodynamics fields. 
+surface divided by the difference of the imposed concentration and the characteristic concentration in the domain.
+ The  concentration distribution in the domain is prescribed by underlying hydrodynamics fields. 
  For example, experimental studies \cite{yue-mass,bercic-mass} show a complex dependency of the mass transfer coefficient on flow parameters:
- bubble and slug lengths, and bubble velocity, which are in turn dependent on the capillary number $Ca$ and the Reynolds number $Re$. 
+ bubble and slug lengths, and bubble velocity, which  in turn relate to the capillary number $Ca$ and the Reynolds number $Re$. 
 \citet{yue-mass} established an experimental correlation for the volumetric mass transfer coefficient for a bubble train as
@@
 \end{equation}
-where $\vol$ is the volumetric mass transfer coefficient, $d_h$ is the hydrodynamic capillary
+where $\vol$ is the volumetric mass transfer coefficient, $d_h$ is the hydraulic
 diameter, $\lbubble$ is the bubble length, $\lslug$ is the slug distance (between bubbles),
@@
 experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
- For the flow of long bubbles between parallel plates chosen here as the study case it is indicated that  there exists a vortex 
+ For the flow of long bubbles between parallel plates chosen here as the study case, it is indicated that  there exists a vortex 
 in the liquid slug for $Ca<0.7$, see Fig. \ref{fig:streamlines:tweaked:velocity}, and that the bubble shape is symmetric for low capillary 
-numbers ($Ca<0.1$ \cite{cerro-bubble-train}).  In the case of flow between plates for $Ca<0.1\div0.7$ the bubble
- shape can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug. This is heavily 
+numbers ($Ca<0.1$ \cite{cerro-bubble-train}) with the capillary number defined as:
+ \beq
+ Ca=\frac{\mu_{\mathrm{liq}} \ububble}{\gamma},
+ \feq
+ where $\mu_{\mathrm{liq}}$ is the liquid viscosity, $\ububble$ is the bubble velocity, and $\gamma$ is the interfacial tension.
+ The fact that bubble shape for $Ca<0.1$ can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug has been 
 utilized for analytical estimations of mass transfer properties.
 
-% TODO: move this later so that there is no forward reference to eq.4?
-Since the mass transfer coefficient is defined in terms of a mass flux from a certain area, Eq. \ref{eq:main:definition},
-analytical estimations \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble shape. The mass
- transfer coefficient is calculated through two separate contributions from two films and two hemicircles. For both 
+% TODO: move this later so that there is no forward reference to eq.4? It's ok to have it here
+Since the mass transfer coefficient is defined in terms of a mass flux through a certain area, Eq. \ref{eq:main:definition},
+analytical estimates \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble shape. The mass
+ transfer coefficient is calculated through two separate contributions from two planar films and two hemicircles. For both 
 contributions the Higbie penetration theory \cite{higbie} is utilized, which states that the mass transfer coefficient
- for a simple flow geometry depends on the average time of liquid packet interaction with a geometrical feature. It 
-can be calculated as $\sqrt{\frac{\pi D}{t_{\mathrm{char}}}}$, where $t_{\mathrm{char}}$ is the characteristic 
-time of the interaction, and $D$ is the diffusion coefficient. As an example of the application of the Higbie penetration theory,
+ for a simple flow geometry depends on the average time a liquid packet interacts with a geometrical feature. It 
+can be calculated as $\sqrt{\frac{\pi D}{t_{\mathrm{char}}}}$, where $t_{\mathrm{char}}$ is the interaction 
+time. As an example of the application of the Higbie penetration theory,
  the mass  transfer coefficient 
@@
 \feq
-where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ states for the interaction time of liquid traveling through the planar part
- of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time in which liquid in the slug travels the distance of half bubble circumference.
-
-Despite their simplicity, analytical expressions work well for flows with low
+where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ stands for the interaction time of liquid traveling below the planar part
+ of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time during which the liquid in the slug travels the distance of half the bubble cap circumference.
+
+Despite their simplicity, such analytical expressions work well for flows with low
 capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape is
@@
 hydrodynamic pattern in the slug (i.e. presence of a vortex in slug), one can
-estimate the time for a fluid batch to travel the whole circumference.   However,
+estimate the time for a fluid batch to travel the entire circumference.   However,
 with the increase of the capillary number the situation drastically changes -- the
 symmetrical bubble shape is lost and the bubble shape resembles a bullet \cite{kuzmin-binary2d}.
-For flows with $Ca>0.7$ there is also no vortex in the liquid slug. In this case the Higbie theory fails
-to estimate the contribution from bubble caps, which explains the need to turn to numerical simulations where all
+For flows with $Ca>0.7$ there is also no vortex in the liquid slug anymore. The Higbie theory fails
+to estimate the mass transfer from bubble caps, which explains the need to turn to numerical simulations where all
 hydrodynamics fields as well as complex bubble shapes are taken into account.
 
-Available numerical studies of mass transfer
-\cite{kreutzer-overview,vanbaten-circular} lack the simulation of
-bubble shapes. The usual simulation of mass transfer is performed as
-follows: \begin{description}
+Typical numerical studies of mass transfer
+\cite{kreutzer-overview,vanbaten-circular} do not consider the simulation of
+bubble shapes for $Ca>0.1$. The usual simulation of mass transfer is performed as
+follows: 
+\begin{description}
  \item[I] The bubble shape is calculated either
 through analytical correlations \cite{bretherton} or experimental correlations
-\cite{cerro-bubble-train} without directly resolving bubbles shapes through
+\cite{cerro-bubble-train} without directly resolving the bubbles shapes through
 multiphase simulations.  The expressions for bubble shapes are available only
-for flows with the capillary number $Ca<0.1$.
+for flows with capillary number $Ca<0.1$.
   \item[II] Hydrodynamic fields
 are then obtained by performing simulations of one-component flow around the
-droplet by imposing the bubble velocity on the walls. Thus, the simulations are
-performed in the reference frame moving with the bubble. The stress-free
+bubble by imposing the bubble velocity on the walls. Thus, the simulations are
+performed in the reference frame moving with the bubble. A stress-free
 condition is imposed at the bubble surface.
@@
 saturation concentration is imposed at the bubble surface. Only one unit cell
-containing a single bubble is used for simulations. Periodic boundary conditions are
+containing a single bubble is used for simulations. Periodic concentration boundary conditions are
 utilized to determine the volumetric mass transfer coefficient, which is
@@
 \begin{equation} \label{main:simulation:equation}
-\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\coutlet\rangle}
+\vol=\frac{\mathrm{\overline{Flux}}}{\cbubble-\langle\cinoutlet\rangle}
 \frac{\mathrm{bubble\ surface\ area}}{\mathrm{unit\ cell\ volume}},
 \end{equation}
- where $\langle\coutlet(t)\rangle=\int{C \uoutlet
-\mathrm{d}A}/\int{\uoutlet\mathrm{d}A}$ is the space-averaged outlet
-concentration as a function of time used as the characteristic concentration
-in the definition, Eq. \ref{eq:main:definition}.  The time-averaged
+ where $\langle\cinoutlet(t)\rangle=\int{C \uinoutlet
+\mathrm{d}A}/\int{\uinoutlet\mathrm{d}A}$ is the space-averaged inlet/outlet (periodic boundary conditions)
+concentration as a function of time. Therefore, in terms of the mass transfer definition, $\langle\cinoutlet(t)\rangle$ plays a role of the 
+characteristic concentration.
+%This is the characteristic concentration in the definition, Eq. \ref{eq:main:definition}.  
+The time-averaged
 concentration flux ($\mathrm{\overline{Flux}}$) is calculated as the difference
@@
 $t_2$ divided by the time difference $t_2-t_1$. The agreement between numerical
-simulations \cite{vanbaten-circular} and correlations of \citet{bercic-mass}
+simulations \cite{vanbaten-circular}, which formulation is presented above, and experimental correlations of \citet{bercic-mass}
 % TODO: was good where?
-was good.  \end{description}
+was good. 
+ \end{description}
 
 The presented numerical approaches \cite{vanbaten-circular,kreutzer-overview}
-can be critized on a number of points. They mainly
+can be criticized on a number of points. They mainly
 originate from the bubble shape approximation, which is taken to be symmetrical, i.e.
-consisting of hemispheres and cylinder film for the case of flow in circular
-capillaries. This is valid  for small capillary numbers $Ca<0.1$. As previously
+consisting of two hemispheres and film for the case of flow in circular
+capillaries. This is valid  for small capillary numbers only ($Ca<0.1$). As previously
 discussed, for such capillary numbers the tracer is well mixed in the slug and 
 the choice of the characteristic concentration needed for the mass transfer
-coefficient, Eq. \ref{eq:main:definition} is obvious. With minimal
-differences in the results, it can either be averaged in the liquid slug
-concentration or the outlet space-averaged concentration as used in the formulation
-of \citet{vanbaten-circular}.
+coefficient, Eq. \ref{eq:main:definition}, is obvious. With minimal
+differences in the results, it can either be the averaged concentration in the liquid slug
+or the inlet/outlet space-averaged concentration. The latter is used in the formulation
+of \citet{vanbaten-circular} presented above.
 
@@
 concentration along the streamwise direction changes exponentially with distance.
-Mass transfer simulations however, are made only for one unit cell
-using periodic boundary conditions with the same concentration at the inlet
-and at the outlet. The question how one unit cell simulation corresponds to
-experimental measurements arises where concentration difference is measured at
-the distances of at least of a few unit cells \cite{bercic-mass}. In
+Mass transfer simulations however, consider only one unit cell
+using periodic boundary conditions, and thus the same concentration at the inlet
+and at the outlet. The question how one unit cell simulations correspond to
+experimental measurements where concentration differences are measured at
+ distances of at least of a few unit cells \cite{bercic-mass}. In
 other words one needs to understand how the discrete one unit cell simulation
 corresponds to the continuous picture in experiments where one does not
-distinguish bubbles but takes measurements of concentration at different
+distinguish discrete bubbles but takes measurements of concentration at different
 locations.
@@
 Addressing situations for a rich number of hydrodynamic patterns, shapes, and
-effects for a bubble train, we feel that there is a need to examine more
+effects of bubble lengths, etc for bubble train flows, we feel that there is a need to examine 
 carefully the strategies and assumptions behind the numerical calculations
@@
 procedures as to how properly obtain the mass transfer coefficient via a study
-of different boundary conditions and different definitions of characteristic concentration.
+of different boundary conditions and different definitions of the characteristic concentration.
 The case we want to examine is a two-dimensional bubble train flow between parallel plates.
@@
 conditions to determine the mass transfer coefficient when the vortex in the slug
-disappears.
+disappears, i.e. $Ca>0.7$.
  \item[II] Validity of the inlet/outlet-averaged or domain-averaged concentrations as
@@
  \item[III] Transition of the continuous experimental picture to
-numerical simulations of a few unit cells, the issue of correspondence
+numerical simulations with a few unit cells, the issue of correspondence
 between space averages (simulations \cite{vanbaten-circular}) and time averages (experiment).
- \item[IV] Influence of the hydrodynamic pattern in flows with $Ca>0.7$ on the mass transfer.
+% \item[IV] Influence of the hydrodynamic pattern in flows with $Ca>0.7$ on the mass transfer.
 \end{description}
-In addition, at the end of the manuscript we present a comparison of the dependence of the volumetric
-mass transfer coefficient on the Peclet number with analytical \cite{irandoust} and experimental correlations
-\cite{yue-mass}.  The thorough determination of the Sherwood number as a
+In addition, at the end of the manuscript we present results of the dependence of the volumetric
+mass transfer coefficient on the Peclet number that we compare with analytical \cite{irandoust} and experimental correlations
+\cite{yue-mass}.  The thorough determination of the mass transfer coefficient and associated Sherwood number as a
 function of other non-dimensional parameters such as gas holdup, bubble/slug
-lenghts, and the capillary number is the goal of future work.
+lenghts, and the capillary number is left for future.
 \begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/benchmark_hydro.eps}
-\caption{Simplified sketch of the bubble train motion. Using periodic
-conditions for the velocity field is natural, but needs validation for the mass
+\caption{Simplified sketch of the bubble motion. Using periodic
+conditions for the velocity field is natural, but needs evaluation for mass
 transfer.
@@
 $Ca=0.1\div 1.0$ to extract bubble shapes. For this range of capillary numbers
-we are able to capture the bubble shape change and the change of hydrodynamic
-patterns. The mass transfer simulations were performed with different boundary
+we were able to capture the bubble shape change and the change of hydrodynamic
+patterns. The mass transfer simulations presented here were performed with various boundary
 conditions (open, periodic) and with a few unit cells ($1$ to $10$ unit cells).
@@
 \cite{frisch,mcnamara,HJ,HSB}. This method was successfully applied to simulate
-not only simple hydrodynamic problems \cite{yu}, but also multiphase
+not only single phase hydrodynamic problems \cite{yu}, but also multiphase
 flows \cite{Shan-chen:extended,swift,gunstensen}, heat transfer
@@
 The mass transfer problems in the lattice Boltzmann framework were mainly
-addressed in series of works of Ginzburg and co-authors
+addressed in a series of works of Ginzburg and co-authors
 \cite{ginzburg-main,ginzburg-boundary-conditions,ginzburg-saturated-flow}.
@@
 \citet{jos-mass} simulating lateral mixing in cross-channel flow.  The last two
-works focused on problems of homogeneous nature and do not provide
+works are focused on problems of homogeneous nature and do not provide
 guidance as to how to obtain the mass transfer coefficient for heterogeneous cases.
@@
 Boltzmann model used to simulate mass transfer is presented and followed by benchmarks. Finally,
-numerical simulations of different boundary conditions and simulations spanning a few unit cells for
+numerical simulations of various boundary conditions and simulations spanning a few unit cells for
 different hydrodynamic patterns are presented to establish the procedure to determine the
@@
 \section{Mass transfer definitions}
-By definition, the mass transfer coefficient from the surface with the imposed constant
+By definition, the mass transfer coefficient from a surface with an imposed constant
 concentration $\cbubble$ is the following:
-\beq
+\beqal
 \label{eq:main:definition}
-k_L=\frac{\dot{m}}{P \Delta C},
-\feq
+&k_L=\frac{\dot{m}}{P \Delta C},\ \Delta C= \cbubble - \cmedium,
+\feqal
 where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
 $\Bigl[m^2\Bigr]$, and $\Delta C$ is the concentration difference between the surface and the surrounding medium
-$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of velocity
-$\Bigl[\frac{m}{s}\Bigr]$. Usually, the surrounding medium concentration is taken at the infinite distance
+$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of 
+$\Bigl[\frac{m}{s}\Bigr]$. Usually, the surrounding medium concentration is taken at an infinite distance
 from the bubble. However, in the case of complicated geometries and non-homogeneous concentrations, 
 the medium concentration can be the average concentration in the domain or the flux-averaged
-concentration at the inlet or outlet, etc. Thus, one needs to establish a thorough definition of the volumetric
+concentration at the inlet or outlet, etc. Thus, one needs to establish a clear definition of  $\Delta C$ to determine the volumetric
 mass transfer coefficient in the case of complex geometries and non-trivial hydrodynamic velocity patterns.
 
-There exist a number of methods to estimate the mass transfer coefficient $k_L$. We first examine the
-theoretical definitions of the mass transfer in the case of point mass sources.
+%There exist a number of methods to estimate the mass transfer coefficient $k_L$. 
+We first examine the
+ definitions of mass transfer in the case of point  sources.
 \subsection{Point mass sources}
 In what follows we will present three approaches to calculate point  mass transfer
-coefficients (by point source we assume the source with an infinitesimally small surface area $P$):
+coefficients (by point source we assume the source to have an infinitesimally small surface area $P$):
 \begin{enumerate}
 \item
-Let us look at the infinitesimal small domain of volume $A \Delta x$, not
-moving and with a point mass source.  The concentration difference can be then found as $\Delta C =
+Let us look at the infinitesimally small domain of volume $A \Delta x$, not
+moving and containing a point source.  The concentration difference is $\Delta C =
 \cstar -
@@
 \feq
-with the initial condition $C(0)=0$
+with the initial condition $C(0)=0$.
 The solution can be found as:
@@
 If one can assume that the point mass sources are distributed in the whole
-medium, the mass accumulated in the unit volume $V=A \Delta x$ can be
+medium, the mass accumulated in the volume $V=A \Delta x$ can be
 calculated as the difference of mass fluxes entering and leaving domain $U
@@
 \feq 
-giving the same equation but only in the coordinate domain:
+giving the same soltuion but only in spatial domain:
 \beq
@@
 \item If one transfers to the frame moving with the liquid velocity $U$, the situation will be
-the same as in the first case. However, one can connect the time and spatial location with the
+the same as in the first case. One can connect  time and space with the
 velocity $U$ ($t=\frac{x}{U}$) to obtain the same equation as in the case 2.
@@
 geometry. As was mentioned before, depending on the capillary
-number the mixing velocity pattern is different. Analytical approaches
+number the velocity pattern and thus scalar mixing is different. Analytical approaches
 \cite{irandoust,vanbaten-circular} assume that the
-contributions from film and bubble caps can be calculated separately. However, one can see that
-such 
-an assumption (slug well mixed and the concentration uniformly distributed over
-the slug) usually overpredicts the mass transfer \cite{irandoust}. This happens since some tracer
-concentration from film is mixed with the slug and increases the overall concentration in the slug, thereby decreasing
-the mass transfer from bubble caps.
-Therefore, all estimations for the analytical mass transfer coefficient calculation  do not account for mutual mass
+contributions from film and bubble caps can be calculated separately.
+Therefore no tracer from a film influences bubble caps diffusion.
+However, this assumption overpredicts mass transfer for number of experiments \cite{irandoust}.
+This happens since some tracer
+concentration from the film is mixed with the slug and increases the overall concentration in the slug, thereby decreasing
+the mass transfer from the bubble caps.
+Therefore, the analytical estimates for the analytical mass transfer coefficient calculation  do not account for mutual mass
 transfer from neighbouring bubbles.
 
-Another issue is that if the bubble is long enough then the film saturates with the tracer
-concentration and its influence on mass transfer can be negligible \cite{vanbaten-circular}.
-Mixing patterns of the film and liquid slugs are of great importance for the analytical
-estimation of mass transfer \cite{yue-mass}. However, the assumptions usually taken for the
-mass transfer calculation are small capillary number and certain mixing patterns which help to
+%Another issue is that if the bubble is long enough then the film saturates with the tracer
+%concentration and its influence on mass transfer can be negligible \cite{vanbaten-circular}.
+Overall, mixing patterns of the film and liquid slugs are of great importance for the analytical
+estimation of mass transfer \cite{yue-mass}. However, the assumptions usually taken for 
+mass transfer calculations are small capillary numbers and certain mixing patterns such to help to
 estimate the mass transfer using the penetration theory of \citet{higbie}.
@@
 In comparison with analytical calculations and simplifications, the numerical approach can take into
-account the complex mixing patterns and geometries. However, there are challenges as to how to
-mimic the continuous picture like moving with bulk velocity $U=\ugas+\uliq$ reacting medium as seen in
+account the complex mixing patterns and geometries. However, there are challenges as  how to
+mimic the continuous picture where reacting medium is moving with bulk velocity $U=\ugas+\uliq$  as it is done in
 experiments. Thus, the questions indicated in Section \ref{intro} arise.  The next section gives more
@@
 \label{section:cases}
-Ideally one needs to mimic the continuous picture as it is seen in experiments.
+Ideally one wants to mimic the continuous picture as it is seen in experiments.
 Thus, mass transfer simulations for a number of unit cells are needed. As was
-indicated above there are two approaches towards it -- either to simulate the
+indicated above, there are two approaches towards it -- either to simulate the
 bubble train and then to measure concentration along the pipe, Eq.~\ref{main:mass:transfer:expression},
 or to transfer to the reference frame moving with the bulk
-velocity $U$ and conduct same measurements. However, both methods require tracking of
+velocity $U$ and conduct the same measurements. However, both methods require tracking of
 moving bubbles which is complicated from the numerical point of view. Therefore, one needs to come
-up with simple smaller domain calculations of the mass transfer coefficient, which mimics the
-continuous picture by an infinite number of closely separated bubbles.
+up with a simple and smaller domain for calculations of the mass transfer coefficient, which closely mimics the
+continuous picture by an infinite number of  separated bubbles.
 
 To avoid complications with moving grids, our
-approach is to simulate mass transfer in the reference frame moving with the bubble. Therefore, one
+approach is to simulate mass transfer in a reference frame moving with the bubble. Therefore, one
 needs to examine  Eq.~\ref{main:mass:transfer:expression} more closely.
@@
 %to be only as a function of time. 
-One can make different choices of
+One can make different choices for
 $\langle C(t) \rangle$ such as the concentration averaged over the whole domain or inlet/outlet space-averaged
@@
 \feq
-Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are
-cornerstones of the present work  Four possible scenarios of numerical simulations are examined: 
+Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are the
+cornerstones of the present work . Four possible scenarios of numerical simulations have been examined: 
 \begin{enumerate}
@@
 cell is simulated with
-periodic boundary conditions, see Fig. \ref{fig:benchmark} so that no tracer leaves the
-domain like for the plug flow. 
+periodic boundary conditions, see Fig. \ref{fig:benchmark}. In this case no tracer leaves the
+domain similarly to the plug flow. 
 %From the physical point of view this case resembles the mass transfer for small Capillary numbers
@@
 %cell, i.e. the outlet and the inlet concentrations are close. 
-Though easier to implement, it rises certain criticisms
-about requiring the inlet concentration to be equal to the outlet one. As was
+Though easier to implement, it gives a rise to the criticism
+that the inlet concentration is equal to the outlet one. As was
 discussed, in experiments there is a concentration difference between the
-inlet and the outlet.
-
-The volumetric mass transfer coefficient is calculated by Eq. \ref{theor:one:concentration:time}.
+inlet and the outlet, even for one unit cell.
+
+In this case, the volumetric mass transfer coefficient is calculated by Eq. \ref{theor:one:concentration:time}.
 The
 characteristic concentration $\langle C(t) \rangle$ required for the volumetric mass
-transfer coefficient, Eq.
-\ref{theor:one:concentration:time}, is taken as the average concentration in the domain:
+transfer coefficient is taken as the average concentration in the domain:
 \beq
@@
 \end{figure}
-\item Periodic boundary conditions are applied as in the first case but the characteristic concentration is taken as the inlet/outlet
+\item Periodic boundary conditions are applied as in the first case but the characteristic concentration is taken as the inlet/outlet flux-averaged
 concentration \cite{vanbaten-circular}:
@@
 The assumptions of this approach are
-that the difference between inlet and outlet is not significant (so that they can be taken to have average
-concentration) and that the tracer is well mixed in the slug.
+that the difference between inlet/outlet and the space-averaged over the whole unit cell concentration is not significant. Thus, the tracer is well mixed in the slug.
 \item
-The approach of \citet{vanbaten-circular}, where [eriodic boundary conditions are used and
+The approach of \citet{vanbaten-circular}, where periodic boundary conditions are used and
 the mass transfer coefficient is calculated as the gain of the mass in the system
@@
 \feq
-where the mass difference in the domain can be calculated as:
-\beq
-\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(\bm{x},t_2)\mathrm{d}V}-\int_{liq}{
+where the mass flux in the domain can be calculated as:
+\beq
+\dot{m}=\frac{m_2-m_1}{t_2-t_1}=\frac{\int_{liq}{C(\bm{x},t_2)\mathrm{d}\bm{x}}-\int_{liq}{
 C(\bm{x},t_1)\mathrm { d } \bm{x}} } {
@@
 \feq
-In the approach of \citeauthor{vanbaten-circular} the inlet and outlet concentrations were taken as the
+In the approach of \citeauthor{vanbaten-circular} the inlet/outlet flux-averaged concentrations were taken as the
 characteristic concentration $\langle C(t) \rangle $.
@@
 \item 
-Simulation of a few unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the simulation of the
-bubble train head, after injection to the pipe and travelling along the pipe. One can see that this
-situation corresponds most closely to the experimental picture, but also requires larger computational
+Simulation of a few unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the head of the
+bubble train, after injection in the pipe and travelling along the channel. One can see that this
+situation best resembles the experimental picture, but also requires larger computational
 resources. By simulating a certain number of the
 bubbles in the train head, the influence of the boundaries can be
-diminished. In this case, there is no ambiguity in the choice of the
+diminished. For example, left and right boundary conditions in this case are taken as open boundaries, i.e. $\partial C/ \partial x = 0 $.  There is no ambiguity in the choice of the
 characteristic concentration. The average concentration of any unit cell far away from boundaries will be governed
 by Eq.
-\ref{theor:continuous:mass:transfer}. \begin{figure}[htb!]
+\ref{theor:continuous:mass:transfer}. 
+\begin{figure}[htb!]
 \includegraphics[width=\textwidth]{Figures/benchmark_alot.eps}\\
@@
 
-Periodic boundary condition is the extreme
+Periodic boundary conditions are the extreme
 limiting case of Eq. \ref{main:main:main}: 
@@
 surface. However, to calculate the mass transfer coefficient one needs to have
-the characteristic concentration  $\langle C(t) \rangle$ and mass gain $\dot{m}$
+the characteristic concentration  $\langle C(t) \rangle$ and the mass gain $\dot{m}$
 which do require the storage of both temporal and spatial information.
 
-Another limiting case (will be shown later) is the hydrodynamic pattern change
-$Ca>0.7$. The mass accumulation rate equals zero in this case, $\dot{m}=0$. One
+Another limiting case (will be shown later) is when the mass accumulation rate equals zero, i.e. $\dot{m}=0$. 
+This situation corresponds for simulation of a few unit cells with open boundary for flows with
+$Ca>0.7$.   One
 can use only spatial information to calculate the mass transfer coefficient,
@@
 
-Before we examine all the test cases above, the lattice Boltzmann mass transfer
+Before we examine all the test cases above, some lattice Boltzmann mass transfer
 benchmarks will be presented.
@@
 are derived  as two separate contributions: the mass transfer from two
-circumferences and the mass transfer from the film. We will examine these
-problems closely with the help of the lattice Boltzmann method and compare them
+half circles and the mass transfer from the film. We will examine these
+mass transfer cases closely with the help of the lattice Boltzmann method and compare them
 against analytical
-solutions. The next sections will give a short introduction on the lattice Boltzmann method and present a few benchmarks.
+solutions. The next sections will give a short introduction to the lattice Boltzmann method and present benchmark results.
 
@@
 two parts: a local collision step, and a propagation step which transports
-information from one node to another along some 
-directions specified by the discrete velocity set.
+information from one node to another along  
+directions specified by a discrete velocity set.
 The LBE is typically implemented as follows:
@@
 where $f_i$ is the probability distribution function in the direction $\bm{c_i}$,
- $f_i^{eq}$ is the equilibrium probability distribution function, $\omega$ is the
-relaxation parameter. Collision operator, $-\omega \bigl(f_i- f_i^{eq}\bigr)$ is so-called BGK
+ $eq_i$ is the equilibrium probability distribution function, and $\omega$ is the
+relaxation parameter. The term $-\omega \bigl(f_i- eq_i\bigr)$ is the so-called BGK
 collision operator \cite{bgk}. However, the approach used here is the TRT
@@
 comparison with the widely used BGK collision operator, the TRT collision operator has better accuracy
-for diffusion and convection fluxes, as well as a larger range of parameters where the LBM scheme is stable.
+for diffusion and convection fluxes, as well as a larger range of parameters where the scheme is stable.
 
@@
 decomposes the populations and the equilibrium
-distribution into the symmetric and antisymmetric parts:
+distribution into a symmetric and an antisymmetric parts:
 \begin{equation}
@@
 \end{equation}
-Note that the BGK collision operator is the particular subclass of the TRT relaxation operator with
+Note that the TRT collision operator reduces to the BGK operator if
 $\omegaplus=\omegaminus$. In comparison with the BGK collision operator,
-the TRT collision operator has the additional degree of freedom. Thus, the TRT operator 
+the TRT collision operator has one additional degree of freedom. The TRT operator 
 introduces
-the free parameter
+the following free parameter
 $\Lambda=\Bigl(\frac{1}{\omegaplus}-\frac{1}{2}\Bigr)\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}
 \Bigr)$. 
-This free parameter controls the effective location of the bounce-back
+This free parameter controls the effective location of  bounce-back
 walls \cite{ginzburg-multireflection}, second-order accuracy of
@@
 In particular, $\Lambda=\frac{1}{4}$ achieves the optimal stability for the
-linear advection-diffusion isotropic equation \cite{kuzmin-stability-optimal}.
+isotropic advection-diffusion equation \cite{kuzmin-stability-optimal}.
 
 The parameters $\omegaplus$, $\omegaminus$ and $eq_i$ fully define the lattice Boltzmann
-procedure. The two-dimensional nine velocities LBM $D2Q9$ we used in this work is defined on the set
+procedure. The two-dimensional, nine velocities LBM $D2Q9$ we used in this work is defined on the set
 of lattice
-velocities with coordinates:
+velocities with components:
 \beqal
@@
 
-The equilibrium functions for $D2Q9$ TRT model are represented as \cite{kuzmin-stability-optimal}:
+The equilibrium functions for the $D2Q9$ TRT model are represented as \cite{kuzmin-stability-optimal}:
 \begin{equation}
@@
 u_y}{4} p_i^{xy}\\
-&eq_i^{(a)}=\frac{K_{xx}-K_{yy}}{4} p_i^{xx}+\frac{K_{xy}}{4} p_i^{(xy)},
+&eq_i^{(a)}=\frac{K_{xx}-K_{yy}}{4} p_i^{xx}+\frac{K_{xy}}{4} p_i^{(xy)}\\
+&eq_i^{-}=t_i^{(a)}  u_{\alpha} c_{i\alpha},
 \end{aligned}
@@
 weights
-$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most spread set of weights, the so called
-``hydrodynamic`` weights, was chosen:
+$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most used set of weights, the so-called
+``hydrodynamic`` weights, were chosen:
 \begin{equation}
@@
 \feq
-where $D_{\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)K_{\alpha\beta}$
-with the
+where the concentration $C=\sum_i{f_i}$, and $D_{\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)K_{\alpha\beta}$ is the
 following diffusion tensor:
@@
 We want to resolve the isotropic advection-diffusion equation, $D=D_{xx}=D_{yy}$ or
-$K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components set to zero $D_{xy}=0$. In
+$K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components set to zero ($D_{xy}=0$). In
 contrast to the $D2Q5$ model, with $D2Q9$ it is
@@
 
-Boundary conditions for the mass transfer used in this work are all of Dirichlet type. We validated
+%Boundary conditions for the mass transfer used in this work are all of Dirichlet type. 
+We validated
 two types of boundary conditions: Inamuro boundary conditions \cite{inamuro-scalar-boundary} and
 pressure anti bounce-back boundary conditions \cite{ginzburg-multireflection}. However, the
-simulation results presented in this work are only pressure anti bounce-back due to their ability
+simulation results  are presented only for pressure anti bounce-back due to their ability
 to handle complex boundaries in a simple way:
@@
 where $\cstar$ is the concentration to be imposed at the surface, $\bm{u}$ is the surface velocity,
-$i$ is the direction number pointing to the domain (unknown) located at the boundary surface $B$,
+$i$ is the direction number pointing to the domain located at the boundary surface $B$,
 $\bar{i}$ is the direction number opposite to $i$ and is located at the fluid node $F$ specifically
@@
 numbers governing the physics of the problem. In our case, this number is the Peclet number, $Pe=\frac{\ububble L}{D}$.
-Therefore, one can substitute any quantity, i.e.
+Therefore, one can choose any quantity, for example 
 $\ububble$ in the lattice Boltzmann units as soon as the
 Peclet number is  matched in physical space and numerical simulations. The fact that $\ububble$
-can be chosen arbitrarily is extremely useful in the context of numerical simulations, since one can
-increase the time step and decrease the computational demand by an order of magnitude while still
-obtaining meaningful results. This point will be used in simulations and covered later.
+can be chosen  is extremely useful in the context of numerical simulations, since one can
+increase the time step and decrease the computational demand by an order of magnitude. 
+% while still obtaining meaningful results. 
+This point will be used in simulations and covered later.
 
@@
 % for the simulations, or that the simulation results are compared to results obtained via this simplification?
-Next section will cover LBM benchmarks that resemble the mass transfer problem from a bubble, as 
-mass transfer from the film  and circumferences.
+The next section will cover LBM benchmarks that resemble the mass transfer from a bubble 
+(mass transfer from the film  and bubble caps).
 
 \subsection{The radial case}
-The case to be examined  is the mass transfer from a stair-case boundary forming a circle. It
+The case to be examined  is the mass transfer from a circle with radius $a$, with the circle approximated as a stair-case. It
 can be described by the following system of equations:
@@
 \feq 
-The solution is represented as \cite{chemical-correlations}:
+The analytical solution is \cite{chemical-correlations}:
 \beq
@@
 $\mu_4=11.7915$, $\mu_5=14.9309$.
-By taking initial concentration to be $0$, one can obtain the following solution:
-\beq
+By taking the initial concentration as $0$, one obtains:
+\beq
+\label{eq:analytical:profile:radial:case}
 C(r,t)=C_0 \Biggl(1 - \sum_{n=1}^{\infty}{\frac{2}{\mu_n
@@
 
-The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$ units. Some examples for
+The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$  lattice units. Some examples for
 different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
@@
 \includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
-\caption{Profiles for different diffusion parameters varied with $\omegaminus$. One can see that the
+\caption{Profiles for different diffusion parameters varied with $\omegaminus$ (lines: Eq. \ref{eq:analytical:profile:radial:case}, symbols: LB results). One can see that the
 diffusion from curved boundaries is captured
-accurately \label{fig:cylinder:benchmark}. $r$ is the distance from the center.}
+accurately \label{fig:cylinder:benchmark}. $r$ is the distance from the center. The profiles are taken along  the axis $x$.}
 \end{figure}
 
-\subsection{Parabolic velocity profile with the velocity zero gradient at the wall}
-The problem is defined in terms of PDEs as follows: 
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
-&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2.
-\end{aligned}
-\feq
-The procedure to solve this PDE is presented in Appendix \ref{appendix:zero:gradient}:
-\beq
-\label{analytical:solution:zero:gradient}
-\begin{aligned}
-&C(x,y)=\cstar+\sum_{m}{C_m
-\sqrt{\frac{y}{\delta}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{\delta^2}\Bigr)\exp\Bigl(-\frac{
-m^4 } { Pe }
-\frac { x }{\delta}\Bigr)}\\
-&C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}
-\end{aligned}
-\feq
-Fig. \ref{fig:parabolic:zero:gradient} shows a comparison of the steady-state contours between the
-analytical solution and the simulation with anti bounce-back boundary conditions used to impose constant
-concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The simulation grid is
-$80\times1600$. Parameter $\omegaminus=1.8$ implies the diffusion coefficient to be
-$D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)=0.0185$.  
-\begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
-\caption{Comparison of the concentration contour levels between the analytical solution, Eq.
-\ref{analytical:solution:zero:gradient}, and simulation for the diffusion coefficient $D=0.0185$. The simulation was
-performed on the grid size of $80\times 1600$. The constant concentration is imposed with the
-anti bounce-back conditions, Eq. \ref{antibb}. Coordinate $x$ and $y$ are non-dimensionalized on
-the height of the channel. $\delta=H/2$ is half of the channel height.
-\label{fig:parabolic:zero:gradient}}
-\end{figure}
+%\subsection{Parabolic velocity profile with the  zero velocity gradient at the wall}
+%The problem is defined in terms of the PDE as follows: 
+%\beq
+%\begin{aligned}
+%&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+%&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+%&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2.
+%\end{aligned}
+%\feq
+%The procedure to solve this PDE analytically is presented in Appendix \ref{appendix:zero:gradient}. The result is:
+%\beq
+%\label{analytical:solution:zero:gradient}
+%\begin{aligned}
+%&C(x,y)=\cstar+\sum_{m}{C_m
+%\sqrt{\frac{y}{\delta}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{\delta^2}\Bigr)\exp\Bigl(-\frac{
+%m^4 } { Pe }
+%\frac { x }{\delta}\Bigr)}\\
+%&C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+%\end{aligned}
+%\feq
+%Fig. \ref{fig:parabolic:zero:gradient} shows a comparison contours between the
+%analytical solution and the simulation with anti bounce-back boundary conditions used to impose constant
+%concentrations at the wall $\cstar=1$ and the inlet $C_0=0$. The simulation grid is
+%$80\times1600$. Parameter $\omegaminus=1.8$ implies the diffusion coefficient to be
+%$D=\frac{1}{3}\Bigl(\frac{1}{\omega}-\frac{1}{2}\Bigr)=0.0185$.  
+%\begin{figure}[htb!]
+%\includegraphics[width=\textwidth]{Figures/parabolic_profile_zero_gradient_comparison.eps}
+%\caption{Comparison of the concentration contour levels between the analytical solution, Eq.
+%\ref{analytical:solution:zero:gradient}, and simulation for the diffusion coefficient $D=0.0185$.
+$\delta=H/2$ is half of the channel height (symmetry is used for the sake of simplicity) .
+The simulation was
+%performed on the grid size of $80\times 1600$. The constant concentration is imposed with the
+%anti bounce-back conditions, Eq. \ref{antibb}. Coordinate $x$ and $y$ are non-dimensionalized on
+%the height of the channel. 
+%\label{fig:parabolic:zero:gradient}}
+%\end{figure}
 
@@
 between contours of analytical and simulation results is presented in Fig.
-\ref{fig:parabolic:comparison}. Parameters were taken  same as in the previous case: the
-diffusion coefficient is $D=0.0185$, the grid dimension is $80\times1600$. 
+\ref{fig:parabolic:comparison}. Parameters were taken the  same as in the previous case: $D=0.0185$, the grid dimension is $80\times1600$. 
 \begin{figure}[htb!]
@@
 
-After the LBM is validated against the benchmarks relevant for the flow around bubbles, one can
-examine all cases mentioned in Section
-\ref{section:cases} to calculate the volumetric mass transfer coefficient.
+Now the LBM is validated against the benchmarks relevant for the flow around bubbles, one can
+examine the cases mentioned in Section
+\ref{section:cases} to calculate the volumetric mass transfer coefficient for Taylor bubble train flow.
 
@@
 \label{sec:numerics}
-The multiphase code was utilized to obtain the flow patterns and bubble shapes for different capillary numbers
+A multiphase code was utilized to obtain the flow patterns and bubble shapes for different capillary numbers
 \cite{kuzmin-binary2d}. Five particular cases were chosen to be examined, their results are summarized
@@
 \caption{Sample results with the binary liquid lattice Boltzmann model \cite{kuzmin-binary2d}. The
-following notations are used: the capillary number $Ca=\frac{\ububble L}{\rho \nu_{\mathrm{liq}}}$, $\delta$ is the
-non-dimensional film thickness, $\uliq$ is the superficial liquid velocity, $\ugas$ is the
-superficial gas velocity. The simulation sketch is presented in Fig.
+following notations are used: the capillary number $Ca=\frac{\ububble L}{\rho \nu_{\mathrm{liq}}}$, $\uliq$ is the superficial liquid velocity, $\ugas$ is the
+superficial gas velocity. $\delta$ is the
+non-dimensional film thickness, $\lbubble$ and $\lslug$ are the non-dimensional bubble and slug lengths (defined in channel heights).The simulation sketch is presented in Fig.
 \ref{fig:benchmark:hydro}. \label{table:capillary:cases}}
 \end{table}
-Note that velocities in Table \ref{table:capillary:cases} are small. It means that to
+Note that the velocities (LB system) in Table \ref{table:capillary:cases} are small. It means that to
 match large Peclet numbers, $Pe=\frac{\ububble L}{D}$, usually used in experiments, one needs to decrease the diffusion coefficient
-$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. Thus, parameter $\omegaminus\approx 0.5$. However, for such parameters
+$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. Thus, the parameter $\omegaminus\approx 0.5$. However, for such parameters
 $\omegaminus$ the stability of the lattice Boltzmann method drastically decreases
 \cite{kuzmin-d1q3}. On the other hand, one iteration in the lattice Boltzmann system corresponds
-to the physical time step  $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
+to a physical time step  $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
 x}{U_{\mathrm{bubble,phys}}}$. The iteration time is proportional to the velocity $U_{\mathrm{LB}}$
 and the typical number of simulation steps to obtain the steady-state mass transfer coefficient for
-$Ca<0.2$ is of the order of a few millions. Therefore, it is desirable to increase  velocity  $U_{\mathrm{LB}}$
-while keeping the Peclet number the same. If one increases the velocity, then
-$\omegaminus$ increases as well, moving away from the stability limit $0.5$ and therefore
-stabilizing the simulation.
+$Ca<0.2$ is of the order of a few millions. Therefore, it is desirable to increase    $U_{\mathrm{LB}}$
+while maintaining the Peclet number. If one increases the velocity, then
+$\omegaminus$ increases as well, which impacts positively on the stability of the LBM.
 
@@
 \begin{description}
- \item[Flow field] Given the capillary number $Ca$, one needs to obtain hydrodynamic fields around
-the bubble using the multiphase binary liquid lattice Boltzmann model according to work
-\cite{kuzmin-binary2d}. Periodic boundary conditions are used. The grid used in this work is
-$202\times 3000$ which corresponds to the fluid domain  of size $200\times3000$. The grid resolution is
+ \item[Flow field] Given a capillary number $Ca$, one needs to obtain hydrodynamic fields around
+the bubble using the multiphase binary liquid lattice Boltzmann model according to our previous work
+\cite{kuzmin-binary2d}. Periodic boundary conditions were used in that work. The grid used  was
+$202\times 3000$ which corresponds to the fluid domain  of size $200\times3000$. That grid resolution was
 taken to ensure grid
 independency of the results \cite{kuzmin-binary2d}. Note that we do not approximate bubble shapes by correlations, but we directly resolve them by using the multiphase solver. 
- \item[Bubble reference frame] Once the hydrodynamics is resolved, the mass transfer simulations
-are conducted in the reference frame moving with the bubble, where the bubble stands still and the
-flow is happening around the
-bubble. We impose a steady concentration on the surface
+ \item[Bubble reference frame] Once the hydrodynamics is solved, the mass transfer simulations
+are conducted in the reference frame moving with the bubble, where the bubble stands still and the liquid
+flows around the
+bubble. We impose an uniform and steady concentration on the surface
 of the bubble with the anti bounce-back condition, Eq. \ref{antibb}.
@@
 This issue arises because of the
-multiphase model used in simulations. The binary liquid lattice Boltzmann model is a diffusive
+multiphase model used in the flow simulations. The binary liquid lattice Boltzmann model is a diffusive
 interface model where no clear boundary between gas and liquid exists.
@@
 % spurious velocities within the model itself?
-We obtain the bubble shape by imposing a condition on the order parameter field $\phi$ as in \cite{kuzmin-binary2d}, say $\phi\leq0$. The velocity of the
-bubble is calculated as the bubble tip velocity. Because of the square grid the shape of the bubble is determined within accuracy of one grid node. Thus,
-there is the error in determination of the bubble velocity. Though these errors are small,
-there is still a small non-zero velocity component pointing to the bubble in some places, see Fig. 8 in
-\cite{kuzmin-binary2d} where some streamlines are penetrating the bubble surface a bit.
+We obtain the bubble shape by imposing a condition on the order parameter field $\phi$ with $\phi\leq0$ in the bubble \cite{kuzmin-binary2d}. The velocity of the
+bubble is defined as the bubble tip velocity. Because of the square grid, the shape of the bubble is determined within an accuracy of one grid spacing. Thus,
+there is an error in the determination of the bubble velocity. Though these errors are small,
+there is still a small non-zero velocity component pointing into the bubble in some places, see Fig. 8 in
+\cite{kuzmin-binary2d} where some streamlines are penetrating the bubble surface.
 This small velocity is amplified upon the velocity scaling and is inconsistent with the
-advection-diffusion equation leading to the instability after many iterations.
-
-Thus, before performing the mass transfer simulations one additional single phase hydrodynamic
-simulation is performed. An additional free-surface solver was developed in order to obtain velocity field
+advection-diffusion equation leading to instability after many iterations.
+
+Thus, before performing the mass transfer simulations an additional single phase hydrodynamic
+simulation is performed. A free-surface solver was developed in order to obtain velocity field
 consistent with the advection-diffusion equation. We take results from the
@@
 bubble shape using the phase indicator $\phi\leq0$, and approximate the bubble shape by the stair-case
-line. The obtained bubble velocity is then imposed on the walls. This corresponds to conducting the
-simulation in the reference frame moving with the bubble. In addition, the free-slip boundary
-condition on the bubble surface is imposed. Appendix \ref{appendix-free-surface} covers the simple
+line with imposed free-slip boundary condition on it. The obtained bubble velocity is then imposed on the walls. This corresponds to conducting 
+simulations in the reference frame moving with the bubble. Appendix \ref{appendix-free-surface} covers the simple
 free-slip boundary condition implementation drastically improving velocity patterns. The system is
 iterated until a
-steady state is reached. Note, that these type of simulations are much faster than original
+steady state is reached. Note, that these type of simulations are much faster than the original
 multiphase simulations. As the output all the non-zero velocity components perpendicular to the
@@
 \includegraphics[angle=90,width=\textwidth]{Figures/performed_ca1040_out.eps}
-\caption{The streamlines patterns produced by the free-surface solver with simplistic approximation
+\caption{The streamline patterns produced by the free-surface flow solver with simplified approximation
 of the free-slip bubble surface, see Appendix \ref{appendix-free-surface}. Two completely different
-velocity patterns are covered, $Ca=0.097$ (top) and $Ca=1.040$ (bottom).
+velocity patterns are obtained, $Ca=0.097$ (top) and $Ca=1.040$ (bottom).
 \label{fig:streamlines:tweaked:velocity}}
@@
 \item[Mass transfer] After improved velocity profiles are obtained one can perform any mass
-transfer simulations with different boundary conditions as covered in Section \ref{section:cases}.
+transfer simulations with the various boundary conditions as covered in Section \ref{section:cases}.
 For this purpose one needs to match the Peclet number $Pe$ taken from experiments. Note that we
@@
 This section covers simulation results. We first examine the possibility to increase the fluid
-velocity while keeping the Peclet number the same. After the periodic boundary
+velocity while keeping the Peclet number the same. After that  the periodic boundary
 conditions for $5$ capillary number cases will be presented. Finally, we will examine
 many
-cell simulations for two representative cases of velocity patterns, $Ca=0.0907$ and $Ca=1.04$
+cell simulations for two representative velocity patterns related to $Ca=0.0907$ and $Ca=1.04$ respectively 
 (see Fig. \ref{fig:streamlines:tweaked:velocity}).
 
-\subsection{Keeping the Peclet number constant}
+\subsection{Velocity scaling at constant Peclet number}
 \label{section:keeping:peclet}
@@
 their corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
-boundary conditions were used and mass transfer coefficient was calculated according to Eq.
+boundary conditions were used and the mass transfer coefficient was calculated according to Eq.
 \ref{main:simulation:equation}. Table \ref{table:scaling:peclet} shows that the velocity limit
-for  periodic boundary conditions is $0.1$. %if  when $\omegaminus=1.99$ ($D=0.000837$). 
-It gives us the
+for  periodic boundary conditions is $0.1$.
+That means that to be on the safe side one shouldn't scale up velocities to obtain them larger than $0.1$.
+For example, in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  one can scale up velocity significantly ($20-40$ times) to obtain velocity around $0.2$ where simulations are still stable.
+However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is smaller than $0.1$ .
+%if  when $\omegaminus=1.99$ ($D=0.000837$).
+It gives us a
 preliminary idea to what extent one can scale periodic mass transfer simulations. 
@@
 \end{tabularx}
-\caption{This table presents the achievable stable velocity $\ububble$ when one scales velocity. Since
+\caption{Indications of the achievable stable velocity $\ububble$ when one scales velocity. Since
 the physical time step represented by a single iteration of the simulation is directly proportional
@@
 Note that time iterations
-indicated in the table correspond to physical time. One can see that
-scaling produces adequate results.  The achievable stable velocity is around $U_{bubble}=0.1$. Average concentrations are in reasonable agreement. The contour
+indicated in the table correspond to the same moment in physical time. One can see that
+scaling produces adequate results when $C_{aver}$ is compared.  
+%The achievable stable velocity is around $U_{bubble}=0.1$. Average concentrations are in reasonable agreement. 
+The contour
 profiles for all of these cases (capillary number $Ca$ and all scales) are presented in Fig.
@@
 velocity scalings are presented in Fig. \ref{fig:contours:scaling:peclet}. One can see an
-acceptable agreement between all of them. Note, that the speedup can be up to $10$ to $40$ times
-higher.
+acceptable agreement between the cases with the same Peclet number but different velocity scalings. Note, that the speedup can be up to $10$ to $40$ times.
 \begin{figure}[htb!]
@@
 all different scales indicated in Table
-\ref{table:scaling:peclet}. Agreement is reasonable. \label{fig:contours:scaling:peclet}}
+\ref{table:scaling:peclet} (top to bottom: 6 scalings, 5 scalings, 2 scalings, 1 scaling, 1 scaling). \label{fig:contours:scaling:peclet}}
 \end{figure}
 
-\subsection{Average concentration}
+\subsection{Average concentration results}
 \label{main:results:periodic}
-As indicated in Section \ref{section:cases} one can calculate the average domain concentration over
-the time. Eq. \ref{theor:one:concentration:time} shows how 
-the volumetric mass transfer coefficient depends on
-time, i.e. streamwise coordinate:
-\beqal
-&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{\cstar}{\cstar-\langle C(t) \rangle}\\
-&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-\langle C(t)
-\rangle},\\
-\feqal
-where $\langle C(t) \rangle$ is the average concentration in the liquid domain.
-Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
+In this section we will examine the case where the volume averaged concentration over
+ time is used as the characteristic concentration. To calculate the volumetric mass transfer coefficient we used Eq. \ref{theor:one:concentration:time}.
+%\beqal
+%&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{\cstar}{\cstar-\langle C(t) \rangle}\\
+%&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-\langle C(t)
+%\rangle},\\
+%\feqal
+%where $\langle C(t) \rangle$ is the average concentration in the liquid domain.
+Results for the coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
 \ref{fig:aver:conc:different:capillaries:time} for different Peclet numbers and velocity scalings
-indicated in Table \ref{table:scaling:peclet}. When the average concentration goes
+indicated in Table \ref{table:scaling:peclet}. When the average concentration gets
 close to $\cstar=1$ then Eq. \ref{theor:one:concentration:time} gives inadequate results due to
- accuracy of the logarithmic function. Fig. \ref{fig:aver:conc:different:capillaries:time} presents
-the volumetric mass transfer coefficient against number of iterations. However, due to scaling
-each simulation has a different physical time step. We scaled curves against number of cell
+ accuracy of the logarithmic function evaluation. 
+ %Fig. \ref{fig:aver:conc:different:capillaries:time} presents
+%the volumetric mass transfer coefficient as a function of number of iterations. 
+Due to velocity scaling
+each simulation has a different physical time step. Thus, we normalized time such that it represents a number of cell
 units which tracer will pass with the given bubble velocity, i.e. 
@@
 \ref{table:steady:state:average} that for different Peclet numbers different time (number of unit
-cells) is required to achieve the steady state. For example, for
+cells) is required to achieve  steady state. For example, for
 larger Peclet numbers fewer iterations are required to achieve the steady state condition.
 
-Overall one is guaranteed to obtain the steady state volumetric mass transfer coefficient for
+Overall one obtains the steady state volumetric mass transfer coefficient for
 periodic boundaries simulations if the following conditions are fulfilled:
@@
 \item[II] The larger the Peclet number, the fewer iterations are required. One can extrapolate data from Table
-\ref{table:steady:state:average}, say $L_{\mathrm{steady}}$ and estimate the  number of
+\ref{table:steady:state:average}, say $L_{\mathrm{steady}}$, and estimate the  number of
 iterations to reach the steady-state as $\mathrm{scale}\cdot \ububble\cdot N_{\mathrm{iter}}\leq L_{\mathrm{steady}}$. 
@@
 the achieved steady state volumetric mass transfer coefficient. 
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time054.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time026.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time05.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time14.eps}
-\caption{Calculated volumetric mass transfer coefficient for different capillaries and scales
-against time. One can see
-that all curves have the same minimum corresponding to the volumetric mass transfer coefficient.
-Some simulations show the volumetric mass transfer coefficient going up due to the average
-concentration being close to $\cstar$. All of them show an excellent agreement. Note, that with the
-velocity scaling one can reduce the amount of calculations drastically. However, one needs to be attentive
-because with large velocity scaling average concentration can quickly approach $\cstar$, thus
-getting an infinite volumetric mass transfer coefficient.
-\label{fig:aver:conc:different:capillaries:time}}
-\end{figure}
+%\begin{figure}[htb!]
+%\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time097.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time054.eps}\\
+%\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time026.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time05.eps}\\
+%\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca_time14.eps}
+%\caption{Calculated volumetric mass transfer coefficient for different capillaries and scales
+%against time. One can see
+%that all curves have the same minimum corresponding to the volumetric mass transfer coefficient.
+%Some simulations show the volumetric mass transfer coefficient going up due to the average
+%concentration being close to $\cstar$. All of them show an excellent agreement. Note, that with the
+%velocity scaling one can reduce the amount of calculations drastically. However, one needs to be attentive
+%because with large velocity scaling average concentration can quickly approach $\cstar$, thus
+%getting an infinite volumetric mass transfer coefficient.
+%\label{fig:aver:conc:different:capillaries:time}}
+%\end{figure}
 \begin{figure}[htb!]
@@
 \includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}
-\caption{Volumetric mass transfer coefficient for different capillaries and scales against the
+\caption{Volumetric mass transfer coefficient for different capillary numbers and scales against the
 bubble travel distance in the laboratory frame. ''Cell Units`` axis refers to the physical
-distance of how many unit cells the bubble passes until the steady state is reached. Table
+distance of how many unit cells the bubble passes until the steady state is reached. Legend is provided for velocity scalings. All of them show a good agreement. Table
 \ref{table:steady:state:average}
-summarizes results.\label{fig:aver:conc:different:capillaries}}
+summarizes results presented here.
+One can see abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
+\label{fig:aver:conc:different:capillaries}}
 \end{figure}
@@
 \caption{The distance which a bubble propagates when the
-steady-state condition is achieved. One can see that increasing
-Peclet number helps to achieve the steady state faster.\label{table:steady:state:average}}
+steady-state condition is achieved. 
+%One can see that increasing Peclet number helps to achieve the steady state faster.
+\label{table:steady:state:average}}
 \end{table}
@@
 \subsection{Periodic boundaries with the inlet/outlet characteristic concentration}
-\label{results:periodic:inlet:outlet} The volumetric mass transfer coefficient
+\label{results:periodic:inlet:outlet} 
+The volumetric mass transfer coefficient
 was calculated using Eq. \ref{theor:one:concentration:time} with the
@@
 as used by \citet{vanbaten-circular}. One can see in Fig.
-\ref{fig:volumetric:char:concentration:vanbaten} the calculated volumetric mass
-transfer is different from the domain averaged calculated volumetric mass
+\ref{fig:volumetric:char:concentration:vanbaten} that the calculated volumetric mass
+transfer behave differently from the domain averaged  volumetric mass
 transfer coefficient. For example, for small capillary numbers, i.e.
-$Ca=0.097,0.254,0.526$ the predicted values are overpredicted
+$Ca=0.097,0.254,0.526$ the values are overpredicted
 ($\volnondim=0.3,0.25,0.1$). When the velocity pattern is changed from having
@@
 the bubble to not having it,  i.e. $Ca=0.75,1.04$ the calculated values
-are underpredicted in contrast to the previous case, i.e. $\volnondim=0.06,0.04$. As we will see later, the domain-averaged characteristic concentration produces proper results. 
+are underpredicted compared to estimates based on volume-averaged concentration, i.e.
+$\volnondim=0.06,0.04$.
+As we will see later, the domain-averaged characteristic concentration produces proper mass transfer coefficients.
 \begin{figure}[htb!]
@@
 
-\subsection{\citeauthor{vanbaten-circular} formulation}
+\subsection{Van Baten and Krishna formulation}
 \label{results:vanbaten}
-The van Baten formulation, Eq. \ref{eq:vanbaten:formulation}, is calculated as
-the change of mass in domain divided by the time difference. We examined two
+The \citet{vanbaten-circular} formulation, Eq. \ref{eq:vanbaten:formulation}, is calculated as
+the change of mass in the domain divided by the time difference. We examined two
 approaches:  the characteristic concentration taken to be as the domain average
 and as the flux-averaged input/output concentration. The latter case
-corresponds to the work \cite{vanbaten-circular}. The results are presented in
+corresponds to  \cite{vanbaten-circular}. The results are presented in
 Fig. \ref{fig:vanbaten} for $Ca=0.097$ and $Ca=1.04$. One can see that the
-inlet/outlet flux averaged concentration is shown to be inconsistent. The
+inlet/outlet flux averaged concentration is inconsistent. The
 reason that \citet{vanbaten-circular} obtained the mass transfer coefficient
-close to the analytical estimation is that the liquid slug is well mixed so that
+close to the analytical estimation is that the liquid slug is well mixed ($Ca<0.1$ which is below the range studied here) so that
 the averaged concentration is close to the inlet/outlet concentration.
@@
 $Ca=0.0097$ has the same value as for the simulations of a few unit cells.
-Therefore this approach produces most accurate results but requires the results
-in time and space to calculate the mass change in time and the averaged domain
+Therefore the approach of \citet{vanbaten-circular} produces most accurate results but with the characteristic concentration being the volume-averaged concentration (not the inlet/outlet flux-averaged concentration used in the original work).
+From the computational point of view, it also requires the concentration fields in time and space to calculate the mass change in time and the averaged domain
 characteristic concentration.
@@
 simulations in Section \ref{main:results:periodic}. However, the characteristic concentration
-being inlet/outlet flux-averaged does not produce consistent results as in Section
-\ref{results:periodic:inlet:outlet}.
+being inlet/outlet flux-averaged does not produce consistent results.
 \label{fig:vanbaten}}
@@
 In order to achieve independence from the boundary conditions and a closer match with
-the physical system being modeled, one can simulate several unit cells, corresponding
-to a bubble train head.  If boundaries are eliminated then the average
+the physical system being modelled, one can simulate several unit cells, corresponding
+to a head of the bubble train.  If boundaries are eliminated then the average
 domain characteristic should change in time according to Eq.
@@
 This section studies the number of unit cells required for the volumetric
-mass transfer coefficient to be independent of boundaries. We chose two
+mass transfer coefficient to be independent of boundaries influence. We chose two
 different
@@
 $4$, $6$, $8$, $10$ cells, and for $Ca=1.040$ only with $4$, $6$, $8$ cells.
-The final run for 10 cells was skipped due to limited computational resources.
+%The final run for 10 cells was skipped due to limited computational resources.
 % TODO: how do we know that this holds true regardless of the Ca number?
@@
 We keep velocity in the range $0.05-0.1$ to avoid excessively long simulation times.
-The number of steps for mass to cross the whole domain is
-limited from above by $1.5 \frac{\lunit}{\ububble}$, which takes into account the bulk
+The number of steps for mass to pass through the whole domain can be approximated as $1.5 \frac{\lunit}{\ububble}$, which takes into account the bulk
 velocity. If $\ububble$ is taken as $0.05$ then for
@@
 for a system consisting of $10$ unit cells. For more accurate estimations of number of time
-iterations depending on the Peclet number one can refer to Section \ref{section:keeping:peclet}.
+iterations depending on the Peclet number we refer to Section \ref{section:keeping:peclet}.
 
@@
 the unit cell with time (see Eq. \ref{theor:continuous:mass:transfer}), and the accumulated mass
-rate in the domain adjusted with inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
-resembles the experimental picture: if one has enough unit cells, then the averaged domain
+rate in the domain which takes into the account inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
+resembles experiments: if one has enough number of unit cells, then the averaged domain
 concentration should change in time according to Eq. \ref{theor:continuous:mass:transfer}: 
@@
 The non-dimensional volumetric mass transfer coefficient calculated based on Eq.
-\ref{moving:average} (domain-averaged concentration changes in time) is
-represented in Fig. \ref{fig:moving:average:ca0097} for different unit cells. One can see that the
-results are consistent with the mass flux
-concentration based on \citeauthor{vanbaten-circular} formulation with the characteristic
-concentration being domain-averaged concentration (see Section
-\ref{results:vanbaten}). This proves two things:  the domain-averaged
+\ref{moving:average} (domain-averaged concentration change in time) is
+represented in Fig. \ref{fig:moving:average:ca0097} for different unit cells. One can see that mass transfer coefficient values are the same as the mass flux
+concentration based on the \citeauthor{vanbaten-circular} formulation with the characteristic
+concentration being the domain-averaged concentration (see Section
+\ref{results:vanbaten}). This demonstrates two things:  the domain-averaged
 concentration is the only choice for the characteristic concentration, and
@@
 \volnondim=\frac{\lunit}{\ugas+\ububble} \frac{V \frac{\langle C(t_2)\rangle - \langle C(t_1)
-\rangle}{t_2-t_1}}{\dots}\\
+\rangle}{t_2-t_1}}{}\\
 \frac{-\int{\coutlet(\lunit,y,t^*) u(\lunit,y) \mathrm{d} y}+\int{\cinlet(0,y,t^*)
@@
 \feq
-where $t^*$ is the medium time between $t_1$ and $t_2$.
+where $t^*$ is the mean between $t_1$ and $t_2$.
 %TODO: what is a medium time?  is it just the mean of the two times?
@@
 Eq.~\ref{main:main:main:thorough} calculated for each unit for velocity
-scale $10$ and  $6$ unit cells (all velocity scales produce same results). It is shown that the
-volumetric mass transfer cofficient is consistent for internal segments, i.e.
-unit cells $3-5$.  The results for the volumetric mass transfer
+scale $10$ and  $6$ unit cells (all velocity scales produce the same results). It is shown that the
+volumetric mass transfer coefficient is consistent for internal segments, i.e.
+unit cells numbers $2-4$.  The results for the volumetric mass transfer
 coefficient calculated by Eq. \ref{main:main:main} for a multiple unit cells are
-close to results for periodic boundary conditions in Section
-\ref{main:results:periodic}. 
+close (less than $10\%$ deviation) to results for periodic boundary conditions in Section
+\ref{main:results:periodic} . 
 %However, they are even closer to results calculated by approach of \citeauthor{vanbaten-circular} with the domain averaged characteristic concentration. 
@@
 $8$ and $10$ unit cells simulations but we do not present them here. We also do not present $4$
-units cells simulation results which are influenced by inlet and outlet boundaries.
+units cells simulation results which are much influenced by inlet and outlet boundaries.
 
@@
 this equation can be significantly simplified in case of larger capillary
-numbers $Ca>0.7$.
+numbers ($Ca>0.7$).
 
@@
 \subsection{$Ca=1.040$ results}
-The same correlations were examined for a different velocity pattern $Ca=1.040$.%, initial
+The same correlations were examined for a different velocity pattern $Ca=1.040$. %, initial
 %velocity $\ububble=0.055$, initial diffusion $D=0.0008375$. If only velocity scaling is
@@
 %this capillary number  are unstable. 
-
-%TODO: I'm not sure what this sentence means here on its own..
-A few unit cells simulations with the original Peclet number $Pe=14041$.
+The original Peclet number we started with is $Pe=14041$ (Table \ref{table:scaling:peclet}).
 To improve stability we changed the original Peclet number by increasing
-diffusion to $Pe=2644$. The results for unit cells are the same as for $Ca=0.097$:
-at least $6$ unit cells are required to be simulated to avoid the influence of boundaries. Thus,
+diffusion to $Pe=2644$. The results with respect to the number of unit cells are the same as for $Ca=0.097$:
+at least $6$ unit cells are required to avoid the influence of boundaries. Thus,
 only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040} which shows the
-average concentration for each unit cell. One can see that the average volume concentration for each unit cell comes to
-a constant value and is not increasing with time. Thus, all the
-mass generated with medium is transferred through the boundaries. This indicates that the
-liquid slug is unmixed. Note that the periodic boundary conditions cannot show whether the
+average concentration for each unit cell. One can see that the average volume concentration for each unit cell converges to
+a constant value. Thus, all the
+mass generated by the bubble is transferred through the boundaries. This indicates that the
+liquid slug is unmixed since no concentration travels back to inlet with the vortex and increases the average concentration in each unit cell.
+Note that the periodic boundary conditions cannot show whether the
 liquid slug is mixed or not due to the fact that the averaged domain concentration always increases in time. 
-Thus, the volumetric mass tranun coefficient $\volnondim$ can be calculated according to the
+Thus, the volumetric mass transfer coefficient $\volnondim$ can be calculated according to the
 definition, Eq. \ref{main:main:main}:
@@
 the calculated volumetric mass transfer coefficient using the time averaged approach and periodic
-boundaries one unit cell simulations presented in the same figure for comparison.
+boundaries one unit cell simulations (presented in the same figure for comparison).
 \begin{figure}[htb!]
@@
 One can see that average concentrations reach certain value and stay constant.
-That means whatever was
-generated by medium is transferred through the outlet
-boundary. This indicates that the tracer in the slug is not
-mixed and the volumetric mass transfer coefficient, $\volnondim$, can be
+%That means whatever was
+%generated by medium is transferred through the outlet
+%boundary. This indicates that the tracer in the slug is not
+%mixed and t
+Thus, the volumetric mass transfer coefficient, $\volnondim$, can be
 calculated using the spatial approach, see Fig.
-\ref{fig:periodic:ca1040}.\label{fig:6:units:ca1040}}
+\ref{fig:periodic:ca1040}.
+\label{fig:6:units:ca1040}}
 \end{figure}
@@
 Note
-that all approaches coincide and therefore, for certain hydrodynamic patterns ($Ca>0.7$), one can
-easily convert time domain to spatial domain calculations.
+that results for approaches which incorporate the volume-averaged characteristic concentration either for one cell or a few unit cells coincide between each other.
+Therefore, for certain hydrodynamic patterns ($Ca>0.7$), one can
+easily convert time domain to spatial domain calculations using a few unit cells simulations.
 \begin{figure}
@@
 \feqal
-One can see that approximately the volumetric mass transfer correlation should be proportional to
+One can see that  the volumetric mass transfer correlation should be approximately proportional to
 $Pe^{-0.5}$.  One can also use analytical estimates of the volumetric mass transfer
-coefficient calculated using the Higbie penetration theory \cite{higbie}. One can derive by following the works
-\cite{irandoust,vanbaten-circular} that the analytical expression for the flow between plates has
-the following form:
+coefficient calculated using the Higbie penetration theory \cite{higbie}.
+One can derive the analytical expression for the mass transfer for bubble train flow between parallel plates by following the works
+\cite{irandoust,vanbaten-circular}:
 \beq
@@
 \feq
-where $H$ is the channel height, and $\delta$ is the film thickness.
-
-Fig. \ref{fig:volume:mass:coefficient} shows a comparison between a correlation by
+where $H$ is the channel height, and $\delta$ is the non-dimensional film thickness (in channel heights).
+
+Fig. \ref{fig:volume:mass:coefficient} shows a comparison between the correlation by
 \citet{yue-mass}, the analytical expression, Eq. \ref{vanbaten:analytical:expresssion}, and the current
-simulation coefficients presented in Table
+simulation results presented in Table
 \ref{table:steady:state:average}. The coefficients are close to each other, especially given that
-the correlation by \citet{yue-mass} is for three-dimensional cases. The fitting procedure showed
+the correlation by \citet{yue-mass} is for three-dimensional cases. The fitting procedure for this work results showed
 that the power of
-the Peclet number $Pe$ is $-0.50038$ which is close to $-0.5$. 
+the Peclet number dependence  is $-0.50038$ which is close to the theoretical value $-0.5$. 
 \begin{figure}[htb!]
@@
 to all correlations. One can as well see that the deviation from the analytical expression becomes
-larger with the increasing Peclet number $Pe$, which happens because the analytical expression does
+larger with the increasing Peclet number, which happens because the analytical expression does
  not account for the velocity pattern and the bubble shape change.\label{fig:volume:mass:coefficient}}
@@
 
-\section{Conclusion}
+\section{Summary}
 This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
@@
 conditions simulations and calculate the volumetric mass transfer coefficient based on the averaged
-domain concentration through any formulation as they produce consistent results. The best accuracy
+domain concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, a few unit cells simulations) as they produce consistent results. The best accuracy
 is achieved with formulations based on the mass difference or on the averaged domain concentrations
@@
 \ref{theor:average:concentration:time} gives a slightly overestimated volumetric mass transfer
-coefficient. The original formulation of
+coefficients (less than $10\%$). The original formulation of
 \citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
 to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
-have indicator of how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
+indicate of how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
 0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
@@
 \appendix
-\section{Analytical solution for parabolic profile with zero velocity gradient at $0$}
-\label{appendix:zero:gradient}
-The problem is defined in terms of PDE as follows: 
-\beq
-\label{diffusion:zero:gradient:start}
-\begin{aligned}
-&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
-&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
-&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
-\end{aligned}
-\feq
-The non-dimensional parameters are introduced:
-\beq
-\begin{aligned}
-&\frac{\partial C}{\partial \frac{x}{\delta}} \frac{U_0}{\delta}
-\Bigl(\frac{y}{\delta}\Bigr)^2=\frac{D}{\delta^2}\frac{\partial^2 C}{\partial
-\frac{y^2}{\delta^2}}\\
-&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
-\end{aligned}
-\feq
-After a change of variables:
-\beq
-\begin{aligned}
-&\zeta=\frac{x}{\delta} \frac{D}{U_0 \delta}=\frac{1}{Pe}\frac{x}{\delta}\\
-&\xi=\frac{y}{\delta},
-\end{aligned}
-\feq 
-Eq. \ref{diffusion:zero:gradient:start} with boundary conditions becomes as follows:
-\beq
-\label{diffusion:zero:gradient:middle}
-\begin{aligned}
-&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
-&C(0,\xi)=C_0\\
-&C(\zeta,0)=\cstar\\
-&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
-\end{aligned}
-\feq 
-Still Eq. \ref{diffusion:zero:gradient:middle} cannot be solved with the separation of variables as it requires homogenous
-boundary conditions. Thus, let us introduce the new variable, $\Theta=C-\cstar$, which makes the system have homogenous boundary conditions:
-\beq
-\begin{aligned}
-&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
-&\Theta(0,\xi)=C_0-\cstar \\
-&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
-\end{aligned}
-\feq 
-This equation can be solved by separation of variables if the solutions are assumed to factorize as
-$\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$:
-\beq
-\begin{aligned}
-&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
-Y(\xi)}{\mathrm{d}\xi^2}\\
-&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
-\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
-\end{aligned}
-\feq
-The left and right parts depend on different variables. Therefore to be equal to each other both
-parts shall equal to a constant, say $-m^4$. The separation of variables leads to two ODEs:
-\begin{equation*}
-\begin{aligned}
-&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
-&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
-\end{aligned}
-\end{equation*}
-The solution of the first equation is the exponential function:
-\beq
-X(\zeta)=\exp(-m^4 \zeta)\\
-\feq
-The solutions of the second equation are two hypergeometric function which can be expressed through
-the Bessel functions \cite{abramowitz}:
-\beq
-\begin{aligned}
-&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
-\end{aligned}
-\feq
-The solution is the summation of two functions:
-\begin{equation*}
-Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
-\end{equation*}
-One can find coefficients from the boundary conditions:
-\beq
-\begin{aligned}
-&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
-&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
-&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
-&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
-\end{aligned}
-\feq
-Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
-numerical values:
-$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
-Therefore, the solution in a general form is represented as:
-\beq
-\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
-\feq
-To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
-condition:
-\beq
-\Theta(0,\xi)=C_0-\cstar=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)}\\
-\feq
-Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
-J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
-\beq
-\begin{aligned}
-&\bigl(C_0-\cstar\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
-&C_m = (C_0-\cstar ) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}
-\end{aligned}
-\feq
-Therefore, the overall solution is specified as:
-\beq
-\begin{aligned}
-&C(x,y)=\cstar+\sum_{m}{C_m
-\sqrt{\frac{y}{\delta}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{\delta^2}\Bigr)\exp\Bigl(-\frac{
-m^4 } { Pe }
-\frac { x }{\delta}\Bigr)}\\
-&C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
-\xi^2}{2}\Bigr)\mathrm{d}\xi}}
-\end{aligned}
-\feq
-For the sake of completeness, we list $5$ first coefficients for a case $C_0=0$ and $\cstar=1$:
-$C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
+%\section{Analytical solution for parabolic profile with zero velocity gradient at $0$}
+%\label{appendix:zero:gradient}
+%The problem is defined in terms of PDE as follows: 
+%\beq
+%\label{diffusion:zero:gradient:start}
+%\begin{aligned}
+%&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
+%&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+%&U(y)=U_0 \Bigl(\frac{y}{\delta}\Bigr)^2
+%\end{aligned}
+%\feq
+%The non-dimensional parameters are introduced:
+%\beq
+%\begin{aligned}
+%&\frac{\partial C}{\partial \frac{x}{\delta}} \frac{U_0}{\delta}
+%\Bigl(\frac{y}{\delta}\Bigr)^2=\frac{D}{\delta^2}\frac{\partial^2 C}{\partial
+%\frac{y^2}{\delta^2}}\\
+%&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
+%\end{aligned}
+%\feq
+%After a change of variables:
+%\beq
+%\begin{aligned}
+%&\zeta=\frac{x}{\delta} \frac{D}{U_0 \delta}=\frac{1}{Pe}\frac{x}{\delta}\\
+%&\xi=\frac{y}{\delta},
+%\end{aligned}
+%\feq 
+%Eq. \ref{diffusion:zero:gradient:start} with boundary conditions becomes as follows:
+%\beq
+%\label{diffusion:zero:gradient:middle}
+%\begin{aligned}
+%&\frac{\partial C}{\partial \zeta}\xi^2=\frac{\partial^2 C}{\partial \xi^2}\\
+%&C(0,\xi)=C_0\\
+%&C(\zeta,0)=\cstar\\
+%&\frac{\partial C}{\partial \xi}(\zeta,1)=0\\
+%\end{aligned}
+%\feq 
+%Still Eq. \ref{diffusion:zero:gradient:middle} cannot be solved with the separation of variables as it requires homogenous
+%boundary conditions. Thus, let us introduce the new variable, $\Theta=C-\cstar$, which makes the system have homogenous boundary conditions:
+%\beq
+%\begin{aligned}
+%&\frac{\partial \Theta}{\partial \zeta}=\frac{1}{\xi^2}\frac{\partial^2 \Theta}{\partial \xi^2}\\
+%&\Theta(0,\xi)=C_0-\cstar \\
+%&\Theta(\zeta,0)=0,\, \partial_{\xi}\Theta(\zeta,1)=0\\
+%\end{aligned}
+%\feq 
+%This equation can be solved by separation of variables if the solutions are assumed to factorize as
+%$\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$:
+%\beq
+%\begin{aligned}
+%&\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}Y(\xi)=\frac{X(\zeta)}{\xi^2}\frac{\mathrm{d^2}
+%Y(\xi)}{\mathrm{d}\xi^2}\\
+%&\frac{1}{X(\zeta)}\frac{\mathrm{d} X(\zeta)}{\mathrm{d} \zeta}=\frac{1}{\xi^{2} Y(\xi)}
+%\frac{\mathrm{d^2} Y(\xi)}{\mathrm{d}\xi^2}
+%\end{aligned}
+%\feq
+%The left and right parts depend on different variables. Therefore to be equal to each other both
+%parts shall equal to a constant, say $-m^4$. The separation of variables leads to two ODEs:
+%\begin{equation*}
+%\begin{aligned}
+%&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}=-m^4 X(\zeta)\\
+%&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 \xi^2 Y(\xi)=0\\ 
+%\end{aligned}
+%\end{equation*}
+%The solution of the first equation is the exponential function:
+%\beq
+%X(\zeta)=\exp(-m^4 \zeta)\\
+%\feq
+%The solutions of the second equation are two hypergeometric function which can be expressed through
+%the Bessel functions \cite{abramowitz}:
+%\beq
+%\begin{aligned}
+%&Y_1=\sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+%&Y_2=\sqrt{\xi}J_{-\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+%&Y'_1=m^2 \xi^{3/2} J_{-\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+%&Y'_2=m^2 \xi^{3/2} J_{\frac{3}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)\\
+%\end{aligned}
+%\feq
+%The solution is the summation of two functions:
+%\begin{equation*}
+%Y(x)=C_1 Y_1(x)+C_2 Y_2(x). 
+%\end{equation*}
+%One can find coefficients from the boundary conditions:
+%\beq
+%\begin{aligned}
+%&Y(0)=0=C_1 Y_1(0)+C_2 Y_2(0)\\
+%&Y_1(0)=0,\,Y_2(0)=\frac{\sqrt{2}}{\sqrt{m} \Gamma(3/4)}\, C_2=0\\
+%&Y'(1)=0=C_1 Y'_1(1)+C_2 Y'_2(1)=C_1 Y'_1(1)\\
+%&J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)=0
+%\end{aligned}
+%\feq
+%Therefore one needs to find zeros of $J_{-\frac{3}{4}}\Bigl(\frac{m^2}{2}\Bigr)$. To give some
+%numerical values:
+%$m_1=1.454997085$, $m_2=2.927133004$, $m_3=3.857578101$, $m_4=4.601777732$, $m_5=5.240824067$.
+%Therefore, the solution in a general form is represented as:
+%\beq
+%\Theta(\zeta,\xi)=\sum_m{C_m \sqrt{\xi} J_{\frac{1}{4}}\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\exp(-m^4 \zeta)}
+%\feq
+%To find unknown coefficients $C_m$ one needs to substitute the expression above to the initial
+%condition:
+%\beq
+%\Theta(0,\xi)=C_0-\cstar=\sum_m{C_m \sqrt{\xi}J_{\frac{1}{4}}\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)}\\
+%\feq
+%Using the Stourm-Liouville theorem one can multiply by $\xi^{5/2}
+%J_{\frac{1}{4}}\Bigl(\frac{m^2 \xi^2}{2}\Bigr)$ and integrate left and right parts of the equation:
+%\beq
+%\begin{aligned}
+%&\bigl(C_0-\cstar\bigr) \int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}=C_m\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}\\
+%&C_m = (C_0-\cstar ) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+%\end{aligned}
+%\feq
+%Therefore, the overall solution is specified as:
+%\beq
+%\begin{aligned}
+%&C(x,y)=\cstar+\sum_{m}{C_m
+%\sqrt{\frac{y}{\delta}}J_{\frac{1}{4}}\Bigl(\frac{m^2}{2}\frac{y^2}{\delta^2}\Bigr)\exp\Bigl(-\frac{
+%m^4 } { Pe }
+%\frac { x }{\delta}\Bigr)}\\
+%&C_m = (C_0-\cstar) \frac{\int_{\xi=0}^{1}{\xi^{5/2} J_{\frac{1}{4}}\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{\xi^3 J_{\frac{1}{4}}^2\Bigl(\frac{m^2
+%\xi^2}{2}\Bigr)\mathrm{d}\xi}}
+%\end{aligned}
+%\feq
+%For the sake of completeness, we list $5$ first coefficients for a case $C_0=0$ and $\cstar=1$:
+%$C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
 \section{The Poiseuille parabolic profile}
@@
 $c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.  
-
-% TOOD: for completeness, this picture shoudl probably include other fluid nodes as well?
 \begin{figure}
@@
 \caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
-Boundary nodes are depicted by crosses, and fluid nodes are represented by circles.
+Boundary nodes are depicted by crosses, and fluid nodes are represented by dots.
 The populations at the corner boundary nodes are 

### 2012-07-16 Benchmarks/FullProfile/film.cpp

@@ -124,10 +124,10 @@ void initialize_geometry()
     		rho[counter]=0.0;
     		ux[counter]=0.0;
     		double factor=double(iX-0.5)/double(NX-1.5);
-    		if (iX<NX/2)
-                    uy[counter]=4.0*u0*factor*factor;//4.0*u0*(1.0-factor)*factor;
-                else
-                    uy[counter]=4.0*u0*(1.0-factor)*(1.0-factor);
+    		//if (iX<NX/2)
+                    uy[counter]=4.0*u0*(1.0-factor)*factor;//4.0*u0*factor*factor;//
+                //else
+                //    uy[counter]=4.0*u0*(1.0-factor)*(1.0-factor);
     		if ((iX==0) || (iX==NX-1))
     			uy[counter]=0.0;
     	}

### 2012-07-16 Python/benchmarks.py

@@ -966,11 +966,13 @@ def final_comparison():
     
     fig=pylab.figure(figsize=(18,5))
     plt=pylab.subplot(1,1,1)    
+    #c1=pylab.contour(conc_antibb,levels=c_levels,colors=['k'],linewidths=[2],extent=(0.0,40.0,-1.0,1.0))
     c1=pylab.contour(conc_antibb,levels=c_levels,colors=['k'],linewidths=[2],extent=(0.0,20.0,0.0,1.0))
     pylab.clabel(c1,fontsize=9, inline=1)    
     #pylab.figure(figsize=(10,1))
     #c2=pylab.contour(conc_inamuro,levels=c_levels,extent=(0.0,20.0,0.0,1.0))
     #pylab.clabel(c2,fontsize=9, inline=1)
+    #pylab.contour(c,levels=c_levels,linestyles="dotted",colors=['k'],linewidths=[2],extent=(0.0,40.0,-1.0,1.0))
     pylab.contour(c,levels=c_levels,linestyles="dotted",colors=['k'],linewidths=[2],extent=(0.0,20.0,0.0,1.0))
     #plt.annotate("local max", xy=(5, 0.5), xytext=(6, 0.7),arrowprops=dict(facecolor="black", shrink=0.05),)
     #plt.text(15, 0.8, "boxed italics text \n in data coords",bbox={"facecolor":"white", "alpha":1.0, "pad":10})
@@ -978,12 +980,12 @@ def final_comparison():
     p1 = pylab.Line2D((0, 1), (0,0),linewidth=2,linestyle="solid",color="k")
     p2 = pylab.Line2D((0, 1), (0,0),linewidth=2,linestyle="dotted",color="k")
     
-    pylab.legend([p1,p2],["AntiBB simulations","Analytics"],fancybox=True)
+    pylab.legend([p1,p2],["Simulations","Analytics"],fancybox=True)
     #pylab.title(r'''$D='''+str(diffusion)[0:6]+'''$''',fontsize=30)
     #pylab.legend(legs,fancybox=True,loc=2)
-    pylab.xlabel(r'''$x$''',fontsize=20)
-    pylab.ylabel(r'''$y$''',fontsize=20)    
-    #fig.subplots_adjust(left=0.2,right=0.8)
+    pylab.xlabel(r'''$\frac{x}{\delta}$''',fontsize=20)
+    pylab.ylabel(r'''$\frac{y}{\delta}$''',fontsize=20)    
+    fig.subplots_adjust(bottom=0.15)
[…]

### 2012-07-21 Text/introduction.tex
A bit of corrections.
Minor fixes in the text.

--- 2012-05-28 Text/introduction.tex
@@
 
-This work is focused on the gas to liquid mass transfer 
+This work is focused on the gas-to-liquid mass transfer 
 study for the Bretherton/Taylor flow. A good understanding of mass transfer and how it depends on the
@@
 
-The understanding of mass transfer for the bubble train flow is not possible without deep understanding of hydrodynamic patterns.
+The understanding of mass transfer for the bubble train flow is not possible without a deep understanding of hydrodynamic patterns.
 There are several works studying the hydrodynamic properties of the bubble train flow, both
@@
 capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape is
-symmetrical and can approximated with good precision. Moreover, because of the
+symmetrical and can be approximated with good precision. Moreover, because of the
 hydrodynamic pattern in the slug (i.e. presence of a vortex in slug), one can
 estimate the time for a fluid batch to travel the whole circumference.   However,
-with the increase of the capillary number the situation drastically changes -- the
+with the increase of the capillary number the situation changes significantly -- the
 symmetrical bubble shape is lost and the bubble shape resembles a bullet \cite{kuzmin-binary2d}.
@@
 to estimate the contribution from bubble caps, which explains the need to turn to numerical simulations where all
-hydrodynamics fields as well as complex bubble shapes are taken into account.
+hydrodynamic fields as well as complex bubble shapes are taken into account.
 
@@
 through analytical correlations \cite{bretherton} or experimental correlations
-\cite{cerro-bubble-train} without directly resolving bubbles shapes through
+\cite{cerro-bubble-train} without directly resolving bubble shapes through
 multiphase simulations.  The expressions for bubble shapes are available only
@@
 using periodic boundary conditions with the same concentration at the inlet
-and at the outlet. The question how one unit cell simulation corresponds to
+and at the outlet. The question is how one unit cell simulation corresponds to
 experimental measurements arises where concentration difference is measured at
-the distances of at least of a few unit cells \cite{bercic-mass}. In
+the distances of at least a few unit cells \cite{bercic-mass}. In
 other words one needs to understand how the discrete one unit cell simulation
@@
 coefficient.
- \item[III] Transition of the continuous experimental picture to
+ \item[III] Translation of the continuous experimental picture to
 numerical simulations of a few unit cells, the issue of correspondence
@@
 patterns. The mass transfer simulations were performed with different boundary
-conditions (open, periodic) and with a few unit cells ($1$ to $10$ unit cells).
+conditions (open, periodic) and with $1$ to $10$ unit cells.
 As our numerical approach we take the lattice Boltzmann method, a relatively
@@
 a bulk velocity or $U=\ugas+\uliq$, where $\ugas$ and $\uliq$ are liquid and gas
-superficial velocities, correspondingly.
+superficial velocities, respectively.
 

### 2012-07-22 Text/introduction.tex

--- 2012-07-16 Text/introduction.tex
@@
 capillary numbers $Ca<0.1$ \cite{bercic-mass} where the bubble shape is
-symmetrical and can approximated with good precision. Moreover, because of the
+symmetrical and can be approximated with good precision. Moreover, because of the
 hydrodynamic pattern in the slug (i.e. presence of a vortex in slug), one can
-estimate the time for a fluid batch to travel the entire circumference.   However,
-with the increase of the capillary number the situation drastically changes -- the
+estimate the time for a fluid batch to travel the whole circumference.   However,
+with the increase of the capillary number the situation changes significantly -- the
 symmetrical bubble shape is lost and the bubble shape resembles a bullet \cite{kuzmin-binary2d}.
-For flows with $Ca>0.7$ there is also no vortex in the liquid slug anymore. The Higbie theory fails
-to estimate the mass transfer from bubble caps, which explains the need to turn to numerical simulations where all
-hydrodynamics fields as well as complex bubble shapes are taken into account.
+For flows with $Ca>0.7$ there is also no vortex in the liquid slug. In this case the Higbie theory fails
+to estimate the contribution from bubble caps, which explains the need to turn to numerical simulations where all
+hydrodynamic fields as well as complex bubble shapes are taken into account.
 
@@
 through analytical correlations \cite{bretherton} or experimental correlations
-\cite{cerro-bubble-train} without directly resolving the bubbles shapes through
+\cite{cerro-bubble-train} without directly resolving bubble shapes through
 multiphase simulations.  The expressions for bubble shapes are available only
@@
 concentration along the streamwise direction changes exponentially with distance.
-Mass transfer simulations however, consider only one unit cell
-using periodic boundary conditions, and thus the same concentration at the inlet
-and at the outlet. The question how one unit cell simulations correspond to
-experimental measurements where concentration differences are measured at
- distances of at least of a few unit cells \cite{bercic-mass}. In
+Mass transfer simulations however, are made only for one unit cell
+using periodic boundary conditions with the same concentration at the inlet
+and at the outlet. The question is how one unit cell simulation corresponds to
+experimental measurements arises where concentration difference is measured at
+the distances of at least a few unit cells \cite{bercic-mass}. In
 other words one needs to understand how the discrete one unit cell simulation
@@
 coefficient.
- \item[III] Transition of the continuous experimental picture to
-numerical simulations with a few unit cells, the issue of correspondence
+ \item[III] Translation of the continuous experimental picture to
+numerical simulations of a few unit cells, the issue of correspondence
 between space averages (simulations \cite{vanbaten-circular}) and time averages (experiment).
@@
 Results for the coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
-\ref{fig:aver:conc:different:capillaries:time} for different Peclet numbers and velocity scalings
+\ref{fig:aver:conc:different:capillaries} for different Peclet numbers and velocity scalings
 indicated in Table \ref{table:scaling:peclet}. When the average concentration gets

### 2012-07-23 Text/introduction.tex
Final fixes in the text.

@@
 as the characteristic concentration. %, Eq. \ref{eq:main:definition}.
-The latter is not valid for flows where tracer is not well mixed, i.e. $Ca>0.7$.  We therefore
+The latter is not valid for flows where the tracer is not well mixed, i.e. $Ca>0.7$.  We therefore
 examine various boundary conditions (periodic, open, open with more than 1 unit cell) and definitions of the characteristic concentration for the range of capillary numbers $0.1<Ca<1.0$.
@@
 transfer from gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.
- Moreover, the low slip velocity between gas and liquid is utilized in the experiments to measure liquid velocity \cite{taylor}:  bubbles
+ Moreover, the low slip velocity between gas and liquid is utilized in experiments to measure liquid velocity \cite{taylor}:  bubbles
  travelling with approximately the same velocity as liquid can be captured with a camera. These properties explain why nowadays one can find a large number of applications
@@
 
-The understanding of mass transfer for the bubble train flow is not possible without a deep understanding of hydrodynamic patterns.
+The understanding of mass transfer for the bubble train flow is not possible without knowledge of hydrodynamic patterns.
 There are several works studying the hydrodynamic properties of the bubble train flow, both
@@
  where $\mu_{\mathrm{liq}}$ is the liquid viscosity, $\ububble$ is the bubble velocity, and $\gamma$ is the interfacial tension.
- The fact that bubble shape for $Ca<0.1$ can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug has been 
+ The fact that the bubble shape for $Ca<0.1$ can be represented as two hemicircles and two planar interfaces with the vortex existing in the liquid slug has been 
 utilized for analytical estimations of mass transfer properties.
@@
 \mathrm{d}A}/\int{\uinoutlet\mathrm{d}A}$ is the space-averaged inlet/outlet (periodic boundary conditions)
-concentration as a function of time. Therefore, in terms of the mass transfer definition, $\langle\cinoutlet(t)\rangle$ plays a role of the 
+concentration as a function of time. Therefore, in terms of the mass transfer definition, $\langle\cinoutlet(t)\rangle$ plays the role of the 
 characteristic concentration.
@@
 $t_2$ divided by the time difference $t_2-t_1$. The agreement between numerical
-simulations \cite{vanbaten-circular}, which formulation is presented above, and experimental correlations of \citet{bercic-mass}
+simulations \cite{vanbaten-circular} and experimental correlations of \citet{bercic-mass}
 % TODO: was good where?
@@
 using periodic boundary conditions with the same concentration at the inlet
-and at the outlet. The question is how one unit cell simulation corresponds to
+and at the outlet. The question is how single unit cell simulation corresponds to
 experimental measurements arises where concentration difference is measured at
 the distances of at least a few unit cells \cite{bercic-mass}. In
-other words one needs to understand how the discrete one unit cell simulation
+other words, one needs to understand how the discrete one unit cell simulation
 corresponds to the continuous picture in experiments where one does not
@@
 function of other non-dimensional parameters such as gas holdup, bubble/slug
-lenghts, and the capillary number is left for future.
+lenghts, and the capillary number is left for future studies.
 \begin{figure}[htb!]
@@
 To establish numerical procedures we performed multiphase simulations
+to extract bubble shapes
 \cite{kuzmin-binary2d,kuzmin-binary3d} for the range of capillary numbers
-$Ca=0.1\div 1.0$ to extract bubble shapes. For this range of capillary numbers
+$Ca=0.1\div 1.0$. For this range of capillary numbers
 we were able to capture the bubble shape change and the change of hydrodynamic
@@
 By definition, the mass transfer coefficient from a surface with an imposed constant
-concentration $\cbubble$ is the following:
+concentration $\cbubble$ is:
 \beqal
@@
 \feqal
-where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
+where $\dot{m}$ is the mass exchange rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
 $\Bigl[m^2\Bigr]$, and $\Delta C$ is the concentration difference between the surface and the surrounding medium
@@
 medium, the mass accumulated in the volume $V=A \Delta x$ can be
-calculated as the difference of mass fluxes entering and leaving domain $U
+calculated as the difference of mass fluxes entering and leaving the domain $U
 \bigl(C(x+\Delta x)-C(x)\bigr)$. The accumulated mass should be proportional to
@@
 \feq 
-giving the same soltuion but only in spatial domain:
+giving the same solution but only in the spatial domain:
 \beq
@@
 In the application to the bubble train flow it is useful to think of one bubble as a point
-source to make all considerations above valid. For example, the expression
-(\ref{main:mass:transfer:expression}) was used in the experiments by
+source to be able to use the calculations presented above. For example, the expression
+(\ref{main:mass:transfer:expression}) was used in experiments by
 \citet{bercic-mass}. However, one should be accurate with the definition of velocities because two
@@
 contributions from film and bubble caps can be calculated separately.
-Therefore no tracer from a film influences bubble caps diffusion.
-However, this assumption overpredicts mass transfer for number of experiments \cite{irandoust}.
+Therefore no tracer from the film influences bubble caps diffusion.
+However, this assumption overpredicts mass transfer for a number of experiments \cite{irandoust}.
 This happens since some tracer
@@
 the mass transfer from the bubble caps.
-Therefore, the analytical estimates for the analytical mass transfer coefficient calculation  do not account for mutual mass
+Therefore, the analytical estimates for the mass transfer coefficient calculation  do not account for mutual mass
 transfer from neighbouring bubbles.
@@
 estimation of mass transfer \cite{yue-mass}. However, the assumptions usually taken for 
-mass transfer calculations are small capillary numbers and certain mixing patterns such to help to
+mass transfer calculations are small capillary numbers and certain mixing patterns such as to help to
 estimate the mass transfer using the penetration theory of \citet{higbie}.
@@
 %cell, i.e. the outlet and the inlet concentrations are close. 
-Though easier to implement, it gives a rise to the criticism
+Though easier to implement, it gives rise to the criticism
 that the inlet concentration is equal to the outlet one. As was
@@
 The assumptions of this approach are
-that the difference between inlet/outlet and the space-averaged over the whole unit cell concentration is not significant. Thus, the tracer is well mixed in the slug.
+that the concentration difference between the inlet/outlet- and the space-averaged over the whole unit cell is not significant. Thus, the tracer is well mixed in the slug.
 \item
@@
 \item 
-Simulation of a few unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the head of the
+Simulation of several unit cells, see Fig. \ref{fig:benchmark:alot}. This situation corresponds to the head of the
 bubble train, after injection in the pipe and travelling along the channel. One can see that this
 situation best resembles the experimental picture, but also requires larger computational
-resources. By simulating a certain number of the
+resources. By simulating a certain number of 
 bubbles in the train head, the influence of the boundaries can be
-diminished. For example, left and right boundary conditions in this case are taken as open boundaries, i.e. $\partial C/ \partial x = 0 $.  There is no ambiguity in the choice of the
+reduced. For example, left and right boundary conditions in this case are taken as open boundaries, i.e. $\partial C/ \partial x = 0 $.  There is no ambiguity in the choice of the
 characteristic concentration. The average concentration of any unit cell far away from boundaries will be governed
@@
 Another limiting case (will be shown later) is when the mass accumulation rate equals zero, i.e. $\dot{m}=0$. 
-This situation corresponds for simulation of a few unit cells with open boundary for flows with
+This situation corresponds to a simulation of a few unit cells with open boundary for flows with
 $Ca>0.7$.   One
@@
 The parameters $\omegaplus$, $\omegaminus$ and $eq_i$ fully define the lattice Boltzmann
-procedure. The two-dimensional, nine velocities LBM $D2Q9$ we used in this work is defined on the set
+procedure. The two-dimensional, nine-velocity LBM $D2Q9$ we used in this work is defined on the set
 of lattice
@@
 weights
-$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most used set of weights, the so-called
+$t_i^{(u,m,a)}$ can be chosen based on stability criteria. The most commonly used set of weights, the so-called
 ``hydrodynamic`` weights, were chosen:
@@
 \end{table}
-Note that the velocities (LB system) in Table \ref{table:capillary:cases} are small. It means that to
+Note that the velocities (LB system) in Table \ref{table:capillary:cases} are small. This means that to
 match large Peclet numbers, $Pe=\frac{\ububble L}{D}$, usually used in experiments, one needs to decrease the diffusion coefficient
@@
 This issue arises because of the
-multiphase model used in the flow simulations. The binary liquid lattice Boltzmann model is a diffusive
+multiphase model used in the flow simulations. The binary liquid lattice Boltzmann model is a diffuse
 interface model where no clear boundary between gas and liquid exists.
@@
 Thus, before performing the mass transfer simulations an additional single phase hydrodynamic
-simulation is performed. A free-surface solver was developed in order to obtain velocity field
+simulation is performed. A free-surface solver was developed in order to obtain a velocity field
 consistent with the advection-diffusion equation. We take results from the
@@
 \ref{main:simulation:equation}. Table \ref{table:scaling:peclet} shows that the velocity limit
-for  periodic boundary conditions is $0.1$.
-That means that to be on the safe side one shouldn't scale up velocities to obtain them larger than $0.1$.
+for  periodic boundary conditions is $0.1$, so to be on the safe side, velocities should not be scaled
+up beyond that value.
 For example, in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  one can scale up velocity significantly ($20-40$ times) to obtain velocity around $0.2$ where simulations are still stable.
@@
 each simulation has a different physical time step. Thus, we normalized time such that it represents a number of cell
-units which tracer will pass with the given bubble velocity, i.e. 
+units which the tracer will pass with the given bubble velocity, i.e. 
 $N_{\text{cell\,units}}=\frac{\text{scale}\cdot \ububble\cdot N_{\mathrm{iter}}}{\lunit}$.  Fig.
@@
 summarizes results presented here.
-One can see abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
+One can see an abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
 \label{fig:aver:conc:different:capillaries}}
@@
 This section studies the number of unit cells required for the volumetric
-mass transfer coefficient to be independent of boundaries influence. We chose two
+mass transfer coefficient to be independent of the influence of boundaries. We chose two
 different
@@
 rate in the domain which takes into the account inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
-resembles experiments: if one has enough number of unit cells, then the averaged domain
+resembles experiments: if one has a large enough number of unit cells, then the averaged domain
 concentration should change in time according to Eq. \ref{theor:continuous:mass:transfer}: 
@@
 unit cells numbers $2-4$.  The results for the volumetric mass transfer
-coefficient calculated by Eq. \ref{main:main:main} for a multiple unit cells are
+coefficient calculated by Eq. \ref{main:main:main} for multiple unit cells are
 close (less than $10\%$ deviation) to results for periodic boundary conditions in Section
@@
 $8$ and $10$ unit cells simulations but we do not present them here. We also do not present $4$
-units cells simulation results which are much influenced by inlet and outlet boundaries.
+units cells simulation results which are highly influenced by inlet and outlet boundaries.
 
@@
 Note
-that results for approaches which incorporate the volume-averaged characteristic concentration either for one cell or a few unit cells coincide between each other.
+that results for approaches which incorporate the volume-averaged characteristic concentration either for one cell or a few unit cells coincide with each other.
 Therefore, for certain hydrodynamic patterns ($Ca>0.7$), one can
-easily convert time domain to spatial domain calculations using a few unit cells simulations.
+easily convert time domain to spatial domain calculations using simulations of several unit cells.
 \begin{figure}
@@
 \subsection{Comparison of experimental and analytical correlations}
-While the goal of this paper is not to compare simulation results with the experimental measurements, but to give the
-procedure to perform numerical simulations  in the lattice Boltzmann framework, we felt that a
-short note about such comparison will be beneficial.
+While the goal of this paper is not to compare simulation results with the experimental measurements, 
+we felt that a short note about such comparison will be beneficial.
 Unfortunately, to the best authors' knowledge, there are no reported experimental results measuring the mass flux for
@@
 \Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3} \propto Pe^{-\frac{1}{2}}\\
-&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D 
-}{\lunit (\ububble+\ugas)} \frac{\ububble}{\ugas+\uliq}\Bigr)^{0.5}
-\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3} \propto Pe^{-\frac{1}{2}}
 \feqal
@@
 This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
-the lattice Boltzmann method. Overall, the easiest recipe is to perform periodic boundary
-conditions simulations and calculate the volumetric mass transfer coefficient based on the averaged
-domain concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, a few unit cells simulations) as they produce consistent results. The best accuracy
+the lattice Boltzmann method. Overall, the easiest recipe is to perform simulations 
+with periodic boundary conditions
+and calculate the volumetric mass transfer coefficient based on the
+domain-averaged concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, simulations of several unit cells) as they produce consistent results.
+The best accuracy
 is achieved with formulations based on the mass difference or on the averaged domain concentrations
@@
 coefficients (less than $10\%$). The original formulation of
-\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux averaged concentration
+\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux-averaged concentration
 to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
-indicate of how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
+indicate how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
 0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer

### 2012-07-23 Text/introduction.tex
Add acknowledgements.

@@
 compared with the experimental correlation of \citet{yue-mass} and shown to be in good agreement.
+
+\section{Acknowledgements}
+M.J. acknowledges a scholarship from the TWING project co-financed by the European Social Fund.
+
 \appendix

### 2012-07-27 Text/introduction.tex
Went to editor.

@@
-\documentclass{article}
+\documentclass[preprint,12pt]{elsarticle}
+\usepackage{lineno}
+\journal{Chemical Engineering Journal}
+
 \usepackage{amsmath,amssymb}
 \usepackage{bm}
-\usepackage[numbers,sort&compress]{natbib}
+%\usepackage[numbers,sort&compress]{natbib}
 \usepackage{graphicx}
@@
 
+\begin{document}
+\begin{frontmatter}
 \title{Lattice Boltzmann study of mass transfer for two-dimensional Bretherton/Taylor bubble train flow}
-
-\begin{document}
-\maketitle
+\author[uofa]{A.~Kuzmin\corref{cor1}}
+\cortext[cor1]{Corresponding author}
+\ead{kuzmin@ualberta.ca}
+\author[us]{M.~Januszewski}
+\ead{michalj@gmail.com}
+\author[schlum]{D.~Eskin}
+\ead{deskin@slb.com}
+\author[schlum]{F.~Mostowfi}
+\ead{fmostowfi@slb.com}
+\author[uofa]{J.J.~Derksen}
+\ead{jos@ualberta.ca}
+\address[uofa]{Chemical and Materials Engineering, University of Alberta\\ 7th Floor, ECERF, 9107
+116 St, Edmonton, Alberta, T6G
+2V4 Canada}
+\address[us]{Insitute of Physics, University of Silesia, 40-007 Katowice, Poland}
+\address[schlum]{Schlumberger DBR Technology Center\\ 9450 17 Ave NW, Edmonton, Alberta, T6N 1M9
+Canada}
 \begin{abstract}
@@
 The latter is not valid for flows where the tracer is not well mixed, i.e. $Ca>0.7$.  We therefore
-examine various boundary conditions (periodic, open, open with more than 1 unit cell) and definitions of the characteristic concentration for the range of capillary numbers $0.1<Ca<1.0$.
-We show that the time-dependent average concentration produces the most robust results and
+examine various boundary conditions (periodic, open, open with more than 1 unit cell) and definitions of the characteristic concentration to estimate mass transfer coefficients  for the range of capillary numbers $0.1<Ca<1.0$.
+We show that the time-dependent volume averaged concentration taken as the characteristic concentration produces the most robust results and
 that all strategies presented in the literature are extreme limits of one unified equation. %,
@@
 \end{abstract}
+\begin{keyword}
+Mass Transfer \sep Taylor/Bretherton bubble train flow \sep Multiphase flow \sep Lattice Boltzmann
+method
+\sep Binary liquid model \sep Flow in microchannels with parallel plates 
+%% keywords here, in the form: keyword \sep keyword
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+\end{keyword}
+
+\end{frontmatter}
+\linenumbers
 
@@
 reactors and trickle bed reactors \cite{kreutzer-overview,bercic-mass}.  These reactors usually operate in
- the Bretherton-Taylor regime \cite{bretherton,taylor} which describes a flow
+ the Bretherton-Taylor regime \cite{bretherton,taylor} which is a flow
  of equally sized, long air bubbles through a liquid medium, see
@@
 reactions are performed in the best possible manner. The mass transfer coefficient is defined as the flux from the 
-surface divided by the difference of the imposed concentration and the characteristic concentration in the domain.
+gas-liquid interface divided by the difference of the imposed concentration and the characteristic concentration in the domain.
  The  concentration distribution in the domain is prescribed by underlying hydrodynamics fields. 
@@
 Since the mass transfer coefficient is defined in terms of a mass flux through a certain area, Eq. \ref{eq:main:definition},
-analytical estimates \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble shape. The mass
+analytical estimates \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble surface in parts. The mass
  transfer coefficient is calculated through two separate contributions from two planar films and two hemicircles. For both 
@@
  the mass  transfer coefficient 
-for the flow of bubbles between parallel plates  is calculated as (similarly to the work of \citet{vanbaten-circular}):
+for the flow of bubbles between parallel plates  is calculated as (similar to the work of \citet{vanbaten-circular}):
 \beq
@@
 \feq
-where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ stands for the interaction time of liquid traveling below the planar part
- of the bubble, $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time during which the liquid in the slug travels the distance of half the bubble cap circumference.
+where $t_{\mathrm{film}}=\frac{\lfilm}{\ububble}$ stands for the interaction time of liquid traveling next to the planar part
+ of the bubble, and $t_{\mathrm{circle}}=\frac{\pi R_{\mathrm{circle}}}{\ububble}$ is the time during which the liquid in the slug travels the distance of half the bubble cap circumference.
 
@@
 with the increase of the capillary number the situation changes significantly -- the
-symmetrical bubble shape is lost and the bubble shape resembles a bullet \cite{kuzmin-binary2d}.
+symmetrical bubble shape is lost and the bubble resembles a bullet \cite{kuzmin-binary2d}.
 For flows with $Ca>0.7$ there is also no vortex in the liquid slug. In this case the Higbie theory fails
@@
 are then obtained by performing simulations of one-component flow around the
-bubble by imposing the bubble velocity on the walls. Thus, the simulations are
+bubble by imposing the bubble velocity on the channel walls. Thus, the simulations are
 performed in the reference frame moving with the bubble. A stress-free
@@
 can be criticized on a number of points. They mainly
-originate from the bubble shape approximation, which is taken to be symmetrical, i.e.
+relate to the bubble shape approximation, which is taken to be symmetrical, i.e.
 consisting of two hemispheres and film for the case of flow in circular
@@
 simulations. Experimental correlations \cite{bercic-mass} show that the
-concentration along the streamwise direction changes exponentially with distance.
+concentration in a bubble train along the streamwise direction changes exponentially with distance.
 Mass transfer simulations however, are made only for one unit cell
@@
 conditions to determine the mass transfer coefficient when the vortex in the slug
-disappears, i.e. $Ca>0.7$.
+disappears, i.e. when $Ca>0.7$.
  \item[II] Validity of the inlet/outlet-averaged or domain-averaged concentrations as
@@
 
-The mass transfer problems in the lattice Boltzmann framework were mainly
+Mass transfer problems in the lattice Boltzmann framework were mainly
 addressed in a series of works of Ginzburg and co-authors
@@
 The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
-for the bubble train flow to derive expressions to connect the space- and time-averages.  Then, the lattice
-Boltzmann model used to simulate mass transfer is presented and followed by benchmarks. Finally,
+to the bubble train flow to derive expressions to connect the space- and time-averages.  Then, the lattice
+Boltzmann model used to simulate mass transfer is presented, followed by benchmarks. Finally,
 numerical simulations of various boundary conditions and simulations spanning a few unit cells for
@@
 \feqal
-where $\dot{m}$ is the mass exchange rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
+where $\dot{m}$ is the mass flux $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
 $\Bigl[m^2\Bigr]$, and $\Delta C$ is the concentration difference between the surface and the surrounding medium
@@
 %concentration and its influence on mass transfer can be negligible \cite{vanbaten-circular}.
-Overall, mixing patterns of the film and liquid slugs are of great importance for the analytical
+Overall, mixing patterns of the film and liquid slugs are of great importance for the 
 estimation of mass transfer \cite{yue-mass}. However, the assumptions usually taken for 
@@
 account the complex mixing patterns and geometries. However, there are challenges as  how to
-mimic the continuous picture where reacting medium is moving with bulk velocity $U=\ugas+\uliq$  as it is done in
+mimic the continuous picture where the medium is moving with bulk velocity $U=\ugas+\uliq$  as it is done in
 experiments. Thus, the questions indicated in Section \ref{intro} arise.  The next section gives more
@@
 Ideally one wants to mimic the continuous picture as it is seen in experiments.
-Thus, mass transfer simulations for a number of unit cells are needed. As was
+Thus, mass transfer simulations for a number of unit cells each containing a bubble are needed. As was
 indicated above, there are two approaches towards it -- either to simulate the
@@
 up with a simple and smaller domain for calculations of the mass transfer coefficient, which closely mimics the
-continuous picture by an infinite number of  separated bubbles.
+continuous picture of a large number of  separated bubbles.
 
@@
 \feq
-Expressions (\ref{theor:average:concentration:time}) and (\ref{theor:continuous:mass:transfer}) are the
+Expressions (\ref{theor:average:concentration:time} - \ref{theor:continuous:mass:transfer}) are the
 cornerstones of the present work . Four possible scenarios of numerical simulations have been examined: 
@@
 The assumptions of this approach are
-that the concentration difference between the inlet/outlet- and the space-averaged over the whole unit cell is not significant. Thus, the tracer is well mixed in the slug.
+that the concentration difference between the inlet/outlet- and the space-averaged over the whole unit cell is not significant. Thus, the tracer is assumed to be well mixed in the slug.
 \item
@@
 describes the mass balance: whatever was generated by the bubble surface equals
-to the domain mass change minus whatever left the domain plus whatever entered it.
+ the domain mass change minus whatever left the domain plus whatever entered it.
 
@@
 \feqstar
-Then the mass change in the domain arises only because of the bubble
-surface. However, to calculate the mass transfer coefficient one needs to have
-the characteristic concentration  $\langle C(t) \rangle$ and the mass gain $\dot{m}$
-which do require the storage of both temporal and spatial information.
-
+%Then the mass change in the domain arises only because of the bubble
+%surface. However, to calculate the mass transfer coefficient one needs to have
+%the characteristic concentration  $\langle C(t) \rangle$ and the mass gain $\dot{m}$
+%which do require the storage of both temporal and spatial information.
 Another limiting case (will be shown later) is when the mass accumulation rate equals zero, i.e. $\dot{m}=0$. 
 This situation corresponds to a simulation of a few unit cells with open boundary for flows with
-$Ca>0.7$.   One
-can use only spatial information to calculate the mass transfer coefficient,
-i.e. $\int{\cinlet(t) u(0,y) \mathrm{d}y}$ and $\int{\coutlet(t)
-u(\lunit,y)\mathrm{d}y}$ require only space information.
+$Ca>0.7$.   
+%One
+%can use only spatial information to calculate the mass transfer coefficient,
+%i.e. $\int{\cinlet(t) u(0,y) \mathrm{d}y}$ and $\int{\coutlet(t)
+%u(\lunit,y)\mathrm{d}y}$ require only space information.
 
@@
 As was discussed earlier, analytical correlations for the mass transfer coefficient
-are derived  as two separate contributions: the mass transfer from two
+have been derived for a Taylor bubble train flow  as two separate contributions: the mass transfer from two
 half circles and the mass transfer from the film. We will examine these
@@
 decomposes the populations and the equilibrium
-distribution into a symmetric and an antisymmetric parts:
+distribution into a symmetric and an antisymmetric part:
 \begin{equation}
@@
 \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
-For a particular choice $\Lambda=\frac{1}{4}$ (the optimal stability parameter), $\omegaplus$ can be found easily as
+For the particular choice $\Lambda=\frac{1}{4}$, $\omegaplus$ can be found easily as
  $\omegaplus=2-\omegaminus$.
@@
 Therefore, one can choose any quantity, for example 
-$\ububble$ in the lattice Boltzmann units as soon as the
+$\ububble$ in the lattice Boltzmann units as long as the
 Peclet number is  matched in physical space and numerical simulations. The fact that $\ububble$
-can be chosen  is extremely useful in the context of numerical simulations, since one can
-increase the time step and decrease the computational demand by an order of magnitude. 
+can be varied in certain ranges  is extremely useful in the context of numerical simulations. This allows to 
+increase the time step and decrease the computational demand (by an order of magnitude). 
 % while still obtaining meaningful results. 
@@
 The next section will cover LBM benchmarks that resemble the mass transfer from a bubble 
-(mass transfer from the film  and bubble caps).
+(mass transfer to the liquid with the parabolic velocity profile  and mass transfer from a cylinder).
 
@@
 
-The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$  lattice units. Some examples for
+The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$  lattice units. Some results for
 different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
+The numerical simulations with the bounce-back boundary conditions are able to accurately reproduce the analytical results.
 \begin{figure}[htb!]
@@
 diffusion from curved boundaries is captured
-accurately \label{fig:cylinder:benchmark}. $r$ is the distance from the center. The profiles are taken along  the axis $x$.}
+accurately \label{fig:cylinder:benchmark}. $r$ is the distance from the center. %The profiles are taken along  the axis $x$.
+}
 \end{figure}
@@
 
-\subsection{Poiseulle velocity parabolic profile}
+\subsection{Poiseulle velocity profile}
 The problem we want to address can be formulated through the following PDE:
@@
 between contours of analytical and simulation results is presented in Fig.
-\ref{fig:parabolic:comparison}. Parameters were taken the  same as in the previous case: $D=0.0185$, the grid dimension is $80\times1600$. 
+\ref{fig:parabolic:comparison}. Parameters were taken as: $D=0.0185$, the grid dimension is $80\times1600$. The centerline velocity is  $U_0=0.05$
+which yields the Peclet number $Pe=U_0 \delta / D= 108.108$.
+The results are in good agreement. The simulations capture accurately the singular derivative for $x=0$.
 \begin{figure}[htb!]
@@
 anti bounce-back conditions, Eq. \ref{antibb}. The simulation was done for $D=0.0185$ with a
-$80\times1600$ grid. \label{fig:parabolic:comparison}}
+$80\times1600$ grid. The centerline velocity is $U_0=0.05$, and the Peclet number is $108.108$. \label{fig:parabolic:comparison}}
 \end{figure}
@@
 match large Peclet numbers, $Pe=\frac{\ububble L}{D}$, usually used in experiments, one needs to decrease the diffusion coefficient
-$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. Thus, the parameter $\omegaminus\approx 0.5$. However, for such parameters
+$D=\frac{1}{3}\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$. Thus, the parameter $\omegaminus\approx 0.5$. However, for such values of 
 $\omegaminus$ the stability of the lattice Boltzmann method drastically decreases
@@
 and the typical number of simulation steps to obtain the steady-state mass transfer coefficient for
-$Ca<0.2$ is of the order of a few millions. Therefore, it is desirable to increase    $U_{\mathrm{LB}}$
+$Ca<0.2$ is of the order of a few million. Therefore, it is desirable to increase    $U_{\mathrm{LB}}$
 while maintaining the Peclet number. If one increases the velocity, then
@@
 flows around the
-bubble. We impose an uniform and steady concentration on the surface
+bubble. We impose a uniform and steady concentration on the surface
 of the bubble with the anti bounce-back condition, Eq. \ref{antibb}.
@@
 transfer simulations with the various boundary conditions as covered in Section \ref{section:cases}.
-For this purpose one needs to match the Peclet number $Pe$ taken from experiments. Note that we
-specifically separated the hydrodynamic problem from the mass transfer problem. 
+For this purpose one needs to match the Peclet number $Pe$ taken from experiments. 
+%Note that we
+%specifically separated the hydrodynamic problem from the mass transfer problem. 
 \end{description}
@@
 This section covers simulation results. We first examine the possibility to increase the fluid
-velocity while keeping the Peclet number the same. After that  the periodic boundary
+velocity while keeping the Peclet number the same. After that  the results for  periodic boundary
 conditions for $5$ capillary number cases will be presented. Finally, we will examine
@@
 one needs to increase the diffusion coefficient when the velocity is increased. Simulation runs were made with
-velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities and
+velocities $2,4,6,8,10,15,20,40$ times larger than the original velocities. The velocities and
 their corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
@@
 up beyond that value.
-For example, in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  one can scale up velocity significantly ($20-40$ times) to obtain velocity around $0.2$ where simulations are still stable.
+For example, in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  one can scale up velocity significantly ($20-40$ times) to obtain a velocity around $0.2$ where simulations are still stable.
 However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is smaller than $0.1$ .
@@
 all different scales indicated in Table
-\ref{table:scaling:peclet} (top to bottom: 6 scalings, 5 scalings, 2 scalings, 1 scaling, 1 scaling). \label{fig:contours:scaling:peclet}}
+\ref{table:scaling:peclet} (top to bottom: 6 scalings, 5 scalings, 2 scalings, 1 scaling, 1 scaling).
+Some lines are indistinguishable showing that simulations with velocity scalings are consistent.
+\label{fig:contours:scaling:peclet}}
 \end{figure}
@@
 close to $\cstar=1$ then Eq. \ref{theor:one:concentration:time} gives inadequate results due to
- accuracy of the logarithmic function evaluation. 
+ accuracy of the logarithmic function evaluation. This is the reason that curves in Fig. \ref{fig:aver:conc:different:capillaries}
+ tend to shoot up for long times.
  %Fig. \ref{fig:aver:conc:different:capillaries:time} presents
@@
 Due to velocity scaling
-each simulation has a different physical time step. Thus, we normalized time such that it represents a number of cell
-units which the tracer will pass with the given bubble velocity, i.e. 
+each simulation has a different physical time step. Thus, we normalized time such that it represents a number of unit cell lengths which the bubble will pass, i.e. 
 $N_{\text{cell\,units}}=\frac{\text{scale}\cdot \ububble\cdot N_{\mathrm{iter}}}{\lunit}$.  Fig.
@@
 
-Overall one obtains the steady state volumetric mass transfer coefficient for
+Overall one obtains  steady state volumetric mass transfer coefficients for
 periodic boundaries simulations if the following conditions are fulfilled:
@@
 \end{description}
-Also, Table \ref{table:steady:state:average} shows
-the achieved steady state volumetric mass transfer coefficient. 
+%Also, Table \ref{table:steady:state:average} shows
+%the achieved steady state volumetric mass transfer coefficient. 
 %\begin{figure}[htb!]
@@
 bubble travel distance in the laboratory frame. ''Cell Units`` axis refers to the physical
-distance of how many unit cells the bubble passes until the steady state is reached. Legend is provided for velocity scalings. All of them show a good agreement. Table
+distance of how many unit cells the bubble travels until the steady state is reached.
+A legend is provided for velocity scalings.
+All of them show a good agreement.One can see an abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
+Table
 \ref{table:steady:state:average}
-summarizes results presented here.
-One can see an abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
-\label{fig:aver:conc:different:capillaries}}
+summarizes results presented here.  \label{fig:aver:conc:different:capillaries}}
 \end{figure}
@@
 $Ca=0.097,0.254,0.526$ the values are overpredicted
-($\volnondim=0.3,0.25,0.1$). When the velocity pattern is changed from having
+($\volnondim=0.3,0.25,0.1$). When the velocity pattern changes from having
 a vortex in front of
@@
 %averaged concentration in the whole range of capillary numbers. 
-Note that for $Ca=0.097$ the obtained mass transfer coefficient value is a bit
+Note that for $Ca=0.097$ the obtained mass transfer coefficient value is $10\%$ 
 lower than the value in Section \ref{main:results:periodic}. However, as will
@@
 $Ca=0.0097$ has the same value as for the simulations of a few unit cells.
-Therefore the approach of \citet{vanbaten-circular} produces most accurate results but with the characteristic concentration being the volume-averaged concentration (not the inlet/outlet flux-averaged concentration used in the original work).
+Therefore the approach of \citet{vanbaten-circular} produces  accurate results but if the characteristic concentration is the volume-averaged concentration (not the inlet/outlet flux-averaged concentration used in the original work).
 From the computational point of view, it also requires the concentration fields in time and space to calculate the mass change in time and the averaged domain
@@
 the physical system being modelled, one can simulate several unit cells, corresponding
-to a head of the bubble train.  If boundaries are eliminated then the average
+to a head of the bubble train.  If end effects are eliminated then the average
 domain characteristic should change in time according to Eq.
 \ref{theor:continuous:mass:transfer}. This eliminates the ambiguity inherent in choosing a definition
-of the characteristic concentration, which now becomes the same domain-averaged concentration
+of the characteristic concentration, it becomes the same domain-averaged concentration
 as the one measured in experiments.
@@
 cross the unit cell $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ iterations are enough
-for a system consisting of $10$ unit cells. For more accurate estimations of number of time
-iterations depending on the Peclet number we refer to Section \ref{section:keeping:peclet}.
+for a system consisting of $10$ unit cells. For more accurate estimations of the number of time
+steps depending on the Peclet number we refer to Section \ref{section:keeping:peclet}.
 
@@
 Eq.~\ref{main:main:main:thorough} calculated for each unit for velocity
-scale $10$ and  $6$ unit cells (all velocity scales produce the same results). It is shown that the
+scale $10$ and  $6$ unit cells (all velocity scales produce the same results). It shows that the
 volumetric mass transfer coefficient is consistent for internal segments, i.e.
@@
 $8$ and $10$ unit cells simulations but we do not present them here. We also do not present $4$
-units cells simulation results which are highly influenced by inlet and outlet boundaries.
+units cells simulation results which are highly influenced by entrance and exit effects.
 
@@
 
+\begin{figure}[htb!]
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window4scale10.eps}
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window8scale10.eps}
+\caption{The non-dimensional volumetric mass transfer coefficient defined in Eq.
+\ref{moving:average} for $4$ (top left), $6$ (top right), $8$ unit cells (bottom). Only scale
+$10$ is presented since all other simulations produce the same results. One can see that $4$ unit
+cells is not enough to avoid the influence of boundaries. However, the results for $6$ and $8$
+unit cells are consistent and show that beginning from third unit cell the results and ending with
+the penultimate cell results are consistent with periodic boundary simulations and
+\citet{vanbaten-circular} formulations.
+\label{fig:moving:average:ca0097}}
+\end{figure}
 \begin{figure}[htb!]
@@
 \end{figure}
-\begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window4scale10.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scale10.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window8scale10.eps}
-\caption{The non-dimensional volumetric mass transfer coefficient defined in Eq.
-\ref{moving:average} for $4$ (top left), $6$ (top right), $8$ unit cells (bottom). Only scale
-$10$ is presented since all other simulations produce the same results. One can see that $4$ unit
-cells is not enough to avoid the influence of boundaries. However, the results for $6$ and $8$
-unit cells are consistent and show that beginning from third unit cell the results and ending with
-the penultimate cell results are consistent with periodic boundary simulations and
-\citet{vanbaten-circular} formulations.
-\label{fig:moving:average:ca0097}}
-\end{figure}
 
 \subsection{$Ca=1.040$ results}
-The same correlations were examined for a different velocity pattern $Ca=1.040$. %, initial
+The same correlations were examined for a different velocity pattern at $Ca=1.040$. %, initial
 %velocity $\ububble=0.055$, initial diffusion $D=0.0008375$. If only velocity scaling is
@@
 diffusion to $Pe=2644$. The results with respect to the number of unit cells are the same as for $Ca=0.097$:
-at least $6$ unit cells are required to avoid the influence of boundaries. Thus,
+at least $6$ unit cells are required to avoid the influence of inlet/outlet effects. Thus,
 only $6$ unit cells results are presented in Fig. \ref{fig:6:units:ca1040} which shows the
@@
 Note
-that results for approaches which incorporate the volume-averaged characteristic concentration either for one cell or a few unit cells coincide with each other.
+that results for approaches which incorporate the volume-averaged characteristic concentration either for one cell or a few unit cells coincide.
 Therefore, for certain hydrodynamic patterns ($Ca>0.7$), one can
@@
 we felt that a short note about such comparison will be beneficial.
-Unfortunately, to the best authors' knowledge, there are no reported experimental results measuring the mass flux for
+Unfortunately, to the authors' knowledge, there are no reported experimental results measuring the mass flux for
   bubbles flowing between parallel plates. However, an interesting
@@
 that the power of
-the Peclet number dependence  is $-0.50038$ which is close to the theoretical value $-0.5$. 
+the Peclet number dependence  is $-0.50038$ which is close to the theoretical value $-0.5$.  The fitting curve is $7.745 Pe^{-0.50038}$.
 \begin{figure}[htb!]
@@
 \cite{irandoust} and the mass transfer coefficient based
-on periodic boundary conditions. The fitting curve is proportional to $Pe^{-0.5}$ which corresponds
+on periodic boundary conditions. The fitting curve ($7.745 Pe^{-0.50038}$) is proportional to $Pe^{-0.5}$ which corresponds
 to all correlations. One can as well see that the deviation from the analytical expression becomes
@@
 \section{Summary}
-This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
+This work examines a way to calculate the volumetric mass transfer coefficient of Taylor/Batchelor bubble train flow in the framework of
 the lattice Boltzmann method. Overall, the easiest recipe is to perform simulations 
@@
 to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
-indicate how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
+indicate how well the liquid slug is mixed.  For velocity patterns related to $Ca\geq
 0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
@@
 approaches. Finally, a sample of results was
-compared with the experimental correlation of \citet{yue-mass} and shown to be in good agreement.
+compared with the experimental correlation of \citet{yue-mass} and shown to be consistent.
 
 \section{Acknowledgements}
-M.J. acknowledges a scholarship from the TWING project co-financed by the European Social Fund.
+M.J. acknowledges a scholarship from the TWING project co-financed by the European Social Fund. A.K. wants to thank Schlumberger for their financial support.
 
@@
 %$C_1=-1.5217$, $C_2=-0.4933$, $C_3=-0.3243$, $C_4=-0.2486$, $C_5=-0.2044$. 
-\section{The Poiseuille parabolic profile}
+\section{Mass transfer for planar Poiseuille flow}
 \label{appendix:poiseuille}
@@
 \feq
-The same procedure can be done as in the previous case to redefine variables. After substitution
+The following substitution simplifies the form of equations: 
+\beq
+\begin{aligned}
+&\zeta=\frac{x}{\delta} \frac{D}{U_0 \delta}=\frac{1}{Pe}\frac{x}{\delta}\\
+&\xi=\frac{y}{\delta}.
+\end{aligned}
+\feq 
+Then
 the following equation can be obtained:
@@
 \beq
-Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
-\feq
+Y''-\Bigl(\frac{1}{4}{\bar{\xi}}^2+a\Bigr)Y=0,
+\feq
+where $Y'=\mathrm{d}Y/\mathrm{d}\bar{\xi}$, and $a=-m^2/2$.
 The equation above has two solutions via parabolic cylinder functions or through the confluent
@@
 \begin{aligned}
-&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
-&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
+&Y_1=e^{-{\bar{\xi}}^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{{\bar{\xi}}^2}{2}\Bigr)\\
+&Y_2=e^{-{\bar{\xi}}^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{{\bar{\xi}}^2}{2}\Bigr)\\
 \end{aligned}
@@
 \beq
-Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
+Y_m=C_m e^{-m^2 \xi^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \xi^2\Bigr) 
 \feq
@@
 \beq
--\cstar=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)} 
-\feq
-One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)$ and through orthogonality (Stourm-Liouiville theorem) obtain coefficients:
+-\cstar=\sum_m{C_m e^{-m^2 \xi^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+\xi^2\Bigr)} 
+\feq
+One can multiply both parts on $(1-\xi^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
+\xi^2\Bigr)$ and through orthogonality (Stourm-Liouiville theorem) obtain coefficients:
 \beq
 \label{coeff:series:parabolic:profile}
-C_m=-\cstar \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+C_m=-\cstar \frac{\int_{\xi=0}^{1}{(1-x^2)e^{-m^2 \xi^2/2}
 {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
+\xi^2\Bigr)\mathrm{d}\xi}}{\int_{\xi=0}^{1}{(1-\xi^2)e^{-m^2 \xi^2/2}
 {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
-x^2\Bigr)^2\mathrm{d}x}}
+\xi^2\Bigr)^2\mathrm{d}\xi}}
 \feq

### 2012-08-02 Text/Submission/introduction.tex
Some files were missing for the submission.

--- 2012-07-27 Text/introduction.tex
@@
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/benchmark_hydro.eps}
+\includegraphics[width=\textwidth]{benchmark_hydro.eps}
 \caption{Simplified sketch of the bubble motion. Using periodic
@@
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/mass_transfer.eps}
+\includegraphics[width=\textwidth]{mass_transfer.eps}
 \caption{The mass transfer in a moving liquid. \label{fig:moving:frame}}
@@
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
+\includegraphics[width=\textwidth]{benchmark_middle.eps}\\
 \caption{The two-dimensional benchmarks for the  the mass transfer
@@
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/benchmark_alot.eps}\\
+\includegraphics[width=\textwidth]{benchmark_alot.eps}\\
 \caption{Benchmark for multiple unit cells. \label{fig:benchmark:alot}}
@@
 \begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/cylinder1666.eps}
-\includegraphics[width=0.5\textwidth]{Figures/cylinder0833.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/cylinder0104.eps}
-\includegraphics[width=0.5\textwidth]{Figures/cylinder0052.eps}\\
+\includegraphics[width=0.5\textwidth]{cylinder1666.eps}
+\includegraphics[width=0.5\textwidth]{cylinder0833.eps}\\
+\includegraphics[width=0.5\textwidth]{cylinder0104.eps}
+\includegraphics[width=0.5\textwidth]{cylinder0052.eps}\\
 \caption{Profiles for different diffusion parameters varied with $\omegaminus$ (lines: Eq. \ref{eq:analytical:profile:radial:case}, symbols: LB results). One can see that the
@@
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
+\includegraphics[width=\textwidth]{parabolic_profile_comparison.eps}
 \caption{Comparison between the analytical concentration contours and simulations with pressure
@@
 \begin{figure}[htb!]
-\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca0097_out.eps}\\
-\includegraphics[angle=90,width=\textwidth]{Figures/performed_ca1040_out.eps}
+\includegraphics[angle=90,width=\textwidth]{performed_ca0097_out.eps}\\
+\includegraphics[angle=90,width=\textwidth]{performed_ca1040_out.eps}
 \caption{The streamline patterns produced by the free-surface flow solver with simplified approximation
@@
 \begin{figure}[htb!]
-\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca097.eps}\\
-\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca054.eps}\\
-\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca026.eps}\\
-\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca05.eps}\\
-\includegraphics[height=0.25\textwidth]{Figures/contourlines_scale_ca14.eps}\\
+\includegraphics[height=0.25\textwidth]{contourlines_scale_ca097.eps}\\
+\includegraphics[height=0.25\textwidth]{contourlines_scale_ca054.eps}\\
+\includegraphics[height=0.25\textwidth]{contourlines_scale_ca026.eps}\\
+\includegraphics[height=0.25\textwidth]{contourlines_scale_ca05.eps}\\
+\includegraphics[height=0.25\textwidth]{contourlines_scale_ca14.eps}\\
 \caption{Concentration contour profiles for velocity scalings as identified in Table
@@
 \begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca054.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca026.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca05.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}
+\includegraphics[width=0.5\textwidth]{aver_conc_scale_ca097.eps}
+\includegraphics[width=0.5\textwidth]{aver_conc_scale_ca054.eps}\\
+\includegraphics[width=0.5\textwidth]{aver_conc_scale_ca026.eps}
+\includegraphics[width=0.5\textwidth]{aver_conc_scale_ca05.eps}\\
+\includegraphics[width=0.5\textwidth]{aver_conc_scale_ca14.eps}
 \caption{Volumetric mass transfer coefficient for different capillary numbers and scales against the
@@
 \begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca054.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca026.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca05.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_vanbaten_scale_ca14.eps}
+\includegraphics[width=0.5\textwidth]{aver_vanbaten_scale_ca097.eps}
+\includegraphics[width=0.5\textwidth]{aver_vanbaten_scale_ca054.eps}\\
+\includegraphics[width=0.5\textwidth]{aver_vanbaten_scale_ca026.eps}
+\includegraphics[width=0.5\textwidth]{aver_vanbaten_scale_ca05.eps}\\
+\includegraphics[width=0.5\textwidth]{aver_vanbaten_scale_ca14.eps}
 \caption{The volumetric mass transfer coefficient
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/vanbaten_aver_scale_ca097.eps}
-\includegraphics[width=0.5\textwidth]{Figures/vanbaten_full_scale_ca097.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/vanbaten_aver_scale_ca14.eps}
-\includegraphics[width=0.5\textwidth]{Figures/vanbaten_full_scale_ca14.eps}\\
+\includegraphics[width=0.5\textwidth]{vanbaten_aver_scale_ca097.eps}
+\includegraphics[width=0.5\textwidth]{vanbaten_full_scale_ca097.eps}\\
+\includegraphics[width=0.5\textwidth]{vanbaten_aver_scale_ca14.eps}
+\includegraphics[width=0.5\textwidth]{vanbaten_full_scale_ca14.eps}\\
 \caption{The \citet{vanbaten-circular} formulations for $Ca=0.097$ (top) and
@@
 \begin{figure}[htb!]
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window4scale10.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scale10.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window8scale10.eps}
+\includegraphics[width=0.5\textwidth]{aver_moving_window4scale10.eps}
+\includegraphics[width=0.5\textwidth]{aver_moving_window6scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{aver_moving_window8scale10.eps}
 \caption{The non-dimensional volumetric mass transfer coefficient defined in Eq.
@@
 %\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale10.eps}\hfill
-\includegraphics[width=0.5\textwidth]{Figures/right_def_6scale10.eps}\\
+\includegraphics[width=0.5\textwidth]{aver_units6scale10.eps}\hfill
+\includegraphics[width=0.5\textwidth]{right_def_6scale10.eps}\\
 %\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{Figures/aver_units6scaleu2scaled5.eps}
+\includegraphics[width=0.5\textwidth]{aver_units6scaleu2scaled5.eps}
 \end{center}
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/volume_ca_104_scaleu2scaled5.eps}
-\includegraphics[width=0.5\textwidth]{Figures/aver_moving_window6scaleu2scaled5.eps}\\
-\includegraphics[width=0.5\textwidth]{Figures/flux_moving_window6scaleu2scaled5.eps}\\
+\includegraphics[width=0.5\textwidth]{volume_ca_104_scaleu2scaled5.eps}
+\includegraphics[width=0.5\textwidth]{aver_moving_window6scaleu2scaled5.eps}\\
+\includegraphics[width=0.5\textwidth]{flux_moving_window6scaleu2scaled5.eps}\\
 \caption{The periodic (top left, $1$ unit cell, Eq. \ref{theor:continuous:mass:transfer}), unit
@@
 \begin{figure}[htb!]
-\includegraphics[width=\textwidth]{Figures/correlations_comparison.eps}
+\includegraphics[width=\textwidth]{correlations_comparison.eps}
 \caption{Comparison between the correlation by \citet{yue-mass}, the analytical correlation derived by following the work
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
+\includegraphics[width=0.5\textwidth]{free_surface.eps}
 \caption{Free-surface boundary condition represented in the lattice Boltzmann method. 

### 2012-12-16 Text/Final/answers.tex
Finished my corrections.

\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage{color}
\usepackage{bm}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[normalem]{ulem}	% Part of the standard distribution

\begin{document}
It is our pleasure to address the reviewers' comments which improve readability of the manuscript.  Please consider our answers below. All corrections in the manuscript are marked by red.
\section{Reviewer I}

Question and Answers:

\textbf{Comment:}
This work extends previous numerical investigations of the authors on hydrodynamics of Taylor flow toward mass transfer. The underlying lattice Boltzmann method is carefully validated and 2D simulations are performed for a certain range of the capillary number while the Reynolds number is low. The numerical results are utilized for a critical comparative analysis of various concepts for evaluating the mass transfer coefficient. A general widely accepted predictive model for two-phase mass transfer in narrow channels is missing, and the present paper presents a valuable contribution to the critical evaluation of various approaches. The paper is of interest for the readers of CEJ and I recommend accepting it with a minor revision taking into account the issues listed below.

\textbf{Answer:} Thank you for your comments.

\textbf{Question:}  In the paper it is not clear which equations and quantities are dimensional and which not. This concerns in particular the lattice Boltzmann equations whose parameters are obviously dimensionless. These parameters are related to physical quantities which should be dimensional but are not; this leads to some confusion. For example on page 22 line 281 the diffusion coefficient D is related to omega- and on page 25 line 310 a value D=0.0185 is taken. Clearly, the physical diffusion coefficient should have dimension m**2/s. The same applies for the velocity which is always given without units, see e.g. Table 1. On the other hand on page 26 line 327 a physical bubble velocity Ububble,phys is introduced. This velocity should certainly have a dimension. To avoid confusion the authors may consider to mark dimensional quantities by supercript *.

\textbf{Answer:}  We added superscript "LB" which stands for the lattice Boltzmann to distinguish non-dimensional numbers from physical ones in Section 3.1 where the lattice Boltzmann method is introduced. After Section 3.1 all simulations are done in the lattice Boltzmann system, which is non-dimensional. Hereafter, for the sake of simplicity we omit the index. Unless, it is specifically specified, all the quantities after Section 3.1 are non-dimensional (corresponding sentence was added). Thus, the quantities on pages 22 and 25 are non-dimensional. The quantity on page 26 is a physical quantity as it is absolutely rightly specified by referee (corresponding sentence is added).

\textbf{Question:} The hydrodynamic simulations are performed for the five fixed combinations of Ca and Re listed in Table 1. In the mass transfer simulations these values stay fixed while the Peclet number Pe is varied by "scaling the velocity" (section 5.1). Changing Pe while keeping Re fixed means changing the Schmidt number Sc. The results for the mass transfer coefficient which are obtained from "velocity scaling" do thus represent different Schmidt numbers. This issue should be discussed in the paper and the respective values of Sc should be given (e.g. in Table 2). The authors should consider/discuss in how far the variation of Sc may have an influence on the profiles of the mass transfer coefficient displayed in Figs. 9, 10, 11.

\textbf{Answer:} We added the values of the corresponding Schmidt numbers to Table 2. For Section 5.1, the diffusion is increased at the same time as velocity increases. Thus, the Schmidt number stays the same  $Sc\approx790$ for all simulations. The value was chosen corresponding to a dye with the low molecular diffusivity in order to avoid diffusion of the dye in the liquid slug and to study mass transfer related to hydrodynamics patterns. The corresponding sentences explaining the influence of the Schmidt number on the numerical simulations are added.

\textbf{Question:} The authors may consider giving some information about the code. Is it an in-house code? Which hardware platform is used? What are typical CPU times?

\textbf{Answer:} The following paragraph was added:
\begin{quote}
"The simulations were performed by using the in-house code with different modifications for different boundary conditions and in parallel. Typical mass transfer simulation (domain size is $3000\times202$ cells) for $10^{6}$ iterations takes around $24$ hours on Intel dual core CPU with the internal frequency $2$ GHz. All simulations (serial for one unit cell and parallel for a few unit cells simulation) are done using computers of WestGRID, high-performance clusters in Western Canada."
\end{quote}

\textbf{Question:} The unit numbers in the legends in Fig. 12, 13 and 14 should better start from 1 instead of 0.

\textbf{Answer:} Thank you for pointing that. The figures are modified (as well Fig.15).

\textbf{Question:} Figure 15 bottom: why are some data for "5 unit" zero?

\textbf{Answer:} Thank you for pointing that. This was an additional line not related to the simulations. That was corrected.

\textbf{Question:} In comparison to the large amount of results presented in the body of the paper, the conclusion section is rather short. It could certainly be improved. Line 552 in conclusions: the phrase "best accuracy achieved" should be put in context to a criterion used to judge on the accuracy.

\textbf{Answer:} We rewrote a conclusion to outline better results and its accuracy.

\textbf{Question:} 7. The authors may consider adding the following references:
- Angeli\&Gavriilidis, Proceedings of the Institution of Mechanical Engineers Part C-Journal of Mechanical Engineering Science, 222 (2008) 737 (review paper on Taylor flow)
- Keskin et al. AICHE J 56 (2010) 1693 (combined numerical and exp. study on Taylor flow hydrodynamics)
- Onea et al. CES 64 (2009) 1416 and Kececi et al. Cat Today 147S (2009) S125 (qualitative numerical studies of mass transfer in Taylor flow)
- In reference [15] the first name of the third author is not correct

\textbf{Answer:} Thank you for excellent references. We added additional citations and corrected the reference.

\section{Reviewer II}
Questions and Answers:

\textbf{Question:} In this manuscript the authors tested a number of procedures to calculate the effective mass transfer coefficient of a 2D bubble train traveling through the gap between two parallel plates using numerical simulations. The authors have obviously worked diligently and tested a couple of approaches. The conclusion that using periodic cell and domain-averaged concentration is sufficiently accurate should be reassuring. However, aside from this conclusion, there is not enough study of the parameter space (though the authors acknowledged that such a study will be conducted in the future), which, in my opinion, has limited the impact of this work.

\textbf{Answer:}  Thank you for your comments. The amount of simulations we put into this work is large. Especially for the lattice Boltzmann method, being a relatively new method in comparison with all others, many concepts and guidelines of how to perform simulations are yet to be established. Moreover, authors (Onea, et al. Cat Today 147S 2009) who used the VOF method argue that there usage of one periodic cell combined with periodic boundary conditions is questionable. That's why we felt strongly that there is a space for the method papers combined with the guidelines for the lattice Boltzmann method.

\textbf{Question:} In many equations $U_{liq}$ and $U_{gas}$ are added together to form a velocity scale (line 171) to describe the effect of advection. However, in multiphase flows shouldn't there be some kind of weighting (e.g. liquid/gas holdup) applied? I do not think the physical meaning is clear when the two velocities are directly added.

\textbf{Answer:} Thank you for your comment.  In the multiphase literature,  some parameters maps, for example flow patterns map, are indicated through superficial velocities of gas and liquid varying as X and Y axes. This is the reason why we wanted to comply. The connection of superficial velocities and gas holdup happens in the equation for the net velocity is $U=U_{\mathrm{liq}} + U_{\mathrm{gas}}=U_{\mathrm{liq,actual}}*\epsilon+U_{\mathrm{gas,actual}}$. However, the actual gas and liquid velocities are connected through the complicated relationship $U_{\mathrm{gas,actual}}=U_{\mathrm{liq,actual}}(Ca,\epsilon)$ as indicated in our previous work and largely depends on the geometry. We added corresponding sentences to the text.

\textbf{Question:} Also, in some equations the authors added $U_{liq}$ and $U_{gas}$ together (eq. 11) and in others the authors added $U_{bubble}$ and $U_{gas}$ together (eq. 12). Why are these additions not consistent?

\textbf{Answer:} Thank you for noticing it. The typo is corrected. We used macros and the error was in the definition and propagated to Eq.12 and 13.

\textbf{Question:} The treatment of the free-slip BC in lattice Boltzmann is not at all clear. Aren't Un,F = Un,B and Ut,F = Ut,B going to lead to a no-slip BC? The implementation should be better explained. Some test cases or velocity field near the bubble surface should be presented to show that the free slip is indeed simulated.

\textbf{Answer:} Thank you for corrections. We corrected the sign before normal component and added the better explanation in Appendix. In fact, the free slip is indeed simulated  - one can see the streamlines in the reference frame moving with the bubble. Those streamlines patterns coincide within $3\%$ with the streamlines already validated in our previous works \cite{kuzmin-binary2d,kuzmin-binary3d}.

\textbf{Question:} Page 30, line 399: The author stated in some places that the velocity limit should be 0.1, but in other places 0.2 (page 31, line 403). What is the limit and why? Shouldn't velocity be limited by the Mach number in lattice Boltzmann simulations?

\textbf{Answer:} We rewrote this paragraph with better explanations. We indicated that the safe velocity limit is $0.1$ across all velocities indicated in simulations (Capillary numbers). The referee is right about Mach number ($c_s=\frac{1}{\sqrt{3}}$) to be a limit for lattice Boltzmann simulations. However, this limit is theoretical and can be achieved only for the LB model without any boundary conditions or periodic boundary conditions \cite{kuzmin-stability-optimal}. In fact, with the presence of almost any boundary conditions this limit is deteriorated, especially with the variance of relaxation parameter $\omega$. Thus, numerical simulations are used to determine the stability limit.

\textbf{Question:} Figure 8: "Some lines are indistinguishable ..." I was not able to see any difference. Maybe using different colors or line styles or enlarged sections to tell them apart?

\textbf{Answer:} We rewrote the caption text to the figure to explain better. All the lines are close to each other and that's the thought we want to deliver. If some lines are laying apart then the simulations produce different results, thus scaling procedure is not consistent.

\textbf{Question:} Page 51, line 57: The authors stated that the abnormal rise is due to the average concentration being too close to C*. Can this be shown by selectively plotting an example of average concentration / C* vs. cell units?

\textbf{Answer:} We want to refer to Fig. 13, where you can see the average concentration and corresponding volumetric factors. One can see that the rise occurs exactly at the point where $C$ is close to $C^{*}$.

\textbf{Question:} Section 5.7 - The comparison is effectively done at a Pe of 2644. Saying that the diffusivity is scaled five times is a confusing statement. Page 57, upper right figure: Why is this figure consistent with the other two? The lines clearly approach zero. Both the caption and the text (page 37) did not give any explanation.

\textbf{Answer:} Thank you for improving readability of the article. We wanted to say that parameters indicated in Table 2  give $Pe=14041$. The velocity due to scaling is around $U\approx 0.1$ and that means to achieve such parameter we need to have extremely low (for lattice Boltzmann simulations) diffusion coefficient $D=U L / Pe$. The diffusion parameter $D$ is connected with the lattice Boltzmann relaxation parameter $\omega$. For low values of diffusion the relaxation parameter $\omega\approx 1.99$ which is close to theoretical stability limit $\omega_{crit}=2$. In simulations we see that simulations are unstable with the velocity pattern for $Ca=1.040$ and $Pe=14041$. This is the reason that we decrease Peclet number (or $Sc=794.84/5=158.96$)  by increasing diffusion parameter $D$ by $5$ times. The high $Pe$ and $Sc$ numbers simulations are difficult to perform not only with the LBM, but with the Volume of Fluid Method as well \cite{onea-mass}. The corresponding sentences with explanations are added.

The explanation for Fig. 15 is added as well. One needs to take a look at initial times of the top right picture, as the concentration of the unit reaches pretty fast the value of $1$, giving the mass transfer coefficient going to zero. In case of the logarithmic definition for the mass transfer coefficient (periodic boundary conditions) the value of the mass transfer coefficient goes to infinity for the same reason.

\textbf{Question:} Table 1 - I did not find what $epsilon_gas$ means. Is it the gas holdup?

\textbf{Answer:} That is right. We added text for that.

\textbf{Question:} Eq. (5) is first mentioned on Page 4 but is not presented till page 10. I think it will be better to present it the first time it is used.

\textbf{Answer:} We referred to the section.

\textbf{Question:} Page 28 (line 372) and 29 (line 43) "Appendix Appendix B"

\textbf{Answer:} The problem is not seen with our Latex compiler. Could be related to the editorial Latex compiler which produces double referral for the appendix.

\textbf{Question:} Page 33 (line 462) Ca = 0.0097?

\textbf{Answer:} Thank you. It is corrected.

\bibliographystyle{unsrtnat}
\bibliography{paper}

\end{document}

### 2012-12-16 Text/Final/introduction.tex
Finished my corrections.

--- 2012-08-02 Text/Submission/introduction.tex
@@
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[review,12pt]{elsarticle}
 \usepackage{lineno}
@@
 \newcommand{\cmedium}{C_{\mathrm{medium}}}
-\newcommand{\volnondim}{\vol \frac{\lunit}{\ububble+\ugas}}
+\newcommand{\volnondim}{\vol \frac{\lunit}{\uliq+\ugas}}
 \newcommand{\omegaplus}{\omega_{+}}
@@
 \author[uofa]{A.~Kuzmin\corref{cor1}}
-\cortext[cor1]{Corresponding author}
+\cortext[cor1]{Corresponding author, Telephone: +1(438)824-3695}
 \ead{kuzmin@ualberta.ca}
@@
 Canada}
+%\address[google]{Google Switzerland GmbH, Brandschenkestrasse 110, 8002 Zurich, Switzerland}
 \begin{abstract}
@@
 There are several works studying the hydrodynamic properties of the bubble train flow, both
-experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim}.
+experimental \cite{kreutzer-pressure-drop,cerro-space,cerro-bubble-train} and numerical \cite{wang-non-circular,kuzmin-binary3d,giavedoni-numerical,heil-threedim,keskin-hydro}.
  For the flow of long bubbles between parallel plates chosen here as the study case, it is indicated that  there exists a vortex 
-in the liquid slug for $Ca<0.7$, see Fig. \ref{fig:streamlines:tweaked:velocity}, and that the bubble shape is symmetric for low capillary 
+in the liquid slug for $Ca<0.7$, %see Fig. \ref{fig:streamlines:tweaked:velocity}, 
+and that the bubble shape is symmetric for low capillary 
 numbers ($Ca<0.1$ \cite{cerro-bubble-train}) with the capillary number defined as:
@@
 % TODO: move this later so that there is no forward reference to eq.4? It's ok to have it here
-Since the mass transfer coefficient is defined in terms of a mass flux through a certain area, Eq. \ref{eq:main:definition},
+Since the mass transfer coefficient is defined in terms of a mass flux through a certain area, see Sec \ref{sec:mass:definitions},
 analytical estimates \cite{kreutzer-overview,irandoust} are based on a decomposition of the bubble surface in parts. The mass
@@
 \cite{kreutzer-overview,vanbaten-circular} do not consider the simulation of
-bubble shapes for $Ca>0.1$. The usual simulation of mass transfer is performed as
+bubble shapes for $Ca>0.1$.
+{\color{red} Interesting work by \citet{onea-mass} only takes into the account short lengths bubble in the squared microchannels.
+As well the Schmidt number around $0.8$ is  used and the thickness of the concentration and momentum boundary layer is similar leading to qualitative results.} The usual simulation of mass transfer is performed as
 follows: 
@@
 \section{Mass transfer definitions}
+\label{sec:mass:definitions}
 By definition, the mass transfer coefficient from a surface with an imposed constant
@@
 superficial velocities, respectively.
+{\color{red} Gas and liquid superficial and actual velocities are connected with each other through complicated dependency on $Ca$, $\epsilon$ \cite{kuzmin-binary3d}.}
 
@@
 The lattice Boltzmann equation (LBE) operates on a square/cubic grid representing the
-physical domain. It utilizes
+physical domain {\color{red} in the non-dimensional space} (hereafter we use subscript LB to denote non-dimensional quantities). It utilizes
 probability distribution functions (also known as particle populations)
@@
 &eq_i^{(m)}=t_i^{(m)} c_e+ eq_i^{(a)}\\
-&eq_i^{(u)}=t_i^{(u)} \frac{u_x^2+u_y^2}{2}+\frac{u_x^2-u_y^2}{4} p_i^{(xx)}+g_{xy}^{(u)}\frac{u_x
-u_y}{4} p_i^{xy}\\
-&eq_i^{(a)}=\frac{K_{xx}-K_{yy}}{4} p_i^{xx}+\frac{K_{xy}}{4} p_i^{(xy)}\\
-&eq_i^{-}=t_i^{(a)}  u_{\alpha} c_{i\alpha},
+&eq_i^{(u)}=t_i^{(u)} \frac{u_{LB,x}^2+u_{LB,y}^2}{2}+\frac{u_{LB,x}^2-u_{LB,y}^2}{4} p_i^{(xx)}+g_{xy}^{(u)}\frac{u_{LB,x}
+u_{LB,y}}{4} p_i^{xy}\\
+&eq_i^{(a)}=\frac{K_{LB,xx}-K_{LB,yy}}{4} p_i^{xx}+\frac{K_{LB,xy}}{4} p_i^{(xy)}\\
+&eq_i^{-}=t_i^{(a)}  u_{LB,\alpha} c_{i\alpha},
 \end{aligned}
 \end{equation}
-where $K_{xx,yy,xy}$ are proportional to components of the diffusion tensor,
-$c_e=\frac{K_{xx}+K_{yy}}{2}$, parameters $g^{(u)}$ and $g^{u}_{xy}$ are either zero or one (see
+where $K_{LB,xx,yy,xy}$ are proportional to components of the diffusion tensor,
+$c_e=\frac{K_{LB,xx}+K_{LB,yy}}{2}$, parameters $g^{(u)}$ and $g^{u}_{xy}$ are either zero or one (see
 below), the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor $p_i^{(xy)}=c_{ix} c_{iy}$, the
@@
 \beq
-\partial_t C+ \partial_{\alpha} C u_{\alpha}=\partial_{\alpha\beta} D_{\alpha\beta} C,
-\feq
-where the concentration $C=\sum_i{f_i}$, and $D_{\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)K_{\alpha\beta}$ is the
+\partial_t C_{LB}+ \partial_{\alpha} C_{LB} u_{LB,\alpha}=\partial_{\alpha\beta} D_{LB,\alpha\beta} C_{LB},
+\feq
+where the concentration $C_{LB}=\sum_i{f_i}$, and $D_{LB,\alpha\beta}=\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)K_{LB,\alpha\beta}$ is the
 following diffusion tensor:
 \begin{equation}
-D_{\alpha\beta}=
+D_{LB,\alpha\beta}=
 \begin{pmatrix}
-D_{xx} + \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g^{(u)}-1) u_x^2 &
-D_{xy}+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g_{xy}^{(u)}-1)u_x u_y\\
-D_{xy} + \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g_{xy}^{(u)}-1) u_x u_y&
-D_{yy}+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g^{(u)}-1) u_y^2. 
-\end{pmatrix}
+D_{LB,xx} + \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g^{(u)}-1) u_{LB,x}^2 &
+D_{LB,xy}+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g_{xy}^{(u)}-1)u_{LB,x} u_{LB,y}\\
+D_{LB,xy} + \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g_{xy}^{(u)}-1) u_{LB,x} u_{LB,y}&
+D_{LB,yy}+\Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)(g^{(u)}-1) u_{LB,y}^2
+\end{pmatrix}.
 \end{equation}
-We want to resolve the isotropic advection-diffusion equation, $D=D_{xx}=D_{yy}$ or
-$K=K_{xx}=K_{yy}$, with the non-diagonal diffusion tensor components set to zero ($D_{xy}=0$). In
+We want to resolve the isotropic advection-diffusion equation, $D_{LB}=D_{LB,xx}=D_{LB,yy}$ or
+$K_{LB}=K_{LB,xx}=K_{LB,yy}$, with the non-diagonal diffusion tensor components set to zero ($D_{LB,xy}=0$). In
 contrast to the $D2Q5$ model, with $D2Q9$ it is
@@
 of the equilibrium functions, i.e. $g_{xy}^{(u)}=g^{(u)}=1$.  The particular choice of parameters
-used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$. Thus, the diffusion coefficient $D$
-is matched through $\omegaminus$, i.e. $D=c_e
+used in simulations is $c_e=\frac{1}{3}$, $\Lambda=\frac{1}{4}$. Thus, the diffusion coefficient {\color{red} in the lattice Boltzmann system} $D_{LB}$
+is matched through $\omegaminus$, i.e. $D_{LB}=c_e
 \Bigl(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)=\frac{1}{3}(\frac{1}{\omegaminus}-\frac{1}{2}\Bigr)$.
@@
 \label{antibb}
-f^{*}_{B,i}=-f^{*}_{F,\bar{i}} + 2 eq^+(\cstar,\bm{u}),
-\feq
-where $\cstar$ is the concentration to be imposed at the surface, $\bm{u}$ is the surface velocity,
+f^{*}_{B,i}=-f^{*}_{F,\bar{i}} + 2 eq^+(\cstar,\bm{u}_{LB}),
+\feq
+where $\cstar$ is the concentration to be imposed at the surface, $\bm{u}_{LB}$ is the surface velocity,
 $i$ is the direction number pointing to the domain located at the boundary surface $B$,
@@
 Therefore, one can choose any quantity, for example 
-$\ububble$ in the lattice Boltzmann units as long as the
-Peclet number is  matched in physical space and numerical simulations. The fact that $\ububble$
+$\ububble$ in the lattice Boltzmann units ($u_{\mathrm{LB,bubble}}$) as long as the
+Peclet number is  matched in physical space and numerical simulations. The fact that $u_{\mathrm{LB,bubble}}$
 can be varied in certain ranges is extremely useful in the context of numerical simulations. This allows to 
@@
 (mass transfer to the liquid with the parabolic velocity profile  and mass transfer from a cylinder). 
+{\color{red} As soon as we move to numerical simulations, all quantities are non-dimensional. Thus, we drop the subscript $LB$ for simplicity reasons.}
 
@@
 \caption{Comparison between the analytical concentration contours and simulations with pressure
-anti bounce-back conditions, Eq. \ref{antibb}. The simulation was done for $D=0.0185$ with a
+anti bounce-back conditions, Eq. \ref{antibb}. The simulation was done for $D_{LB}=0.0185$ with a
 $80\times1600$ grid. The centerline velocity is $U_0=0.05$, and the Peclet number is $108.108$. \label{fig:parabolic:comparison}}
@@
 following notations are used: the capillary number $Ca=\frac{\ububble L}{\rho \nu_{\mathrm{liq}}}$, $\uliq$ is the superficial liquid velocity, $\ugas$ is the
-superficial gas velocity. $\delta$ is the
+superficial gas velocity, $\holdup$ is the gas holdup. $\delta$ is the
 non-dimensional film thickness, $\lbubble$ and $\lslug$ are the non-dimensional bubble and slug lengths (defined in channel heights).The simulation sketch is presented in Fig.
@@
 \cite{kuzmin-d1q3}. On the other hand, one iteration in the lattice Boltzmann system corresponds
-to a physical time step  $\Delta t=U_{\mathrm{bubble,LB}} \frac{\Delta
-x}{U_{\mathrm{bubble,phys}}}$. The iteration time is proportional to the velocity $U_{\mathrm{LB}}$
+to a physical time step  $\Delta t_{\mathrm{phys}}=U_{\mathrm{bubble,LB}} \frac{\Delta
+x}{U_{\mathrm{bubble,phys}}}$, {\color{red} where $U_{\mathrm{bubble,phys}}$ is the physical velocity $\bigl[\mathrm{m^2}/\mathrm{s}\bigr]$}, and $t_{\mathrm{phys}}$ is the physical time step $\bigl[\mathrm{s}\bigr]$.
+The iteration time is proportional to the velocity $U_{\mathrm{LB}}$
 and the typical number of simulation steps to obtain the steady-state mass transfer coefficient for
@@
 within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. 
-One can see in Fig. \ref{fig:free:surface} two streamline profiles for $Ca=0.097$  and $Ca=1.040$.
+One can see in Fig. \ref{fig:streamlines:tweaked:velocity} two streamline profiles for $Ca=0.097$  and $Ca=1.040$.
 \begin{figure}[htb!]
@@
 
+{\color{red} The simulations were performed by using the in-house code with different modifications for different boundary conditions and in parallel.
+Typical mass transfer simulation (domain size is $3000\times202$ cells) for $10^{6}$ iterations takes around $24$ hours on Intel dual core CPU with the internal frequency $2$ GHz.
+All simulations (serial for one unit cell and parallel for a few unit cells simulation) are done using computers of WestGRID, high-performance clusters in Western Canada.
+}
+
 \subsection{Velocity scaling at constant Peclet number}
@@
 one needs to increase the diffusion coefficient when the velocity is increased. Simulation runs were made with
-velocities $2,4,6,8,10,15,20,40$ times larger than the original velocities. The velocities and
-their corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
+velocities $2,4,6,8,10,15,20,40$ times larger than the original velocities. {\color{red} The velocities,
+their corresponding capillary and Schmidt numbers are presented in Table \ref{table:scaling:peclet}.
+One can see that the Schmidt number, $Sc=Pe/Re\approx 790$, has a value corresponding to a dye with the low molecular diffusivity.
+This is done to minimize the dye diffusion influence on results but rather study the mass transfer in hydrodynamics patterns provided by Taylor bubble flow.} Periodic
 boundary conditions were used and the mass transfer coefficient was calculated according to Eq.
-\ref{main:simulation:equation}. Table \ref{table:scaling:peclet} shows that the velocity limit
-for  periodic boundary conditions is $0.1$, so to be on the safe side, velocities should not be scaled
-up beyond that value.
-For example, in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  one can scale up velocity significantly ($20-40$ times) to obtain a velocity around $0.2$ where simulations are still stable.
-However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is smaller than $0.1$ .
-%if  when $\omegaminus=1.99$ ($D=0.000837$).
+\ref{main:simulation:equation}. 
+{\color{red} One can see} in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  it is possible to scale up velocity significantly ($20-40$ times) to obtain a velocity around $0.2$ where simulations are still stable.
+However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is around $0.1$ .
+Therefore, Table \ref{table:scaling:peclet} shows that the velocity limit
+for  periodic boundary conditions is $0.1$ {\color{red} across all velocities and capillary numbers}. To be on the safe side, velocities should not be scaled
+up beyond that value.   %if  when $\omegaminus=1.99$ ($D=0.000837$). 
 It gives us a
@@
 \multicolumn{5}{c}{}\\
-\multicolumn{5}{c}{$Ca=0.097$,$Pe=1313$}\\
+\multicolumn{5}{c}{$Ca=0.097$,$Pe=1313$,$Sc=792.87$}\\
 \hline
@@
 \multicolumn{5}{c}{}\\
-\multicolumn{5}{c}{$Ca=0.254$,$Pe=3414$}\\
+\multicolumn{5}{c}{$Ca=0.254$,$Pe=3414$,$Sc=790.64$}\\
 \hline
@@
 \multicolumn{5}{c}{}\\
-\multicolumn{5}{c}{$Ca=0.526$,$Pe=7092$}\\
+\multicolumn{5}{c}{$Ca=0.526$,$Pe=7092$,$Sc=793.46$}\\
 \hline
@@
 \multicolumn{5}{c}{}\\
-\multicolumn{5}{c}{$Ca=0.750$,$Pe=10125$}\\
+\multicolumn{5}{c}{$Ca=0.750$,$Pe=10125$,$Sc=794.49$}\\
 \hline
@@
 \multicolumn{5}{c}{}\\
-\multicolumn{5}{c}{$Ca=1.040$,$Pe=14041$}\\
+\multicolumn{5}{c}{$Ca=1.040$,$Pe=14041$,$Sc=794.84$}\\
 \hline
@@
 \ref{table:scaling:peclet} (top to bottom: 6 scalings, 5 scalings, 2 scalings, 1 scaling, 1 scaling).
-Some lines are indistinguishable showing that simulations with velocity scalings are consistent.
+{\color{red} Lines for different scaling parameters coincide with or close to} each other showing that simulations with velocity scalings are consistent.
 \label{fig:contours:scaling:peclet}}
@@
 be shown later the obtained volumetric mass transfer coefficient for
-$Ca=0.0097$ has the same value as for the simulations of a few unit cells.
+$Ca=0.097$ has the same value as for the simulations of a few unit cells.
 Therefore the approach of \citet{vanbaten-circular} produces  accurate results but if the characteristic concentration is the volume-averaged concentration (not the inlet/outlet flux-averaged concentration used in the original work).
@@
 The original Peclet number we started with is $Pe=14041$ (Table \ref{table:scaling:peclet}).
-To improve stability we changed the original Peclet number by increasing
-diffusion to $Pe=2644$. The results with respect to the number of unit cells are the same as for $Ca=0.097$:
+To avoid stability problems of the lattice Boltzmann method we changed the original Peclet number by increasing
+diffusion to $Pe=2644$ (corresponding Schmidt number $Sc=709.84/5=158.96$).
+{\color{red} Our goal is to understand the velocity pattern influence, but not to perform simulations with the certain Peclet number.
+Thus, we have a certain degree of freedom to vary the simulations Peclet number.
+This is achieved by adjusting velocity and diffusion coefficients.
+For example, if the velocity scaling is $2$, then by increasing initial diffusion coefficient by $10$ times one will eventually obtain the Peclet number $5$ times less then initial Peclet number.
+} The results with respect to the number of unit cells are the same as for $Ca=0.097$:
 at least $6$ unit cells are required to avoid the influence of inlet/outlet effects. Thus,
@@
 calculated using the spatial approach, see Fig.
-\ref{fig:periodic:ca1040}.
+\ref{fig:periodic:ca1040}. {\color{red}To decrease the initial Peclet number from $14041$ to $2644$, the corresponding scaling parameters for velocity and diffusion equal to $2$ and $10$.}
 \label{fig:6:units:ca1040}}
@@
 transfer
-coefficients. One can see that they all coincide. However, the calculations based on periodic boundary conditions
+coefficients.
+One can see that they all coincide.
+{\color{red} For the unit cells domain averaged calculation of the volumetric mass transfer coefficient, one needs to take into the account only initial times values as after that the unit cells concentration reach the value of $C^{*}$ giving unreliable results going to zero.} However, the calculations based on periodic boundary conditions
 produce a slightly overestimated volumetric mass transfer
@@
 This work examines a way to calculate the volumetric mass transfer coefficient of Taylor/Batchelor bubble train flow in the framework of
-the lattice Boltzmann method. Overall, the easiest recipe is to perform simulations 
+the lattice Boltzmann method.
+{\color{red} The volumetric mass transfer for Taylor/Batchelor bubble train flow can be relatively easily estimated by measuring concentrations of scalar along the streamwise direction.
+In comparison with the continuous nature of experiments, i.e.
+one doesn't distinguish bubbles, the numerical simulations are performed with discrete simulation of one or a few unit cells, each containing a bubble.
+This work bridges the continuous nature of experiments and a few unit cells simulations performed in the reference frame moving with the bubble.
+We thoroughly examined and performed simulations with different definitions of the volumetric mass transfer coefficient and characteristic concentration, i.e.
+domain-averaged or flux-averaged inlet/outlet concentrations, for different hydrodynamic patterns seen in bubble train flow.
+As well, we performed a few unit cells open inlet/outlet mass transfer simulations to resemble continuous picture seen in experiments.
+By thorough comparison it was shown that the easiest recipe is to perform simulations
 with periodic boundary conditions
@@
 domain-averaged concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, simulations of several unit cells) as they produce consistent results.
-The best accuracy
+The best accuracy in terms of closeness to results of a few unit cells simulations (continuous picture seen in experiments)
 is achieved with formulations based on the mass difference or on the averaged domain concentrations
@@
 \citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux-averaged concentration
-to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
-indicate how well the liquid slug is mixed.  For velocity patterns related to $Ca\geq
-0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
+to be the characteristic concentration as in their original work.
+Simulations of several unit cells are harder to perform, but it is a reference point since it resembles the continuous nature of bubble train flow.
+In addition, simulations of several unit cells
+indicate how well the liquid slug is mixed. This can be used for velocity patterns related to $Ca\geq
+0.7$ (weak liquid slug mixing) which allows to calculate the volumetric mass transfer
 coefficient based on the spatial location only, without requiring the time snapshots of domain concentration values used in all other
 approaches. Finally, a sample of results was
-compared with the experimental correlation of \citet{yue-mass} and shown to be consistent.
+compared with the experimental correlation of \citet{yue-mass} and shown to be consistent. }
 
@@
 Because the boundary is a staircase approximation, one can find the normal to the boundary which
-is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}. This
-can be done automatically by the simple coding. Imposing the
-symmetric boundary conditions requires $U_{n,F}$=$U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
+is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}. {\color{red} The finding normals
+can be done automatically by the simple coding.} Imposing the
+symmetric boundary conditions requires $U_{n,F}$=$-U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
 populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
@@
 $c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.
+{\color{red} One can check by taking definition of velocity $\rho \bm{u}=\sum_i{f_i \bm{c_i}}$ and substituting relationships above, that in the normal velocities are canceled, i.e.
+$U_{n,F}=-U_{n,B}$, but tangential velocity component is conserved, $U_{\tau,F}=U_{\tau,B}$.}
 \begin{figure}

### 2012-12-16 Text/Submission/introduction.tex
Add Google affil to the submission text.
Finished my corrections.

@@
 \author[uofa]{A.~Kuzmin\corref{cor1}}
-\cortext[cor1]{Corresponding author}
+\cortext[cor1]{Corresponding author, Telephone: +1(438)824-3695}
 \ead{kuzmin@ualberta.ca}
-\author[us]{M.~Januszewski}
+\author[us,google]{M.~Januszewski}
 \ead{michalj@gmail.com}
@@
 Canada}
+\address[google]{Google Switzerland GmbH, Brandschenkestrasse 110, 8002 Zurich, Switzerland}
 \begin{abstract}
@@
  For the flow of long bubbles between parallel plates chosen here as the study case, it is indicated that  there exists a vortex 
-in the liquid slug for $Ca<0.7$, see Fig. \ref{fig:streamlines:tweaked:velocity}, and that the bubble shape is symmetric for low capillary 
+in the liquid slug for $Ca<0.7$, %see Fig. \ref{fig:streamlines:tweaked:velocity}, 
+and that the bubble shape is symmetric for low capillary 
 numbers ($Ca<0.1$ \cite{cerro-bubble-train}) with the capillary number defined as:

### 2012-12-17 Text/Final/introduction.tex
Minor corrections in the text (mostly the new additions, but also some old parts).

@@
 \cite{kreutzer-overview,vanbaten-circular} do not consider the simulation of
-bubble shapes for $Ca>0.1$.
-{\color{red} Interesting work by \citet{onea-mass} only takes into the account short lengths bubble in the squared microchannels.
-As well the Schmidt number around $0.8$ is  used and the thickness of the concentration and momentum boundary layer is similar leading to qualitative results.} The usual simulation of mass transfer is performed as
-follows: 
+bubble shapes for $Ca>0.1$. {\color{red} The interesting work by
+\citet{onea-mass} only takes into account short length bubbles in microchannels
+with a square cross section. As well the Schmidt number around $0.8$ is  used
+and the thickness of the concentration and momentum boundary layer is similar
+leading to qualitative results.} The usual simulation of mass transfer is
+performed as follows: 
 \begin{description}
@@
 using periodic boundary conditions with the same concentration at the inlet
-and at the outlet. The question is how single unit cell simulation corresponds to
-experimental measurements arises where concentration difference is measured at
-the distances of at least a few unit cells \cite{bercic-mass}. In
+and at the outlet. The question how a single unit cell simulation corresponds to
+experimental measurements arises where the concentration difference is measured at
+distances of at least a few unit cells \cite{bercic-mass}. In
 other words, one needs to understand how the discrete one unit cell simulation
@@
 As our numerical approach we take the lattice Boltzmann method, a relatively
-new CFD competitor developed during last $20$ years
+new CFD competitor developed during the last $20$ years
 \cite{frisch,mcnamara,HJ,HSB}. This method was successfully applied to simulate
@@
 different hydrodynamic patterns are presented to establish the procedure to determine the
-volumetric mass transfer coefficient. The comparison with analytical correlations is also presented.
+volumetric mass transfer coefficient. The comparison with analytical correlations is also discussed.
 
@@
 superficial velocities, respectively.
-{\color{red} Gas and liquid superficial and actual velocities are connected with each other through complicated dependency on $Ca$, $\epsilon$ \cite{kuzmin-binary3d}.}
+{\color{red} The gas and liquid superficial and actual velocities are connected with each other through a complex dependency on $Ca$, $\epsilon$ \cite{kuzmin-binary3d}.}
 
@@
 In comparison with analytical calculations and simplifications, the numerical approach can take into
-account the complex mixing patterns and geometries. However, there are challenges as  how to
+account the complex mixing patterns and geometries. However, there are challenges as to how to
 mimic the continuous picture where the medium is moving with bulk velocity $U=\ugas+\uliq$  as it is done in
@@
 containing information about
-macroscopic variables, such as fluid density and momentum. LBE consists of
+macroscopic variables, such as fluid density and momentum. The LBE consists of
 two parts: a local collision step, and a propagation step which transports
@@
 $c_e=\frac{K_{LB,xx}+K_{LB,yy}}{2}$, parameters $g^{(u)}$ and $g^{u}_{xy}$ are either zero or one (see
-below), the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor $p_i^{(xy)}=c_{ix} c_{iy}$, the
+below), and the tensor $p_i^{(xx)}=c_{ix}^2-c_{iy}^2$, the tensor $p_i^{(xy)}=c_{ix} c_{iy}$, the
 weights
@@
 
-\subsection{Poiseulle velocity profile}
+\subsection{Poiseuille velocity profile}
 The problem we want to address can be formulated through the following PDE:
@@
 
-Now the LBM is validated against the benchmarks relevant for the flow around bubbles, one can
+Now that the LBM is validated against the benchmarks relevant for the flow around bubbles, one can
 examine the cases mentioned in Section
-\ref{section:cases} to calculate the volumetric mass transfer coefficient for Taylor bubble train flow.
+\ref{section:cases} to calculate the volumetric mass transfer coefficient for the Taylor bubble train flow.
 
@@
 superficial gas velocity, $\holdup$ is the gas holdup. $\delta$ is the
-non-dimensional film thickness, $\lbubble$ and $\lslug$ are the non-dimensional bubble and slug lengths (defined in channel heights).The simulation sketch is presented in Fig.
+non-dimensional film thickness, $\lbubble$ and $\lslug$ are the non-dimensional bubble and slug lengths (defined as multiplies of the channel height). The simulation sketch is presented in Fig.
 \ref{fig:benchmark:hydro}. \label{table:capillary:cases}}
@@
 to a physical time step  $\Delta t_{\mathrm{phys}}=U_{\mathrm{bubble,LB}} \frac{\Delta
-x}{U_{\mathrm{bubble,phys}}}$, {\color{red} where $U_{\mathrm{bubble,phys}}$ is the physical velocity $\bigl[\mathrm{m^2}/\mathrm{s}\bigr]$}, and $t_{\mathrm{phys}}$ is the physical time step $\bigl[\mathrm{s}\bigr]$.
+x}{U_{\mathrm{bubble,phys}}}$, {\color{red} where $U_{\mathrm{bubble,phys}}$ is the physical velocity $\bigl[\mathrm{m}/\mathrm{s}\bigr]$}, and $t_{\mathrm{phys}}$ is the physical time step $\bigl[\mathrm{s}\bigr]$.
 The iteration time is proportional to the velocity $U_{\mathrm{LB}}$
@@
 taken to ensure grid
-independency of the results \cite{kuzmin-binary2d}. Note that we do not approximate bubble shapes by correlations, but we directly resolve them by using the multiphase solver. 
+independency of the results \cite{kuzmin-binary2d}. Note that we do not approximate bubble shapes by correlations, but directly resolve them using the multiphase solver. 
  \item[Bubble reference frame] Once the hydrodynamics is solved, the mass transfer simulations
@@
 iterated until a
-steady state is reached. Note, that these type of simulations are much faster than the original
-multiphase simulations. As the output all the non-zero velocity components perpendicular to the
-bubble surface are completely eliminated. We compared original multiphase simulations with
+steady state is reached
+and as a result, all non-zero velocity components perpendicular to the bubble surface are completely eliminated.
+Note, that these types of simulations are much faster than the original
+multiphase simulations.  We compared original multiphase simulations with
 one-component free-slip simulations. All quantities such as superficial slug and liquid velocities are
@@
 
-{\color{red} The simulations were performed by using the in-house code with different modifications for different boundary conditions and in parallel.
-Typical mass transfer simulation (domain size is $3000\times202$ cells) for $10^{6}$ iterations takes around $24$ hours on Intel dual core CPU with the internal frequency $2$ GHz.
-All simulations (serial for one unit cell and parallel for a few unit cells simulation) are done using computers of WestGRID, high-performance clusters in Western Canada.
+{\color{red} The simulations were performed using an in-house code with different modifications for different boundary conditions.
+A typical mass transfer simulation (domain size is $3000\times202$ cells) for $10^{6}$ iterations takes around $24$ hours on an Intel dual core CPU with the internal clock frequency of $2$ GHz.
+All simulations (serial for one unit cell and parallel for a few unit cells simulation) are done using computers of the WestGRID high-performance clusters in Western Canada.
 }
@@
 their corresponding capillary and Schmidt numbers are presented in Table \ref{table:scaling:peclet}.
-One can see that the Schmidt number, $Sc=Pe/Re\approx 790$, has a value corresponding to a dye with the low molecular diffusivity.
+One can see that the Schmidt number, $Sc=Pe/Re\approx 790$, has a value corresponding to a dye with a low molecular diffusivity.
 This is done to minimize the dye diffusion influence on results but rather study the mass transfer in hydrodynamics patterns provided by Taylor bubble flow.} Periodic
@@
 {\color{red} One can see} in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  it is possible to scale up velocity significantly ($20-40$ times) to obtain a velocity around $0.2$ where simulations are still stable.
-However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is around $0.1$ .
-Therefore, Table \ref{table:scaling:peclet} shows that the velocity limit
-for  periodic boundary conditions is $0.1$ {\color{red} across all velocities and capillary numbers}. To be on the safe side, velocities should not be scaled
+However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is around $0.1$.
+Table \ref{table:scaling:peclet} shows that the velocity limit
+for periodic boundary conditions is $0.1$ {\color{red} across all capillary numbers}. To be on the safe side, velocities should not be scaled
 up beyond that value.   %if  when $\omegaminus=1.99$ ($D=0.000837$). 
@@
 \ref{table:scaling:peclet} (top to bottom: 6 scalings, 5 scalings, 2 scalings, 1 scaling, 1 scaling).
-{\color{red} Lines for different scaling parameters coincide with or close to} each other showing that simulations with velocity scalings are consistent.
+{\color{red} Lines for different scaling parameters coincide with or are close to} each other showing that simulations with velocity scalings are consistent.
 \label{fig:contours:scaling:peclet}}
@@
 \begin{description}
-\item[I] Scaling is performed as $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
+\item[I] Scaling is performed so that $U_{max}=\mathrm{scale}\cdot\ububble\leq 0.1$.
 \item[II] The larger the Peclet number, the fewer iterations are required. One can extrapolate data from Table
@@
 A legend is provided for velocity scalings.
-All of them show a good agreement.One can see an abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
+All of them show a good agreement.
+One can see an abnormal rise of the mass transfer coefficient when the average concentration is close to $\cstar$ due to the logarithmic function evaluation.
 Table
@@
 \ref{fig:volumetric:char:concentration:vanbaten} that the calculated volumetric mass
-transfer behave differently from the domain averaged  volumetric mass
+transfer coefficient behaves differently from the domain averaged  volumetric mass
 transfer coefficient. For example, for small capillary numbers, i.e.
@@
  the values are either overpredicted or underpredicted
-in comparison to values specified in Table \ref{table:steady:state:average} 
+in comparison to values specified in Table \ref{table:steady:state:average}.
 \label{fig:volumetric:char:concentration:vanbaten}}
@@
 the unit cell with time (see Eq. \ref{theor:continuous:mass:transfer}), and the accumulated mass
-rate in the domain which takes into the account inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
+rate in the domain which takes into account inlet/outlet fluxes (see Eq. \ref{main:main:main}). The former
 resembles experiments: if one has a large enough number of unit cells, then the averaged domain
@@
 $8$ and $10$ unit cells simulations but we do not present them here. We also do not present $4$
-units cells simulation results which are highly influenced by entrance and exit effects.
+unit cells simulation results which are highly influenced by entrance and exit effects.
 
@@
 cells is not enough to avoid the influence of boundaries. However, the results for $6$ and $8$
-unit cells are consistent and show that beginning from third unit cell the results and ending with
-the penultimate cell results are consistent with periodic boundary simulations and
+unit cells are consistent and show that beginning from the third unit cell and ending with
+the penultimate cell, the results are consistent with periodic boundary simulations and
 \citet{vanbaten-circular} formulations.
@@
 diffusion to $Pe=2644$ (corresponding Schmidt number $Sc=709.84/5=158.96$).
-{\color{red} Our goal is to understand the velocity pattern influence, but not to perform simulations with the certain Peclet number.
-Thus, we have a certain degree of freedom to vary the simulations Peclet number.
+{\color{red} Our goal is to understand the influence of velocity pattern, not to perform simulations with a certain Peclet number.
+Thus, we have a certain degree of freedom to vary the simulations' Peclet number.
 This is achieved by adjusting velocity and diffusion coefficients.
-For example, if the velocity scaling is $2$, then by increasing initial diffusion coefficient by $10$ times one will eventually obtain the Peclet number $5$ times less then initial Peclet number.
+For example, if the velocity scaling is $2$, then by increasing the initial diffusion coefficient $10$ times one will eventually obtain a Peclet number $5$ times smaller than the initial Peclet number.
 } The results with respect to the number of unit cells are the same as for $Ca=0.097$:
@@
 %\includegraphics[width=0.5\textwidth]{Figures/novortex6scaleu2scaled5.eps}\\
-\caption{Results for $6$ unit cells. The Peclet number equals to $Pe=2644$.
+\caption{Results for $6$ unit cells. The Peclet number is $Pe=2644$.
 One can see that average concentrations reach certain value and stay constant.
@@
 One can see that they all coincide.
-{\color{red} For the unit cells domain averaged calculation of the volumetric mass transfer coefficient, one needs to take into the account only initial times values as after that the unit cells concentration reach the value of $C^{*}$ giving unreliable results going to zero.} However, the calculations based on periodic boundary conditions
+{\color{red} For the unit cells domain-averaged calculation of the volumetric mass transfer coefficient, one needs to take into account only initial time values as after that the unit cells concentration reaches the value of $C^{*}$ giving unreliable results going to zero.} However, the calculations based on periodic boundary conditions
 produce a slightly overestimated volumetric mass transfer
@@
 \section{Summary}
-This work examines a way to calculate the volumetric mass transfer coefficient of Taylor/Batchelor bubble train flow in the framework of
-the lattice Boltzmann method.
-{\color{red} The volumetric mass transfer for Taylor/Batchelor bubble train flow can be relatively easily estimated by measuring concentrations of scalar along the streamwise direction.
-In comparison with the continuous nature of experiments, i.e.
-one doesn't distinguish bubbles, the numerical simulations are performed with discrete simulation of one or a few unit cells, each containing a bubble.
-This work bridges the continuous nature of experiments and a few unit cells simulations performed in the reference frame moving with the bubble.
-We thoroughly examined and performed simulations with different definitions of the volumetric mass transfer coefficient and characteristic concentration, i.e.
-domain-averaged or flux-averaged inlet/outlet concentrations, for different hydrodynamic patterns seen in bubble train flow.
-As well, we performed a few unit cells open inlet/outlet mass transfer simulations to resemble continuous picture seen in experiments.
-By thorough comparison it was shown that the easiest recipe is to perform simulations
-with periodic boundary conditions
+This work examines a way to calculate the volumetric mass transfer coefficient
+of Taylor/Batchelor bubble train flow in the framework of the lattice Boltzmann
+method. {\color{red} The volumetric mass transfer for the Taylor/Batchelor bubble
+train flow can be relatively easily estimated by measuring concentrations of
+a scalar along the streamwise direction. In comparison with the continuous nature
+of experiments, i.e. where one doesn't distinguish bubbles, the numerical simulations
+are performed with a small number of discrete unit cells, each
+containing a bubble. This work bridges the continuous nature of experiments and
+a few unit cells simulations performed in the reference frame moving with the
+bubble.  We thoroughly examined and performed simulations with different
+definitions of the volumetric mass transfer coefficient and characteristic
+concentration, i.e. domain-averaged or flux-averaged inlet/outlet
+concentrations, for different hydrodynamic patterns seen in the bubble train flow.
+We also performed open inlet/outlet mass transfer
+simulations for a few unit cells to resemble the continuous picture seen in experiments. By thorough
+comparison it was shown that the easiest recipe is to perform simulations with
+periodic boundary conditions
 and calculate the volumetric mass transfer coefficient based on the
-domain-averaged concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, simulations of several unit cells) as they produce consistent results.
-The best accuracy in terms of closeness to results of a few unit cells simulations (continuous picture seen in experiments)
-is achieved with formulations based on the mass difference or on the averaged domain concentrations
+domain-averaged concentration through any formulation
+(\citeauthor{vanbaten-circular}, periodic boundary conditions, simulations of
+several unit cells) as they produce consistent results. The best accuracy in
+terms of closeness to the results of simulations of several unit cells (continuous
+picture seen in experiments)
+is achieved with formulations based on the mass difference or on the domain-averaged concentrations
 taken in different times, Eq. \ref{theor:continuous:mass:transfer}. Eq.
@@
 coefficients (less than $10\%$). The original formulation of
-\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux-averaged concentration
-to be the characteristic concentration as in their original work.
-Simulations of several unit cells are harder to perform, but it is a reference point since it resembles the continuous nature of bubble train flow.
-In addition, simulations of several unit cells
+\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet
+flux-averaged concentration to be the characteristic concentration as in their
+original work. Simulations of several unit cells are harder to perform, but they provide
+a good reference point since they more closely resemble the continuous nature of the bubble train
+flow. In addition, simulations of several unit cells
 indicate how well the liquid slug is mixed. This can be used for velocity patterns related to $Ca\geq
 0.7$ (weak liquid slug mixing) which allows to calculate the volumetric mass transfer
-coefficient based on the spatial location only, without requiring the time snapshots of domain concentration values used in all other
+coefficient based on the spatial location only, without requiring the time
+snapshots of domain concentration values used in all other
 approaches. Finally, a sample of results was
@@
 Because the boundary is a staircase approximation, one can find the normal to the boundary which
-is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}. {\color{red} The finding normals
-can be done automatically by the simple coding.} Imposing the
+is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}. {\color{red} The finding
+identification of normals can be done automatically by a simple code.} Imposing the
 symmetric boundary conditions requires $U_{n,F}$=$-U_{n,B}$ and $U_{\tau,F}=U_{\tau,B}$. We can copy
-populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
+populations in a certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
 $c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and
@@
 $c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.
-{\color{red} One can check by taking definition of velocity $\rho \bm{u}=\sum_i{f_i \bm{c_i}}$ and substituting relationships above, that in the normal velocities are canceled, i.e.
-$U_{n,F}=-U_{n,B}$, but tangential velocity component is conserved, $U_{\tau,F}=U_{\tau,B}$.}
+{\color{red} One can check by taking the definition of velocity $\rho \bm{u}=\sum_i{f_i \bm{c_i}}$ and substituting it in the relationships above, that the normal velocities are canceled, i.e.
+$U_{n,F}=-U_{n,B}$, but the tangential velocity component is conserved, $U_{\tau,F}=U_{\tau,B}$.}
 \begin{figure}

### 2012-12-17 Text/Final/introduction.tex
Minor-minor change.

@@
 \citet{onea-mass} only takes into account short length bubbles in microchannels
-with a square cross section. As well the Schmidt number around $0.8$ is  used
-and the thickness of the concentration and momentum boundary layer is similar
+with a square cross section. As well, in this work  the Schmidt number around $0.8$ is  used:
+thus, the thickness of the concentration and momentum boundary layer is similar
 leading to qualitative results.} The usual simulation of mass transfer is

### 2012-12-22 Text/Final/answers.tex
Did answers.tex

@@
 \begin{document}
-It is our pleasure to address the reviewers' comments which improve readability of the manuscript.  Please consider our answers below. All corrections in the manuscript are marked by red.
+It is our pleasure to address the reviewers' comments which improved the manuscript.  Please consider our answers below. All corrections in the manuscript are marked by red.
 \section{Reviewer I}
@@
 Thus, the quantities on pages 22 and 25 are non-dimensional.
-The quantity on page 26 is a physical quantity as it is absolutely rightly specified by referee (corresponding sentence is added).
+The quantity on page 26 is a physical quantity as it is absolutely rightly specified by the referee (corresponding sentence is added).
 
@@
 \textbf{Answer:} We added the values of the corresponding Schmidt numbers to Table 2.
-For Section 5.1, the diffusion is increased at the same time as velocity increases.
+For Section 5.1, the diffusion is increased with the same factor as  the velocity increases.
 Thus, the Schmidt number stays the same  $Sc\approx790$ for all simulations.
@@
 
-\textbf{Answer:} We rewrote a conclusion to outline better results and its accuracy.
+\textbf{Answer:} We rewrote a conclusion to outline better results and their accuracy.
 
@@
 
-\textbf{Answer:} Thank you for excellent references. We added additional citations and corrected the reference.
+\textbf{Answer:} Thank you for excellent references. We added the additional citations and corrected the reference.
 
@@
 Moreover, authors (Onea, et al.
-Cat Today 147S 2009) who used the VOF method argue that there usage of one periodic cell combined with periodic boundary conditions is questionable.
-That's why we felt strongly that there is a space for the method papers combined with the guidelines for the lattice Boltzmann method.
+Cat Today 147S 2009) who used the VOF method argue that their usage of one periodic cell combined with periodic boundary conditions is questionable.
+That's why we felt strongly that there is space for a  methods paper combined with the guidelines for the lattice Boltzmann method.
 
@@
 This is the reason why we wanted to comply.
-The connection of superficial velocities and gas holdup happens in the equation for the net velocity is $U=U_{\mathrm{liq}} + U_{\mathrm{gas}}=U_{\mathrm{liq,actual}}*\epsilon+U_{\mathrm{gas,actual}}$.
-However, the actual gas and liquid velocities are connected through the complicated relationship $U_{\mathrm{gas,actual}}=U_{\mathrm{liq,actual}}(Ca,\epsilon)$ as indicated in our previous work and largely depends on the geometry.
+The connection of superficial velocities and gas holdup happens in the equation for the net velocity is $U=U_{\mathrm{liq}} + U_{\mathrm{gas}}=U_{\mathrm{liq,actual}}*\epsilon+U_{\mathrm{gas,actual}} (1-\epsilon)$.
+Thus, the gas holdup is already included in the equation.
+Note that the actual gas and liquid velocities are connected through the complicated relationship $U_{\mathrm{gas,actual}}=U_{\mathrm{liq,actual}}(Ca,\epsilon)$ as indicated in our previous work and largely depends on the geometry.
 We added corresponding sentences to the text.
@@
 
-\textbf{Answer:} Thank you for noticing it. The typo is corrected. We used macros and the error was in the definition and propagated to Eq.12 and 13.
+\textbf{Answer:} Thank you for noticing it. The typo is corrected.
 
@@
 \textbf{Answer:} Thank you for corrections.
-We corrected the sign before normal component and added the better explanation in Appendix.
+We corrected the sign before the normal component and added a better explanation in  the Appendix.
 In fact, the free slip is indeed simulated  - one can see the streamlines in the reference frame moving with the bubble.
@@
 \textbf{Answer:} We rewrote the caption text to the figure to explain better.
-All the lines are close to each other and that's the thought we want to deliver.
-If some lines are laying apart then the simulations produce different results, thus scaling procedure is not consistent.
+All the lines are close to each other and that's the message we want to deliver.
+If some lines are laying apart then the simulations produce different results, and the scaling procedure is not consistent.
 
@@
 
-\textbf{Answer:} Thank you for improving readability of the article.
+\textbf{Answer:} Thank you for improving the readability of the article.
 We wanted to say that parameters indicated in Table 2  give $Pe=14041$.
@@
 In simulations we see that simulations are unstable with the velocity pattern for $Ca=1.040$ and $Pe=14041$.
-This is the reason that we decrease Peclet number (or $Sc=794.84/5=158.96$)  by increasing diffusion parameter $D$ by $5$ times.
+This is the reason that we decrease the Peclet number (or $Sc=794.84/5=158.96$)  by increasing the diffusion parameter $D$ by $5$ times.
 The high $Pe$ and $Sc$ numbers simulations are difficult to perform not only with the LBM, but with the Volume of Fluid Method as well \cite{onea-mass}.
@@
 
-\textbf{Question:} Table 1 - I did not find what $epsilon_gas$ means. Is it the gas holdup?
+\textbf{Question:} Table 1 - I did not find what $\epsilon_{gas}$ means. Is it the gas holdup?
 

### 2012-12-22 Text/Final/introduction.tex
Did answers.tex

@@
 flow for capillary numbers $0.1 < Ca < 1.0$. We address the case where the hydrodynamic pattern changes from having a
-vortex in a slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.  In the latter case
+vortex in the slug ($Ca<0.7$) to not having it ($Ca>0.7$) \cite{giavedoni-numerical}.  In the latter case
 the bubble shape is asymmetric and cannot be approximated through flat surfaces and circular circumferences as
@@
  properties which cannot be achieved
-in its macroscopic counterparts: liquid thin films \cite{bretherton} between bubbles and walls strongly enhance mass
+in its macroscopic counterparts: thin liquid films \cite{bretherton} between bubbles and walls strongly enhance mass
 transfer from gas and walls to liquid; the plug flow regime occurring in monolith reactors allows to perform chemical reactions in slugs only \cite{kreutzer-overview}.

### 2012-12-24 Text/Final/introduction.tex
After revision - submission is done. Hopefully, it's final.

@@
 symmetrical and can be approximated with good precision. Moreover, because of the
-hydrodynamic pattern in the slug (i.e. presence of a vortex in slug), one can
+hydrodynamic pattern in the slug (i.e. presence of a vortex in the slug), one can
 estimate the time for a fluid batch to travel the whole circumference.   However,
@@
 \citet{onea-mass} only takes into account short length bubbles in microchannels
-with a square cross section. As well, in this work  the Schmidt number around $0.8$ is  used:
+with a square cross section. As well, in this work  a Schmidt number of around $0.8$ is  used:
 thus, the thickness of the concentration and momentum boundary layer is similar
-leading to qualitative results.} The usual simulation of mass transfer is
+leading to qualitative results since it's not possible to separate mixing due to hydrodynamics patterns from mixing due to diffusion.}
+
+The usual simulation of mass transfer is
 performed as follows: 
@@
 The case we want to examine is a two-dimensional bubble train flow between parallel plates.
-We address the following issues:
+We address the following:
  \begin{description}
@@
 The paper is organized as follows. We start with definitions of the volumetric mass transfer coefficient and apply them 
-to the bubble train flow to derive expressions to connect the space- and time-averages.  Then, the lattice
+to  bubble train flow in order to derive expressions to connect space- and time-averages.  Then, the lattice
 Boltzmann model used to simulate mass transfer is presented, followed by benchmarks. Finally,
@@
 $\Bigl[m^2\Bigr]$, and $\Delta C$ is the concentration difference between the surface and the surrounding medium
-$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has a dimension of 
+$\Bigl[\frac{kg}{m^3}\Bigr]$. Therefore, $k_L$ has units of 
 $\Bigl[\frac{m}{s}\Bigr]$. Usually, the surrounding medium concentration is taken at an infinite distance
@@
 \feq 
-giving the same solution but only in the spatial domain:
+giving the same solution, now in the spatial domain:
 \beq
@@
 the same as in the first case. One can connect  time and space with the
-velocity $U$ ($t=\frac{x}{U}$) to obtain the same equation as in the case 2.
+velocity $U$ ($t=\frac{x}{U}$).  %to obtain the same equation as in the case 2.
 \end{enumerate}
@@
 \subsection{Bubble train}
-In the application to the bubble train flow it is useful to think of one bubble as a point
+In the application to bubble train flow it is useful to think of one bubble as a point
 source to be able to use the calculations presented above. For example, the expression
@@
 contributions from film and bubble caps can be calculated separately.
-Therefore no tracer from the film influences bubble caps diffusion.
+Therefore, tracer from the film does not influence bubble caps diffusion.
 However, this assumption overpredicts mass transfer for a number of experiments \cite{irandoust}.
@@
 $\langle C(t) \rangle$ such as the concentration averaged over the whole domain or inlet/outlet space-averaged
-concentrations used in works \cite{vanbaten-circular,kreutzer-overview}.  
+concentrations as used in \cite{vanbaten-circular,kreutzer-overview}.  
 %Note that $C(x)$ is not averaged in time as $\overline{C(x)}$ since $C(x)$
@@
 periodic boundary conditions, see Fig. \ref{fig:benchmark}. In this case no tracer leaves the
-domain similarly to the plug flow. 
+domain similarly to plug flow. 
 %From the physical point of view this case resembles the mass transfer for small Capillary numbers
@@
 \includegraphics[width=\textwidth]{benchmark_middle.eps}\\
-\caption{The two-dimensional benchmarks for the  the mass transfer
-coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
-(bottom). \label{fig:benchmark}}
+\caption{The two-dimensional benchmark for the  the mass transfer
+coefficient for the bubble located at the middle of the domain. \label{fig:benchmark}}
 \end{figure}
@@
 
-Periodic boundary conditions are the extreme
-limiting case of Eq. \ref{main:main:main}: 
+With periodic boundary conditions: 
 \beqstar
@@
 \feqstar
+In this case, Eq. \ref{main:main:main} reduces to Eq. \ref{eq:vanbaten:formulation}.
+
 %Then the mass change in the domain arises only because of the bubble
@@
 The lattice Boltzmann equation (LBE) operates on a square/cubic grid representing the
-physical domain {\color{red} in the non-dimensional space} (hereafter we use subscript LB to denote non-dimensional quantities). It utilizes
+physical domain {\color{red} in non-dimensional terms} (hereafter we use subscript LB to denote non-dimensional quantities). It utilizes
 probability distribution functions (also known as particle populations)
@@
 \end{equation}
-where $\bar{i}$ is the opposite direction to the $i$-th direction.
+where $\bar{i}$ is the direction opposite to the $i$-th direction.
 The collision is performed with two independent relaxation rates for 
@@
 This free parameter controls the effective location of  bounce-back
-walls \cite{ginzburg-multireflection}, second-order accuracy of
+walls \cite{ginzburg-multireflection}, second-order accuracy of the
 boundary \cite{ginzburg-boundary-main} and interface schemes \cite{ginzburg-discontinious}, 
@@
 Boltzmann scheme are connected with  physical parameters only through  non-dimensional
-numbers governing the physics of the problem. In our case, this number is the Peclet number, $Pe=\frac{\ububble L}{D}$.
+numbers governing the physics of the problem. In our case, this  is the Peclet number, $Pe=\frac{\ububble L}{D}$.
 Therefore, one can choose any quantity, for example 
@@
 % while still obtaining meaningful results. 
-This point will be used in simulations and covered later.
+This point will be used in the simulations and covered later.
 
@@
 (mass transfer to the liquid with the parabolic velocity profile  and mass transfer from a cylinder). 
-{\color{red} As soon as we move to numerical simulations, all quantities are non-dimensional. Thus, we drop the subscript $LB$ for simplicity reasons.}
+{\color{red} As soon as we move to numerical simulations, all quantities are non-dimensional. Thus, we drop the subscript $LB$ for brevity.}
 
@@
 
-The solution depends only on the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$  lattice units. Some results for
+Time dependency goes via the non-dimensional time: $\tau=\frac{D t}{a^2}$. The domain size was $129\times 129$ with the circle radius $a=40$  lattice units. Some results for
 different diffusion coefficients are presented in Fig.\ref{fig:cylinder:benchmark}.
@@
 \ref{fig:parabolic:comparison}. Parameters were taken as: $D=0.0185$, the grid dimension is $80\times1600$. The centerline velocity is  $U_0=0.05$
-which yields the Peclet number $Pe=U_0 \delta / D= 108.108$.
+which yields the Peclet number $Pe=U_0 \delta / (2 D)= 108.108$.
 The results are in good agreement. The simulations capture accurately the singular derivative for $x=0$.
@@
 bubble shape using the phase indicator $\phi\leq0$, and approximate the bubble shape by the stair-case
-line with imposed free-slip boundary condition on it. The obtained bubble velocity is then imposed on the walls. This corresponds to conducting 
+line with imposed free-slip boundary condition on it. The bubble velocity is then imposed on the walls. This corresponds to conducting 
 simulations in the reference frame moving with the bubble. Appendix \ref{appendix-free-surface} covers the simple
@@
 one-component free-slip simulations. All quantities such as superficial slug and liquid velocities are
-within $3\%$ for the capillary number in the range $0.05\leq Ca \leq 1.0$. 
+within $3\%$ for all capillary numbers in the range $0.05\leq Ca \leq 1.0$. 
 One can see in Fig. \ref{fig:streamlines:tweaked:velocity} two streamline profiles for $Ca=0.097$  and $Ca=1.040$.
@@
 
-\item[Mass transfer] After improved velocity profiles are obtained one can perform any mass
-transfer simulations with the various boundary conditions as covered in Section \ref{section:cases}.
+\item[Mass transfer] After the improved velocity profiles are obtained one can perform any mass
+transfer simulation with the various boundary conditions as covered in Section \ref{section:cases}.
 For this purpose one needs to match the Peclet number $Pe$ taken from experiments. 
@@
 A typical mass transfer simulation (domain size is $3000\times202$ cells) for $10^{6}$ iterations takes around $24$ hours on an Intel dual core CPU with the internal clock frequency of $2$ GHz.
-All simulations (serial for one unit cell and parallel for a few unit cells simulation) are done using computers of the WestGRID high-performance clusters in Western Canada.
+All simulations (serial for one unit cell and parallel for a few unit cells) are done using computers of the WestGRID high-performance clusters in Western Canada.
 }
@@
 One can see that the Schmidt number, $Sc=Pe/Re\approx 790$, has a value corresponding to a dye with a low molecular diffusivity.
-This is done to minimize the dye diffusion influence on results but rather study the mass transfer in hydrodynamics patterns provided by Taylor bubble flow.} Periodic
+This is done to minimize the dye diffusion influence on results but rather study the mass transfer in hydrodynamics patterns provided by the Taylor bubble flow.} Periodic
 boundary conditions were used and the mass transfer coefficient was calculated according to Eq.
 \ref{main:simulation:equation}. 
-{\color{red} One can see} in Table \ref{table:scaling:peclet} for small capillary numbers ($Ca<0.2$)  it is possible to scale up velocity significantly ($20-40$ times) to obtain a velocity around $0.2$ where simulations are still stable.
+{\color{red} One can see} in Table \ref{table:scaling:peclet} that for small capillary numbers ($Ca<0.2$)  it is possible to scale up velocity significantly ($20-40$ times) to obtain a velocity around $0.2$ where simulations are still stable.
 However, for larger capillary numbers the scale up is smaller ($2-4$ times), and the velocity for stable simulations is around $0.1$.
@@
 Results for the coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
-\ref{fig:aver:conc:different:capillaries} for different Peclet numbers and velocity scalings
+\ref{fig:aver:conc:different:capillaries} for different capillary, Peclet numbers and velocity scalings
 indicated in Table \ref{table:scaling:peclet}. When the average concentration gets
-close to $\cstar=1$ then Eq. \ref{theor:one:concentration:time} gives inadequate results due to
+close to $\cstar=1$, Eq. \ref{theor:one:concentration:time} gives inadequate results due to the 
  accuracy of the logarithmic function evaluation. This is the reason that curves in Fig. \ref{fig:aver:conc:different:capillaries}
@@
 Due to velocity scaling
-each simulation has a different physical time step. Thus, we normalized time such that it represents a number of unit cell lengths which the bubble will pass, i.e. 
+each simulation has a different physical time step. Thus, we normalized time such that it represents a number of unit cell lengths which the bubble has travelled, i.e. 
 $N_{\text{cell\,units}}=\frac{\text{scale}\cdot \ububble\cdot N_{\mathrm{iter}}}{\lunit}$.  Fig.
@@
 cells) is required to achieve  steady state. For example, for
-larger Peclet numbers fewer iterations are required to achieve the steady state condition.
+larger Peclet numbers fewer length is required to achieve the steady state condition.
 
@@
 \includegraphics[width=0.5\textwidth]{aver_conc_scale_ca14.eps}
-\caption{Volumetric mass transfer coefficient for different capillary numbers and scales against the
-bubble travel distance in the laboratory frame. ''Cell Units`` axis refers to the physical
-distance of how many unit cells the bubble travels until the steady state is reached.
+\caption{Volumetric mass transfer coefficient for different capillary numbers and velocity scales against the
+bubble travel distance in the laboratory frame. The ''Cell Units`` axis refers to the physical
+distance in unit cells lengths the bubble travels.
 A legend is provided for velocity scalings.
@@
 \ref{table:steady:state:average}
-summarizes results presented here.  \label{fig:aver:conc:different:capillaries}}
+summarizes the results presented here.  \label{fig:aver:conc:different:capillaries}}
 \end{figure}
@@
 $Ca=0.097$ has the same value as for the simulations of a few unit cells.
-Therefore the approach of \citet{vanbaten-circular} produces  accurate results but if the characteristic concentration is the volume-averaged concentration (not the inlet/outlet flux-averaged concentration used in the original work).
+Therefore the approach of \citet{vanbaten-circular} produces  accurate results if the characteristic concentration is the volume-averaged concentration (not the inlet/outlet flux-averaged concentration used in the original work).
 From the computational point of view, it also requires the concentration fields in time and space to calculate the mass change in time and the averaged domain
@@
 the average concentration. Moreover, the values are closer to values obtained with many cell
-simulations, see Fig. \ref{fig:moving:average:ca0097}, than in comparison with periodic boundary
-simulations in Section \ref{main:results:periodic}. However, the characteristic concentration
+simulations, see Fig. \ref{fig:moving:average:ca0097}, than with periodic boundary
+simulations in Section \ref{main:results:periodic}. The characteristic concentration
 being inlet/outlet flux-averaged does not produce consistent results.
@@
 the physical system being modelled, one can simulate several unit cells, corresponding
-to a head of the bubble train.  If end effects are eliminated then the average
+to the head of a bubble train.  If end effects are eliminated then the average
 domain characteristic should change in time according to Eq.
@@
 \caption{Results for $6$ unit cells. The Peclet number is $Pe=2644$.
-One can see that average concentrations reach certain value and stay constant.
+One can see that the average concentrations reach a certain value and stay constant.
 %That means whatever was
@@
 reach the steady volumetric concentration fast and start decaying after that. It is not convenient
-to use them in practical cases for unmixed slug, i.e. $Ca>0.7$. \label{fig:periodic:ca1040}}
+to use them in practical cases for unmixed slugs, i.e. $Ca>0.7$. \label{fig:periodic:ca1040}}
 \end{figure}
@@
   bubbles flowing between parallel plates. However, an interesting
-correlation for the mass transfer volumetric coefficient was presented by
+correlation for the volumetric mass transfer coefficient was presented by
 \citet{yue-mass} for three-dimensional microchannel geometries:
@@
 \ref{table:steady:state:average}. The coefficients are close to each other, especially given that
-the correlation by \citet{yue-mass} is for three-dimensional cases. The fitting procedure for this work results showed
+the correlation by \citet{yue-mass} is for three-dimensional cases. The fitting procedure based on the results of this work showed
 that the power of
@@
 a few unit cells simulations performed in the reference frame moving with the
-bubble.  We thoroughly examined and performed simulations with different
+bubble.  We thoroughly performed and examined simulations with different
 definitions of the volumetric mass transfer coefficient and characteristic

### 2012-12-24 Benchmarks/cylinder.cpp

@@ -37,7 +37,7 @@ int *bottom;
 int *top;
 
 //BGK relaxation parameter
-double omega=1.0/(0.5+0.5/1.0); ///1.99;
+double omega=1.0/(0.5+0.5/32.0); ///1.99;
 double omega_plus=2.0-omega;
 double omega_minus=omega;
 

### 2012-12-24 Python/benchmarks.py

@@ -5,7 +5,7 @@ import scipy.special
 import math
 #import matplotlib.tri as tri
 
-coeff=1
+coeff=32
 omega=1.0/(0.5+0.5/coeff)
 radius=39
 diffusion=1.0/3.0*(1.0/omega-0.5)
@@ -50,7 +50,7 @@ def read_files(file_dir):
     legs=numpy.ravel(legs)   
     pylab.title(r'''$D='''+str(diffusion)[0:6]+'''$''',fontsize=30)
     pylab.legend(legs,fancybox=True,loc=2)
-    pylab.xlabel(r'''$r$''',fontsize=20)
+    pylab.xlabel(r'''$r/a$''',fontsize=20)
     pylab.ylabel(r'''$C$''',fontsize=20)
     #pylab.legend(legs,fancybox=True,labelspacing=0.1)
     pylab.savefig("cylinder"+str(diffusion)[2:6]+".eps",dpi=300)        
@@ -1098,7 +1098,7 @@ if __name__=="__main__":
 
     #read_file(file_name)
     
-    #read_files(file_dir)
+    read_files(file_dir)
     #show_bessel()    
     #read_film(file_dir)    
     #film_analytical()    
@@ -1111,6 +1111,6 @@ if __name__=="__main__":
     #check_irandoust(file_dir)    
     #comparison_two_analytics(file_dir)    
     #irandoust_construction(file_dir)    
-    final_comparison()
+    #final_comparison()
     #final_comparison_zero_gradient()    
     pylab.show()
